### 2020-05-07 paper/authors.tex
init commit paper

\correspondingauthor{L.\,G.\,Bouma}
\email{luke@astro.princeton.edu}

%
% key authors:
%

\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

%PENDING
\author[0000-0002-9158-7315]{R. Brahm}
\affiliation{Center of Astro-Engineering UC, Pontificia Universidad
Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, 782-0436 Macul,
Santiago, Chile}
\affiliation{Instituto de Astrof\'isica, Facultad de F\'isica,
Pontificia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna
4860, 782-0436 Macul, Santiago, Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

\author[0000-0001-8732-6166]{J. D. Hartman}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

%PENDING
\author{J. de Leon}
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}

%
% SG1 contributors: ask Karen -- are there others?
%
%PENDING
\author{P. Evans}
\affiliation{El Sauce Observatory, Coquimbo Province, Chile}

%PENDING
\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%
% SG2 contributors
%
%PENDING
\author[0000-0002-4891-3517]{G. Zhou}
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%PENDING
\author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

%
% SG4 contributors
%
\author[0000-0002-0619-7639]{C.~Ziegler}
\affiliation{Dunlap Institute for Astronomy and Astrophysics,
University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4,
Canada}

%
% UToyko team
%
%PENDING
\author[0000-0002-4881-3620]{J. Livingston}
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}

%
% MPIA team
%
%PENDING
\author{T. Henning}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17,
69117 Heidelberg, Germany}

%PENDING
\author[0000-0002-5389-3944]{A. Jord\'an}
\affiliation{Facultad de Ingenier\'ia y Ciencias, Universidad Adolfo
Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago,
Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

%PENDING
\author[0000-0001-9513-1449]{N. Espinoza}
\affil{Space Telescope Science Institute, 3700 San Martin Drive,
Baltimore, MD 21218, USA}

%
% Princeton team
%
%PENDING
\author[0000-0002-0628-0088]{W. Bhatti}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J. N. Winn}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0001-7204-6727]{G. \'A. Bakos}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%PENDING
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for Astrophysics
and Space Research, Massachusetts Institute of Technology, Cambridge, MA
02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%PENDING
\author{S. Seager} % seager@mit.edu
\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
%
%PENDING
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

\author{TSO/SPOC/POC representatives}

### 2020-05-07 paper/ms.tex
init commit paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\newcommand{\tn}{TOI~837} % target star name
\newcommand{\pn}{TOI~837.01} % planet name
\newcommand{\cn}{IC~2602} % cluster name

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

\begin{document}

\defcitealias{bouma_wasp4b_2019}{B19}

\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602}

\input{authors.tex}

\begin{abstract}
We report the discovery of the transiting planet TOI 837.01,
a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602, also known as the
``Southern Pleiades'', and is therefore 50 million years old.
We characterize the system using data from the NASA {\it Transiting
Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
XXX/FEROS, and AAT/Veloce.
TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
bright host stars, and is amenable for studies of planetary
atmospheric and orbital evolution.
\end{abstract}

\keywords{
	Exoplanets (XXX),
	Exoplanet evolution (491),
	Stellar ages (1581),
	Young star clusters (XXX)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Recently, young planets have been hype.

Section~\ref{sec:observations} 
Section~\ref{sec:star}
Section~\ref{sec:planet}
Section~\ref{sec:discussion}
Section~\ref{sec:conclusions}.

\section{The Data}
\label{sec:observations}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS lightcurve of \tn\ (Sectors 10 and 11).}
		{\it Top}: \texttt{PDCSAP} mean-subtracted relative flux at 2-minute
		sampling. Spot-induced stellar variability is the dominant signal.  Dashed
		lines show the five transits observed by TESS.
    {\it Bottom}: Zoomed windows of individual transits.
		\label{fig:rawzoom}
	}
\end{figure*}

\subsection{TESS Photometry}

\tn\ (TIC 460205581, GAIA DR2 5251470948229949568) was observed by the
TESS spacecraft from X to Y in two-minute cadence mode.

Figure~\ref{fig:rawzoom}.

\subsection{Ground-based Time-Series Photometry}

\subsection{Imaging}

\subsection{Spectroscopy}

\subsubsection{CHIRON}
9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
6 were usable.

\subsubsection{FEROS}
N spectra with XXX/FEROS

\subsubsection{Veloce}
M spectra with AAT/Veloce.

\subsection{Astrometry}

\section{The Star}
\label{sec:star}

\subsection{The Cluster}
\label{subsec:cluster}

% NOTE: might want a table of all ages

IC~2602 canonically has an age of $30\pm20\,{\rm Myr}$ (CITE: Van
Leeuwen 2009).
Or logage between 7.533 and 7.563	\citep{bossini_age_2019}.

Or Li age of 40-50Myr (David+19, comparison with other Li stars).

Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range between
slightly super-solar ($0.04\pm0.01$, \citealt{baratella_gaia-eso_2020}) and
slightly sub-solar ($-0.02 \pm 0.02$, \citealt{netopil_metallicity_2016}).

IC~2602 is supervirial, in the sense that the observed stellar velocity
dispersion is larger than the value expected if it were in virial equilibrium
by about a factor of two \citep{bravi_gaia-eso_2018}.

\subsection{Cluster Membership}
\label{subsec:member}

The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
Veloce) is strong; the rotation period and vsini agree with
sub-Pleiades age expected for an IC 2602 member.

\subsubsection{Kinematics}

Gaia

\subsubsection{Rotation}

TESS photometric rotation period = 3.5days ish.

vsini = 17.48 $\pm$ 0.15 (CHIRON).

The two agree.

For comparison, gyrochrones would predict X.XX.

This implies sub-Pleiades age expected for an IC 2602 member.

\subsubsection{Lithium}

Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
154 milliangstrom (see attached).

As a reminder, Teff=6100K (TICv8). 
Or Teff = 5946 $\pm$ 39 (CHIRON).
Rafael, if you have a better
determination of Teff, it would be helpful!  SpType is early-G,
late-F from your quicklook spectral typing earlier.

Relevant colors are V-K = 1.7,  V-I ~= V-T = 0.7

Summarizing relevant lithium facts:

Lithium depletion for a star of TOI-837's spectral type happens
over timescales >100 Myr (Soderblom+2013). This is because the
convective envelopes are very shallow, so they don't cycle material
down to the >3e6 K core until much later.

Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
Hyads shows that the depletion does happen over gigayear timescales
(Berger+2018, fig 7).

Comparing to the Li EWs measured by Berger+2018 (their Fig 5),
TOI-837 is consistent with being younger than almost all CKS
planet-hosting field stars.

The TOI-837 Li EW measured here (150 milliangstrom) is consistent
with what's seen for stars of similar colors in <100 Myr old moving
groups (Elliott+2016, Fig 11 -- attached).  This is sensible, because
IC 2602 is supposed to be 50 Myr old.

\subsubsection{Literature Membership}
The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
in what they dubbed ``Group 5''.
Analyzing the clusters of \citet{oh_comoving_2017},
\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
WISE photometry with MIST isochrones, and reported stellar masses,
radii, metallicities, ages, distances, and extinction for 9754 stars,
including \tn.

\tn\ was also listed as a member of ``Theia 92'' by
\citet{kounkel_untangling_2019}.
These authors identified 999 candidate cluster members, and
reported a cluster isochrone age $\log t = 7.55$ with uncertainty
$\approx 0.15\,{\rm dex}$.

\subsection{Stellar Parameters}

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f6.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Spectral energy distribution of \tn\ from archival
    photometry.}
    {\bf Keivan: please describe!}
    \label{fig:sed}
	}
\end{figure}

\subsubsection{Physical}
 (Lstar, Rstar, Teff, Age and Mstar)

Figure~\ref{fig:sed}.

\paragraph{Astrometric information}
The RUWE (CITE, CITE) for \tn\ is 1.02, indicative that there are no
obviously present astometric companions.

\subsubsection{Rotation}
Stellar vsini
Stellar rotation

\subsection{RVs}
I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
mass measurement. The reason is that with vsini=17km/s, and 2\%
rotation amplitude signal, we expect an RV RMS of 300m/s at the
Prot=3.5 day rotation period (vsini*rotation amplitude). This is
probably larger than the expected planet signal (100m/s, 8 days).

\section{The Planet}
\label{sec:planet}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$, scaled such that
    brighter stars are larger. The \texttt{X} and \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale. The circles show
    apertures of radii 1, 1.5, and 2.25 pixels used in our blend
    analysis (Section~\ref{subsec:validation}).  Two stars of interest
    are ``Star A'' and ``Star B'', which were eventually excluded as
    being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
		{\bf SOAR HRCam contrast limits derived from point-source
			injection-recovery experiments.} 
      Star A ($\Delta T=4.7$, $\rho=2.3$'' west) is detected in the
      autocorrelation function, in addition to being a resolved Gaia
      source.
      It is co-moving with \tn, and
      its parallax and on-sky position imply that
      it is physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		\label{fig:soar}
	}
\end{figure}

\subsection{Transit Fitting}
Simultaneous dip plus rotation period (GP) fit. Use celerite plus PyMC3/exoplanet.
Mention FPP?

\subsection{Validation of \pn}

Exclude possibilities:
"The transits are blended from a background, unassociated eclipsing binary
system or transiting exoplanet: We take the same approach outlined in
Vanderburg et al. (2019). In short, if the transits are a blend from the
background system, the true radius ratio is constrained by the ratio of the
ingress time (T12) to the..."

\subsubsection{Visual Binarity}
Figure~\ref{fig:scene} shows the scene.
In the upper panels, the pixels used to measure the background level
in the SPOC lightcurve are indicated with `\texttt{X}' hatching, and
the pixels used in the final lightcurve aperture are shown with
`\texttt{/}' hatching.

Stars brighter than $T=16$, as queried from the Gaia DR2 source
catalog, are shown with orange circles.
The relevant stars for a blend analysis are as follows.
\begin{itemize}
  \item \tn\ = TIC 460205581 (T=9.9). The target star.
  \item Star A = TIC 847769574 (T=14.6). $2.3$'' west. Proper motions
    and parallax imply it is comoving with \tn, though with a physical
    separation of $6.6\pm 0.1\,{\rm pc}$, it may not be bound.
  \item Star B = TIC 460205587 (T=13.1). $5.4$'' north.  This is a
    giant background star.
\end{itemize}
An additional source, TIC 847769581, is $4.9$'' from the target, but
too faint (T=18.8) to be the source of the observed transit signal.

The Gaia DR2 data for Star A seems somewhat poorly behaved.  While
Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE value is available (CITE).  The astrometric
reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
astrometric observations) seems rather poor, at $8.6$.  We suspect
that the photometric failure to produce an $Rp$ magnitude, as well as
the poor astrometric fit, are likely due to blending with \tn.

At the angular resolution of the TESS data, if either Star A or Star B
were eclipsing binaries, they could be the sources of the transit
signal.  Coincidence stellar sources below the resolution limit of
Gaia are also a concern (CITE). To rule out these possibilities, we
took a number of approaches.

\subsubsection{High-resolution imaging}

We imaged the system using SOAR-HRCam.
{\bf Carl: please describe}.
Figure~\ref{fig:soar}.
\citet{ziegler_soar_2020}

\subsubsection{TESS analysis}

We examined the CDIPS FFI lightcurves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three lightcurves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels.  In the raw difference-image light-curves, as well as the
PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
and their properties do not significantly vary with aperture size.
Within $\approx20$'', the dips are consistent with originating from
the target star.

\subsubsection{Seeing-limited time-series photometry}

%FIXME:
{\bf left off here}
Co-author P{.} Evans obtained a total transit that showed that, within
1.5'', the transit comes from \tn.  We can be even more certain with a
pixel-level analysis. This 2.1 arcsec neighbor is also a mid to late M
dwarf, and bound given the Gaia parallax + proper motion. The transit
duration is rather long for the signal to come from the M dwarf,
rather than the G dwarf.  I think the state of photometric followup
could be improved (there is only one good total transit), but I think
over this month and next we can pull another few partials.

A total eclipse of Ziegler's faint companion would produce a 1.4\%
dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
dips at exactly the right depth (0.4\%).

\subsubsection{Summary}

Possible false-positive scenarios are as follows.

\begin{itemize}
  \item {\it Neighboring blends}.

  \item {\it Hierarchical blends}.
    Limited by i) FEROS + Veloce RVs, and ii) the star being nicely on the
    cluster HR diagram. Any extra hidden close-in binary stars would
    need to be very low-mass M dwarfs, and then the transit duration
    again helps.

  \item {\it Background blends}.
  Archival imaging (POSS) available in the south?
\end{itemize}

\subsection{Additional Companions}

None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
spikes at BTJD 1572 and 1601) seem likely to be planetary
We checked that i) they were not present in the SAPFLUX light-curves,
and ii) that they were not present in the CDIPS light-curves (either
raw, or PCA-detrended).

To make this quantitative, we did injection-recovery.

\section{Discussion}
\label{sec:discussion}

In context,...

\section{Conclusions}
\label{sec:conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
  \texttt{IPython} \citep{perez_2007},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  %\texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}

\facilities{
 	{\it Astrometry}:
 	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}.
 	{\it Imaging}:
  Second Generation Digitized Sky Survey,
 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
 	{\it Spectroscopy}:
 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
% 	Euler1.2m~(CORALIE),
% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
 	{\it Photometry}:
% 	CTIO:1.0m (Y4KCam),
% 	Danish 1.54m Telescope,
% 	El Sauce:0.356m,
% 	Elizabeth 1.0m at SAAO,
% 	Euler1.2m (EulerCam),
% 	Magellan:Baade (MagIC),
% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
% 	NTT,
% 	SOAR (SOI),
 	TESS \citep{ricker_transiting_2015}.
% 	TRAPPIST \citep{jehin_trappist_2011},
% 	VLT:Antu (FORS2).
}

%
% The following are entries from Table 1 that are not otherwise cited
% in the text
%
% \nocite{wilson_wasp-4b_2008}
% \nocite{gillon_improved_2009}
% \nocite{winn_transit_2009}
% \nocite{hoyer_tramos_2013}
% \nocite{dragomir_terms_2011}
% \nocite{sanchis-ojeda_starspots_2011}
% \nocite{nikolov_wasp-4b_2012}
% \nocite{ranjan_atmospheric_2014}
% \nocite{huitson_gemini_2017}

% \input{WASP-4b_transit_time_table.tex}
% \input{WASP-4b_rv_table.tex}
% \input{model_fit_table.tex}
% \input{rv_model_posterior_table.tex}
% \input{pdot_table.tex}

\clearpage
\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage

\bibliographystyle{yahapj}                            
\bibliography{bibliography}

\listofchanges

\end{document}

### 2020-05-07 paper/collect.sh

@@ -1,0 +1,27 @@
+# Usage: copy in figures for the paper
+
+pdir=../results/paper_plots/
+
+cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
+
+# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_splitsignalmap_ii.pdf f2.pdf
+# 
+# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_phasefoldmap.pdf f3.pdf
+# 
+
+cp ${pdir}scene.pdf f3.pdf
+
+cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.pdf
+
+cp ${pdir}toi_837_sed.png f6.png
+
+# 
+# cp ../results/cluster_membership/hr.pdf f5a.pdf
+# cp ../results/cluster_membership/astrometric_excess.pdf f5b.pdf
+# 
+# cp ../results/ephemeris/O_minus_C.pdf f6.pdf
+# 
+# cp ../results/brethren/brethren.pdf f7.pdf
+# 
+# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_cornerplot.png f6.png
+# pngquant f6.png --output f6_comp.png

### 2020-05-08 paper/collect.sh
update paper

@@ -4,6 +4,8 @@ pdir=../results/paper_plots/
 
 cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
 
+cp /Users/luke/Dropbox/proj/timmy/results/TOI_837_transit_phot_results/20200506/TOI_837_transit_phaseplot.pdf f2.pdf
+
 # cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_splitsignalmap_ii.pdf f2.pdf
 # 
 # cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_phasefoldmap.pdf f3.pdf

### 2020-05-08 paper/ms.tex
update per phase-fold

@@
 
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.48\textwidth]{f2.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Phase-folded transit of \pn.} Gray points are
+    2-minute PDCSAP flux measurements, detrended with
+    a 0.3-day robust Huber spline (see Section~\ref{subsec:tess}).
+    Black points are binned to approximately 1 point per 6 minutes.
+    One hundred samples from the posterior are shown with orange lines.
+    % The bottom panel shows the residuals.
+    \label{fig:phasefold}
+	}
+\end{figure}
+
 \subsection{TESS Photometry}
+\label{subsec:tess}
 
@@
 TESS spacecraft from X to Y in two-minute cadence mode.
+
+%TODO: describe 0.3-day robust Huber spline
 

### 2020-05-08 timmy/plotting.py

@@ -3,15 +3,10 @@ Plots:
 
     plot_quicklooklc
     plot_raw_zoom
-
     plot_phasefold
-
-    plot_phasefold_post
-    #FIXME FIXME ... I think this is what's wanted.
 
     plot_MAP_data
     plot_sampleplot
-    plot_phasefold_map
     plot_traceplot
     plot_cornerplot
 
@@ -325,102 +320,6 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     savefig(fig, outpath, writepdf=1, dpi=300)
 
 
-def plot_phasefold_map(m, d, outpath):
-
-    if os.path.exists(outpath) and not m.OVERWRITE:
-        return
-
-    # recover periods and epochs.
-    P_rot = 2*np.pi/float(m.map_estimate['omegarot'])
-    t0_rot = float(m.map_estimate['phirot']) * P_rot / (2*np.pi)
-    P_orb = float(m.map_estimate['period'])
-    t0_orb = float(m.map_estimate['t0'])
-
-    # phase and bin them.
-    orb_d = phase_magseries(
-        d['x_obs'], d['y_orb'], P_orb, t0_orb, wrap=True, sort=True
-    )
-    orb_bd = phase_bin_magseries(
-        orb_d['phase'], orb_d['mags'], binsize=0.01
-    )
-    rot_d = phase_magseries(
-        d['x_obs'], d['y_rot'], P_rot, t0_rot, wrap=True, sort=True
-    )
-    rot_bd = phase_bin_magseries(
-        rot_d['phase'], rot_d['mags'], binsize=0.01
-    )
-
-    # make tha plot
-    plt.close('all')
-    fig, axs = plt.subplots(nrows=2, figsize=(6, 6), sharex=True)
-
-    axs[0].scatter(rot_d['phase'], rot_d['mags'], color='gray', s=2, alpha=0.8,
-                   zorder=4, linewidths=0, rasterized=True)
-    axs[0].scatter(rot_bd['binnedphases'], rot_bd['binnedmags'], color='black',
-                   s=8, alpha=1, zorder=5, linewidths=0)
-
-    txt0 = '$P_{{\mathrm{{\ell}}}}$ = {:.5f}$\,$d'.format(P_rot)
-    props = dict(boxstyle='square', facecolor='white', alpha=0.9, pad=0.15,
-                 linewidth=0)
-
[…]

### 2020-05-08 paper/ms.tex
update paper

@@
 
+do a 5 subplot olympic arrangement...
+
+plx vs pmdec
+plx vs pmra
+pmdec vs pmra
+plx vs rv
+ra vs dec
+
+(or could just do 2 3d plots... one of positions, one of velocities. i
+like this idea best, tbh.).
+
+...
+OR could do it as a corner plot, 6 dimensions...
+
+ra
+dec
+plx
+pmra
+pmdec
+rv
+
+this would be sicker.
+
+\subsubsection{HR Diagram}
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.9\textwidth]{f7.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ 
+  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
+  Members (black circles) were identified by
+  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
+  within 5 standard deviations of the mean \cn\ right ascension,
+  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
+  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
+  arcseconds. 
+  \label{fig:hr}
+	}
+\end{figure*}
+
+Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
+reference to the broader \cn\ cluster, as well as its neighborhood.
+Cluster members were identified by \citet{cantatgaudin_gaia_2018}
+using using Gaia-DR2 positions, proper motions, and parallaxes.  
+We included candidate members with formal membership probability
+exceeding 10\%.  Save for a few low-mass outliers, most members appear
+to be young and coeval.
+
+\tn\ is in its expected position relative to the other members along
+the cluster isochrone.  This photometrically limits the presence of
+binary companions in \tn\ system, to a magnitude difference of perhaps
+half the brightness of the target star.
+
+Figure~\ref{fig:hr} also shows that the membership census of \cn\ is
+likely incomplete.  We defined the reference ``neighborhood'' as the
+group of at most $10^4$ randomly selected non-member stars within 5
+standard deviations of the mean \cn\ 1 right ascension, declination,
+and parallax.  We queried Gaia DR2 for these stars using
+\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
+appear above the main sequence, even though they were not identified
+as 5-dimensional kinematic members through the unsupervised
+\citet{cantat-gaudin_gaia_2018} membership assignment process.
+
 \subsubsection{Rotation}
@@
 
+From CHIRON spectra, my current best guess spectroscopic parameters
+ are as follows.
+ Teff = 5946 +/- 39
+ logg = 4.48 +/- 0.03
+ feh = -0.065 +/- 0.035
+ vsini = 17.48 +/- 0.15
+
 Figure~\ref{fig:sed}.
+The SED fit, looking really good with rchi2 = 1.6:
+
+The fit parameters are: 
+Av = 0.20 +/- 0.03
+Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
+Rstar = 1.049 +/- 0.019 Rsun
+
+From the spectroscopic logg and the above Rstar, we get an independent
+mass estimate of 
+Mstar = 1.21 +/- 0.10 Msun 
+At face value, the mass seems a bit high for the radius, but I'm
+guessing that just means the spectroscopic logg is a bit too high.
 
@@
 \subsection{Validation of \pn}
+\label{subsec:validation}
 

### 2020-05-08 paper/collect.sh

@@ -1,15 +1,11 @@
 # Usage: copy in figures for the paper
 
+rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
 cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
 
-cp /Users/luke/Dropbox/proj/timmy/results/TOI_837_transit_phot_results/20200506/TOI_837_transit_phaseplot.pdf f2.pdf
-
-# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_splitsignalmap_ii.pdf f2.pdf
-# 
-# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_phasefoldmap.pdf f3.pdf
-# 
+cp ${rdir}TOI_837_transit_phot_results/20200506/TOI_837_transit_phaseplot.pdf f2.pdf
 
 cp ${pdir}scene.pdf f3.pdf
 
@@ -17,13 +13,4 @@ cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.p
 
 cp ${pdir}toi_837_sed.png f6.png
 
-# 
-# cp ../results/cluster_membership/hr.pdf f5a.pdf
-# cp ../results/cluster_membership/astrometric_excess.pdf f5b.pdf
-# 
-# cp ../results/ephemeris/O_minus_C.pdf f6.pdf
-# 
-# cp ../results/brethren/brethren.pdf f7.pdf
-# 
-# cp ${pdir}PTFO_8-8695_transit_2sincosPorb_2sincosProt_cornerplot.png f6.png
-# pngquant f6.png --output f6_comp.png
+cp ${rdir}cluster_membership/hr.pdf f7.pdf

### 2020-05-08 paper/ms.tex
update paper

@@
 
+TESS \citep{ricker_transiting_2015}.
+
 Section~\ref{sec:observations} 
@@
 
-\tn\ (TIC 460205581, GAIA DR2 5251470948229949568) was observed by the
+\tn\ (GAIA DR2 5251470948229949568) was observed by the
 TESS spacecraft from X to Y in two-minute cadence mode.
+The star was designated
+TIC\,460205581 in the TESS Input Catalog
+\citep{stassun_TIC_2018,stassun_TIC8_2019}.
+%FIXME make words more original
+The pixel data for an
+$11\times11$ array surrounding \tn\ were averaged into 2-minute
+stacks by the onboard computer.  Each 2048$\times$2048 image from the
+CCD was also averaged into 30-minute stacks, and saved as a ``full
+frame image'' (FFI).
+
+%FIXME make words more original
+The pixel data for an
+The 2-minute stacks for \tn\ were reduced to lightcurves by the
+Science Processing Operations Center (SPOC) at NASA
+Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
+Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
+pixels chosen to maximize the SNR of the total flux of the target
+\citep{smith_finding_2016}.  Non-astrophysical variability
+was removed by fitting out trends common to many stars
+\citep{smith_kepler_2012,stumpe_multiscale_2014}.
+
+%FIXME make words more original
+As an independent check on the 2-minute SPOC lightcurve, we examined
+the lightcurve based upon 30-minute image stacks which was produced as
+part of the Cluster Difference Imaging Photometric Survey (CDIPS;
+\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
+circular aperture with radius 1 pixel.
 
@@
 
+\tn\ has been reported as a member of \cn\ by multiple independent 
+investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
+%FIXME FIXME finish these citations
+
 The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
@@
 sub-Pleiades age expected for an IC 2602 member.
-
-\subsubsection{Kinematics}
-
-Gaia
-
-do a 5 subplot olympic arrangement...
-
-plx vs pmdec
-plx vs pmra
-pmdec vs pmra
-plx vs rv
-ra vs dec
-
-(or could just do 2 3d plots... one of positions, one of velocities. i
-like this idea best, tbh.).
-
-...
-OR could do it as a corner plot, 6 dimensions...
-
-ra
-dec
-plx
-pmra
-pmdec
-rv
-
-this would be sicker.
 
@@
 the cluster isochrone.  This photometrically limits the presence of
-binary companions in \tn\ system, to a magnitude difference of perhaps
-half the brightness of the target star.
+binary companions in the \tn\ system, to a magnitude difference of
+perhaps half the brightness of the target star.
 
-Figure~\ref{fig:hr} also shows that the membership census of \cn\ is
-likely incomplete.  We defined the reference ``neighborhood'' as the
-group of at most $10^4$ randomly selected non-member stars within 5
-standard deviations of the mean \cn\ 1 right ascension, declination,
-and parallax.  We queried Gaia DR2 for these stars using
+Figure~\ref{fig:hr} also suggests that the membership census of \cn\
+is incomplete.  We defined the reference ``neighborhood'' as the group
+of at most $10^4$ randomly selected non-member stars within 5 standard
+deviations of the mean \cn\ right ascension, declination, and
+parallax.  We queried Gaia DR2 for these stars using
 \texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
@@
 \citet{cantat-gaudin_gaia_2018} membership assignment process.
+
+\subsubsection{Position and Kinematics}
+
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.9\textwidth]{f8.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ 
+  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black),
+  and stars in the neighborhood (gray).} Members (black circles) were
+  identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
+  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
+  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
+  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
+  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
+  proper motion projection ($\mu_{\rm delta}$ vs{.} $\mu_{\rm
+  \alpha}\cos\delta$) highlights the incomplete membership selection
+  function.
+  \label{fig:full_kinematics}
+	}
+\end{figure*}
+
+We examine the six-dimensional positions and kinematics in greater
+depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
+defined here identically to as in Figure~\ref{fig:hr}.  The axes
+limits for the right ascension, declination, and parallax dimensions
+are as in the Gaia archive query.  The axes limits for the proper
+motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
+75$^{\rm th}$ percentiles, in order to give a sense of the
+population's distribution, while excluding outlying points.  The
+radial velocities suffer the greatest incompleteness due to the
+current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.
+
+Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
+existence of the \cn\ open cluster and {\it (ii)} for the membership
+of \tn\ within \cn.
+The only dimension that could perhaps lead to some worry is the
+parallax, as \tn\ is one of the closest \cn\ members reported by
+\citet{cantatgaudin_gaia_2018}.
+Fortunately, there are independent means of verifying stellar youth.
 
@@
 
+% \appendix
+% \section{Gaia query}
+% bounding by 5 stdevns
+% Launched query: '
+%         select top 10000
+%             g.source_id, g.phot_bp_mean_mag, g.phot_rp_mean_mag,
+%             g.phot_g_mean_mag, g.parallax, g.ra, g.dec, g.pmra, g.pmdec,
+%             g.radial_velocity, g.radial_velocity_error
+%         from gaiadr2.gaia_source as g
+%         where
+%             g.parallax > 5.69
+%         and
+%             g.parallax < 7.41
+%         and
+%             g.dec < -58.41
+%         and
+%             g.dec > -70.33
+%         and
+%             g.ra > 145.01
+%         and
+%             g.ra < 175.85
+%         and
+%             g.phot_g_mean_mag < 18
+%         order by
+%             random_index
+
 \listofchanges

### 2020-05-08 paper/collect.sh

@@ -14,3 +14,5 @@ cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.p
 cp ${pdir}toi_837_sed.png f6.png
 
 cp ${rdir}cluster_membership/hr.pdf f7.pdf
+
+cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf

### 2020-05-08 timmy/plotting.py

@@ -9,6 +9,7 @@ Plots:
     plot_hr
 """
 import os, corner, pickle
+from datetime import datetime
 from glob import glob
 import numpy as np, matplotlib.pyplot as plt, pandas as pd
 from numpy import array as nparr
@@ -806,16 +807,19 @@ def plot_full_kinematics(outdir):
         'radial_velocity': 'RV [km/s]'
     }
 
-    f, axs = plt.subplots(figsize=(8,8), nrows=nparams, ncols=nparams)
+    f, axs = plt.subplots(figsize=(8,8), nrows=nparams-1, ncols=nparams-1)
 
     for i in range(nparams):
         for j in range(nparams):
-            if j>i or j==i:
+            print(i,j)
+            if j == nparams-1 or i == nparams-1:
+                continue
+            if j>i:
                 axs[i,j].set_axis_off()
                 continue
 
             xv = params[j]
-            yv = params[i]
+            yv = params[i+1]
             print(i,j,xv,yv)
 
             axs[i,j].scatter(
@@ -845,13 +849,13 @@ def plot_full_kinematics(outdir):
             # fix labels
             if j == 0 :
                 axs[i,j].set_ylabel(ldict[yv])
-                if not i == nparams - 1:
+                if not i == nparams - 2:
                     # hide xtick labels
                     labels = [item.get_text() for item in axs[i,j].get_xticklabels()]
                     empty_string_labels = ['']*len(labels)
                     axs[i,j].set_xticklabels(empty_string_labels)
 
-            if i == nparams - 1:
+            if i == nparams - 2:
                 axs[i,j].set_xlabel(ldict[xv])
                 if not j == 0:
                     # hide ytick labels
@@ -859,7 +863,7 @@ def plot_full_kinematics(outdir):
                     empty_string_labels = ['']*len(labels)
                     axs[i,j].set_yticklabels(empty_string_labels)
 
-            if (not (j == 0)) and (not (i == nparams - 1)):
+            if (not (j == 0)) and (not (i == nparams - 2)):
                 # hide ytick labels
                 labels = [item.get_text() for item in axs[i,j].get_yticklabels()]
                 empty_string_labels = ['']*len(labels)
@@ -869,12 +873,34 @@ def plot_full_kinematics(outdir):
[…]

### 2020-05-11 paper/ms.tex
update paper

@@
 8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
-TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602, also known as the
-``Southern Pleiades'', and is therefore 50 million years old.
+TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
+``Southern Pleiades'') and is therefore 50 million years old.
 We characterize the system using data from the NASA {\it Transiting
@@
 	\caption{ 
-  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black),
-  and stars in the neighborhood (gray).} Members (black circles) were
-  identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
+  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
+  circles), and stars in the neighborhood (gray circles).} Members
+  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
   right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
@@
   RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
-  proper motion projection ($\mu_{\rm delta}$ vs{.} $\mu_{\rm
-  \alpha}\cos\delta$) highlights the incomplete membership selection
-  function.
+  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
+  \alpha}\cos\delta$) highlights the membership selection function.
   \label{fig:full_kinematics}

### 2020-05-13 paper/ms.tex
minor paper update
update fig1 for flares

@@
     {\it Bottom}: Zoomed windows of individual transits.
+    Red points show manually identified stellar flares.
 		\label{fig:rawzoom}
@@
 
+dmag = 4.7, transit depth is 0.4\%. This dmag converts to a flux
+fraction of 0.0132. A 30\% eclipse on T1 could therefore nominally
+explain the TESS data.  % (depth_obs = depth_true * flux fraction).
+
+However in the aperture from this green r=2px green LC, say 90\% of the
+flux from T1 is excluded. The eclipse on T1 would therefore need to be
+much deeper -- in fact, over 100\%. This argument holds as long as at
+least 70\% of the flux from T1 is excluded, so I think we're likely in
+the clear.
+
 \subsubsection{Summary}
@@
 the Oschin Schmidt Telescope on Palomar Mountain.
+%
+This research made use of the Exoplanet Follow-up Observation
+Program website, which is operated by the California Institute of
+Technology, under contract with the National Aeronautics and Space
+Administration under the Exoplanet Exploration Program.
 %

### 2020-05-13 timmy/plotting.py

@@ -281,6 +281,14 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     t_offset = np.nanmin(time)
     time -= t_offset
 
+    FLARETIMES = [
+        (4.60, 4.63),
+        (37.533, 37.62)
+    ]
+    flaresel = np.zeros_like(time).astype(bool)
+    for ft in FLARETIMES:
+        flaresel |= ( (time > min(ft)) & (time < max(ft)) )
+
     t0 = 1574.2738 - t_offset
     per = 8.32467
     epochs = np.arange(-100,100,1)
@@ -291,7 +299,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     ##########################################
 
     # figsize=(8.5, 10) full page... 10 leaves space.
-    fig = plt.figure(figsize=(8.5, 6))
+    fig = plt.figure(figsize=(8.5, 5))
 
     ax0 = plt.subplot2grid(shape=(2,5), loc=(0,0), colspan=5)
 
@@ -309,6 +317,8 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     yval = (flux - np.nanmean(flux))*1e3
     ax0.scatter(time, yval, c='k', zorder=3, s=0.75, rasterized=True,
                 linewidths=0)
+    ax0.scatter(time[flaresel], yval[flaresel], c='r', zorder=3, s=1,
+                rasterized=True, linewidths=0)
     ax0.set_ylim((-20, 20)) # omitting like 1 upper point from the big flare at time 38
     ymin, ymax = ax0.get_ylim()
     ax0.vlines(
@@ -323,16 +333,23 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
 
         mid_time = t0 + per*tra_ix
         tdur = 2/24. # roughly, in units of days
-        n = 3.5
+        n = 4.5
         start_time = mid_time - n*tdur
         end_time = mid_time + n*tdur
 
         s = (time > start_time) & (time < end_time)
+        ax.scatter(time[s], (flux[s] - np.nanmean(flux[s]))*1e3, c='k',
+                   zorder=3, s=7, rasterized=False, linewidths=0)
 
-        yval = (flux[s] - np.nanmean(flux[s]))*1e3
+        _flaresel = np.zeros_like(time[s]).astype(bool)
+        for ft in FLARETIMES:
[…]

### 2020-05-15 paper/ms.tex
paper: add some comments on BEBs and NEBs

@@
     photometry.}
-    {\bf Keivan: please describe!}
+    {\bf Keivan: please describe, and if possible, send me the data
+    (photometry + the atmosphere model) used to generate the plot so I
+    can regenerate it in a consistent style with the rest of the paper}
     \label{fig:sed}
@@
 
+Given its galactic latitude of only $-6^\circ$, it is not surprising
+that the field of \tn\ is crowded.
+A number of possible false-positive explanations, including
+the usual neighboring, background, and hierarchical eclipsing binary
+scenarios, must therefore be considered.
+
+For these scenarios to be viable, the flux from \tn\ and the true
+eclipsing binary host would blend together, reducing the ``true''
+eclipse depth $\delta_{\rm true}$ to produce the observed depth
+$\delta_{\rm obs}$:
+\begin{equation}
+  \delta_{\rm obs}
+  = 
+  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
+\end{equation}
+where the total flux and the flux from the neighbor are labelled as
+such.
+The requirement that the true eclipse depth is less than one
+translates to a bound on the faintest possible blended companion
+stars:
+\begin{equation}
+    \Delta m < - \frac{5}{2} \log_{10} \delta_{\rm obs}.
+\end{equation}
+For \tn\ ($T=9.93$), this implies that any star invoked to explain the
+transit depth must be brighter than $T=15.92$.
+
+% TODO: there's an even stronger argument advanced by Vanderburg et al
+% (2019), and used by Rizzuto+2020.
+There's also
+\begin{equation}
+  \Delta m <
+  -\frac{5}{2} \log_{10} (\delta_{\rm obs} t_{12}^2/t_{13}^2).
+\end{equation}
+
 \subsubsection{Visual Binarity}
@@
   \item {\it Background blends}.
-  Archival imaging (POSS) available in the south?
+    Archival SERC-J and AAO-SES plates are available for the \tn\
+    field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
+    These plates were acquired in 1982 and 1992, respectively.
+    For high proper motion stars archival imagery can be used to
+    detect slowly moving background stars that might be an
+    astrophysical false-positive source
+    ({\it e.g.}, \citealt{huang_pimen_2018}).
+    However \tn\ has only moved $\approx0.7''$ between 1982 and
+    present, in comparison to the $\approx2.0''$ FWHM of the target on
+    the plates.
+    We therefore cannot resolve it with great confidence from
+    background sources not already resolved through more modern
+    imaging.
+
 \end{itemize}

### 2020-05-15 drivers/calc_onsky_motion.py

@@ -1,0 +1,30 @@
+from astropy.coordinates import SkyCoord
+from astropy import units as u, constants as c
+from astropy.table import Table
+import pandas as pd
+from astropy.time import Time
+
+t = Table.read('../data/gaia_csvs/gaia_vizier_asu.fits')
+t['source_id'] = t['DR2Name'].astype(str)
+
+df = t.to_pandas()
+
+a = '5251470948229949568'
+
+adf = df[df.source_id.str.contains(a)]
+
+c = SkyCoord(ra=float(adf.RA_ICRS)*u.degree,
+             dec=float(adf.DE_ICRS)*u.degree,
+             distance=(1/(float(adf.Plx)*1e-3))*u.pc,
+             pm_dec=float(adf.pmRA)*u.mas/u.yr,
+             pm_ra_cosdec=float(adf.pmDE)*u.mas/u.yr,
+             obstime=Time('2015-06-01 05:00:00'), # roughly gaia time
+             frame='icrs')
+
+new_obstime = Time('1982-05-16 09:43:00')
+c_new = c.apply_space_motion(new_obstime=new_obstime)
+
+print(c)
+print(c_new)
+
+print(c.separation(c_new).to(u.arcsec))

### 2020-05-15 drivers/groundphot.py

@@ -13,9 +13,9 @@ def main():
     do_vis_groundimgs = 0
     do_shift_groundimgs = 0
     do_pixel_lc = 0
-    do_pu_apphot = 0
-    do_blendcheck = 0
-    do_vis_groundimg_customap = 1
+    do_pu_apphot = 1
+    do_stackviz_blendcheck = 1
+    do_vis_groundimg_customap = 0
 
     datestrs = ['2020-04-01', '2020-04-26']
 
@@ -51,9 +51,10 @@ def main():
                     tgp.compstar_detrend(datestr, ap, target='customap',
                                          customid=_id)
 
-        if do_blendcheck:
+        if do_stackviz_blendcheck:
             for apn in range(0,7):
-                tp.stackviz_blend_check(datestr, apn, soln=0)
+                tp.stackviz_blend_check(datestr, apn, soln=0, adaptiveoffset=1)
+                tp.stackviz_blend_check(datestr, apn, soln=0, adaptiveoffset=0)
 
         if do_vis_groundimg_customap:
             tgp.vis_groundimgs(datestr, customap=1)

### 2020-05-15 timmy/groundphot.py

@@ -596,7 +596,7 @@ def compstar_detrend(datestr, ap, target='837', customid=None):
     tp._plot_quicklooklc(
         outpath, time, target_flux, target_flux*1e-3, flat_flux, model_flux,
         showvlines=1, figsize=(18,8), provenance=provenance, timepad=0.05,
-        titlestr=titlestr
+        titlestr=titlestr, ylim=(0.985, 1.015)
     )
 
     # save the LC

### 2020-05-18 drivers/make_posterior_table.py
add make_posterior_table

@@ -1,0 +1,240 @@
+import os, re
+from copy import deepcopy
+import numpy as np, pandas as pd, matplotlib.pyplot as plt, pymc3 as pm
+from os.path import join
+from itertools import product
+
+from timmy.modelfitter import ModelFitter, ModelParser
+from timmy.convenience import get_clean_data, detrend_data
+from timmy.priors import initialize_prior_d
+from timmy.paths import RESULTSDIR
+
+def main(modelid):
+
+    assert modelid == 'transit'
+    yval = 'PDCSAP_FLUX' # could be SAP_FLUX 
+
+    OVERWRITE = 0
+    REALID = 'TOI_837'
+    provenance = 'spoc'
+    PLOTDIR = os.path.join(
+        RESULTSDIR, '{}_{}_phot_results'.format(REALID, modelid)
+    )
+    PLOTDIR = os.path.join(PLOTDIR, '20200515')
+
+    summarypath = os.path.join(
+        PLOTDIR, 'posterior_table_raw_{}.csv'.format(modelid)
+    )
+    pklpath = os.path.join(
+        os.path.expanduser('~'), 'local', 'timmy',
+        '{}_model_{}.pkl'.format(REALID, modelid)
+    )
+    np.random.seed(42)
+
+    x_obs, y_obs, y_err = get_clean_data(provenance, yval, binsize=None,
+                                         maskflares=1)
+    y_flat, y_trend = detrend_data(x_obs, y_obs, y_err)
+    s = np.isfinite(y_flat) & np.isfinite(x_obs) & np.isfinite(y_err)
+    x_obs, y_flat, y_err = x_obs[s], y_flat[s], y_err[s]
+
+    # note: we're fitting the detrended data
+    mp = ModelParser(modelid)
+    prior_d = initialize_prior_d(mp.modelcomponents)
+
+    if not os.path.exists(summarypath):
+
+        m = ModelFitter(modelid, x_obs, y_flat, y_err, prior_d, plotdir=PLOTDIR,
+                        pklpath=pklpath, overwrite=OVERWRITE)
+
+        df = pm.summary(
+            m.trace,
+            round_to=10, kind='stats'
+        )
+
+        df.to_csv(summarypath, index=True)
+
+    else:
+        df = pd.read_csv(summarypath, index_col=0)
+
+    fitted_params = [
[…]

### 2020-05-18 drivers/make_posterior_table.py
update posterior table

@@ -20,7 +20,7 @@ def main(modelid):
     PLOTDIR = os.path.join(
         RESULTSDIR, '{}_{}_phot_results'.format(REALID, modelid)
     )
-    PLOTDIR = os.path.join(PLOTDIR, '20200515')
+    PLOTDIR = os.path.join(PLOTDIR, '20200518')
 
     summarypath = os.path.join(
         PLOTDIR, 'posterior_table_raw_{}.csv'.format(modelid)
@@ -67,10 +67,10 @@ def main(modelid):
         df = pd.read_csv(summarypath, index_col=0)
 
     fitted_params = [
-        'period', 't0', 'r', 'b', 'u[0]', 'u[1]', 'mean', 'r_star', 'logg_star'
+        'period', 't0', 'log_r', 'b', 'u[0]', 'u[1]', 'mean', 'r_star', 'logg_star'
     ]
     derived_params = [
-        'rho_star', 'r_planet', 'a_Rs', 'cosi', 'T_14', 'T_13'
+        'r', 'rho_star', 'r_planet', 'a_Rs', 'cosi', 'T_14', 'T_13'
     ]
 
     srows = []
@@ -98,7 +98,9 @@ def main(modelid):
         't0': normal_str(
             mu=prior_d['t0'], sd=5e-3, fmtstr='({:.6f}; {:.4f})'
         ),
-        'r': r'$\mathcal{U}(10^{-3}; 1)$',
+        'log_r': uniform_str(
+            lower=1e-2, upper=1, fmtstr='({:.2f}; {:.2f})'
+        ),
         'b': r'$\mathcal{U}(0; 1+R_{\mathrm{p}}/R_\star)$',
         'u[0]': '(2)',
         'u[1]': '(2)',
@@ -136,7 +138,7 @@ def main(modelid):
     ud = {
         'period': 'd',
         't0': 'd',
-        'r': '--',
+        'log_r': '--',
         'b': '--',
         'u[0]': '--',
         'u[1]': '--',
@@ -145,6 +147,7 @@ def main(modelid):
         'logg_star': 'cgs'
     }
 
+    ud['r'] = '--'
     ud['rho_star'] = 'g$\ $cm$^{-3}$'
     ud['r_planet'] = '$R_{\mathrm{Jup}}$'
     ud['a_Rs'] = '--'
@@ -161,7 +164,7 @@ def main(modelid):
     latexparams = [
         r"$P_{\rm s}$",
[…]

### 2020-05-18 paper/collect.sh
minor updates

@@ -5,7 +5,7 @@ pdir=../results/paper_plots/
 
 cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
 
-cp ${rdir}TOI_837_transit_phot_results/20200515/TOI_837_transit_phaseplot.pdf f2.pdf
+cp ${rdir}TOI_837_transit_phot_results/20200518/TOI_837_transit_phaseplot.pdf f2.pdf
 
 cp ${pdir}scene.pdf f3.pdf
 

### 2020-05-19 drivers/make_posterior_table.py
update

@@ -98,12 +98,14 @@ def main(modelid):
         't0': normal_str(
             mu=prior_d['t0'], sd=5e-3, fmtstr='({:.6f}; {:.4f})'
         ),
-        'log_r': uniform_str(
+        'log_r': loguniform_str(
             lower=1e-2, upper=1, fmtstr='({:.2f}; {:.2f})'
         ),
         'b': r'$\mathcal{U}(0; 1+R_{\mathrm{p}}/R_\star)$',
-        'u[0]': '(2)',
-        'u[1]': '(2)',
+        'u[0]': uniform_str(prior_d['u[0]']-0.15, prior_d['u[0]']+0.15,
+                            fmtstr='({:.3f}; {:.3f})') + '^{(2)}',
+        'u[1]': uniform_str(prior_d['u[1]']-0.15, prior_d['u[1]']+0.15,
+                            fmtstr='({:.3f}; {:.3f})') + '^{(2)}',
         'mean': uniform_str(
             lower=prior_d['mean']-1e-2, upper=prior_d['mean']+1e-2
         ),
@@ -259,6 +261,15 @@ def uniform_str(lower, upper, fmtstr=None):
         return '$\\mathcal{U}'+'({}; {})$'.format(lower, upper)
     else:
         return '$\\mathcal{U}'+'{}$'.format(fmtstr).format(lower, upper)
+
+
+def loguniform_str(lower, upper, fmtstr=None):
+    # fmtstr: e.g., "({:.5f}; {:.2f})"
+    if fmtstr is None:
+        return '$\log\\mathcal{U}'+'({}; {})$'.format(lower, upper)
+    else:
+        return '$\log\\mathcal{U}'+'{}$'.format(fmtstr).format(lower, upper)
+
 
 
 if __name__ == "__main__":

### 2020-05-19 paper/ms.tex
minor updates
update
add simple calculation of prob BEB

@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f2.pdf}
+		\includegraphics[width=0.9\textwidth]{f2.pdf}
 	\end{center}
@@
     Black points are binned to approximately 1 point per 6 minutes.
-    One hundred samples from the posterior are shown with orange lines.
+    The blue line shows the transit model corresponding to the median
+    transit parameters (Table~2).
     % The bottom panel shows the residuals.
@@
 	}
-\end{figure}
+\end{figure*}
 
@@
     need to be very low-mass M dwarfs, and then the transit duration
-    again helps.
+		(and lack of chromaticity???) again helps.
 
   \item {\it Background blends}.
+	An argument on the a priori probability of background blends follows from
+	counting statistics. Within 360 arcseconds, there are 298 T<16 stars in TIC8
+	(i.e., Gaia DR2). At 2.0 arcseconds, SOAR archives dmag(I) of 6. Inside of 2
+	arcseconds, we expect $\pi r^2 $ times (Nstar per sq arcsec) = 9e-3 T<16 stars.
+	Any with T$\gtrsim$15 outside of 0.3 arcseconds would have been detected by
+	SOAR, which brings down the expected number of possible hidden sources by a
+	factor of a few.  Within 0.3 arcseconds, where SOAR gets worse than dmag(I) of
+	3, we expect 2e-4 T<16 stars. So (order of magnitude), background blends would
+	be a ~0.1\% coincidence.
+
     Archival SERC-J and AAO-SES plates are available for the \tn\

### 2020-05-19 drivers/calc_prob_beb.py

@@ -1,0 +1,25 @@
+"""
+I queried TIC8, and asked MAST "how many T<16 stars are within a radius of 360
+arcseconds of TOI 837?". The answer was 298.
+
+
+"""
+from math import pi
+
+r = 360  # arcseconds
+Nstar = 298  # 
+
+Nstar_per_arcsecsq = Nstar/(pi*r**2)
+
+r_min = 0.3  # at 0.3 arcseconds, SOAR stops getting decent constraints.
+r_max = 2.0  # at 2.0 arcseconds, SOAR achieves dmag(I) of 6.
+allowed_area = (pi*(r_min**2))
+
+Nstar_expected = allowed_area*Nstar_per_arcsecsq
+
+print(f'{Nstar_expected:.2e}')
+
+allowed_bigarea = (pi*(r_max**2))
+Nstar_expected_big = allowed_bigarea*Nstar_per_arcsecsq
+
+print(f'{Nstar_expected_big:.2e}')

### 2020-05-19 paper/ms.tex
update text

@@
 
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.48\textwidth]{f5.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Lithium 6708\AA\ equivalent widths for \tn, field stars, and
+    young open clusters.}
+    The field star sample is drawn from Kepler planet hosts,
+    and was measured by
+    \citet{berger_identifying_2018} using Keck-HIRES.
+    The young open clusters members were surveyed by
+    \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
+    spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018}
+    found lithium depletion boundary ages for these clusters of
+    $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
+    $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).
+    \label{fig:lithium}
+	}
+\end{figure}
+
 Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
-154 milliangstrom (see attached).
-
-As a reminder, Teff=6100K (TICv8). 
-Or Teff = 5946 $\pm$ 39 (CHIRON).
-Rafael, if you have a better
-determination of Teff, it would be helpful!  SpType is early-G,
-late-F from your quicklook spectral typing earlier.
-
-Relevant colors are V-K = 1.7,  V-I ~= V-T = 0.7
-
-Summarizing relevant lithium facts:
+154 milliangstrom.
 
@@
 Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
-Hyads shows that the depletion does happen over gigayear timescales
+Hyads has shown that the depletion does happen over gigayear timescales
 (Berger+2018, fig 7).
 
-Comparing to the Li EWs measured by Berger+2018 (their Fig 5),
+Figure~\ref{fig:lithium} compares our measured \tn\ Li EW 
+to stars in the field, and to young open cluster members.
+The field star measurements were collected by
+\citet{berger_identifying_2018}.
+We have shown the points with lithium detections at ${\rm SNR}>3$.
 TOI-837 is consistent with being younger than almost all CKS
@@
 
+The young open cluster members were selected for the presence of
+lithium, as described by \citet{randich_gaiaeso_2018}.
 The TOI-837 Li EW measured here (150 milliangstrom) is consistent
 with what's seen for stars of similar colors in <100 Myr old moving
-groups (Elliott+2016, Fig 11 -- attached).  This is sensible, because
+groups.
+(Elliott+2016, Fig 11 -- attached).  This is sensible, because
 IC 2602 is supposed to be 50 Myr old.
@@
  	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
+ 	{\bf VLT (number), UVES and GIRAFFE} (CITE: Pasquini et al 2002)
 % 	Euler1.2m~(CORALIE),

### 2020-05-19 paper/collect.sh

@@ -11,6 +11,8 @@ cp ${pdir}scene.pdf f3.pdf
 
 cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.pdf
 
+cp ${rdir}lithium/lithium.pdf f5.pdf
+
 cp ${pdir}toi_837_sed.png f6.png
 
 cp ${rdir}cluster_membership/hr.pdf f7.pdf

### 2020-05-20 paper/ms.tex
add rotation plot

@@
 
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.48\textwidth]{f9.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Rotation periods for \tn\ and selected open clusters.}
+    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
+    (1000$\,$Myr) are shown.  Their rotation periods were measured by
+    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
+    and \citet{curtis_temporary_2019}, respectively.
+    \label{fig:rotation}
+	}
+\end{figure}
+
 TESS photometric rotation period = 3.5days ish.
-
 vsini = 17.48 $\pm$ 0.15 (CHIRON).
-
 The two agree.
 
-For comparison, gyrochrones would predict X.XX.
+For comparison, gyrochrones would ``predict'' X.XX.
 
 This implies sub-Pleiades age expected for an IC 2602 member.
+
+Figure~\ref{fig:rotation} compares the stellar rotation period of \tn\ to
+periods that have been measured in a number of well-studied open clusters.
+\tn\ seems to be gyrochronologically coeval with the Pleiades sequence.
+
+We note that this is still in the ``sub 500 Myr'' range, when classical
+Skumanich spin-down is not expected to be happening (why is this the number?).
+
+This agrees with recent empirical results from Rebull et al 2020 and perhaps also 2018(?):
+they observed the Taurus foreground (age 30 Myr) and saw that it was 
+roughly consistent with the Pleaides.
+Upper Sco had a consistent mean, but a much larger scatter.
+
+%NOTE: begs the question... is there a large population of ~30-50 Myr old
+% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?
 

### 2020-05-20 drivers/plot_rotation.py

@@ -1,0 +1,7 @@
+import os
+import timmy.plotting as tp
+from timmy.paths import RESULTSDIR
+
+PLOTDIR = os.path.join(RESULTSDIR, 'rotation')
+
+tp.plot_rotation(PLOTDIR)

### 2020-05-20 paper/collect.sh

@@ -13,6 +13,8 @@ cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.p
 
 cp ${rdir}lithium/lithium.pdf f5.pdf
 
+cp ${rdir}rotation/rotation.pdf f9.pdf
+
 cp ${pdir}toi_837_sed.png f6.png
 
 cp ${rdir}cluster_membership/hr.pdf f7.pdf

### 2020-05-20 timmy/plotting.py

@@ -8,6 +8,7 @@ Plots:
     plot_scene
     plot_hr
     plot_lithium
+    plot_rotation
 
     plot_full_kinematics
         (plot_positions)
@@ -1624,15 +1625,62 @@ def plot_lithium(outdir):
         TEFF,
         LI_EW,
         alpha=1, mew=0.5, zorder=8, label='TOI 837', markerfacecolor='yellow',
-        markersize=9, marker='*', color='black', lw=0
+        markersize=10, marker='*', color='black', lw=0
     )
 
     ax.legend(loc='best', handletextpad=0.1, fontsize='x-small', framealpha=0.7)
-    ax.set_ylabel('EW Li$_{6708}$ [m$\AA$]', fontsize='large')
-    ax.set_xlabel('T$_{\mathrm{eff}}$ [K]', fontsize='large')
+    ax.set_ylabel('Li$_{6708}$ EW [m$\mathrm{\AA}$]', fontsize='large')
+    ax.set_xlabel('Effective Temperature [K]', fontsize='large')
 
     ax.set_xlim((4900, 6600))
 
     format_ax(ax)
     outpath = os.path.join(outdir, 'lithium.png')
     savefig(f, outpath)
+
+
+def plot_rotation(outdir):
+
+    from timmy.paths import DATADIR
+    rotdir = os.path.join(DATADIR, 'rotation')
+
+    # make plot
+    plt.close('all')
+
+    f, ax = plt.subplots(figsize=(4,3))
+
+    classes = ['pleiades', 'praesepe', 'ngc6811']
+    colors = ['k', 'gray', 'darkgray']
+    zorders = [3, 2, 1]
+    markers = ['o', 'X', 's']
+    labels = ['Pleaides', 'Praesepe', 'NGC$\,$6811']
+
+    # plot vals
+    for _cls, _col, z, m, l in zip(classes, colors, zorders, markers, labels):
+        df = pd.read_csv(os.path.join(rotdir, f'curtis19_{_cls}.csv'))
+        ax.scatter(
+            df['teff'], df['prot'], c=_col, alpha=1, zorder=z, s=5,
+            rasterized=False, linewidths=0, label=l, marker=m
+        )
+
+
+    from timmy.priors import TEFF, P_ROT
+    ax.plot(
+        TEFF,
+        P_ROT,
+        alpha=1, mew=0.5, zorder=8, label='TOI 837', markerfacecolor='yellow',
[…]

### 2020-05-20 timmy/priors.py

@@ -13,6 +13,7 @@ LOGG_STDEV = 0.03*3
 
 TEFF = 5946 # CHIRON spectra
 LI_EW = 154 # mA
+P_ROT = 3.3 # days, by eye.
 
 def initialize_prior_d(modelcomponents):
 

### 2020-05-25 paper/authors.tex
update paper
minor manuscript updates

@@
 %
-% key authors:
+% key contributions
 %
@@
 
-%PENDING
 \author[0000-0002-9158-7315]{R. Brahm}
@@
 %PENDING
+\author{P. Evans}
+\affiliation{El Sauce Observatory, Coquimbo Province, Chile}
+
+%PENDING
+\author[0000-0002-4891-3517]{G. Zhou}
+\affiliation{Center for Astrophysics \textbar \ Harvard \&
+Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%PENDING
 \author{J. de Leon}
@@
 
+%PENDING
+\author[0000-0003-2989-7774]{C. Bergmann}
+\affilation{Exoplanetary Science at UNSW, School of Physics, UNSW
+Sydney, NSW 2052, Australia}
+
+%PENDING
+\author[0000-0002-3481-9052]{K. G. Stassun}
+\affiliation{Vanderbilt University, Department of Physics \& Astronomy,
+6301 Stevenson Center Lane, Nashville, TN 37235, USA}
+\affiliation{Fisk University, Department of Physics, 1000 17th Avenue
+N., Nashville, TN 37208, USA}
+%
+
 %
@@
 %
-%PENDING
-\author{P. Evans}
-\affiliation{El Sauce Observatory, Coquimbo Province, Chile}
 
@@
 %
-%PENDING
-\author[0000-0002-4891-3517]{G. Zhou}
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 
@@
 Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%PENDING
+\author[0000-0002-7595-0970]{C.~.G.~Tinney}
+\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
+Sydney, NSW 2052, Australia}
+\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
+2052, Australia}
 
@@
 %
-%CONFIRMED
+%PENDING
 \author{G. R. Ricker} % grr@space.mit.edu
@@
 %
-%CONFIRMED
+%PENDING
 \author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu

### 2020-05-25 paper/ms.tex
minor manuscript updates

@@
 \begin{abstract}
-We report the discovery of the transiting planet TOI 837.01,
+We report the validation of the transiting planet TOI 837.01,
 a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
-8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
+8.3Y\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$ (3$\sigma$).
 TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
-``Southern Pleiades'') and is therefore 50 million years old.
+``Southern Pleiades''). It is therefore 50 million years old.
 We characterize the system using data from the NASA {\it Transiting
@@
 
+"""Validation is the process of statistically arguing that a
+transit-like signal is due to a planet rather than an astrophysical
+false positive. """
+(CITE blender, Torres+04,05,10; vespa Morton 12, 15; pastis Diaz+14
+Santerne+15; triceratops Giacalone \& Dressing 20).
+In this study, we provide such statistical arguments.
+
 Exclude possibilities:
@@
   \texttt{tesscut} \citep{brasseur_astrocut_2019},
+  \texttt{webplotdigitzer} \citep{rohatgi_2019},
   \texttt{wotan} \citep{hippke_wotan_2019}.

### 2020-05-25 drivers/make_posterior_table.py

@@ -164,8 +164,8 @@ def main(modelid):
     ]
 
     latexparams = [
-        r"$P_{\rm s}$",
-        r"$t_{\rm s}^{(1)}$",
+        r"$P$",
+        r"$t_0^{(1)}$",
         r"$\log R_{\rm p}/R_\star$",
         "$b$",
         "$u_1$",

### 2020-05-28 paper/authors.tex
update authors
merge fpscenarios plot to paper

@@
 \author[0000-0003-2989-7774]{C. Bergmann}
-\affilation{Exoplanetary Science at UNSW, School of Physics, UNSW
+\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
 Sydney, NSW 2052, Australia}
@@
 %
-\author[0000-0002-0619-7639]{C.~Ziegler}
+\author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
 \affiliation{Dunlap Institute for Astronomy and Astrophysics,
@@
 Canada}
+
+%FIXME ORCIDs
+\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
+\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La
+Serena, Chile}
+
+\author{N.~Law} % nlaw@unc.edu
+\affiliation{Department of Physics and Astronomy, The University of
+North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
+
+\author{A.~W.~Mann} % awmann@unc.edu
+\affiliation{Department of Physics and Astronomy, The University of
+North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
 

### 2020-05-28 paper/ms.tex
merge fpscenarios plot to paper

@@
 
+"""Although IC 2602 does not belong to Sco OB2, it is
+spatially and dynamically a close relative, and for this reason
+we include it in this work, if even marginally"" (Damiani+2019).
+"""We also find that the open cluster IC 2602 has a similar dynamics
+to Sco OB2, and its PMS members are currently evaporating and forming
+a diffuse (size 10deg) halo around its double-peaked core"""
+
 \subsection{Cluster Membership}
@@
 %FIXME FIXME finish these citations
+%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed as
+%IC2602
 
@@
 including \tn.
+%Bochanski reported:
+%logAge 9.38 +0.42 -0.26
+%dist 138.3 +7.0 -7.2
+%A_v = 0.27 +0.18 - 0.18
+%
 
@@
 $\approx 0.15\,{\rm dex}$.
+They reported an average extinction of Av=0.243 mag.
 
@@
 \end{figure}
+
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.7\textwidth]{f10.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Astrophysical false positive scenarios.}
+		{\it Top}: for bound companions,
+    {\it Bottom}: for unassociated companions along the same line of
+    sight.
+		\label{fig:rawzoom}
+	}
+\end{figure*}
 
@@
 %
+% This research has made use of the SVO Filter Profile Service
+% (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
+% MINECO through grant AYA2017-84089
+%
 % %

### 2020-05-28 paper/collect.sh

@@ -20,3 +20,5 @@ cp ${pdir}toi_837_sed.png f6.png
 cp ${rdir}cluster_membership/hr.pdf f7.pdf
 
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
+
+cp ${rdir}fpscenarios/fpscenarios.pdf f10.pdf

### 2020-05-28 timmy/plotting.py

@@ -2101,24 +2101,21 @@ def plot_fpscenarios(outdir):
 
     plt.close('all')
 
-    f, axs = plt.subplots(nrows=2, ncols= 1, figsize=(4,6))
+    f, axs = plt.subplots(nrows=2, ncols= 1, figsize=(4.5,6))
 
     for ax_ix, ax in enumerate(axs):
         for cdf, name, side, w in zip(constraint_dfs, names, sides, which):
 
-            if ax_ix == 0:
-                xval = cdf.sep_arcsec * dist_pc
-            else:
-                xval = cdf.sep_arcsec
+            xval = cdf.sep_arcsec * dist_pc if ax_ix == 0 else cdf.sep_arcsec
             yval = cdf.dmag
 
             dofill = False
             if w == 'both':
-                ax.plot(xval, yval, label='name')
+                ax.plot(xval, yval, label=name)
                 dofill = True
 
             if w == 'assoc' and ax_ix == 0:
-                ax.plot(xval, yval, label='name')
+                ax.plot(xval, yval, label=name)
                 dofill = True
             elif w == 'assoc' and ax_ix == 1:
                 pass
@@ -2167,24 +2164,44 @@ def plot_fpscenarios(outdir):
 
     tax.yaxis.set_major_formatter(ticker.FormatStrFormatter('%.1f'))
 
-    # tax.yaxis.set_major_formatter(
-    #     ticker.FuncFormatter(
-    #         lambda y,pos:
-    #         ('{{:.{:1d}f}}'.format(int(np.maximum(-np.log10(y),0)))).format(y)
-    #     )
-    # )
-
     tax.yaxis.set_ticks_position('right')
     tax.get_yaxis().set_tick_params(which='both', direction='in')
     for tick in tax.yaxis.get_major_ticks():
         tick.label.set_fontsize('small')
 
+    # Add the legend
+    handles, labels = axs[0].get_legend_handles_labels()
+    # lgd = axs[0].legend(handles, labels,
+    #                 bbox_to_anchor=(2.0,-0.1))
 
+    lgd = f.legend(
+        handles=handles,
+        labels=labels,
+        loc='center left', borderaxespad=0.1,
+        bbox_to_anchor=(0.92,0.5)
+    )
 
     f.tight_layout()
 
     outpath = os.path.join(outdir, 'fpscenarios.png')
 
-    savefig(f, outpath)
[…]

### 2020-05-29 paper/ms.tex
update manuscript

@@
 
-\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602}
+\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: Validation of a Jupiter-Sized Planet in IC~2602}
 
@@
 We report the validation of the transiting planet TOI 837.01,
-a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
-8.3Y\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$ (3$\sigma$).
-TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
-``Southern Pleiades''). It is therefore 50 million years old.
-We characterize the system using data from the NASA {\it Transiting
+and characterization of the system using data from the NASA {\it Transiting
 	Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
 ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
-XXX/FEROS, and AAT/Veloce.
-TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
-bright host stars, and is amenable for studies of planetary
-atmospheric and orbital evolution.
+MPG2.2/FEROS, and AAT/Veloce.
+We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
+``Southern Pleiades''). 
+The star is therefore 40$\pm$10 million years old.
+The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
+Jupiter-sized. 
+However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
+From transit photometry alone, the planetary size lies within
+0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
+between the planetary size and its impact parameter.
+From radial velocity monitoring, we find 
+that its mass is less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
+This mass limit requires the planetary size to be below $\approx$2.X$R_{\rm Jup}$.
+Non-planetary explanations for the data, most notably
+hierarchical or background eclipsing binaries, are argued to be
+highly unlikely on statistical grounds.
+TOI 837.01 therefore tentatively joins the ranks of adolescent exoplanets orbiting
+bright host stars. Further analysis of its mass, atmosphere, and obliquity could
+confirm its planetary nature beyond doubt, and are worthwhile because
+young planets do interesting things.
 \end{abstract}
@@
 		\leavevmode
-		\includegraphics[width=0.7\textwidth]{f10.pdf}
+		\includegraphics[width=1\textwidth]{f10.pdf}
 	\end{center}
@@
     sight.
-		\label{fig:rawzoom}
+		\label{fig:fpscenario}
 	}
@@
 Santerne+15; triceratops Giacalone \& Dressing 20).
-In this study, we provide such statistical arguments.
 
-Exclude possibilities:
-"The transits are blended from a background, unassociated eclipsing binary
-system or transiting exoplanet: We take the same approach outlined in
-Vanderburg et al. (2019). In short, if the transits are a blend from the
-background system, the true radius ratio is constrained by the ratio of the
-ingress time (T12) to the..."
-
-Given its galactic latitude of only $-6^\circ$, it is not surprising
-that the field of \tn\ is crowded.
-A number of possible false-positive explanations, including
-the usual neighboring, background, and hierarchical eclipsing binary
-scenarios, must therefore be considered.
+Figure~\ref{fig:fpscenario} provides a visual summary of
+the possible astrophysical false positive scenarios.
+If the \tn\ signal is not planetary, it must come from
+the near-total eclipse of a background star (a BEB), or else a hierarchical companion
+of the primary star (an HEB).
+It must also be verified that to the angular
+resolution possible, the transit signal originates from
+\tn, and not a neighboring star (an NEB).
 
@@
 
-% TODO: there's an even stronger argument advanced by Vanderburg et al
-% (2019), and used by Rizzuto+2020.
-There's also
-\begin{equation}
-  \Delta m <
-  -\frac{5}{2} \log_{10} (\delta_{\rm obs} t_{12}^2/t_{13}^2).
-\end{equation}
+Typically, the shape of the transit enables this argument to be 
+scaled to even more restrictive depths (e.g., CITE Vanderburg+2019, Rizzuto+2020, David+2018 1298Tau).
+However, since the transits of \tn\ are grazing,
+these arguments do not apply.
 
@@
 catalog, are shown with orange circles.
+Given its galactic latitude of only $-6^\circ$, it is not surprising
+that the field of \tn\ is crowded.
 The relevant stars for a blend analysis are as follows.
@@
   \item {\it Neighboring blends}.
+    Ruled out to within 2 arcseconds by Phil Evans.
 
   \item {\it Hierarchical blends}.
-    Limited by i) FEROS + Veloce RVs, and ii) the star being nicely on the
-    cluster HR diagram. Any extra hidden close-in binary stars would
-    need to be very low-mass M dwarfs, and then the transit duration
-		(and lack of chromaticity???) again helps.
+    Limited by i) FEROS + Veloce RVs, and ii) speckle imaging.
+
+  At present our data do not rule out the presence of bound companion
+    stars from $\approx$10--100$\,$AU, with masses in the range of
+    $\approx$0.1--0.2$\,$M$_\odot$ (Figure~\ref{fig:fpscenario}).
+  Roughly 2-3\% of Sun-like stars in the solar neighborhood with
+    binary companions have companions in this region of parameter space
+  (assuming the Raghavan+2010 CITE log-normal binary
+    separation distribution, and a uniform companion mass function.)
+
+  Companion statistics for hierarchical triples are somewhat less 
+    robust, but they have been studied, for instance by CITE
+    Tokovinin 2014.
+  CITE Tokovinin 2014 found that 7\% of Sun-like stars are
+    hierarchical triples with two companions in the compact orbit (the
+    ``L$_{12}$'' configuration, rather than the ``L$_{11}$''
+    configuration of say, $\alpha$~Centauri).
+  A priori then, given a Sun-like primary, the probability that it is in a
+    hierarchical triple configuration in which the outer orbit
+    satisfies the mass and semi-major axis constraints of
+    Figure~\ref{fig:fpscenario} is $\approx 7\% \times 3\% = 0.2\%$. 
+  This is independent of the issue that the inner pair would require
+    finely tuned orbital parameters (i) to eclipse, and (ii) to
+    be so compact.
 
@@
 	3, we expect 2e-4 T<16 stars. So (order of magnitude), background blends would
-	be a ~0.1\% coincidence.
+	be a $\sim$0.1\% coincidence.
+	%For the background blend to be {\it eclipsing} would require an additional
+	%$\sim$2\% coincidence (CITE Kirk+2017 KEBC).
+	%Combining the two probabilities yields a prior probability of $\approx$0.002\%.
 

### 2020-06-02 paper/ms.tex
update transit depth constraint

@@
 
-\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: Validation of a Jupiter-Sized Planet in IC~2602}
+\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A
+Jupiter-Sized Planet Candidate in IC~2602}
 
@@
 \begin{abstract}
-We report the validation of the transiting planet TOI 837.01,
-and characterization of the system using data from the NASA {\it Transiting
+We report analysis and arguments for the planetary nature of the
+  transiting planet TOI 837.01.
+We characterize the system using data from the NASA {\it Transiting
   Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
@@
 such.
-The requirement that the true eclipse depth is less than one
+The requirement that the eclipse is produced by stars
+and that $\delta_{\rm true} < 0.5$
 translates to a bound on the faintest possible blended companion
@@
 \begin{equation}
-    \Delta m < - \frac{5}{2} \log_{10} \delta_{\rm obs}.
+    \Delta m < - \frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
 \end{equation}
 For \tn\ ($T=9.93$), this implies that any star invoked to explain the
-transit depth must be brighter than $T=15.92$.
+transit depth must be brighter than $T=15.07$.
 

### 2020-06-02 timmy/plotting.py

@@ -2037,12 +2037,15 @@ def plot_fpscenarios(outdir):
 
     # transit depth constraint: within 2 arcseconds from ground-based seeing
     # limited resolution.
-    # within dmag~5.9 from transit depth.
+    # within dmag~5.2 from transit depth (and assumption of a totally eclipsing
+    # M+M dwarf type scenario. Totally eclipsing dark companion+Mdwarf is a bit
+    # ridiculous).
+    N = 0.5 # N=1 for the dark companion scenario.
     Tmag = 9.9322
     depth_obs = (4374e-6) # QLP depth
     tdepth_ap = 2    # arcsec
     tdepth_sep = sep_arcsec[sep_arcsec < tdepth_ap]
-    tdepth_dmag = -5/2*np.log10(depth_obs)*np.ones_like(tdepth_sep)
+    tdepth_dmag = 5/2*np.log10(N/depth_obs)*np.ones_like(tdepth_sep)
     tdepth_sep = np.append(tdepth_sep, tdepth_ap)
     tdepth_dmag = np.append(tdepth_dmag, 0)
     tdepth_df = pd.DataFrame({'sep_arcsec': tdepth_sep, 'dmag': tdepth_dmag})

### 2020-06-02 paper/ms.tex
update paper

@@
 \begin{abstract}
-We report analysis and arguments for the planetary nature of the
-  transiting planet TOI 837.01.
+We validate the planetary nature of the transiting planet TOI 837.01.
 We characterize the system using data from the NASA {\it Transiting
@@
 ``Southern Pleiades''). 
-The star is therefore 40$\pm$10 million years old.
+The star is therefore 30$\pm$20 million years old.
 The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
@@
   between the planetary size and its impact parameter.
-From radial velocity monitoring, we find 
-that its mass is less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
-This mass limit requires the planetary size to be below $\approx$2.X$R_{\rm Jup}$.
-Non-planetary explanations for the data, most notably
-hierarchical or background eclipsing binaries, are argued to be
-highly unlikely on statistical grounds.
-TOI 837.01 therefore tentatively joins the ranks of adolescent exoplanets orbiting
-bright host stars. Further analysis of its mass, atmosphere, and obliquity could
-confirm its planetary nature beyond doubt, and are worthwhile because
-young planets do interesting things.
+From radial velocity monitoring, we find that its mass is less than
+  2.XX $M_{\rm Jup}$ (3$\sigma$).
+This mass limit requires the planetary size to be below
+  $\approx$2.0$R_{\rm Jup}$.
+Non-planetary explanations for the data, most notably hierarchical or
+  background eclipsing binaries, are argued to be highly unlikely on
+  statistical grounds.
+TOI 837.01 therefore tentatively joins the ranks of adolescent
+  exoplanets orbiting bright host stars. Further analysis of its mass,
+  atmosphere, and obliquity could confirm its planetary nature beyond
+  doubt, and are worthwhile because young planets do interesting
+  things.
 \end{abstract}
@@
     {\bf TESS lightcurve of \tn\ (Sectors 10 and 11).}
-		{\it Top}: \texttt{PDCSAP} mean-subtracted relative flux at 2-minute
-		sampling. Spot-induced stellar variability is the dominant signal.  Dashed
-		lines show the five transits observed by TESS.
-    {\it Bottom}: Zoomed windows of individual transits.
-    Red points show manually identified stellar flares.
+    {\it Top}: \texttt{PDCSAP} mean-subtracted relative flux at
+    2-minute sampling. Spot-induced stellar variability is the
+    dominant signal.  Dashed lines show the five transits observed by
+    TESS.
+    {\it Bottom}: Zoomed windows of individual transits.  Red points
+    show manually identified stellar flares.
 		\label{fig:rawzoom}
@@
 \subsection{Ground-based Time-Series Photometry}
+\label{subsec:groundphot}
 
@@
 %FIXME FIXME finish these citations
-%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed as
+%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed it as
 %IC2602
@@
 
-\section{The Planet}
-\label{sec:planet}
+\section{Validation of \pn}
+\label{subsec:validation}
+
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=1\textwidth]{f10.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+		{\bf Astrophysical false positive scenarios.}
+		{\it Top}: for bound companions,
+		{\it Bottom}: for unassociated companions along the same line of
+		sight.
+		\label{fig:fpscenario}
+	}
+\end{figure*}
 
@@
 
-\begin{figure*}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=1\textwidth]{f10.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Astrophysical false positive scenarios.}
-		{\it Top}: for bound companions,
-    {\it Bottom}: for unassociated companions along the same line of
-    sight.
-		\label{fig:fpscenario}
-	}
-\end{figure*}
-
-\subsection{Transit Fitting}
-Simultaneous dip plus rotation period (GP) fit. Use celerite plus PyMC3/exoplanet.
-Mention FPP?
-
-\subsection{Validation of \pn}
-\label{subsec:validation}
-
 """Validation is the process of statistically arguing that a
@@
 
-Figure~\ref{fig:fpscenario} provides a visual summary of
-the possible astrophysical false positive scenarios.
-If the \tn\ signal is not planetary, it must come from
-the near-total eclipse of a background star (a BEB), or else a hierarchical companion
-of the primary star (an HEB).
-It must also be verified that to the angular
-resolution possible, the transit signal originates from
-\tn, and not a neighboring star (an NEB).
+Many validation analyses are inherently flawed because they do
+not deal with the fact that you are conditioned on having observed
+many stars, and having found an eclipsing system.
 
-For these scenarios to be viable, the flux from \tn\ and the true
-eclipsing binary host would blend together, reducing the ``true''
-eclipse depth $\delta_{\rm true}$ to produce the observed depth
+Figure~\ref{fig:fpscenario} provides a visual summary of the possible
+astrophysical false positive scenarios.  If the \tn\ signal is not
+planetary, it must come from the near-total eclipse of a background
+star (a BEB), or else a hierarchical companion of the primary star
+(an HEB).  It must also be verified that to the angular resolution
+possible, the transit signal originates from \tn, and not a
+neighboring star (an NEB).
+We proceed by describing each constraint in detail.
+
+\subsection{Limits on Companions from the Transit Depth}
+
+In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
+binary host would blend together, reducing the ``true'' eclipse depth
+$\delta_{\rm true}$ to produce the observed depth
 $\delta_{\rm obs}$:
@@
 where the total flux and the flux from the neighbor are labelled as
-such.
-The requirement that the eclipse is produced by stars
-and that $\delta_{\rm true} < 0.5$
-translates to a bound on the faintest possible blended companion
-stars:
+such.  The requirement that the eclipse is produced by stars and that
+$\delta_{\rm true} < 0.5$ translates to a bound on the faintest
+possible blended companion stars:
 \begin{equation}
@@
 \end{equation}
-For \tn\ ($T=9.93$), this implies that any star invoked to explain the
-transit depth must be brighter than $T=15.07$.
+For \tn\ ($T=9.93$), this implies that any stellar companion invoked
+to explain the transit depth must be brighter than $T=15.07$.
 
-Typically, the shape of the transit enables this argument to be 
-scaled to even more restrictive depths (e.g., CITE Vanderburg+2019, Rizzuto+2020, David+2018 1298Tau).
-However, since the transits of \tn\ are grazing,
-these arguments do not apply.
+Typically, the shape of the transits enables this argument to be scaled to even
+more restrictive depths (e.g., CITE Seager 2003, Vanderburg+2019,
+Rizzuto+2020, David+2018 1298Tau).  However, since the transits of
+\tn\ are grazing, these arguments do not apply.
 
-\subsubsection{Visual Binarity}
-Figure~\ref{fig:scene} shows the scene.
-In the upper panels, the pixels used to measure the background level
-in the SPOC lightcurve are indicated with `\texttt{X}' hatching, and
-the pixels used in the final lightcurve aperture are shown with
-`\texttt{/}' hatching.
+\subsection{Limits on Companions from Imaging}
+
+\subsubsection{Gaia Imaging}
+Figure~\ref{fig:scene} shows the scene as viewed in the DSS2 plates
+and by TESS.  In the upper panels, the pixels used to measure the
+background level in the SPOC lightcurve are indicated with
+`\texttt{X}' hatching, and the pixels used in the final lightcurve
+aperture are shown with `\texttt{/}' hatching.
 
 Stars brighter than $T=16$, as queried from the Gaia DR2 source
-catalog, are shown with orange circles.
-Given its galactic latitude of only $-6^\circ$, it is not surprising
-that the field of \tn\ is crowded.
-The relevant stars for a blend analysis are as follows.
+catalog, are shown with orange circles.  Given its galactic latitude
+of $b=-6^\circ$, it is not surprising that the field of \tn\ is
+crowded.  The stars that were of immediate concern for a blend
+analysis were as follows.
 \begin{itemize}
@@
 
-The Gaia DR2 data for Star A seems somewhat poorly behaved.  While
+The Gaia DR2 data for Star A seems poorly behaved.  While
 Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
@@
 were eclipsing binaries, they could be the sources of the transit
-signal.  Coincidence stellar sources below the resolution limit of
-Gaia are also a concern (CITE). To rule out these possibilities, we
-took a number of approaches.
+signal.  We ruled out both Star A and Star B as hosts of the eclipse
+through a detailed analysis of the ground-based seeing-limited
+photometry (\S~\ref{subsec:groundphot}).
 
-\subsubsection{High-resolution imaging}
+\subsubsection{Speckle Imaging}
 
-We imaged the system using SOAR-HRCam.
+Additional point-sources could be present beyond the angular
+resolution of the Gaia source catalog.
+To limit this possibility,
+we imaged the system using SOAR-HRCam, as described in
+\citet{ziegler_soar_2020}.
 {\bf Carl: please describe}.
-Figure~\ref{fig:soar}.
-\citet{ziegler_soar_2020}
+The bandpass was a Johnson-Cousins,
+where I is centered at 879 nm and has a width of 289 nm.
 
-\subsubsection{TESS analysis}
+Figure~\ref{fig:soar} shows the result.
+Star A (TIC 847769574) is detected as expected, and no additional
+companions are found.
+"""
+The points on the plot are measured 5-sigma detectable contrasts. The
+lines are linear smoothing fits between two regimes. In general, the
+sensitivity of speckle imaging to companions rises sharply from the
+diffraction limit to a ``knee'' at a separation of 0.15--0.2
+arcseconds, where it then continues to slowly increase out to 1.5$''$,
+beyond which the speckle patterns become de-correlated. For this
+target, I suspect the measurement at 1$''$ is slightly larger than
+expected due to some increase in speckle noise at that radius.
+"""
 
+We convert the contrast ratios obtained through the SOAR imaging to
+constraints on the masses of putative companions following Montet+2014
+(CITE and others!).  We employed the Baraffe+2003 models for
+substellar mass objects and the MESA isochrones for stellar mass
+objects (Choi et al XXXX).  We assumed that the system age was 35 Myr,
+to ensure that companions would be at a plausible state of
+contraction.
+
+Due to the specific filters of the SOAR HRcam imager, we further
+assumed that all sources had blackbody spectra. While this is clearly
+false, we do not readily have access to the planetary and stellar
+atmosphere models needed for the correct calculation. However, the
+Baraffe+2003 and MESA models do report effective temperatures and
+bolometric luminosities.  We opt to use these theoretical quantities,
+combined with the measured transmission functions, to calculate the
+absolute magnitudes in the HRCam bandpasses (CITE Tokovinin 2018
+summary paper with the bandpasses).
+
+\subsubsection{Archival Imaging}
+    Archival SERC-J and AAO-SES plates are available for the \tn\
+field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
+These plates were acquired in 1982 and 1992, respectively.
+For high proper motion stars archival imagery can be used to
+detect slowly moving background stars that might be an
+astrophysical false-positive source
+({\it e.g.}, \citealt{huang_pimen_2018}).
+However \tn\ has only moved $\approx0.7''$ between 1982 and
+present, in comparison to the $\approx2.0''$ FWHM of the target on
+the plates.
+We therefore cannot resolve it with great confidence from
+background sources not already resolved through more modern
+imaging.
+
+\subsection{Limits on Companions from Radial Velocities}
+
+The combined radial velocities from FEROS, CHIRON, and Veloce 
+can be used to place limits on the presence of massive, close-in
+bounds companion to \tn.
+
+We derived the relevant limits using \texttt{radvel} \citep{fulton_radvel_2018}.
+We assumed circular orbits for the massive companion.
+We then fitted the RV data for the semiamplitude, period, time
+of conjunction,
+instrument offsets, and jitter parameters.
+We placed a wide log-uniform prior on the semiamplitude
+and period to ensure appropriate sampling of the relevant
+spaces.
+($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim \mathcal{U}(0.1, 10^{15})$).
+
+We then converting the resulting posterior in period and semiamplitude
+to minimum mass and semi-major axis assuming Kepler's third law.
+The resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
+
+\subsection{Limits on Companions from Time-Series Photometry}
+
+\subsubsection{TESS}
 We examined the CDIPS FFI lightcurves of the target, which are
@@
 
-\subsubsection{Seeing-limited time-series photometry}
+\subsubsection{Custom Apertures on Ground-Based Time-Series Photometry}
+% See "TOI-837 : a planet!" thread, May 2020
 
-%FIXME:
-{\bf left off here}
-Co-author P{.} Evans obtained a total transit that showed that, within
-1.5'', the transit comes from \tn.  We can be even more certain with a
-pixel-level analysis. This 2.1 arcsec neighbor is also a mid to late M
-dwarf, and bound given the Gaia parallax + proper motion. The transit
-duration is rather long for the signal to come from the M dwarf,
-rather than the G dwarf.  I think the state of photometric followup
-could be improved (there is only one good total transit), but I think
-over this month and next we can pull another few partials.
+A total eclipse of Star A would produce a 1.4\%
+dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
+dips of exactly the right depth (0.4\%).
 
-A total eclipse of Ziegler's faint companion would produce a 1.4\%
-dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
-dips at exactly the right depth (0.4\%).
+To assess this possibility with the ground-based photometry, we
+produced lightcurves centered on \tn\ with
+circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
+We did not detect any statistically significant variation in the depth
+of the transits.
 
-dmag = 4.7, transit depth is 0.4\%. This dmag converts to a flux
-fraction of 0.0132. A 30\% eclipse on T1 could therefore nominally
-explain the TESS data.  % (depth_obs = depth_true * flux fraction).
+We also created lightcurves with a custom set of $r=2.1''$ apertures
+with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
+east of \tn.  We did not detect any variation of the transit depth
+along this line of lightcurves, as would be expected if Star A were
+the eclipse host.  The apertures east of \tn\ are particularly
+constraining, as they exclude over 90\% of the flux from Star A.
+The eclipse on Star A would therefore need to be excessively deep to
+produce the observed eclipse depth.
+We take this to indicate that \tn\ is the source of the transit signal
+to within $\approx2.0''$.
 
-However in the aperture from this green r=2px green LC, say 90\% of the
-flux from T1 is excluded. The eclipse on T1 would therefore need to be
-much deeper -- in fact, over 100\%. This argument holds as long as at
-least 70\% of the flux from T1 is excluded, so I think we're likely in
-the clear.
+\subsubsection{Color Photometry}
+
+HEB and, to a lesser extent, BEB scenarios, can be limited
+by color photometry.
+
+Ignoring color photometry,
+the most plausible HEB scenarios for TOI 837 involve pairs of eclipsing M dwarfs.
+
+\paragraph{Simple Example}
+% SEE June 1, 2020 email in "Re: TOI-837.01" thread
+As a simple example,
+assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
+Assume PMS evolution, and convert between Mstar, delta mag, and Teff using MIST isochrones for a 50 Myr system. 
+Take transmission functions (filters only; no instrument or atmosphere response) from the SVO filter profile service (CITE).
+Integrate up blackbody functions over each bandpass for each star, and get estimates of the eclipse depths if there were a total eclipse (of either of the secondary or tertiary) with this set of parameters.
+The apparent eclipse depths in each bandpass were:
+
+BessellU: 5.03e-04
+BessellB: 1.39e-03
+BessellV: 3.31e-03
+CousinsR: 5.59e-03
+CousinsI: 9.69e-03
+TESS: 9.18e-03
+
+The relative depths are what are important (geometry lets them all be scaled to match the observed TESS depth of 40 ppt).
+The attached plot shows each bandpass, where the narrow ones are as in the order above, and the wide one is TESS.
+
+U and B are ~10x shallower than TESS-band, because the M dwarf blackbody function turns over at ~2x longer wavelengths than the G dwarf blackbody (Wien's law).
+
+Therefore if TOI 837 were a hierarchical eclipsing M dwarf pair, Phil's two R-band observations should have shown eclipses a factor of 1.64x shallower than TESS observed (so, 24ppt, instead of the ~40ppt observed).
+So, the 40 (+/- 10ish) ppt R-band depths seen in Phil's transits vs TESS-band argue for a planet, but the level of confidence could probably be improved with U or B.
+
+\paragraph{Complicated Implementation}
+TODO, probably after U or B-band obtained.
 
@@
     Limited by i) FEROS + Veloce RVs, and ii) speckle imaging. 
+    Multicolor photometry also limits.
 
@@
     stars from $\approx$10--100$\,$AU, with masses in the range of
-    $\approx$0.1--0.2$\,$M$_\odot$ (Figure~\ref{fig:fpscenario}).
+    $\approx$0.15--0.25$\,$M$_\odot$ (Figure~\ref{fig:fpscenario}).
   Roughly 2-3\% of Sun-like stars in the solar neighborhood with
@@
 
-    Archival SERC-J and AAO-SES plates are available for the \tn\
-    field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
-    These plates were acquired in 1982 and 1992, respectively.
-    For high proper motion stars archival imagery can be used to
-    detect slowly moving background stars that might be an
-    astrophysical false-positive source
-    ({\it e.g.}, \citealt{huang_pimen_2018}).
-    However \tn\ has only moved $\approx0.7''$ between 1982 and
-    present, in comparison to the $\approx2.0''$ FWHM of the target on
-    the plates.
-    We therefore cannot resolve it with great confidence from
-    background sources not already resolved through more modern
-    imaging.
-
 \end{itemize}
 
-\subsection{Additional Companions}
+\section{The Planet}
+\label{sec:planet}
+
+\subsection{Transit Fitting}
+Simultaneous dip plus rotation period (GP) fit. Use celerite plus PyMC3/exoplanet.
+Mention FPP?
+
+\subsection{Additional Transits}
 

### 2020-06-03 paper/ms.tex
update paper for multicolor

@@
 
+\newpage
 \subsubsection{Color Photometry}
 
-HEB and, to a lesser extent, BEB scenarios, can be limited
+HEB and to a lesser extent BEB scenarios can be limited
 by color photometry.
-
-Ignoring color photometry,
-the most plausible HEB scenarios for TOI 837 involve pairs of eclipsing M dwarfs.
+In the absense of color photometry, the most plausible HEB scenarios for TOI
+837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
+These eclipses are redder than eclipses of the G-dwarf \tn.
+Observations that the transit depth does not decrease
+going to blue bands therefore limits the plausibility of these scenarios.
 
@@
 % SEE June 1, 2020 email in "Re: TOI-837.01" thread
-As a simple example,
-assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
-Assume PMS evolution, and convert between Mstar, delta mag, and Teff using MIST isochrones for a 50 Myr system. 
-Take transmission functions (filters only; no instrument or atmosphere response) from the SVO filter profile service (CITE).
-Integrate up blackbody functions over each bandpass for each star, and get estimates of the eclipse depths if there were a total eclipse (of either of the secondary or tertiary) with this set of parameters.
-The apparent eclipse depths in each bandpass were:
-
-BessellU: 5.03e-04
-BessellB: 1.39e-03
-BessellV: 3.31e-03
-CousinsR: 5.59e-03
-CousinsI: 9.69e-03
-TESS: 9.18e-03
-
-The relative depths are what are important (geometry lets them all be scaled to match the observed TESS depth of 40 ppt).
-The attached plot shows each bandpass, where the narrow ones are as in the order above, and the wide one is TESS.
-
-U and B are ~10x shallower than TESS-band, because the M dwarf blackbody function turns over at ~2x longer wavelengths than the G dwarf blackbody (Wien's law).
-
-Therefore if TOI 837 were a hierarchical eclipsing M dwarf pair, Phil's two R-band observations should have shown eclipses a factor of 1.64x shallower than TESS observed (so, 24ppt, instead of the ~40ppt observed).
-So, the 40 (+/- 10ish) ppt R-band depths seen in Phil's transits vs TESS-band argue for a planet, but the level of confidence could probably be improved with U or B.
-
-\paragraph{Complicated Implementation}
-TODO, probably after U or B-band obtained.
-
+As a simple example, assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
+Assume PMS evolution, and
+use MIST isochrones for a 35 Myr system to convert between stellar properties. 
+Take transmission functions (filters only; no instrument or atmosphere
+response) from the SVO filter profile service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.
+Integrate up blackbody functions over each bandpass for each star, and
+get estimates of the eclipse depths if there were a total eclipse (of
+either of the secondary or tertiary) with this set of parameters.  The
+apparent eclipse depths in various Bessel and Cousins bandpasses are:
+\begin{align}
+%FIXME: check these numbers
+  \delta_{\rm U_B} &= 5.03\times10^{-4} \ ({\rm Bessel\ U})\nonumber \\
+  \delta_{\rm B_B} &= 1.39\times10^{-3}\ ({\rm Bessel\ B})\nonumber \\
+  \delta_{\rm V_B} &= 3.31\times10^{-3}\ ({\rm Bessel\ V})\nonumber \\
+  \delta_{\rm R_C} &= 5.59\times10^{-3}\ ({\rm Cousins\ R})\nonumber \\
+  \delta_{\rm I_C} &= 9.69\times10^{-3}\ ({\rm Cousins\ I})\nonumber \\
+  \delta_{\rm T}   &= 9.18\times10^{-3}\ ({\rm TESS})
+\end{align}
+
+Our chief interest is the relative depths, because geometry lets all the
+depths be scaled to match the observed TESS depth of $\approx$43 ppt.
+(In this case, all depths would be scaled down by a multiplicative factor of
+2.1).
+
+The crucial point is that the bluest bands--- U and B---are roughly 10
+times shallower than TESS-band, because the M dwarf blackbody function
+turns over at 2 times longer wavelengths than the G dwarf blackbody
+(Wien's law).
+
+Therefore if TOI 837 were a hierarchical eclipsing M dwarf pair,
+Phil's two R-band observations should have shown eclipses a factor of
+1.64x shallower than TESS observed (so, 24ppt, instead of the ~40ppt
+observed). So, the 40 (+/- 10ish) ppt R-band depths seen in Phil's
+transits vs TESS-band argue for a planet, but the level of confidence
+could probably be improved with U or B.
+
+\paragraph{Limits on Masses of Bound Companions}
+
+With this intuition in place, we derived the limits on masses of bound
+hierarchical eclipsing companions as follows.  We assumed that each
+system was composed of the primary (\tn), plus a tertiary companion
+eclipsing a secondary companion every 8.3 days.
+
+For secondary masses ranging from 0.07 to 1.10 $M_\odot$, and
+mass ratios ($M_3/M_2$) from 0.1 to 1, we then 
+calculated the observed maximal eclipse depth of Star 3 in front of
+Star 2 in a number of bandpasses.
+As before, we interpolated between mass, effective temperature, and radius
+assuming the MIST isochrones for a 35$\,$Myr old system,
+and also assumed that each source had a blackbody spectrum.
+
+We excluded systems for which the maximal eclipse depth in TESS-band
+was less than the observed depth ({\it i.e.}, systems for which the tertiary
+was too small).
+For the systems with maximal eclipse depths in TESS-band greater than
+the observed TESS-band depth, we then calculated the multiplicative
+factor required to shrink the depth (from the $b=0$ case) to match the
+observed eclipse depth in the TESS-band.
+We then scaled the depths in each of the other bandpasses by this
+fixed geometric factor.
+
+We then asked: given a fixed secondary mass, are there any tertiary
+companions for which the expected $\delta_{\rm R_C}$ is larger than
+the observed Rc-band depth?
+In cases for which the answer was yes, we could not rule out such
+hierarchical eclipsing binary systems.
+Conversely, we were able to rule out systems
+for which at fixed secondary mass no tertiary mass would
+enable eclipses (in ${\rm R_C}$-band) of the necessary depth.
+
+For a lower limit on $\delta_{\rm R_C}$ of 32 parts per thousand,
+we found that the transition between systems that would produce
+eclipses that no matter what were ``too red'', and systems that would
+produce eclipses that could be sufficiently blue happens in \tn\ (for
+${\rm R_C}$-band) at 0.54$M_\odot$.
+The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
+
+{\bf If we could obtain a similar limit in B-band, it would 
+	solidify this result (because it would drive the HEB system to be even bluer).}
+
+\paragraph{Limits on Masses of Projected Companions}
+
+Ignoring the effects of interstellar reddening,
+the constraint that $M_2 \gtrsim 0.54 M_\odot$ based on
+colors applies to background eclipsing binaries as well.
+However, the blue eclipses produced by such systems ({\it e.g.}, a background G2V+K6V binary)
+can be kept while making the systems fainter by moving them to greater
+distances.
+The only way to definitively rule out such scenarios is to 
+prove that the loss of light is from the target star,
+for instance by detecting the Rossiter-McLaughlin effect
+during a transit.
+
+Such scenarios are somewhat contrived in that since 
+no secondary eclipse is observed, they require either
+eccentric orbits to avoid secondary eclipses, or else a
+background twin binary system at double
+the orbital period.
+
+\newpage
 \subsubsection{Summary}
@@
 %
-% This research has made use of the SVO Filter Profile Service
-% (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
-% MINECO through grant AYA2017-84089
+This research has made use of the SVO Filter Profile Service
+(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
+MINECO through grant AYA2017-84089
 %

### 2020-06-09 paper/ms.tex
minor paper updates

@@
 
-\subsubsection{Archival Imaging}
+\subsubsection{Patient Imaging}
     Archival SERC-J and AAO-SES plates are available for the \tn\
@@
 astrophysical false-positive source
-({\it e.g.}, \citealt{huang_pimen_2018}).
+({\it e.g.}, \citealt{huang_pimen_2018}, CITE VANDERBURG 19).
 However \tn\ has only moved $\approx0.7''$ between 1982 and

### 2020-06-17 paper/ms.tex
minor

@@
 
-\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A
-Jupiter-Sized Planet Candidate in IC~2602}
+\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated
+Jupiter-Sized Planet in IC~2602}
 
@@
 \begin{abstract}
-We validate the planetary nature of the transiting planet TOI 837.01.
-We characterize the system using data from the NASA {\it Transiting
-  Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
-  ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
-  MPG2.2/FEROS, and AAT/Veloce.
+We present the discovery of TOI 837.01 and its validation as
+a transiting planet.
+We characterize the system using data from the NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA Gaia mission, ground-based photometry, and spectroscopy from CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.
 We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
@@
 The star is therefore 30$\pm$20 million years old.
-The validated planet is warm ($P = 8.YY\,{\rm d}$) and likely
+The validated planet is warm ($P = 8.YY\,{\rm d}$) and roughly
   Jupiter-sized. 
 However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
-From transit photometry alone, the planetary size lies within
+From TESS photometry alone, the planetary size lies within
   0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
-  between the planetary size and its impact parameter.
-From radial velocity monitoring, we find that its mass is less than
-  2.XX $M_{\rm Jup}$ (3$\sigma$).
-This mass limit requires the planetary size to be below
-  $\approx$2.0$R_{\rm Jup}$.
-Non-planetary explanations for the data, most notably hierarchical or
-  background eclipsing binaries, are argued to be highly unlikely on
-  statistical grounds.
-TOI 837.01 therefore tentatively joins the ranks of adolescent
+  between the planetary size and the impact parameter of the transit.
+From radial velocity monitoring, we limit the mass of planet
+to less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
+Grazing transits are cause for concern, as they most often are indicative of astrophysical false positive scenarios.
+Our combined data render such scenarios highly unlikely.
+Multi-color photometry requires eclipsing companions to be nearly the same
+colors as TOI$\,$837, eliminating hierarchical eclipsing
+binary scenarios.
+Background eclipsing binary scenarios are limited by speckle
+imaging, but formally remain a 0.2\% possibility.
+TOI 837.01 therefore joins the ranks of adolescent
   exoplanets orbiting bright host stars. Further analysis of its mass,
-  atmosphere, and obliquity could confirm its planetary nature beyond
+  atmosphere, and obliquity should confirm its planetary nature beyond
   doubt, and are worthwhile because young planets do interesting
@@
 
-\begin{figure}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f6.png}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Spectral energy distribution of \tn\ from archival
-    photometry.}
-    {\bf Keivan: please describe, and if possible, send me the data
-    (photometry + the atmosphere model) used to generate the plot so I
-    can regenerate it in a consistent style with the rest of the paper}
-    \label{fig:sed}
-	}
-\end{figure}
+% TODO: decide whether to include
+
+% \begin{figure}[t!]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.48\textwidth]{f6.png}
+% 	\end{center}
+% 	\vspace{-0.7cm}
+% 	\caption{
+%     {\bf Spectral energy distribution of \tn\ from archival
+%     photometry.}
+%     {\bf Keivan: please describe, and if possible, send me the data
+%     (photometry + the atmosphere model) used to generate the plot so I
+%     can regenerate it in a consistent style with the rest of the paper}
+%     \label{fig:sed}
+% 	}
+% \end{figure}
 
@@
 		\label{fig:fpscenario}
+	}
+\end{figure*}
+
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=1\textwidth]{f11.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Multicolor photometry from the El Sauce 0.36m.}
+		\label{fig:multicolor}
 	}

### 2020-06-17 paper/collect.sh

@@ -22,3 +22,5 @@ cp ${rdir}cluster_membership/hr.pdf f7.pdf
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
 
 cp ${rdir}fpscenarios/fpscenarios.pdf f10.pdf
+
+cp ${rdir}TOI_837_transit_phot_results/20200518/TOI_837_transit_grounddepth.pdf f11.pdf

### 2020-06-17 paper/ms.tex
minor

@@
 
-\title{Cluster Difference Imaging Photometric Survey (CDIPS) II: A Validated
-Jupiter-Sized Planet in IC~2602}
+\title{
+  Cluster Difference Imaging Photometric Survey (CDIPS) II:
+  Validatation of a Jupiter-Sized Planet in IC~2602
+}
 
@@
 \begin{abstract}
-We present the discovery of TOI 837.01 and its validation as
-a transiting planet.
-We characterize the system using data from the NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA Gaia mission, ground-based photometry, and spectroscopy from CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.
-We find that TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the
-``Southern Pleiades''). 
-The star is therefore 30$\pm$20 million years old.
-The validated planet is warm ($P = 8.YY\,{\rm d}$) and roughly
-  Jupiter-sized. 
-However, its transits are grazing: $b > 0.92$ at 3$\sigma$.
-From TESS photometry alone, the planetary size lies within
-  0.58--3.87 $R_{\rm Jup}$, due to the degeneracy
-  between the planetary size and the impact parameter of the transit.
-From radial velocity monitoring, we limit the mass of planet
-to less than 2.XX $M_{\rm Jup}$ (3$\sigma$).
-Grazing transits are cause for concern, as they most often are indicative of astrophysical false positive scenarios.
-Our combined data render such scenarios highly unlikely.
-Multi-color photometry requires eclipsing companions to be nearly the same
-colors as TOI$\,$837, eliminating hierarchical eclipsing
-binary scenarios.
-Background eclipsing binary scenarios are limited by speckle
-imaging, but formally remain a 0.2\% possibility.
-TOI 837.01 therefore joins the ranks of adolescent
-  exoplanets orbiting bright host stars. Further analysis of its mass,
-  atmosphere, and obliquity should confirm its planetary nature beyond
-  doubt, and are worthwhile because young planets do interesting
-  things.
+  We present the discovery of TOI 837.01 and its validation as a
+  transiting planet.  We characterize the system using data from the
+  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
+  Gaia mission, ground-based photometry, and spectroscopy from
+  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
+  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
+  Pleiades'').  The star and validated planet are therefore 30$\pm$20
+  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
+  roughly Jupiter-sized.  However, its transits are grazing: $b >
+  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
+  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
+  the planetary size and the impact parameter of the transit.  From
+  radial velocity monitoring, we limit the mass of planet to less than
+  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
+  concern, as they usually are indicative of astrophysical false
+  positive scenarios.  Our follow-up data render such scenarios highly
+  unlikely.  Multi-color photometry requires eclipsing companions to
+  have nearly identical color as TOI$\,$837, eliminating hierarchical
+  eclipsing binary scenarios.  Background eclipsing binary scenarios
+  are limited by speckle imaging, but formally remain a 0.2\%
+  possibility.  TOI 837.01 therefore joins the ranks of adolescent
+  exoplanets orbiting bright host stars as a validated planet.
+  Further analysis of its mass, atmosphere, and obliquity should
+  confirm its planetary nature beyond doubt, and are worthwhile
+  because young planets are expected to do interesting things.
 \end{abstract}
 
+%FIXME these keywords.
 \keywords{
@@
 Recently, young planets have been hype.
+
+%TODO: pull from the cdips repo! I already wrote a lot of this...
 

### 2020-06-17 paper/ms.tex
minor words

@@
 
+IC~2602 happens to be near the western edge of the Sco OB2
+association, and is relatively close to it in proper motion space
+(Damiani+2019).
+Damini+2019 also reported evidence for the ongoing evaporation of
+\cn, in the form of a diffuse halo of young stars around the central
+density cusps.
+
+While \cn\ is older than most known Sco OB2 members,
+
 """Although IC 2602 does not belong to Sco OB2, it is

### 2020-06-18 paper/ms.tex
restructure paper

@@
 \begin{abstract}
-  We present the discovery of TOI 837.01 and its validation as a
+  We report the discovery of TOI 837.01 and its validation as a
   transiting planet.  We characterize the system using data from the
@@
   are limited by speckle imaging, but formally remain a 0.2\%
-  possibility.  TOI 837.01 therefore joins the ranks of adolescent
-  exoplanets orbiting bright host stars as a validated planet.
+  possibility.  TOI 837.01 is therefore a validated adolescent exoplanet
+  orbiting a bright host star.
   Further analysis of its mass, atmosphere, and obliquity should
@@
 
-Section~\ref{sec:observations} 
-Section~\ref{sec:star}
-Section~\ref{sec:planet}
-Section~\ref{sec:discussion}
-Section~\ref{sec:conclusions}.
-
-\section{The Data}
+Section~\ref{sec:observations} describes the identification of the
+candidate, and the follow-up observations collected.
+Section~\ref{sec:validation} combines these data to assess the 
+system's false positive probability, and finds that \pn\ is almost
+certainly a planet.  Section~\ref{sec:system} presents our knowledge
+of the cluster (Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
+and the planet (Section~\ref{subsec:planet}).  We conclude
+with a discussion in
+Section~\ref{sec:discussion}.
+
+\section{Identification and Follow-up Observations}
 \label{sec:observations}
@@
 
+%TODO: the scale of this plot is off. (Different font-sizes from
+%subplots).
+\begin{figure*}[t]
+	\begin{center}
+		\leavevmode
+		\subfloat{
+			\includegraphics[width=0.7\textwidth]{f2a.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.7\textwidth]{f2b.pdf}
+		}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ {\bf Joint TESS and multicolor photometry.}
+    {\it Top:} Phase-folded TESS transit. Gray points are 2-minute
+    PDCSAP flux measurements, detrended with a 0.3-day robust Huber
+    spline (see Section~\ref{subsec:tess}).  Black points are binned
+    to 6 minute intervals.  The line shows the transit model
+    corresponding to the median transit parameters (Table~2).
+    {\it Bottom:} Multicolor photometry from the El Sauce 0.36m.
+    The consistent transit depths between TESS-band and the bluer
+    Cousins-R and Johnson-B bandpasses rules out select false positive
+    scenarios.
+		\label{fig:jointphot}
+	}
+\end{figure*}
+
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.47\textwidth]{f3.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+		{\bf Radial velocities.}
+		\label{fig:rvs}
+	}
+\end{figure}
+
 \begin{figure*}[t!]
@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{f2.pdf}
+		\includegraphics[width=1\textwidth]{f4.pdf}
 	\end{center}
@@
 	\caption{
-    {\bf Phase-folded transit of \pn.} Gray points are
-    2-minute PDCSAP flux measurements, detrended with
-    a 0.3-day robust Huber spline (see Section~\ref{subsec:tess}).
-    Black points are binned to approximately 1 point per 6 minutes.
-    The blue line shows the transit model corresponding to the median
-    transit parameters (Table~2).
-    % The bottom panel shows the residuals.
-    \label{fig:phasefold}
+		{\bf Astrophysical false positive scenarios.}
+		{\it Top}: for bound companions,
+		{\it Bottom}: for unassociated companions along the same line of
+		sight.
+		\label{fig:fpscenario}
 	}
@@
 
-\subsection{TESS Photometry}
-\label{subsec:tess}
-
-\tn\ (GAIA DR2 5251470948229949568) was observed by the
-TESS spacecraft from X to Y in two-minute cadence mode.
-The star was designated
-TIC\,460205581 in the TESS Input Catalog
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.
-%FIXME make words more original
-The pixel data for an
-$11\times11$ array surrounding \tn\ were averaged into 2-minute
-stacks by the onboard computer.  Each 2048$\times$2048 image from the
-CCD was also averaged into 30-minute stacks, and saved as a ``full
-frame image'' (FFI).
-
-%FIXME make words more original
-The pixel data for an
-The 2-minute stacks for \tn\ were reduced to lightcurves by the
-Science Processing Operations Center (SPOC) at NASA
-Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
-Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
-pixels chosen to maximize the SNR of the total flux of the target
-\citep{smith_finding_2016}.  Non-astrophysical variability
-was removed by fitting out trends common to many stars
-\citep{smith_kepler_2012,stumpe_multiscale_2014}.
-
-%FIXME make words more original
-As an independent check on the 2-minute SPOC lightcurve, we examined
-the lightcurve based upon 30-minute image stacks which was produced as
-part of the Cluster Difference Imaging Photometric Survey (CDIPS;
-\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
-circular aperture with radius 1 pixel.
-
-%TODO: describe 0.3-day robust Huber spline
-
-Figure~\ref{fig:rawzoom}.
-
-\subsection{Ground-based Time-Series Photometry}
-\label{subsec:groundphot}
-
-\subsection{Imaging}
-
-\subsection{Spectroscopy}
-
-\subsubsection{CHIRON}
-9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
-6 were usable.
-
-\subsubsection{FEROS}
-N spectra with XXX/FEROS
-
-\subsubsection{Veloce}
-M spectra with AAT/Veloce.
-
-\subsection{Astrometry}
-
-\section{The Star}
-\label{sec:star}
-
-\subsection{The Cluster}
-\label{subsec:cluster}
-
-% NOTE: might want a table of all ages
-
-IC~2602 canonically has an age of $30\pm20\,{\rm Myr}$ (CITE: Van
-Leeuwen 2009).
-Or logage between 7.533 and 7.563	\citep{bossini_age_2019}.
-
-Or Li age of 40-50Myr (David+19, comparison with other Li stars).
-
-Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range between
-slightly super-solar ($0.04\pm0.01$, \citealt{baratella_gaia-eso_2020}) and
-slightly sub-solar ($-0.02 \pm 0.02$, \citealt{netopil_metallicity_2016}).
-
-IC~2602 is supervirial, in the sense that the observed stellar velocity
-dispersion is larger than the value expected if it were in virial equilibrium
-by about a factor of two \citep{bravi_gaia-eso_2018}.
-
-IC~2602 happens to be near the western edge of the Sco OB2
-association, and is relatively close to it in proper motion space
-(Damiani+2019).
-Damini+2019 also reported evidence for the ongoing evaporation of
-\cn, in the form of a diffuse halo of young stars around the central
-density cusps.
-
-While \cn\ is older than most known Sco OB2 members,
-
-"""Although IC 2602 does not belong to Sco OB2, it is
-spatially and dynamically a close relative, and for this reason
-we include it in this work, if even marginally"" (Damiani+2019).
-"""We also find that the open cluster IC 2602 has a similar dynamics
-to Sco OB2, and its PMS members are currently evaporating and forming
-a diffuse (size 10deg) halo around its double-peaked core"""
-
-\subsection{Cluster Membership}
-\label{subsec:member}
-
-\tn\ has been reported as a member of \cn\ by multiple independent 
-investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
-%FIXME FIXME finish these citations
-%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed it as
-%IC2602
-
-The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
-Veloce) is strong; the rotation period and vsini agree with
-sub-Pleiades age expected for an IC 2602 member.
-
-\subsubsection{HR Diagram}
-\begin{figure*}[t!]
+\begin{figure}[t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{f7.pdf}
+		\includegraphics[width=0.45\textwidth]{f5.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ {\bf Scene used for blend analysis.}
+		{\it Top:} Mean TESS image of \tn\ over Sector~10, with a
+		logarithmic grayscale. The yellow star is the position of \tn.
+		Orange circles are neighboring stars with $T<16$, scaled such that
+		brighter stars are larger. The \texttt{X} and \texttt{/} hatches
+		show the apertures used to measure the background and target star
+		flux, respectively. Dashed lines of constant declination and right
+		ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
+		image of the same field, with a linear grayscale. The circles show
+		apertures of radii 1, 1.5, and 2.25 pixels used in our blend
+		analysis (Section~\ref{subsec:validation}).  Two stars of interest
+		are ``Star A'' and ``Star B'', which were eventually excluded as
+		being possible sources of the transits.
+		\label{fig:scene}
+	}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{f6.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ 
+		{\bf SOAR HRCam contrast limits derived from point-source
+			injection-recovery experiments.} 
+		Star A ($\Delta T=4.7$, $\rho=2.3$'' west) is detected in the
+		autocorrelation function, in addition to being a resolved Gaia
+		source.
+		It is co-moving with \tn, and
+		its parallax and on-sky position imply that
+		it is physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
+		\label{fig:soar}
+	}
+\end{figure}
+
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{f7.pdf}
 	\end{center}
@@
 	}
-\end{figure*}
-
-Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
-reference to the broader \cn\ cluster, as well as its neighborhood.
-Cluster members were identified by \citet{cantatgaudin_gaia_2018}
-using using Gaia-DR2 positions, proper motions, and parallaxes.  
-We included candidate members with formal membership probability
-exceeding 10\%.  Save for a few low-mass outliers, most members appear
-to be young and coeval.
-
-\tn\ is in its expected position relative to the other members along
-the cluster isochrone.  This photometrically limits the presence of
-binary companions in the \tn\ system, to a magnitude difference of
-perhaps half the brightness of the target star.
-
-Figure~\ref{fig:hr} also suggests that the membership census of \cn\
-is incomplete.  We defined the reference ``neighborhood'' as the group
-of at most $10^4$ randomly selected non-member stars within 5 standard
-deviations of the mean \cn\ right ascension, declination, and
-parallax.  We queried Gaia DR2 for these stars using
-\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
-appear above the main sequence, even though they were not identified
-as 5-dimensional kinematic members through the unsupervised
-\citet{cantat-gaudin_gaia_2018} membership assignment process.
-
-\subsubsection{Position and Kinematics}
+\end{figure}
 
@@
 
-We examine the six-dimensional positions and kinematics in greater
-depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
-defined here identically to as in Figure~\ref{fig:hr}.  The axes
-limits for the right ascension, declination, and parallax dimensions
-are as in the Gaia archive query.  The axes limits for the proper
-motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
-75$^{\rm th}$ percentiles, in order to give a sense of the
-population's distribution, while excluding outlying points.  The
-radial velocities suffer the greatest incompleteness due to the
-current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.
-
-Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
-existence of the \cn\ open cluster and {\it (ii)} for the membership
-of \tn\ within \cn.
-The only dimension that could perhaps lead to some worry is the
-parallax, as \tn\ is one of the closest \cn\ members reported by
-\citet{cantatgaudin_gaia_2018}.
-Fortunately, there are independent means of verifying stellar youth.
-
-\subsubsection{Rotation}
-
-\begin{figure}[t!]
+\begin{figure}[t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f9.pdf}
+		\subfloat{
+			\includegraphics[width=0.45\textwidth]{f9a.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.45\textwidth]{f9b.pdf}
+		}
 	\end{center}
 	\vspace{-0.7cm}
-	\caption{
-    {\bf Rotation periods for \tn\ and selected open clusters.}
+	\caption{ {\bf Youth diagnostics.}
+    {\it Top:} Lithium 6708\AA\ equivalent widths for \tn, field
+    stars, and young open clusters.  The field star sample is drawn
+    from Kepler planet hosts, and was measured by
+    \citet{berger_identifying_2018} using Keck-HIRES.  The young open
+    clusters members were surveyed by \citet{randich_gaiaeso_2018}
+    using the UVES and GIRAFFE spectrographs at the ESO VLT.
+    \citet{randich_gaiaeso_2018} found lithium depletion boundary ages
+    for these clusters of $37.7^{+5.7}_{-4.8}\,{\rm Myr}$
+    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  {\it
+    Bottom:} Rotation periods for \tn\ and selected open clusters.
     The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
@@
     and \citet{curtis_temporary_2019}, respectively.
-    \label{fig:rotation}
+    \label{fig:lithium_rotation}
 	}
@@
 
-TESS photometric rotation period = 3.5days ish.
-vsini = 17.48 $\pm$ 0.15 (CHIRON).
-The two agree.
-
-For comparison, gyrochrones would ``predict'' X.XX.
-
-This implies sub-Pleiades age expected for an IC 2602 member.
-
-Figure~\ref{fig:rotation} compares the stellar rotation period of \tn\ to
-periods that have been measured in a number of well-studied open clusters.
-\tn\ seems to be gyrochronologically coeval with the Pleiades sequence.
-
-We note that this is still in the ``sub 500 Myr'' range, when classical
-Skumanich spin-down is not expected to be happening (why is this the number?).
-
-This agrees with recent empirical results from Rebull et al 2020 and perhaps also 2018(?):
-they observed the Taurus foreground (age 30 Myr) and saw that it was 
-roughly consistent with the Pleaides.
-Upper Sco had a consistent mean, but a much larger scatter.
-
-%NOTE: begs the question... is there a large population of ~30-50 Myr old
-% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?
-
-\subsubsection{Lithium}
-
-\begin{figure}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f5.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Lithium 6708\AA\ equivalent widths for \tn, field stars, and
-    young open clusters.}
-    The field star sample is drawn from Kepler planet hosts,
-    and was measured by
-    \citet{berger_identifying_2018} using Keck-HIRES.
-    The young open clusters members were surveyed by
-    \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
-    spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018}
-    found lithium depletion boundary ages for these clusters of
-    $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
-    $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).
-    \label{fig:lithium}
-	}
-\end{figure}
-
-Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
-154 milliangstrom.
-
-Lithium depletion for a star of TOI-837's spectral type happens
-over timescales >100 Myr (Soderblom+2013). This is because the
-convective envelopes are very shallow, so they don't cycle material
-down to the >3e6 K core until much later.
-
-Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
-Hyads has shown that the depletion does happen over gigayear timescales
-(Berger+2018, fig 7).
-
-Figure~\ref{fig:lithium} compares our measured \tn\ Li EW 
-to stars in the field, and to young open cluster members.
-The field star measurements were collected by
-\citet{berger_identifying_2018}.
-We have shown the points with lithium detections at ${\rm SNR}>3$.
-TOI-837 is consistent with being younger than almost all CKS
-planet-hosting field stars.
-
-The young open cluster members were selected for the presence of
-lithium, as described by \citet{randich_gaiaeso_2018}.
-The TOI-837 Li EW measured here (150 milliangstrom) is consistent
-with what's seen for stars of similar colors in <100 Myr old moving
-groups.
-(Elliott+2016, Fig 11 -- attached).  This is sensible, because
-IC 2602 is supposed to be 50 Myr old.
-
-\subsubsection{Literature Membership}
-The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
-in what they dubbed ``Group 5''.
-Analyzing the clusters of \citet{oh_comoving_2017},
-\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
-WISE photometry with MIST isochrones, and reported stellar masses,
-radii, metallicities, ages, distances, and extinction for 9754 stars,
-including \tn.
-%Bochanski reported:
-%logAge 9.38 +0.42 -0.26
-%dist 138.3 +7.0 -7.2
-%A_v = 0.27 +0.18 - 0.18
-%
-
-\tn\ was also listed as a member of ``Theia 92'' by
-\citet{kounkel_untangling_2019}.
-These authors identified 999 candidate cluster members, and
-reported a cluster isochrone age $\log t = 7.55$ with uncertainty
-$\approx 0.15\,{\rm dex}$.
-They reported an average extinction of Av=0.243 mag.
-
-\subsection{Stellar Parameters}
-
-% TODO: decide whether to include
-
-% \begin{figure}[t!]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.48\textwidth]{f6.png}
-% 	\end{center}
-% 	\vspace{-0.7cm}
-% 	\caption{
-%     {\bf Spectral energy distribution of \tn\ from archival
-%     photometry.}
-%     {\bf Keivan: please describe, and if possible, send me the data
-%     (photometry + the atmosphere model) used to generate the plot so I
-%     can regenerate it in a consistent style with the rest of the paper}
-%     \label{fig:sed}
-% 	}
-% \end{figure}
-
-\subsubsection{Physical}
- (Lstar, Rstar, Teff, Age and Mstar)
-
-From CHIRON spectra, my current best guess spectroscopic parameters
- are as follows.
- Teff = 5946 +/- 39
- logg = 4.48 +/- 0.03
- feh = -0.065 +/- 0.035
- vsini = 17.48 +/- 0.15
-
-Figure~\ref{fig:sed}.
-The SED fit, looking really good with rchi2 = 1.6:
-
-The fit parameters are: 
-Av = 0.20 +/- 0.03
-Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
-Rstar = 1.049 +/- 0.019 Rsun
-
-From the spectroscopic logg and the above Rstar, we get an independent
-mass estimate of 
-Mstar = 1.21 +/- 0.10 Msun 
-At face value, the mass seems a bit high for the radius, but I'm
-guessing that just means the spectroscopic logg is a bit too high.
-
-\paragraph{Astrometric information}
-The RUWE (CITE, CITE) for \tn\ is 1.02, indicative that there are no
-obviously present astometric companions.
-
-\subsubsection{Rotation}
-Stellar vsini
-Stellar rotation
-
-\subsection{RVs}
-I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
-mass measurement. The reason is that with vsini=17km/s, and 2\%
-rotation amplitude signal, we expect an RV RMS of 300m/s at the
-Prot=3.5 day rotation period (vsini*rotation amplitude). This is
-probably larger than the expected planet signal (100m/s, 8 days).
-
-\section{Validation of \pn}
-\label{subsec:validation}
-
-\begin{figure*}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=1\textwidth]{f10.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-		{\bf Astrophysical false positive scenarios.}
-		{\it Top}: for bound companions,
-		{\it Bottom}: for unassociated companions along the same line of
-		sight.
-		\label{fig:fpscenario}
-	}
-\end{figure*}
-
-\begin{figure*}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=1\textwidth]{f11.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Multicolor photometry from the El Sauce 0.36m.}
-		\label{fig:multicolor}
-	}
-\end{figure*}
-
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f3.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ {\bf Scene used for blend analysis.}
-		{\it Top:} Mean TESS image of \tn\ over Sector~10, with a
-		logarithmic grayscale. The yellow star is the position of \tn.
-		Orange circles are neighboring stars with $T<16$, scaled such that
-		brighter stars are larger. The \texttt{X} and \texttt{/} hatches
-		show the apertures used to measure the background and target star
-		flux, respectively. Dashed lines of constant declination and right
-		ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
-		image of the same field, with a linear grayscale. The circles show
-		apertures of radii 1, 1.5, and 2.25 pixels used in our blend
-		analysis (Section~\ref{subsec:validation}).  Two stars of interest
-		are ``Star A'' and ``Star B'', which were eventually excluded as
-		being possible sources of the transits.
-		\label{fig:scene}
-	}
-\end{figure}
-
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f4.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ 
-		{\bf SOAR HRCam contrast limits derived from point-source
-			injection-recovery experiments.} 
-		Star A ($\Delta T=4.7$, $\rho=2.3$'' west) is detected in the
-		autocorrelation function, in addition to being a resolved Gaia
-		source.
-		It is co-moving with \tn, and
-		its parallax and on-sky position imply that
-		it is physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
-		\label{fig:soar}
-	}
-\end{figure}
+\subsection{TESS Photometry}
+\label{subsec:tess}
+
+\tn\ (GAIA DR2 5251470948229949568) was observed by the
+TESS spacecraft from X to Y in two-minute cadence mode.
+The star was designated
+TIC\,460205581 in the TESS Input Catalog
+\citep{stassun_TIC_2018,stassun_TIC8_2019}.
+%FIXME make words more original
+The pixel data for an
+$11\times11$ array surrounding \tn\ were averaged into 2-minute
+stacks by the onboard computer.  Each 2048$\times$2048 image from the
+CCD was also averaged into 30-minute stacks, and saved as a ``full
+frame image'' (FFI).
+
+%FIXME make words more original
+The pixel data for an
+The 2-minute stacks for \tn\ were reduced to lightcurves by the
+Science Processing Operations Center (SPOC) at NASA
+Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
+Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
+pixels chosen to maximize the SNR of the total flux of the target
+\citep{smith_finding_2016}.  Non-astrophysical variability
+was removed by fitting out trends common to many stars
+\citep{smith_kepler_2012,stumpe_multiscale_2014}.
+
+%FIXME make words more original
+As an independent check on the 2-minute SPOC lightcurve, we examined
+the lightcurve based upon 30-minute image stacks which was produced as
+part of the Cluster Difference Imaging Photometric Survey (CDIPS;
+\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
+circular aperture with radius 1 pixel.
+
+%TODO: describe 0.3-day robust Huber spline
+
+Figure~\ref{fig:rawzoom}.
+
+\subsection{Ground-based Time-Series Photometry}
+\label{subsec:groundphot}
+
+\subsection{Imaging}
+
+\subsection{Spectroscopy}
+
+\subsubsection{CHIRON}
+9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
+6 were usable.
+
+\subsubsection{FEROS}
+N spectra with XXX/FEROS
+
+\subsubsection{Veloce}
+M spectra with AAT/Veloce.
+
+\subsection{Astrometry}
+
+\section{Elimination of False Positive Scenarios}
+\label{sec:validation}
 
@@
 
-\section{The Planet}
-\label{sec:planet}
-
-\subsection{Transit Fitting}
+\section{System Modelling}
+\label{sec:system}
+
+\subsection{The Cluster}
+\label{subsec:cluster}
+
+% NOTE: might want a table of all ages
+
+IC~2602 canonically has an age of $30\pm20\,{\rm Myr}$ (CITE: Van
+Leeuwen 2009).
+Or logage between 7.533 and 7.563	\citep{bossini_age_2019}.
+
+Or Li age of 40-50Myr (David+19, comparison with other Li stars).
+
+Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range between
+slightly super-solar ($0.04\pm0.01$, \citealt{baratella_gaia-eso_2020}) and
+slightly sub-solar ($-0.02 \pm 0.02$, \citealt{netopil_metallicity_2016}).
+
+IC~2602 is supervirial, in the sense that the observed stellar velocity
+dispersion is larger than the value expected if it were in virial equilibrium
+by about a factor of two \citep{bravi_gaia-eso_2018}.
+
+IC~2602 happens to be near the western edge of the Sco OB2
+association, and is relatively close to it in proper motion space
+(Damiani+2019).
+Damini+2019 also reported evidence for the ongoing evaporation of
+\cn, in the form of a diffuse halo of young stars around the central
+density cusps.
+
+While \cn\ is older than most known Sco OB2 members,
+
+"""Although IC 2602 does not belong to Sco OB2, it is
+spatially and dynamically a close relative, and for this reason
+we include it in this work, if even marginally"" (Damiani+2019).
+"""We also find that the open cluster IC 2602 has a similar dynamics
+to Sco OB2, and its PMS members are currently evaporating and forming
+a diffuse (size 10deg) halo around its double-peaked core"""
+
+\subsection{The Star}
+\label{subsec:star}
+\subsubsection{Cluster Membership}
+\label{subsec:member}
+
+\tn\ has been reported as a member of \cn\ by multiple independent 
+investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
+%FIXME FIXME finish these citations
+%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed it as
+%IC2602
+
+The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
+Veloce) is strong; the rotation period and vsini agree with
+sub-Pleiades age expected for an IC 2602 member.
+
+\subsubsection{HR Diagram}
+
+Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
+reference to the broader \cn\ cluster, as well as its neighborhood.
+Cluster members were identified by \citet{cantatgaudin_gaia_2018}
+using using Gaia-DR2 positions, proper motions, and parallaxes.  
+We included candidate members with formal membership probability
+exceeding 10\%.  Save for a few low-mass outliers, most members appear
+to be young and coeval.
+
+\tn\ is in its expected position relative to the other members along
+the cluster isochrone.  This photometrically limits the presence of
+binary companions in the \tn\ system, to a magnitude difference of
+perhaps half the brightness of the target star.
+
+Figure~\ref{fig:hr} also suggests that the membership census of \cn\
+is incomplete.  We defined the reference ``neighborhood'' as the group
+of at most $10^4$ randomly selected non-member stars within 5 standard
+deviations of the mean \cn\ right ascension, declination, and
+parallax.  We queried Gaia DR2 for these stars using
+\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
+appear above the main sequence, even though they were not identified
+as 5-dimensional kinematic members through the unsupervised
+\citet{cantat-gaudin_gaia_2018} membership assignment process.
+
+\subsubsection{Position and Kinematics}
+
+We examine the six-dimensional positions and kinematics in greater
+depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
+defined here identically to as in Figure~\ref{fig:hr}.  The axes
+limits for the right ascension, declination, and parallax dimensions
+are as in the Gaia archive query.  The axes limits for the proper
+motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
+75$^{\rm th}$ percentiles, in order to give a sense of the
+population's distribution, while excluding outlying points.  The
+radial velocities suffer the greatest incompleteness due to the
+current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.
+
+Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
+existence of the \cn\ open cluster and {\it (ii)} for the membership
+of \tn\ within \cn.
+The only dimension that could perhaps lead to some worry is the
+parallax, as \tn\ is one of the closest \cn\ members reported by
+\citet{cantatgaudin_gaia_2018}.
+Fortunately, there are independent means of verifying stellar youth.
+
+\subsubsection{Rotation}
+
+TESS photometric rotation period = 3.5days ish.
+vsini = 17.48 $\pm$ 0.15 (CHIRON).
+The two agree.
+
+For comparison, gyrochrones would ``predict'' X.XX.
+
+This implies sub-Pleiades age expected for an IC 2602 member.
+
+Figure~\ref{fig:lithium_rotation} compares the stellar rotation period of \tn\ to
+periods that have been measured in a number of well-studied open clusters.
+\tn\ seems to be gyrochronologically coeval with the Pleiades sequence.
+
+We note that this is still in the ``sub 500 Myr'' range, when classical
+Skumanich spin-down is not expected to be happening (why is this the number?).
+
+This agrees with recent empirical results from Rebull et al 2020 and perhaps also 2018(?):
+they observed the Taurus foreground (age 30 Myr) and saw that it was 
+roughly consistent with the Pleaides.
+Upper Sco had a consistent mean, but a much larger scatter.
+
+%NOTE: begs the question... is there a large population of ~30-50 Myr old
+% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?
+
+\subsubsection{Lithium}
+
+Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
+154 milliangstrom.
+
+Lithium depletion for a star of TOI-837's spectral type happens
+over timescales >100 Myr (Soderblom+2013). This is because the
+convective envelopes are very shallow, so they don't cycle material
+down to the >3e6 K core until much later.
+
+Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
+Hyads has shown that the depletion does happen over gigayear timescales
+(Berger+2018, fig 7).
+
+Figure~\ref{fig:lithium_rotation} compares our measured \tn\ Li EW 
+to stars in the field, and to young open cluster members.
+The field star measurements were collected by
+\citet{berger_identifying_2018}.
+We have shown the points with lithium detections at ${\rm SNR}>3$.
+TOI-837 is consistent with being younger than almost all CKS
+planet-hosting field stars.
+
+The young open cluster members were selected for the presence of
+lithium, as described by \citet{randich_gaiaeso_2018}.
+The TOI-837 Li EW measured here (150 milliangstrom) is consistent
+with what's seen for stars of similar colors in <100 Myr old moving
+groups.
+(Elliott+2016, Fig 11 -- attached).  This is sensible, because
+IC 2602 is supposed to be 50 Myr old.
+
+\subsubsection{Literature Membership}
+The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
+in what they dubbed ``Group 5''.
+Analyzing the clusters of \citet{oh_comoving_2017},
+\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
+WISE photometry with MIST isochrones, and reported stellar masses,
+radii, metallicities, ages, distances, and extinction for 9754 stars,
+including \tn.
+%Bochanski reported:
+%logAge 9.38 +0.42 -0.26
+%dist 138.3 +7.0 -7.2
+%A_v = 0.27 +0.18 - 0.18
+%
+
+\tn\ was also listed as a member of ``Theia 92'' by
+\citet{kounkel_untangling_2019}.
+These authors identified 999 candidate cluster members, and
+reported a cluster isochrone age $\log t = 7.55$ with uncertainty
+$\approx 0.15\,{\rm dex}$.
+They reported an average extinction of Av=0.243 mag.
+
+\subsubsection{Stellar Parameters}
+
+% TODO: decide whether to include
+
+% \begin{figure}[t!]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=0.48\textwidth]{f6.png}
+% 	\end{center}
+% 	\vspace{-0.7cm}
+% 	\caption{
+%     {\bf Spectral energy distribution of \tn\ from archival
+%     photometry.}
+%     {\bf Keivan: please describe, and if possible, send me the data
+%     (photometry + the atmosphere model) used to generate the plot so I
+%     can regenerate it in a consistent style with the rest of the paper}
+%     \label{fig:sed}
+% 	}
+% \end{figure}
+
+\subsubsection{Physical}
+ (Lstar, Rstar, Teff, Age and Mstar)
+
+From CHIRON spectra, my current best guess spectroscopic parameters
+ are as follows.
+ Teff = 5946 +/- 39
+ logg = 4.48 +/- 0.03
+ feh = -0.065 +/- 0.035
+ vsini = 17.48 +/- 0.15
+
+Figure~\ref{fig:sed}.
+The SED fit, looking really good with rchi2 = 1.6:
+
+The fit parameters are: 
+Av = 0.20 +/- 0.03
+Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
+Rstar = 1.049 +/- 0.019 Rsun
+
+From the spectroscopic logg and the above Rstar, we get an independent
+mass estimate of 
+Mstar = 1.21 +/- 0.10 Msun 
+At face value, the mass seems a bit high for the radius, but I'm
+guessing that just means the spectroscopic logg is a bit too high.
+
+\paragraph{Astrometric information}
+The RUWE (CITE, CITE) for \tn\ is 1.02, indicative that there are no
+obviously present astometric companions.
+
+\subsubsection{Rotation}
+Stellar vsini
+Stellar rotation
+
+\subsubsection{RVs}
+I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
+mass measurement. The reason is that with vsini=17km/s, and 2\%
+rotation amplitude signal, we expect an RV RMS of 300m/s at the
+Prot=3.5 day rotation period (vsini*rotation amplitude). This is
+probably larger than the expected planet signal (100m/s, 8 days).
+
+\subsection{The Planet}
+\label{subsec:planet}
+
+\subsubsection{Transit Fitting}
 Simultaneous dip plus rotation period (GP) fit. Use celerite plus PyMC3/exoplanet.
@@
 
-\subsection{Additional Transits}
+\subsubsection{Additional Transits}
 
@@
 
-In context,...
-
-\section{Conclusions}
-\label{sec:conclusions}
+Rossiter measurements will confirm.
+
+After, a mass measurement should be worthwhile.
+
+We'll get more TESS data in January(?).
 

### 2020-06-18 paper/collect.sh

@@ -5,22 +5,24 @@ pdir=../results/paper_plots/
 
 cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
 
-cp ${rdir}TOI_837_transit_phot_results/20200518/TOI_837_transit_phaseplot.pdf f2.pdf
+cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
 
-cp ${pdir}scene.pdf f3.pdf
+cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
 
-cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.pdf
+cp ${rdir}radvel_fitting/20200525_simple_planet/TOI837_rv_multipanel.pdf f3.pdf
 
-cp ${rdir}lithium/lithium.pdf f5.pdf
+cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
 
-cp ${rdir}rotation/rotation.pdf f9.pdf
+cp ${pdir}scene.pdf f5.pdf
 
-cp ${pdir}toi_837_sed.png f6.png
+cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f6.pdf
 
 cp ${rdir}cluster_membership/hr.pdf f7.pdf
 
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
 
-cp ${rdir}fpscenarios/fpscenarios.pdf f10.pdf
+cp ${rdir}lithium/lithium.pdf f9a.pdf
 
-cp ${rdir}TOI_837_transit_phot_results/20200518/TOI_837_transit_grounddepth.pdf f11.pdf
+cp ${rdir}rotation/rotation.pdf f9b.pdf
+
+# cp ${pdir}toi_837_sed.png f6.png

### 2020-06-18 paper/ms.tex
WIP manuscript

@@
   Cluster Difference Imaging Photometric Survey (CDIPS) II:
-  Validatation of a Jupiter-Sized Planet in IC~2602
+  A Validated Jupiter-Sized Planet in IC~2602
 }
@@
 
+% TODO: SpType subtype?
 \begin{abstract}
@@
   2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
-  concern, as they usually are indicative of astrophysical false
+  concern: they usually are indicative of astrophysical false
   positive scenarios.  Our follow-up data render such scenarios highly
@@
   are limited by speckle imaging, but formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent exoplanet
-  orbiting a bright host star.
-  Further analysis of its mass, atmosphere, and obliquity should
-  confirm its planetary nature beyond doubt, and are worthwhile
-  because young planets are expected to do interesting things.
+  possibility.  TOI 837.01 is therefore a validated adolescent
+  exoplanet.  Further analysis of its mass, atmosphere, and obliquity
+  should confirm its planetary nature beyond doubt, and will improve
+  our understanding of how the physical and orbital properties of
+  exoplanets change in time.
 \end{abstract}
 
-%FIXME these keywords.
 \keywords{
-	Exoplanets (XXX),
+	Exoplanets (498),
+  Transits (1711),
 	Exoplanet evolution (491),
 	Stellar ages (1581),
-	Young star clusters (XXX)
+	Young star clusters (1833)
 }
@@
 
-Recently, young planets have been hype.
-
-%TODO: pull from the cdips repo! I already wrote a lot of this...
-
-TESS \citep{ricker_transiting_2015}.
+Over the first hundred million years of their lives, exoplanetary
+systems are expected to undergo major physical and dynamical changes.
+For a typical Sun-like star, the protoplanetary disk is observed to
+dissipate within $\sim$3 million years (CITE).  The planet formation
+process presumably finishes within this time for gas giants (CITE).
+The rocky planet population will also be mostly evolved within $\sim$3
+million years (CITE), but it may undergo significant changes over the
+next $\sim$10-100 million years through giant impacts.  In the solar
+system, for instance, the Moon was thought to be formed at an age of
+XX million years through such an impact (CITE).
+
+A number of other processes are thought to happen relatively quickly.
+Physical changes in the sizes of planets are expected as they
+contract, and as their atmospheres undergo photoevaporation (CITE,
+CITE).  The relative importance of these two processes is set by the
+planetary mass, as well as the radiation environment.
+Photoevaporation in particular can be directly observed in {\it e.g.},
+the He 10830\AA\ line (CITE, CITE).  Dynamical changes are expected in
+the semi-major axes, eccentricities, and stellar obliquities of young
+planets.  When the gas disk is present, the planetary semi-major axis
+is thought to change due to viscous coupling (CITE).
+High-eccentricity migration processes including planet-planet
+scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
+(CITE) can also occur.  The circularization timescale is thought to be
+such that for any giant planets that migrated early, their orbits
+should circularize within 100 million years (CITE).
+
+The topic of exoplanetary evolution through time has enticed many
+observers.  However, since most dwarf stars do not appreciably change
+until evolving off the main sequence, creative approaches must be used
+to infer stellar ages \citep{soderblom_ages_2010}.  One approach
+beginning to bear fruit in exoplanet studies is to search for planets
+in coeval groups of stars, hereafter ``clusters''.  This includes the
+open clusters of yore, as well as the moving groups and stellar
+associations that began to be uncovered in the late 1990s
+\citep{zuckerman_young_2004}.  The ages of these stellar ensembles are
+inferred through isochrone analyses of color-magnitude diagrams, using
+a combination of main-sequence turnoff locations,
+pre-main-sequence isochronal tracks, and averaged MS isochronal ages
+across known cluster members \citep[{\it e.g.},][Section
+3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
+also be used to verify the age of a stellar ensemble (CITE: Angus too) \citep[{\it
+e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
+The ages of planets discovered in these cluster stars are then assumed
+to equal the age of the larger stellar ensemble.
+
+The first planets to be detected in open clusters were found through
+radial velocity (RV) measurements of red giants in the Hyades and
+NGC~2423 \citep{Sato_et_al_2007,lovis_mayor_2007}.  Subsequent
+spectroscopic searches in Praesepe led to the detection of the first
+hot Jupiter in a cluster \citep{Quinn_et_al_2012}, and also the first
+multi-planet system in a cluster \citep{Malavolta_et_al_2016}.
+Surveys of pre-main sequence T Tauri stars in the Taurus star-forming
+region have also led to the youngest hot Jupiters yet reported
+\citep[V830~Tau~b and
+CI~Tau~b][]{donati_hj_2016,johns-krull_candidate_2016,flagg_co_2019}.
+A final RV survey of note was conducted by
+\citet{brucalassi_search_2017}, who followed 88 stars in M~67 over 7
+years.  They reported detections of three hot Jupiters around main
+sequence stars, and of one giant planet around an evolved star.
+
+The transit method was comparatively slow to catch up.  Deep transit
+searches typically comprising days to weeks of observations were
+performed for NGC~2158, 6791, and 1245, among other clusters
+\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006}.
+Related projects include a search of M~37 by
+\citet{hartman_MMT_IV_2009}, of Praesepe by
+\citet{pepper_photometric_2008}, and of nine young clusters in the
+solar neighborhood by the Monitor team
+\citep{aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008}.
+Though these studies led to measurements of stellar rotation periods
+\citep{hartman_rotation_2009,Irwin_NGC2516_2007} as well as the
+discovery of pre-main-sequence (PMS) eclipsing binaries (EBs)
+\citep{irwin_monitor_PMSEB_2007}, no definitive transiting planets in
+open clusters were found.  Transit searches in globular clusters were
+similarly met with null results \citep{gilliland_lack_2000,
+weldrake_searching_2006} (CITE: Masuda).  These searches were
+typically sensitive to planets larger than Jupiter, on $\lesssim 3$
+day orbital periods.  Hot Jupiter occurrence rate limits were derived
+at the $\lesssim 5\%$ level \citep[{\it e.g.},][]{burke_survey_2006,
+hartman_MMT_IV_2009}.  The modern 0.5-1\% occurrence rate suggests
+that these early transit surveys needed a greater data volume, at
+higher precision for detection to be possible
+\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
+
+Kepler \citep{borucki_kepler_2010} observed enough stars for long
+enough and with sufficient precision to detect transiting planets in
+open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
+\citep{Meibom_et_al_2013}.  Though a broken reaction wheel ended the
+prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
+switched between fields along the ecliptic every quarter-year, and was
+able to observe far more clusters and young stars.  The resulting
+discoveries made by K2 through its surveys of the Pleiades, Hyades,
+Praesepe, and Upper Sco were a major inspiration for the present work.
+
+K2-25b, discovered in the Hyades, has a radius ($3.43\,R_\oplus$) that
+is larger than older Kepler planets around M dwarfs at similar insolation levels
+\citep{Mann_K2_25_2016}.  This inflated radius is perhaps a hint that
+the planet is contracting, or losing its atmosphere \citep[{\it
+e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
+super-Neptune sized K2-33b ($P\approx 5.4\,{\rm d}$), found in Upper
+Sco, showed that at least some close-in planets must form within about
+10 Myr \citep{Mann_K2_33b_2016,David_et_al_2017}.  Further discoveries
+included six transiting planets in Praesepe
+\citep{obermeier_k2_2016,Mann_et_al_2017}, a long-period candidate
+super-Earth in the Hyades \citep{vanderburg_zeitVII_2018}, the
+three-planet K2-136 system in the Hyades
+\citep{ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018}, and
+later the two-planet system K2-264 in Praesepe
+\citep{rizzuto_zeitVIII_2018,livingston_k2-264_2019}.  There has also
+recently been a detection by K2 of a Jupiter-sized planet orbiting
+every 24 days around V1298~Tau \citep{david_v1298_2019}.
+
+A significant amount of effort continues to be devoted towards the
+discovery and characterization of planets around young stars.
+Sometimes, cluster membership may not even be necessary, if a star's
+youth can be inferred from combined rotation, activity, and kinematic
+indicators \citep[{e.g.}, K2-233;][]{david_k2-233_2018}.  To
+investigate demographics in time, the detection sensitivities and
+reliabilities of these searchers need to be calibrated, likely with a
+machinery similar to that outlined by \citet{rizzuto_zeitV_2017}.  A
+separate requirement for population studies to be statistically
+robust, imposed by the geometric rarity of transits, is that many tens
+of thousands of stars with known ages must be monitored at high
+precision.
+
+The TESS mission \citep{ricker_transiting_2015}, though designed for
+other purposes, holds the promise to deliver the most homogeneous and
+comprehensive cluster photometric survey in history.  More
+quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
+database indicates that $\approx 2\times10^5$ open cluster members
+brighter than $T=16$ will be observed in the full-frame images over
+the first two years of TESS observations.  This count includes the
+``most probable'' members within each cluster's radius, which by the
+\citet[][]{kharchenko_global_2012} definition requires the independent
+kinematic, photometric, and spatial membership probabilities to each
+exceed 61\%.  The actual number of stars in clusters may be larger, as
+the membership catalogs are not yet complete, even at these relatively
+bright magnitudes \citep[{\it
+e.g.},][]{roser_nine_RSG_2016,cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
 

### 2020-06-19 paper/ms.tex
minor

@@
 \title{
-  Cluster Difference Imaging Photometric Survey (CDIPS) II:
-  A Validated Jupiter-Sized Planet in IC~2602
+  Cluster Difference Imaging Photometric Survey (CDIPS) II.
+  TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602
 }
@@
   Pleiades'').  The star and validated planet are therefore 30$\pm$20
-  million years old.  The planet is warm ($P = 8.YY\,{\rm d}$) and
+  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
   roughly Jupiter-sized.  However, its transits are grazing: $b >
@@
   concern: they usually are indicative of astrophysical false
-  positive scenarios.  Our follow-up data render such scenarios highly
-  unlikely.  Multi-color photometry requires eclipsing companions to
-  have nearly identical color as TOI$\,$837, eliminating hierarchical
-  eclipsing binary scenarios.  Background eclipsing binary scenarios
-  are limited by speckle imaging, but formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent
-  exoplanet.  Further analysis of its mass, atmosphere, and obliquity
-  should confirm its planetary nature beyond doubt, and will improve
-  our understanding of how the physical and orbital properties of
-  exoplanets change in time.
+  positive scenarios.  Our follow-up data show that such scenarios are
+  highly unlikely.  Multi-color photometry requires eclipsing
+  companions to have nearly identical color as TOI$\,$837, ruling out
+  hierarchical eclipsing binary scenarios.  Background eclipsing
+  binary scenarios are limited by speckle imaging, but formally remain
+  a 0.2\% possibility.  TOI 837.01 is therefore a validated adolescent
+  exoplanet.  Further observations of its stellar obliquity,
+  atmosphere, and mass should confirm its planetary nature beyond
+  doubt, and could improve our understanding of how the physical and
+  orbital properties of exoplanets change in time.
 \end{abstract}

### 2020-06-19 timmy/plotting.py

@@ -1101,12 +1101,14 @@ def plot_hr(outdir):
         target_df['phot_bp_mean_mag']-target_df['phot_rp_mean_mag'],
         target_yval,
         alpha=1, mew=0.5, zorder=8, label='TOI 837', markerfacecolor='yellow',
-        markersize=9, marker='*', color='black', lw=0
+        markersize=14, marker='*', color='black', lw=0
     )
 
     ax.legend(loc='best', handletextpad=0.1, fontsize='x-small', framealpha=0.7)
-    ax.set_ylabel('G + $5\log_{10}(\omega_{\mathrm{as}}) + 5$', fontsize='large')
-    ax.set_xlabel('Bp - Rp', fontsize='large')
+    # ax.set_ylabel('G + $5\log_{10}(\omega_{\mathrm{as}}) + 5$', fontsize='large')
+    # ax.set_xlabel('Bp - Rp', fontsize='large')
+    ax.set_ylabel('Absolute G [mag]', fontsize='large')
+    ax.set_xlabel('Bp - Rp [mag]', fontsize='large')
 
     ylim = ax.get_ylim()
     ax.set_ylim((max(ylim),min(ylim)))
@@ -1303,9 +1305,9 @@ def plot_full_kinematics(outdir):
                 zorder=3, s=5, rasterized=True, linewidths=0, label='Members'
             )
             axs[i,j].plot(
-                target_df[xv], target_df[yv], alpha=1, mew=0.5, zorder=8,
-                label='TOI 837', markerfacecolor='yellow', markersize=9, marker='*',
-                color='black', lw=0
+                target_df[xv], target_df[yv], alpha=1, mew=0.5,
+                zorder=8, label='TOI 837', markerfacecolor='yellow',
+                markersize=14, marker='*', color='black', lw=0
             )
 
             # set the axis limits as needed
@@ -2008,7 +2010,7 @@ def plot_lithium(outdir):
         TEFF,
         LI_EW,
         alpha=1, mew=0.5, zorder=8, label='TOI 837', markerfacecolor='yellow',
-        markersize=10, marker='*', color='black', lw=0
+        markersize=14, marker='*', color='black', lw=0
     )
 
     ax.legend(loc='best', handletextpad=0.1, fontsize='x-small', framealpha=0.7)
@@ -2052,7 +2054,7 @@ def plot_rotation(outdir):
         TEFF,
         P_ROT,
[…]

### 2020-06-22 paper/ms.tex
update manuscript

--- 2020-06-18 paper/ms.tex
@@
 
+\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
+\newcommand{\datasetlink}{\textsc{\dataset[doi.org/10.17909/t9-ayd0-k727]{https://doi.org/10.17909/t9-ayd0-k727}}}
+
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2.
@@
 \title{
-  Cluster Difference Imaging Photometric Survey (CDIPS) II:
-  Validatation of a Jupiter-Sized Planet in IC~2602
+  Cluster Difference Imaging Photometric Survey (CDIPS) II.
+  TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602
 }
@@
   2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
-  concern, as they usually are indicative of astrophysical false
-  positive scenarios.  Our follow-up data render such scenarios highly
-  unlikely.  Multi-color photometry requires eclipsing companions to
-  have nearly identical color as TOI$\,$837, eliminating hierarchical
-  eclipsing binary scenarios.  Background eclipsing binary scenarios
-  are limited by speckle imaging, but formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent exoplanet
-  orbiting a bright host star.
-  Further analysis of its mass, atmosphere, and obliquity should
-  confirm its planetary nature beyond doubt, and are worthwhile
-  because young planets are expected to do interesting things.
+  concern: they usually are indicative of astrophysical false
+  positive scenarios.  Our follow-up data show that such scenarios are
+  highly unlikely.  Multi-color photometry requires eclipsing
+  companions to have nearly identical color as TOI$\,$837, ruling out
+  hierarchical eclipsing binary scenarios.  Background eclipsing
+  binary scenarios are limited by speckle imaging, but formally remain
+  a 0.2\% possibility.  TOI 837.01 is therefore a validated adolescent
+  exoplanet.  Further observations of its stellar obliquity,
+  atmosphere, and mass should confirm its planetary nature beyond
+  doubt, and could improve our understanding of how the physical and
+  orbital properties of exoplanets change in time.
 \end{abstract}
 
-%FIXME these keywords.
 \keywords{
-	Exoplanets (XXX),
+	Exoplanets (498),
+  Transits (1711),
 	Exoplanet evolution (491),
 	Stellar ages (1581),
-	Young star clusters (XXX)
+	Young star clusters (1833)
 }
@@
 
-Recently, young planets have been hype.
-
-%TODO: pull from the cdips repo! I already wrote a lot of this...
-
-TESS \citep{ricker_transiting_2015}.
+Over the first one hundred million years of their lives, exoplanet
+systems are expected to undergo major physical and dynamical changes.
+For a typical Sun-like star, the protoplanetary disk disperses within
+$\sim$3 million years (CITE IR + sub-mm results).  The planet
+formation process presumably finishes within this time for gas giants
+(CITE).  The rocky planet population will also be mostly evolved
+within $\sim$3 million years (CITE), but may undergo significant
+changes over the next $\sim$10-100 million years through giant
+impacts.  The Moon, for instance, is thought to have formed when the
+solar system was XX million years old through such an impact (CITE).
+
+A number of other processes are thought to happen relatively quickly.
+Physical changes in the sizes of planets are expected as they
+contract, and as their atmospheres undergo photoevaporation
+\citep[{\it
+e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
+relative importance of these two processes is set by the planetary
+mass, as well as the radiation environment.  Photoevaporation in
+particular can be directly observed in {\it e.g.}, the He 10830\AA\
+line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in the semi-major
+axes, eccentricities, and stellar obliquities of young planets.  When
+the gas disk is present, the planetary semi-major axis is thought to
+change due to viscous coupling (CITE).  High-eccentricity migration
+processes including planet-planet scattering (CITE), secular chaos
+(CITE), and Kozai-Lidov oscillations (CITE) can also occur.  The
+circularization timescale is thought to be such that for any giant
+planets that migrated early, their orbits should circularize within
+100 million years (CITE).
+
+Finding and studying systems undergoing these evolutionary changes is
+a major goal in contemporary exoplanet research.  To identify stars
+younger than say 1$\,$Gyr, a number of direct and indirect methods
+are available \citep{soderblom_ages_2010}.  The traditional approach
+is to isochronally age-date coeval groups of stars, hereafter ``clusters''
+\citep[{\it
+e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
+Young field stars can also be identified using age indicators such as
+stellar rotation periods, the abundance of photospheric lithium, and
+chromospheric diagnostics such as calcium emission and broadband UV
+emission.  Studies by for instance \citet{david_discovery_2018} and
+G{.}~Zhou et al. (2020, submitted) have combined these methods for
+individual field stars.  Many of the latter methods were summarized by
+\citet{mamajek_improved_2008}, and have since been calibrated by
+{\it e.g.},
+\citet{barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
+and \citet{curtis_tess_2019} for stellar rotation,
+\citet{zerjal_chromospherically_2017} for chromospheric activity, and
+{\it e.g.}, \citet{berger_identifying_2018} and
+\citet{zerjal_galah_2019} for lithium abundances.
+
+A few dozen planets in clusters have been detected, and fewer
+still have been closely characterized.  Despite the challenges of starspot-induced radial
+velocity (RV) variations, RV surveys found success in the
+Hyades, NGC~2523, Praesepe, and M~67
+\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
+RV surveys of highly active pre-main sequence stars in Taurus also led to the
+youngest hot Jupiters yet reported
+\citep{donati_hj_2016,johns-krull_candidate_2016,biddle_k2_2018,flagg_co_2019}.
+
+The transit method was comparatively slow to catch up.  Early deep
+transit searches of open clusters by many groups did not yield
+definitive planet detections
+\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006,aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008,pepper_photometric_2008,hartman_MMT_IV_2009}.
+These searches were typically sensitive to planets larger than
+Jupiter, on $\lesssim 3$ day orbital periods.  Hot Jupiter occurrence
+rate limits were derived at the $\lesssim 5\%$ level \citep[{\it
+e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
+occurrence rate suggests that these early transit surveys needed a
+greater data volume, at higher precision for detection to be possible
+\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
+
+Kepler observed a large enough number of stars 
+with sufficient baseline and precision to detect transiting planets in
+open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
+\citep{borucki_kepler_2010,Meibom_et_al_2013}.  Though a broken reaction wheel ended the
+prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
+switched between fields along the ecliptic every quarter-year, and was
+able to observe far more clusters and young stars.
+
+The discoveries made by K2 through its surveys of Taurus, the Hyades,
+Praesepe, and Upper Sco were a major inspiration for the present work
+\citep[{\it
+e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
+Observations with K2 convincingly showed that at least some close-in
+planets must form within about 10 Myr
+\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
+hints that young planets may in fact be qualtiatively different from
+their field counterparts.  For instance, based on its observed mass,
+radius, and UV environment, the 700$\,$Myr K2-100b is probably
+actively losing its atmosphere, and should become a bare rocky planet
+over the next few hundred Myr
+\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
+planets in V1298~Tau (23$\,$Myr) are also likely to be actively
+photoevaporating, and could represent a precursor to Kepler's compact
+multiple systems \citep{david_four_2019,david_warm_2019}.
+
+With the aim of advancing the young planet census, we have been using
+data from the TESS spacecraft \citep{ricker_transiting_2015} to
+perform a Cluster Difference Imaging Photometric Survey
+\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
+candidate young stars that have been reported in the literature.  At
+the time writing, of order $6\times10^5$ light curves from the first
+year of TESS observations have been reduced, and are available at
+MAST\footnote{\stscilink} through \datasetlink.  Searching these light
+curves yielded the candidate transiting planet, \pn, that is the
+subject of this analysis.
 
@@
 certainly a planet.  Section~\ref{sec:system} presents our knowledge
-of the cluster (Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
-and the planet (Section~\ref{subsec:planet}).  We conclude
-with a discussion in
-Section~\ref{sec:discussion}.
+of the cluster (Section~\ref{subsec:cluster}), the star
+(Section~\ref{subsec:star}) and the planet
+(Section~\ref{subsec:planet}).  We conclude by discussing avenues for
+improved characterization in Section~\ref{sec:discussion}.
 
@@
     {\bf TESS lightcurve of \tn\ (Sectors 10 and 11).}
-    {\it Top}: \texttt{PDCSAP} mean-subtracted relative flux at
-    2-minute sampling. Spot-induced stellar variability is the
+    {\it Top}: \texttt{PDCSAP} median-subtracted relative flux at
+    2-minute sampling in units of parts-per-thousand ($\times 10^{-3}$).
+    Spot-induced stellar variability is the
     dominant signal.  Dashed lines show the five transits observed by
@@
     {\it Bottom}: Zoomed windows of individual transits.  Red points
-    show manually identified stellar flares.
+    highlight manually identified stellar flares.
 		\label{fig:rawzoom}
@@
 
-%TODO: the scale of this plot is off. (Different font-sizes from
-%subplots).
 \begin{figure*}[t]

### 2020-06-22 drivers/fit_alltransit.py

@@ -31,9 +31,9 @@ def main(modelid):
     make_threadsafe = 0
     cut_tess = 1
 
-    phaseplot = 0
-    fittedzoom = 0
+    phaseplot = 1
     grounddepth = 1
+    fittedzoom = 0
     cornerplot = 0
 
     OVERWRITE = 1

### 2020-06-22 timmy/plotting.py

@@ -651,7 +651,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     tra_ixs = [0,2,3,4,5]
 
     # main lightcurve
-    yval = (flux - np.nanmean(flux))*1e3
+    yval = (flux - np.nanmedian(flux))*1e3
     ax0.scatter(time, yval, c='k', zorder=3, s=0.75, rasterized=True,
                 linewidths=0)
     ax0.scatter(time[flaresel], yval[flaresel], c='r', zorder=3, s=1,
@@ -675,7 +675,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
         end_time = mid_time + n*tdur
 
         s = (time > start_time) & (time < end_time)
-        ax.scatter(time[s], (flux[s] - np.nanmean(flux[s]))*1e3, c='k',
+        ax.scatter(time[s], (flux[s] - np.nanmedian(flux[s]))*1e3, c='k',
                    zorder=3, s=7, rasterized=False, linewidths=0)
 
         _flaresel = np.zeros_like(time[s]).astype(bool)
@@ -684,7 +684,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
 
         if np.any(_flaresel):
             ax.scatter(time[s][_flaresel],
-                       (flux[s] - np.nanmean(flux[s]))[_flaresel]*1e3,
+                       (flux[s] - np.nanmedian(flux[s]))[_flaresel]*1e3,
                        c='r', zorder=3, s=8, rasterized=False, linewidths=0)
 
         ax.set_xlim((start_time, end_time))
@@ -712,7 +712,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
     fig.text(-0.01,0.5, 'Relative flux [ppt]', va='center',
              rotation=90, fontsize='x-large')
 
-    fig.tight_layout(h_pad=0.2, w_pad=-1.0)
+    fig.tight_layout(h_pad=0.2, w_pad=-0.5)
     savefig(fig, outpath, writepdf=1, dpi=300)
 
 
@@ -780,7 +780,7 @@ def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
     plt.close('all')
 
     fig, (a0, a1) = plt.subplots(nrows=2, ncols=1, sharex=True,
-                                 figsize=(0.8*6,0.8*4), gridspec_kw=
[…]

### 2020-06-22 paper/ms.tex
update manuscript

@@
 particular can be directly observed in {\it e.g.}, the He 10830\AA\
-line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in the semi-major
-axes, eccentricities, and stellar obliquities of young planets.  When
-the gas disk is present, the planetary semi-major axis is thought to
-change due to viscous coupling (CITE).  High-eccentricity migration
-processes including planet-planet scattering (CITE), secular chaos
-(CITE), and Kozai-Lidov oscillations (CITE) can also occur.  The
-circularization timescale is thought to be such that for any giant
-planets that migrated early, their orbits should circularize within
-100 million years (CITE).
+line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in
+the semi-major axes, eccentricities, and stellar obliquities of young
+planets.  When the gas disk is present, the planetary semi-major axis
+is thought to change due to viscous coupling (CITE).
+High-eccentricity migration processes including planet-planet
+scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
+(CITE) can also occur.  The circularization timescale is thought to be
+such that for any giant planets that migrated early, their orbits
+should circularize within 100 million years (CITE).
 
@@
 a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1$\,$Gyr, a number of direct and indirect methods
-are available \citep{soderblom_ages_2010}.  The traditional approach
-is to isochronally age-date coeval groups of stars, hereafter ``clusters''
+younger than say 1$\,$Gyr, a number of direct and indirect methods are
+available \citep{soderblom_ages_2010}.  The traditional approach is to
+isochronally age-date coeval groups of stars, hereafter ``clusters''
 \citep[{\it
@@
 individual field stars.  Many of the latter methods were summarized by
-\citet{mamajek_improved_2008}, and have since been calibrated by
-{\it e.g.},
+\citet{mamajek_improved_2008}, and have since been calibrated by {\it
+e.g.},
 \citet{barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
@@
 
-A few dozen planets in clusters have been detected, and fewer
-still have been closely characterized.  Despite the challenges of starspot-induced radial
-velocity (RV) variations, RV surveys found success in the
-Hyades, NGC~2523, Praesepe, and M~67
+A few dozen planets in clusters have been detected, and fewer still
+have been closely characterized.  Despite the challenges of
+starspot-induced radial velocity (RV) variations, RV surveys found
+success in the Hyades, NGC~2523, Praesepe, and M~67
 \citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
-RV surveys of highly active pre-main sequence stars in Taurus also led to the
-youngest hot Jupiters yet reported
+RV surveys of highly active pre-main sequence stars in Taurus also led
+to the youngest hot Jupiters yet reported
 \citep{donati_hj_2016,johns-krull_candidate_2016,biddle_k2_2018,flagg_co_2019}.
@@
 
-Kepler observed a large enough number of stars 
-with sufficient baseline and precision to detect transiting planets in
-open clusters:  Kepler-66b and 67b, in the gigayear-old NGC~6811
-\citep{borucki_kepler_2010,Meibom_et_al_2013}.  Though a broken reaction wheel ended the
-prime Kepler mission, the repurposed K2 \citep{howell_k2_2014}
-switched between fields along the ecliptic every quarter-year, and was
-able to observe far more clusters and young stars.
+Kepler observed a large enough number of stars with sufficient
+baseline and precision to detect transiting planets in open clusters:
+Kepler-66b and 67b, in the gigayear-old NGC~6811
+\citep{borucki_kepler_2010,Meibom_et_al_2013}.  Though a broken
+reaction wheel ended the prime Kepler mission, the repurposed K2
+\citep{howell_k2_2014} switched between fields along the ecliptic
+every quarter-year, and was able to observe far more clusters and
+young stars.
 
@@
 
+\subsection{TESS Photometry}
+\label{subsec:tess}
+
 \begin{figure*}[t!]
@@
 	\caption{
-    {\bf TESS lightcurve of \tn\ (Sectors 10 and 11).}
-    {\it Top}: \texttt{PDCSAP} median-subtracted relative flux at
-    2-minute sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Spot-induced stellar variability is the
-    dominant signal.  Dashed lines show the five transits observed by
-    TESS.
-    {\it Bottom}: Zoomed windows of individual transits.  Red points
-    highlight manually identified stellar flares.
+    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
+    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
+    sampling in units of parts-per-thousand ($\times 10^{-3}$).
+    Spot-induced stellar variability is the dominant signal.  Dashed
+    lines show the five transits observed by TESS.  {\it Bottom}:
+    Zoomed windows of individual transits.  Red points are manually
+    identified stellar flares.
 		\label{fig:rawzoom}
@@
 	\vspace{-0.7cm}
-	\caption{ {\bf Joint TESS and multicolor photometry.}
-    {\it Top:} Phase-folded TESS transit. Gray points are 2-minute
-    PDCSAP flux measurements, detrended with a 0.3-day robust Huber
-    spline (see Section~\ref{subsec:tess}).  Black points are binned
-    to 6 minute intervals.  The line shows the transit model
-    corresponding to the median transit parameters (Table~2).
-    {\it Bottom:} Multicolor photometry from the El Sauce 0.36m.
-    The consistent transit depths between TESS-band and the bluer
-    Cousins-R and Johnson-B bandpasses rules out select false positive
-    scenarios.
+  \caption{
+    {\bf Joint TESS and multicolor photometry.} {\it Top:}
+    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
+    measurements, detrended with a 0.3-day robust Huber spline (see
+    Section~\ref{subsec:tess}).  Black points are binned to 6 minute
+    intervals.  The line shows the transit model corresponding to the
+    median transit parameters (Table~2).  {\it Bottom:} Multicolor
+    photometry from the El Sauce 0.36m.  The consistent transit depths
+    between TESS-band and the bluer Cousins-R and Johnson-B bandpasses
+    rules out select false positive scenarios.
     \label{fig:jointphot}
@@
 
-\begin{figure}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.47\textwidth]{f3.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-		{\bf Radial velocities.}
-		\label{fig:rvs}
-	}
-\end{figure}
-
-\begin{figure*}[t!]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=1\textwidth]{f4.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-		{\bf Astrophysical false positive scenarios.}
-		{\it Top}: for bound companions,
-		{\it Bottom}: for unassociated companions along the same line of
-		sight.
-		\label{fig:fpscenario}
-	}
-\end{figure*}
+\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
+the tenth and eleventh sectors of science operations
+\citep{ricker_transiting_2015}.  The star was designated
+TIC\,460205581 in the TESS Input Catalog
+\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
+$11\times11$ array surrounding the star were averaged and saved at
+2-minute cadence.  The $2048\times2048$ image from the entire CCD was
+also averaged into 30-minute stacks, and saved as a ``full frame
+image'' (FFI).
+
+The TESS project detected the transits in the 2-minute data and the
+community was alerted on 17 June 2019.  While our CDIPS FFI light
+curves also show the transits, the 2-minute data have better sampling
+cadence, and so we opted to use the Presearch Data Conditioning (PDC)
+light curve with the default aperture for our
+analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.
+
+Figure~\ref{fig:rawzoom} shows the data.  The dominant modulation
+induced by starspots coming into and out of view has a peak-to-peak
+amplitude of about 2.3\%, and a period of about 3 days.  The dips
+suggestive of a grazing transiting planet recur roughly every 8 days,
+and have a depth of about 0.4\%.  A few flares are visible.  A
+phase-folded version of the TESS transits with starspot variability
+removed is shown in Figure~\ref{fig:jointphot}, and is described in
+depth in Section~\ref{subsec:planet}.
+
+\subsection{Gaia Astrometry and Imaging}
+\label{subsec:gaia}
 
@@
 
+Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
+about 300 billion centroid positions of 1{.}6 billion stars.  The
+positions, proper motions, and parallaxes of the brighest 1{.}3
+billion were calculated for the second data release (DR2)
+\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
+\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
+276 ``good'' astrometric observations. Its brightness was measured in
+the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
+\citep{cropper_gaia_2018,evans_gaia_2018}.
+
+The Gaia imaging, as represented by its point-source catalog, provides
+the initial context for analyzing the TESS data.  Stars brighter than
+$T=16$, as queried from the Gaia DR2 source catalog, are shown with
+orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
+and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
+not surprising that the field of \tn\ is crowded.  The stars that were
+of immediate concern for our false positive analysis were as follows.
+\begin{itemize}
+  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
+  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
+    proper motions and parallax of this star imply it is comoving with
+    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
+    it may not be bound.
+  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
+    Gaia parallax implies this is a giant background star.
+\end{itemize}
+An additional source, TIC 847769581, is $4.9$'' from the target, but
+too faint (T=18.8) to be the source of the observed transit signal.
+
+The Gaia DR2 data for Star A seems poorly behaved.  While
+Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
+Correspondingly, no RUWE\footnote{ See the Gaia
+DPAC technical note GAIA-C3-TN-LU-LL-124-01,
+\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
+2020-06-22. } value is available.  The astrometric
+reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
+astrometric observations) seems rather poor, at $8.6$.  We suspect
+that the photometric failure to produce an $Rp$ magnitude, as well as
+the poor astrometric fit, are likely due to blending with \tn.
+
+At the $\approx1'$ resolution of the TESS data, if either Star A
+or Star B were eclipsing binaries, they could be the sources of the
+transit signal.  A detailed analysis of ground-based seeing-limited
+photometry was necessary to assess and rule out this possibility
+(Section~\ref{subsec:groundphot}).
+
+\subsection{High-Resolution Imaging}
+\label{subsec:speckle}
+
 \begin{figure}[t]
@@
     {\bf SOAR HRCam contrast limits derived from point-source
-			injection-recovery experiments.} 
-		Star A ($\Delta T=4.7$, $\rho=2.3$'' west) is detected in the
-		autocorrelation function, in addition to being a resolved Gaia
-		source.
-		It is co-moving with \tn, and
-		its parallax and on-sky position imply that
-		it is physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
+    injection-recovery experiments.} Star A ($\Delta T=4.7$,
+    $\rho=2.3$'' west) is detected in the autocorrelation function, in
+    addition to being a resolved Gaia source.  It is co-moving with
+    \tn, and its parallax and on-sky position imply that it is
+    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
 		\label{fig:soar}
@@
 \end{figure}
+
+To determine if any fainter point sources existed closer to \tn\
+inside of Gaia's point-source detection limits, we acquired
+high-resolution speckle images. We then searched the autocorrelation
+functions of these images for peaks indicative of nearby companions.
+
+{\bf Carl TODO: please describe and correct as appropriate}
+The observations of \tn\ were initially acquired by
+\citet{ziegler_soar_2020} as part of the Southern Astrophysical
+Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
+\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
+by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:soar}
+show the resulting measured 5-$\sigma$ detectable contrasts.  The
+lines are linear smoothing fits between the regimes of the diffraction
+limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
+$\approx 1.5''$, beyond which the speckle patterns become
+de-correlated.  Star A (TIC 847769574) was detected at the expected
+location and brightness contrast, and no additional companions were
+found.
+
+\subsection{Ground-based Time-Series Photometric Follow-up}
+\label{subsec:groundphot}
+
+We obtained ground-based seeing-limited time series photometric
+observations of \tn\ bracketed around the times of transit.  These
+observations confirmed that the transits occurred on-target to within
+$\approx 2''$, and that they were achromatic. Both features are
+essential for our ability to eliminate false-positive scenarios.
+
+\subsubsection{El Sauce 0.36m}
+
+We observed four transits with the 0.36m at Observatario El Sauce,
+located in the R\'io Hurtado Valley in Chile, and operated by
+co-author P{.}~Evans.  The observations were obtained in Cousins-R
+band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
+on the night of 21 May 2020, and Johnson-B band on the night of 14
+June 2020.  The final 14 June transit began shortly after twilight.
+
+{\bf Phil + Karen TODO: please correct as appropriate}
+We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
+The photometric data were calibrated and extracted using the
+\texttt{AstroImageJ} software package
+\citep{collins_astroimagej_2017}.  Comparison stars of similar
+brightness were used to produce the final light curves, each of which
+showed a roughly 4$\,$ppt dip near the expected transit time.
+We produced and examined light curves with at custom positions and
+with custom aperture sizes, and...
+
+The data were reduced using... (e.g., astroimageJ)
+
+{\bf LGB TODO: Describe custom analysis of apertures}
+
+\subsubsection{ASTEP400}
+
+{\bf Amaury TODO: please correct as appropriate}
+We observed {\bf N} transits with the 0.40m ASTEP 400 telescope at
+Concordia Station, located at Dome C on the Antarctic Plateau
+\citep{daban_astep_2010}.  ASTEP 400 has a dichroic that sends blue
+wavelengths to a guiding camera, and red wavelengths to a filter-free
+science camera with wavelength sensitivity roughly akin to R band.
+The observations were acquired on the nights of {\bf DATE 1} and {\bf
+DATE 2}.  The outdoor temperature was a balmy {\bf XX$^\circ$}.  The
+data were reduced using {\bf XX} software, and showed the transit
+roughly at the expected time and depth.
+
+\subsection{Spectroscopic Follow-up}
+\label{subsec:spectra}
 
@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f7.pdf}
+		\includegraphics[width=0.47\textwidth]{f3.pdf}
 	\end{center}
@@
 	\caption{
-  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
-  Members (black circles) were identified by
-  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
-  within 5 standard deviations of the mean \cn\ right ascension,
-  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
-  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
-  arcseconds. 
-  \label{fig:hr}
+		{\bf Radial velocities.}
+		\label{fig:rvs}
 	}
 \end{figure}
+
+\subsubsection{CHIRON}
+9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
+6 were usable.
+
+\subsubsection{FEROS}
+N spectra with XXX/FEROS
+
+\subsubsection{Veloce}
+M spectra with AAT/Veloce.
+
+\section{Elimination of False Positive Scenarios}
+\label{sec:validation}
 
@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{f8.pdf}
+		\includegraphics[width=1\textwidth]{f4.pdf}
 	\end{center}
@@
 	\caption{
-  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
-  circles), and stars in the neighborhood (gray circles).} Members
-  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
-  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
-  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
-  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
-  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
-  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
-  \alpha}\cos\delta$) highlights the membership selection function.
-  \label{fig:full_kinematics}
+		{\bf Astrophysical false positive scenarios.}
+		{\it Top}: for bound companions,
+		{\it Bottom}: for unassociated companions along the same line of
+		sight.
+		\label{fig:fpscenario}
 	}
 \end{figure*}
-
-\begin{figure}[t]
-	\begin{center}
-		\leavevmode
-		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9a.pdf}
-		}
-
-		\vspace{-0.5cm}
-		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9b.pdf}
-		}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ {\bf Youth diagnostics.}
-    {\it Top:} Lithium 6708\AA\ equivalent widths for \tn, field
-    stars, and young open clusters.  The field star sample is drawn
-    from Kepler planet hosts, and was measured by
-    \citet{berger_identifying_2018} using Keck-HIRES.  The young open
-    clusters members were surveyed by \citet{randich_gaiaeso_2018}
-    using the UVES and GIRAFFE spectrographs at the ESO VLT.
-    \citet{randich_gaiaeso_2018} found lithium depletion boundary ages
-    for these clusters of $37.7^{+5.7}_{-4.8}\,{\rm Myr}$
-    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  {\it
-    Bottom:} Rotation periods for \tn\ and selected open clusters.
-    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
-    (1000$\,$Myr) are shown.  Their rotation periods were measured by
-    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
-    and \citet{curtis_temporary_2019}, respectively.
-    \label{fig:lithium_rotation}
-	}
-\end{figure}
-
-\subsection{TESS Photometry}
-\label{subsec:tess}
-
-\tn\ (GAIA DR2 5251470948229949568) was observed by the
-TESS spacecraft from X to Y in two-minute cadence mode.
-The star was designated
-TIC\,460205581 in the TESS Input Catalog
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.
-%FIXME make words more original
-The pixel data for an
-$11\times11$ array surrounding \tn\ were averaged into 2-minute
-stacks by the onboard computer.  Each 2048$\times$2048 image from the
-CCD was also averaged into 30-minute stacks, and saved as a ``full
-frame image'' (FFI).
-
-%FIXME make words more original
-The pixel data for an
-The 2-minute stacks for \tn\ were reduced to lightcurves by the
-Science Processing Operations Center (SPOC) at NASA
-Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
-Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
-pixels chosen to maximize the SNR of the total flux of the target
-\citep{smith_finding_2016}.  Non-astrophysical variability
-was removed by fitting out trends common to many stars
-\citep{smith_kepler_2012,stumpe_multiscale_2014}.
-
-%FIXME make words more original
-As an independent check on the 2-minute SPOC lightcurve, we examined
-the lightcurve based upon 30-minute image stacks which was produced as
-part of the Cluster Difference Imaging Photometric Survey (CDIPS;
-\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
-circular aperture with radius 1 pixel.
-
-%TODO: describe 0.3-day robust Huber spline
-
-Figure~\ref{fig:rawzoom}.
-
-\subsection{Ground-based Time-Series Photometry}
-\label{subsec:groundphot}
-
-\subsection{Imaging}
-
-\subsection{Spectroscopy}
-
-\subsubsection{CHIRON}
-9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
-6 were usable.
-
-\subsubsection{FEROS}
-N spectra with XXX/FEROS
-
-\subsubsection{Veloce}
-M spectra with AAT/Veloce.
-
-\subsection{Astrometry}
-
-\section{Elimination of False Positive Scenarios}
-\label{sec:validation}
 
@@
 \subsubsection{Gaia Imaging}
-Figure~\ref{fig:scene} shows the scene as viewed in the DSS2 plates
-and by TESS.  In the upper panels, the pixels used to measure the
-background level in the SPOC lightcurve are indicated with
-`\texttt{X}' hatching, and the pixels used in the final lightcurve
-aperture are shown with `\texttt{/}' hatching.
-
-Stars brighter than $T=16$, as queried from the Gaia DR2 source
-catalog, are shown with orange circles.  Given its galactic latitude
-of $b=-6^\circ$, it is not surprising that the field of \tn\ is
-crowded.  The stars that were of immediate concern for a blend
-analysis were as follows.
-\begin{itemize}
-  \item \tn\ = TIC 460205581 (T=9.9). The target star.
-  \item Star A = TIC 847769574 (T=14.6). $2.3$'' west. Proper motions
-    and parallax imply it is comoving with \tn, though with a physical
-    separation of $6.6\pm 0.1\,{\rm pc}$, it may not be bound.
-  \item Star B = TIC 460205587 (T=13.1). $5.4$'' north.  This is a
-    giant background star.
-\end{itemize}
-An additional source, TIC 847769581, is $4.9$'' from the target, but
-too faint (T=18.8) to be the source of the observed transit signal.
-
-The Gaia DR2 data for Star A seems poorly behaved.  While
-Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
-Correspondingly, no RUWE value is available (CITE).  The astrometric
-reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
-astrometric observations) seems rather poor, at $8.6$.  We suspect
-that the photometric failure to produce an $Rp$ magnitude, as well as
-the poor astrometric fit, are likely due to blending with \tn.
-
-At the angular resolution of the TESS data, if either Star A or Star B
-were eclipsing binaries, they could be the sources of the transit
-signal.  We ruled out both Star A and Star B as hosts of the eclipse
-through a detailed analysis of the ground-based seeing-limited
-photometry (\S~\ref{subsec:groundphot}).
+{\it empty}
 
 \subsubsection{Speckle Imaging}
-
-Additional point-sources could be present beyond the angular
-resolution of the Gaia source catalog.
-To limit this possibility,
-we imaged the system using SOAR-HRCam, as described in
-\citet{ziegler_soar_2020}.
-{\bf Carl: please describe}.
-The bandpass was a Johnson-Cousins,
-where I is centered at 879 nm and has a width of 289 nm.
-
-Figure~\ref{fig:soar} shows the result.
-Star A (TIC 847769574) is detected as expected, and no additional
-companions are found.
-"""
-The points on the plot are measured 5-sigma detectable contrasts. The
-lines are linear smoothing fits between two regimes. In general, the
-sensitivity of speckle imaging to companions rises sharply from the
-diffraction limit to a ``knee'' at a separation of 0.15--0.2
-arcseconds, where it then continues to slowly increase out to 1.5$''$,
-beyond which the speckle patterns become de-correlated. For this
-target, I suspect the measurement at 1$''$ is slightly larger than
-expected due to some increase in speckle noise at that radius.
-"""
 
@@
 \subsubsection{TESS}
-We examined the CDIPS FFI lightcurves of the target, which are
-available on MAST \citep{bouma_cluster_2019}. Three lightcurves are
+We examined the CDIPS FFI light curves of the target, which are
+available on MAST \citep{bouma_cluster_2019}. Three light curves are
 available, based on photometric apertures with a radius of 1, 1.5, or
@@
 To assess this possibility with the ground-based photometry, we
-produced lightcurves centered on \tn\ with
+produced light curves centered on \tn\ with
 circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
@@
 
-We also created lightcurves with a custom set of $r=2.1''$ apertures
+We also created light curves with a custom set of $r=2.1''$ apertures
 with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
 east of \tn.  We did not detect any variation of the transit depth
-along this line of lightcurves, as would be expected if Star A were
+along this line of light curves, as would be expected if Star A were
 the eclipse host.  The apertures east of \tn\ are particularly
@@
 
+\begin{figure}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.45\textwidth]{f7.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ 
+  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
+  Members (black circles) were identified by
+  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
+  within 5 standard deviations of the mean \cn\ right ascension,
+  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
+  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
+  arcseconds. 
+  \label{fig:hr}
+	}
+\end{figure}
+
+\begin{figure*}[t!]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.9\textwidth]{f8.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ 
+  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
+  circles), and stars in the neighborhood (gray circles).} Members
+  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
+  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
+  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
+  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
+  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
+  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
+  \alpha}\cos\delta$) highlights the membership selection function.
+  \label{fig:full_kinematics}
+	}
+\end{figure*}
+
+\begin{figure}[t]
+	\begin{center}
+		\leavevmode
+		\subfloat{
+			\includegraphics[width=0.45\textwidth]{f9a.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.45\textwidth]{f9b.pdf}
+		}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{ {\bf Youth diagnostics.}
+    {\it Top:} Lithium 6708\AA\ equivalent widths for \tn, field
+    stars, and young open clusters.  The field star sample is drawn
+    from Kepler planet hosts, and was measured by
+    \citet{berger_identifying_2018} using Keck-HIRES.  The young open
+    clusters members were surveyed by \citet{randich_gaiaeso_2018}
+    using the UVES and GIRAFFE spectrographs at the ESO VLT.
+    \citet{randich_gaiaeso_2018} found lithium depletion boundary ages
+    for these clusters of $37.7^{+5.7}_{-4.8}\,{\rm Myr}$
+    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  {\it
+    Bottom:} Rotation periods for \tn\ and selected open clusters.
+    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
+    (1000$\,$Myr) are shown.  Their rotation periods were measured by
+    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
+    and \citet{curtis_temporary_2019}, respectively.
+    \label{fig:lithium_rotation}
+	}
+\end{figure}
+
 \subsection{The Cluster}
@@
 
+%TODO: describe 0.3-day robust Huber spline (or whatever detrending is
+%eventually used)
+
 \subsubsection{Additional Transits}
@@
 MINECO through grant AYA2017-84089
+%
+\tn\ was included on the TESS ``short-cadence'' target list in part
+thanks to the Guest Investigator program of G.\ Sacco (G011265).
+
 %
@@
   %\texttt{astroplan} \citep{astroplan2018},
+	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
   \texttt{astropy} \citep{astropy_2018},

### 2020-06-22 paper/collect.sh

@@ -9,13 +9,13 @@ cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_phaseplot.pdf 
 
 cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
 
-cp ${rdir}radvel_fitting/20200525_simple_planet/TOI837_rv_multipanel.pdf f3.pdf
-
-cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
-
 cp ${pdir}scene.pdf f5.pdf
 
 cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f6.pdf
+
+cp ${rdir}radvel_fitting/20200525_simple_planet/TOI837_rv_multipanel.pdf f3.pdf
+
+cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
 
 cp ${rdir}cluster_membership/hr.pdf f7.pdf
 

### 2020-06-23 paper/ms.tex
manuscript update and it's 17:30

@@
 
+Reconaissance spectroscopic follow-up is an essential step in vetting
+planet candidates.  Medium to high-resolution spectra enable physical
+characterization of the star and therefore planet.  Reducing multiple
+spectra to a radial velocity time-series can enable planet mass
+measurements, and also set limits on the mass of any nearby
+companions.  Finally, if there are close or bright companions,
+reconaissance spectra can also reveal the presence of a secondary set
+of stellar lines.
+
 \subsubsection{CHIRON}
-9 spectra with CTIO1.5/CHIRON, from January 28 through March 14, 2020.
-6 were usable.
+We acquired nine spectra with CTIO1.5/CHIRON, from January 28 2020 through
+March 14 2020.
+Six met our signal-to-noise requirements for radial velocity
+measurements.
+
+{\bf George TODO: please describe the formal secondary line search in
+more depth in this paragraph}
+We searched for secondary lines in the CHIRON spectra by
+cross-correlating against a {\bf template of some kind}.
+This rules out lines with flux ratios of $\approx 2\%$, if the
+lines are well-separated in velocity.
+We measured the radial velocities against the same template.
+To derved the star's physical parameters, we cross-correlated the
+template against {\bf something}, and used the {\bf
+\texttt{nameofcode}}. 
+This yielded:
+\begin{align}
+  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
+  \log g        &= 4.48 \pm 0.03, \nonumber \\
+  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
+  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
+\end{align}
+These spectroscopic parameters were used in our final analysis 
+of the system (Section~\ref{sec:system}).
 
 \subsubsection{FEROS}
-N spectra with XXX/FEROS
+We acquired N spectra with XXX/FEROS.
 
 \subsubsection{Veloce}
-M spectra with AAT/Veloce.
+We acquired M spectra with AAT/Veloce.
 
@@
 
-\newpage
 \subsubsection{Color Photometry}
@@
 \clearpage
+\input{TOI837_phot_table.tex}
+\input{TOI837_rv_table.tex}
 \input{model_comparison_table.tex}

### 2020-06-23 drivers/make_WASP-4b_rv_table.py

@@ -1,0 +1,76 @@
+'''
+make table of RVs
+'''
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt, pandas as pd, numpy as np
+
+from numpy import array as nparr
+
+from glob import glob
+import os, pickle
+
+def main():
+
+    df = pd.read_csv(
+        '../data/RVs_all_WASP4b_for_fitting_20190911.csv', sep=','
+    )
+    jump_df = pd.read_csv(
+        '../data/20190911_jump_wasp4_rv.csv', comment='#', sep=','
+    )
+
+    svalue = np.hstack((
+        np.ones(len(df[df.tel != 'HIRES']))*np.nan,
+        nparr(jump_df.svalue)
+    ))
+
+    original_references = np.array(df['Source'])
+    references = []
+    for ref in original_references:
+        if ref == 'Triaud+2010_vizier':
+            references.append('T+10')
+        elif ref == 'Pont+2011_vizierMNRAS':
+            references.append('P+11')
+        elif ref == 'jump_20190911':
+            references.append('B+20')
+    references = np.array(references)
+
+    outdf = pd.DataFrame(
+        {'time': np.round(nparr(df.time-2450000),6),
+         'mnvel': np.round(nparr(df.mnvel),5),
+         'errvel': np.round(nparr(df.errvel),5),
+         'svalue': svalue,
+         'tel': nparr(df.tel),
+         'provenance': references
+        }
+    )
+
+    outpath = '../paper/WASP-4b_rv_data.tex'
+    with open(outpath,'w') as tf:
+        tf.write(outdf.to_latex(index=False, escape=False, float_format='%.6f'))
+    print('wrote {:s}'.format(outpath))
+
+    outdf.to_csv('../paper/WASP-4b_rv_data.csv', index=False,
+                 float_format='%.6f')
+    print('also wrote ../paper/WASP-4b_rv_data.csv')
+
+
+    #
+    # trim this tex output to remove the annoying first rows, so you
+    # can \input{WASP-4b_rv_data.tex} from the table file.
+    #
+    with open(outpath,'r') as f:
+        lines = f.readlines()
+    midrule_ix = [ix for ix,l in enumerate(lines)
+                  if r'\midrule' in l][0]
+    bottomrule_ix = [ix for ix,l in enumerate(lines)
+                     if r'\bottomrule' in l][0]
[…]

### 2020-06-23 paper/authors.tex
minor
restructure paper
update manuscript

@@
 %
-
 \author[0000-0002-0514-5538]{L. G. Bouma}
@@
 University, 4 Ivy Lane, Princeton, NJ 08540, USA}
-
-\author[0000-0002-9158-7315]{R. Brahm}
-\affiliation{Center of Astro-Engineering UC, Pontificia Universidad
-Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, 782-0436 Macul,
-Santiago, Chile}
-\affiliation{Instituto de Astrof\'isica, Facultad de F\'isica,
-Pontificia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna
-4860, 782-0436 Macul, Santiago, Chile}
-\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
-Mackenna 4860, 782-0436 Macul, Santiago, Chile}
 
@@
 
+%PENDING (MPIA)
+\author{P. Sarkis} %Paula sarkis@mpia.de PI of FEROS time
+\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+
 %PENDING
@@
 \affiliation{El Sauce Observatory, Coquimbo Province, Chile}
+
+%PENDING
+\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
+\affiliation{Center for Astrophysics \textbar \ Harvard \&
+	Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 
@@
 %PENDING
+\author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
+\affiliation{Center for Astrophysics \textbar \ Harvard \&
+	Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%PENDING
 \author{J. de Leon}
+\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
+Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}
+
+%PENDING
+\author[0000-0002-4881-3620]{J. Livingston}
 \affiliation{Department of Astronomy, University of Tokyo, 7-3-1
@@
 
-%PENDING
-\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
-
 %
@@
 %PENDING
-\author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
-
-%PENDING
-\author[0000-0002-7595-0970]{C.~.G.~Tinney}
+\author[0000-0002-7595-0970]{C.~G.~Tinney}
 \affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
@@
 2052, Australia}
+
+%
+% Princeton team
+%
+%PENDING
+\author[0000-0002-0628-0088]{W. Bhatti}
+\affiliation{Department of Astrophysical Sciences, Princeton
+	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+%
+\author[0000-0002-4265-047X]{J. N. Winn}
+\affiliation{Department of Astrophysical Sciences, Princeton
+	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+%
+\author[0000-0001-7204-6727]{G. \'A. Bakos}
+\affiliation{Department of Astrophysical Sciences, Princeton
+	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+
+%
+% WINE MPIA team
+%
+
+\author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
+\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+
+\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
+\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
+\affiliation{Millennium Institute for Astrophysics, Chile}
+
+\author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
+\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
+
+\author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
+\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
+\affiliation{Millennium Institute for Astrophysics, Chile}
+
+\author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
+\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}
+
+\author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
+\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}
+
+\author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
+\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+
+\author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
+\affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}
+
+\author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
+\affiliation{Instituto de F\'isica y Astronom\'ia, Universidad de Vapara\'iso, Casilla 5030, Valpara\'iso, Chile}
 
@@
 	North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
-
-%
-% UToyko team
-%
-%PENDING
-\author[0000-0002-4881-3620]{J. Livingston}
-\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
-Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}
-
-%
-% MPIA team
-%
-%PENDING
-\author{T. Henning}
-\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17,
-69117 Heidelberg, Germany}
-
-%PENDING
-\author[0000-0002-5389-3944]{A. Jord\'an}
-\affiliation{Facultad de Ingenier\'ia y Ciencias, Universidad Adolfo
-Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago,
-Chile}
-\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
-Mackenna 4860, 782-0436 Macul, Santiago, Chile}
-
-%PENDING
-\author[0000-0001-9513-1449]{N. Espinoza}
-\affil{Space Telescope Science Institute, 3700 San Martin Drive,
-Baltimore, MD 21218, USA}
-
-%
-% Princeton team
-%
-%PENDING
-\author[0000-0002-0628-0088]{W. Bhatti}
-\affiliation{Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
-%
-\author[0000-0002-4265-047X]{J. N. Winn}
-\affiliation{Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
-%
-\author[0000-0001-7204-6727]{G. \'A. Bakos}
-\affiliation{Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 
@@
 
+\author{ASTEP400 collaboration}
 \author{TSO/SPOC/POC representatives}

### 2020-06-23 paper/ms.tex
update manuscript

@@
 
-\documentclass[12pt,twocolumn,tighten]{aastex62}
-%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
+\documentclass[12pt,twocolumn,tighten]{aastex63}
+%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
 \usepackage{amsmath,amstext,amssymb}
@@
 
+\suppressAffiliations
+%\NewPageAfterKeywords
 \input{authors.tex}
@@
   transiting planet.  We characterize the system using data from the
-  NASA {\it Transiting Exoplanet Survey Satellite} (TESS), the ESA
-  Gaia mission, ground-based photometry, and spectroscopy from
-  CTIO1.5/CHIRON, MPG2.2/FEROS, and AAT/Veloce.  We find that
-  TOI$\,$837 is a $T=9.9$ G-dwarf in IC~2602 (the ``Southern
-  Pleiades'').  The star and validated planet are therefore 30$\pm$20
+  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
+  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
+  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
+  Pleiades'').  The star and validated planet are therefore 30$\pm$15
   million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
@@
   2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
-  concern: they usually are indicative of astrophysical false
-  positive scenarios.  Our follow-up data show that such scenarios are
-  highly unlikely.  Multi-color photometry requires eclipsing
-  companions to have nearly identical color as TOI$\,$837, ruling out
-  hierarchical eclipsing binary scenarios.  Background eclipsing
-  binary scenarios are limited by speckle imaging, but formally remain
-  a 0.2\% possibility.  TOI 837.01 is therefore a validated adolescent
+  concern: they usually are indicative of astrophysical false positive
+  scenarios.  Our follow-up data show that such scenarios are highly
+  unlikely.  Multi-color photometry requires eclipsing companions to
+  have nearly identical color as TOI$\,$837, ruling out hierarchical
+  eclipsing binary scenarios.  Background eclipsing binary scenarios
+  are limited by speckle imaging, but formally remain a 0.2\%
+  possibility.  TOI 837.01 is therefore a validated adolescent
   exoplanet.  Further observations of its stellar obliquity,
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[!t]
 	\begin{center}
@@
 
-\begin{figure*}[t]
+\begin{figure*}[!t]
 	\begin{center}
@@
 		\subfloat{
-			\includegraphics[width=0.7\textwidth]{f2a.pdf}
+			\includegraphics[width=0.8\textwidth]{f2a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.7\textwidth]{f2b.pdf}
+			\includegraphics[width=0.8\textwidth]{f2b.pdf}
 		}
@@
 and have a depth of about 0.4\%.  A few flares are visible.  A
-phase-folded version of the TESS transits with starspot variability
+phase-folded view of the TESS transits with starspot variability
 removed is shown in Figure~\ref{fig:jointphot}, and is described in
@@
 
+%TODO: you must check custom lightkurve apertures, too
+
+%FIXME: this paragraph doesn't really belong here?
+We examined the CDIPS FFI light curves of the target, which are
+available on MAST \citep{bouma_cluster_2019}. Three light curves are
+available, based on photometric apertures with a radius of 1, 1.5, or
+2.5 pixels.  In the raw difference-image light-curves, as well as the
+PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
+and their properties do not significantly vary with aperture size.
+Within $\approx20$'', the dips are consistent with originating from
+the target star.
+
 \subsection{Gaia Astrometry and Imaging}
@@
 
-\begin{figure}[t]
+\begin{figure}[!t]
 	\begin{center}
@@
 
-The Gaia imaging, as represented by its point-source catalog, provides
+The Gaia imaging, reduced to its point-source catalog, provides
 the initial context for analyzing the TESS data.  Stars brighter than
@@
 and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
-not surprising that the field of \tn\ is crowded.  The stars that were
-of immediate concern for our false positive analysis were as follows.
+not surprising that the field of \tn\ is crowded.  The resolved stars
+that were of immediate concern for our false positive analysis were as
+follows.
 \begin{itemize}
@@
 An additional source, TIC 847769581, is $4.9$'' from the target, but
-too faint (T=18.8) to be the source of the observed transit signal.
-
-The Gaia DR2 data for Star A seems poorly behaved.  While
-Star A has $G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
-Correspondingly, no RUWE\footnote{ See the Gaia
-DPAC technical note GAIA-C3-TN-LU-LL-124-01,
+too faint ($T=18.8$) to be the source of the observed transit signal.
+
+The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
+$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
+Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
+GAIA-C3-TN-LU-LL-124-01,
 \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
-2020-06-22. } value is available.  The astrometric
-reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number of good
-astrometric observations) seems rather poor, at $8.6$.  We suspect
-that the photometric failure to produce an $Rp$ magnitude, as well as
-the poor astrometric fit, are likely due to blending with \tn.
+2020-06-22. } value is available.
+% The astrometric reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number
+% of good astrometric observations) seems rather poor, at $8.6$.
+We suspect that the photometric failure to produce an $Rp$ magnitude,
+as well as its poor astrometric fit, are likely due to blending with
+\tn.
 
@@
 
+\paragraph{Acquisition}
 We observed four transits with the 0.36m at Observatario El Sauce,
@@
 
-{\bf LGB TODO: Describe custom analysis of apertures}
+%TODO TODO
+% See "TOI-837 : a planet!" thread, May 2020
+\paragraph{Custom aperture analysis}
+{\bf LGB TODO: Describe custom analysis of apertures. }
+"""
+While ``Star A'' was detected in the SOAR images, our ground-based
+photometry rules it out as a possible source of the eclipse signal
+(Section~\ref{subsec:groundphot}).
+"""
+
+A total eclipse of Star A would produce a 1.4\%
+dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
+dips of exactly the right depth (0.4\%).
+
+To assess this possibility with the ground-based photometry, we
+produced light curves centered on \tn\ with
+circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
+We did not detect any statistically significant variation in the depth
+of the transits.
+
+We also created light curves with a custom set of $r=2.1''$ apertures
+with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
+east of \tn.  We did not detect any variation of the transit depth
+along this line of light curves, as would be expected if Star A were
+the eclipse host.  The apertures east of \tn\ are particularly
+constraining, as they exclude over 90\% of the flux from Star A.
+The eclipse on Star A would therefore need to be excessively deep to
+produce the observed eclipse depth.
+We take this to indicate that \tn\ is the source of the transit signal
+to within $\approx2.0''$.
 
@@
 
-\begin{figure}[t!]
+\begin{figure}[!t]
 	\begin{center}
@@
 
-\subsubsection{CHIRON}
-We acquired nine spectra with CTIO1.5/CHIRON, from January 28 2020 through
-March 14 2020.
-Six met our signal-to-noise requirements for radial velocity
-measurements.
+\subsubsection{SMARTS 1.5m / CHIRON}
+\label{subsec:chiron}
+
+We acquired nine spectra using CHIRON at the SMARTS 1.5m telescope at
+Cerro Tollo Inter-American Observatory, Chile
+\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
+requirements for radial velocity measurements and stellar parameter
+extraction.  We used CHIRON in its image slicer configuration,
+yielding a spectral resolution of $\approx 79{,}000$ across
+415--880$\,$nm.
 
 {\bf George TODO: please describe the formal secondary line search in
-more depth in this paragraph}
-We searched for secondary lines in the CHIRON spectra by
-cross-correlating against a {\bf template of some kind}.
-This rules out lines with flux ratios of $\approx 2\%$, if the
-lines are well-separated in velocity.
-We measured the radial velocities against the same template.
-To derved the star's physical parameters, we cross-correlated the
-template against {\bf something}, and used the {\bf
-\texttt{nameofcode}}. 
-This yielded:
+more depth in this paragraph} We searched for secondary lines in the
+CHIRON spectra by cross-correlating against a {\bf template of some
+kind}.  This rules out lines with flux ratios of $\approx 2\%$, if the
+lines are well-separated in velocity.  To derive the star's physical
+parameters, we cross-correlated the template against {\bf something},
+and used the {\bf \texttt{nameofcode}}.  This yielded:
 \begin{align}
@@
 \end{align}
-These spectroscopic parameters were used in our final analysis 
-of the system (Section~\ref{sec:system}).
+These spectroscopic parameters were used in our final analysis of the
+system (Section~\ref{sec:system}).  We measured the radial velocities
+through a least-squares deconvolution of the observed spectra against
+the same synthetic template.  The resulting velocities are given in
+Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.
 
 \subsubsection{FEROS}
-We acquired N spectra with XXX/FEROS.
+We acquired 13 spectra using the FEROS echelle spectrograph, mounted
+on the MPG 2.2m telescope at the European Soutern Observatory in La
+Sille, Chile \citep{kaufer_commissioning_1999}.  FEROS has a
+resolution of $\approx 48{,}000$ across a spectra range of
+350--920$\,$nm. It has a remarkably high efficiency of $\approx 20\%$.
+
+We used the dedicated instrument pipeline to extract 1-dimensional,
+wavelength calibrated spectra.  To measure radial velocities, {\bf
+Rafael TODO: what procedure was used?  What software packages?}.  The
+velocities are given in Table~\ref{tab:rvs}, and shown in
+Figure~\ref{fig:rvs}.
 
 \subsubsection{Veloce}
-We acquired M spectra with AAT/Veloce.
+We acquired 34 spectra over 10 visits of \tn\ with using the Veloce
+spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
+Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
+In Rosso form, Veloce provides coverage from 600--950$\,$nm at a
+spectral resolution of $\approx 80{,}000$.
+
+Many of the exposures were taken in average or poor seeing conditions,
+when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
+strongest.  To reduce the spectra to velocities, we cross-correlated
+against a high S/N template of $\delta$ Pavonis.  The velocity RMS
+seen across each visit was hundreds of meters per second, likely due to
+uncorrected fiber-to-fiber cross-contamination.  For
+analysis purposes, we averaged across each visit, and set the velocity
+uncertainties as the standard deviation in the per-visit exposures.
+The velocities are given in Table~\ref{tab:rvs}, and shown in
+Figure~\ref{fig:rvs}.
 
@@
 
-"""Validation is the process of statistically arguing that a
-transit-like signal is due to a planet rather than an astrophysical
-false positive. """
-(CITE blender, Torres+04,05,10; vespa Morton 12, 15; pastis Diaz+14
-Santerne+15; triceratops Giacalone \& Dressing 20).
-
-Many validation analyses are inherently flawed because they do
-not deal with the fact that you are conditioned on having observed
-many stars, and having found an eclipsing system.
+``Validating'' a transiting planet means statistically arguing that
+the data are much more likely to be caused by a planet than by other
+astrophysical false positives.  The concept of validation has been
+developed and calibrated by {\it e.g.},
+\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
+and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
+from ``confirmation'', which means that there is overwhelming evidence
+that the data must be explained by a planet, for instance through
+combined transits and a mass measurement.
+
+Assuming the eclipse has been localized to the target star within the
+available angular resolution, potential false positive scenarios
+include eclipses of a background binary (BEB), eclipses of a
+hierarchical companion to the primary star (HEB), and the possibility
+that the eclipses of \tn\ are simply caused by a stellar companion,
+rather than a planetary one (EB).
 
 Figure~\ref{fig:fpscenario} provides a visual summary of the possible
-astrophysical false positive scenarios.  If the \tn\ signal is not
-planetary, it must come from the near-total eclipse of a background
-star (a BEB), or else a hierarchical companion of the primary star
-(an HEB).  It must also be verified that to the angular resolution
-possible, the transit signal originates from \tn, and not a
-neighboring star (an NEB).
-We proceed by describing each constraint in detail.
-
-\subsection{Limits on Companions from the Transit Depth}
-
+astrophysical false positive scenarios, as well as our ability to rule
+them out based on our combined photometry, velocimetry, and imaging.
+We proceed by describing each constraint in detail, and then present a
+statistical calculation using \texttt{VESPA}
+\citep{morton_efficient_2012} to demonstrate that the probability \tn\
+is an astrophysical false positive is small enough to consider it
+``validated''.
+
+\subsection{Constraints on False Positive Scenarios}
+
+\subsubsection{Transit Depth}
 In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
@@
 \begin{equation}
-    \Delta m < - \frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
+  \Delta m < -\frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
 \end{equation}
 For \tn\ ($T=9.93$), this implies that any stellar companion invoked
-to explain the transit depth must be brighter than $T=15.07$.
-
-Typically, the shape of the transits enables this argument to be scaled to even
-more restrictive depths (e.g., CITE Seager 2003, Vanderburg+2019,
-Rizzuto+2020, David+2018 1298Tau).  However, since the transits of
-\tn\ are grazing, these arguments do not apply.
-
-\subsection{Limits on Companions from Imaging}
-
-\subsubsection{Gaia Imaging}
-{\it empty}
+to explain the transit depth must be brighter than $T=15.07$.  In
+Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
+on the precision at which we have localized the transits using
+seeing-limited ground-based photometry.
+
+Typically, the shape of the transits enables this argument to be
+scaled to even more restrictive depths \citep[{\it
+e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
+However, since the transits of \tn\ are grazing, the second and third
+contact points do not occur, and the shape of the transit is not
+restrictive.
 
 \subsubsection{Speckle Imaging}
-
-We convert the contrast ratios obtained through the SOAR imaging to
-constraints on the masses of putative companions following Montet+2014
-(CITE and others!).  We employed the Baraffe+2003 models for
-substellar mass objects and the MESA isochrones for stellar mass
-objects (Choi et al XXXX).  We assumed that the system age was 35 Myr,
-to ensure that companions would be at a plausible state of
-contraction.
-
-Due to the specific filters of the SOAR HRcam imager, we further
-assumed that all sources had blackbody spectra. While this is clearly
-false, we do not readily have access to the planetary and stellar
-atmosphere models needed for the correct calculation. However, the
-Baraffe+2003 and MESA models do report effective temperatures and
-bolometric luminosities.  We opt to use these theoretical quantities,
-combined with the measured transmission functions, to calculate the
-absolute magnitudes in the HRCam bandpasses (CITE Tokovinin 2018
-summary paper with the bandpasses).
-
-\subsubsection{Patient Imaging}
-    Archival SERC-J and AAO-SES plates are available for the \tn\
-field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
-These plates were acquired in 1982 and 1992, respectively.
-For high proper motion stars archival imagery can be used to
-detect slowly moving background stars that might be an
-astrophysical false-positive source
-({\it e.g.}, \citealt{huang_pimen_2018}, CITE VANDERBURG 19).
-However \tn\ has only moved $\approx0.7''$ between 1982 and
-present, in comparison to the $\approx2.0''$ FWHM of the target on
-the plates.
-We therefore cannot resolve it with great confidence from
-background sources not already resolved through more modern
-imaging.
-
-\subsection{Limits on Companions from Radial Velocities}
-
-The combined radial velocities from FEROS, CHIRON, and Veloce 
-can be used to place limits on the presence of massive, close-in
-bounds companion to \tn.
-
-We derived the relevant limits using \texttt{radvel} \citep{fulton_radvel_2018}.
-We assumed circular orbits for the massive companion.
-We then fitted the RV data for the semiamplitude, period, time
-of conjunction,
-instrument offsets, and jitter parameters.
-We placed a wide log-uniform prior on the semiamplitude
-and period to ensure appropriate sampling of the relevant
-spaces.
-($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim \mathcal{U}(0.1, 10^{15})$).
-
-We then converting the resulting posterior in period and semiamplitude
-to minimum mass and semi-major axis assuming Kepler's third law.
-The resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
-
-\subsection{Limits on Companions from Time-Series Photometry}
-
-\subsubsection{TESS}
-We examined the CDIPS FFI light curves of the target, which are
-available on MAST \citep{bouma_cluster_2019}. Three light curves are
-available, based on photometric apertures with a radius of 1, 1.5, or
-2.5 pixels.  In the raw difference-image light-curves, as well as the
-PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
-and their properties do not significantly vary with aperture size.
-Within $\approx20$'', the dips are consistent with originating from
-the target star.
-
-\subsubsection{Custom Apertures on Ground-Based Time-Series Photometry}
-% See "TOI-837 : a planet!" thread, May 2020
-
-A total eclipse of Star A would produce a 1.4\%
-dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
-dips of exactly the right depth (0.4\%).
-
-To assess this possibility with the ground-based photometry, we
-produced light curves centered on \tn\ with
-circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
-We did not detect any statistically significant variation in the depth
-of the transits.
-
-We also created light curves with a custom set of $r=2.1''$ apertures
-with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
-east of \tn.  We did not detect any variation of the transit depth
-along this line of light curves, as would be expected if Star A were
-the eclipse host.  The apertures east of \tn\ are particularly
-constraining, as they exclude over 90\% of the flux from Star A.
-The eclipse on Star A would therefore need to be excessively deep to
-produce the observed eclipse depth.
-We take this to indicate that \tn\ is the source of the transit signal
-to within $\approx2.0''$.
-
-\subsubsection{Color Photometry}
+The contrast limits obtained through the SOAR $I$-band speckle imaging
+(Section~\ref{subsec:speckle}) are shown in
+Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
+SOAR images, our ground-based photometry rules it out as a possible
+source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
+convert the remaining contrast constraints to limits on the masses of
+putative bound companions, we opted to employ the
+\citet{baraffe_evolutionary_2003} models for substellar mass objects
+and the MIST isochrones for stellar mass objects
+\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
+We assumed that the system age was 35 Myr, to ensure that companions
+would be at a plausible state of contraction.
+
+To convert from theoretical effective temperatures and bolometric
+luminosities to expected magnitudes in instrumental bandpasses, we
+assumed that all soruces had blackbody spectra.  While this is clearly
+a simplification, the custom instrumental bandpasses prevented a fully
+consistent stellar evolutionary calculation.  Using the theoretical
+stellar parameters and the measured transmission functions
+\citep{tokovinin_ten_2018}, we then calculated the apparent magnitude
+of putative stellar companions of different masses, and interpolated
+to produce the scale shown on the right in
+Figure~\ref{fig:fpscenario}.
+
+\subsubsection{Not SB2}
+As described in Section~\ref{subsec:chiron}, we searched the CCFs of
+the CHIRON spectra to determine whether \tn\ is double-lined.  For a
+stellar companion well-separated in velocity, this typically shows
+companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
+purposes, in Figure~\ref{fig:fpscenario} we have assumed a
+flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).
+
+\subsubsection{RVs}
+The combined radial velocities from FEROS, CHIRON, and Veloce can be
+used to place limits on the presence of massive, close-in bounds
+companion to \tn.  We derived the relevant limits using
+\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
+orbits for the massive companion.  We then fitted the RV data for the
+semiamplitude, period, time of conjunction, instrument offsets, and
+jitter parameters.  We placed a wide log-uniform prior on the
+semiamplitude and period to ensure appropriate sampling of the
+relevant spaces.  ($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim
+\mathcal{U}(0.1, 10^{15})$).  We converted the resulting posterior in
+period and semiamplitude to minimum mass and semi-major axis assuming
+Kepler's third law.  The resulting $3\sigma$ limits are shown in
+Figure~\ref{fig:fpscenario}.
+
+\subsubsection{Multicolor Photometry}
+% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
+% at most.
 
@@
 
-For a lower limit on $\delta_{\rm R_C}$ of 32 parts per thousand,
+For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
 we found that the transition between systems that would produce
@@
 produce eclipses that could be sufficiently blue happens in \tn\ (for
-${\rm R_C}$-band) at 0.54$M_\odot$.
+${\rm R_C}$-band) at 0.38$M_\odot$.
 The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
-
-{\bf If we could obtain a similar limit in B-band, it would 
-	solidify this result (because it would drive the HEB system to be even bluer).}
+For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
+limit is 0.82$M_\odot$.
 
@@
 
-\newpage
+\subsubsection{Gaia}
+
+The ``Gaia'' curve in Figure~\ref{fig:fpscenarios} combines both
+point-source detections from imaging, and sources that show an
+astrometric excess.  The curve was interpolated from Figure~4 of
+\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
+indicative that there are no obviously present astometric companions.
+The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
+1.38, which is consistent with comparably bright and blue stars
+\citep[][Appendix A]{lindegren_gaiasoln_2018}.
+
+% chi2AL is 526.88
+% NgAL is 276
+% so, well, reduced chi2 is ~2, which seems bad. but it might (in fact,
+% probably is) be because of the color-dependent stuff in the Gaia PSF
+% model. Most Rp=10 PTFO members had red chi2 of at least 2.
+% Also, looking at Lindegren+2018 Fig A.1., sqrt(reduced chi2) ~= 1.4
+% is expected.
+%
+% --> you could still create the same RUWE vs cluster membership
+%  diagnostic plot, just to be sure.
+
+\subsubsection{Patient Imaging}
+
+Archival SERC-J and AAO-SES plates are available for the \tn\
+field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
+These plates were acquired in 1982 and 1992, respectively.  For high
+proper motion stars archival imagery can be used to detect slowly
+moving background stars that might be an astrophysical false-positive
+source ({\it e.g.}, \citealt{huang_pimen_2018},
+\citealt{vanderburg_hr858_2019}).  However \tn\ has only moved
+$\approx0.7''$ between 1982 and present, in comparison to the
+$\approx2.0''$ FWHM of the target on the plates.  We therefore cannot
+resolve it with great confidence from background sources not already
+resolved through more modern imaging.
+
+\subsection{False positive probability}
+
 \subsubsection{Summary}
@@
 
-\paragraph{Astrometric information}
-The RUWE (CITE, CITE) for \tn\ is 1.02, indicative that there are no
-obviously present astometric companions.
-
 \subsubsection{Rotation}
@@
 \label{sec:discussion}
+
+\tn\ joins a number of other young planetary systems reported from
+TESS, including DS Tuc Ab \citep{newton_tess_2019}, HIP 67522
+\citep{rizzuto_tess_2020}, and TOI 1726 \citep{mann_tess_2020}.
 
@@
     Second Generation Digitized Sky Survey,
- 	Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
+    SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
+ 	%Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
  	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
  	{\it Spectroscopy}:
- 	Keck:I~(HIRES; \citealt{vogt_hires_1994}).
- 	{\bf VLT (number), UVES and GIRAFFE} (CITE: Pasquini et al 2002)
+	CTIO1.5m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
+    MPG2.2m~(FEROS; \citealt{kaufer_commissioning_1999}),
+	AAT~(Veloce; \citealt{gilbert_veloce_2018}).
+ 	%Keck:I~(HIRES; \citealt{vogt_hires_1994}).
+ 	%{\bf VLT (number), UVES and GIRAFFE} (CITE: Pasquini et al 2002)
 % 	Euler1.2m~(CORALIE),
@@
 % 	Danish 1.54m Telescope,
-% 	El Sauce:0.356m,
+	  El Sauce:0.356m,
 % 	Elizabeth 1.0m at SAAO,

### 2020-06-23 timmy/plotting.py

@@ -2139,11 +2139,14 @@ def plot_fpscenarios(outdir):
     tdepth_df = tdepth_df.append(_append_df)
 
     #
-    # no double lined SB2 constraint
+    # no double lined SB2 constraint. Zhou quoted F2/F1 ~= 2% as
+    # limit. use 5%.
     #
     outer_lim = 1.0  # arcsec
     sb2_sep = sep_arcsec[sep_arcsec < outer_lim]
-    sb2_dmag = 3 * np.ones_like(sb2_sep)
+    flux_frac = 5e-2
+    dmag = -5/2 * np.log10(flux_frac)
+    sb2_dmag = dmag * np.ones_like(sb2_sep)
     sb2_sep = np.append(sb2_sep, outer_lim)
     sb2_dmag = np.append(sb2_dmag, 0)
     sb2_df = pd.DataFrame({'sep_arcsec': sb2_sep, 'dmag': sb2_dmag})
@@ -2206,13 +2209,13 @@ def plot_fpscenarios(outdir):
     # make plot
 
     from timmy.multicolor import DELTA_LIM_RC, DELTA_LIM_B
-    names = ['Speckle imaging', 'Transit depth', 'Not SB2', 'RVs',
+    names = ['Transit depth', 'Speckle imaging', 'Not SB2', 'RVs',
              '$\delta_{R_C}>'+f'{1e3*DELTA_LIM_RC:.1f}'+'\,$ppt',
              '$\delta_{B_J}>'+f'{1e3*DELTA_LIM_B:.1f}'+'\,$ppt',
              'Gaia'
             ]
-    sides = ['above', 'below', 'above', 'above', 'below', 'below', 'above']
-    constraint_dfs = [speckle_df, tdepth_df, sb2_df, srv_df, color_df_Rc,
+    sides = ['below', 'above', 'above', 'above', 'below', 'below', 'above']
+    constraint_dfs = [tdepth_df, speckle_df, sb2_df, srv_df, color_df_Rc,
                       color_df_B, gaia_df]
     which = ['both', 'both', 'both', 'assoc', 'assoc', 'assoc', 'both']
 

### 2020-06-24 paper/ms.tex
update manuscript

@@
 
+The transits of \pn\ are grazing, which is a cause for concern.
+Particularly for a target near the galactic plane ($b=-5.8^\circ$),
+background eclipsing binaries are a major source of astrophysical
+false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
+follow-up data show that this and related scenarios are unlikely to
+the degree that we can ``validate'' the planet, {\it i.e.}, rule that
+its probability of being an astrophysical false positive is negligibly
+small.  We considered this effort worthwhile because of the planet's
+youth.
+
 Section~\ref{sec:observations} describes the identification of the
@@
 Section~\ref{sec:validation} combines these data to assess the
-system's false positive probability, and finds that \pn\ is almost
-certainly a planet.  Section~\ref{sec:system} presents our knowledge
-of the cluster (Section~\ref{subsec:cluster}), the star
-(Section~\ref{subsec:star}) and the planet
-(Section~\ref{subsec:planet}).  We conclude by discussing avenues for
-improved characterization in Section~\ref{sec:discussion}.
+system's false positive probability, and validates \pn\ as a planet.
+Section~\ref{sec:system} presents our knowledge of the cluster
+(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
+and the planet (Section~\ref{subsec:planet}).  We conclude by
+discussing avenues for confirmation and improved characterization in
+Section~\ref{sec:discussion}.
 
@@
 
-\paragraph{Acquisition}
+\paragraph{Acquisition and reduction}
 We observed four transits with the 0.36m at Observatario El Sauce,
@@
 showed a roughly 4$\,$ppt dip near the expected transit time.
-We produced and examined light curves with at custom positions and
-with custom aperture sizes, and...
-
-The data were reduced using... (e.g., astroimageJ)
-
-%TODO TODO
-% See "TOI-837 : a planet!" thread, May 2020
+
 \paragraph{Custom aperture analysis}
-{\bf LGB TODO: Describe custom analysis of apertures. }
-"""
-While ``Star A'' was detected in the SOAR images, our ground-based
-photometry rules it out as a possible source of the eclipse signal
-(Section~\ref{subsec:groundphot}).
-"""
-
-A total eclipse of Star A would produce a 1.4\%
-dip. A 30\% eclipse, more plausible for a NEB scenario, would produce
-dips of exactly the right depth (0.4\%).
+Based solely on the TESS data, both Star A and Star B
+were possible sources of blended eclipsing binary signals.
+For instance, a 30\% eclipse of Star A could produce
+dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
+Star B is resolved in the ground-based images, while Star A is not.
 
@@
 We did not detect any statistically significant variation in the depth
-of the transits.
-
-We also created light curves with a custom set of $r=2.1''$ apertures
-with positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
+of the transits with aperture size.
+Two lines evidence rule out Star B as the eclipsing source:
+first, the transits
+were detected in the smallest apertures.
+Second, we made light curves with $2.1''$ apertures centered on Star B,
+and they did not show the transit.
+
+To assess the possibility of Star A as the eclipsing body,
+we created light curves with a custom set of circular apertures
+with radii of $2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
 east of \tn.  We did not detect any variation of the transit depth
@@
 produce the observed eclipse depth.
-We take this to indicate that \tn\ is the source of the transit signal
+We take this as evidence that \tn\ is the source of the transit signal
 to within $\approx2.0''$.
@@
 		\leavevmode
-		\includegraphics[width=1\textwidth]{f4.pdf}
+		\includegraphics[width=0.85\textwidth]{f4.pdf}
 	\end{center}
@@
 
-``Validating'' a transiting planet means statistically arguing that
+Validating a transiting planet means statistically arguing that
 the data are much more likely to be caused by a planet than by other
@@
 that the data must be explained by a planet, for instance through
-combined transits and a mass measurement.
-
-Assuming the eclipse has been localized to the target star within the
-available angular resolution, potential false positive scenarios
+combined photometric transits and a radial velocity mass measurement.
+
+Assuming the eclipse is localized to the target star, potential false positive scenarios
 include eclipses of a background binary (BEB), eclipses of a
-hierarchical companion to the primary star (HEB), and the possibility
-that the eclipses of \tn\ are simply caused by a stellar companion,
+hierarchical system bound to the primary star (HEB), and the possibility
+that the eclipses are simply caused by a stellar companion,
 rather than a planetary one (EB).
@@
 is an astrophysical false positive is small enough to consider it
-``validated''.
+validated.
 
 \subsection{Constraints on False Positive Scenarios}
+\label{subsec:fp_constraints}
 
@@
 
-Typically, the shape of the transits enables this argument to be
-scaled to even more restrictive depths \citep[{\it
+For box-shaped transits, this argument can be
+extended to even more restrictive depths \citep[{\it
 e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
@@
 convert the remaining contrast constraints to limits on the masses of
-putative bound companions, we opted to employ the
-\citet{baraffe_evolutionary_2003} models for substellar mass objects
+possible bound companions, we used the
+\citet{baraffe_evolutionary_2003} models for sub-stellar mass objects
 and the MIST isochrones for stellar mass objects
@@
 luminosities to expected magnitudes in instrumental bandpasses, we
-assumed that all soruces had blackbody spectra.  While this is clearly
+assumed that all soruces had blackbody spectra.  While this is
 a simplification, the custom instrumental bandpasses prevented a fully
@@
 stellar parameters and the measured transmission functions
-\citep{tokovinin_ten_2018}, we then calculated the apparent magnitude
-of putative stellar companions of different masses, and interpolated
-to produce the scale shown on the right in
+\citep{tokovinin_ten_2018}, we then calculated the apparent magnitudes
+of stellar companions of different masses, and interpolated
+to produce the scale shown on the upper-right in
 Figure~\ref{fig:fpscenario}.
@@
 837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
-These eclipses are redder than eclipses of the G-dwarf \tn.
+These eclipses are redder than eclipses of the G0V \tn.
 Observations that the transit depth does not decrease
-going to blue bands therefore limits the plausibility of these scenarios.
+going to blue bands can therefore rule out these scenarios.
 
@@
 
-The ``Gaia'' curve in Figure~\ref{fig:fpscenarios} combines both
+The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
 point-source detections from imaging, and sources that show an
@@
 The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
-1.38, which is consistent with comparably bright and blue stars
+1.38, which is consistent with stars of similar brightness and color
 \citep[][Appendix A]{lindegren_gaiasoln_2018}.
@@
 
-\subsubsection{Summary}
-
-Possible false-positive scenarios are as follows.
-
-\begin{itemize}
-  \item {\it Neighboring blends}.
-    Ruled out to within 2 arcseconds by Phil Evans.
-
-  \item {\it Hierarchical blends}.
-    Limited by i) FEROS + Veloce RVs, and ii) speckle imaging. 
-    Multicolor photometry also limits.
-
-  At present our data do not rule out the presence of bound companion
-    stars from $\approx$10--100$\,$AU, with masses in the range of
-    $\approx$0.15--0.25$\,$M$_\odot$ (Figure~\ref{fig:fpscenario}).
-  Roughly 2-3\% of Sun-like stars in the solar neighborhood with
-    binary companions have companions in this region of parameter space
-  (assuming the Raghavan+2010 CITE log-normal binary
-    separation distribution, and a uniform companion mass function.)
-
-  Companion statistics for hierarchical triples are somewhat less 
-    robust, but they have been studied, for instance by CITE
-    Tokovinin 2014.
-  CITE Tokovinin 2014 found that 7\% of Sun-like stars are
-    hierarchical triples with two companions in the compact orbit (the
-    ``L$_{12}$'' configuration, rather than the ``L$_{11}$''
-    configuration of say, $\alpha$~Centauri).
-  A priori then, given a Sun-like primary, the probability that it is in a
-    hierarchical triple configuration in which the outer orbit
-    satisfies the mass and semi-major axis constraints of
-    Figure~\ref{fig:fpscenario} is $\approx 7\% \times 3\% = 0.2\%$. 
-  This is independent of the issue that the inner pair would require
-    finely tuned orbital parameters (i) to eclipse, and (ii) to
-    be so compact.
-
-  \item {\it Background blends}.
-	An argument on the a priori probability of background blends follows from
-	counting statistics. Within 360 arcseconds, there are 298 T<16 stars in TIC8
-	(i.e., Gaia DR2). At 2.0 arcseconds, SOAR archives dmag(I) of 6. Inside of 2
-	arcseconds, we expect $\pi r^2 $ times (Nstar per sq arcsec) = 9e-3 T<16 stars.
-	Any with T$\gtrsim$15 outside of 0.3 arcseconds would have been detected by
-	SOAR, which brings down the expected number of possible hidden sources by a
-	factor of a few.  Within 0.3 arcseconds, where SOAR gets worse than dmag(I) of
-	3, we expect 2e-4 T<16 stars. So (order of magnitude), background blends would
-	be a $\sim$0.1\% coincidence.
-	%For the background blend to be {\it eclipsing} would require an additional
-	%$\sim$2\% coincidence (CITE Kirk+2017 KEBC).
-	%Combining the two probabilities yields a prior probability of $\approx$0.002\%.
-
-\end{itemize}
+% 151 T<15.1 stars within 360 arcseconds
+% 298 T<16.0 stars within 360 arcseconds
+The constraints on false-positive scenarios summarized in
+Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
+the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
+are caused by hierarchical blends, and {\it iii)} the eclipses are
+caused by neighboring stars outside $\approx 2''$.  The only scenario
+not formally ruled out is a background eclipsing binary.  A simple
+(fallacious) argument on the a priori probability of background blends
+follows from counting statistics.  The local density of $T<15.1$ stars
+around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
+arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
+not excluded by the SOAR HRCam contrast curve, for a randomly selected
+star we would expect $1.0\times10^{-4}$ potential $T<15.1$
+contaminants, which appears small.
+
+The reason the above statement is an insufficient argument against
+BEBs is that \tn\ is not a randomly selected star---it was selected
+because it shows eclipses.  Given a foreground star that shows
+eclipses, the probability of a background star being present is much
+greater than for an arbitrary foreground star.  The relevant
+populations need to be modelled at the Monte Carlo level.  We opt to
+use \texttt{VESPA} to perform this population modelling
+\citep{morton_efficient_2012,vespa_2015}.
+
+\texttt{VESPA} calculates the false positive probability for a transit
+signal as
+\begin{equation}
+  {\rm FPP} = 1 - P_{\rm pl},
+\end{equation}
+where in our case the probability that the signal comes from a planet,
+$P_{\rm pl}$, is given by
+\begin{align}
+  P_{\rm pl} = 
+  \frac{
+    \mathcal{L}_{\rm pl}\pi_{\rm pl}
+  }{
+    \mathcal{L}_{\rm pl}\pi_{\rm pl} + \mathcal{L}_{\rm BEB}\pi_{\rm BEB}
+  },
+\end{align}
+where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
+scenarios, and $\pi_i$ is the model prior.  The terms labelled as
+``BEB'' usually include other false positive scenarios (HEBs and EBs),
+but our followup data have excluded these possibilities.  The priors
+are evaluated using a combination of galactic population synthesis
+\citep{girardi_star_2005}, binary star statistics
+\citep{raghavan_survey_2010}, and specific planet occurrence rates
+\citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
+evaluated by forward-modelling a representative population of
+eclipsing bodies for model class, in which each population member has
+a particular trapezoidal eclipse depth, total duration, and ingress
+duration.  The likelihood is then calculated by multiplying the
+probability distribution function of simulated population's shape
+parameters with the posterior probability of the actual observed
+eclipse shape.
+
+% results from 20200624_simple_fpp_weak_sec 
+We ran \texttt{VESPA}\footnote{We used
+\texttt{VESPA-0.6} and \texttt{isochrones-1.2.2}.}, and directly
+incorporated our constraints of the SOAR $I$-band contrast curve and a
+non-detection of secondary eclipses with a depth set at roughly twice
+the limits from the SPOC vetting report (0.1\%).  We verified that
+changing the secondary eclipse depth limit did not significantly
+affect the results.  We set the maximum aperture radius at $2''$,
+based on our ground-based photometry.  Incorporating the constraints
+from Figure~\ref{fig:fpscenario}, our nominal false positive
+probability analysis excluded EB and HEB scenarios.  This yielded a
+FPP of 0.21\% for \pn, sufficient for formal validation as a
+planet \citep{morton_efficient_2012}.  We did not incorporate our constraint that \tn\ is not
+double-lined, which rules out an additional portion of BEB parameter
+space.  Had we not acquired multicolor ground-based photometry, and
+been unable to exclude HEB scenarios, the FPP would have risen to 8\%.
+However, since the transits are achromatic
+(Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
+rule out HEB scenarios.
 
@@
   \texttt{IPython} \citep{perez_2007},
+	\texttt{isochrones} \citep{morton_2015_isochrones},
 	\texttt{lightkurve} \citep{lightkurve_2018},
@@
   \texttt{tesscut} \citep{brasseur_astrocut_2019},
+	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
   \texttt{webplotdigitzer} \citep{rohatgi_2019},

### 2020-06-24 paper/ms.tex
minor manuscript updates

@@
   0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
-  lies within 0.58--3.87 $R_{\rm Jup}$, due to the degeneracy between
-  the planetary size and the impact parameter of the transit.  From
-  radial velocity monitoring, we limit the mass of planet to less than
-  2.XX $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are cause for
-  concern: they usually are indicative of astrophysical false positive
-  scenarios.  Our follow-up data show that such scenarios are highly
-  unlikely.  Multi-color photometry requires eclipsing companions to
-  have nearly identical color as TOI$\,$837, ruling out hierarchical
-  eclipsing binary scenarios.  Background eclipsing binary scenarios
-  are limited by speckle imaging, but formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent
-  exoplanet.  Further observations of its stellar obliquity,
-  atmosphere, and mass should confirm its planetary nature beyond
-  doubt, and could improve our understanding of how the physical and
-  orbital properties of exoplanets change in time.
+  lies within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
+  percentile), due to the degeneracy between the planetary size and
+  the impact parameter of the transit.  From radial velocity
+  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
+  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
+  usually are indicative of astrophysical false positive scenarios.
+  Our follow-up data show that such scenarios are highly unlikely.
+  Multi-color photometry requires eclipsing companions to have nearly
+  identical color as TOI$\,$837, ruling out hierarchical eclipsing
+  binary scenarios.  Background eclipsing binary scenarios are limited
+  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
+  837.01 is therefore a validated adolescent exoplanet.  Further
+  observations of its stellar obliquity, atmosphere, and mass should
+  confirm its planetary nature beyond doubt, and could improve our
+  understanding of how the physical and orbital properties of
+  exoplanets change in time.
 \end{abstract}
@@
 analysis purposes, we averaged across each visit, and set the velocity
-uncertainties as the standard deviation in the per-visit exposures.
+uncertainties to be the standard deviation of the per-visit exposures.
 The velocities are given in Table~\ref{tab:rvs}, and shown in
@@
 The combined radial velocities from FEROS, CHIRON, and Veloce can be
-used to place limits on the presence of massive, close-in bounds
+used to place limits on the presence of massive, close-in bound
 companion to \tn.  We derived the relevant limits using
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits for the massive companion.  We then fitted the RV data for the
-semiamplitude, period, time of conjunction, instrument offsets, and
-jitter parameters.  We placed a wide log-uniform prior on the
-semiamplitude and period to ensure appropriate sampling of the
-relevant spaces.  ($\log K \sim \mathcal{U}(1,10^5)$, $\log P \sim
-\mathcal{U}(0.1, 10^{15})$).  We converted the resulting posterior in
-period and semiamplitude to minimum mass and semi-major axis assuming
-Kepler's third law.  The resulting $3\sigma$ limits are shown in
-Figure~\ref{fig:fpscenario}.
+orbits for the companion, and then performed two sets of fits.
+
+% timmy.drivers.oneoff_drivers.get_mass_upper_limit
+For the first fit, we assumed a restrictive prior on the period and
+time of periapse, using the known ephemeris from the transit.  We then
+fitted for the period, time of periapse, semi-amplitude, instrument
+offsets, and jitter parameters.  This yielded a non-detection of the
+planet's orbit.  The corresponding 3-$\sigma$ (99.7$^{\rm th}$
+percentile) upper limit on $M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.
+The data and corresponding model are shown in Figure~\ref{fig:rvs}.
+
+The above exercise rules out the possibility that the observed
+eclipses are caused by a star orbiting \tn.  The lack of a linear
+trend in the radial velocities, particularly in the FEROS data, can be
+used to further limit the presence of a hierarchical binary system.
+To constrain this second possibility, we placed a wide log-uniform
+prior on the semi-amplitude and period ($\log K\ [{\rm m\,s^{-1}}]
+\sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
+10^{15})$).  We then fitted again for the semi-amplitude, period, time
+of conjunction, instrument offsets, and jitter parameters.  We
+converted the resulting posterior in period and semi-amplitude to
+minimum mass and semi-major axis assuming Kepler's third law.  The
+resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
 
@@
 
+\subsubsection{Comments on Joint Transit and Radial Velocity Fitting}
+
+The available data for \tn\ put us in an odd position. The transit
+data provide a minimum size due to the grazing geometry; the radial
+velocity data provide a maximum mass ($\approx$1.20 $M_{\rm jup}$).
+We could combine the two with an empirically-calibrated planetary
+mass-radius relation to force a more restrictive upper bound on the
+planetary size \citep[{\it e.g.},][]{chen_probabilistic_2016}.  The
+result of such an exercise would tautologically be that the planet
+would be smaller than the largest known Jovian planets ($\approx
+2R_{\rm Jup}$).  This would also imply that the impact parameter is
+slightly below unity.  The planet's size, in our eyes, would remain
+poorly constrained even if we were to do this exercise. {\bf So we
+don't do it.}
+
 \subsubsection{Additional Transits}
-
 None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
@@
   \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
-  %\texttt{radvel} \citep{fulton_radvel_2018},
+  \texttt{radvel} \citep{fulton_radvel_2018},
   %\texttt{scikit-learn} \citep{scikit-learn},

### 2020-06-24 drivers/oneoff_drivers/get_mass_upper_limit.py
add one-off rv mass upper limit script

@@ -1,0 +1,21 @@
+import os
+import pandas as pd, numpy as np
+from astrobase.lcmath import find_lc_timegroups
+from numpy import array as nparr
+from astropy import units as u
+
+from timmy.paths import DATADIR, RESULTSDIR
+
+datestr = '20200624'
+postpath = os.path.join(RESULTSDIR, 'radvel_fitting',
+                        f'{datestr}_simple_planet',
+                        'TOI837_derived.csv.tar.bz2')
+
+df = pd.read_csv(postpath)
+
+cutoff = 99.7 # 3-sigma
+
+val = np.percentile(nparr(df.mpsini1), cutoff)*u.Mearth
+
+print(f'3sigma (99.7th percentile): {val}')
+print(f'3sigma (99.7th percentile): {val.to(u.Mjup)}')

### 2020-06-25 paper/ms.tex
merge rv plot to manuscript

@@
 	\caption{
-		{\bf Radial velocities.}
+		{\bf Radial velocities of \tn.}
+		{\it Top:} RV measurements, with best-fit instrument offsets
+    and jitter terms included.  The expected scatter from starspots
+    based on $v\sin i$ and the photometric modulation amplitude is of
+    order 300m$\,$s$^{-1}$.
+		{\it Bottom:}
+    RV measurements phased to the orbital ephemeris of \pn.  The
+    planet is not detected.  The black line shows a circular
+    Keplerian orbit representing the $3\sigma$ upper mass limit.
 		\label{fig:rvs}

### 2020-06-25 paper/collect.sh

@@ -13,7 +13,7 @@ cp ${pdir}scene.pdf f5.pdf
 
 cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f6.pdf
 
-cp ${rdir}radvel_fitting/20200525_simple_planet/TOI837_rv_multipanel.pdf f3.pdf
+cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f3.pdf
 
 cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
 

### 2020-06-25 paper/ms.tex
update manuscript

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%
+% TODO:
+% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
+% text. G0V has been assumed.
+%
 
@@
 
-% TODO: SpType subtype?
 \begin{abstract}
@@
 
-Over the first one hundred million years of their lives, exoplanet
+Over the first 100 million years of their lives, exoplanet
 systems are expected to undergo major physical and dynamical changes.
 For a typical Sun-like star, the protoplanetary disk disperses within
-$\sim$3 million years (CITE IR + sub-mm results).  The planet
-formation process presumably finishes within this time for gas giants
-(CITE).  The rocky planet population will also be mostly evolved
-within $\sim$3 million years (CITE), but may undergo significant
-changes over the next $\sim$10-100 million years through giant
-impacts.  The Moon, for instance, is thought to have formed when the
-solar system was XX million years old through such an impact (CITE).
-
-A number of other processes are thought to happen relatively quickly.
-Physical changes in the sizes of planets are expected as they
+roughly 1--10 million years
+\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
+Gas giants presumably finish accreting before the disk
+disperses \citep{pollack_formation_1996}.  While rocky planets may
+fully form within only a few million years
+\citep{dauphas_hf-w-th_2011}, they can also undergo significant
+changes over the next $\sim$10-100 million years through giant impacts
+\citep[{\it
+e.g.},][]{kleine_hf-w_2009,konig_earths_2011,raymond_terrestrial_2014}.
+The Moon, for instance, may have formed from debris ejected during a
+collision between the proto-Earth and a planetesimal
+during Earth's first 100 million years
+\citep{cameron_origin_1976,canup_origin_2001}.
+
+A number of other processes are thought to shape young exoplanets.
+Planets with gaseous envelopes are expected to shrink as they
 contract, and as their atmospheres undergo photoevaporation
@@
 		sight.
+		Each constraint is described in Section~\ref{subsec:fp_constraints}.
 		\label{fig:fpscenario}

### 2020-06-25 paper/ms.tex
update manuscript

@@
 
-Over the first 100 million years of their lives, exoplanet
-systems are expected to undergo major physical and dynamical changes.
-For a typical Sun-like star, the protoplanetary disk disperses within
+Over the first 100 million years of their lives, exoplanet systems are
+expected to undergo major physical and dynamical changes.  For a
+typical Sun-like star, the protoplanetary disk disperses within
 roughly 1--10 million years
 \citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
-Gas giants presumably finish accreting before the disk
-disperses \citep{pollack_formation_1996}.  While rocky planets may
+Gas giants presumably finish accreting before the end of disk
+dispersal \citep{pollack_formation_1996}.  While rocky planets may
 fully form within only a few million years
@@
 The Moon, for instance, may have formed from debris ejected during a
-collision between the proto-Earth and a planetesimal
-during Earth's first 100 million years
-\citep{cameron_origin_1976,canup_origin_2001}.
-
-A number of other processes are thought to shape young exoplanets.
-Planets with gaseous envelopes are expected to shrink as they
-contract, and as their atmospheres undergo photoevaporation
-\citep[{\it
+collision between the proto-Earth and a planetesimal during Earth's
+first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.
+
+A number of other processes are expected to shape young exoplanets.
+Planets with gaseous envelopes are thought to shrink as they contract
+and as their atmospheres undergo photoevaporation \citep[{\it
 e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
-relative importance of these two processes is set by the planetary
-mass, as well as the radiation environment.  Photoevaporation in
-particular can be directly observed in {\it e.g.}, the He 10830\AA\
-line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in
-the semi-major axes, eccentricities, and stellar obliquities of young
-planets.  When the gas disk is present, the planetary semi-major axis
-is thought to change due to viscous coupling (CITE).
-High-eccentricity migration processes including planet-planet
-scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
-(CITE) can also occur.  The circularization timescale is thought to be
-such that for any giant planets that migrated early, their orbits
-should circularize within 100 million years (CITE).
-
-Finding and studying systems undergoing these evolutionary changes is
-a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1$\,$Gyr, a number of direct and indirect methods are
-available \citep{soderblom_ages_2010}.  The traditional approach is to
-isochronally age-date coeval groups of stars, hereafter ``clusters''
-\citep[{\it
-e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
-Young field stars can also be identified using age indicators such as
-stellar rotation periods, the abundance of photospheric lithium, and
-chromospheric diagnostics such as calcium emission and broadband UV
-emission.  Studies by for instance \citet{david_discovery_2018} and
-G{.}~Zhou et al. (2020, submitted) have combined these methods for
-individual field stars.  Many of the latter methods were summarized by
-\citet{mamajek_improved_2008}, and have since been calibrated by {\it
-e.g.},
+relative importance of contraction and photoevaporation is set by the
+planetary mass, as well as the radiation environment.  The
+effectiveness of photoevaporation can be inferred from observations of
+planetary winds in the metastable 1083$\,$nm He line
+\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.
+
+Beyond physical changes, dynamical changes are expected in the semi-major axes,
+eccentricities, and stellar obliquities of young planets.  When the gas disk is
+present, the planetary semi-major axis is thought to change in step with the
+viscous evolution of the disk \citep{lin_orbital_1996}.  High-eccentricity
+migration processes including planet-planet scattering, secular chaos, and
+Kozai-Lidov oscillations can also occur \citep[{\it
+e.g.},][]{chatterjee_dynamical_2008,lithwick_secular_2014,fabrycky_shrinking_2007}.
+The circularization timescale is thought to be such that for any giant planets
+that migrated early, their orbits should circularize within 100 million years
+\citep{zahn_tidal_1977}.
+
+Finding and studying systems undergoing these evolutionary changes is a major
+goal in contemporary exoplanet research.  To identify stars younger than say
+1$\,$Gyr, a number of direct and indirect methods are available
+\citep{soderblom_ages_2010}.  The traditional approach is to isochronally
+age-date coeval groups of stars, hereafter ``clusters'' \citep[{\it
+e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.  Young
+field stars can also be identified using age indicators such as stellar
+rotation periods, the abundance of photospheric lithium, and chromospheric
+diagnostics such as calcium emission and broadband UV emission.  Studies by for
+instance \citet{david_discovery_2018} and G{.}~Zhou et al. (2020, submitted)
+have combined these methods for individual field stars.  Many of the latter
+methods were summarized by \citet{mamajek_improved_2008}, and have since been
+calibrated by {\it e.g.},
 \citet{barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
 and \citet{curtis_tess_2019} for stellar rotation,
-\citet{zerjal_chromospherically_2017} for chromospheric activity, and
-{\it e.g.}, \citet{berger_identifying_2018} and
-\citet{zerjal_galah_2019} for lithium abundances.
+\citet{zerjal_chromospherically_2017} for chromospheric activity, and {\it
+e.g.}, \citet{berger_identifying_2018} and \citet{zerjal_galah_2019} for
+lithium abundances.
 
@@
 its probability of being an astrophysical false positive is negligibly
-small.  We considered this effort worthwhile because of the planet's
+small.  We considered this result worth reporting because of the planet's
 youth.
@@
 	\vspace{-0.7cm}
-	\caption{ {\bf Scene used for blend analysis.}
+	\caption{ {\bf Scene of \tn.}
     {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
     logarithmic grayscale. The yellow star is the position of \tn.
-    Orange circles are neighboring stars with $T<16$, scaled such that
-    brighter stars are larger. The \texttt{X} and \texttt{/} hatches
-    show the apertures used to measure the background and target star
-    flux, respectively. Dashed lines of constant declination and right
+    Orange circles are neighboring stars with $T<16$ (brighter stars
+    are larger). The \texttt{X} and \texttt{/} hatches show the
+    apertures used to measure the background and target star flux,
+    respectively. Dashed lines of constant declination and right
     ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
-    image of the same field, with a linear grayscale. The circles show
-    apertures of radii 1, 1.5, and 2.25 pixels used in our blend
-    analysis (Section~\ref{subsec:validation}).  Two stars of interest
-    are ``Star A'' and ``Star B'', which were eventually excluded as
-    being possible sources of the transits.
+    image of the same field, with a linear grayscale.  Two stars of
+    interest are ``Star A'' and ``Star B'', which were eventually
+    excluded as being possible sources of the transits.
 		\label{fig:scene}
@@
     injection-recovery experiments.} Star A ($\Delta T=4.7$,
-    $\rho=2.3$'' west) is detected in the autocorrelation function, in
+    $2.3''$ west) is detected in the autocorrelation function, in
     addition to being a resolved Gaia source.  It is co-moving with
@@
 		{\bf Astrophysical false positive scenarios.}
-		{\it Top}: for bound companions,
+    {\it Top}: for bound companions (EB and HEB scenarios),
 		{\it Bottom}: for unassociated companions along the same line of
-		sight.
+    sight (BEB scenarios).
 		Each constraint is described in Section~\ref{subsec:fp_constraints}.

### 2020-06-25 drivers/calc_rvoutersensitivity.py

@@ -21,7 +21,8 @@ n_grid = int(5e1)       # number of points in logspaced grid
 smooth = 2              # gaussian smoothing over of sampling grid
 ##########################################
 
-chainpath = os.path.join(RESULTSDIR, 'radvel_fitting', '20200525_fpscenario',
+datestr = '20200624'
+chainpath = os.path.join(RESULTSDIR, 'radvel_fitting', f'{datestr}_fpscenario',
                          'TOI837_fpscenario_limits_chains.csv.tar.bz2')
 
 df = pd.read_csv(chainpath)

### 2020-06-25 timmy/plotting.py

@@ -1038,11 +1038,11 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
         cb1 = fig.colorbar(cset1, ax=ax1, extend='neither', fraction=0.046,
                            pad=0.04)
 
-    # DSS is ~1 arcsecond per pixel. overplot apertures on axes 6,7
-    for ix, radius_px in enumerate([21,21*1.5,21*2.25]):
-        circle = plt.Circle((sizepix/2, sizepix/2), radius_px,
-                            color='C{}'.format(ix), fill=False, zorder=5+ix)
-        ax1.add_artist(circle)
+    # # DSS is ~1 arcsecond per pixel. overplot apertures on axes 6,7
+    # for ix, radius_px in enumerate([21,21*1.5,21*2.25]):
+    #     circle = plt.Circle((sizepix/2, sizepix/2), radius_px,
+    #                         color='C{}'.format(ix), fill=False, zorder=5+ix)
+    #     ax1.add_artist(circle)
 
     #
     # ITNERMEDIATE SINCE TESS IMAGES NOW PLOTTED
@@ -2219,7 +2219,9 @@ def plot_fpscenarios(outdir):
                       color_df_B, gaia_df]
     which = ['both', 'both', 'both', 'assoc', 'assoc', 'assoc', 'both']
 
-    colors = [f'C{ix}' for ix in range(len(constraint_dfs))]
+    # colors = [f'C{ix}' for ix in range(len(constraint_dfs))]
+    N_constraint = len(constraint_dfs)
+    colors = plt.cm.YlGnBu(np.linspace(0.2,1,N_constraint))
 
     plt.close('all')
 
@@ -2247,11 +2249,11 @@ def plot_fpscenarios(outdir):
             if dofill:
                 if side == 'above':
                     ax.fill_between(
-                        xval, yval, 0, color='gray', alpha=0.7, lw=0
+                        xval, yval, 0, color='gray', alpha=0.8, lw=0
                     )
                 elif side == 'below':
                     ax.fill_between(
-                        xval, 7, yval, color='gray', alpha=0.7, lw=0
+                        xval, 7, yval, color='gray', alpha=0.8, lw=0
                     )
 
     axs[0].set_title('Associated companions')

### 2020-06-25 paper/ms.tex
wrote cluster properties section

@@
 % results from 20200624_simple_fpp_weak_sec 
-We ran \texttt{VESPA}\footnote{We used
-\texttt{VESPA-0.6} and \texttt{isochrones-1.2.2}.}, and directly
-incorporated our constraints of the SOAR $I$-band contrast curve and a
-non-detection of secondary eclipses with a depth set at roughly twice
-the limits from the SPOC vetting report (0.1\%).  We verified that
-changing the secondary eclipse depth limit did not significantly
-affect the results.  We set the maximum aperture radius at $2''$,
-based on our ground-based photometry.  Incorporating the constraints
-from Figure~\ref{fig:fpscenario}, our nominal false positive
-probability analysis excluded EB and HEB scenarios.  This yielded a
-FPP of 0.21\% for \pn, sufficient for formal validation as a
-planet \citep{morton_efficient_2012}.  We did not incorporate our constraint that \tn\ is not
-double-lined, which rules out an additional portion of BEB parameter
-space.  Had we not acquired multicolor ground-based photometry, and
-been unable to exclude HEB scenarios, the FPP would have risen to 8\%.
-However, since the transits are achromatic
+We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
+\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
+of the SOAR $I$-band contrast curve and a non-detection of secondary
+eclipses with a depth set at roughly twice the limits from the SPOC
+vetting report (0.1\%).  We verified that changing the secondary
+eclipse depth limit did not significantly affect the results.  We set
+the maximum aperture radius at $2''$, based on our ground-based
+photometry.  Incorporating the constraints from
+Figure~\ref{fig:fpscenario}, our nominal false positive probability
+analysis excluded EB and HEB scenarios.  This yielded a FPP of 0.21\%
+for \pn, sufficient for formal validation as a planet
+\citep{morton_efficient_2012}.  We did not incorporate our constraint
+that \tn\ is not double-lined, which rules out an additional portion
+of BEB parameter space.  Had we not acquired multicolor ground-based
+photometry, and been unable to exclude HEB scenarios, the FPP would
+have risen to 8\%.  However, since the transits are achromatic
 (Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
@@
 
-% NOTE: might want a table of all ages
-
-IC~2602 canonically has an age of $30\pm20\,{\rm Myr}$ (CITE: Van
-Leeuwen 2009).
-Or logage between 7.533 and 7.563	\citep{bossini_age_2019}.
-
-Or Li age of 40-50Myr (David+19, comparison with other Li stars).
-
-Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range between
-slightly super-solar ($0.04\pm0.01$, \citealt{baratella_gaia-eso_2020}) and
-slightly sub-solar ($-0.02 \pm 0.02$, \citealt{netopil_metallicity_2016}).
-
-IC~2602 is supervirial, in the sense that the observed stellar velocity
-dispersion is larger than the value expected if it were in virial equilibrium
-by about a factor of two \citep{bravi_gaia-eso_2018}.
-
-IC~2602 happens to be near the western edge of the Sco OB2
-association, and is relatively close to it in proper motion space
-(Damiani+2019).
-Damini+2019 also reported evidence for the ongoing evaporation of
-\cn, in the form of a diffuse halo of young stars around the central
-density cusps.
-
-While \cn\ is older than most known Sco OB2 members,
-
-"""Although IC 2602 does not belong to Sco OB2, it is
-spatially and dynamically a close relative, and for this reason
-we include it in this work, if even marginally"" (Damiani+2019).
-"""We also find that the open cluster IC 2602 has a similar dynamics
-to Sco OB2, and its PMS members are currently evaporating and forming
-a diffuse (size 10deg) halo around its double-peaked core"""
+\input{ic2602_ages.tex}
+
+The \cn\ cluster is about 150$\,$pc from the Earth, and is near the
+galactic plane with $(l,b)\approx(289.6^\circ, -5.0^\circ)$
+\citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
+$\theta$ Carinae cluster, after its brightest member.  While \cn\ is
+close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus OB2
+association in both position and proper motion space, its older age
+and clear kinematic separation indicate that it is a distinct stellar
+population \citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.
+
+Reliable ages reported for \cn\ range from 30--46$\,$Myr.  We have
+collected ages reported over the years in Table~\ref{tab:ages}.  The
+Li depletion boundary technique yields slightly older absolute
+ages than isochrone fitting.  Rather than redetermine the age of the cluster and add another
+line to the table, we simply adopt the absolute age range for \tn\ of
+30--46$\,$Myr.
+
+Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range
+between slightly super-solar ($0.04\pm0.01$,
+\citealt{baratella_gaia-eso_2020}) and slightly sub-solar ($-0.02 \pm
+0.02$, \citealt{netopil_metallicity_2016}).  The extinction $E(B-V)$
+is rather low, with reported values ranging from 0.03 to 0.07
+\citep[{\it e.g.},][]{randich_gaiaeso_2018}.
+
+Kinematically, IC~2602 seems to be supervirial, in the sense that the
+observed stellar velocity dispersion is larger than the value expected
+if it were in virial equilibrium by about a factor of two
+\citep{bravi_gaia-eso_2018}.  \citet{damiani_stellar_2019} also
+reported evidence for the ongoing evaporation of \cn, in the form of a
+diffuse $\approx10^\circ$ halo of young stars around the central
+density cusps.  A gyrochronological study of these stars could confirm
+that these stars are truly coeval with the cluster.
 

### 2020-06-25 paper/ms.tex
tweak plots

@@
   and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
-  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
-  Pleiades'').  The star and validated planet are therefore 30$\pm$15
-  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
-  roughly Jupiter-sized.  However, its transits are grazing: $b >
-  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
-  lies within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
-  percentile), due to the degeneracy between the planetary size and
-  the impact parameter of the transit.  From radial velocity
-  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
-  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
-  usually are indicative of astrophysical false positive scenarios.
-  Our follow-up data show that such scenarios are highly unlikely.
-  Multi-color photometry requires eclipsing companions to have nearly
-  identical color as TOI$\,$837, ruling out hierarchical eclipsing
-  binary scenarios.  Background eclipsing binary scenarios are limited
-  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
-  837.01 is therefore a validated adolescent exoplanet.  Further
-  observations of its stellar obliquity, atmosphere, and mass should
-  confirm its planetary nature beyond doubt, and could improve our
-  understanding of how the physical and orbital properties of
-  exoplanets change in time.
+  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602.  The star and validated
+  planet are therefore between 30 and 46 million years old.  The
+  planet is warm ($P = 8.32\,{\rm d}$) and roughly Jupiter-sized.
+  However, its transits are grazing: $b > 0.92$ at 3$\sigma$.  From
+  TESS photometry alone, the planetary size lies within 0.58--3.87
+  $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile), due to the
+  degeneracy between the planetary size and the impact parameter of
+  the transit.  From radial velocity monitoring, we limit the minimum
+  mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits
+  are cause for concern: they usually are indicative of astrophysical
+  false positive scenarios.  Our follow-up data show that such
+  scenarios are highly unlikely.  Multi-color photometry requires
+  eclipsing companions to have nearly identical color as TOI$\,$837,
+  ruling out hierarchical eclipsing binary scenarios.  Background
+  eclipsing binary scenarios are limited by speckle imaging, but
+  formally remain a 0.2\% possibility.  TOI 837.01 is therefore a
+  validated adolescent exoplanet.  Further observations of its stellar
+  obliquity, atmosphere, and mass should confirm its planetary nature
+  beyond doubt, and could improve our understanding of how the
+  physical and orbital properties of exoplanets change in time.
 \end{abstract}
@@
 
-		\vspace{-0.5cm}
+		\vspace{-0.6cm}
 		\subfloat{
@@
   \caption{
-    {\bf Joint TESS and multicolor photometry.} {\it Top:}
+    {\bf Photometry of \tn.} {\it Top:}
     Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
     measurements, detrended with a 0.3-day robust Huber spline (see
-    Section~\ref{subsec:tess}).  Black points are binned to 6 minute
-    intervals.  The line shows the transit model corresponding to the
-    median transit parameters (Table~2).  {\it Bottom:} Multicolor
-    photometry from the El Sauce 0.36m.  The consistent transit depths
-    between TESS-band and the bluer Cousins-R and Johnson-B bandpasses
-    rules out select false positive scenarios.
+    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
+    intervals.  The gray line shows the median transit model corresponding to the
+    fitted to both the TESS and ground-based transits
+    (Table~2).  {\it Bottom:} Multicolor
+    photometry from the El Sauce 0.36m; gray points are binned to 10-minute intervals.  Models
+    show lower limits on the transit depths in 
+    the Cousins-R and Johnson-B bandpasses used to rule out specific false positive scenarios.
     \label{fig:jointphot}
@@
 \input{TOI837_rv_table.tex}
-\input{model_comparison_table.tex}
+%\input{model_comparison_table.tex}
 \input{model_posterior_table.tex}

### 2020-06-25 drivers/fit_alltransit.py

@@ -32,7 +32,7 @@ def main(modelid):
     cut_tess = 1
 
     phaseplot = 1
-    grounddepth = 1
+    grounddepth = 0
     fittedzoom = 0
     cornerplot = 0
 

### 2020-06-25 timmy/plotting.py

@@ -803,22 +803,22 @@ def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
     else:
 
         a0.scatter(orb_d['phase']*P_orb*24, 1e3*(orb_d['mags']-1),
-                   color='gray', s=4, alpha=0.5, zorder=4, linewidths=0,
+                   color='darkgray', s=7, alpha=0.5, zorder=4, linewidths=0,
                    rasterized=True)
         a0.scatter(orb_bd['binnedphases']*P_orb*24,
-                   1e3*(orb_bd['binnedmags']-1), color='black', s=12, alpha=1,
+                   1e3*(orb_bd['binnedmags']-1), color='black', s=18, alpha=1,
                    zorder=5, linewidths=0)
         a0.plot(mod_d['phase']*P_orb*24, 1e3*(mod_d['mags']-1),
-                color='darkgray', alpha=0.8, rasterized=False, lw=1, zorder=1)
+                color='gray', alpha=0.8, rasterized=False, lw=1, zorder=1)
 
         a1.scatter(orb_d['phase']*P_orb*24, 1e3*(orb_d['mags']-mod_d['mags']),
-                   color='gray', s=4, alpha=0.5, zorder=4, linewidths=0,
+                   color='darkgray', s=7, alpha=0.5, zorder=4, linewidths=0,
                    rasterized=True)
         a1.scatter(resid_bd['binnedphases']*P_orb*24,
-                   1e3*resid_bd['binnedmags'], color='black', s=12, alpha=1,
+                   1e3*resid_bd['binnedmags'], color='black', s=18, alpha=1,
                    zorder=5, linewidths=0)
         a1.plot(mod_d['phase']*P_orb*24, 1e3*(mod_d['mags']-mod_d['mags']),
-                color='darkgray', alpha=0.8, rasterized=False, lw=1, zorder=1)
+                color='gray', alpha=0.8, rasterized=False, lw=1, zorder=1)
 
 
     if show_samples:
@@ -2368,10 +2368,10 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None):
     tra_axs = axs.flatten()
     tra_ixs = [44, 47, 50, 53]
 
-    titles = ['2020-04-01\nEvans R$_\mathrm{C}$',
-              '2020-04-26\nEvans R$_\mathrm{C}$',
[…]

### 2020-06-25 drivers/make_TOI837_rv_table.py
table and figure updates

@@ -10,54 +10,39 @@ from numpy import array as nparr
 from glob import glob
 import os, pickle
 
+from timmy.paths import DATADIR, RESULTSDIR
+
 def main():
 
-    df = pd.read_csv(
-        '../data/RVs_all_WASP4b_for_fitting_20190911.csv', sep=','
-    )
-    jump_df = pd.read_csv(
-        '../data/20190911_jump_wasp4_rv.csv', comment='#', sep=','
-    )
+    objname = 'TOI837'
+    rvpath = os.path.join(DATADIR, 'spectra', 'RVs_20200624_clean.csv')
 
-    svalue = np.hstack((
-        np.ones(len(df[df.tel != 'HIRES']))*np.nan,
-        nparr(jump_df.svalue)
-    ))
+    outdir = os.path.join(RESULTSDIR, 'paper_tables')
 
-    original_references = np.array(df['Source'])
-    references = []
-    for ref in original_references:
-        if ref == 'Triaud+2010_vizier':
-            references.append('T+10')
-        elif ref == 'Pont+2011_vizierMNRAS':
-            references.append('P+11')
-        elif ref == 'jump_20190911':
-            references.append('B+20')
-    references = np.array(references)
+    df = pd.read_csv(rvpath)
 
     outdf = pd.DataFrame(
         {'time': np.round(nparr(df.time-2450000),6),
-         'mnvel': np.round(nparr(df.mnvel),5),
-         'errvel': np.round(nparr(df.errvel),5),
-         'svalue': svalue,
-         'tel': nparr(df.tel),
-         'provenance': references
+         'mnvel': np.round(nparr(df.mnvel),2),
+         'errvel': np.round(nparr(df.errvel),2),
+         'tel': nparr(df.tel)
         }
     )
 
-    outpath = '../paper/WASP-4b_rv_data.tex'
+    outpath = os.path.join(outdir, f'{objname}_rv_data.tex')
     with open(outpath,'w') as tf:
-        tf.write(outdf.to_latex(index=False, escape=False, float_format='%.6f'))
+        tf.write(outdf.to_latex(index=False, escape=False))
+
     print('wrote {:s}'.format(outpath))
 
-    outdf.to_csv('../paper/WASP-4b_rv_data.csv', index=False,
-                 float_format='%.6f')
-    print('also wrote ../paper/WASP-4b_rv_data.csv')
+    outcsv = os.path.join(outdir, f'{objname}_rv_data.csv')
[…]

### 2020-06-25 drivers/plot_rvs.py

@@ -191,8 +191,8 @@ class MultipanelPlot(object):
     def __init__(self, post, saveplot=None, epoch=2450000, yscale_auto=False,
                  yscale_sigma=3.0, phase_nrows=None, phase_ncols=None,
                  uparams=None, telfmts={}, legend=True, phase_limits=[],
-                 nobin=False, phasetext_size='large', rv_phase_space=0.08,
-                 figwidth=5.5, fit_linewidth=1.0, set_xlim=None, text_size=9,
+                 nobin=False, phasetext_size='medium', rv_phase_space=0.08,
+                 figwidth=4.2, fit_linewidth=1.0, set_xlim=None, text_size=9,
                  highlight_last=False, show_rms=False,
                  legend_kwargs=dict(loc='best')):
 
@@ -348,7 +348,7 @@ class MultipanelPlot(object):
             scale = np.std(self.rawresid+self.rvmod)
             ax.set_ylim(-self.yscale_sigma * scale, self.yscale_sigma * scale)
 
-        ax.set_ylabel('Radial velocity [{ms:}]'.format(**plot.latex))
+        ax.set_ylabel('RV [{ms:}]'.format(**plot.latex))
         ax.set_xlabel('Time [JD - {:d}]'.format(int(np.round(self.epoch))))
         ticks = ax.yaxis.get_majorticklocs()
         ax.yaxis.set_ticks(ticks[1:])
@@ -489,7 +489,7 @@ class MultipanelPlot(object):
         if not self.yscale_auto:
             scale = np.std(rvdatcat)
             ax.set_ylim(-self.yscale_sigma*scale, self.yscale_sigma*scale)
-        ax.set_ylim((-425, 425))
+        ax.set_ylim((-510, 510))
 
         keys = [p+str(pnum) for p in ['per', 'k', 'e']]
 
@@ -498,7 +498,7 @@ class MultipanelPlot(object):
             ticks = ax.yaxis.get_majorticklocs()
             ax.yaxis.set_ticks(ticks[1:-1])
 
-        ax.set_ylabel('Radial velocity [{ms:}]'.format(**plot.latex))
+        ax.set_ylabel('RV [{ms:}]'.format(**plot.latex))
         ax.set_xlabel('Phase')
 
         ax.get_yaxis().set_tick_params(which='both', direction='in')
@@ -625,6 +625,7 @@ class MultipanelPlot(object):
                 pltletter += 1
 
         if self.saveplot is not None:
[…]

### 2020-06-26 paper/ms.tex
table and figure updates
update manuscript

@@
 		\leavevmode
-		\includegraphics[width=0.47\textwidth]{f3.pdf}
+		\includegraphics[width=0.48\textwidth]{f3.pdf}
 	\end{center}
@@
   right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
-  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
-  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
+  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
+  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
   RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
   proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
-  \alpha}\cos\delta$) highlights the membership selection function.
+  \alpha}\cos\delta$) highlights incompleteness in the membership selection function.
   \label{fig:full_kinematics}
@@
 
+\subsubsection{Physical Characteristics}
+
 \input{ic2602_ages.tex}
@@
 $\theta$ Carinae cluster, after its brightest member.  While \cn\ is
-close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus OB2
-association in both position and proper motion space, its older age
-and clear kinematic separation indicate that it is a distinct stellar
-population \citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.
+close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus
+OB2 association in both position and proper motion space, its older
+age and clear kinematic separation indicate that it is a distinct
+stellar population
+\citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.
 
@@
 collected ages reported over the years in Table~\ref{tab:ages}.  The
-Li depletion boundary technique yields slightly older absolute
-ages than isochrone fitting.  Rather than redetermine the age of the cluster and add another
-line to the table, we simply adopt the absolute age range for \tn\ of
-30--46$\,$Myr.
+Li depletion boundary technique yields slightly older absolute ages
+than isochrone fitting.  Rather than redetermine the age of the
+cluster and add another line to the table, we simply adopt the
+absolute age range for \tn\ of 30--46$\,$Myr.
 
@@
 
-\subsection{The Star}
-\label{subsec:star}
-\subsubsection{Cluster Membership}
-\label{subsec:member}
-
-\tn\ has been reported as a member of \cn\ by multiple independent 
-investigators \citep{Kharchenko_et_al_2013,cantatgaudin_gaia_2018}.
-%FIXME FIXME finish these citations
-%include: Damiani+2019, Cantat-Gaudin+2020 who explicitly listed it as
-%IC2602
-
-The Gaia kinematics are good; gamma velocity is correct; Li (FEROS +
-Veloce) is strong; the rotation period and vsini agree with
-sub-Pleiades age expected for an IC 2602 member.
-
 \subsubsection{HR Diagram}
 
-Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn\ in
-reference to the broader \cn\ cluster, as well as its neighborhood.
-Cluster members were identified by \citet{cantatgaudin_gaia_2018}
-using using Gaia-DR2 positions, proper motions, and parallaxes.  
-We included candidate members with formal membership probability
-exceeding 10\%.  Save for a few low-mass outliers, most members appear
-to be young and coeval.
+Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
+\cn\ cluster, and the ``neighborhood'' of spatially nearby stars.
+Stars labelled as ``cluster members'' are those reported by
+\citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
+motions, and parallaxes.  We included candidate members with formal
+membership probability exceeding 10\%.  Save for a few low-mass
+outliers, most members appear to be young and coeval.
 
@@
 the cluster isochrone.  This photometrically limits the presence of
-binary companions in the \tn\ system, to a magnitude difference of
-perhaps half the brightness of the target star.
+binary companions in the \tn\ system, to within perhaps half the
+brightness ($\approx0.75$ magnitudes) of the target star.
 
@@
 as 5-dimensional kinematic members through the unsupervised
-\citet{cantat-gaudin_gaia_2018} membership assignment process.
-
-\subsubsection{Position and Kinematics}
-
-We examine the six-dimensional positions and kinematics in greater
-depth in Figure~\ref{fig:full_kinematics}.  The ``neighborhood'' is
-defined here identically to as in Figure~\ref{fig:hr}.  The axes
-limits for the right ascension, declination, and parallax dimensions
-are as in the Gaia archive query.  The axes limits for the proper
-motion and radial velocity dimensions are set at the 25$^{\rm th}$ and
-75$^{\rm th}$ percentiles, in order to give a sense of the
-population's distribution, while excluding outlying points.  The
-radial velocities suffer the greatest incompleteness due to the
-current $G\approx12$ magnitude limit of the Gaia-DR2 data processing.
-
-Figure~\ref{fig:full_kinematics} provides strong evidence {\it (i)} for the
-existence of the \cn\ open cluster and {\it (ii)} for the membership
-of \tn\ within \cn.
-The only dimension that could perhaps lead to some worry is the
-parallax, as \tn\ is one of the closest \cn\ members reported by
-\citet{cantatgaudin_gaia_2018}.
-Fortunately, there are independent means of verifying stellar youth.
+\citet{cantatgaudin_gaia_2018} membership assignment process.
+
+\subsection{The Star}
+\label{subsec:star}
+
+\subsubsection{Membership of \tn\ in \cn}
+\label{subsec:member}
+
+\tn\ has been reported as a member of \cn\ by many independent
+investigators \citep[{\it
+e.g.},][]{Kharchenko_et_al_2013,oh_comoving_2017,cantatgaudin_gaia_2018,damiani_stellar_2019,kounkel_untangling_2019}.
+The simplest way to verify the membership is through inspection of the
+Gaia DR2 position and kinematics.  Figure~\ref{fig:full_kinematics}
+shows the six-dimensional positions and kinematics of \tn, \cn\
+members, and nearby stars.  The ``neighborhood'' is defined as in
+Figure~\ref{fig:hr}.  The axes limits for the right ascension,
+declination, and parallax dimensions are set by being within 5
+standard deviations of the mean \cn\ right ascension, declination, and
+parallax.  The axes limits for the proper motion and radial velocity
+dimensions are set at the 25$^{\rm th}$ and 75$^{\rm th}$ percentiles,
+in order to give a sense of the population's distribution, while
+excluding outliers.  The radial velocities suffer the greatest
+incompleteness due to the current $G\approx12$ magnitude limit of the
+Gaia DR2 data processing.
+
+Figure~\ref{fig:full_kinematics} provides strong evidence that \tn\ is
+a member of \cn.  The only dimension that could lead to some worry is
+the parallax, as \tn\ is one of the closest \cn\ members reported by
+\citet{cantatgaudin_gaia_2018}.  Fortunately, there are independent
+means of verifying the star's youth.
 
@@
 
-%NOTE: begs the question... is there a large population of ~30-50 Myr old
-% stars for which we could measure the rotation periods, and clarify if the scatter of Upper Sco chills out?
+%NOTE: begs the question... is there a large population of ~30-50 Myr
+%old stars for which we could measure the rotation periods, and
+%clarify if the scatter of Upper Sco chills out?
 
@@
 
-\subsubsection{Literature Membership}
-The membership of \tn\ in \cn\ was noted by \citet{oh_comoving_2017},
-in what they dubbed ``Group 5''.
-Analyzing the clusters of \citet{oh_comoving_2017},
-\citet{bochanski_fundamental_2018} fitted the Gaia, 2MASS, and
-WISE photometry with MIST isochrones, and reported stellar masses,
-radii, metallicities, ages, distances, and extinction for 9754 stars,
-including \tn.
-%Bochanski reported:
-%logAge 9.38 +0.42 -0.26
-%dist 138.3 +7.0 -7.2
-%A_v = 0.27 +0.18 - 0.18
-%
-
-\tn\ was also listed as a member of ``Theia 92'' by
-\citet{kounkel_untangling_2019}.
-These authors identified 999 candidate cluster members, and
-reported a cluster isochrone age $\log t = 7.55$ with uncertainty
-$\approx 0.15\,{\rm dex}$.
-They reported an average extinction of Av=0.243 mag.
-
 \subsubsection{Stellar Parameters}
+
+\input{stellar_parameters.tex}
 
@@
 
-\subsubsection{Physical}
  (Lstar, Rstar, Teff, Age and Mstar)
@@
 
-Figure~\ref{fig:sed}.
-The SED fit, looking really good with rchi2 = 1.6:
+% Figure~\ref{fig:sed}.
+Mention The SED fit, looking really good with rchi2 = 1.6:
 
@@
 \label{subsec:planet}
+
+\input{model_posterior_table.tex}
 
@@
 %\input{model_comparison_table.tex}
-\input{model_posterior_table.tex}
 \clearpage

### 2020-06-26 paper/ms.tex
update paper

@@
 
-Finding and studying systems undergoing these evolutionary changes is a major
-goal in contemporary exoplanet research.  To identify stars younger than say
-1$\,$Gyr, a number of direct and indirect methods are available
-\citep{soderblom_ages_2010}.  The traditional approach is to isochronally
-age-date coeval groups of stars, hereafter ``clusters'' \citep[{\it
-e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.  Young
-field stars can also be identified using age indicators such as stellar
-rotation periods, the abundance of photospheric lithium, and chromospheric
-diagnostics such as calcium emission and broadband UV emission.  Studies by for
-instance \citet{david_discovery_2018} and G{.}~Zhou et al. (2020, submitted)
-have combined these methods for individual field stars.  Many of the latter
-methods were summarized by \citet{mamajek_improved_2008}, and have since been
-calibrated by {\it e.g.},
-\citet{barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
+Finding and studying systems undergoing these evolutionary changes is
+a major goal in contemporary exoplanet research.  To identify stars
+younger than say 1$\,$Gyr, a number of direct and indirect methods are
+available \citep{soderblom_ages_2010}.  The traditional approach is to
+isochronally age-date coeval groups of stars, hereafter ``clusters''
+\citep[{\it
+e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
+Young field stars can also be identified using age indicators such as
+stellar rotation periods, the abundance of photospheric lithium, and
+chromospheric diagnostics such as calcium emission and broadband UV
+emission.  Studies by for instance \citet{david_discovery_2018} and
+G{.}~Zhou et al. (2020, submitted) have combined these methods for
+individual field stars.  Many of the latter methods were summarized by
+\citet{mamajek_improved_2008}, and have since been calibrated by {\it
+e.g.},
+\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
 and \citet{curtis_tess_2019} for stellar rotation,
-\citet{zerjal_chromospherically_2017} for chromospheric activity, and {\it
-e.g.}, \citet{berger_identifying_2018} and \citet{zerjal_galah_2019} for
-lithium abundances.
+\citet{zerjal_chromospherically_2017} for chromospheric activity, and
+{\it e.g.}, \citet{elliott_search_2016,berger_identifying_2018} and
+\citet{zerjal_galah_2019} for lithium abundances.
 
@@
 Li depletion boundary technique yields slightly older absolute ages
-than isochrone fitting.  Rather than redetermine the age of the
-cluster and add another line to the table, we simply adopt the
-absolute age range for \tn\ of 30--46$\,$Myr.
+than isochrone fitting \citep{dobbie_ic_2010,randich_gaiaeso_2018}.
+Rather than redetermine the age of the cluster and add another line to
+the table, we simply adopt the absolute age range for \tn\ of
+30--46$\,$Myr.
 
@@
 
-TESS photometric rotation period = 3.5days ish.
-vsini = 17.48 $\pm$ 0.15 (CHIRON).
-The two agree.
-
-For comparison, gyrochrones would ``predict'' X.XX.
-
-This implies sub-Pleiades age expected for an IC 2602 member.
-
-Figure~\ref{fig:lithium_rotation} compares the stellar rotation period of \tn\ to
-periods that have been measured in a number of well-studied open clusters.
-\tn\ seems to be gyrochronologically coeval with the Pleiades sequence.
-
-We note that this is still in the ``sub 500 Myr'' range, when classical
-Skumanich spin-down is not expected to be happening (why is this the number?).
-
-This agrees with recent empirical results from Rebull et al 2020 and perhaps also 2018(?):
-they observed the Taurus foreground (age 30 Myr) and saw that it was 
-roughly consistent with the Pleaides.
-Upper Sco had a consistent mean, but a much larger scatter.
-
-%NOTE: begs the question... is there a large population of ~30-50 Myr
-%old stars for which we could measure the rotation periods, and
-%clarify if the scatter of Upper Sco chills out?
+As stars get older, their rotation rates incrementally slow due to
+magnetic braking \cite{weber_angular_1967,skumanich_time_1972}.  One
+way to verify the youth of \tn\ is by comparing its rotation period to
+other stars with known ages.
+
+We measured the rotation period from the PDCSAP light curve using the
+Lomb-Scargle periodogram implemented in \texttt{astropy}
+\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
+We fitted the light curve without masking out the transits or flares,
+as these represent a small fraction of the overall time series.  To
+derive the uncertainty on the best period, we fitted a gaussian to the
+dominant peak, after first ensuring that we had oversampled the initial
+frequency grid.  This gave a rotation period of $P_{\rm rot} = 2.987
+\pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in the
+periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$ when
+allowing for two Fourier terms.  As the second model provides a better
+fit to the data, we adopt the second measurement.
+
+As we will discuss in Section~\ref{subsec:starparams}, we measured the
+star's radius by combining the spectroscopic effective temperature
+with a broadband photometry SED fit.  We would expect, combining our
+$R_\star$ and $P_{\rm rot}$ measurements, that the equatorial velocity
+$v$ of the star would be $17.67 \pm 0.32
+\,{\rm km\,s}^{-1}$.  Our spectroscopically measured $v\sin i$ from
+CHIRON, $17.48 \pm 0.15 \,{\rm km\,s}^{-1}$ agrees reasonably well
+with this expectation.
+
+The star is clearly a rapid rotator.
+Figure~\ref{fig:lithium_rotation} compares its rotation period with
+rotation periods that have been measured in a number of well-studied
+open clusters.  \tn\ seems to be gyrochronologically coeval with the
+Pleiades sequence.  This is not to say that \tn\ is ``Pleaides-aged'',
+because the observed scatter in the rotation-period diagram for the
+first 10--100$\,$Myr is quite high \citep[see Figure~9 of][]{rebull_rotation_2020}.  Instead, we interpret it as a
+piece of evidence to support the claim that \tn\ is younger than $\sim
+500\,{\rm Myr}$.
 
@@
 
-Rafael's co-added FEROS spectra gave a Li doublet equivalent width of
-154 milliangstrom.
-
-Lithium depletion for a star of TOI-837's spectral type happens
-over timescales >100 Myr (Soderblom+2013). This is because the
-convective envelopes are very shallow, so they don't cycle material
-down to the >3e6 K core until much later.
-
-Nonetheless, comparison of early-G field stars to e.g., 600 Myr old
-Hyads has shown that the depletion does happen over gigayear timescales
-(Berger+2018, fig 7).
-
-Figure~\ref{fig:lithium_rotation} compares our measured \tn\ Li EW 
-to stars in the field, and to young open cluster members.
-The field star measurements were collected by
-\citet{berger_identifying_2018}.
-We have shown the points with lithium detections at ${\rm SNR}>3$.
-TOI-837 is consistent with being younger than almost all CKS
-planet-hosting field stars.
-
-The young open cluster members were selected for the presence of
-lithium, as described by \citet{randich_gaiaeso_2018}.
-The TOI-837 Li EW measured here (150 milliangstrom) is consistent
-with what's seen for stars of similar colors in <100 Myr old moving
-groups.
-(Elliott+2016, Fig 11 -- attached).  This is sensible, because
-IC 2602 is supposed to be 50 Myr old.
+Lithium depletion for early G-dwarfs like \tn\ requires
+hundreds of megayears \citep{soderblom_ages_2014}. This is because
+their convective envelopes are shallow, and so transport of
+photospheric lithium to the hot core takes place over diffusive timescales,
+rather than convective timescales.  Nonetheless, comparison of early G-dwarfs in
+the field to {\it e.g.}, 600 Myr old Hyads has shown that the
+depletion does indeed happen over many gigayears
+\citep{berger_identifying_2018}.
+
+The spectra of \tn\ all show the 6708$\,$\AA\ lithium doublet in
+absorption. Opting to use our FEROS spectra because of their high S/N,
+we measured the line's equivalent width (EW) to be $154 \pm 9 \, $m\AA.  Figure~\ref{fig:lithium_rotation} compares this EW to stars
+in the field, and other young open cluster members.  The field star
+measurements were collected by \citet{berger_identifying_2018}; we
+show their reported lithium detections with ${\rm S/N}>3$.  The young
+open cluster members were selected for the presence of lithium, as
+described by \citet{randich_gaiaeso_2018}.  The measured \tn\ Li EW is
+much larger than observed for field stars, and is consistent with
+lithium absorption seen in stars with similar colors in sub-100$\,{\rm Myr}$
+moving groups.
 
 \subsubsection{Stellar Parameters}
+\label{subsec:starparams}
 
@@
 
-% TODO: decide whether to include
+some words
 
@@
   %\texttt{scikit-learn} \citep{scikit-learn},
-  \texttt{scipy} \citep{jones_scipy_2001}.
+  \texttt{scipy} \citep{jones_scipy_2001},
   \texttt{tesscut} \citep{brasseur_astrocut_2019},

### 2020-06-26 timmy/priors.py
add rotation period measurement

@@ -13,7 +13,7 @@ LOGG_STDEV = 0.03*3
 
 TEFF = 5946 # CHIRON spectra
 LI_EW = 154 # mA
-P_ROT = 3.3 # days, by eye.
+P_ROT = 3.004 # days, from Lomb-Scargle fit.
 
 ROT_AMP = 0.027 # i.e. 27 parts per thousands, peak-to-peak, by eye
 

### 2020-06-26 timmy/rotationperiod.py

@@ -1,0 +1,101 @@
+import numpy as np, matplotlib.pyplot as plt
+from astropy.timeseries import LombScargle
+from astropy.modeling import models, fitting
+from timmy.plotting import format_ax, savefig
+
+def measure_rotation_period_and_unc(time, flux, period_min, period_max,
+                                    period_fit_cut=0.5, nterms=1,
+                                    samples_per_peak=50,
+                                    plotpath=None):
+    """
+    You know a light curve contains rotational modulation. You want to get the
+    period, and the uncertainty.  Get the period as the peak of the LS
+    periodogram. Get the uncertainty by fitting a gaussian to that
+    (oversampled) peak, and saying the std dev is the uncertainty.
+
+    args:
+        nterms (int): number of fourier terms in the periodogram
+
+        period_fit_cut (float): the width in days of the periodogram to fit.
+        essentially an upper limit on your period uncertainty.
+
+        samples_per_peak (int): targetted samples per peak in the periodogram.
+        astropy default is 5. to oversample, do more than 5.
+
+    returns: period, period_unc
+    """
+
+    #
+    # run initial lomb scargle
+    #
+    ls = LombScargle(time, flux, nterms=nterms)
+
+    freq, power = ls.autopower(
+        minimum_frequency=1/period_max, maximum_frequency=1/period_min,
+        samples_per_peak=samples_per_peak
+    )
+    period = 1/freq
+
+    ls_freq_0 = freq[np.argmax(power)]
+    ls_period_0 = 1/ls_freq_0
+    ls_power_0 = power[np.argmax(power)]
+
+    #
+    # now fit the gaussian, get the uncertainty as the oversampled width.
+    #
+    stddev_init = 0.1 # days
+    g_init = models.Gaussian1D(amplitude=ls_power_0, mean=ls_period_0,
+                               stddev=stddev_init)
+    g_init.mean.fixed = True
+
+    fit_g = fitting.LevMarLSQFitter()
+
+    sel = (
+        (period < ls_period_0 + period_fit_cut/2)
+        &
+        (period > ls_period_0 - period_fit_cut/2)
+    )
+
+    g = fit_g(g_init, period[sel], power[sel])
+
+    if isinstance(plotpath, str):
+
[…]

### 2020-06-26 paper/ms.tex
update manuscript

@@
 \newcommand{\cn}{IC~2602} % cluster name
+
+\newcommand{\kms}{\,km\,s$^{-1}$}
 
@@
 parameters, we cross-correlated the template against {\bf something},
-and used the {\bf \texttt{nameofcode}}.  This yielded:
-\begin{align}
-  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
-  \log g        &= 4.48 \pm 0.03, \nonumber \\
-  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
-  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
-\end{align}
-These spectroscopic parameters were used in our final analysis of the
-system (Section~\ref{sec:system}).  We measured the radial velocities
-through a least-squares deconvolution of the observed spectra against
-the same synthetic template.  The resulting velocities are given in
-Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.
+and used the {\bf \texttt{nameofcode}}.  We measured the radial
+velocities through a least-squares deconvolution of the observed
+spectra against the same synthetic template.  The resulting velocities
+are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.
 
@@
 derive the uncertainty on the best period, we fitted a gaussian to the
-dominant peak, after first ensuring that we had oversampled the initial
-frequency grid.  This gave a rotation period of $P_{\rm rot} = 2.987
-\pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in the
-periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$ when
-allowing for two Fourier terms.  As the second model provides a better
-fit to the data, we adopt the second measurement.
+dominant peak, after first ensuring that we had oversampled the
+initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
+2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
+the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
+when allowing for two Fourier terms.  As the second model provides a
+better fit to the data, we adopt the second measurement.
 
@@
 $R_\star$ and $P_{\rm rot}$ measurements, that the equatorial velocity
-$v$ of the star would be $17.67 \pm 0.32
-\,{\rm km\,s}^{-1}$.  Our spectroscopically measured $v\sin i$ from
-CHIRON, $17.48 \pm 0.15 \,{\rm km\,s}^{-1}$ agrees reasonably well
-with this expectation.
+$v$ of the star would be $17.67 \pm 0.32 \,{\rm km\,s}^{-1}$.  Our
+spectroscopically measured $v\sin i$ from CHIRON, $17.48 \pm 0.15
+\,{\rm km\,s}^{-1}$ agrees reasonably well with this expectation.
 
@@
 because the observed scatter in the rotation-period diagram for the
-first 10--100$\,$Myr is quite high \citep[see Figure~9 of][]{rebull_rotation_2020}.  Instead, we interpret it as a
-piece of evidence to support the claim that \tn\ is younger than $\sim
+first 10--100$\,$Myr is quite high \citep[see Figure~9
+of][]{rebull_rotation_2020}.  Instead, we interpret it as a piece of
+evidence to support the claim that \tn\ is younger than $\sim
 500\,{\rm Myr}$.
@@
 
-Lithium depletion for early G-dwarfs like \tn\ requires
-hundreds of megayears \citep{soderblom_ages_2014}. This is because
-their convective envelopes are shallow, and so transport of
-photospheric lithium to the hot core takes place over diffusive timescales,
-rather than convective timescales.  Nonetheless, comparison of early G-dwarfs in
-the field to {\it e.g.}, 600 Myr old Hyads has shown that the
+Lithium depletion for early G-dwarfs like \tn\ requires hundreds of
+megayears \citep{soderblom_ages_2014}. This is because their
+convective envelopes are shallow, and so transport of photospheric
+lithium to the hot core takes place over diffusive timescales, rather
+than convective timescales.  Nonetheless, comparison of early G-dwarfs
+in the field to {\it e.g.}, 600 Myr old Hyads has shown that the
 depletion does indeed happen over many gigayears
@@
 absorption. Opting to use our FEROS spectra because of their high S/N,
-we measured the line's equivalent width (EW) to be $154 \pm 9 \, $m\AA.  Figure~\ref{fig:lithium_rotation} compares this EW to stars
-in the field, and other young open cluster members.  The field star
+we measured the line's equivalent width (EW) to be $154 \pm 9 \,
+$m\AA.  Figure~\ref{fig:lithium_rotation} compares this EW to stars in
+the field, and other young open cluster members.  The field star
 measurements were collected by \citet{berger_identifying_2018}; we
@@
 much larger than observed for field stars, and is consistent with
-lithium absorption seen in stars with similar colors in sub-100$\,{\rm Myr}$
-moving groups.
+lithium absorption seen in stars with similar colors in sub-100$\,{\rm
+Myr}$ moving groups.
 
@@
 
-\input{stellar_parameters.tex}
-
-some words
-
-% \begin{figure}[t!]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=0.48\textwidth]{f6.png}
-% 	\end{center}
-% 	\vspace{-0.7cm}
-% 	\caption{
-%     {\bf Spectral energy distribution of \tn\ from archival
-%     photometry.}
-%     {\bf Keivan: please describe, and if possible, send me the data
-%     (photometry + the atmosphere model) used to generate the plot so I
-%     can regenerate it in a consistent style with the rest of the paper}
-%     \label{fig:sed}
-% 	}
-% \end{figure}
+\input{starparams.tex}
+
+We measured the physical properties of \tn\ as follows.
+
+The spectroscopic parameters were measured from each of the six CHIRON
+spectra (Section~\ref{subsec:chiron}). We then averaged the results,
+and adopted the standard deviation across the spectra as the
+uncertainty.
+
+This yielded:
+\begin{align}
+  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
+  \log g        &= 4.48 \pm 0.03, \nonumber \\
+  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
+  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
+\end{align}
+These spectroscopic parameters were used in our final analysis of the
+system (Section~\ref{sec:system}).
 

### 2020-06-26 paper/ms.tex
update manuscript

@@
 		\leavevmode
-		\includegraphics[width=0.9\textwidth]{f8.pdf}
+		\includegraphics[width=0.7\textwidth]{f8.pdf}
 	\end{center}
@@
 
+\input{ic2602_ages.tex}
+
+\input{starparams.tex}
+
+\input{model_posterior_table.tex}
+
 \subsection{The Cluster}
@@
 \subsubsection{Physical Characteristics}
-
-\input{ic2602_ages.tex}
+\label{subsec:clusterchar}
 
@@
 first 10--100$\,$Myr is quite high \citep[see Figure~9
-of][]{rebull_rotation_2020}.  Instead, we interpret it as a piece of
-evidence to support the claim that \tn\ is younger than $\sim
-500\,{\rm Myr}$.
+of][]{rebull_rotation_2020}.  Instead, we interpret the rotation
+period as evidence to support the claim that \tn\ is younger than $\sim$
+$500\,{\rm Myr}$.
 
@@
 
-\input{starparams.tex}
-
-We measured the physical properties of \tn\ as follows.
-
-The spectroscopic parameters were measured from each of the six CHIRON
-spectra (Section~\ref{subsec:chiron}). We then averaged the results,
-and adopted the standard deviation across the spectra as the
-uncertainty.
-
-This yielded:
-\begin{align}
-  T_{\rm eff}   &= 5946 \pm 39\,{\rm K}, \nonumber \\
-  \log g        &= 4.48 \pm 0.03, \nonumber \\
-  {\rm [Fe/H] } &= -0.065 \pm 0.035, \nonumber \\
-  v \sin i      &= 17.48 \pm 0.15\,{\rm km\,s}^{-1}.
-\end{align}
-These spectroscopic parameters were used in our final analysis of the
-system (Section~\ref{sec:system}).
-
- (Lstar, Rstar, Teff, Age and Mstar)
-
-From CHIRON spectra, my current best guess spectroscopic parameters
- are as follows.
- Teff = 5946 +/- 39
- logg = 4.48 +/- 0.03
- feh = -0.065 +/- 0.035
- vsini = 17.48 +/- 0.15
-
-% Figure~\ref{fig:sed}.
-Mention The SED fit, looking really good with rchi2 = 1.6:
-
-The fit parameters are: 
-Av = 0.20 +/- 0.03
-Fbol = 1.967 +/- 0.046 e-9 erg/s/cm2 
-Rstar = 1.049 +/- 0.019 Rsun
-
-From the spectroscopic logg and the above Rstar, we get an independent
-mass estimate of 
-Mstar = 1.21 +/- 0.10 Msun 
-At face value, the mass seems a bit high for the radius, but I'm
-guessing that just means the spectroscopic logg is a bit too high.
-
-\subsubsection{Rotation}
-Stellar vsini
-Stellar rotation
-
-\subsubsection{RVs}
-I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
-mass measurement. The reason is that with vsini=17km/s, and 2\%
-rotation amplitude signal, we expect an RV RMS of 300m/s at the
-Prot=3.5 day rotation period (vsini*rotation amplitude). This is
-probably larger than the expected planet signal (100m/s, 8 days).
+Select properties of \tn\ from the literature and our analysis are
+presented in Table~\ref{tab:starparams}.  The spectroscopic parameters
+were measured from each of the six CHIRON spectra
+(Section~\ref{subsec:chiron}). We then averaged the results, and
+adopted the standard deviation across the spectra as the uncertainty.
+
+We then calculated the stellar radius and reddening following
+\citet{stassun_accurate_2017}.  We first derived the bolometric flux
+by combining available broadband magnitudes from Gaia, Tycho-2, APASS,
+2MASS, and WISE.  We then fitted the SED with the
+\citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
+find $F_{\rm bol}$.  When fitting the atmosphere model, we varied the
+extinction ($A_{\rm V}$) and the overall normalization.  This
+procedure yielded $A_{\rm V} = 0.20\pm0.03$, which independently
+agrees with the average from the \cn\ isochrone fits of
+\citet{randich_gaiaeso_2018}.
+We then combined the spectroscopic effective temperature, bolometric
+flux, and Gaia distance to determine the stellar radius, using the
+Stefan-Boltzmann law.
 
@@
 
-\input{model_posterior_table.tex}
+To derive physical parameters of \pn\ based on the photometry, we
+fitted the TESS and ground-based transits simultaneously.
 
@@
 We'll get more TESS data in January(?).
+
+I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
+mass measurement. The reason is that with vsini=17km/s, and 2\%
+rotation amplitude signal, we expect an RV RMS of 300m/s at the
+Prot=3.5 day rotation period (vsini*rotation amplitude). This is
+probably larger than the expected planet signal (100m/s, 8 days).
 

### 2020-06-26 paper/ms.tex
update manuscript

@@
 \tn\ joins a number of other young planetary systems reported from
-TESS, including DS Tuc Ab \citep{newton_tess_2019}, HIP 67522
-\citep{rizzuto_tess_2020}, and TOI 1726 \citep{mann_tess_2020}.
-
-Rossiter measurements will confirm.
-
-After, a mass measurement should be worthwhile.
-
-We'll get more TESS data in January(?).
-
-I don't strongly expect the Veloce RVs or the FEROS ones to lead to a
-mass measurement. The reason is that with vsini=17km/s, and 2\%
-rotation amplitude signal, we expect an RV RMS of 300m/s at the
-Prot=3.5 day rotation period (vsini*rotation amplitude). This is
-probably larger than the expected planet signal (100m/s, 8 days).
+TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
+\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
+However, unlike these planets, \pn\ is validated but not yet confirmed.
+
+The easiest path towards definitively confirming
+whether \tn\ is a planet will be a Rossiter-McLaughlin (RM) measurement.  
+Detection of the RM signal
+would rule out BEB and HEB scenarios, as it would imply that the
+eclipsing object is bound to the target star. Combined with our
+non-detection of the planet's mass from radial velocity monitoring,
+this would confirm that \pn\ is a planet.
+
+The maximum amplitude of the Rossiter-McLaughlin anomaly is
+\citep{winn_exoplanet_2010}
+\begin{equation}
+  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
+  \approx 21\,{\rm m\,s}^{-1},
+\end{equation}
+where we have assumed stellar and transit parameters from
+Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
+calculation purposes we assumed $b=0.95$.  This is challenging, but
+for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
+with modern spectrographs.  The next viable total transit windows from
+Chile occur in January and February of 2021; there are also a few
+visible per season from other southern locations.
+
+The Rossiter-McLaughlin approach is more likely to yield short-term
+success than a direct mass measurement because of the RV noise
+expected to be induced by stellar rotation.  The photometric amplitude
+induced by starspots on \tn\ is $\approx 2\%$. 
+The RV noise expected over the course of the $\approx 3\,{\rm d}$
+rotation period can then be estimated by multiplying the photometric amplitude and
+spectroscopic equatorial velocity.  This gives $\sigma_{\rm RV,rot}
+\approx 300\,{\rm m\,s}^{-1}$, and is consistent with the scatter we
+observe in our radial velocities from FEROS.  Detecting
+a planet's Doppler signal in these regimes is
+challenging, and requires a significant amount of data and care in
+signal extraction \citep{barragan_radial_2019}.  The
+Rossiter-McLaughlin measurement avoids the majority of this issue
+because the transit occurs over a much shorter duration than a single
+stellar rotation period.
+
+If the RM measurements prove that the planet
+is real, a campaign to measure the mass timed to coincide with
+TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
+2021) would significantly ease the extraction of the planetary Doppler
+signal.  The reason is that the radial velocities, activity
+indicators, and photometry could then be fit simultaneously, which
+would greatly constrain any gaussian process model for the
+spot-induced RV signal.
 

### 2020-06-29 paper/ms.tex
minor
update phot plots w/ errorbar

@@
   and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
-  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602.  The star and validated
-  planet are therefore between 30 and 46 million years old.  The
-  planet is warm ($P = 8.32\,{\rm d}$) and roughly Jupiter-sized.
-  However, its transits are grazing: $b > 0.92$ at 3$\sigma$.  From
-  TESS photometry alone, the planetary size lies within 0.58--3.87
-  $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile), due to the
-  degeneracy between the planetary size and the impact parameter of
-  the transit.  From radial velocity monitoring, we limit the minimum
-  mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits
-  are cause for concern: they usually are indicative of astrophysical
-  false positive scenarios.  Our follow-up data show that such
-  scenarios are highly unlikely.  Multi-color photometry requires
-  eclipsing companions to have nearly identical color as TOI$\,$837,
-  ruling out hierarchical eclipsing binary scenarios.  Background
-  eclipsing binary scenarios are limited by speckle imaging, but
-  formally remain a 0.2\% possibility.  TOI 837.01 is therefore a
-  validated adolescent exoplanet.  Further observations of its stellar
-  obliquity, atmosphere, and mass should confirm its planetary nature
-  beyond doubt, and could improve our understanding of how the
-  physical and orbital properties of exoplanets change in time.
+  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
+  star and validated planet are therefore between 30 and 46 million
+  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
+  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
+  3$\sigma$.  From TESS photometry alone, the planetary size lies
+  within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
+  percentile), due to the degeneracy between the planetary size and
+  the impact parameter of the transit.  From radial velocity
+  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
+  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
+  usually are indicative of astrophysical false positive scenarios.
+  Our follow-up data show that such scenarios are highly unlikely.
+  Multi-color photometry requires eclipsing companions to have nearly
+  identical color as TOI$\,$837, ruling out hierarchical eclipsing
+  binary scenarios.  Background eclipsing binary scenarios are limited
+  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
+  837.01 is therefore a validated adolescent exoplanet.  Further
+  observations of its stellar obliquity, atmosphere, and mass should
+  confirm its planetary nature beyond doubt, and could improve our
+  understanding of how the physical and orbital properties of
+  exoplanets change in time.
 \end{abstract}
@@
     Section~\ref{subsec:tess}).  Black points are binned to 6-minute
-    intervals.  The gray line shows the median transit model corresponding to the
-    fitted to both the TESS and ground-based transits
-    (Table~2).  {\it Bottom:} Multicolor
-    photometry from the El Sauce 0.36m; gray points are binned to 10-minute intervals.  Models
-    show lower limits on the transit depths in 
-    the Cousins-R and Johnson-B bandpasses used to rule out specific false positive scenarios.
+    intervals, and the errorbar shows the median uncertainty for the
+    black points.  The gray line shows the median model corresponding
+    to the combined TESS and ground-based transit fit.
+    (Table~2).  {\it Bottom:} Multicolor photometry from the El Sauce
+    0.36m; gray points are binned to 10-minute intervals.  Models show
+    lower limits on the transit depths in the Cousins-R and Johnson-B
+    bandpasses used to rule out specific false positive scenarios.
     \label{fig:jointphot}

### 2020-06-29 drivers/fit_alltransit.py

@@ -35,10 +35,10 @@ def main(modelid):
     make_threadsafe = 0
     cut_tess = 1
 
-    phaseplot = 0
-    grounddepth = 0
+    phaseplot = 1
+    grounddepth = 1
     fittedzoom = 0
-    cornerplot = 1
+    cornerplot = 0
 
     OVERWRITE = 1
     REALID = 'TOI_837'
@@ -140,5 +140,5 @@ def main(modelid):
 if __name__ == "__main__":
 
     # main('alltransit')
-    # main('alltransit_quad')
-    main('alltransit_quaddepthvar')
+    main('alltransit_quad')
+    # main('alltransit_quaddepthvar')

### 2020-06-29 timmy/plotting.py

@@ -72,6 +72,7 @@ from matplotlib.ticker import MaxNLocator, NullLocator
 from matplotlib.colors import LinearSegmentedColormap, colorConverter
 from matplotlib.ticker import ScalarFormatter
 import matplotlib.ticker as ticker
+import matplotlib.transforms as transforms
 
 
 ##################################################
@@ -717,7 +718,7 @@ def plot_raw_zoom(outdir, yval='PDCSAP_FLUX', provenance='spoc',
 
 
 def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
-                   modelid=None, inppt=0):
+                   modelid=None, inppt=0, showerror=1):
 
     if modelid is None:
         d, params, paramd = _get_fitted_data_dict(m, summdf)
@@ -731,17 +732,18 @@ def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
     t0_orb = summdf.loc['t0', 'median']
 
     # phase and bin them.
+    binsize = 5e-4
     orb_d = phase_magseries(
         _d['x_obs'], _d['y_obs'], P_orb, t0_orb, wrap=True, sort=True
     )
     orb_bd = phase_bin_magseries(
-        orb_d['phase'], orb_d['mags'], binsize=5e-4, minbinelems=3
+        orb_d['phase'], orb_d['mags'], binsize=binsize, minbinelems=3
     )
     mod_d = phase_magseries(
         _d['x_obs'], _d['y_mod'], P_orb, t0_orb, wrap=True, sort=True
     )
     resid_bd = phase_bin_magseries(
-        mod_d['phase'], orb_d['mags'] - mod_d['mags'], binsize=5e-4,
+        mod_d['phase'], orb_d['mags'] - mod_d['mags'], binsize=binsize,
         minbinelems=3
     )
 
@@ -882,6 +884,33 @@ def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
             a.set_xticks(xval)
         yval = np.arange(-5,5,2.5)
         a0.set_yticks(yval)
+
+    if showerror:
+        trans = transforms.blended_transform_factory(
+                a0.transAxes, a0.transData)
+        if inppt:
+            _e = 1e3*np.median(_d['y_err'])
+            # a0.errorbar(
+            #     0.9, -5, yerr=_e, fmt='none',
+            #     ecolor='darkgray', alpha=0.8, elinewidth=1, capsize=2,
+            #     transform=trans
[…]

### 2020-06-29 paper/ms.tex
update manuscript

@@
     black points.  The gray line shows the median model corresponding
-    to the combined TESS and ground-based transit fit.
-    (Table~2).  {\it Bottom:} Multicolor photometry from the El Sauce
+    to the combined TESS and ground-based transit fit
+    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
     0.36m; gray points are binned to 10-minute intervals.  Models show
-    lower limits on the transit depths in the Cousins-R and Johnson-B
-    bandpasses used to rule out specific false positive scenarios.
+    $2\sigma$ lower limits on the transit depths in the Cousins-R and
+    Johnson-B bandpasses used to rule out specific false positive
+    scenarios (see Section~\ref{subsec:colorphot}).
     \label{fig:jointphot}
@@
 \subsubsection{Multicolor Photometry}
+\label{subsec:colorphot}
 % TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
@@
 
+%FIXME FIXME
 For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,

### 2020-06-29 paper/ms.tex
update manuscript

@@
     Section~\ref{subsec:tess}).  Black points are binned to 6-minute
-    intervals, and the errorbar shows the median uncertainty for the
+    intervals, and the error-bar shows the median uncertainty for the
     black points.  The gray line shows the median model corresponding
@@
 dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
-Star B is resolved in the ground-based images, while Star A is not.
-
-To assess this possibility with the ground-based photometry, we
+Star B is resolved in the ground-based images; Star A is not.
+
+To rule out blend scenarios with the ground-based photometry, we
 produced light curves centered on \tn\ with
@@
 of the transits with aperture size.
-Two lines evidence rule out Star B as the eclipsing source:
+Two lines of evidence rule out Star B as the eclipsing source:
 first, the transits
@@
 
-To assess the possibility of Star A as the eclipsing body,
+To assess the possibility that Star A is the eclipsing body,
 we created light curves with a custom set of circular apertures
@@
 along this line of light curves, as would be expected if Star A were
-the eclipse host.  The apertures east of \tn\ are particularly
-constraining, as they exclude over 90\% of the flux from Star A.
+the eclipse host.  The apertures east of \tn\ exclude over 90\% of the flux from Star A.
 The eclipse on Star A would therefore need to be excessively deep to
@@
 
-Validating a transiting planet means statistically arguing that
-the data are much more likely to be caused by a planet than by other
-astrophysical false positives. The concept of validation has been
+Validating a transiting planet means statistically arguing that the
+data are much more likely to be explained by a planet than by an
+astrophysical false positive. The concept of validation has been
 developed and calibrated by {\it e.g.},
@@
 from ``confirmation'', which means that there is overwhelming evidence
-that the data must be explained by a planet, for instance through
-combined photometric transits and a radial velocity mass measurement.
-
-Assuming the eclipse is localized to the target star, potential false positive scenarios
-include eclipses of a background binary (BEB), eclipses of a
-hierarchical system bound to the primary star (HEB), and the possibility
-that the eclipses are simply caused by a stellar companion,
-rather than a planetary one (EB).
+that the data {\it must} be explained by a planet, for instance
+through combined photometric transits and a radial velocity mass
+measurement.
+
+Assuming an eclipse has been localized to the target star, potential
+false positive scenarios include eclipses of a background binary
+(BEB), eclipses of a hierarchical system bound to the primary star
+(HEB), and the possibility that the eclipses are simply caused by a
+stellar companion, rather than a planetary one (EB).
 
@@
 them out based on our combined photometry, velocimetry, and imaging.
-We proceed by describing each constraint in detail, and then present a
-statistical calculation using \texttt{VESPA}
-\citep{morton_efficient_2012} to demonstrate that the probability \tn\
-is an astrophysical false positive is small enough to consider it
-validated.
+In this Section we describe each constraint in turn, and then present a
+calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
+demonstrate that the probability \tn\ is an astrophysical false
+positive is small enough to formally validate it as a planet.
 
@@
 In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
-binary host would blend together, reducing the ``true'' eclipse depth
-$\delta_{\rm true}$ to produce the observed depth
+binary host blend together, and reduce the ``true'' eclipse depth
+$\delta_{\rm true}$ to the observed depth
 $\delta_{\rm obs}$:
@@
   = 
-  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
+  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
 \end{equation}
-where the total flux and the flux from the neighbor are labelled as
-such.  The requirement that the eclipse is produced by stars and that
-$\delta_{\rm true} < 0.5$ translates to a bound on the faintest
-possible blended companion stars:
+where the total system flux and the flux from only the companion
+(``comp'') binary are labeled appropriately.  The requirement that the
+eclipse is produced by stars and that $\delta_{\rm true} < 0.5$
+translates to a bound on the faintest possible blended companion
+system:
 \begin{equation}
-  \Delta m < -\frac{5}{2} \log_{10} \left( \frac{0.5}{\delta_{\rm obs}} \right).
+  \Delta m < -\frac{5}{2} \log_{10}
+             \left( \frac{0.5}{\delta_{\rm obs}} \right).
 \end{equation}
@@
 
-For box-shaped transits, this argument can be
-extended to even more restrictive depths \citep[{\it
+If the transit were box-shaped, this argument could be extended to
+even more restrictive depths \citep[{\it
 e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
@@
 convert the remaining contrast constraints to limits on the masses of
-possible bound companions, we used the
-\citet{baraffe_evolutionary_2003} models for sub-stellar mass objects
-and the MIST isochrones for stellar mass objects
+bound companions, we used the \citet{baraffe_evolutionary_2003} models
+for sub-stellar mass objects and the MIST models for stellar mass
+objects
 \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
-We assumed that the system age was 35 Myr, to ensure that companions
-would be at a plausible state of contraction.
+We assumed that the system age was 35 Myr, so that companions would be
+at a plausible state of contraction.
 
@@
 luminosities to expected magnitudes in instrumental bandpasses, we
-assumed that all soruces had blackbody spectra.  While this is
-a simplification, the custom instrumental bandpasses prevented a fully
-consistent stellar evolutionary calculation.  Using the theoretical
-stellar parameters and the measured transmission functions
-\citep{tokovinin_ten_2018}, we then calculated the apparent magnitudes
-of stellar companions of different masses, and interpolated
+made the simplying assumption that all sources had blackbody spectra.
+Using the theoretical stellar parameters and the measured transmission
+functions \citep{tokovinin_ten_2018}, we then calculated the apparent
+magnitudes of stellar companions of different masses, and interpolated
 to produce the scale shown on the upper-right in
@@
 the CHIRON spectra to determine whether \tn\ is double-lined.  For a
-stellar companion well-separated in velocity, this typically shows
+stellar companion well-separated in velocity, this typically reveals
 companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
@@
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits for the companion, and then performed two sets of fits.
+orbits for the companion, and performed two sets of fits.
 
@@
 time of periapse, using the known ephemeris from the transit.  We then
-fitted for the period, time of periapse, semi-amplitude, instrument
-offsets, and jitter parameters.  This yielded a non-detection of the
-planet's orbit.  The corresponding 3-$\sigma$ (99.7$^{\rm th}$
-percentile) upper limit on $M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.
-The data and corresponding model are shown in Figure~\ref{fig:rvs}.
-
-The above exercise rules out the possibility that the observed
-eclipses are caused by a star orbiting \tn.  The lack of a linear
-trend in the radial velocities, particularly in the FEROS data, can be
-used to further limit the presence of a hierarchical binary system.
-To constrain this second possibility, we placed a wide log-uniform
-prior on the semi-amplitude and period ($\log K\ [{\rm m\,s^{-1}}]
-\sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
-10^{15})$).  We then fitted again for the semi-amplitude, period, time
-of conjunction, instrument offsets, and jitter parameters.  We
-converted the resulting posterior in period and semi-amplitude to
-minimum mass and semi-major axis assuming Kepler's third law.  The
-resulting $3\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
+fitted for the semi-amplitude, instrument offsets, and jitter
+parameters.  This yielded a non-detection of the planet's orbit.  The
+corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
+$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
+model are shown in Figure~\ref{fig:rvs}.
+
+The above exercise ruled out the possibility that the observed
+eclipses are caused by a stellar-mass object orbiting \tn.  The lack
+of a linear trend in the radial velocities, particularly in the FEROS
+data, further constrains the presence of a hierarchical binary system.
+To derive limits for this second possibility, we placed a wide
+log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
+m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
+\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
+period, time of conjunction, instrument offsets, and jitter
+parameters.  We converted the resulting posterior in period and
+semi-amplitude to minimum mass and semi-major axis assuming Kepler's
+third law.  The resulting $3\sigma$ limits are shown in
+Figure~\ref{fig:fpscenario}.
 
@@
 \label{subsec:colorphot}
-% TODO: this section is ridiculously long. Abbreviate to 2 paragraphs, 3
-% at most.
-
-HEB and to a lesser extent BEB scenarios can be limited
-by color photometry.
-In the absense of color photometry, the most plausible HEB scenarios for TOI
-837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
-These eclipses are redder than eclipses of the G0V \tn.
-Observations that the transit depth does not decrease
-going to blue bands can therefore rule out these scenarios.
-
-\paragraph{Simple Example}
-% SEE June 1, 2020 email in "Re: TOI-837.01" thread
-As a simple example, assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
-Assume PMS evolution, and
-use MIST isochrones for a 35 Myr system to convert between stellar properties. 
-Take transmission functions (filters only; no instrument or atmosphere
-response) from the SVO filter profile service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.
-Integrate up blackbody functions over each bandpass for each star, and
-get estimates of the eclipse depths if there were a total eclipse (of
-either of the secondary or tertiary) with this set of parameters.  The
-apparent eclipse depths in various Bessel and Cousins bandpasses are:
-\begin{align}
-%FIXME: check these numbers
-  \delta_{\rm U_B} &= 5.03\times10^{-4} \ ({\rm Bessel\ U})\nonumber \\
-  \delta_{\rm B_B} &= 1.39\times10^{-3}\ ({\rm Bessel\ B})\nonumber \\
-  \delta_{\rm V_B} &= 3.31\times10^{-3}\ ({\rm Bessel\ V})\nonumber \\
-  \delta_{\rm R_C} &= 5.59\times10^{-3}\ ({\rm Cousins\ R})\nonumber \\
-  \delta_{\rm I_C} &= 9.69\times10^{-3}\ ({\rm Cousins\ I})\nonumber \\
-  \delta_{\rm T}   &= 9.18\times10^{-3}\ ({\rm TESS})
-\end{align}
-
-Our chief interest is the relative depths, because geometry lets all the
-depths be scaled to match the observed TESS depth of $\approx$43 ppt.
-(In this case, all depths would be scaled down by a multiplicative factor of
-2.1).
-
-The crucial point is that the bluest bands--- U and B---are roughly 10
-times shallower than TESS-band, because the M dwarf blackbody function
-turns over at 2 times longer wavelengths than the G dwarf blackbody
-(Wien's law).
-
-Therefore if TOI 837 were a hierarchical eclipsing M dwarf pair,
-Phil's two R-band observations should have shown eclipses a factor of
-1.64x shallower than TESS observed (so, 24ppt, instead of the ~40ppt
-observed). So, the 40 (+/- 10ish) ppt R-band depths seen in Phil's
-transits vs TESS-band argue for a planet, but the level of confidence
-could probably be improved with U or B.
-
-\paragraph{Limits on Masses of Bound Companions}
-
-With this intuition in place, we derived the limits on masses of bound
-hierarchical eclipsing companions as follows.  We assumed that each
-system was composed of the primary (\tn), plus a tertiary companion
-eclipsing a secondary companion every 8.3 days.
-
-For secondary masses ranging from 0.07 to 1.10 $M_\odot$, and
-mass ratios ($M_3/M_2$) from 0.1 to 1, we then 
-calculated the observed maximal eclipse depth of Star 3 in front of
-Star 2 in a number of bandpasses.
-As before, we interpolated between mass, effective temperature, and radius
-assuming the MIST isochrones for a 35$\,$Myr old system,
-and also assumed that each source had a blackbody spectrum.
-
-We excluded systems for which the maximal eclipse depth in TESS-band
-was less than the observed depth ({\it i.e.}, systems for which the tertiary
-was too small).
-For the systems with maximal eclipse depths in TESS-band greater than
-the observed TESS-band depth, we then calculated the multiplicative
-factor required to shrink the depth (from the $b=0$ case) to match the
-observed eclipse depth in the TESS-band.
-We then scaled the depths in each of the other bandpasses by this
-fixed geometric factor.
-
-We then asked: given a fixed secondary mass, are there any tertiary
-companions for which the expected $\delta_{\rm R_C}$ is larger than
-the observed Rc-band depth?
-In cases for which the answer was yes, we could not rule out such
-hierarchical eclipsing binary systems.
-Conversely, we were able to rule out systems
-for which at fixed secondary mass no tertiary mass would
-enable eclipses (in ${\rm R_C}$-band) of the necessary depth.
-
-%FIXME FIXME
-For a lower limit on $\delta_{\rm R_C}$ of 30$\,$ppt,
-we found that the transition between systems that would produce
-eclipses that no matter what were ``too red'', and systems that would
-produce eclipses that could be sufficiently blue happens in \tn\ (for
-${\rm R_C}$-band) at 0.38$M_\odot$.
-The corresponding limit is shown in Figure~\ref{fig:fpscenario}.
-For a $\delta_{\rm B_J}$ limit of 30$\,$ppt, the corresponding mass
-limit is 0.82$M_\odot$.
-
-\paragraph{Limits on Masses of Projected Companions}
-
-Ignoring the effects of interstellar reddening,
-the constraint that $M_2 \gtrsim 0.54 M_\odot$ based on
-colors applies to background eclipsing binaries as well.
-However, the blue eclipses produced by such systems ({\it e.g.}, a background G2V+K6V binary)
-can be kept while making the systems fainter by moving them to greater
-distances.
-The only way to definitively rule out such scenarios is to 
-prove that the loss of light is from the target star,
-for instance by detecting the Rossiter-McLaughlin effect
-during a transit.
-
-Such scenarios are somewhat contrived in that since 
-no secondary eclipse is observed, they require either
-eccentric orbits to avoid secondary eclipses, or else a
-background twin binary system at double
-the orbital period.
+
+\paragraph{Multicolor photometry and HEB scenarios}
+The most plausible HEB scenarios for \tn\ involve pairs of eclipsing M
+dwarfs (Figure~\ref{fig:fpscenario}).  Eclipses of such stars are much
+redder than eclipses of the G-dwarf \tn.  Limits on whether the
+transit depth decreases in bluer bandpasses can therefore rule out
+some HEB scenarios.
+
+We fitted for the observed depths in different bandpasses using a
+similar machinery as described in Section~\ref{subsec:planet}.  We fitted
+each ground-based transit individually for the planet-to-star size
+ratio, the impact parameter, and a local quadratic trend (the
+ephemeris was assumed from an initial fit of only the TESS data).  The
+corresponding $2$-$\sigma$ limits on the transit depths in Cousins-R
+and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
+respectively, and are shown in
+Figure~\ref{fig:jointphot}.  Particularly in our Johnson-B light
+curve, the transit depth is correlated with the mean and linear slope
+of the light curve: a smaller depth is allowed if the data are fitted
+with a larger linear slope and a larger mean.  Our quoted limits
+marginalize over these correlations, and the depth measurement itself
+is nearly Gaussian.
+
+To determine what classes of HEB are eliminated by these limits, we
+performed the following calculation.  We assumed that each system was
+composed of the primary (\tn), plus a tertiary companion eclipsing a
+secondary companion every 8.3 days.  For secondary masses ranging from
+0.07 to 1.10 $M_\odot$, and mass ratios ($M_3/M_2$) from 0.1 to 1, we
+then calculated the observed maximal eclipse depth caused by Star 3
+eclipsing Star 2 in each observed bandpass.  As before, we
+interpolated between mass, effective temperature, and radius assuming
+the MIST isochrones for a 35$\,$Myr old system, and also assumed that
+each source had a blackbody spectrum.  We used the transmission
+functions from the SVO filter profile
+service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.  For
+a typical HEB system ({\it e.g.}, $M_2=M_3=0.2M_\odot$), the bluest
+optical bandpasses produced eclipses roughly 10 times shallower than
+in TESS-band, because the M-dwarf blackbody function turns over at
+much redder wavelengths than the G-dwarf blackbody (Wien's law).
+
+For a fixed secondary mass, we then asked whether any tertiary
+companions existed for which the maximal expected eclipse depth could have
+been larger than the observed depth.  In cases for which the answer
+was yes, we could not rule out such hierarchical eclipsing binary
+systems.  Conversely, we were ruled out systems for which at fixed
+secondary mass no tertiary mass could enable eclipses of the necessary
+depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).
+The ${\rm R_C}$-band limit corresponded to a secondary mass limit of 
+$M_2 > 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a
+stronger limit of $M_2 > 0.70 M_\odot$.
+
+\paragraph{Multicolor photometry and BEB scenarios}
+
+While the above constraints rule out HEBs, certain configurations of BEB systems 
+({\it e.g.}, a background G2V+K6V binary)
+can produce blue eclipses while remaining undetected along the line of
+sight.  Such scenarios are constrained by the lack of an observed
+secondary eclipse, and therefore require either eccentric orbits to
+avoid secondary eclipses, or else a background twin binary system at
+double the orbital period.  The only way to definitively rule out such
+scenarios is to prove that the loss of light is from the target star,
+for instance by detecting the Rossiter-McLaughlin effect during a
+transit.
 
@@
 
-To derive physical parameters of \pn\ based on the photometry, we
+We derived physical parameters of \pn\ based on the photometry, we
 fitted the TESS and ground-based transits simultaneously.
+We trimmed the data to
 
@@
 don't do it.}
+
+\subsubsection{multicolor transit fits}
+Single transit at a time, with limited
 

### 2020-07-01 paper/ms.tex
update manuscript

@@
     sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Spot-induced stellar variability is the dominant signal.  Dashed
-    lines show the five transits observed by TESS.  {\it Bottom}:
-    Zoomed windows of individual transits.  Red points are manually
-    identified stellar flares.
+    Spot-induced stellar variability is the dominant signal; flares are
+    shown with gray crosses.  Dashed
+    lines indicate the five transits observed by TESS.  {\it Bottom}:
+    Zoomed windows of individual transits.
+    Gray lines are the best-fit transit model, which includes a local
+    quadratic trend in each transit window.
 		\label{fig:rawzoom}

### 2020-07-01 paper/collect.sh

@@ -3,11 +3,12 @@
 rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
-cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
+# cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_fitindiv.pdf f1.pdf
 
-cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
+# cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
 
-cp ${rdir}TOI_837_alltransit_quad_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
+# cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
 
 cp ${pdir}scene.pdf f5.pdf
 

### 2020-07-01 paper/collect.sh
update manuscript

@@ -3,10 +3,9 @@
 rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
-# cp ${pdir}raw_zoom_spoc_PDCSAP_FLUX.pdf f1.pdf
 cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_fitindiv.pdf f1.pdf
 
-# cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
 
 # cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
 

### 2020-07-01 drivers/fit_allindivtransit.py
minor driver tweaks

@@ -25,10 +25,12 @@ def main(modelid):
     make_threadsafe = 0
     cut_tess = 1
 
-    phaseplot = 0
+    phaseplot = 1
     grounddepth = 1
-    fitindiv = 0
-    cornerplot = 0
+    fitindiv = 1
+    cornerplot = 1
+
+    N_samples = 2000
 
     OVERWRITE = 1
     REALID = 'TOI_837'
@@ -89,7 +91,7 @@ def main(modelid):
     prior_d = initialize_prior_d(mp.modelcomponents, datasets=datasets)
 
     m = ModelFitter(modelid, datasets, prior_d, plotdir=PLOTDIR,
-                    pklpath=pklpath, overwrite=OVERWRITE)
+                    pklpath=pklpath, overwrite=OVERWRITE, N_samples=N_samples)
 
     print(pm.summary(m.trace, var_names=list(prior_d.keys())))
     summdf = pm.summary(m.trace, var_names=list(prior_d.keys()), round_to=10,

### 2020-07-01 drivers/plot_rvs.py

@@ -192,7 +192,7 @@ class MultipanelPlot(object):
                  yscale_sigma=3.0, phase_nrows=None, phase_ncols=None,
                  uparams=None, telfmts={}, legend=True, phase_limits=[],
                  nobin=False, phasetext_size='medium', rv_phase_space=0.08,
-                 figwidth=4.2, fit_linewidth=1.0, set_xlim=None, text_size=9,
+                 figwidth=4.2, fit_linewidth=1.0, set_xlim=None, text_size=11,
                  highlight_last=False, show_rms=False,
                  legend_kwargs=dict(loc='best')):
 
@@ -292,7 +292,7 @@ class MultipanelPlot(object):
         # list for Axes objects
         self.ax_list = []
 
-    def plot_timeseries(self):
+    def plot_timeseries(self, ylim=(-510, 510)):
         """
         Make a plot of the RV data and model in the current Axes.
         """
@@ -344,14 +344,17 @@ class MultipanelPlot(object):
         axyrs.set_xlabel('Year')
         plt.locator_params(axis='x', nbins=5)
 
-        if not self.yscale_auto:
-            scale = np.std(self.rawresid+self.rvmod)
-            ax.set_ylim(-self.yscale_sigma * scale, self.yscale_sigma * scale)
+        # if not self.yscale_auto:
+        #     scale = np.std(self.rawresid+self.rvmod)
+        #     ax.set_ylim(-self.yscale_sigma * scale, self.yscale_sigma * scale)
+
+        if isinstance(ylim, tuple):
+            ax.set_ylim(ylim)
 
         ax.set_ylabel('RV [{ms:}]'.format(**plot.latex))
         ax.set_xlabel('Time [JD - {:d}]'.format(int(np.round(self.epoch))))
-        ticks = ax.yaxis.get_majorticklocs()
-        ax.yaxis.set_ticks(ticks[1:])
+        # ticks = ax.yaxis.get_majorticklocs()
+        # ax.yaxis.set_ticks(ticks[1:])
 
         ax.get_yaxis().set_tick_params(which='both', direction='in')
         ax.get_xaxis().set_tick_params(which='both', direction='in')
@@ -536,10 +539,15 @@ class MultipanelPlot(object):
         #anotext = '\n'.join(anotext)
         anotext = anotext[1] # just the semi-amplitude
[…]

### 2020-07-01 paper/ms.tex
update manuscript

@@
     Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
-    measurements, detrended with a 0.3-day robust Huber spline (see
-    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
-    intervals, and the error-bar shows the median uncertainty for the
-    black points.  The gray line shows the median model corresponding
-    to the combined TESS and ground-based transit fit
-    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry from the El Sauce
-    0.36m; gray points are binned to 10-minute intervals.  Models show
-    $2\sigma$ lower limits on the transit depths in the Cousins-R and
-    Johnson-B bandpasses used to rule out specific false positive
-    scenarios (see Section~\ref{subsec:colorphot}).
+    measurements with the local spot-induced variation removed as
+    described in Section~\ref{subsec:planet}.  Black points are binned
+    to 6-minute intervals, and the error-bar shows the median
+    uncertainty for the black points.  The gray line shows the median
+    model corresponding to the combined TESS and ground-based transit
+    fit (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor
+    photometry from the El Sauce 0.36m; gray points are binned to
+    10-minute intervals.  Models show $2\sigma$ lower limits on the
+    transit depths in the Cousins-R and Johnson-B bandpasses used to
+    rule out specific false positive scenarios (see
+    Section~\ref{subsec:colorphot}).
     \label{fig:jointphot}
@@
 
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f6.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ 
-    {\bf SOAR HRCam contrast limits derived from point-source
-    injection-recovery experiments.} Star A ($\Delta T=4.7$,
-    $2.3''$ west) is detected in the autocorrelation function, in
-    addition to being a resolved Gaia source.  It is co-moving with
-    \tn, and its parallax and on-sky position imply that it is
-    physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
-		\label{fig:soar}
-	}
-\end{figure}
-
 To determine if any fainter point sources existed closer to \tn\
@@
 \citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
-by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:soar}
+by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
 show the resulting measured 5-$\sigma$ detectable contrasts.  The
@@
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f3.pdf}
+		\subfloat{
+			\includegraphics[width=0.47\textwidth]{f6.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.47\textwidth]{f3.pdf}
+		}
 	\end{center}
-	\vspace{-0.7cm}
+	\vspace{-0.6cm}
 	\caption{
-		{\bf Radial velocities of \tn.}
-		{\it Top:} RV measurements, with best-fit instrument offsets
+		{\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
+		SOAR HRCam contrast limits derived from point-source
+		injection-recovery experiments. A companion dubbed Star A ($\Delta T=4.7$,
+	$2.3''$ west) is detected in the autocorrelation function,
+	and is also a resolved Gaia source.  It is co-moving with
+	\tn, and its parallax and on-sky position imply that it is
+	physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
+		{\it Middle:} RV measurements, with best-fit instrument offsets
 	and jitter terms included.  The expected scatter from starspots
@@
 	Keplerian orbit representing the $3\sigma$ upper mass limit.
-		\label{fig:rvs}
+		\label{fig:followup}
 	}
@@
 spectra against the same synthetic template.  The resulting velocities
-are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:rvs}.
+are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.
 
@@
 velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:rvs}.
+Figure~\ref{fig:followup}.
 
@@
 The velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:rvs}.
+Figure~\ref{fig:followup}.
 
@@
 $M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
-model are shown in Figure~\ref{fig:rvs}.
+model are shown in Figure~\ref{fig:followup}.
 

### 2020-07-01 paper/collect.sh

@@ -7,7 +7,7 @@ cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_fitindiv.pdf f
 
 cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
 
-# cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
 
 cp ${pdir}scene.pdf f5.pdf
 

### 2020-07-02 paper/ms.tex
update manuscript

@@
 % text. G0V has been assumed.
+% * remove all bf todo's
 %
@@
 		\leavevmode
-		\includegraphics[width=1\textwidth]{f1.pdf}
+		\includegraphics[width=.9\textwidth]{f1.pdf}
 	\end{center}
@@
     Gray lines are the best-fit transit model, which includes a local
-    quadratic trend in each transit window.
+    quadratic trend in each window.
 		\label{fig:rawzoom}
@@
 community was alerted on 17 June 2019.  While our CDIPS FFI light
-curves also show the transits, the 2-minute data have better sampling
+curves also showed the transits, the 2-minute data had better sampling
 cadence, and so we opted to use the Presearch Data Conditioning (PDC)
@@
 phase-folded view of the TESS transits with starspot variability
-removed is shown in Figure~\ref{fig:jointphot}, and is described in
-depth in Section~\ref{subsec:planet}.
+removed is shown in Figure~\ref{fig:jointphot}. Our fitting procedure
+for the models shown in these plots is described in
+Section~\ref{subsec:planet}.
 
@@
 
-%FIXME: this paragraph doesn't really belong here?
-We examined the CDIPS FFI light curves of the target, which are
-available on MAST \citep{bouma_cluster_2019}. Three light curves are
-available, based on photometric apertures with a radius of 1, 1.5, or
-2.5 pixels.  In the raw difference-image light-curves, as well as the
-PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
-and their properties do not significantly vary with aperture size.
-Within $\approx20$'', the dips are consistent with originating from
-the target star.
+% %FIXME: this paragraph doesn't really belong here?
+% We examined the CDIPS FFI light curves of the target, which are
+% available on MAST \citep{bouma_cluster_2019}. Three light curves are
+% available, based on photometric apertures with a radius of 1, 1.5, or
+% 2.5 pixels.  In the raw difference-image light-curves, as well as the
+% PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
+% and their properties do not significantly vary with aperture size.
+% Within $\approx20$'', the dips are consistent with originating from
+% the target star.
 
@@
 
-{\bf Carl TODO: please describe and correct as appropriate}
+\edit1{Carl TODO: please describe and correct as appropriate}
 The observations of \tn\ were initially acquired by
@@
 
-{\bf Phil + Karen TODO: please correct as appropriate}
+\edit1{Phil + Karen TODO: please correct as appropriate}
 We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
@@
 were possible sources of blended eclipsing binary signals.
-For instance, a 30\% eclipse of Star A could produce
-dips with the correct depth ($\approx$0.4\%) to explain the \tn\ signal.
 Star B is resolved in the ground-based images; Star A is not.
@@
 
-To assess the possibility that Star A is the eclipsing body,
+To assess the possibility that Star A is an eclipsing body,
 we created light curves with a custom set of circular apertures
@@
 
-{\bf Amaury TODO: please correct as appropriate}
+\edit1{Amaury TODO: please correct as appropriate}
 We observed {\bf N} transits with the 0.40m ASTEP 400 telescope at
@@
 
-{\bf George TODO: please describe the formal secondary line search in
+\edit1{George TODO: please describe the formal secondary line search in
 more depth in this paragraph} We searched for secondary lines in the
@@
 We used the dedicated instrument pipeline to extract 1-dimensional,
-wavelength calibrated spectra.  To measure radial velocities, {\bf
+wavelength calibrated spectra.  To measure radial velocities, \edit1{
 Rafael TODO: what procedure was used?  What software packages?}.  The
@@
 Figure~\ref{fig:fpscenario}, our nominal false positive probability
-analysis excluded EB and HEB scenarios.  This yielded a FPP of 0.21\%
+analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
 for \pn, sufficient for formal validation as a planet
@@
 
-We derived physical parameters of \pn\ based on the photometry, we
-fitted the TESS and ground-based transits simultaneously.
-We trimmed the data to
-
-\subsubsection{Transit Fitting}
-Simultaneous dip plus rotation period (GP) fit. Use celerite plus PyMC3/exoplanet.
-Mention FPP?
-
-%TODO: describe 0.3-day robust Huber spline (or whatever detrending is
-%eventually used)
-
-\subsubsection{Comments on Joint Transit and Radial Velocity Fitting}
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.48\textwidth]{f10.png}
+	\end{center}
+	\vspace{-0.5cm}
+	\caption{ 
+		{\bf Posterior probabilities of
+			impact parameter, planet-to-star size ratio, and stellar density.} The photometric
+		data fitted in Section~\ref{subsec:planet} allow for
+		nonphysical planet sizes ($R_{\rm p}>2R_{\rm Jup}$;
+		$\log(R_{\rm p}/R_\star) \gtrsim -1.6$) due to a classic degeneracy
+		between the planet size and impact parameter.  Non-planetary sizes
+		would however imply non-planetary masses, which are ruled out by our
+		radial velocity measurements.
+		This plot was made using \texttt{corner} \citep{corner_2016}.
+		\label{fig:subsetcorner}
+	}
+\end{figure}
+
+We fitted the available time-series photometry of \pn\ as follows.
+For the PDCSAP light curve, we first eliminated points that had
+quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
+This excluded cadences affected by coarse spacecraft pointing,
+reaction wheel desaturation events, manual flags, cosmic ray hits, and
+straylight from the Earth or Moon being present.  Inspecting the data,
+we also manually excluded the two flares shown in
+Figure~\ref{fig:rawzoom}.  We then trimmed the TESS data to windows of
+$\pm 7\,{\rm hr}$ centered on each transit.
+
+Our joint model for the TESS and ground-based data was a
+\citet{exoplanet:agol19} transit with physical and orbital parameters
+shared across all transit windows, plus a local quadratic trend
+allowed within each window.  The parameters and priors
+are listed in Table~\ref{tab:posterior}.  In brief, we fitted for the
+shared stellar parameters ($\log g, R_\star, u_0, u_1$), and the
+shared planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).
+There were also three free trend parameters for each of the nine
+transits to account for the rotational variability.  This yielded a
+total of 35 free parameters, of which 8 have physical relevance, and
+27 are nuisance parameters.
+
+We fitted the model using \texttt{PyMC3}
+\citep{salvatier_2016_PyMC3,exoplanet:theano}. 
+For the exoplanet transit, we used the \texttt{exoplanet} code
+\citep{exoplanet:exoplanet}.  
+After initializing each model with the parameters of the
+maximum {\it a posteriori} model, we assumed a Gaussian
+likelihood, and sampled using \texttt{PyMC3}'s gradient-based
+No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$
+as our convergence diagnostic \citep{gelman_inference_1992}.
+
+While alternative approaches are available for simultaneously fitting
+space and ground based photometry (in addition to radial velocimetry),
+we opted for this approach because {\it i)} the radial velocitmetry on
+its own did not show evidence for a planetary signal, and {\it ii)} we
+expected that this approach would provide the best measurement of the
+planetary ephemeris, which is key for follow-up efforts.  The
+assumption of a constant radius across all bandpasses was tested by
+independently fitting each ground-based transit while letting the
+planetary radius float (Section~\ref{subsec:colorphot}). The transit
+depths did not significantly change between different bandpasses.
+
+The posteriors from this procedure are given in
+Table~\ref{tab:posterior}.  Crucially important is the point that the
+transit is grazing.  The grazing geometry hinders our ability to infer
+the stellar density and planet-to-star size ratio. The relevant
+posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
 
@@
 slightly below unity.  The planet's size, in our eyes, would remain
-poorly constrained even if we were to do this exercise. {\bf So we
-don't do it.}
-
-\subsubsection{multicolor transit fits}
-Single transit at a time, with limited
-
-\subsubsection{Additional Transits}
-None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
-spikes at BTJD 1572 and 1601) seem likely to be planetary
-We checked that i) they were not present in the SAPFLUX light-curves,
-and ii) that they were not present in the CDIPS light-curves (either
-raw, or PCA-detrended).
-
-To make this quantitative, we did injection-recovery.
+poorly constrained even if we were to do this exercise, so we opt to 
+fit the photometry and radial velocities separately, to ensure clarity
+about which datasets are providing which constraints.
+
+% TODO: decide whether to include this. it's not necessary!
+% \subsubsection{Additional Transits}
+% None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
+% spikes at BTJD 1572 and 1601) seem likely to be planetary
+% We checked that i) they were not present in the SAPFLUX light-curves,
+% and ii) that they were not present in the CDIPS light-curves (either
+% raw, or PCA-detrended).
+% To make this quantitative, we did injection-recovery(?)
 
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
-However, unlike these planets, \pn\ is validated but not yet confirmed.
-
-The easiest path towards definitively confirming
-whether \tn\ is a planet will be a Rossiter-McLaughlin (RM) measurement.  
-Detection of the RM signal
-would rule out BEB and HEB scenarios, as it would imply that the
-eclipsing object is bound to the target star. Combined with our
-non-detection of the planet's mass from radial velocity monitoring,
-this would confirm that \pn\ is a planet.
+However, unlike these planets, \pn\ is validated but not yet
+confirmed.
+
+The easiest path towards definitively confirming whether \tn\ is a
+planet will be a Rossiter-McLaughlin (RM) measurement.  Detection of
+the RM signal would rule out BEB and HEB scenarios, as it would imply
+that the eclipsing object is bound to the target star. Combined with
+our non-detection of the planet's mass from radial velocity
+monitoring, this would confirm that \pn\ is a planet.
 
@@
 
-% \input{WASP-4b_transit_time_table.tex}
-% \input{WASP-4b_rv_table.tex}
-% \input{model_fit_table.tex}
-% \input{rv_model_posterior_table.tex}
-% \input{pdot_table.tex}
-
 \clearpage
@@
 \input{TOI837_rv_table.tex}
-%\input{model_comparison_table.tex}
 \clearpage

### 2020-07-02 paper/collect.sh

@@ -25,4 +25,6 @@ cp ${rdir}lithium/lithium.pdf f9a.pdf
 
 cp ${rdir}rotation/rotation.pdf f9b.pdf
 
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_subsetcorner.png f10.png
+
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-07-02 paper/ms.tex
update manuscript

@@
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f5.pdf}
+		\includegraphics[width=0.43\textwidth]{f5.pdf}
 	\end{center}
@@
 		\subfloat{
-			\includegraphics[width=0.47\textwidth]{f6.pdf}
+			\includegraphics[width=0.44\textwidth]{f6.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.47\textwidth]{f3.pdf}
+			\includegraphics[width=0.45\textwidth]{f3.pdf}
 		}
@@
 The combined radial velocities from FEROS, CHIRON, and Veloce can be
-used to place limits on the presence of massive, close-in bound
-companion to \tn.  We derived the relevant limits using
+used to detect massive bound
+companions orbiting \tn.  We searched for the presence of planetary and
+stellar-mass companions using
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits for the companion, and performed two sets of fits.
+orbits, and performed two sets of fits.
 
@@
 
-\input{ic2602_ages.tex}
-
-\input{starparams.tex}
-
-\input{model_posterior_table.tex}
-
 \subsection{The Cluster}
 \label{subsec:cluster}
+
+\input{ic2602_ages.tex}
 
@@
 
+\input{starparams.tex}
+
 Select properties of \tn\ from the literature and our analysis are
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
-However, unlike these planets, \pn\ is validated but not yet
+Unlike these planets, \pn\ is validated but not yet
 confirmed.
@@
 \citep{winn_exoplanet_2010}
-\begin{equation}
+\begin{align}
   \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
   \approx 21\,{\rm m\,s}^{-1},
-\end{equation}
+\end{align}
 where we have assumed stellar and transit parameters from
@@
 signal.  The reason is that the radial velocities, activity
-indicators, and photometry could then be fit simultaneously, which
-would greatly constrain any gaussian process model for the
+indicators, and photometry could then be modeled simultaneously, which
+would greatly constrain any Gaussian process model for the
 spot-induced RV signal.
@@
 
+\input{TOI837_phot_table.tex}
+
+\input{TOI837_rv_table.tex}
+
+%\clearpage
 \acknowledgements
+\tn\ was included on the TESS ``short-cadence'' target list in part
+thanks to the Guest Investigator program of G.\ Sacco (G011265).
 %
-%This paper includes data collected by the TESS mission, which are
-%publicly available from the Mikulski Archive for Space Telescopes
-%(MAST).
+This paper includes data collected by the TESS mission, which are
+publicly available from the Mikulski Archive for Space Telescopes
+(MAST).
 %
-%Funding for the TESS mission is provided by NASA's Science Mission
-%directorate.
-%
-The authors thank...
-%
-We also thank the Heising-Simons Foundation for
-their generous support of this work.
+Funding for the TESS mission is provided by NASA's Science Mission
+directorate.
 %
@@
 (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
-MINECO through grant AYA2017-84089
+MINECO through grant AYA2017-84089.
 %
-\tn\ was included on the TESS ``short-cadence'' target list in part
-thanks to the Guest Investigator program of G.\ Sacco (G011265).
-
+%
 %
@@
 
-%
-% The following are entries from Table 1 that are not otherwise cited
-% in the text
-%
-% \nocite{wilson_wasp-4b_2008}
-% \nocite{gillon_improved_2009}
-% \nocite{winn_transit_2009}
-% \nocite{hoyer_tramos_2013}
-% \nocite{dragomir_terms_2011}
-% \nocite{sanchis-ojeda_starspots_2011}
-% \nocite{nikolov_wasp-4b_2012}
-% \nocite{ranjan_atmospheric_2014}
-% \nocite{huitson_gemini_2017}
-
-\clearpage
-\input{TOI837_phot_table.tex}
-\input{TOI837_rv_table.tex}
-\clearpage
+% \clearpage
+% \clearpage
 
@@
 
-% \appendix
-% \section{Gaia query}
-% bounding by 5 stdevns
-% Launched query: '
-%         select top 10000
-%             g.source_id, g.phot_bp_mean_mag, g.phot_rp_mean_mag,
-%             g.phot_g_mean_mag, g.parallax, g.ra, g.dec, g.pmra, g.pmdec,
-%             g.radial_velocity, g.radial_velocity_error
-%         from gaiadr2.gaia_source as g
-%         where
-%             g.parallax > 5.69
-%         and
-%             g.parallax < 7.41
-%         and
-%             g.dec < -58.41
-%         and
-%             g.dec > -70.33
-%         and
-%             g.ra > 145.01
-%         and
-%             g.ra < 175.85
-%         and
-%             g.phot_g_mean_mag < 18
-%         order by
-%             random_index
-
 \listofchanges

### 2020-07-02 drivers/plot_rvs.py

@@ -579,7 +579,7 @@ class MultipanelPlot(object):
         figheight = self.ax_rv_height + self.ax_phase_height * scalefactor
 
         # provision figure
-        fig = plt.figure(figsize=(self.figwidth, figheight+0.8))
+        fig = plt.figure(figsize=(self.figwidth, figheight+1.0))
 
         fig.subplots_adjust(left=0.12, right=0.95)
         gs_rv = gridspec.GridSpec(1, 1, height_ratios=[1.])

### 2020-07-02 timmy/plotting.py

@@ -1317,7 +1317,7 @@ def plot_full_kinematics(outdir):
         'radial_velocity': 'RV [km/s]'
     }
 
-    f, axs = plt.subplots(figsize=(8,8), nrows=nparams-1, ncols=nparams-1)
+    f, axs = plt.subplots(figsize=(6,6), nrows=nparams-1, ncols=nparams-1)
 
     for i in range(nparams):
         for j in range(nparams):

### 2020-07-02 paper/ms.tex
update manuscript

@@
   3$\sigma$.  From TESS photometry alone, the planetary size lies
-  within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
+  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
   percentile), due to the degeneracy between the planetary size and
@@
 
-Beyond physical changes, dynamical changes are expected in the semi-major axes,
-eccentricities, and stellar obliquities of young planets.  When the gas disk is
-present, the planetary semi-major axis is thought to change in step with the
-viscous evolution of the disk \citep{lin_orbital_1996}.  High-eccentricity
-migration processes including planet-planet scattering, secular chaos, and
-Kozai-Lidov oscillations can also occur \citep[{\it
+Beyond physical changes, dynamical changes are expected in the
+semi-major axes, eccentricities, and stellar obliquities of young
+planets.  When the gas disk is present, the planetary semi-major axis
+is thought to change in step with the viscous evolution of the disk
+\citep{lin_orbital_1996}.  High-eccentricity migration processes
+including planet-planet scattering, secular chaos, and Kozai-Lidov
+oscillations can also occur \citep[{\it
 e.g.},][]{chatterjee_dynamical_2008,lithwick_secular_2014,fabrycky_shrinking_2007}.
-The circularization timescale is thought to be such that for any giant planets
-that migrated early, their orbits should circularize within 100 million years
-\citep{zahn_tidal_1977}.
+The circularization timescale is thought to be such that for any giant
+planets that migrated early, their orbits should circularize within
+100 million years \citep{zahn_tidal_1977}.
 
@@
 its probability of being an astrophysical false positive is negligibly
-small.  We considered this result worth reporting because of the planet's
-youth.
+small.  We considered this result worth reporting because of the
+planet's youth.
 
@@
     sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Spot-induced stellar variability is the dominant signal; flares are
-    shown with gray crosses.  Dashed
-    lines indicate the five transits observed by TESS.  {\it Bottom}:
-    Zoomed windows of individual transits.
-    Gray lines are the best-fit transit model, which includes a local
-    quadratic trend in each window.
+    Spot-induced stellar variability is the dominant signal; flares
+    are shown with gray crosses.  Dashed lines indicate the five
+    transits observed by TESS.  {\it Bottom}: Zoomed windows of
+    individual transits.  Gray lines are the best-fit transit model,
+    which includes a local quadratic trend in each window.
 		\label{fig:rawzoom}
@@
 \begin{itemize}
+  %
   \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
+  %
   \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
@@
     it may not be bound.
+  %
   \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
@@
 \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
-2020-06-22. } value is available.
-% The astrometric reduced $\chi^2$ ($\chi^2 / (N-5)$, for $N$ the number
-% of good astrometric observations) seems rather poor, at $8.6$.
-We suspect that the photometric failure to produce an $Rp$ magnitude,
-as well as its poor astrometric fit, are likely due to blending with
-\tn.
-
-At the $\approx1'$ resolution of the TESS data, if either Star A
-or Star B were eclipsing binaries, they could be the sources of the
+2020-06-22. } value is available.  We suspect that the photometric
+failure to produce an $Rp$ magnitude, as well as its poor astrometric
+fit, are likely due to blending with \tn.
+
+At the $\approx1'$ resolution of the TESS data, if either Star A or
+Star B were eclipsing binaries, they could be the sources of the
 transit signal.  A detailed analysis of ground-based seeing-limited
@@
 \paragraph{Custom aperture analysis}
-Based solely on the TESS data, both Star A and Star B
-were possible sources of blended eclipsing binary signals.
-Star B is resolved in the ground-based images; Star A is not.
+Based solely on the TESS data, both Star A and Star B were possible
+sources of blended eclipsing binary signals.  Star B is resolved in
+the ground-based images; Star A is not.
 
 To rule out blend scenarios with the ground-based photometry, we
-produced light curves centered on \tn\ with
-circular apertures of radii ranging from 0.7$''$ to 5.1$''$.
-We did not detect any statistically significant variation in the depth
-of the transits with aperture size.
-Two lines of evidence rule out Star B as the eclipsing source:
-first, the transits
-were detected in the smallest apertures.
-Second, we made light curves with $2.1''$ apertures centered on Star B,
-and they did not show the transit.
-
-To assess the possibility that Star A is an eclipsing body,
-we created light curves with a custom set of circular apertures
-with radii of $2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to 2.3$''$
-east of \tn.  We did not detect any variation of the transit depth
-along this line of light curves, as would be expected if Star A were
-the eclipse host.  The apertures east of \tn\ exclude over 90\% of the flux from Star A.
-The eclipse on Star A would therefore need to be excessively deep to
-produce the observed eclipse depth.
-We take this as evidence that \tn\ is the source of the transit signal
-to within $\approx2.0''$.
+produced light curves centered on \tn\ with circular apertures of
+radii ranging from 0.7$''$ to 5.1$''$.  We did not detect any
+statistically significant variation in the depth of the transits with
+aperture size.  Two lines of evidence rule out Star B as the eclipsing
+source: first, the transits were detected in the smallest apertures.
+Second, we made light curves with $2.1''$ apertures centered on Star
+B, and they did not show the transit.
+
+To assess the possibility that Star A is an eclipsing body, we created
+light curves with a custom set of circular apertures with radii of
+$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
+2.3$''$ east of \tn.  We did not detect any variation of the transit
+depth along this line of light curves, as would be expected if Star A
+were the eclipse host.  The apertures east of \tn\ exclude over 90\%
+of the flux from Star A.  The eclipse on Star A would therefore need
+to be excessively deep to produce the observed eclipse depth.  We take
+this as evidence that \tn\ is the source of the transit signal to
+within $\approx2.0''$.
 
@@
     SOAR HRCam contrast limits derived from point-source
-		injection-recovery experiments. A companion dubbed Star A ($\Delta T=4.7$,
-	$2.3''$ west) is detected in the autocorrelation function,
-	and is also a resolved Gaia source.  It is co-moving with
-	\tn, and its parallax and on-sky position imply that it is
-	physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
-		{\it Middle:} RV measurements, with best-fit instrument offsets
-	and jitter terms included.  The expected scatter from starspots
-	based on $v\sin i$ and the photometric modulation amplitude is of
-	order 300m$\,$s$^{-1}$.
-	{\it Bottom:}
-	RV measurements phased to the orbital ephemeris of \pn.  The
-	planet is not detected.  The black line shows a circular
-	Keplerian orbit representing the $3\sigma$ upper mass limit.
+    injection-recovery experiments. A companion dubbed Star A ($\Delta
+    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
+    and is also a resolved Gaia source.  It is co-moving with \tn, and
+    its parallax and on-sky position imply that it is physically
+    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} RV
+    measurements, with best-fit instrument offsets and jitter terms
+    included.  The expected scatter from starspots based on $v\sin i$
+    and the photometric modulation amplitude is of order
+    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
+    orbital ephemeris of \pn.  The planet is not detected.  The black
+    line shows a circular Keplerian orbit representing the $3\sigma$
+    upper mass limit.
 		\label{fig:followup}
@@
 
-\edit1{George TODO: please describe the formal secondary line search in
-more depth in this paragraph} We searched for secondary lines in the
-CHIRON spectra by cross-correlating against a {\bf template of some
-kind}.  This rules out lines with flux ratios of $\approx 2\%$, if the
-lines are well-separated in velocity.  To derive the star's physical
-parameters, we cross-correlated the template against {\bf something},
-and used the {\bf \texttt{nameofcode}}.  We measured the radial
-velocities through a least-squares deconvolution of the observed
-spectra against the same synthetic template.  The resulting velocities
-are given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.
+\edit1{George TODO: please describe the formal secondary line search
+in more depth in this paragraph} We searched for secondary lines in
+the CHIRON spectra by cross-correlating against a {\bf template of
+some kind}.  This rules out lines with flux ratios of $\approx 2\%$,
+if the lines are well-separated in velocity.  To derive the star's
+physical parameters, we cross-correlated the template against {\bf
+something}, and used the {\bf \texttt{nameofcode}}.  We measured the
+radial velocities through a least-squares deconvolution of the
+observed spectra against the same synthetic template.  The resulting
+velocities are given in Table~\ref{tab:rvs}, and shown in
+Figure~\ref{fig:followup}.
 
@@
 them out based on our combined photometry, velocimetry, and imaging.
-In this Section we describe each constraint in turn, and then present a
-calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
+In this Section we describe each constraint in turn, and then present
+a calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
 demonstrate that the probability \tn\ is an astrophysical false
@@
 The combined radial velocities from FEROS, CHIRON, and Veloce can be
-used to detect massive bound
-companions orbiting \tn.  We searched for the presence of planetary and
-stellar-mass companions using
+used to detect massive bound companions orbiting \tn.  We searched for
+the presence of planetary and stellar-mass companions using
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
@@
 We fitted for the observed depths in different bandpasses using a
-similar machinery as described in Section~\ref{subsec:planet}.  We fitted
-each ground-based transit individually for the planet-to-star size
-ratio, the impact parameter, and a local quadratic trend (the
+similar machinery as described in Section~\ref{subsec:planet}.  We
+fitted each ground-based transit individually for the planet-to-star
+size ratio, the impact parameter, and a local quadratic trend (the
 ephemeris was assumed from an initial fit of only the TESS data).  The
@@
 and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
-respectively, and are shown in
-Figure~\ref{fig:jointphot}.  Particularly in our Johnson-B light
-curve, the transit depth is correlated with the mean and linear slope
-of the light curve: a smaller depth is allowed if the data are fitted
-with a larger linear slope and a larger mean.  Our quoted limits
-marginalize over these correlations, and the depth measurement itself
-is nearly Gaussian.
+respectively, and are shown in Figure~\ref{fig:jointphot}.
+Particularly in our Johnson-B light curve, the transit depth is
+correlated with the mean and linear slope of the light curve: a
+smaller depth is allowed if the data are fitted with a larger linear
+slope and a larger mean.  Our quoted limits marginalize over these
+correlations, and the depth measurement itself is nearly Gaussian.
 
@@
 For a fixed secondary mass, we then asked whether any tertiary
-companions existed for which the maximal expected eclipse depth could have
-been larger than the observed depth.  In cases for which the answer
-was yes, we could not rule out such hierarchical eclipsing binary
-systems.  Conversely, we were ruled out systems for which at fixed
-secondary mass no tertiary mass could enable eclipses of the necessary
-depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).
-The ${\rm R_C}$-band limit corresponded to a secondary mass limit of 
-$M_2 > 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a
-stronger limit of $M_2 > 0.70 M_\odot$.
+companions existed for which the maximal expected eclipse depth could
+have been larger than the observed depth.  In cases for which the
+answer was yes, we could not rule out such hierarchical eclipsing
+binary systems.  Conversely, we were ruled out systems for which at
+fixed secondary mass no tertiary mass could enable eclipses of the
+necessary depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The
+${\rm R_C}$-band limit corresponded to a secondary mass limit of $M_2
+> 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger
+limit of $M_2 > 0.70 M_\odot$.
 
@@
 
-While the above constraints rule out HEBs, certain configurations of BEB systems 
-({\it e.g.}, a background G2V+K6V binary)
-can produce blue eclipses while remaining undetected along the line of
-sight.  Such scenarios are constrained by the lack of an observed
-secondary eclipse, and therefore require either eccentric orbits to
-avoid secondary eclipses, or else a background twin binary system at
-double the orbital period.  The only way to definitively rule out such
+While the above constraints rule out HEBs, certain configurations of
+BEB systems ({\it e.g.}, a background G2V+K6V binary) can produce blue
+eclipses while remaining undetected along the line of sight.  Such
+scenarios are constrained by the lack of an observed secondary
+eclipse, and therefore require either eccentric orbits to avoid
+secondary eclipses, or else a background twin binary system at double
+the orbital period.  The only way to definitively rule out such
 scenarios is to prove that the loss of light is from the target star,
@@
 space and ground based photometry (in addition to radial velocimetry),
-we opted for this approach because {\it i)} the radial velocitmetry on
+we opted for this approach because {\it i)} the radial velocimetry on
 its own did not show evidence for a planetary signal, and {\it ii)} we

### 2020-07-03 paper/ms.tex
Incorporate JNW suggestions (part 1)
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
   Multi-color photometry requires eclipsing companions to have nearly
-  identical color as TOI$\,$837, ruling out hierarchical eclipsing
-  binary scenarios.  Background eclipsing binary scenarios are limited
-  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
+  identical color as TOI$\,$837. Combined with spectroscopic and
+  imaging constraints, hierarchical eclipsing binary scenarios are
+  ruled out.  Background eclipsing binary scenarios are limited by
+  speckle imaging, but formally remain a 0.2\% possibility.  TOI
   837.01 is therefore a validated adolescent exoplanet.  Further
@@
     logarithmic grayscale. The yellow star is the position of \tn.
-    Orange circles are neighboring stars with $T<16$ (brighter stars
-    are larger). The \texttt{X} and \texttt{/} hatches show the
-    apertures used to measure the background and target star flux,
-    respectively. Dashed lines of constant declination and right
+    White circles are neighboring stars with $T<16$ (brighter stars
+    are larger). The black \texttt{X} and white \texttt{/} hatches
+    show the apertures used to measure the background and target star
+    flux, respectively. Dashed lines of constant declination and right
     ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
@@
 $T=16$, as queried from the Gaia DR2 source catalog, are shown with
-orange circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
+white circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
 and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
@@
 location and brightness contrast, and no additional companions were
-found.
+found.  Star B was not detected; with a separation of $5.4''$ from
+\tn, it fell outside the field of view.
 
@@
 from ``confirmation'', which means that there is overwhelming evidence
-that the data {\it must} be explained by a planet, for instance
-through combined photometric transits and a radial velocity mass
-measurement.
+that the transits {\it must} be explained by a planet, through
+elimination of all false positive scenarios and determination that the
+planety's mass is in the substellar regime.
 

### 2020-07-03 timmy/plotting.py

@@ -76,7 +76,7 @@ from matplotlib.colors import LinearSegmentedColormap, colorConverter
 from matplotlib.ticker import ScalarFormatter
 import matplotlib.ticker as ticker
 import matplotlib.transforms as transforms
-
+import matplotlib.patheffects as path_effects
 
 ##################################################
 # wrappers to generic plots implemented in billy #
@@ -1027,7 +1027,8 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
                 ax0.add_patch(
                     patches.Rectangle(
                         (x-.5, y-.5), 1, 1, hatch='//', fill=False, snap=False,
-                        linewidth=0., zorder=2, alpha=0.7, rasterized=True
+                        linewidth=0., zorder=2, alpha=1, rasterized=True,
+                        color='white'
                     )
                 )
 
@@ -1041,16 +1042,20 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
                     )
                 )
 
-    ax0.scatter(px, py, marker='o', c='C1', s=5e4/(tmags**3), rasterized=True,
-                zorder=6, linewidths=0.8)
+    ax0.scatter(px, py, marker='o', c='white', s=5e4/(tmags**3),
+                rasterized=False, zorder=6, linewidths=0.5, edgecolors='k')
     # ax0.scatter(px, py, marker='x', c='C1', s=20, rasterized=True,
     #             zorder=6, linewidths=0.8)
     ax0.plot(target_x, target_y, mew=0.5, zorder=5,
              markerfacecolor='yellow', markersize=15, marker='*',
              color='k', lw=0)
 
-    ax0.text(4.2, 5, 'A', fontsize=16, color='C1', zorder=6, style='italic')
-    ax0.text(4.6, 4.0, 'B', fontsize=16, color='C1', zorder=6, style='italic')
+    t = ax0.text(4.0, 5.2, 'A', fontsize=20, color='k', zorder=6)#, style='italic')
+    t.set_path_effects([path_effects.Stroke(linewidth=1.5, foreground='white'),
+                        path_effects.Normal()])
+    t = ax0.text(4.6, 3.8, 'B', fontsize=20, color='k', zorder=6)#, style='italic')
+    t.set_path_effects([path_effects.Stroke(linewidth=1.5, foreground='white'),
+                        path_effects.Normal()])
 
[…]

### 2020-07-04 paper/ms.tex
update manuscript

@@
   Our follow-up data show that such scenarios are highly unlikely.
-  Multi-color photometry requires eclipsing companions to have nearly
-  identical color as TOI$\,$837. Combined with spectroscopic and
-  imaging constraints, hierarchical eclipsing binary scenarios are
-  ruled out.  Background eclipsing binary scenarios are limited by
-  speckle imaging, but formally remain a 0.2\% possibility.  TOI
-  837.01 is therefore a validated adolescent exoplanet.  Further
-  observations of its stellar obliquity, atmosphere, and mass should
-  confirm its planetary nature beyond doubt, and could improve our
-  understanding of how the physical and orbital properties of
-  exoplanets change in time.
+  Our combined multi-color photometry, high-resolution imaging, and
+  radial velocities rule out hierarchical eclipsing binary scenarios.
+  Background eclipsing binary scenarios, though limited by speckle
+  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
+  therefore a validated adolescent exoplanet.  Further observations of
+  its stellar obliquity, atmosphere, and mass should confirm its
+  planetary nature beyond doubt, and could improve our understanding
+  of how the physical and orbital properties of exoplanets change in
+  time.
 \end{abstract}

### 2020-07-04 drivers/fit_allindivtransit.py
Incorporate JNW suggestions (part 2)
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@ -25,11 +25,11 @@ def main(modelid):
     make_threadsafe = 0
     cut_tess = 1
 
-    phaseplot = 0
-    grounddepth = 0
-    fitindiv = 0
+    phaseplot = 1
+    grounddepth = 1
+    fitindiv = 1
     cornerplot = 0
-    subsetcorner = 1
+    subsetcorner = 0
 
     N_samples = 6000 # took 31m 40s
 

### 2020-07-04 drivers/plot_rvs.py

@@ -545,7 +545,7 @@ class MultipanelPlot(object):
         #)
         anotext = (
             #f'K < {np.exp(logk1_limit):.1f}' +' m$\,$s$^{-1}$ (3$\sigma$)\n'
-            '$M_{\mathrm{p}} \sin i < 1.20\,M_{\mathrm{Jup}}$'
+            '$M_{\mathrm{p}} \sin i < 1.20\,M_{\mathrm{Jup}}\ (3\sigma)$'
         )
 
         add_anchored(

### 2020-07-04 timmy/plotting.py

@@ -858,11 +858,11 @@ def plot_phasefold(m, summdf, outpath, overwrite=0, show_samples=0,
         #                 color='C1', alpha=0.5, zorder=3, linewidth=0)
 
     if not inppt:
-        a0.set_ylabel('Relative flux', fontsize='medium')
+        a0.set_ylabel('Relative flux', fontsize='small')
     else:
-        a0.set_ylabel('Relative flux [ppt]', fontsize='medium')
-    a1.set_ylabel('Residual [ppt]', fontsize='medium')
-    a1.set_xlabel('Hours from mid-transit', fontsize='medium')
+        a0.set_ylabel('Relative flux [ppt]', fontsize='small')
+    a1.set_ylabel('Residual [ppt]', fontsize='small')
+    a1.set_xlabel('Hours from mid-transit', fontsize='small')
 
     if not inppt:
         a0.set_ylim((0.9925, 1.005))
@@ -2521,7 +2521,8 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None, showerror=1)
         if d in ['20200401', '20200426']:
             l1 = (
                 '$\delta_{\mathrm{R_C}}$ > '+
-                f'{1e3*DELTA_LIM_RC:.2f}'+'$\,$ppt'
+                f'{1e3*DELTA_LIM_RC:.2f}'+'$\,$ppt ' +
+                '(2$\sigma$)'
             )
             color = 'red'
         elif d in ['20200521']:
@@ -2530,7 +2531,8 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None, showerror=1)
         elif d in ['20200614']:
             l1 = (
                 '$\delta_{\mathrm{B_J}}$ > '+
-                f'{1e3*DELTA_LIM_B:.2f}'+'$\,$ppt'
+                f'{1e3*DELTA_LIM_B:.2f}'+'$\,$ppt '+
+                '(2$\sigma$)'
             )
             color = 'C0'
 
@@ -2605,9 +2607,9 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None, showerror=1)
         format_ax(ax)
 
     fig.text(0.5,-0.01, 'Hours from mid-transit', ha='center',
-             fontsize='medium')
+             fontsize='small')
     fig.text(-0.02,0.5, 'Relative flux [ppt]', va='center',
[…]

### 2020-07-04 paper/ms.tex
Incorporate JNW suggestions (part 2)
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>
Remove needless howevers
Co-authored-by: joshwinn <jwinn@astro.princeton.edu>

@@
   years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
-  Jupiter-sized.  However, its transits are grazing: $b > 0.92$ at
+  Jupiter-sized.  Its transits are grazing: $b > 0.92$ at
   3$\sigma$.  From TESS photometry alone, the planetary size lies
@@
 		\leavevmode
-		\includegraphics[width=.9\textwidth]{f1.pdf}
+		\includegraphics[width=.85\textwidth]{f1.pdf}
 	\end{center}
@@
 e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
-However, since the transits of \tn\ are grazing, the second and third
+Since the transits of \tn\ are grazing, the second and third
 contact points do not occur, and the shape of the transit is not
@@
 photometry, and been unable to exclude HEB scenarios, the FPP would
-have risen to 8\%.  However, since the transits are achromatic
+have risen to 8\%.  Since the transits are achromatic
 (Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
@@
 	\caption{ 
-		{\bf Posterior probabilities of
-			impact parameter, planet-to-star size ratio, and stellar density.} The photometric
-		data fitted in Section~\ref{subsec:planet} allow for
-		nonphysical planet sizes ($R_{\rm p}>2R_{\rm Jup}$;
-		$\log(R_{\rm p}/R_\star) \gtrsim -1.6$) due to a classic degeneracy
-		between the planet size and impact parameter.  Non-planetary sizes
-		would however imply non-planetary masses, which are ruled out by our
-		radial velocity measurements.
-		This plot was made using \texttt{corner} \citep{corner_2016}.
+    {\bf Posterior probabilities of impact parameter, planet-to-star
+    size ratio, and stellar density.} The photometric data fitted in
+    Section~\ref{subsec:planet} allow for nonphysical planet sizes
+    ($R_{\rm p}>2R_{\rm Jup}$; $\log(R_{\rm p}/R_\star) \gtrsim -1.6$)
+    due to a classic degeneracy between the planet size and impact
+    parameter.  Non-planetary sizes would imply non-planetary masses,
+    which are ruled out by our radial velocity measurements.  This
+    plot was made using \texttt{corner} \citep{corner_2016}.
 		\label{fig:subsetcorner}

### 2020-07-06 paper/ms.tex
update manuscript
... minor tweaks

@@
   monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
-  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
-  usually are indicative of astrophysical false positive scenarios.
+  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as they
+  are usually indicative of astrophysical false positive scenarios.
   Our follow-up data show that such scenarios are highly unlikely.
@@
     sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Spot-induced stellar variability is the dominant signal; flares
+    Starspot-induced variability is the dominant signal; flares
     are shown with gray crosses.  Dashed lines indicate the five
@@
     Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
-    measurements with the local spot-induced variation removed as
-    described in Section~\ref{subsec:planet}.  Black points are binned
-    to 6-minute intervals, and the error-bar shows the median
-    uncertainty for the black points.  The gray line shows the median
-    model corresponding to the combined TESS and ground-based transit
-    fit (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor
-    photometry from the El Sauce 0.36m; gray points are binned to
-    10-minute intervals.  Models show $2\sigma$ lower limits on the
-    transit depths in the Cousins-R and Johnson-B bandpasses used to
-    rule out specific false positive scenarios (see
+    measurements with the local spot-induced variation removed.  Black
+    points are binned to 6-minute intervals. The black error-bar shows
+    the median uncertainty for the black points.  The gray line is the
+    best-fit model to the combined TESS and ground-based data
+    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry
+    from the El Sauce 0.36m; black points are binned to 10-minute
+    intervals.  Models show $2\sigma$ lower limits on the transit
+    depths in the Cousins-R and Johnson-B bandpasses used to rule out
+    specific false positive scenarios (see
     Section~\ref{subsec:colorphot}).
@@
     SOAR HRCam contrast limits derived from point-source
-    injection-recovery experiments. A companion dubbed Star A ($\Delta
+    injection-recovery experiments. Star A ($\Delta
     T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
@@
     its parallax and on-sky position imply that it is physically
-    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} RV
-    measurements, with best-fit instrument offsets and jitter terms
-    included.  The expected scatter from starspots based on $v\sin i$
-    and the photometric modulation amplitude is of order
-    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
-    orbital ephemeris of \pn.  The planet is not detected.  The black
-    line shows a circular Keplerian orbit representing the $3\sigma$
-    upper mass limit.
+    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
+    Radial velocity (RV) measurements, with best-fit instrument
+    offsets and jitter terms included.  The expected scatter from
+    starspots based on $v\sin i$ and the photometric modulation
+    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
+    measurements phased to the orbital ephemeris of \pn.  The planet
+    is not detected.  The black line shows a circular Keplerian orbit
+    representing the $3\sigma$ upper mass limit.
 		\label{fig:followup}
@@
 		Each constraint is described in Section~\ref{subsec:fp_constraints}.
+    Gray regions are ruled out by at least one constraint.
 		\label{fig:fpscenario}
@@
   declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
-  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
-  arcseconds. 
+  $Bp$ Gaia blue, and $Rp$ Gaia red. 
   \label{fig:hr}
@@
 Rather than redetermine the age of the cluster and add another line to
-the table, we simply adopt the absolute age range for \tn\ of
+the table, we simply adopt an absolute age range for \tn\ of
 30--46$\,$Myr.

### 2020-07-06 drivers/fit_allindivtransit.py

@@ -27,9 +27,9 @@ def main(modelid):
 
     phaseplot = 0
     grounddepth = 0
-    fitindiv = 0
-    cornerplot = 1
-    subsetcorner = 1
+    fitindiv = 1
+    cornerplot = 0
+    subsetcorner = 0
 
     N_samples = 30000 # took 4h 52m, but Rhat=1.0 for all
     # N_samples = 6000 # took 31m 40s, Rhat=1.03 for rp_rs/b, 1.00 for rest

### 2020-07-06 timmy/plotting.py

@@ -1042,19 +1042,19 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
                     )
                 )
 
-    ax0.scatter(px, py, marker='o', c='white', s=5e4/(tmags**3),
+    ax0.scatter(px, py, marker='o', c='white', s=1.5*5e4/(tmags**3),
                 rasterized=False, zorder=6, linewidths=0.5, edgecolors='k')
     # ax0.scatter(px, py, marker='x', c='C1', s=20, rasterized=True,
     #             zorder=6, linewidths=0.8)
     ax0.plot(target_x, target_y, mew=0.5, zorder=5,
-             markerfacecolor='yellow', markersize=15, marker='*',
+             markerfacecolor='yellow', markersize=18, marker='*',
              color='k', lw=0)
 
     t = ax0.text(4.0, 5.2, 'A', fontsize=20, color='k', zorder=6)#, style='italic')
-    t.set_path_effects([path_effects.Stroke(linewidth=1.5, foreground='white'),
+    t.set_path_effects([path_effects.Stroke(linewidth=2.5, foreground='white'),
                         path_effects.Normal()])
     t = ax0.text(4.6, 3.8, 'B', fontsize=20, color='k', zorder=6)#, style='italic')
-    t.set_path_effects([path_effects.Stroke(linewidth=1.5, foreground='white'),
+    t.set_path_effects([path_effects.Stroke(linewidth=2.5, foreground='white'),
                         path_effects.Normal()])
 
     ax0.set_title('TESS', fontsize='xx-large')
@@ -2732,12 +2732,12 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
         ax.set_xlim((24*(start_time-mid_time), 24*(end_time-mid_time)))
         ax.set_ylim((-8, 8))
 
-        ymin, ymax = ax.get_ylim()
-        ax.vlines(
-            24*(mid_time-mid_time), ymin, ymax, colors='darkgray', alpha=0.5,
-            linestyles='--', zorder=-2, linewidths=0.2
-        )
-        ax.set_ylim((ymin, ymax))
+        # ymin, ymax = ax.get_ylim()
+        # ax.vlines(
+        #     24*(mid_time-mid_time), ymin, ymax, colors='darkgray', alpha=0.5,
+        #     linestyles='--', zorder=-2, linewidths=0.2
+        # )
[…]

### 2020-07-06 paper/ms.tex
update RM amplitude for limb darkening

@@
 		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f3.pdf}
+			\includegraphics[width=0.46\textwidth]{f3.pdf}
 		}
@@
 The maximum amplitude of the Rossiter-McLaughlin anomaly is
-\citep{winn_exoplanet_2010}
+\citep{gaudi_prospects_2007}
 \begin{align}
-  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
-  \approx 21\,{\rm m\,s}^{-1},
+  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
+  \approx 14\,{\rm m\,s}^{-1},
 \end{align}
-where we have assumed stellar and transit parameters from
-Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
-calculation purposes we assumed $b=0.95$.  This is challenging, but
-for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
-with modern spectrographs.  The next viable total transit windows from
-Chile occur in January and February of 2021; there are also a few
-visible per season from other southern locations.
+for
+\begin{align}
+  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
+\end{align}
+where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
+assumed $b=0.95$ and used stellar and transit parameters from
+Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
+challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
+could be achieved with modern spectrographs.  The next viable total
+transit windows from Chile occur in January and February of 2021;
+there are also a few visible per season from other southern locations.
 

### 2020-07-06 drivers/calc_rm_amplitude.py

@@ -1,0 +1,16 @@
+from astropy import units as u, constants as c
+
+depth = 4e-3
+vsini = 17.48*u.km/u.s
+b = 0.95
+
+u1 = .37
+u2 = .25
+mu = (1-b**2)**(1/2)
+
+I_factor = 1 - u1*(1-mu) - u2*(1-mu)**2
+
+delta_v_RM = (depth * vsini * (1-b**2)**(1/2)).to(u.m/u.s)
+
+print(f'{delta_v_RM:.2f}')
+print(f'{delta_v_RM*I_factor:.2f}')

### 2020-07-07 paper/ms.tex
update manuscript
Incorporate JH suggestions (part 1)
Co-authored-by: Joel Hartman <jhartman@astro.princeton.edu>

@@
   %
-  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3$'' west. The
+  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ west. The
     proper motions and parallax of this star imply it is comoving with
-    \tn, though with a physical separation of $6.6\pm 0.1\,{\rm pc}$,
-    it may not be bound.
-  %
-  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4$'' north.  The
+    \tn and is separated from it by $6.6\pm 0.1\,{\rm pc}$.
+    It is therefore likely an \cn\ member, but unlikely to be a bound
+    binary compnaion.
+  %
+  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ north.  The
     Gaia parallax implies this is a giant background star.
 \end{itemize}
-An additional source, TIC 847769581, is $4.9$'' from the target, but
+An additional source, TIC 847769581, is $4.9''$ from the target, but
 too faint ($T=18.8$) to be the source of the observed transit signal.
@@
 2.3$''$ east of \tn.  We did not detect any variation of the transit
-depth along this line of light curves, as would be expected if Star A
-were the eclipse host.  The apertures east of \tn\ exclude over 90\%
-of the flux from Star A.  The eclipse on Star A would therefore need
-to be excessively deep to produce the observed eclipse depth.  We take
-this as evidence that \tn\ is the source of the transit signal to
-within $\approx2.0''$.
+depth along this line of light curves. The apertures east of \tn\
+exclude over 90\% of the flux from Star A.  The eclipse on Star A
+would therefore need to have depth greater than unity to produce the
+observed eclipse depth.  We take the lack of a transit depth variation
+along these light curves as evidence that \tn\ is the source of the
+transit signal to within $\approx2.0''$.  The lack of variation of
+transit depth with aperture location is consistent with \tn\ being the
+source of transits, because the uncertainty of the transit depth
+measurements ($\approx 15\%$) is much greater than the maximum
+dilution from Star A ($\approx 1\%$).
 
@@
 wavelength calibrated spectra.  To measure radial velocities, \edit1{
-Rafael TODO: what procedure was used?  What software packages?}.  The
+Rafael/Paula TODO: what procedure was used?  What software packages?}.  The
 velocities are given in Table~\ref{tab:rvs}, and shown in
@@
 \subsubsection{Veloce}
-We acquired 34 spectra over 10 visits of \tn\ with using the Veloce
+We acquired 34 spectra over 10 visits of \tn\ using the Veloce
 spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
 Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
-In Rosso form, Veloce provides coverage from 600--950$\,$nm at a
-spectral resolution of $\approx 80{,}000$.
+In the ``Rosso'' instrument-mode, Veloce provides coverage from
+600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.
 
@@
 (``comp'') binary are labeled appropriately.  The requirement that the
-eclipse is produced by stars and that $\delta_{\rm true} < 0.5$
+eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
 translates to a bound on the faintest possible blended companion
@@
 answer was yes, we could not rule out such hierarchical eclipsing
-binary systems.  Conversely, we were ruled out systems for which at
+binary systems.  Conversely, we ruled out systems for which at
 fixed secondary mass no tertiary mass could enable eclipses of the
@@
 for instance by detecting the Rossiter-McLaughlin effect during a
-transit.
+transit, and confirming that the spectroscopic transit is consistent
+with the photometric transit.
 
@@
 we opted for this approach because {\it i)} the radial velocimetry on
-its own did not show evidence for a planetary signal, and {\it ii)} we
+its own did not show evidence for a planetary signal, {\it ii)} we
 expected that this approach would provide the best measurement of the
-planetary ephemeris, which is key for follow-up efforts.  The
-assumption of a constant radius across all bandpasses was tested by
-independently fitting each ground-based transit while letting the
+planetary ephemeris, which is key for follow-up efforts, and {\it
+iii)} the assumption of identical limb-darkening across all bandpasses
+seemed justified by the level of precision in the ground-based data.
+The assumption of a constant radius across all bandpasses was tested
+by independently fitting each ground-based transit while letting the
 planetary radius float (Section~\ref{subsec:colorphot}). The transit
@@
 
+\clearpage
 \bibliographystyle{yahapj}                            

### 2020-07-07 paper/ms.tex
Incorporate JH suggestions (part 2)
Co-authored-by: Joel Hartman <jhartman@astro.princeton.edu>

@@
 
-\edit1{Carl TODO: please describe and correct as appropriate}
 The observations of \tn\ were initially acquired by
@@
 
+One potential caveat in our approach is that \texttt{VESPA} uses a galactic
+population synthesis to model the sight-line. Since \tn\ is in the
+foreground of \cn\ (see Section~\ref{subsec:star}), for roughly
+$25\,{\rm pc}$ behind the sightline to the star, the number of
+background stars is higher than \texttt{VESPA} would predict due to the
+presence of the cluster.  To quantify the importance of this effect,
+we assessed the sky-plane density of potential contaminants by
+counting stars brighter than $T=15.07$ within 0.5 degrees of \tn\
+\citep{stassun_TIC8_2019}. We then compared this density against
+sightlines rotated in galactic longitude towards and away from the
+galactic center. Within $\pm10^\circ$ in galactic longitude, the
+sky-plane density of stars fluctuated at the level of $\approx 15\%$,
+with a local maximum a few degrees away from \tn, towards the center of \cn.
+The overall density also slowly increased towards the galactic center.
+We therefore do not expect this consideration to significantly alter
+our FPP calculation.
+
 \section{System Modelling}

### 2020-07-08 paper/ms.tex
update paper with IC2602 stellar params
With credit to JH for the idea to do it this way!

Co-authored-by: Joel Hartman <jhartman@astro.princeton.edu>

@@
   Cluster Difference Imaging Photometric Survey (CDIPS) II.
-  TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602
+  TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602
 }
@@
   star and validated planet are therefore between 30 and 46 million
-  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
-  Jupiter-sized.  Its transits are grazing: $b > 0.92$ at
-  3$\sigma$.  From TESS photometry alone, the planetary size lies
-  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
-  percentile), due to the degeneracy between the planetary size and
-  the impact parameter of the transit.  From radial velocity
-  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
-  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as they
-  are usually indicative of astrophysical false positive scenarios.
-  Our follow-up data show that such scenarios are highly unlikely.
-  Our combined multi-color photometry, high-resolution imaging, and
-  radial velocities rule out hierarchical eclipsing binary scenarios.
+  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and roughly
+  Jupiter-sized.  Combining the photometry with a prior on the stellar
+  parameters derived from the cluster color-magnitude diagram, we find
+  that the transits are grazing with $b=0.951\pm0.012$ and $R_{\rm p}
+  = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity monitoring, we
+  limit the minimum mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).
+  Grazing transits are a cause for concern, as they are usually
+  indicative of astrophysical false positive scenarios.  Our follow-up
+  data show that such scenarios are highly unlikely.  Our combined
+  multi-color photometry, high-resolution imaging, and radial
+  velocities rule out hierarchical eclipsing binary scenarios.
   Background eclipsing binary scenarios, though limited by speckle
@@
 
-\begin{figure}[!t]
+\begin{figure*}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.45\textwidth]{f7.pdf}
+		\includegraphics[width=0.75\textwidth]{f7.pdf}
 	\end{center}
@@
   declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
-  $Bp$ Gaia blue, and $Rp$ Gaia red. 
+  $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST isochrones (colored lines)
+  fit the upper main sequence well, but diverge from the data for
+  $M_\star \lesssim 0.7 M_\odot$. This is a known problem with PMS
+  models (see Section~\ref{subsec:hr}).
   \label{fig:hr}
 	}
-\end{figure}
+\end{figure*}
 
@@
   proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
-  \alpha}\cos\delta$) highlights incompleteness in the membership selection function.
+  \alpha}\cos\delta$) highlights incompleteness in the membership
+  selection function.
   \label{fig:full_kinematics}
@@
 \subsubsection{HR Diagram}
+\label{subsec:hr}
 
@@
 motions, and parallaxes.  We included candidate members with formal
-membership probability exceeding 10\%.  Save for a few low-mass
-outliers, most members appear to be young and coeval.
-
+membership probability exceeding 10\%.  Most members appear to be
+young and coeval.
 \tn\ is in its expected position relative to the other members along
@@
 
-Figure~\ref{fig:hr} also suggests that the membership census of \cn\
+Figure~\ref{fig:hr} suggests that the membership census of \cn\
 is incomplete.  We defined the reference ``neighborhood'' as the group
@@
 \citet{cantatgaudin_gaia_2018} membership assignment process.
+
+Figure~\ref{fig:hr} also compares the data to the MIST isochrones
+\citep{choi_mesa_2016}.  We used the
+web-interace\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
+\texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
+million years. We assumed solar metallicity, and a fixed extinction
+value of $A_V = 0.217$ \citep{randich_gaiaeso_2018}.  The 30 and 40
+Myr models align well with the data for stars with masses ranging from
+roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are
+bluer than observed in the Gaia photometry.  This discrepancy was noted and discussed at
+length by \citet{choi_mesa_2016}.  The most plausible explanation
+seems to be that strong magnetic fields in low-mass pre-main-sequence
+stars inhibit convection and produce a high filling factor of
+starspots \citep[{\it
+e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}. To conserve flux,
+the stellar radius expands, and the star becomes cooler than a
+1-dimensional model would predict.
 
@@
 Select properties of \tn\ from the literature and our analysis are
-presented in Table~\ref{tab:starparams}.  The spectroscopic parameters
-were measured from each of the six CHIRON spectra
-(Section~\ref{subsec:chiron}). We then averaged the results, and
-adopted the standard deviation across the spectra as the uncertainty.
-
-We then calculated the stellar radius and reddening following
-\citet{stassun_accurate_2017}.  We first derived the bolometric flux
-by combining available broadband magnitudes from Gaia, Tycho-2, APASS,
-2MASS, and WISE.  We then fitted the SED with the
+presented in Table~\ref{tab:starparams}.  We calculated the stellar
+parameters using two different approaches.
+
+In ``Method 1'', we measured spectroscopic parameters from each of the
+CHIRON spectra (Section~\ref{subsec:chiron}).
+We then calculated the stellar radius and reddening
+following \citet{stassun_accurate_2017}.  We first derived the
+bolometric flux by combining available broadband magnitudes from Gaia,
+Tycho-2, APASS, 2MASS, and WISE.  We then fitted the SED with the
 \citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
@@
 extinction ($A_{\rm V}$) and the overall normalization.  This
-procedure yielded $A_{\rm V} = 0.20\pm0.03$, which independently
-agrees with the average from the \cn\ isochrone fits of
-\citet{randich_gaiaeso_2018}.
-We then combined the spectroscopic effective temperature, bolometric
-flux, and Gaia distance to determine the stellar radius, using the
-Stefan-Boltzmann law.
+procedure yielded $A_{\rm V} = 0.20\pm0.03$, which agrees with the
+average from the \cn\ isochrone fits of \citet{randich_gaiaeso_2018}.
+Combining the spectroscopic effective temperature, bolometric flux,
+and Gaia distance, we determined the stellar radius using the
+Stefan-Boltzmann law.  Combining this radius the spectroscopic $\log
+g$ also yields a stellar mass.
+
+In ``Method 2'', we simply used the observed location of \tn\ in the
+HR diagram and interpolated against the 40$\,$Myr isochrone.  This
+method leverages the relative location of \tn\ within the narrow \cn\
+isochrone to derive precise, theoretically self-consistent constraints
+on all of the stellar parameters.  Although this approach would fail
+for a low-mass star, \tn\ is above the stellar masses where the Gaia
+photometry and isochrone models begin to diverge.
+
+Method 1 yielded a stellar mass that seemed to be high relative to the
+observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
+K}$, with relative uncertainties of a few percent on each). To avoid
+poorly understood systematics,  we adopted the stellar parameters
+from Method 2, and report them in Table~\ref{tab:starparams}.
 
@@
     {\bf Posterior probabilities of impact parameter, planet-to-star
-    size ratio, and stellar density.} The photometric data fitted in
-    Section~\ref{subsec:planet} allow for nonphysical planet sizes
-    ($R_{\rm p}>2R_{\rm Jup}$; $\log(R_{\rm p}/R_\star) \gtrsim -1.6$)
-    due to a classic degeneracy between the planet size and impact
-    parameter.  Non-planetary sizes would imply non-planetary masses,
-    which are ruled out by our radial velocity measurements.  This
+    size ratio, and stellar density.} The 3$^{\rm rd}$ and 97$^{\rm
+    th}$ percentiles in the planet-to-star size ratio correspond to
+    planet sizes $0.65\,R_{\rm Jup}$ and $0.91\,R_{\rm Jup}$.  This
     plot was made using \texttt{corner} \citep{corner_2016}.
@@
 
-Our joint model for the TESS and ground-based data was a
+Our joint model for the TESS and ground-based data was an
 \citet{exoplanet:agol19} transit with physical and orbital parameters
@@
 The posteriors from this procedure are given in
-Table~\ref{tab:posterior}.  Crucially important is the point that the
-transit is grazing.  The grazing geometry hinders our ability to infer
-the stellar density and planet-to-star size ratio. The relevant
-posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
-
-The available data for \tn\ put us in an odd position. The transit
-data provide a minimum size due to the grazing geometry; the radial
-velocity data provide a maximum mass ($\approx$1.20 $M_{\rm jup}$).
-We could combine the two with an empirically-calibrated planetary
-mass-radius relation to force a more restrictive upper bound on the
-planetary size \citep[{\it e.g.},][]{chen_probabilistic_2016}.  The
-result of such an exercise would tautologically be that the planet
-would be smaller than the largest known Jovian planets ($\approx
-2R_{\rm Jup}$).  This would also imply that the impact parameter is
-slightly below unity.  The planet's size, in our eyes, would remain
-poorly constrained even if we were to do this exercise, so we opt to 
-fit the photometry and radial velocities separately, to ensure clarity
-about which datasets are providing which constraints.
+Table~\ref{tab:posterior}.  The transit is grazing.  In the absence of
+a strong prior on the stellar density, the grazing geometry would
+hinder our ability to infer the planet-to-star size ratio.  However,
+our prior on the stellar parameters from the cluster isochrone fit is
+strong enough that we can derive two-sided limits on the
+planet-to-star size ratio.  The relevant posterior probabilities are
+shown in Figure~\ref{fig:subsetcorner}.
+
+% The available data for \tn\ put us in an odd position. The transit
+% data provide a minimum size due to the grazing geometry; the radial
+% velocity data provide a maximum mass ($\approx$1.20 $M_{\rm jup}$).
+% We could combine the two with an empirically-calibrated planetary
+% mass-radius relation to force a more restrictive upper bound on the
+% planetary size \citep[{\it e.g.},][]{chen_probabilistic_2016}.  The
+% result of such an exercise would tautologically be that the planet
+% would be smaller than the largest known Jovian planets ($\approx
+% 2R_{\rm Jup}$).  This would also imply that the impact parameter is
+% slightly below unity.  The planet's size, in our eyes, would remain
+% poorly constrained even if we were to do this exercise, so we opt to 
+% fit the photometry and radial velocities separately, to ensure clarity
+% about which datasets are providing which constraints.
 
@@
 Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
-challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
+challenging, for a 1.84$\,$hr transit of a $V=10.6$ star, a detection
 could be achieved with modern spectrographs.  The next viable total

### 2020-07-08 paper/collect.sh

@@ -3,11 +3,11 @@
 rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_fitindiv.pdf f1.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_fitindiv.pdf f1.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_phaseplot.pdf f2a.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_phaseplot.pdf f2a.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_grounddepth.pdf f2b.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_grounddepth.pdf f2b.pdf
 
 cp ${pdir}scene.pdf f5.pdf
 
@@ -17,7 +17,7 @@ cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f3
 
 cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
 
-cp ${rdir}cluster_membership/hr.pdf f7.pdf
+cp ${rdir}cluster_membership/hr_withiso.pdf f7.pdf
 
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
 
@@ -25,6 +25,6 @@ cp ${rdir}lithium/lithium.pdf f9a.pdf
 
 cp ${rdir}rotation/rotation.pdf f9b.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200617/TOI_837_*_subsetcorner.png f10.png
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_subsetcorner.png f10.png
 
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-07-08 paper/ms.tex
update manuscript

@@
   TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
-  star and validated planet are therefore between 30 and 46 million
-  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and roughly
-  Jupiter-sized.  Combining the photometry with a prior on the stellar
-  parameters derived from the cluster color-magnitude diagram, we find
-  that the transits are grazing with $b=0.951\pm0.012$ and $R_{\rm p}
-  = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity monitoring, we
-  limit the minimum mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).
-  Grazing transits are a cause for concern, as they are usually
-  indicative of astrophysical false positive scenarios.  Our follow-up
-  data show that such scenarios are highly unlikely.  Our combined
-  multi-color photometry, high-resolution imaging, and radial
-  velocities rule out hierarchical eclipsing binary scenarios.
-  Background eclipsing binary scenarios, though limited by speckle
-  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
-  therefore a validated adolescent exoplanet.  Further observations of
-  its stellar obliquity, atmosphere, and mass should confirm its
-  planetary nature beyond doubt, and could improve our understanding
-  of how the physical and orbital properties of exoplanets change in
-  time.
+  star and validated planet are therefore $35^{+11}_{-5}$ million
+  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and slightly
+  smaller than Jupiter.  Combining the photometry with a prior on the
+  stellar parameters derived from the cluster color-magnitude diagram,
+  we find that the transits are grazing with $b=0.951\pm0.012$ and
+  $R_{\rm p} = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity
+  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
+  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
+  they are usually indicative of astrophysical false positive
+  scenarios.  Our follow-up data show that such scenarios are highly
+  unlikely.  Our combined multi-color photometry, high-resolution
+  imaging, and radial velocities rule out hierarchical eclipsing
+  binary scenarios.  Background eclipsing binary scenarios, though
+  limited by speckle imaging, formally remain a 0.2\% possibility.
+  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
+  observations of its stellar obliquity, atmosphere, and mass should
+  confirm its planetary nature beyond doubt, and could improve our
+  understanding of how the physical and orbital properties of
+  exoplanets change in time.
 \end{abstract}
@@
     {\bf Posterior probabilities of impact parameter, planet-to-star
-    size ratio, and stellar density.} The 3$^{\rm rd}$ and 97$^{\rm
-    th}$ percentiles in the planet-to-star size ratio correspond to
-    planet sizes $0.65\,R_{\rm Jup}$ and $0.91\,R_{\rm Jup}$.  This
-    plot was made using \texttt{corner} \citep{corner_2016}.
+    size ratio, and stellar density.} The  planet-to-star size ratio
+    corresponds to a planet size between $0.65\,R_{\rm Jup}$ and
+    $0.91\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
+    This plot was made using \texttt{corner} \citep{corner_2016}.
 		\label{fig:subsetcorner}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{TOI837_phot_table.tex}
-
-\input{TOI837_rv_table.tex}
 
@@
 
+\input{TOI837_phot_table.tex}
+
+\input{TOI837_rv_table.tex}
+
 \clearpage

### 2020-07-08 paper/ms.tex
fix typos

@@
 and Gaia distance, we determined the stellar radius using the
-Stefan-Boltzmann law.  Combining this radius the spectroscopic $\log
-g$ also yields a stellar mass.
+Stefan-Boltzmann law.  Combining this radius with the spectroscopic
+$\log g$ also yields a stellar mass.
 
@@
 hinder our ability to infer the planet-to-star size ratio.  However,
-our prior on the stellar parameters from the cluster isochrone fit is
-strong enough that we can derive two-sided limits on the
+our priors on the stellar parameters from the cluster isochrone fit
+are strong enough that we can derive two-sided limits on the
 planet-to-star size ratio.  The relevant posterior probabilities are
@@
 TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
-\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
+\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
 Unlike these planets, \pn\ is validated but not yet
@@
 expected to be induced by stellar rotation.  The photometric amplitude
-induced by starspots on \tn\ is $\approx 2\%$. 
-The RV noise expected over the course of the $\approx 3\,{\rm d}$
-rotation period can then be estimated by multiplying the photometric amplitude and
-spectroscopic equatorial velocity.  This gives $\sigma_{\rm RV,rot}
-\approx 300\,{\rm m\,s}^{-1}$, and is consistent with the scatter we
-observe in our radial velocities from FEROS.  Detecting
-a planet's Doppler signal in these regimes is
-challenging, and requires a significant amount of data and care in
-signal extraction \citep{barragan_radial_2019}.  The
-Rossiter-McLaughlin measurement avoids the majority of this issue
-because the transit occurs over a much shorter duration than a single
-stellar rotation period.
+induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
+variation expected over the course of the $\approx 3\,{\rm d}$
+rotation period can then be estimated by multiplying the photometric
+amplitude and spectroscopic equatorial velocity.  This gives
+$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
+with the scatter we observe in our radial velocities from FEROS.
+Detecting a planet's Doppler signal in these regimes is challenging,
+and requires a significant amount of data and care in signal
+extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
+measurement avoids the majority of this issue because the transit
+occurs over a much shorter duration than a single stellar rotation
+period.
 
@@
 indicators, and photometry could then be modeled simultaneously, which
-would greatly constrain any Gaussian process model for the
+would greatly constrain a Gaussian process model for the
 spot-induced RV signal.

### 2020-07-09 paper/ms.tex
update manuscript
(non-converged chains, but looking decent)

@@
 \citep{dauphas_hf-w-th_2011}, they can also undergo significant
-changes over the next $\sim$10-100 million years through giant impacts
+growth over the next $\sim$10-100 million years through giant impacts
 \citep[{\it
-e.g.},][]{kleine_hf-w_2009,konig_earths_2011,raymond_terrestrial_2014}.
+e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
 The Moon, for instance, may have formed from debris ejected during a
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\begin{center}
 		\leavevmode
-		\subfloat{
-			\includegraphics[width=0.8\textwidth]{f2a.pdf}
-		}
-
-		\vspace{-0.6cm}
-		\subfloat{
-			\includegraphics[width=0.8\textwidth]{f2b.pdf}
-		}
+		\includegraphics[width=.47\textwidth]{f2a.pdf}
 	\end{center}
@@
 	\caption{
-    {\bf Photometry of \tn.} {\it Top:}
-    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
+    {\bf Phase-folded TESS transit.} Gray points are 2-minute PDCSAP flux
     measurements with the local spot-induced variation removed.  Black
@@
     best-fit model to the combined TESS and ground-based data
-    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry
-    from the El Sauce 0.36m; black points are binned to 10-minute
-    intervals.  Models show $2\sigma$ lower limits on the transit
-    depths in the Cousins-R and Johnson-B bandpasses used to rule out
-    specific false positive scenarios (see
-    Section~\ref{subsec:colorphot}).
-    \label{fig:jointphot}
-	}
-\end{figure*}
+    (Table~\ref{tab:posterior}). 
+		\label{fig:phasefold}
+	}
+\end{figure}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=.47\textwidth]{f2b.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Ground-based follow-up photometry.} The data were acquired
+    using the El Sauce 0.36m and ASTEP400 (0.40m). Black points are
+    binned to 10-minute intervals.  The gray line is the best-fit
+    model to the combined TESS and ground-based data. Models show
+    $2\sigma$ lower limits on the transit depths in the Cousins-R and
+    Johnson-B bandpasses used to rule out specific false positive
+    scenarios (see Section~\ref{subsec:colorphot}).
+		\label{fig:groundphot}
+	}
+\end{figure}
 
@@
 phase-folded view of the TESS transits with starspot variability
-removed is shown in Figure~\ref{fig:jointphot}. Our fitting procedure
+removed is shown in Figure~\ref{fig:phasefold}. Our fitting procedure
 for the models shown in these plots is described in
@@
 		\leavevmode
-		\includegraphics[width=0.85\textwidth]{f4.pdf}
+		\includegraphics[width=0.8\textwidth]{f4.pdf}
 	\end{center}
@@
 and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
-respectively, and are shown in Figure~\ref{fig:jointphot}.
+respectively, and are shown in Figure~\ref{fig:groundphot}.
 Particularly in our Johnson-B light curve, the transit depth is
@@
 have risen to 8\%.  Since the transits are achromatic
-(Figure~\ref{fig:jointphot}), particularly in Johnson-B band, we can
+(Figure~\ref{fig:groundphot}), particularly in Johnson-B band, we can
 rule out HEB scenarios.
@@
 
-\begin{figure*}[!t]
+\begin{figure}[!t]
 	\begin{center}
 		\leavevmode
-		\includegraphics[width=0.75\textwidth]{f7.pdf}
+		\includegraphics[width=0.48\textwidth]{f7.pdf}
 	\end{center}
@@
 	}
-\end{figure*}
+\end{figure}
 
@@
 
-\input{starparams.tex}
+%
 
@@
 
-\input{model_posterior_table.tex}
+%
 
@@
 shared across all transit windows, plus a local quadratic trend
-allowed within each window.  The parameters and priors
+allowed within each window.  Select parameters and priors
 are listed in Table~\ref{tab:posterior}.  In brief, we fitted for the
@@
 shared planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).
-There were also three free trend parameters for each of the nine
+There were also three free trend parameters for each of the twelve
 transits to account for the rotational variability.  This yielded a
-total of 35 free parameters, of which 8 have physical relevance, and
-27 are nuisance parameters.
+total of 44 free parameters, of which 8 have physical relevance, and
+36 are nuisance parameters.  To keep the table at a manageable length,
+we only report the physically relevant parameters and derived
+quantities.
 
 We fitted the model using \texttt{PyMC3}
-\citep{salvatier_2016_PyMC3,exoplanet:theano}. 
-For the exoplanet transit, we used the \texttt{exoplanet} code
-\citep{exoplanet:exoplanet}.  
-After initializing each model with the parameters of the
-maximum {\it a posteriori} model, we assumed a Gaussian
-likelihood, and sampled using \texttt{PyMC3}'s gradient-based
-No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$
-as our convergence diagnostic \citep{gelman_inference_1992}.
+\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the exoplanet
+transit, we used the \texttt{exoplanet} code
+\citep{exoplanet:exoplanet}.  After initializing each model with the
+parameters of the maximum {\it a posteriori} model, we assumed a
+Gaussian likelihood, and sampled using \texttt{PyMC3}'s gradient-based
+No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as
+our convergence diagnostic \citep{gelman_inference_1992}.
 
@@
 % \clearpage
-% \clearpage
-
+%\clearpage
+\input{starparams.tex}
+%\clearpage
+\input{model_posterior_table.tex}
+\clearpage
 \input{TOI837_phot_table.tex}
-
 \input{TOI837_rv_table.tex}
+\clearpage
 

### 2020-07-09 drivers/make_posterior_table.py

@@ -8,7 +8,7 @@ from timmy.modelfitter import ModelFitter, ModelParser
 from timmy.priors import initialize_prior_d
 from timmy.paths import RESULTSDIR
 from timmy.convenience import (
-    get_clean_tessphot, get_elsauce_phot, _subset_cut
+    get_clean_tessphot, get_elsauce_phot, _subset_cut, get_astep_phot
 )
 from collections import OrderedDict
 from astrobase.lcmath import find_lc_timegroups
@@ -24,7 +24,7 @@ def main(modelid):
     PLOTDIR = os.path.join(
         RESULTSDIR, '{}_{}_phot_results'.format(REALID, modelid)
     )
-    datestr = '20200708'
+    datestr = '20200709'
     PLOTDIR = os.path.join(PLOTDIR, datestr)
 
     summarypath = os.path.join(
@@ -63,6 +63,14 @@ def main(modelid):
         x_obs -= 2457000 # convert to BTJD
         elsauce_texp = np.nanmedian(np.diff(x_obs))
         datasets[f'elsauce_{ix}'] = [x_obs, y_obs, y_err, elsauce_texp]
+
+    datestrs = ['20200529', '20200614', '20200623']
+    for ix, d in enumerate(datestrs):
+        x_obs, y_obs, y_err = get_astep_phot(datestr=d)
+        x_obs += 2450000 # convert to BJD_TDB
+        x_obs -= 2457000 # convert to BTJD
+        astep_texp = np.nanmedian(np.diff(x_obs))
+        datasets[f'astep_{ix}'] = [x_obs, y_obs, y_err, astep_texp]
 
     mp = ModelParser(modelid)
 
@@ -107,6 +115,11 @@ def main(modelid):
         fitted_params.append(f'elsauce_{i}_mean')
         fitted_params.append(f'elsauce_{i}_a1')
         fitted_params.append(f'elsauce_{i}_a2')
+    for i in range(3):
+        fitted_params.append(f'astep_{i}_mean')
+        fitted_params.append(f'astep_{i}_a1')
+        fitted_params.append(f'astep_{i}_a2')
+
     n_fitted = len(fitted_params)
 
     derived_params = [
@@ -132,21 +145,24 @@ def main(modelid):
[…]

### 2020-07-09 paper/collect.sh

@@ -3,11 +3,11 @@
 rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_fitindiv.pdf f1.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200709/TOI_837_*_fitindiv.pdf f1.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_phaseplot.pdf f2a.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200709/TOI_837_*_phaseplot.pdf f2a.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_grounddepth.pdf f2b.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200709/TOI_837_*_grounddepth.pdf f2b.pdf
 
 cp ${pdir}scene.pdf f5.pdf
 
@@ -25,6 +25,6 @@ cp ${rdir}lithium/lithium.pdf f9a.pdf
 
 cp ${rdir}rotation/rotation.pdf f9b.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200708/TOI_837_*_subsetcorner.png f10.png
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200709/TOI_837_*_subsetcorner.png f10.png
 
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-07-09 timmy/plotting.py

@@ -2365,11 +2365,11 @@ def plot_fpscenarios(outdir):
 
             dofill = False
             if w == 'both':
-                ax.plot(xval, yval, label=name, color=c, lw=3)
+                ax.plot(xval, yval, label=name, color=c, lw=2)
                 dofill = True
 
             if w == 'assoc' and ax_ix == 0:
-                ax.plot(xval, yval, label=name, color=c, lw=3)
+                ax.plot(xval, yval, label=name, color=c, lw=2)
                 dofill = True
             elif w == 'assoc' and ax_ix == 1:
                 pass

### 2020-07-10 paper/ms.tex
update manuscript
Rhat = 1.0!

@@
   transiting planet.  We characterize the system using data from the
-  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
+  NASA TESS mission, the ESA Gaia mission, photometry from El Sauce
+  and ASTEP400,
   and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
@@
   years old.  The planet is warm ($P = 8.3\,{\rm d}$) and slightly
-  smaller than Jupiter.  Combining the photometry with a prior on the
+  smaller than Jupiter.  Combining the transit photometry with a prior on the
   stellar parameters derived from the cluster color-magnitude diagram,
-  we find that the transits are grazing with $b=0.951\pm0.012$ and
-  $R_{\rm p} = 0.77 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity
+  we find that the transits are grazing with $b=0.93\pm0.01$ and
+  $R_{\rm p} = 0.79 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity
   monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
@@
 \citep{dauphas_hf-w-th_2011}, they can also undergo significant
-growth over the next $\sim$10-100 million years through giant impacts
+growth over the next 10--100 million years through giant impacts
 \citep[{\it
@@
 		\leavevmode
-		\includegraphics[width=.85\textwidth]{f1.pdf}
+		\subfloat{
+			\includegraphics[width=0.79\textwidth]{f1.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.77\textwidth]{f2a.pdf}
+		}
 	\end{center}
-	\vspace{-0.7cm}
+	\vspace{-0.6cm}
 	\caption{
-    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
+    {\bf TESS light curve of \tn.}
+    {\it Top}:
     \texttt{PDCSAP} median-subtracted relative flux at 2-minute
@@
     are shown with gray crosses.  Dashed lines indicate the five
-    transits observed by TESS.  {\it Bottom}: Zoomed windows of
+    transits observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed windows of
     individual transits.  Gray lines are the best-fit transit model,
     which includes a local quadratic trend in each window.
-		\label{fig:rawzoom}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.47\textwidth]{f2a.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Phase-folded TESS transit.} Gray points are 2-minute PDCSAP flux
+    {\it Bottom}: Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
     measurements with the local spot-induced variation removed.  Black
@@
     (Table~\ref{tab:posterior}). 
-		\label{fig:phasefold}
-	}
-\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.47\textwidth]{f2b.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Ground-based follow-up photometry.} The data were acquired
-    using the El Sauce 0.36m and ASTEP400 (0.40m). Black points are
-    binned to 10-minute intervals.  The gray line is the best-fit
-    model to the combined TESS and ground-based data. Models show
-    $2\sigma$ lower limits on the transit depths in the Cousins-R and
-    Johnson-B bandpasses used to rule out specific false positive
-    scenarios (see Section~\ref{subsec:colorphot}).
-		\label{fig:groundphot}
-	}
-\end{figure}
+		\label{fig:tessphot}
+	}
+\end{figure*}
+
+% \begin{figure*}[!t]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=.85\textwidth]{f1.pdf}
+% 	\end{center}
+% 	\vspace{-0.7cm}
+% 	\caption{
+%     {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
+%     \texttt{PDCSAP} median-subtracted relative flux at 2-minute
+%     sampling in units of parts-per-thousand ($\times 10^{-3}$).
+%     Starspot-induced variability is the dominant signal; flares
+%     are shown with gray crosses.  Dashed lines indicate the five
+%     transits observed by TESS.  {\it Bottom}: Zoomed windows of
+%     individual transits.  Gray lines are the best-fit transit model,
+%     which includes a local quadratic trend in each window.
+% 		\label{fig:rawzoom}
+% 	}
+% \end{figure*}
+
+% \begin{figure}[!t]
+% 	\begin{center}
+% 		\leavevmode
+% 		\includegraphics[width=.47\textwidth]{f2a.pdf}
+% 	\end{center}
+% 	\vspace{-0.7cm}
+% 	\caption{
+%     {\bf Phase-folded TESS transit.} Gray points are 2-minute PDCSAP flux
+%     measurements with the local spot-induced variation removed.  Black
+%     points are binned to 6-minute intervals. The black error-bar shows
+%     the median uncertainty for the black points.  The gray line is the
+%     best-fit model to the combined TESS and ground-based data
+%     (Table~\ref{tab:posterior}). 
+% 		\label{fig:phasefold}
+% 	}
+% \end{figure}
 
@@
 
-Figure~\ref{fig:rawzoom} shows the data.  The dominant modulation
+Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
 induced by starspots coming into and out of view has a peak-to-peak
@@
 phase-folded view of the TESS transits with starspot variability
-removed is shown in Figure~\ref{fig:phasefold}. Our fitting procedure
+removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
 for the models shown in these plots is described in
@@
 		\leavevmode
-		\includegraphics[width=0.43\textwidth]{f5.pdf}
+		\includegraphics[width=0.48\textwidth]{f5.pdf}
 	\end{center}
@@
     logarithmic grayscale. The yellow star is the position of \tn.
-    White circles are neighboring stars with $T<16$ (brighter stars
+    White circles are resolved Gaia sources with $T<16$ (brighter stars
     are larger). The black \texttt{X} and white \texttt{/} hatches
@@
     flux, respectively. Dashed lines of constant declination and right
-    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
-    image of the same field, with a linear grayscale.  Two stars of
-    interest are ``Star A'' and ``Star B'', which were eventually
-    excluded as being possible sources of the transits.
+    ascension are shown.
+    Two stars of interest are ``Star A'' and ``Star B'', which were eventually excluded as being possible sources of the transits.
+    %{\it Bottom:} Digitized Sky Survey $R$-band
+   % image of the same field, with a linear grayscale. 
 		\label{fig:scene}
@@
 $T=16$, as queried from the Gaia DR2 source catalog, are shown with
-white circles in Figure~\ref{fig:scene}, overlaid on the DSS2 plates
-and TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
+white circles in Figure~\ref{fig:scene}, overlaid on 
+the TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
 not surprising that the field of \tn\ is crowded.  The resolved stars
@@
 GAIA-C3-TN-LU-LL-124-01,
-\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
-2020-06-22. } value is available.  We suspect that the photometric
+\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
+\texttt{2020-07-08}. } value is available.  We suspect that the photometric
 failure to produce an $Rp$ magnitude, as well as its poor astrometric
@@
 \label{subsec:groundphot}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=.47\textwidth]{f2b.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+		{\bf Ground-based follow-up photometry.} The data were acquired
+		using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C. Black points are
+		binned to 10-minute intervals.  The gray line is the best-fit
+		model to the combined TESS and ground-based data. Models show
+		$2\sigma$ lower limits on the transit depths in the Cousins-R and
+		Johnson-B bandpasses used to rule out specific false positive
+		scenarios (see Section~\ref{subsec:colorphot}).
+		\label{fig:groundphot}
+	}
+\end{figure}
 
@@
 we also manually excluded the two flares shown in
-Figure~\ref{fig:rawzoom}.  We then trimmed the TESS data to windows of
+Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows of
 $\pm 7\,{\rm hr}$ centered on each transit.

### 2020-07-10 drivers/fit_allindivtransit.py

@@ -32,8 +32,8 @@ def main(modelid):
     cornerplot = 1
     subsetcorner = 1
 
-    #N_samples = 30000 # took 26m, but Rhat=1.0 for all
-    N_samples = 2000
+    N_samples = 30000 # took 2h 20m, but Rhat=1.0 for all
+    # N_samples = 2000 # took 16m, 14s. but Rhat=1.01 for b, rp/rs, + a few a1/a2s
 
     OVERWRITE = 1
     REALID = 'TOI_837'

### 2020-07-10 drivers/plot_scene.py

@@ -43,7 +43,8 @@ def main():
 
     outpath = '../results/paper_plots/scene.png'
     plot_scene(c_obj, img_wcs, mean_img, outpath, ap_mask=ap_mask,
-               bkgd_mask=bkgd_mask, ticid=ticid, Tmag_cutoff=16)
+               bkgd_mask=bkgd_mask, ticid=ticid, Tmag_cutoff=16,
+               showdss=0)
 
 
 if __name__ == "__main__":

### 2020-07-10 paper/ms.tex
update manuscript

@@
   NASA TESS mission, the ESA Gaia mission, photometry from El Sauce
-  and ASTEP400,
-  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
-  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
-  star and validated planet are therefore $35^{+11}_{-5}$ million
-  years old.  The planet is warm ($P = 8.3\,{\rm d}$) and slightly
-  smaller than Jupiter.  Combining the transit photometry with a prior on the
-  stellar parameters derived from the cluster color-magnitude diagram,
-  we find that the transits are grazing with $b=0.93\pm0.01$ and
-  $R_{\rm p} = 0.79 \pm 0.07 \,R_{\rm Jup}$.  From radial velocity
-  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
-  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
-  they are usually indicative of astrophysical false positive
-  scenarios.  Our follow-up data show that such scenarios are highly
-  unlikely.  Our combined multi-color photometry, high-resolution
-  imaging, and radial velocities rule out hierarchical eclipsing
-  binary scenarios.  Background eclipsing binary scenarios, though
-  limited by speckle imaging, formally remain a 0.2\% possibility.
-  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
-  observations of its stellar obliquity, atmosphere, and mass should
-  confirm its planetary nature beyond doubt, and could improve our
-  understanding of how the physical and orbital properties of
-  exoplanets change in time.
+  and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
+  find that TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC
+  2602.  The star and planet are therefore $35^{+11}_{-5}$
+  million years old.  The planet is warm ($P = 8.3\,{\rm d}$) and
+  slightly smaller than Jupiter.  Combining the transit photometry
+  with a prior on the stellar parameters derived from the cluster
+  color-magnitude diagram, we find that the transits are grazing with
+  $b=0.93\pm0.01$ and $R_{\rm p} = 0.79 \pm 0.07 \,R_{\rm Jup}$.  From
+  radial velocity monitoring, we limit the minimum mass to less than
+  1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause for
+  concern, as they are usually indicative of astrophysical false
+  positive scenarios.  Our follow-up data show that such scenarios are
+  highly unlikely.  Our combined multi-color photometry,
+  high-resolution imaging, and radial velocities rule out hierarchical
+  eclipsing binary scenarios.  Background eclipsing binary scenarios,
+  though limited by speckle imaging, formally remain a 0.2\%
+  possibility.  TOI 837.01 is therefore a validated adolescent
+  exoplanet.  Further observations of its stellar obliquity,
+  atmosphere, and mass should confirm its planetary nature beyond
+  doubt, and could improve our understanding of how the physical and
+  orbital properties of exoplanets change in time.
 \end{abstract}
@@
 fully form within only a few million years
-\citep{dauphas_hf-w-th_2011}, they can also undergo significant
-growth over the next 10--100 million years through giant impacts
-\citep[{\it
+\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
+over the next 10--100 million years through giant impacts \citep[{\it
 e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
@@
     sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Starspot-induced variability is the dominant signal; flares
-    are shown with gray crosses.  Dashed lines indicate the five
-    transits observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed windows of
-    individual transits.  Gray lines are the best-fit transit model,
-    which includes a local quadratic trend in each window.
-    {\it Bottom}: Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
-    measurements with the local spot-induced variation removed.  Black
-    points are binned to 6-minute intervals. The black error-bar shows
-    the median uncertainty for the black points.  The gray line is the
-    best-fit model to the combined TESS and ground-based data
-    (Table~\ref{tab:posterior}). 
+    Starspot-induced variability is the dominant signal; flares are
+    shown with gray crosses.  Dashed lines indicate the five transits
+    observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed
+    windows of individual transits.  Gray lines are the best-fit
+    transit model, which includes a local quadratic trend in each
+    window.  {\it Bottom}: Phase-folded TESS transit. Gray points are
+    2-minute PDCSAP flux measurements with the local spot-induced
+    variation removed.  Black points are binned to 6-minute intervals.
+    The black error-bar shows the median uncertainty for the black
+    points.  The gray line is the best-fit model to the combined TESS
+    and ground-based data (Table~\ref{tab:posterior}). 
 		\label{fig:tessphot}
@@
 
-%TODO: you must check custom lightkurve apertures, too
-
-% %FIXME: this paragraph doesn't really belong here?
-% We examined the CDIPS FFI light curves of the target, which are
-% available on MAST \citep{bouma_cluster_2019}. Three light curves are
-% available, based on photometric apertures with a radius of 1, 1.5, or
-% 2.5 pixels.  In the raw difference-image light-curves, as well as the
-% PCA-detrended light-curves, dips of depth $\approx$0.35\% are visible,
-% and their properties do not significantly vary with aperture size.
-% Within $\approx20$'', the dips are consistent with originating from
-% the target star.
-
 \subsection{Gaia Astrometry and Imaging}
@@
 	\caption{ {\bf Scene of \tn.}
-    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
-    logarithmic grayscale. The yellow star is the position of \tn.
-    White circles are resolved Gaia sources with $T<16$ (brighter stars
-    are larger). The black \texttt{X} and white \texttt{/} hatches
-    show the apertures used to measure the background and target star
-    flux, respectively. Dashed lines of constant declination and right
-    ascension are shown.
-    Two stars of interest are ``Star A'' and ``Star B'', which were eventually excluded as being possible sources of the transits.
-    %{\it Bottom:} Digitized Sky Survey $R$-band
-   % image of the same field, with a linear grayscale. 
+    Mean TESS image of \tn\ over Sector~10, with a logarithmic
+    grayscale. The yellow star is the position of \tn.  White circles
+    are resolved Gaia sources with $T<16$ (brighter stars are larger).
+    The black \texttt{X} and white \texttt{/} hatches show the
+    apertures used to measure the background and target star flux,
+    respectively. Dashed lines of constant declination and right
+    ascension are shown.  Two stars of interest are ``Star A'' and
+    ``Star B'', which were eventually excluded as being possible
+    sources of the transits.
 		\label{fig:scene}
@@
 
-The Gaia imaging, reduced to its point-source catalog, provides
-the initial context for analyzing the TESS data.  Stars brighter than
+The Gaia imaging, reduced to its point-source catalog, provides the
+initial context for analyzing the TESS data.  Stars brighter than
 $T=16$, as queried from the Gaia DR2 source catalog, are shown with
-white circles in Figure~\ref{fig:scene}, overlaid on 
-the TESS image.  Given its galactic latitude of $b=-6^\circ$, it is
-not surprising that the field of \tn\ is crowded.  The resolved stars
-that were of immediate concern for our false positive analysis were as
-follows.
+white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
+Given its galactic latitude of $b=-6^\circ$, it is not surprising that
+the field of \tn\ is crowded.  The resolved stars that were of
+immediate concern for our false positive analysis were as follows.
 \begin{itemize}
@@
     proper motions and parallax of this star imply it is comoving with
-    \tn and is separated from it by $6.6\pm 0.1\,{\rm pc}$.
-    It is therefore likely an \cn\ member, but unlikely to be a bound
+    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
+    Star A is therefore likely an \cn\ member, but unlikely to be a bound
     binary compnaion.
@@
 \texttt{2020-07-08}. } value is available.  We suspect that the photometric
-failure to produce an $Rp$ magnitude, as well as its poor astrometric
-fit, are likely due to blending with \tn.
+failure to produce an $Rp$ magnitude as well as its poor astrometric
+fit are due to blending with \tn.
 
@@
 		\leavevmode
-		\includegraphics[width=.47\textwidth]{f2b.pdf}
+		\includegraphics[width=.49\textwidth]{f2b.pdf}
 	\end{center}
@@
 membership probability exceeding 10\%.  Most members appear to be
-young and coeval.
-\tn\ is in its expected position relative to the other members along
-the cluster isochrone.  This photometrically limits the presence of
-binary companions in the \tn\ system, to within perhaps half the
-brightness ($\approx0.75$ magnitudes) of the target star.
-
-Figure~\ref{fig:hr} suggests that the membership census of \cn\
-is incomplete.  We defined the reference ``neighborhood'' as the group
-of at most $10^4$ randomly selected non-member stars within 5 standard
+young and coeval.  \tn\ is in its expected position relative to the
+other members along the cluster isochrone.  This photometrically
+limits the presence of binary companions in the \tn\ system, to within
+perhaps half the brightness ($\approx0.75$ magnitudes) of the target
+star.
+
+Figure~\ref{fig:hr} suggests that the membership census of \cn\ is
+incomplete.  We defined the reference ``neighborhood'' as the group of
+at most $10^4$ randomly selected non-member stars within 5 standard
 deviations of the mean \cn\ right ascension, declination, and
@@
 Myr models align well with the data for stars with masses ranging from
-roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are
-bluer than observed in the Gaia photometry.  This discrepancy was noted and discussed at
-length by \citet{choi_mesa_2016}.  The most plausible explanation
-seems to be that strong magnetic fields in low-mass pre-main-sequence
-stars inhibit convection and produce a high filling factor of
-starspots \citep[{\it
+roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are bluer
+than observed in the Gaia photometry.  This discrepancy was noted and
+discussed at length by \citet{choi_mesa_2016}.  The most plausible
+explanation seems to be that strong magnetic fields in low-mass
+pre-main-sequence stars inhibit convection and produce a high filling
+factor of starspots \citep[{\it
 e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}. To conserve flux,
@@
 of][]{rebull_rotation_2020}.  Instead, we interpret the rotation
-period as evidence to support the claim that \tn\ is younger than $\sim$
-$500\,{\rm Myr}$.
+period as evidence to support the claim that \tn\ is younger than
+$\sim$ $500\,{\rm Myr}$.
 
@@
 
-%
-
 Select properties of \tn\ from the literature and our analysis are
@@
 In ``Method 1'', we measured spectroscopic parameters from each of the
-CHIRON spectra (Section~\ref{subsec:chiron}).
-We then calculated the stellar radius and reddening
-following \citet{stassun_accurate_2017}.  We first derived the
-bolometric flux by combining available broadband magnitudes from Gaia,
-Tycho-2, APASS, 2MASS, and WISE.  We then fitted the SED with the
-\citet{kurucz_atlas12_2013} stellar atmopshere models, and summed to
-find $F_{\rm bol}$.  When fitting the atmosphere model, we varied the
-extinction ($A_{\rm V}$) and the overall normalization.  This
-procedure yielded $A_{\rm V} = 0.20\pm0.03$, which agrees with the
-average from the \cn\ isochrone fits of \citet{randich_gaiaeso_2018}.
-Combining the spectroscopic effective temperature, bolometric flux,
-and Gaia distance, we determined the stellar radius using the
-Stefan-Boltzmann law.  Combining this radius with the spectroscopic
-$\log g$ also yields a stellar mass.
+CHIRON spectra (Section~\ref{subsec:chiron}).  We then calculated the
+stellar radius and reddening following \citet{stassun_accurate_2017}.
+We first derived the bolometric flux by combining available broadband
+magnitudes from Gaia, Tycho-2, APASS, 2MASS, and WISE.  We then fitted
+the SED with the \citet{kurucz_atlas12_2013} stellar atmopshere
+models, and summed to find $F_{\rm bol}$.  When fitting the atmosphere
+model, we varied the extinction ($A_{\rm V}$) and the overall
+normalization.  This procedure yielded $A_{\rm V} = 0.20\pm0.03$,
+which agrees with the average from the \cn\ isochrone fits of
+\citet{randich_gaiaeso_2018}.  Combining the spectroscopic effective
+temperature, bolometric flux, and Gaia distance, we determined the
+stellar radius using the Stefan-Boltzmann law.  Combining this radius
+with the spectroscopic $\log g$ also yields a stellar mass.
 
@@
 K}$, with relative uncertainties of a few percent on each). To avoid
-poorly understood systematics,  we adopted the stellar parameters
-from Method 2, and report them in Table~\ref{tab:starparams}.
+poorly understood systematics,  we adopted the stellar parameters from
+Method 2, and report them in Table~\ref{tab:starparams}.
 
@@
 we also manually excluded the two flares shown in
-Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows of
-$\pm 7\,{\rm hr}$ centered on each transit.
+Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
+of $\pm 7\,{\rm hr}$ centered on each transit.
 
@@
 shared across all transit windows, plus a local quadratic trend
-allowed within each window.  Select parameters and priors
-are listed in Table~\ref{tab:posterior}.  In brief, we fitted for the
-shared stellar parameters ($\log g, R_\star, u_0, u_1$), and the
-shared planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).
-There were also three free trend parameters for each of the twelve
-transits to account for the rotational variability.  This yielded a
-total of 44 free parameters, of which 8 have physical relevance, and
-36 are nuisance parameters.  To keep the table at a manageable length,
-we only report the physically relevant parameters and derived
-quantities.
+allowed within each window.  Select parameters and priors are listed
+in Table~\ref{tab:posterior}.  In brief, we fitted for the shared
+stellar parameters ($\log g, R_\star, u_0, u_1$), and the shared
+planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).  There
+were also three free trend parameters for each of the twelve transits
+to account for the rotational variability.  This yielded a total of 44
+free parameters, of which 8 have physical relevance, and 36 are
+nuisance parameters.  To keep the table at a manageable length, we
+only report the physically relevant parameters and derived quantities.
 
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Unlike these planets, \pn\ is validated but not yet
-confirmed.
+Unlike these planets, \pn\ is validated but not yet confirmed.
 
@@
 planet will be a Rossiter-McLaughlin (RM) measurement.  Detection of
-the RM signal would rule out BEB and HEB scenarios, as it would imply
-that the eclipsing object is bound to the target star. Combined with
-our non-detection of the planet's mass from radial velocity
-monitoring, this would confirm that \pn\ is a planet.
+an RM signal consistent with the photometric transit would rule out
+BEB and HEB scenarios, as it would imply that the eclipsing object is
+bound to the target star. Combined with our non-detection of the
+planet's mass from radial velocity monitoring, this would confirm that
+\pn\ is a planet.
 
@@
 %
-The Digitized Sky Survey was produced at the Space Telescope Science
-Institute under U.S. Government grant NAG W-2166.
-Figure~\ref{fig:scene} is based on photographic data obtained using
-the Oschin Schmidt Telescope on Palomar Mountain.
+% The Digitized Sky Survey was produced at the Space Telescope Science
+% Institute under U.S. Government grant NAG W-2166.
+% Figure~\ref{fig:scene} is based on photographic data obtained using
+% the Oschin Schmidt Telescope on Palomar Mountain.
 %

### 2020-07-10 paper/authors.tex
manuscript: add ASTEP methods

@@
 %
-% SG1 contributors: ask Karen -- are there others?
-%
-
-%
-% SG2 contributors
-%
-
-%PENDING
-\author[0000-0002-7595-0970]{C.~G.~Tinney}
-\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
-Sydney, NSW 2052, Australia}
-\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
-2052, Australia}
-
-%
 % Princeton team
@@
 	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+
+%
+% SG1 contributors
+%
+
+% begin (ASTEP team)
+\author{L. Abe} % Lyu
+\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}
+
+\author{A. Agabi} % Abdelkrim 
+\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}
+
+\author[0000-0001-7866-8738]{N. Crouzet} % Nicolas
+\affiliation{European Space Agency, European Space Research and Technology Centre (ESA/ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, The Netherlands}
+
+\author[0000-0002-3937-630X]{G. Dransfield} % Georgina
+\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
+
+\author[0000-0002-7188-8428]{T. Guillot} % Tristan 
+\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}
+
+\author{W. Marie-Sainte} % Wenceslas
+\affiliation{Institut Paul \’Emile Victor, Concordia Station, Antarctica}
+
+\author{D. M\'ekarnia} % Djamel
+\affiliation{Universit\'e C\^{o}te d'Azur, Observatoire de la C\^ote d'Azur, CNRS, Laboratoire Lagrange, Bd de l'Observatoire, CS 34229, 06304 Nice cedex 4, France}
+
+\author[0000-0002-5510-8751]{A. H.M.J. Triaud} % Amaury
+\affiliation{School of Physics \& Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
+% end (ASTEP team)
+
+%
+% SG2 contributors
+%
+
+%PENDING
+\author[0000-0002-7595-0970]{C.~G.~Tinney}
+\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
+Sydney, NSW 2052, Australia}
+\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
+2052, Australia}
 
@@
 
-\author{ASTEP400 collaboration}
 \author{TSO/SPOC/POC representatives}

### 2020-07-10 paper/ms.tex
manuscript: add ASTEP methods

@@
 
-\edit1{Amaury TODO: please correct as appropriate}
-We observed {\bf N} transits with the 0.40m ASTEP 400 telescope at
-Concordia Station, located at Dome C on the Antarctic Plateau
-\citep{daban_astep_2010}.  ASTEP 400 has a dichroic that sends blue
-wavelengths to a guiding camera, and red wavelengths to a filter-free
-science camera with wavelength sensitivity roughly akin to R band.
-The observations were acquired on the nights of {\bf DATE 1} and {\bf
-DATE 2}.  The outdoor temperature was a balmy {\bf XX$^\circ$}.  The
-data were reduced using {\bf XX} software, and showed the transit
-roughly at the expected time and depth.
+We observed three transits with the 0.40m ASTEP telescope at the Concordia base on the Antarctic Plateau
+\citep{daban_astep_2010}.  Concordia base is operated jointly by the
+French and Italian polar institutes, IPEV and PNRA.  Its position on
+the Antarctic Plateau at lat $75.06^\circ$S, long $123.3^\circ$E
+allows it to take advantage of the continuous night during Austral
+winter.  The weather is of photometric quality for about two-thirds of
+each winter \citep{crouzet_four_2018}.
+
+ASTEP is equipped with a FLI Proline science camera with a KAF-16801E,
+$4096\times4096$ front-illuminated CCD. The camera has an image scale
+of 0.93\,arcsec pixel$^{-1}$ resulting in a $1^{\circ}\times1^{\circ}$
+corrected field of view. The focal instrument dichroic plate splits
+the beam into a blue wavelength channel for guiding, and a
+non-filtered red science channel roughly matching a Cousins-R
+transmission curve
+\citep{abe_secondary_2013,mekarnia_transiting_2016}.
+The images were
+processed on-site using an automated aperture  photometry pipeline
+based on the \texttt{daophot} package of the IDL astronomy user's
+library \citep{landsman_1995}.
+
+\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
+2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure
+time of $25\,$s, readout and processed overhead of $25\,$s).
+Except for 12 May, our observations were conducted under stable
+weather conditions, with clear skies, temperatures of about
+$-70^\circ$C, and wind speeds inferior to 5\,ms$^{-1}$. Due to their
+poor quality, we exclude from the analysis all data collected on May
+12. We found that the optimal calibrated light curves of \tn\
+correspond to an 11 pixel (10\,arcsec) and 14 pixel (12\,arcsec)
+radius aperture for observations carried out on June and May,
+respectively.  The data are reported in Table~\ref{tab:phot}, and are
+plotted in Figure~\ref{fig:groundphot}.
 
@@
 
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 directorate.
+%
+We acknowledge support from the French and Italian Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI (ANR-15-IDEX-01).
+We thank the dedicated staff at Concordia for their continuous presence and support throughout the Austral winter.
+%
+This research received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement n$^\circ$ 803193/BEBOP), and from the Science and Technology Facilities Council (STFC; grant n$^\circ$ ST/S00193X/1).
 %
@@
   	exoplanet:theano}.
+	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
   \texttt{IPython} \citep{perez_2007},
@@
  	{\it Photometry}:
+ 	  ASTEP:0.40m (ASTEP400),
 % 	CTIO:1.0m (Y4KCam),
@@
 \input{TOI837_rv_table.tex}
-\clearpage
-
-\clearpage
+%\clearpage
+
+%\clearpage
 \bibliographystyle{yahapj}                            
@@
 
+%\allauthors
 \end{document}

### 2020-07-10 paper/ms.tex
update manuscript

@@
 
-\edit1{Phil + Karen TODO: please correct as appropriate}
-We scheduled the observations using {\bf \texttt{SOFTWARE}} (CITE).
-The photometric data were calibrated and extracted using the
-\texttt{AstroImageJ} software package
-\citep{collins_astroimagej_2017}.  Comparison stars of similar
-brightness were used to produce the final light curves, each of which
-showed a roughly 4$\,$ppt dip near the expected transit time.
+We scheduled our transit observations using the {\tt TESS Transit Finder}, which is a customized version
+of the {\tt Tapir} software package \citep{Jensen:2013}.  The photometric data were calibrated and
+extracted using \texttt{AstroImageJ} \citep{collins_astroimagej_2017}.
+Comparison stars of similar brightness were used to produce the final
+light curves, each of which showed a roughly 4$\,$ppt dip near the
+expected transit time.  The data are reported in Table~\ref{tab:phot}
+and plotted in Figure~\ref{fig:groundphot}.
 
@@
 sources of blended eclipsing binary signals.  Star B is resolved in
-the ground-based images; Star A is not.
+the 0.36m images; Star A is not.
 
@@
 would therefore need to have depth greater than unity to produce the
-observed eclipse depth.  We take the lack of a transit depth variation
-along these light curves as evidence that \tn\ is the source of the
-transit signal to within $\approx2.0''$.  The lack of variation of
-transit depth with aperture location is consistent with \tn\ being the
-source of transits, because the uncertainty of the transit depth
-measurements ($\approx 15\%$) is much greater than the maximum
-dilution from Star A ($\approx 1\%$).
+observed eclipse depth.  We therefore interpret the lack of asymmetry
+between the western-most (centered on Star A) and eastern-most
+(furthest from Star A) light curves as conclusive evidence that \tn\
+is the source of the transit signal to within $\approx2.0''$. 
+To verify self-consistency, we checked that the maximum dilution from Star A
+($\approx 1\%$) is less than the uncertainty of the transit depth
+measurements ($\approx 15\%$), and so the lack of variation of transit
+depth with aperture location is consistent with \tn\ being the source
+of transits.
 
@@
 \label{subsec:cluster}
-
-\input{ic2602_ages.tex}
 
@@
 %\clearpage
+
+\input{ic2602_ages.tex}
 \input{starparams.tex}

### 2020-07-13 paper/ms.tex
update manuscript

@@
 % * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
-% text. G0V has been assumed.
+% text. G0/F9V has been assumed.
 % * remove all bf todo's
@@
   and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
-  find that TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC
-  2602.  The star and planet are therefore $35^{+11}_{-5}$
+  find that TOI$\,$837 is a $T=9.9$ G0/F9 dwarf in the southern open
+  cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
   million years old.  The planet is warm ($P = 8.3\,{\rm d}$) and
@@
   color-magnitude diagram, we find that the transits are grazing with
-  $b=0.93\pm0.01$ and $R_{\rm p} = 0.79 \pm 0.07 \,R_{\rm Jup}$.  From
-  radial velocity monitoring, we limit the minimum mass to less than
-  1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause for
-  concern, as they are usually indicative of astrophysical false
-  positive scenarios.  Our follow-up data show that such scenarios are
-  highly unlikely.  Our combined multi-color photometry,
+  $b=0.95\pm0.01$ and $R_{\rm p} = 0.80^{+0.04}_{-0.03} \,R_{\rm
+  Jup}$.  From radial velocity monitoring, we limit the minimum mass
+  to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a
+  cause for concern, as they are usually indicative of astrophysical
+  false positive scenarios.  Our follow-up data show that such
+  scenarios are highly unlikely.  Our combined multi-color photometry,
   high-resolution imaging, and radial velocities rule out hierarchical
@@
 A number of other processes are expected to shape young exoplanets.
-Planets with gaseous envelopes are thought to shrink as they contract
-and as their atmospheres undergo photoevaporation \citep[{\it
+After accreting, planets with gaseous envelopes are thought to cool
+and contract, and their atmospheres are expected to undergo
+photoevaporation \citep[{\it
 e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
@@
 \citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
-hints that young planets may in fact be qualtiatively different from
+hints that young planets in clusters may in fact be qualitatively different from
 their field counterparts.  For instance, based on its observed mass,
@@
     The black error-bar shows the median uncertainty for the black
-    points.  The gray line is the best-fit model to the combined TESS
-    and ground-based data (Table~\ref{tab:posterior}). 
+    points.  The gray line is the best-fit model to the TESS
+    data. 
 		\label{fig:tessphot}
@@
 \end{figure*}
-
-% \begin{figure*}[!t]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=.85\textwidth]{f1.pdf}
-% 	\end{center}
-% 	\vspace{-0.7cm}
-% 	\caption{
-%     {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
-%     \texttt{PDCSAP} median-subtracted relative flux at 2-minute
-%     sampling in units of parts-per-thousand ($\times 10^{-3}$).
-%     Starspot-induced variability is the dominant signal; flares
-%     are shown with gray crosses.  Dashed lines indicate the five
-%     transits observed by TESS.  {\it Bottom}: Zoomed windows of
-%     individual transits.  Gray lines are the best-fit transit model,
-%     which includes a local quadratic trend in each window.
-% 		\label{fig:rawzoom}
-% 	}
-% \end{figure*}
-
-% \begin{figure}[!t]
-% 	\begin{center}
-% 		\leavevmode
-% 		\includegraphics[width=.47\textwidth]{f2a.pdf}
-% 	\end{center}
-% 	\vspace{-0.7cm}
-% 	\caption{
-%     {\bf Phase-folded TESS transit.} Gray points are 2-minute PDCSAP flux
-%     measurements with the local spot-induced variation removed.  Black
-%     points are binned to 6-minute intervals. The black error-bar shows
-%     the median uncertainty for the black points.  The gray line is the
-%     best-fit model to the combined TESS and ground-based data
-%     (Table~\ref{tab:posterior}). 
-% 		\label{fig:phasefold}
-% 	}
-% \end{figure}
 
@@
 \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
-\texttt{2020-07-08}. } value is available.  We suspect that the photometric
-failure to produce an $Rp$ magnitude as well as its poor astrometric
-fit are due to blending with \tn.
+\texttt{2020-07-08}. } value is available.  We suspect that the
+photometric failure to produce an $Rp$ magnitude as well as its poor
+astrometric fit are due to blending with \tn.
 
@@
 \citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
-by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:followup}
-show the resulting measured 5-$\sigma$ detectable contrasts.  The
-lines are linear smoothing fits between the regimes of the diffraction
-limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
-$\approx 1.5''$, beyond which the speckle patterns become
-de-correlated.  Star A (TIC 847769574) was detected at the expected
-location and brightness contrast, and no additional companions were
-found.  Star B was not detected; with a separation of $5.4''$ from
-\tn, it fell outside the field of view.
+by \citet{tokovinin_ten_2018}.  The points in
+Figure~\ref{fig:followup} show the resulting measured 5-$\sigma$
+detectable contrasts.  The lines are linear smoothing fits between the
+regimes of the diffraction limit, the ``knee'' at $\approx 0.2''$, and
+the slow decrease until $\approx 1.5''$, beyond which the speckle
+patterns become de-correlated.  Star A (TIC 847769574) was detected at
+the expected location and brightness contrast, and no additional
+companions were found.  Star B was not detected; with a separation of
+$5.4''$ from \tn, it fell outside the field of view.
 
@@
     {\bf Ground-based follow-up photometry.} The data were acquired
-		using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C. Black points are
-		binned to 10-minute intervals.  The gray line is the best-fit
-		model to the combined TESS and ground-based data. Models show
-		$2\sigma$ lower limits on the transit depths in the Cousins-R and
-		Johnson-B bandpasses used to rule out specific false positive
-		scenarios (see Section~\ref{subsec:colorphot}).
+    using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C.
+    Black points are binned to 10-minute intervals.  The gray line is
+    the best-fit model to the combined TESS and ground-based data.
+    Red and blue lines show $2\sigma$ lower limits on the transit depths in the
+    Cousins-R and Johnson-B bandpasses used to rule out specific false
+    positive scenarios (see Section~\ref{subsec:colorphot}).
 		\label{fig:groundphot}
@@
 
-We scheduled our transit observations using the {\tt TESS Transit Finder}, which is a customized version
-of the {\tt Tapir} software package \citep{Jensen:2013}.  The photometric data were calibrated and
+We scheduled our transit observations using the {\tt TESS Transit
+Finder}, which is a customized version of the {\tt Tapir} software
+package \citep{Jensen:2013}.  The photometric data were calibrated and
 extracted using \texttt{AstroImageJ} \citep{collins_astroimagej_2017}.
@@
 Based solely on the TESS data, both Star A and Star B were possible
-sources of blended eclipsing binary signals.  Star B is resolved in
-the 0.36m images; Star A is not.
+sources of blended eclipsing binary signals.  The typical FWHM for
+stars in the El Sauce observations was $\approx 2.3''$, with a
+variance of $\approx 0.2''$.  Star B is resolved in the 0.36m images;
+Star A is not.
 
@@
 (furthest from Star A) light curves as conclusive evidence that \tn\
-is the source of the transit signal to within $\approx2.0''$. 
-To verify self-consistency, we checked that the maximum dilution from Star A
-($\approx 1\%$) is less than the uncertainty of the transit depth
-measurements ($\approx 15\%$), and so the lack of variation of transit
-depth with aperture location is consistent with \tn\ being the source
-of transits.
+is the source of the transit signal to within $\approx2.0''$.  To
+verify self-consistency, we checked that the maximum dilution from
+Star A ($\approx 1\%$) is less than the uncertainty of the transit
+depth measurements ($\approx 15\%$), and so the lack of variation of
+transit depth with aperture location is consistent with \tn\ being the
+source of transits.
 
@@
 
-We observed three transits with the 0.40m ASTEP telescope at the Concordia base on the Antarctic Plateau
-\citep{daban_astep_2010}.  Concordia base is operated jointly by the
-French and Italian polar institutes, IPEV and PNRA.  Its position on
-the Antarctic Plateau at lat $75.06^\circ$S, long $123.3^\circ$E
-allows it to take advantage of the continuous night during Austral
-winter.  The weather is of photometric quality for about two-thirds of
-each winter \citep{crouzet_four_2018}.
+We observed three transits with the 0.40m ASTEP telescope at the
+Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
+Concordia base is operated jointly by the French and Italian polar
+institutes, IPEV and PNRA.  Its position on the Antarctic Plateau at
+lat $75.06^\circ$S, long $123.3^\circ$E allows it to take advantage of
+the continuous night during Austral winter.  The weather is of
+photometric quality for about two-thirds of each winter
+\citep{crouzet_four_2018}.
 
@@
 transmission curve
-\citep{abe_secondary_2013,mekarnia_transiting_2016}.
-The images were
+\citep{abe_secondary_2013,mekarnia_transiting_2016}.  The images were
 processed on-site using an automated aperture  photometry pipeline
@@
 \tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
-2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure
-time of $25\,$s, readout and processed overhead of $25\,$s).
-Except for 12 May, our observations were conducted under stable
-weather conditions, with clear skies, temperatures of about
-$-70^\circ$C, and wind speeds inferior to 5\,ms$^{-1}$. Due to their
-poor quality, we exclude from the analysis all data collected on May
-12. We found that the optimal calibrated light curves of \tn\
-correspond to an 11 pixel (10\,arcsec) and 14 pixel (12\,arcsec)
-radius aperture for observations carried out on June and May,
-respectively.  The data are reported in Table~\ref{tab:phot}, and are
-plotted in Figure~\ref{fig:groundphot}.
+2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
+of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
+May, our observations were conducted under stable weather conditions,
+with clear skies, temperatures of about $-70^\circ$C, and wind speeds
+inferior to 5\,ms$^{-1}$. Due to their poor quality, we exclude from
+the analysis all data collected on May 12. We found that the optimal
+calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
+and 14 pixel (12\,arcsec) radius aperture for observations carried out
+on June and May, respectively.  The data are reported in
+Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.
 
@@
 	\caption{
-    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
+    {\bf Follow-up speckle-imaging and velocimetry of \tn.} {\it Top:}
     SOAR HRCam contrast limits derived from point-source
-    injection-recovery experiments. Star A ($\Delta
-    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
-    and is also a resolved Gaia source.  It is co-moving with \tn, and
-    its parallax and on-sky position imply that it is physically
-    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
-    Radial velocity (RV) measurements, with best-fit instrument
-    offsets and jitter terms included.  The expected scatter from
-    starspots based on $v\sin i$ and the photometric modulation
-    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
-    measurements phased to the orbital ephemeris of \pn.  The planet
-    is not detected.  The black line shows a circular Keplerian orbit
-    representing the $3\sigma$ upper mass limit.
+    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
+    west) is detected in the autocorrelation function, and is also a
+    resolved Gaia source.  It is co-moving with \tn, and its parallax
+    and on-sky position imply that it is physically separated from
+    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
+    (RV) measurements, with best-fit instrument offsets and jitter
+    terms included.  The expected scatter from starspots based on
+    $v\sin i$ and the photometric modulation amplitude is of order
+    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
+    orbital ephemeris of \pn.  The planet is not detected.  The black
+    line shows a circular Keplerian orbit representing the $3\sigma$
+    upper mass limit.
 		\label{fig:followup}
@@
 	\caption{
-		{\bf Astrophysical false positive scenarios.}
-    {\it Top}: for bound companions (EB and HEB scenarios),
-		{\it Bottom}: for unassociated companions along the same line of
-    sight (BEB scenarios).
-		Each constraint is described in Section~\ref{subsec:fp_constraints}.
+    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
+    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
+    companions along the same line of sight (BEB scenarios).  Each
+    constraint is described in Section~\ref{subsec:fp_constraints}.
     Gray regions are ruled out by at least one constraint.
@@
 While the above constraints rule out HEBs, certain configurations of
-BEB systems ({\it e.g.}, a background G2V+K6V binary) can produce blue
+BEB systems ({\it e.g.}, a background G0V+K3V binary) can produce blue
 eclipses while remaining undetected along the line of sight.  Such
@@
 \citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
-indicative that there are no obviously present astometric companions.
+indicative that there are no obviously present astrometric companions.
 The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
@@
 \citep[][Appendix A]{lindegren_gaiasoln_2018}.
-
-% chi2AL is 526.88
-% NgAL is 276
-% so, well, reduced chi2 is ~2, which seems bad. but it might (in fact,
-% probably is) be because of the color-dependent stuff in the Gaia PSF
-% model. Most Rp=10 PTFO members had red chi2 of at least 2.
-% Also, looking at Lindegren+2018 Fig A.1., sqrt(reduced chi2) ~= 1.4
-% is expected.
-%
-% --> you could still create the same RUWE vs cluster membership
-%  diagnostic plot, just to be sure.
 
@@
 
-% 151 T<15.1 stars within 360 arcseconds
-% 298 T<16.0 stars within 360 arcseconds
 The constraints on false-positive scenarios summarized in
@@
 
-%
-
 \begin{figure}[!t]
@@
     size ratio, and stellar density.} The  planet-to-star size ratio
-    corresponds to a planet size between $0.65\,R_{\rm Jup}$ and
-    $0.91\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
+    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
+    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
     This plot was made using \texttt{corner} \citep{corner_2016}.
@@
 
-We fitted the available time-series photometry of \pn\ as follows.
+We also fitted the available time-series photometry of \pn\ using two
+different approaches.  To derive the most precise possible ephemeris,
+we fitted the ground and space-based transits simultaneously.  To the
+derive the physical parameters of the planet, we fitted the TESS data
+alone, due to our better understanding of the underlying systematic
+trends and the higher precision.
+
 For the PDCSAP light curve, we first eliminated points that had
@@
 
-Our joint model for the TESS and ground-based data was an
+Our model for time-series photometry data was an
 \citet{exoplanet:agol19} transit with physical and orbital parameters
@@
 allowed within each window.  Select parameters and priors are listed
-in Table~\ref{tab:posterior}.  In brief, we fitted for the shared
-stellar parameters ($\log g, R_\star, u_0, u_1$), and the shared
-planetary parameters ($t_0, P, b, \log(R_{\rm p}/R_\star)$).  There
-were also three free trend parameters for each of the twelve transits
-to account for the rotational variability.  This yielded a total of 44
-free parameters, of which 8 have physical relevance, and 36 are
-nuisance parameters.  To keep the table at a manageable length, we
-only report the physically relevant parameters and derived quantities.
+in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
+fitted for the shared stellar parameters ($\log g, R_\star, u_0,
+u_1$), and the shared planetary parameters ($t_0, P, b, \log(R_{\rm
+p}/R_\star)$).  There were also three free trend parameters for each
+transit window to account for the local rotational variability.  In
+the TESS-only model this yielded 23 free parameters, of which 8 were
+physically relevant and 15 were nuisance parameters.  In the combined
+TESS and ground-based model, there were an additional 7 transits, and
+therefore an additional 21 nuisance parameters for a total of 44 free
+parameters.
 
@@
 
-While alternative approaches are available for simultaneously fitting
-space and ground based photometry (in addition to radial velocimetry),
-we opted for this approach because {\it i)} the radial velocimetry on
-its own did not show evidence for a planetary signal, {\it ii)} we
-expected that this approach would provide the best measurement of the
-planetary ephemeris, which is key for follow-up efforts, and {\it
-iii)} the assumption of identical limb-darkening across all bandpasses
-seemed justified by the level of precision in the ground-based data.
-The assumption of a constant radius across all bandpasses was tested
-by independently fitting each ground-based transit while letting the
-planetary radius float (Section~\ref{subsec:colorphot}). The transit
-depths did not significantly change between different bandpasses.
-
-The posteriors from this procedure are given in
-Table~\ref{tab:posterior}.  The transit is grazing.  In the absence of
-a strong prior on the stellar density, the grazing geometry would
-hinder our ability to infer the planet-to-star size ratio.  However,
-our priors on the stellar parameters from the cluster isochrone fit
-are strong enough that we can derive two-sided limits on the
-planet-to-star size ratio.  The relevant posterior probabilities are
-shown in Figure~\ref{fig:subsetcorner}.
-
-% The available data for \tn\ put us in an odd position. The transit
-% data provide a minimum size due to the grazing geometry; the radial
-% velocity data provide a maximum mass ($\approx$1.20 $M_{\rm jup}$).
-% We could combine the two with an empirically-calibrated planetary
-% mass-radius relation to force a more restrictive upper bound on the
-% planetary size \citep[{\it e.g.},][]{chen_probabilistic_2016}.  The
-% result of such an exercise would tautologically be that the planet
-% would be smaller than the largest known Jovian planets ($\approx
-% 2R_{\rm Jup}$).  This would also imply that the impact parameter is
-% slightly below unity.  The planet's size, in our eyes, would remain
-% poorly constrained even if we were to do this exercise, so we opt to 
-% fit the photometry and radial velocities separately, to ensure clarity
-% about which datasets are providing which constraints.
+We opted for this approach rather than a joint fit of the photometry
+and radial velocities because the RVs on their own did not show
+evidence for a planetary signal.  Our preference for using only the
+TESS data to derive the transit parameters was in our view justified
+by the systematic uncertainties inherent to ground-based light curve
+production, particularly in comparison star selection.  Our assumption
+of a constant radius across all bandpasses was tested by independently
+fitting each ground-based transit while letting the planetary radius
+float (Section~\ref{subsec:colorphot}). The transit depths did not
+significantly change between different bandpasses.
+
+The posteriors from fitting the TESS data alone are given in
+Table~\ref{tab:posterior}.  Both approaches show that the transit is
+nearly grazing.   The relevant posterior probabilities are shown in
+Figure~\ref{fig:subsetcorner}.  To be precise, some of the posterior
+has $b < 1 - R_{\rm p}/R_\star$ and therefore formally is not grazing,
+and some of the posterior formally is grazing. For short-hand
+convenience, we refer to this as grazing.  From experimenting with the
+fits, we found that in the absence of a strong prior on the stellar
+density, the inherent degeneracy between the impact parameter and
+planet-to-star size ratio would have been much stronger.  However, our
+priors on the stellar parameters from the cluster isochrone fit are
+strong enough that we can derive two-sided limits on the
+planet-to-star size ratio.
 
@@
 Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
-challenging, for a 1.84$\,$hr transit of a $V=10.6$ star, a detection
+challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
 could be achieved with modern spectrographs.  The next viable total
@@
 there are also a few visible per season from other southern locations.
+The most precise available ephemeris, found from our joint fit of the
+TESS and ground-based photometry, is as follows.
+\begin{align}
+  t_0\ [{\rm BJD_{TDB}}] &= 2458574.2725293 \pm 0.0005870 \\
+  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \\
+  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
+\end{align}
 
@@
 
-If the RM measurements prove that the planet
-is real, a campaign to measure the mass timed to coincide with
-TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
-2021) would significantly ease the extraction of the planetary Doppler
-signal.  The reason is that the radial velocities, activity
-indicators, and photometry could then be modeled simultaneously, which
-would greatly constrain a Gaussian process model for the
-spot-induced RV signal.
+If the RM measurements prove that the validated planet is real, a
+campaign to measure the mass timed to coincide with TESS sectors 36
+and 37 ({\it i.e.}, from late March to late May of 2021) would
+significantly ease the extraction of the planetary Doppler signal.
+The reason is that the radial velocities, activity indicators, and
+photometry could then be modeled simultaneously, which would greatly
+constrain a Gaussian process model for the spot-induced RV signal.
 

### 2020-07-13 paper/ms.tex
update manuscript

@@
 Concordia base is operated jointly by the French and Italian polar
-institutes, IPEV and PNRA.  Its position on the Antarctic Plateau at
-lat $75.06^\circ$S, long $123.3^\circ$E allows it to take advantage of
+institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
+allows it to take advantage of
 the continuous night during Austral winter.  The weather is of
@@
 
-		\vspace{-0.5cm}
+		\vspace{-0.3cm}
 		\subfloat{
-			\includegraphics[width=0.46\textwidth]{f3.pdf}
+			\includegraphics[width=0.47\textwidth]{f3.pdf}
 		}
@@
 	\caption{
-    {\bf Follow-up speckle-imaging and velocimetry of \tn.} {\it Top:}
+    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:}
     SOAR HRCam contrast limits derived from point-source
     injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
-    west) is detected in the autocorrelation function, and is also a
+    west) is detected, and is also a
     resolved Gaia source.  It is co-moving with \tn, and its parallax
@@
 \subsubsection{FEROS}
-We acquired 13 spectra using the FEROS echelle spectrograph, mounted
-on the MPG 2.2m telescope at the European Soutern Observatory in La
-Sille, Chile \citep{kaufer_commissioning_1999}.  FEROS has a
-resolution of $\approx 48{,}000$ across a spectra range of
-350--920$\,$nm. It has a remarkably high efficiency of $\approx 20\%$.
-
-We used the dedicated instrument pipeline to extract 1-dimensional,
-wavelength calibrated spectra.  To measure radial velocities, \edit1{
-Rafael/Paula TODO: what procedure was used?  What software packages?}.  The
-velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:followup}.
+TOI 837.01 was monitored with the FEROS echelle spectrograph
+\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2m telescope
+at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
+$\approx$48,000 across a spectral range of 350–920 nm. It has a
+remarkably high efficiency of $\approx$20\%. We obtained 13 spectra of
+\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
+Warm gIaNts with tEss (WINE) collaboration, which focuses on the
+systematic characterization of TESS transiting giant planets with
+moderately long orbital periods \citep[{\it
+e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
+and 600 seconds and the observations were performed with the
+simultaneous calibration mode for tracing the instrumental velocity
+variations with a comparison fiber illuminated with a ThAr lamp. FEROS
+data was processed with the \texttt{ceres} pipeline
+\citep{brahm_2017_ceres}, which delivers precision radial velocities
+and bisector span measurements through cross-correlation of the
+extracted spectra with a binary mask resembling the properties of a
+G2V star. The radial velocities are given in Table~\ref{tab:rvs},
+and shown in Figure~\ref{fig:followup}.
 
@@
 In the ``Rosso'' instrument-mode, Veloce provides coverage from
-600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.
-
-Many of the exposures were taken in average or poor seeing conditions,
-when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
+600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
+of the exposures were taken in average or poor seeing conditions, when
+fiber-to-fiber cross-contamination on the IFU-style fiber feed is
 strongest.  To reduce the spectra to velocities, we cross-correlated
 against a high S/N template of $\delta$ Pavonis.  The velocity RMS
-seen across each visit was hundreds of meters per second, likely due to
-uncorrected fiber-to-fiber cross-contamination.  For
-analysis purposes, we averaged across each visit, and set the velocity
+seen across each visit was hundreds of meters per second, likely due
+to uncorrected fiber-to-fiber cross-contamination.  For analysis
+purposes, we averaged across each visit, and set the velocity
 uncertainties to be the standard deviation of the per-visit exposures.
@@
 The posteriors from fitting the TESS data alone are given in
-Table~\ref{tab:posterior}.  Both approaches show that the transit is
-nearly grazing.   The relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  To be precise, some of the posterior
-has $b < 1 - R_{\rm p}/R_\star$ and therefore formally is not grazing,
-and some of the posterior formally is grazing. For short-hand
-convenience, we refer to this as grazing.  From experimenting with the
-fits, we found that in the absence of a strong prior on the stellar
-density, the inherent degeneracy between the impact parameter and
-planet-to-star size ratio would have been much stronger.  However, our
-priors on the stellar parameters from the cluster isochrone fit are
-strong enough that we can derive two-sided limits on the
-planet-to-star size ratio.
-
-% TODO: decide whether to include this. it's not necessary!
-% \subsubsection{Additional Transits}
-% None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
-% spikes at BTJD 1572 and 1601) seem likely to be planetary
-% We checked that i) they were not present in the SAPFLUX light-curves,
-% and ii) that they were not present in the CDIPS light-curves (either
-% raw, or PCA-detrended).
-% To make this quantitative, we did injection-recovery(?)
+Table~\ref{tab:posterior}.  The condition for a grazing transit is
+whether the impact parameter is below $1 - R_{\rm p}/R_\star$.  The
+transit is therefore either grazing, or nearly grazing.   The relevant
+posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
+From experimenting with the priors, we found that in the absence of a
+strong prior on the stellar density, the inherent degeneracy between
+the impact parameter and planet-to-star size ratio would have been
+much stronger.  In the absence of precise information about the star,
+a larger fraction of the posterior would therefore have been grazing.
+However, our priors on the stellar parameters from the cluster
+isochrone fit break this degeneracy, enabling us to report two-sided
+limits on the planet-to-star size ratio.
 
@@
   %\texttt{BATMAN} \citep{kreidberg_batman_2015},
-  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
+  \texttt{ceres} \citep{brahm_2017_ceres},
+  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
   \texttt{corner} \citep{corner_2016},
@@
   dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
-  	exoplanet:theano}.
+  	exoplanet:theano},
 	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},

### 2020-07-13 paper/authors.tex
update manuscript

@@
 \author{P. Sarkis} %Paula sarkis@mpia.de PI of FEROS time
-\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
 
@@
 \author{W. Marie-Sainte} % Wenceslas
-\affiliation{Institut Paul \’Emile Victor, Concordia Station, Antarctica}
+\affiliation{Institut Paul \'{E}mile Victor, Concordia Station, Antarctica}
 
@@
 \author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
-\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
 
 \author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
-\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
+\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
 \affiliation{Millennium Institute for Astrophysics, Chile}
@@
 \author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
-\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
+\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
 \affiliation{Millennium Institute for Astrophysics, Chile}
@@
 \author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
-\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
+\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }
 

### 2020-07-13 paper/ms.tex
update manuscript

@@
 
-\suppressAffiliations
+%\suppressAffiliations
 %\NewPageAfterKeywords
@@
   transiting planet.  We characterize the system using data from the
-  NASA TESS mission, the ESA Gaia mission, photometry from El Sauce
+  NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce
   and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
@@
   cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
-  million years old.  The planet is warm ($P = 8.3\,{\rm d}$) and
-  slightly smaller than Jupiter.  Combining the transit photometry
+  million years old. Combining the transit photometry
   with a prior on the stellar parameters derived from the cluster
-  color-magnitude diagram, we find that the transits are grazing with
-  $b=0.95\pm0.01$ and $R_{\rm p} = 0.80^{+0.04}_{-0.03} \,R_{\rm
-  Jup}$.  From radial velocity monitoring, we limit the minimum mass
-  to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a
-  cause for concern, as they are usually indicative of astrophysical
-  false positive scenarios.  Our follow-up data show that such
-  scenarios are highly unlikely.  Our combined multi-color photometry,
-  high-resolution imaging, and radial velocities rule out hierarchical
-  eclipsing binary scenarios.  Background eclipsing binary scenarios,
-  though limited by speckle imaging, formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent
-  exoplanet.  Further observations of its stellar obliquity,
-  atmosphere, and mass should confirm its planetary nature beyond
-  doubt, and could improve our understanding of how the physical and
-  orbital properties of exoplanets change in time.
+  color-magnitude diagram, we find that the 
+  planet is warm ($P = 8.3\,{\rm d}$) and
+  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$). 
+  The transits are either grazing or nearly grazing.  From radial velocity
+  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
+  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
+  they are usually indicative of astrophysical false positive
+  scenarios.  Our follow-up data show that such scenarios are highly
+  unlikely.  Our combined multi-color photometry, high-resolution
+  imaging, and radial velocities rule out hierarchical eclipsing
+  binary scenarios.  Background eclipsing binary scenarios, though
+  limited by speckle imaging, formally remain a 0.2\% possibility.
+  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
+  observations of its stellar obliquity, atmosphere, and mass should
+  confirm its planetary nature beyond doubt, and could improve our
+  understanding of how the physical and orbital properties of
+  exoplanets change in time.
 \end{abstract}
@@
 photoevaporation \citep[{\it
-e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
-relative importance of contraction and photoevaporation is set by the
-planetary mass, as well as the radiation environment.  The
+e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
+The relative importance of contraction and photoevaporation is set by
+the planetary mass, as well as the radiation environment.  The
 effectiveness of photoevaporation can be inferred from observations of
@@
 e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
-Young field stars can also be identified using age indicators such as
+Young field stars can also be identified
+isochronally, provided that they are sufficiently massive \citep{berger_gaia-kepler_2020}. 
+Other age indicators include
 stellar rotation periods, the abundance of photospheric lithium, and
@@
 emission.  Studies by for instance \citet{david_discovery_2018} and
-G{.}~Zhou et al. (2020, submitted) have combined these methods for
-individual field stars.  Many of the latter methods were summarized by
+G{.}~Zhou et al. (2020, submitted) have combined these methods to age-date
+individual field stars hosting transiting planets.  Many of these latter methods were summarized by
 \citet{mamajek_improved_2008}, and have since been calibrated by {\it
@@
 Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.
+
+\input{TOI837_phot_table.tex}
 
@@
 Figure~\ref{fig:followup}.
+
+\input{TOI837_rv_table.tex}
 
@@
 
+\input{ic2602_ages.tex}
+
 \subsubsection{Physical Characteristics}
@@
 
+\input{starparams.tex}
+
 \subsubsection{Membership of \tn\ in \cn}
@@
 $v$ of the star would be $17.67 \pm 0.32 \,{\rm km\,s}^{-1}$.  Our
-spectroscopically measured $v\sin i$ from CHIRON, $17.48 \pm 0.15
+spectroscopically measured $v\sin i$ from CHIRON, $16.2 \pm 1.1
 \,{\rm km\,s}^{-1}$ agrees reasonably well with this expectation.
@@
 \begin{align}
-  t_0\ [{\rm BJD_{TDB}}] &= 2458574.2725293 \pm 0.0005870 \\
-  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \\
+  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272529 \pm 0.000587 \nonumber \\
+  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \nonumber \\
   T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
@@
 
-\clearpage
+% \clearpage
 
@@
 
-% \clearpage
-%\clearpage
-
-\input{ic2602_ages.tex}
-\input{starparams.tex}
-%\clearpage
-\input{model_posterior_table.tex}
+% \input{ic2602_ages.tex}
+% \input{starparams.tex}
+% \input{model_posterior_table.tex}
+% \input{TOI837_phot_table.tex}
+% \input{TOI837_rv_table.tex}
+
 \clearpage
-\input{TOI837_phot_table.tex}
-\input{TOI837_rv_table.tex}
-%\clearpage
-
-%\clearpage
 \bibliographystyle{yahapj}                            

### 2020-07-13 drivers/abbreviate_the_bibliography.py

@@ -1,0 +1,35 @@
+"""
+Zotero generates long journal names. Abbreviate them in bulk to conform to the
+AAS style guide.
+"""
+
+from collections import OrderedDict
+
+mdict = OrderedDict({})
+
+mdict['The Astrophysical Journal Letters'] = r'\apjl'
+mdict['The Astrophysical Journal Supplement Series'] = r'\apjs'
+mdict['The Astronomical Journal'] = r'\aj'
+mdict['Annual Review of Astronomy and Astrophysics'] = r'\araa'
+mdict['The Astrophysical Journal'] = r'\apj'
+mdict['Publications of the Astronomical Society of the Pacific'] = r'\pasp'
+mdict['Astronomy and Astrophysics'] = r'\aap'
+mdict['Astronomy & Astrophysics'] = r'\aap'
+mdict['Monthly Notices of the Royal Astronomical Society: Letters'] = r'\mnras:l'
+mdict['Monthly Notices of the Royal Astronomical Society'] = r'\mnras'
+mdict['Nature'] = r'\nat'
+
+with open('../paper/bibliography.bib', 'r') as f:
+    lines = f.readlines()
+
+for k,v in mdict.items():
+    for ix, l in enumerate(lines):
+        if k in l:
+            _newline = l.replace(k, v)
+            lines[ix] = _newline
+
+outpath = 'abbrevbib.bib'
+with open(outpath, 'w') as f:
+    f.writelines(lines)
+
+print('made {}'.format(outpath))

### 2020-07-13 drivers/fit_tessindivtransit.py

@@ -98,9 +98,9 @@ def main(modelid):
     printparams = ['r_planet', 'b']
     print(42*'-')
     for p in printparams:
-        med = np.percentile(m.trace[p], 100*0.5)
-        up = np.percentile(m.trace[p], 100*0.6827)
-        low = np.percentile(m.trace[p], 100*(1-0.6827))
+        med = np.percentile(m.trace[p], 50)
+        up = np.percentile(m.trace[p], 84)
+        low = np.percentile(m.trace[p], 36)
         print(f'{p} limit: {med:.3f} +{up-med:.3f} -{med-low:.3f}')
     print(42*'-')
 

### 2020-07-14 paper/ms.tex
add da figure

@@
 
-\input{starparams.tex}
+%\input{starparams.tex}
 
@@
 
-\input{model_posterior_table.tex}
+%\input{model_posterior_table.tex}
 
@@
 
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=0.48\textwidth]{f11.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Planet radius versus age, for the known transiting planets.} 
+    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
+    were queried from the NASA Exoplanet Archive on 13 July 2020.
+    Precise ages are known for only a small fraction of the gray points.
+		\label{fig:rpvsage}
+	}
+\end{figure}
+
 \tn\ joins a number of other young planetary systems reported from
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Unlike these planets, \pn\ is validated but not yet confirmed.
+Figure~\ref{fig:rpvsage} shows \tn\ in the space of planets sizes and ages.
+\tn\ is among the youngest transiting planets known, which was the
+primary motivation for this study.
+While we have statistically validated that \tn\ seems to be a planet,
+the possibility that it is a background eclipsing binary has not
+been excluded with sufficient confidence to call the planet ``confirmed''.
 
@@
 \begin{align}
-  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272529 \pm 0.000587 \nonumber \\
-  P\ [{\rm d}] &= 8.3248764 \pm 0.0000155 \nonumber \\
+  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
+  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
   T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
 \end{align}
+% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex
 
@@
 
-% \clearpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\clearpage
+\clearpage
 \acknowledgements
@@
 Administration under the Exoplanet Exploration Program.
+%
+This research has made use of the NASA Exoplanet Archive, which is
+operated by the California Institute of Technology, under contract
+with the National Aeronautics and Space Administration under the
+Exoplanet Exploration Program.
 %
@@
 
-% \input{ic2602_ages.tex}
-% \input{starparams.tex}
-% \input{model_posterior_table.tex}
 % \input{TOI837_phot_table.tex}
 % \input{TOI837_rv_table.tex}
+% \input{ic2602_ages.tex}
+\input{starparams.tex}
+\input{model_posterior_table.tex}
 

### 2020-07-14 drivers/make_posterior_table.py

@@ -13,7 +13,7 @@ from timmy.convenience import (
 from collections import OrderedDict
 from astrobase.lcmath import find_lc_timegroups
 
-def main(modelid):
+def main(modelid, datestr):
 
     assert modelid in ['allindivtransit', 'tessindivtransit']
     yval = 'PDCSAP_FLUX' # could be SAP_FLUX 
@@ -24,7 +24,6 @@ def main(modelid):
     PLOTDIR = os.path.join(
         RESULTSDIR, '{}_{}_phot_results'.format(REALID, modelid)
     )
-    datestr = '20200711'
     PLOTDIR = os.path.join(PLOTDIR, datestr)
 
     summarypath = os.path.join(
@@ -383,5 +382,5 @@ def loguniform_str(lower, upper, fmtstr=None):
 
 if __name__ == "__main__":
 
-    #main('allindivtransit')
-    main('tessindivtransit')
+    main('tessindivtransit', '20200711')
+    main('allindivtransit', '20200711')

### 2020-07-14 drivers/plot_rp_vs_age_scatter.py

@@ -1,0 +1,170 @@
+'''
+DESCRIPTION
+----------
+Make scatter plot of Rp vs age using exoplanet archive and TOI 837.
+'''
+
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.ticker as mticker
+from matplotlib.ticker import StrMethodFormatter
+
+import pandas as pd, numpy as np
+import os
+from copy import deepcopy
+
+from astropy.table import Table
+from astropy.io import ascii
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+
+from astroquery.nasa_exoplanet_archive import NasaExoplanetArchive
+
+from cdips.utils import today_YYYYMMDD
+from billy.plotting import savefig, format_ax
+
+def arr(x):
+    return np.array(x)
+
+def plot_rp_vs_age_scatter(active_targets=1, specialyoung=1):
+
+    #
+    # columns described at
+    # https://exoplanetarchive.ipac.caltech.edu/docs/API_exoplanet_columns.html
+    #
+    ea_tab = NasaExoplanetArchive.query_criteria(
+        table="exoplanets", select="*", cache=True
+    )
+
+    #
+    # get systems with finite ages (has a value, and +/- error bar)
+    #
+    has_age_value = ~ea_tab['st_age'].mask
+    has_age_errs  = (~ea_tab['st_ageerr1'].mask) & (~ea_tab['st_ageerr2'].mask)
+    has_rp_value = ~ea_tab['pl_rade'].mask
+    has_rp_errs  = (~ea_tab['pl_radeerr1'].mask) & (~ea_tab['pl_radeerr2'].mask)
+
+    transits = (ea_tab['pl_tranflag']==1)
+
+    sel = (
+        has_age_value & has_age_errs & has_rp_value & has_rp_errs & transits
+    )
+
+    t = ea_tab[sel]
+    tyoung = t[(t['st_age'] < 0.1*u.Gyr) & (t['st_age'] > 0*u.Gyr)]
+
+    #
+    # read params
+    #
+    age = t['st_age']
+    age_perr = t['st_ageerr1']
+    age_merr = np.abs(t['st_ageerr2'])
+    age_errs = np.array([age_perr, age_merr]).reshape(2, len(age))
+
+    rp = t['pl_rade']
+    rp_perr = t['pl_radeerr1']
+    rp_merr = t['pl_radeerr2']
[…]

### 2020-07-14 paper/collect.sh

@@ -27,4 +27,6 @@ cp ${rdir}rotation/rotation.pdf f9b.pdf
 
 cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.png f10.png
 
+cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200713_toi837.pdf f11.pdf
+
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-07-14 paper/ms.tex
update manuscript

@@
 Figure~\ref{fig:rpvsage} shows \tn\ in the space of planets sizes and ages.
-\tn\ is among the youngest transiting planets known, which was the
-primary motivation for this study.
+\tn\ is among the youngest transiting planets known.
 While we have statistically validated that \tn\ seems to be a planet,
@@
   T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
+  \label{eq:ephem}
 \end{align}
@@
 
-\clearpage
+%\clearpage
 \acknowledgements
-\tn\ was included on the TESS ``short-cadence'' target list in part
-thanks to the Guest Investigator program of G.\ Sacco (G011265).
-%
+\raggedbottom
+
 This paper includes data collected by the TESS mission, which are
@@
 directorate.
-%
+\tn\ was included on the TESS ``short-cadence'' target list in part
+thanks to the Guest Investigator program of G.\ Sacco (G011265).
+%
+
 We acknowledge support from the French and Italian Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI (ANR-15-IDEX-01).
@@
 %
+
 This research made use of the Exoplanet Follow-up Observation
@@
 %
-This research has made use of the NASA Exoplanet Archive, which is
+This research made use of the NASA Exoplanet Archive, which is
 operated by the California Institute of Technology, under contract
@@
 %
-This research has made use of the SVO Filter Profile Service
+
+This research made use of the SVO Filter Profile Service
 (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
 MINECO through grant AYA2017-84089.
+
 %
@@
 }
+\
 

### 2020-07-14 paper/ms.tex
update manuscript

@@
 		\leavevmode
-		\includegraphics[width=0.7\textwidth]{f8.pdf}
+		\includegraphics[width=0.65\textwidth]{f8.pdf}
 	\end{center}
-	\vspace{-0.7cm}
+	\vspace{-0.6cm}
 	\caption{ 
@@
 	\caption{
-    {\bf Planet radius versus age, for the known transiting planets.} 
+    {\bf Planet radii versus ages, for the known transiting planets.} 
     Systems younger than 100$\,$Myr are emphasized.  Ages and radii
-    were queried from the NASA Exoplanet Archive on 13 July 2020.
+    are from the NASA Exoplanet Archive on 13 July 2020.
     Precise ages are known for only a small fraction of the gray points.
@@
 	}
+	\vspace{-0.5cm}
 \end{figure}
@@
 campaign to measure the mass timed to coincide with TESS sectors 36
-and 37 ({\it i.e.}, from late March to late May of 2021) would
+and 37 (late March to late May of 2021) would
 significantly ease the extraction of the planetary Doppler signal.
-The reason is that the radial velocities, activity indicators, and
-photometry could then be modeled simultaneously, which would greatly
-constrain a Gaussian process model for the spot-induced RV signal.
+The reason is that the RVs, activity indicators, and photometry could
+be modeled simultaneously. This would greatly constrain models of
+the spot-induced RV signal.  The mass measurement would likely be
+worthwhile in order to improve understanding of the planet's
+contraction and photoevaporation history.
+
+While we hope that RV observations will be pursued, data acquired
+during the first TESS mission extension may also help in
+understanding the system
+\citep{bouma_extend_2017,huang_expected_2018}.  Any misalignment
+between the star's spin axis and the planet's orbit should induce
+nodal precession, which could yield large changes in the transit
+duration given the system's high impact parameter.
+If observed, this could be a spectroscopy-free method for 
+confirming the planet
 

### 2020-07-14 paper/ms.tex
update manuscript
Update manuscript with secondary line search
Co-authored-by: georgezhou <george.zhou@cfa.harvard.edu>

@@
 
-\edit1{George TODO: please describe the formal secondary line search
-in more depth in this paragraph} We searched for secondary lines in
-the CHIRON spectra by cross-correlating against a {\bf template of
-some kind}.  This rules out lines with flux ratios of $\approx 2\%$,
-if the lines are well-separated in velocity.  To derive the star's
-physical parameters, we cross-correlated the template against {\bf
-something}, and used the {\bf \texttt{nameofcode}}.  We measured the
-radial velocities through a least-squares deconvolution of the
-observed spectra against the same synthetic template.  The resulting
-velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:followup}.
+We derived radial velocities and spectroscopic line profiles from the
+CHIRON observations using a least-squares deconvolution of the spectra
+against non-rotating synthetic spectral templates
+\citep{donati_1997_spectropolarimetric}. The spectral templates were
+generated using ATLAS9 atmosphere models \citep{Castelli:2004} with
+the \texttt{SPECTRUM} script \citep{gray_1994_spectrum}. These line
+profiles were fitted with a broadening kernel that describes the
+rotational, radial-tangential macroturbulent, and instrumental
+broadening of the spectrum. The rotational and macroturbulent
+broadening are computed per \citet{gray_2005_book}, following the
+methods described in \citet{zhou_2018_hd106315obliq}. We fitted the
+line profile from each observation independently, yielding the radial
+velocities listed in Table~\ref{tab:rvs} and shown in
+Figure~\ref{fig:followup}. We found a mean rotational broadening
+velocity of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
+macroturbulent broadening of $v_\mathrm{Mac} = 8.4 \pm 2.9
+\mathrm{km\,s}^{-1}$.
+
+To derive the stellar parameters, we matched the set of CHIRON spectra
+against a library of observed spectra, previously
+obtained using the Tillinghast Reflect Echelle Spectrograph
+\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
+Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
+the Stellar Parameter Classification pipeline
+\citep{buchhave_hatp16b_class_2010}.  We found the best matching
+stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
+4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.
+% TODO note to Zhou: inflated Fe/H uncertainty by factor of 2.
+
+The spectroscopic line profiles were thoroughly examined for any signs
+of secondary lines that might indicate the presence of another star,
+either associated or in chance alignment with TOI 837. No such set of
+lines were found. To determine our detection limits to a blended
+spectroscopic companion, we injected a second set of lines to the mean
+least-squares deconvolution profile derived from the CHIRON
+observations. The injection spanned 10,000 different combinations of
+line broadening, velocity separation, and flux
+ratio $F_2/F_1$. The recovery results showed that for rotational
+broadenings of the secondary of $5$, $15$,
+and $25\,\mathrm{km\,s}^{-1}$, we were able to exclude sources with
+flux fractions $F_2/F_1$ brighter than roughly $0.03$, $0.08$, and
+$0.20$, provided that the secondary was separated from the primary by
+at least $\approx 15\,{\rm km\,s}^{-1}$.  At smaller velocity
+separations, the injected lines begin to blend with the target
+spectrum.
 
@@
 \subsubsection{Not SB2}
-As described in Section~\ref{subsec:chiron}, we searched the CCFs of
-the CHIRON spectra to determine whether \tn\ is double-lined.  For a
-stellar companion well-separated in velocity, this typically reveals
-companions with flux-fractions $F_2/F_1 \gtrsim 2\%$.  For plotting
-purposes, in Figure~\ref{fig:fpscenario} we have assumed a
-flux-fraction limit of 5\% ($\Delta {\rm mag} \approx 3.25$).
+We determined our detection limits to blended spectroscopic companions
+using the CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
+slowly rotating stellar companion well-separated in velocity, this
+would have revealed companions with flux fractions $F_2/F_1 \gtrsim
+3\%$.  For a companion with rotational broadening of $15\,{\rm
+km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
+exclude companions with flux fractions exceeding $\approx$8\%.  For
+plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
+latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
+For bound companions this is justified through reasoning that coeval
+binary companions to \tn\ would have both longer rotation periods and
+smaller stellar radii, and therefore smaller equatorial velocities.
 
@@
 If observed, this could be a spectroscopy-free method for 
-confirming the planet
+confirming the planet.
 

### 2020-07-14 timmy/plotting.py

@@ -2274,12 +2274,12 @@ def plot_fpscenarios(outdir):
     tdepth_df = tdepth_df.append(_append_df)
 
     #
-    # no double lined SB2 constraint. Zhou quoted F2/F1 ~= 2% as
-    # limit. use 5%.
+    # no double lined SB2 constraint. use 8% (15km/s rot), based on
+    # Zhou's injection recovery.
     #
     outer_lim = 1.0  # arcsec
     sb2_sep = sep_arcsec[sep_arcsec < outer_lim]
-    flux_frac = 5e-2
+    flux_frac = 8e-2
     dmag = -5/2 * np.log10(flux_frac)
     sb2_dmag = dmag * np.ones_like(sb2_sep)
     sb2_sep = np.append(sb2_sep, outer_lim)

### 2020-07-14 paper/ms.tex
update manuscript

@@
 % TODO:
-% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
-% text. G0/F9V has been assumed.
 % * remove all bf todo's
@@
 emission.  Studies by for instance \citet{david_discovery_2018} and
-G{.}~Zhou et al. (2020, submitted) have combined these methods to age-date
+G{.}~Zhou et al{.}~(2020, submitted) have combined these methods to age-date
 individual field stars hosting transiting planets.  Many of these latter methods were summarized by
@@
 Section~\ref{sec:observations} describes the identification of the
-candidate, and the follow-up observations collected.
-Section~\ref{sec:validation} combines these data to assess the
+candidate, and our follow-up observations.
+Section~\ref{sec:validation} combines the available data to assess the
 system's false positive probability, and validates \pn\ as a planet.
@@
 Figure~\ref{fig:fpscenario}.
+{\it LGB TODO: the procedure in the preceding paragraph might be modified to
+	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
+		day}^{-1}$ directly into a semi-amplitude limit.}
 
@@
 \acknowledgements
-\raggedbottom
+%\raggedbottom
 
@@
 MINECO through grant AYA2017-84089.
+
+Resources supporting this work were provided by the NASA High-End
+Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
+Division at Ames Research Center for the production of the SPOC data
+products.
 

### 2020-07-15 paper/authors.tex
update manuscript

@@
 \author[0000-0002-0514-5538]{L. G. Bouma}
-\affiliation{Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 
 \author[0000-0001-8732-6166]{J. D. Hartman}
-\affiliation{Department of Astrophysical Sciences, Princeton
-University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 
@@
 \author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-	Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 
@@
 \author[0000-0002-4891-3517]{G. Zhou}
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 
@@
 \author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-	Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 
@@
 \author[0000-0002-3481-9052]{K. G. Stassun}
-\affiliation{Vanderbilt University, Department of Physics \& Astronomy,
-6301 Stevenson Center Lane, Nashville, TN 37235, USA}
-\affiliation{Fisk University, Department of Physics, 1000 17th Avenue
-N., Nashville, TN 37208, USA}
+\affiliation{Vanderbilt University, Department of Physics \& Astronomy, 6301 Stevenson Center Lane, Nashville, TN 37235, USA}
+\affiliation{Fisk University, Department of Physics, 1000 17th Avenue N., Nashville, TN 37208, USA}
 %
@@
 \author[0000-0002-0628-0088]{W. Bhatti}
-\affiliation{Department of Astrophysical Sciences, Princeton
-	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 %
 \author[0000-0002-4265-047X]{J. N. Winn}
-\affiliation{Department of Astrophysical Sciences, Princeton
-	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 %
 \author[0000-0001-7204-6727]{G. \'A. Bakos}
-\affiliation{Department of Astrophysical Sciences, Princeton
-	University, 4 Ivy Lane, Princeton, NJ 08540, USA}
+\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
 
@@
 % begin (ASTEP team)
+%PENDING
 \author{L. Abe} % Lyu
@@
 
+%PENDING
 \author{A. Agabi} % Abdelkrim 
@@
 
+%PENDING
 \author[0000-0001-7866-8738]{N. Crouzet} % Nicolas
@@
 
+%PENDING
 \author[0000-0002-3937-630X]{G. Dransfield} % Georgina
@@
 
+%PENDING
 \author[0000-0002-7188-8428]{T. Guillot} % Tristan 
@@
 
+%PENDING
 \author{W. Marie-Sainte} % Wenceslas
@@
 
+%PENDING
 \author{D. M\'ekarnia} % Djamel
@@
 
+%PENDING
 \author[0000-0002-5510-8751]{A. H.M.J. Triaud} % Amaury
@@
 \author[0000-0002-7595-0970]{C.~G.~Tinney}
-\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
-	Sydney, NSW 2052, Australia}
-\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
-	2052, Australia}
+\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW Sydney, NSW 2052, Australia}
+\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW 2052, Australia}
 
@@
 
+%PENDING
 \author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
@@
 
+%PENDING
 \author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
@@
 
+%PENDING
 \author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
@@
 
+%PENDING
 \author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
@@
 
+%PENDING
 \author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
@@
 
+%PENDING
 \author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
@@
 
+%PENDING
 \author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
@@
 
+%PENDING
 \author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
@@
 
+%PENDING
 \author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
@@
 %
+%PENDING
 \author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
-\affiliation{Dunlap Institute for Astronomy and Astrophysics,
-	University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4,
-	Canada}
+\affiliation{Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St. George Street, Toronto, Ontario M5S 3H4, Canada}
 
-%FIXME ORCIDs
+%PENDING
 \author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
-\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La
-	Serena, Chile}
+\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La Serena, Chile}
 
+%PENDING
 \author{N.~Law} % nlaw@unc.edu
-\affiliation{Department of Physics and Astronomy, The University of
-	North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
+\affiliation{Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
 
+%PENDING
 \author{A.~W.~Mann} % awmann@unc.edu
-\affiliation{Department of Physics and Astronomy, The University of
-	North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
+\affiliation{Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
 
@@
 \author{G. R. Ricker} % grr@space.mit.edu
-\affiliation{Department of Physics and Kavli Institute for Astrophysics
-and Space Research, Massachusetts Institute of Technology, Cambridge, MA
-02139, USA}
+\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 %
@@
 \author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
-\affiliation{Department of Physics and Kavli Institute for Astrophysics
-and Space Research, Massachusetts Institute of Technology, Cambridge, MA
-02139, USA}
+\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 %
@@
 \author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
-\affiliation{Center for Astrophysics \textbar \ Harvard \&
-Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 %
@@
 \author{S. Seager} % seager@mit.edu
-\affiliation{Department of Earth, Atmospheric, and Planetary Sciences,
-Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+\affiliation{Department of Earth, Atmospheric, and Planetary Sciences, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 %
@@
 \affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
+
 %
@@
 %-------------------------------------
-% 3 TSO COAUTHORS
-%     Karen Collins karenacollins@outlook.com
-%     Sam Quinn squinn@cfa.harvard.edu
-%     Dana Louie danalouie@astro.umd.edu
-% 3 SPOC COAUTHORS
-%     Mark E. Rose mark.rose@nasa.gov
-%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
-%     Bill Wohler  bill.wohler@nasa.gov
-% 3 POC COAUTHORS: 
-%     John Doty (jpd@noqsi.com)
-%     Joel Villaseñor (jsvilla@space.mit.edu)
-%     Tom Barclay (barclay.astro@gmail.com)
 
-\author{TSO/SPOC/POC representatives}
+%PENDING
+\author[0000-0002-7754-9486]{C~J.~Burke} % cjburke@mit.edu
+\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+
+%PENDING
+\author[0000-0003-2313-467X]{D.~Dragomir}
+\affiliation{Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}
+
+%PENDING
+\author[0000-0003-0918-7484]{C.~X.~Huang}
+\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+
+%PENDING
+\author{R.~C.~Kidwell, Jr.} % rkidwell@stsci.edu
+\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21218 }
+
+%PENDING
+\author{A.~M.~Levine} % aml@space.mit.edu
+\affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
+
+%PENDING
+\author{E. Quintana} % elisa.quintana@nasa.gov
+\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
+
+%PENDING
+\author[0000-0001-8812-0565]{J.~E.~Rodriguez}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%PENDING
+\author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
+\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
+\affiliation{SETI Institute, Mountain View, CA 94043, USA}
+
+%PENDING
+\author[0000-0002-5402-9613]{B. Wohler} % bill.wohler@nasa.gov
+\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
+\affiliation{SETI Institute, Mountain View, CA 94043, USA}

### 2020-07-15 paper/ms.tex
update manuscript

@@
 % TODO:
-% * remove all bf todo's
+% * gammadot second method check
 %
@@
 4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.
-% TODO note to Zhou: inflated Fe/H uncertainty by factor of 2.
 
@@
 binary companions to \tn\ would have both longer rotation periods and
-smaller stellar radii, and therefore smaller equatorial velocities.
+smaller stellar radii. The equatorial velocities of such companions
+would therefore be expected to be smaller than that of \tn.
 
@@
 Figure~\ref{fig:fpscenario}.
-{\it LGB TODO: the procedure in the preceding paragraph might be modified to
+{\it LGB NOTE: the procedure in the preceding paragraph might be modified to
 	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm

### 2020-07-20 paper/ms.tex
Incorporate GB suggestions (part 1)

@@
   NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce
-  and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.  We
-  find that TOI$\,$837 is a $T=9.9$ G0/F9 dwarf in the southern open
+  and ASTEP400, and spectroscopy from the CHIRON, FEROS, and Veloce
+  spectrographs.  We
+  find that TOI$\,$837 is a $T=9.9\,{\rm mag}$ G0/F9 dwarf in the southern open
   cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
@@
 e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
-occurrence rate suggests that these early transit surveys needed a
-greater data volume, at higher precision for detection to be possible
+occurrence rate suggests that these early transit surveys would have needed a
+greater data volume at higher precision for detection to be possible
 \citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
@@
 \citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
-planets in V1298~Tau (23$\,$Myr) are also likely to be actively
+planets around V1298~Tau (23$\,$Myr) are also likely to be actively
 photoevaporating, and could represent a precursor to Kepler's compact
@@
 suggestive of a grazing transiting planet recur roughly every 8 days,
-and have a depth of about 0.4\%.  A few flares are visible.  A
+and have a depth of about 0.4\%.  A few flares are also visible.  A
 phase-folded view of the TESS transits with starspot variability
@@
 about 300 billion centroid positions of 1{.}6 billion stars.  The
-positions, proper motions, and parallaxes of the brighest 1{.}3
+positions, proper motions, and parallaxes of the brightest 1{.}3
 billion were calculated for the second data release (DR2)
@@
   %
-  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ west. The
+  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
     proper motions and parallax of this star imply it is comoving with
@@
   %
-  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ north.  The
+  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
     Gaia parallax implies this is a giant background star.
@@
     {\bf Ground-based follow-up photometry.} The data were acquired
-    using the 0.36m at El Sauce and the 0.40m ASTEP400 at Dome C.
+    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome C.
     Black points are binned to 10-minute intervals.  The gray line is
@@
 
-\subsubsection{El Sauce 0.36m}
+\subsubsection{El Sauce 0.36$\,$m}
 
 \paragraph{Acquisition and reduction}
-We observed four transits with the 0.36m at Observatario El Sauce,
+We observed four transits with the 0.36$\,$m at Observatario El Sauce,
 located in the R\'io Hurtado Valley in Chile, and operated by
@@
 stars in the El Sauce observations was $\approx 2.3''$, with a
-variance of $\approx 0.2''$.  Star B is resolved in the 0.36m images;
+variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m images;
 Star A is not.
@@
 light curves with a custom set of circular apertures with radii of
-$2.1''$ and positions ranging from Star A (2.3$''$ west of \tn) to
-2.3$''$ east of \tn.  We did not detect any variation of the transit
-depth along this line of light curves. The apertures east of \tn\
+$2.1''$ and positions ranging from Star A (2.3$''$ West of \tn) to
+2.3$''$ East of \tn.  We did not detect any variation of the transit
+depth along this line of light curves. The apertures East of \tn\
 exclude over 90\% of the flux from Star A.  The eclipse on Star A
@@
 observed eclipse depth.  We therefore interpret the lack of asymmetry
-between the western-most (centered on Star A) and eastern-most
+between the Western-most (centered on Star A) and Eastern-most
 (furthest from Star A) light curves as conclusive evidence that \tn\
@@
 
-We observed three transits with the 0.40m ASTEP telescope at the
+We observed three transits with the 0.40$\,$m ASTEP telescope at the
 Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
@@
 with clear skies, temperatures of about $-70^\circ$C, and wind speeds
-inferior to 5\,ms$^{-1}$. Due to their poor quality, we exclude from
+less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from
 the analysis all data collected on May 12. We found that the optimal
@@
     injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
-    west) is detected, and is also a
+    West) is detected, and is also a
     resolved Gaia source.  It is co-moving with \tn, and its parallax
@@
 
-\subsubsection{SMARTS 1.5m / CHIRON}
+\subsubsection{SMARTS 1.5$\,$m / CHIRON}
 \label{subsec:chiron}
 
-We acquired nine spectra using CHIRON at the SMARTS 1.5m telescope at
+We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope at
 Cerro Tollo Inter-American Observatory, Chile
@@
 \citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
-Lawrence Whipple Observatory (FLWO), Arizona, US, and classified using
+Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified using
 the Stellar Parameter Classification pipeline
@@
 stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
-4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} -0.069 \pm 0.042$ dex.
+4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.
 
@@
 TOI 837.01 was monitored with the FEROS echelle spectrograph
-\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2m telescope
+\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m telescope
 at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
@@
 We acquired 34 spectra over 10 visits of \tn\ using the Veloce
-spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
+spectrograph, mounted on the AAT 3.9$\,$m telescope at Siding Spring
 Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
@@
 strongest.  To reduce the spectra to velocities, we cross-correlated
-against a high S/N template of $\delta$ Pavonis.  The velocity RMS
-seen across each visit was hundreds of meters per second, likely due
-to uncorrected fiber-to-fiber cross-contamination.  For analysis
-purposes, we averaged across each visit, and set the velocity
-uncertainties to be the standard deviation of the per-visit exposures.
-The velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:followup}.
+against a high S/N template of $\delta$ Pavonis, because with spectral
+type G8 IV it was the closest \tn\ analog available in the Veloce
+spectral database.  The velocity RMS seen across each visit was
+hundreds of meters per second, likely due to uncorrected
+fiber-to-fiber cross-contamination.  For analysis purposes, we
+averaged across each visit, and set the velocity uncertainties to be
+the standard deviation of the per-visit exposures.  The velocities are
+given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.
 
@@
 even more restrictive depths \citep[{\it
-e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}
+e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}.
 Since the transits of \tn\ are grazing, the second and third
@@
 luminosities to expected magnitudes in instrumental bandpasses, we
-made the simplying assumption that all sources had blackbody spectra.
+made the simplifying assumption that all sources had blackbody spectra.
 Using the theoretical stellar parameters and the measured transmission
@@
 ephemeris was assumed from an initial fit of only the TESS data).  The
-corresponding $2$-$\sigma$ limits on the transit depths in Cousins-R
+corresponding $2$-$\sigma$ lower limits on the transit depths in Cousins-R
 and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
@@
 moving background stars that might be an astrophysical false-positive
-source ({\it e.g.}, \citealt{huang_pimen_2018},
-\citealt{vanderburg_hr858_2019}).  However \tn\ has only moved
+source \citep[{\it e.g.},][]{bakos_stellar_2006,huang_pimen_2018,vanderburg_hr858_2019}.  However \tn\ has only moved
 $\approx0.7''$ between 1982 and present, in comparison to the
@@
 \citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
-$\theta$ Carinae cluster, after its brightest member.  While \cn\ is
-close to the Lower Centaurus Crux subgroup of the Scorpio-Centaurus
-OB2 association in both position and proper motion space, its older
-age and clear kinematic separation indicate that it is a distinct
-stellar population
+$\theta$ Carinae cluster, after its brightest member, or also the
+``Southern Pleiades''.  While \cn\ is close to the Lower Centaurus
+Crux subgroup of the Scorpio-Centaurus OB2 association in both
+position and proper motion space, its older age and clear kinematic
+separation indicate that it is a distinct stellar population
 \citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.
@@
 
-We measured the rotation period from the PDCSAP light curve using the
+We measured the rotation period from the TESS PDCSAP light curve using the
 Lomb-Scargle periodogram implemented in \texttt{astropy}
@@
 as these represent a small fraction of the overall time series.  To
-derive the uncertainty on the best period, we fitted a gaussian to the
+derive the uncertainty on the best period, we fitted a Gaussian to the
 dominant peak, after first ensuring that we had oversampled the
@@
 
-For the PDCSAP light curve, we first eliminated points that had
+For the TESS PDCSAP light curve, we first eliminated points that had
 quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
@@
 in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
-fitted for the shared stellar parameters ($\log g, R_\star, u_0,
-u_1$), and the shared planetary parameters ($t_0, P, b, \log(R_{\rm
-p}/R_\star)$).  There were also three free trend parameters for each
+fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
+u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
+p}/R_\star)\}$.  There were also three free trend parameters for each
 transit window to account for the local rotational variability.  In
@@
 Table~\ref{tab:posterior}.  The condition for a grazing transit is
-whether the impact parameter is below $1 - R_{\rm p}/R_\star$.  The
+whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.  The
 transit is therefore either grazing, or nearly grazing.   The relevant
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Figure~\ref{fig:rpvsage} shows \tn\ in the space of planets sizes and ages.
+Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and ages.
 \tn\ is among the youngest transiting planets known.
-While we have statistically validated that \tn\ seems to be a planet,
+While we have statistically validated that \tn\ is a planet,
 the possibility that it is a background eclipsing binary has not
@@
  	{\it Spectroscopy}:
-	CTIO1.5m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
-    MPG2.2m~(FEROS; \citealt{kaufer_commissioning_1999}),
+	CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
+    MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
 	AAT~(Veloce; \citealt{gilbert_veloce_2018}).
@@
  	{\it Photometry}:
- 	  ASTEP:0.40m (ASTEP400),
+ 	  ASTEP:0.40$\,$m (ASTEP400),
 % 	CTIO:1.0m (Y4KCam),
 % 	Danish 1.54m Telescope,
-	  El Sauce:0.356m,
+	  El Sauce:0.356$\,$m,
 % 	Elizabeth 1.0m at SAAO,

### 2020-07-20 paper/ms.tex
Incorporate GB suggestions (part 2)
Co-authored-by: Gaspar Bakos <gbakos@astro.princeton.edu>

@@
     shown with gray crosses.  Dashed lines indicate the five transits
-    observed by TESS over Sectors 10 and 11.  {\it Middle}: Zoomed
-    windows of individual transits.  Gray lines are the best-fit
-    transit model, which includes a local quadratic trend in each
-    window.  {\it Bottom}: Phase-folded TESS transit. Gray points are
-    2-minute PDCSAP flux measurements with the local spot-induced
+    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
+    transits.  Gray lines are the best-fit transit model, which
+    includes a local quadratic trend in each window. Gray points are
+    2-minute \texttt{PDCSAP} flux measurements, black points are binned to
+    15-minute intervals.  {\it Bottom}: Phase-folded TESS transit.
+    Gray points are 2-minute measurements with the local spot-induced
     variation removed.  Black points are binned to 6-minute intervals.
     The black error-bar shows the median uncertainty for the black
-    points.  The gray line is the best-fit model to the TESS
-    data. 
+    points.  The gray line shows the best-fit model to the TESS data. 
 		\label{fig:tessphot}
@@
 
-We measured the rotation period from the TESS PDCSAP light curve using the
+We measured the rotation period from the TESS \texttt{PDCSAP} light curve using the
 Lomb-Scargle periodogram implemented in \texttt{astropy}
@@
 
-For the TESS PDCSAP light curve, we first eliminated points that had
+For the TESS \texttt{PDCSAP} light curve, we first eliminated points that had
 quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.

### 2020-07-20 timmy/plotting.py

@@ -52,7 +52,7 @@ from timmy.convenience import (
 
 from astrobase.lcmath import (
     phase_magseries, phase_bin_magseries, sigclip_magseries,
-    find_lc_timegroups, phase_magseries_with_errs
+    find_lc_timegroups, phase_magseries_with_errs, time_bin_magseries
 )
 
 from astrobase import periodbase
@@ -2481,7 +2481,6 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None, showerror=1)
     )
     from copy import deepcopy
     from timmy.multicolor import DELTA_LIM_RC, DELTA_LIM_B
-    from astrobase.lcmath import time_bin_magseries
 
     if os.path.exists(outpath) and not overwrite:
         print('found {} and no overwrite'.format(outpath))
@@ -2850,22 +2849,55 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
         for ft in FLARETIMES:
             _flaresel |= ( (time[s] > min(ft)) & (time[s] < max(ft)) )
 
-        size = 6
-        if np.any(_flaresel):
-            ax.scatter(24*(time[s][~_flaresel]-mid_time),
-                       (flux[s] - np.nanmedian(flux[s]))[~_flaresel]*1e3,
-                       c='k', zorder=3, s=size, rasterized=False, linewidths=0)
-            ax.scatter(24*(time[s][_flaresel]-mid_time),
-                       (flux[s] - np.nanmedian(flux[s]))[_flaresel]*1e3,
-                       c='darkgray', zorder=3, s=size, rasterized=False,
-                       linewidth=0.1, marker='x')
-        else:
-            ax.scatter(24*(time[s]-mid_time),
-                       (flux[s] - np.nanmedian(flux[s]))*1e3,
-                       c='k', zorder=3, s=size, rasterized=False, linewidths=0)
+        size = 2
+        do_bin = 1
 
+        if np.any(_flaresel):
+            if not do_bin:
+                ax.scatter(24*(time[s][~_flaresel]-mid_time),
+                           (flux[s] - np.nanmedian(flux[s]))[~_flaresel]*1e3,
+                           c='k', zorder=3, s=size, rasterized=False, linewidths=0)
+                ax.scatter(24*(time[s][_flaresel]-mid_time),
+                           (flux[s] - np.nanmedian(flux[s]))[_flaresel]*1e3,
+                           c='darkgray', zorder=3, s=size, rasterized=False,
[…]

### 2020-07-21 paper/ms.tex
update manuscript

@@
   Cluster Difference Imaging Photometric Survey (CDIPS) II.
-  TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602
+  TOI$\,$837: A Young Validated Saturn-Sized Planet in IC~2602
 }
@@
   transiting planet.  We characterize the system using data from the
-  NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce
-  and ASTEP400, and spectroscopy from the CHIRON, FEROS, and Veloce
-  spectrographs.  We
-  find that TOI$\,$837 is a $T=9.9\,{\rm mag}$ G0/F9 dwarf in the southern open
-  cluster IC 2602.  The star and planet are therefore $35^{+11}_{-5}$
-  million years old. Combining the transit photometry
-  with a prior on the stellar parameters derived from the cluster
-  color-magnitude diagram, we find that the 
-  planet is warm ($P = 8.3\,{\rm d}$) and
-  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$). 
-  The transits are either grazing or nearly grazing.  From radial velocity
-  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
-  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as
-  they are usually indicative of astrophysical false positive
-  scenarios.  Our follow-up data show that such scenarios are highly
-  unlikely.  Our combined multi-color photometry, high-resolution
-  imaging, and radial velocities rule out hierarchical eclipsing
-  binary scenarios.  Background eclipsing binary scenarios, though
-  limited by speckle imaging, formally remain a 0.2\% possibility.
-  TOI 837.01 is therefore a validated adolescent exoplanet.  Further
-  observations of its stellar obliquity, atmosphere, and mass should
-  confirm its planetary nature beyond doubt, and could improve our
-  understanding of how the physical and orbital properties of
-  exoplanets change in time.
+  NASA TESS mission, the ESA Gaia mission, ground-based photometry
+  from El Sauce and ASTEP400, and spectroscopy from the CHIRON, FEROS,
+  and Veloce spectrographs.  We find that TOI$\,$837 is a $T=9.9\,{\rm
+  mag}$ G0/F9 dwarf in the southern open cluster IC 2602.  The star
+  and planet are therefore $35^{+11}_{-5}$ million years old.
+  Combining the transit photometry with a prior on the stellar
+  parameters derived from the cluster color-magnitude diagram, we find
+  that the planet is warm ($P = 8.3\,{\rm d}$) and slightly smaller
+  than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).
+  The transits are either grazing or nearly grazing.  From radial
+  velocity monitoring, we limit the minimum mass to less than 1.20
+  $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause for
+  concern, as they are usually indicative of astrophysical false
+  positive scenarios.  Our follow-up data show that such scenarios are
+  highly unlikely.  Our combined multi-color photometry,
+  high-resolution imaging, and radial velocities rule out hierarchical
+  eclipsing binary scenarios.  Background eclipsing binary scenarios,
+  though limited by speckle imaging, formally remain a 0.2\%
+  possibility.  TOI 837.01 is therefore a validated adolescent
+  exoplanet.  Further observations of its stellar obliquity,
+  atmosphere, and mass should confirm its planetary nature beyond
+  doubt, and could improve our understanding of how the physical and
+  orbital properties of exoplanets change in time.
 \end{abstract}
@@
 roughly 1--10 million years
-\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
+\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
 Gas giants presumably finish accreting before the end of disk
@@
 e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
-Young field stars can also be identified
-isochronally, provided that they are sufficiently massive \citep{berger_gaia-kepler_2020}. 
-Other age indicators include
-stellar rotation periods, the abundance of photospheric lithium, and
-chromospheric diagnostics such as calcium emission and broadband UV
-emission.  Studies by for instance \citet{david_discovery_2018} and
-G{.}~Zhou et al{.}~(2020, submitted) have combined these methods to age-date
-individual field stars hosting transiting planets.  Many of these latter methods were summarized by
+Young field stars can also be identified isochronally, provided that
+they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
+age indicators include stellar rotation periods, the abundance of
+photospheric lithium, and chromospheric diagnostics such as calcium
+emission and broadband UV emission.  Studies by for instance
+\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
+have combined these methods to age-date individual field stars hosting
+transiting planets.  Many of these latter methods were summarized by
 \citet{mamajek_improved_2008}, and have since been calibrated by {\it
@@
 to the youngest hot Jupiters yet reported
-\citep{donati_hj_2016,johns-krull_candidate_2016,biddle_k2_2018,flagg_co_2019}.
+\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
 
@@
 e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
-occurrence rate suggests that these early transit surveys would have needed a
-greater data volume at higher precision for detection to be possible
+occurrence rate suggests that these early transit surveys would have
+needed a greater data volume at higher precision for detection to be
+possible
 \citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
@@
 \citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
-hints that young planets in clusters may in fact be qualitatively different from
-their field counterparts.  For instance, based on its observed mass,
-radius, and UV environment, the 700$\,$Myr K2-100b is probably
-actively losing its atmosphere, and should become a bare rocky planet
-over the next few hundred Myr
+hints that young planets in clusters may in fact be qualitatively
+different from their field counterparts.  For instance, based on its
+observed mass, radius, and UV environment, the 700$\,$Myr K2-100b is
+probably actively losing its atmosphere, and should become a bare
+rocky planet over the next few hundred Myr
 \citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
@@
     includes a local quadratic trend in each window. Gray points are
-    2-minute \texttt{PDCSAP} flux measurements, black points are binned to
-    15-minute intervals.  {\it Bottom}: Phase-folded TESS transit.
-    Gray points are 2-minute measurements with the local spot-induced
-    variation removed.  Black points are binned to 6-minute intervals.
-    The black error-bar shows the median uncertainty for the black
-    points.  The gray line shows the best-fit model to the TESS data. 
+    2-minute \texttt{PDCSAP} flux measurements, black points are
+    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
+    transit.  Gray points are 2-minute measurements with the local
+    spot-induced variation removed.  Black points are binned to
+    6-minute intervals.  The black error-bar shows the median
+    uncertainty for the black points.  The gray line shows the
+    best-fit model to the TESS data. 
 		\label{fig:tessphot}
@@
     {\bf Ground-based follow-up photometry.} The data were acquired
-    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome C.
-    Black points are binned to 10-minute intervals.  The gray line is
-    the best-fit model to the combined TESS and ground-based data.
-    Red and blue lines show $2\sigma$ lower limits on the transit depths in the
-    Cousins-R and Johnson-B bandpasses used to rule out specific false
-    positive scenarios (see Section~\ref{subsec:colorphot}).
+    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome
+    C.  Black points are binned to 10-minute intervals.  The gray line
+    is the best-fit model to the combined TESS and ground-based data.
+    Red and blue lines show $2\sigma$ lower limits on the transit
+    depths in the Cousins-R and Johnson-B bandpasses used to rule out
+    specific false positive scenarios (see
+    Section~\ref{subsec:colorphot}).
 		\label{fig:groundphot}
@@
 stars in the El Sauce observations was $\approx 2.3''$, with a
-variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m images;
-Star A is not.
+variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m
+images; Star A is not.
 
@@
 institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
-allows it to take advantage of
-the continuous night during Austral winter.  The weather is of
-photometric quality for about two-thirds of each winter
-\citep{crouzet_four_2018}.
+allows it to take advantage of the continuous night during Austral
+winter.  The weather is of photometric quality for about two-thirds of
+each winter \citep{crouzet_four_2018}.
 
@@
 with clear skies, temperatures of about $-70^\circ$C, and wind speeds
-less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from
-the analysis all data collected on May 12. We found that the optimal
+less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from the
+analysis all data collected on May 12. We found that the optimal
 calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
@@
 	\caption{
-    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:}
-    SOAR HRCam contrast limits derived from point-source
-    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
-    West) is detected, and is also a
-    resolved Gaia source.  It is co-moving with \tn, and its parallax
-    and on-sky position imply that it is physically separated from
-    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
-    (RV) measurements, with best-fit instrument offsets and jitter
-    terms included.  The expected scatter from starspots based on
-    $v\sin i$ and the photometric modulation amplitude is of order
-    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
-    orbital ephemeris of \pn.  The planet is not detected.  The black
-    line shows a circular Keplerian orbit representing the $3\sigma$
-    upper mass limit.
+    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:} SOAR
+    HRCam contrast limits derived from point-source injection-recovery
+    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
+    and is also a resolved Gaia source.  It is co-moving with \tn, and
+    its parallax and on-sky position imply that it is physically
+    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
+    Radial velocity (RV) measurements, with best-fit instrument
+    offsets and jitter terms included.  The expected scatter from
+    starspots based on $v\sin i$ and the photometric modulation
+    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
+    measurements phased to the orbital ephemeris of \pn.  The planet
+    is not detected.  The black line shows a circular Keplerian orbit
+    representing the $3\sigma$ upper mass limit.
 		\label{fig:followup}
@@
 
-We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope at
-Cerro Tollo Inter-American Observatory, Chile
+We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope
+at Cerro Tollo Inter-American Observatory, Chile
 \citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
@@
 To derive the stellar parameters, we matched the set of CHIRON spectra
-against a library of observed spectra, previously
-obtained using the Tillinghast Reflect Echelle Spectrograph
+against a library of observed spectra, previously obtained using the
+Tillinghast Reflect Echelle Spectrograph
 \citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
-Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified using
-the Stellar Parameter Classification pipeline
+Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified
+using the Stellar Parameter Classification pipeline
 \citep{buchhave_hatp16b_class_2010}.  We found the best matching
@@
 observations. The injection spanned 10,000 different combinations of
-line broadening, velocity separation, and flux
-ratio $F_2/F_1$. The recovery results showed that for rotational
-broadenings of the secondary of $5$, $15$,
-and $25\,\mathrm{km\,s}^{-1}$, we were able to exclude sources with
-flux fractions $F_2/F_1$ brighter than roughly $0.03$, $0.08$, and
-$0.20$, provided that the secondary was separated from the primary by
-at least $\approx 15\,{\rm km\,s}^{-1}$.  At smaller velocity
-separations, the injected lines begin to blend with the target
-spectrum.
+line broadening, velocity separation, and flux ratio $F_2/F_1$. The
+recovery results showed that for rotational broadenings of the
+secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
+exclude sources with flux fractions $F_2/F_1$ brighter than roughly
+$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
+from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
+smaller velocity separations, the injected lines begin to blend with
+the target spectrum.
 
@@
 TOI 837.01 was monitored with the FEROS echelle spectrograph
-\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m telescope
-at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
-$\approx$48,000 across a spectral range of 350–920 nm. It has a
-remarkably high efficiency of $\approx$20\%. We obtained 13 spectra of
-\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
-Warm gIaNts with tEss (WINE) collaboration, which focuses on the
-systematic characterization of TESS transiting giant planets with
-moderately long orbital periods \citep[{\it
+\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
+telescope at the ESO La Sille Observatory, in Chile. FEROS has a
+resolution of $\approx$48,000 across a spectral range of 350–920 nm.
+It has a remarkably high efficiency of $\approx$20\%. We obtained 13
+spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
+context of the Warm gIaNts with tEss (WINE) collaboration, which
+focuses on the systematic characterization of TESS transiting giant
+planets with moderately long orbital periods \citep[{\it
 e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
@@
 extracted spectra with a binary mask resembling the properties of a
-G2V star. The radial velocities are given in Table~\ref{tab:rvs},
-and shown in Figure~\ref{fig:followup}.
+G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
+shown in Figure~\ref{fig:followup}.
 
@@
 ephemeris was assumed from an initial fit of only the TESS data).  The
-corresponding $2$-$\sigma$ lower limits on the transit depths in Cousins-R
-and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
+corresponding $2$-$\sigma$ lower limits on the transit depths in
+Cousins-R and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
 respectively, and are shown in Figure~\ref{fig:groundphot}.
@@
 answer was yes, we could not rule out such hierarchical eclipsing
-binary systems.  Conversely, we ruled out systems for which at
-fixed secondary mass no tertiary mass could enable eclipses of the
-necessary depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The
-${\rm R_C}$-band limit corresponded to a secondary mass limit of $M_2
-> 0.27 M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger
-limit of $M_2 > 0.70 M_\odot$.
+binary systems.  Conversely, we ruled out systems for which at fixed
+secondary mass no tertiary mass could enable eclipses of the necessary
+depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The ${\rm
+R_C}$-band limit corresponded to a secondary mass limit of $M_2 > 0.27
+M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger limit of
+$M_2 > 0.70 M_\odot$.
 
@@
 moving background stars that might be an astrophysical false-positive
-source \citep[{\it e.g.},][]{bakos_stellar_2006,huang_pimen_2018,vanderburg_hr858_2019}.  However \tn\ has only moved
-$\approx0.7''$ between 1982 and present, in comparison to the
-$\approx2.0''$ FWHM of the target on the plates.  We therefore cannot
-resolve it with great confidence from background sources not already
-resolved through more modern imaging.
+source \citep[{\it
+e.g.},][]{bakos_stellar_2006,huang_pimen_2018,vanderburg_hr858_2019}.
+However \tn\ has only moved $\approx0.7''$ between 1982 and present,
+in comparison to the $\approx2.0''$ FWHM of the target on the plates.
+We therefore cannot resolve it with great confidence from background
+sources not already resolved through more modern imaging.
 
@@
 
-One potential caveat in our approach is that \texttt{VESPA} uses a galactic
-population synthesis to model the sight-line. Since \tn\ is in the
-foreground of \cn\ (see Section~\ref{subsec:star}), for roughly
+One potential caveat in our approach is that \texttt{VESPA} uses a
+galactic population synthesis to model the sight-line. Since \tn\ is
+in the foreground of \cn\ (see Section~\ref{subsec:star}), for roughly
 $25\,{\rm pc}$ behind the sightline to the star, the number of
-background stars is higher than \texttt{VESPA} would predict due to the
-presence of the cluster.  To quantify the importance of this effect,
-we assessed the sky-plane density of potential contaminants by
+background stars is higher than \texttt{VESPA} would predict due to
+the presence of the cluster.  To quantify the importance of this
+effect, we assessed the sky-plane density of potential contaminants by
 counting stars brighter than $T=15.07$ within 0.5 degrees of \tn\
@@
 sky-plane density of stars fluctuated at the level of $\approx 15\%$,
-with a local maximum a few degrees away from \tn, towards the center of \cn.
-The overall density also slowly increased towards the galactic center.
-We therefore do not expect this consideration to significantly alter
-our FPP calculation.
+with a local maximum a few degrees away from \tn, towards the center
+of \cn.  The overall density also slowly increased towards the
+galactic center.  We therefore do not expect this consideration to
+significantly alter our FPP calculation.
 
@@
 
-We measured the rotation period from the TESS \texttt{PDCSAP} light curve using the
-Lomb-Scargle periodogram implemented in \texttt{astropy}
+We measured the rotation period from the TESS \texttt{PDCSAP} light
+curve using the Lomb-Scargle periodogram implemented in
+\texttt{astropy}
 \citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
@@
 $v$ of the star would be $17.67 \pm 0.32 \,{\rm km\,s}^{-1}$.  Our
-spectroscopically measured $v\sin i$ from CHIRON, $16.2 \pm 1.1
-\,{\rm km\,s}^{-1}$ agrees reasonably well with this expectation.
+spectroscopically measured $v\sin i$ from CHIRON, $16.2 \pm 1.1 \,{\rm
+km\,s}^{-1}$ agrees reasonably well with this expectation.
 
@@
 
-For the TESS \texttt{PDCSAP} light curve, we first eliminated points that had
-quality flags corresponding to any of bits $\{3, 4, 6, 8, 11, 12\}$.
-This excluded cadences affected by coarse spacecraft pointing,
+For the TESS \texttt{PDCSAP} light curve, we first eliminated points
+that had quality flags corresponding to any of bits $\{3, 4, 6, 8, 11,
+12\}$.  This excluded cadences affected by coarse spacecraft pointing,
 reaction wheel desaturation events, manual flags, cosmic ray hits, and
@@
 Table~\ref{tab:posterior}.  The condition for a grazing transit is
-whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.  The
-transit is therefore either grazing, or nearly grazing.   The relevant
-posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
-From experimenting with the priors, we found that in the absence of a
-strong prior on the stellar density, the inherent degeneracy between
-the impact parameter and planet-to-star size ratio would have been
-much stronger.  In the absence of precise information about the star,
-a larger fraction of the posterior would therefore have been grazing.
-However, our priors on the stellar parameters from the cluster
-isochrone fit break this degeneracy, enabling us to report two-sided
-limits on the planet-to-star size ratio.
+whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
+The transit is therefore either grazing, or nearly grazing.   The
+relevant posterior probabilities are shown in
+Figure~\ref{fig:subsetcorner}.  From experimenting with the priors, we
+found that in the absence of a strong prior on the stellar density,
+the inherent degeneracy between the impact parameter and
+planet-to-star size ratio would have been much stronger.  In the
+absence of precise information about the star, a larger fraction of
+the posterior would therefore have been grazing.  However, our priors
+on the stellar parameters from the cluster isochrone fit break this
+degeneracy, enabling us to report two-sided limits on the
+planet-to-star size ratio.
 
@@
     Systems younger than 100$\,$Myr are emphasized.  Ages and radii
-    are from the NASA Exoplanet Archive on 13 July 2020.
-    Precise ages are known for only a small fraction of the gray points.
+    are from the NASA Exoplanet Archive on 13 July 2020.  Precise ages
+    are known for only a small fraction of the gray points.
 		\label{fig:rpvsage}
@@
 \citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and ages.
-\tn\ is among the youngest transiting planets known.
-While we have statistically validated that \tn\ is a planet,
-the possibility that it is a background eclipsing binary has not
-been excluded with sufficient confidence to call the planet ``confirmed''.
+Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
+ages.  \tn\ is among the youngest transiting planets known.  While we
+have statistically validated that \tn\ is a planet, the possibility
+that it is a background eclipsing binary has not been excluded with
+sufficient confidence to call the planet ``confirmed''.
 
@@
 campaign to measure the mass timed to coincide with TESS sectors 36
-and 37 (late March to late May of 2021) would
-significantly ease the extraction of the planetary Doppler signal.
-The reason is that the RVs, activity indicators, and photometry could
-be modeled simultaneously. This would greatly constrain models of
-the spot-induced RV signal.  The mass measurement would likely be
-worthwhile in order to improve understanding of the planet's
-contraction and photoevaporation history.
+and 37 (late March to late May of 2021) would significantly ease the
+extraction of the planetary Doppler signal.  The reason is that the
+RVs, activity indicators, and photometry could be modeled
+simultaneously \citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This
+would greatly constrain models of the spot-induced RV signal.  The
+mass measurement would likely be worthwhile in order to improve
+understanding of the planet's contraction and photoevaporation
+history.
 
 While we hope that RV observations will be pursued, data acquired
-during the first TESS mission extension may also help in
-understanding the system
-\citep{bouma_extend_2017,huang_expected_2018}.  Any misalignment
-between the star's spin axis and the planet's orbit should induce
-nodal precession, which could yield large changes in the transit
-duration given the system's high impact parameter.
-If observed, this could be a spectroscopy-free method for 
-confirming the planet.
+during the first TESS mission extension may also help in understanding
+the system \citep{bouma_extend_2017,huang_expected_2018}.  Any
+misalignment between the star's spin axis and the planet's orbit
+should induce nodal precession, which could yield large changes in the
+transit duration given the system's high impact parameter.  If
+observed, this could be a spectroscopy-free method for confirming the
+planet.
 
@@
 
-We acknowledge support from the French and Italian Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI (ANR-15-IDEX-01).
-We thank the dedicated staff at Concordia for their continuous presence and support throughout the Austral winter.
-%
-This research received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement n$^\circ$ 803193/BEBOP), and from the Science and Technology Facilities Council (STFC; grant n$^\circ$ ST/S00193X/1).
+We acknowledge support from the French and Italian Polar Agencies,
+IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI
+(ANR-15-IDEX-01). We thank the dedicated staff at Concordia for their
+continuous presence and support throughout the Austral winter.
+%
+This research received funding from the European Research Council
+(ERC) under the European Union's Horizon 2020 research and innovation
+programme (grant agreement n$^\circ$ 803193/BEBOP), and from the
+Science and Technology Facilities Council (STFC; grant n$^\circ$
+ST/S00193X/1).
 %
@@
 products.
+%
+
+A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
+Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
+Chilean Ministry of Economy. A.J.\ acknowledges additional support
+from FONDECYT project 1171208.
 

### 2020-07-21 paper/ms.tex
Update manuscript
Co-authored-by: Andrew Mann <awmann@unc.edu>

@@
   parameters derived from the cluster color-magnitude diagram, we find
-  that the planet is warm ($P = 8.3\,{\rm d}$) and slightly smaller
-  than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).
-  The transits are either grazing or nearly grazing.  From radial
-  velocity monitoring, we limit the minimum mass to less than 1.20
-  $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause for
-  concern, as they are usually indicative of astrophysical false
+  that the planet orbits close to its star ($P = 8.3\,{\rm d}$) and is
+  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
+  \,R_{\rm Jup}$).  The transits are either grazing or nearly grazing.
+  From radial velocity monitoring, we limit the minimum mass to less
+  than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause
+  for concern, as they are usually indicative of astrophysical false
   positive scenarios.  Our follow-up data show that such scenarios are
@@
 \citet{zerjal_chromospherically_2017} for chromospheric activity, and
-{\it e.g.}, \citet{elliott_search_2016,berger_identifying_2018} and
+{\it e.g.}, \citet{berger_identifying_2018} and
 \citet{zerjal_galah_2019} for lithium abundances.
@@
 \paragraph{Acquisition and reduction}
-We observed four transits with the 0.36$\,$m at Observatario El Sauce,
+We observed four transits with the 0.36$\,$m at Observatorio El Sauce,
 located in the R\'io Hurtado Valley in Chile, and operated by
@@
 e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}.
-Since the transits of \tn\ are grazing, the second and third
-contact points do not occur, and the shape of the transit is not
-restrictive.
+Since the transits of \tn\ could be grazing, the second and third
+contact points do not necessarily occur, and the shape of the transit
+is not particularly restrictive.
 
@@
 We determined our detection limits to blended spectroscopic companions
-using the CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
+using the stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
 slowly rotating stellar companion well-separated in velocity, this
@@
 in comparison to the $\approx2.0''$ FWHM of the target on the plates.
-We therefore cannot resolve it with great confidence from background
-sources not already resolved through more modern imaging.
+We therefore cannot resolve it from background sources not already
+resolved through more modern imaging.
 
@@
 than observed in the Gaia photometry.  This discrepancy was noted and
-discussed at length by \citet{choi_mesa_2016}.  The most plausible
-explanation seems to be that strong magnetic fields in low-mass
+discussed at length by \citet{choi_mesa_2016}.  One suggested
+explanation was that strong magnetic fields in low-mass
 pre-main-sequence stars inhibit convection and produce a high filling
 factor of starspots \citep[{\it
-e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}. To conserve flux,
-the stellar radius expands, and the star becomes cooler than a
-1-dimensional model would predict.
+e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
+however fails to explain poor isochrone fits in old open clusters
+({\it e.g.}, M$\,$67) as well as the field, particularly in blue
+bandpasses. A more likely explanation could be that the molecular line
+lists for M dwarf atmospheres are incomplete in these wavelength
+ranges.
 
@@
     {\bf Posterior probabilities of impact parameter, planet-to-star
-    size ratio, and stellar density.} The  planet-to-star size ratio
+    size ratio, and stellar density.} 
+    Contours are shown at 1, 2, 3, and 4-$\sigma$ confidence.
+    The planet-to-star size ratio
     corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
@@
 Chilean Ministry of Economy. A.J.\ acknowledges additional support
-from FONDECYT project 1171208.
+from FONDECYT project 1171208.  J.I.V\ acknowledges support from
+CONICYT-PFCHA/Doctorado Nacional-21191829.
+%
+
+C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
+Astronomy \& Astrophysics, funded through an endowment established by
+the Dunlap family and the University of Toronto.
+%
 

### 2020-07-21 timmy/plotting.py

@@ -1196,7 +1196,7 @@ def plot_hr(outdir, isochrone=None, do_cmd=0):
             print(f'{mediancorr:.2f}')
         ages = [10, 20, 30, 40]
         N_ages = len(ages)
-        colors = plt.cm.YlGnBu(np.linspace(0.2,1,N_ages))[::-1]
+        colors = plt.cm.cool(np.linspace(0,1,N_ages))[::-1]
 
         for i, (a, c) in enumerate(zip(ages, colors)):
             mstar = isocmd.isocmds[i]['star_mass']
@@ -2136,13 +2136,15 @@ def plot_lithium(outdir):
     colors = ['k', 'gray']
     zorders = [2, 1]
     markers = ['o', '.']
+    ss = [13, 5]
     labels = ['NGC$\,$2547 & IC$\,$2602', 'Kepler Field']
 
     # plot vals
-    for _cls, _col, z, m, l in zip(classes, colors, zorders, markers, labels):
+    for _cls, _col, z, m, l, s in zip(classes, colors, zorders, markers,
+                                      labels, ss):
         ax.scatter(
             d[f'val_teff_{_cls}'], d[f'val_li_ew_{_cls}'], c=_col, alpha=1,
-            zorder=z, s=5, rasterized=False, linewidths=0, label=l, marker=m
+            zorder=z, s=s, rasterized=False, linewidths=0, label=l, marker=m
         )
 
 
@@ -2151,7 +2153,7 @@ def plot_lithium(outdir):
         TEFF,
         LI_EW,
         alpha=1, mew=0.5, zorder=8, label='TOI 837', markerfacecolor='yellow',
-        markersize=14, marker='*', color='black', lw=0
+        markersize=18, marker='*', color='black', lw=0
     )
 
     ax.legend(loc='best', handletextpad=0.1, fontsize='x-small', framealpha=0.7)
@@ -2178,24 +2180,35 @@ def plot_rotation(outdir):
     classes = ['pleiades', 'praesepe', 'ngc6811']
     colors = ['k', 'gray', 'darkgray']
     zorders = [3, 2, 1]
-    markers = ['o', 'X', 's']
+    markers = ['o', 'x', 's']
+    lws = [0, 0., 0]
+    mews= [0.5, 0.5, 0.5]
+    ss = [3.0, 6, 3.0]
     labels = ['Pleaides', 'Praesepe', 'NGC$\,$6811']
 
     # plot vals
-    for _cls, _col, z, m, l in zip(classes, colors, zorders, markers, labels):
[…]

### 2020-07-21 paper/ms.tex
Update manuscript
Co-authored-by: Rafael Brahm <rbrahm@gmail.com>

@@
   from El Sauce and ASTEP400, and spectroscopy from the CHIRON, FEROS,
-  and Veloce spectrographs.  We find that TOI$\,$837 is a $T=9.9\,{\rm
-  mag}$ G0/F9 dwarf in the southern open cluster IC 2602.  The star
+  and Veloce spectrographs.  We find that TOI$\,$837 is a $T=9.9$ mag
+  G0/F9 dwarf in the southern open cluster IC 2602.  The star
   and planet are therefore $35^{+11}_{-5}$ million years old.
@@
   parameters derived from the cluster color-magnitude diagram, we find
-  that the planet orbits close to its star ($P = 8.3\,{\rm d}$) and is
+  that the planet has an orbital period of $8.3\,{\rm d}$ and is
   slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
@@
   \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
-    proper motions and parallax of this star imply it is comoving with
+    proper motions and parallax of this star imply it is co-moving with
     \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
     Star A is therefore likely an \cn\ member, but unlikely to be a bound
-    binary compnaion.
+    binary companion.
   %
@@
 
-Reconaissance spectroscopic follow-up is an essential step in vetting
+Reconnaissance spectroscopic follow-up is an essential step in vetting
 planet candidates.  Medium to high-resolution spectra enable physical
@@
 companions.  Finally, if there are close or bright companions,
-reconaissance spectra can also reveal the presence of a secondary set
+reconnaissance spectra can also reveal the presence of a secondary set
 of stellar lines.
@@
 4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.
+We ultimately adopted a different set of stellar parameters for 
+our analysis (see Section~\ref{subsec:starparams}).
 
@@
 data, further constrains the presence of a hierarchical binary system.
+The consistency of the Gaia DR2 RV ($17.44 \pm 0.64\,$\kms) with
+the FEROS RVs ($18.0 \pm 0.1$\kms) in theory places an even stronger limit on 
+linear trends, since the two observation epochs are separated by roughly
+five years.
 To derive limits for this second possibility, we placed a wide
@@
 greater than for an arbitrary foreground star.  The relevant
-populations need to be modelled at the Monte Carlo level.  We opt to
-use \texttt{VESPA} to perform this population modelling
+populations need to be modeled at the Monte Carlo level.  We opt to
+use \texttt{VESPA} to perform this population modeling
 \citep{morton_efficient_2012,vespa_2015}.
@@
 where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
-scenarios, and $\pi_i$ is the model prior.  The terms labelled as
+scenarios, and $\pi_i$ is the model prior.  The terms labeled as
 ``BEB'' usually include other false positive scenarios (HEBs and EBs),
@@
 \citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
-evaluated by forward-modelling a representative population of
+evaluated by forward-modeling a representative population of
 eclipsing bodies for model class, in which each population member has
@@
 
-\section{System Modelling}
+\section{System Modeling}
 \label{sec:system}
@@
 		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9a.pdf}
+			\includegraphics[width=0.45\textwidth]{f9b.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9b.pdf}
+			\includegraphics[width=0.45\textwidth]{f9a.pdf}
 		}
@@
 	\caption{ {\bf Youth diagnostics.}
-    {\it Top:} Lithium 6708\AA\ equivalent widths for \tn, field
+	{\it Top:} Rotation periods for \tn\ and selected open clusters.
+    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
+    (1000$\,$Myr) are shown.  Their rotation periods were measured by
+    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
+    and \citet{curtis_temporary_2019}, respectively.
+    {\it Bottom:} Lithium 6708\AA\ equivalent widths for \tn, field
     stars, and young open clusters.  The field star sample is drawn
@@
     for these clusters of $37.7^{+5.7}_{-4.8}\,{\rm Myr}$
-    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  {\it
-    Bottom:} Rotation periods for \tn\ and selected open clusters.
-    The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
-    (1000$\,$Myr) are shown.  Their rotation periods were measured by
-    \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
-    and \citet{curtis_temporary_2019}, respectively.
+    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
     \label{fig:lithium_rotation}
@@
 \cn\ cluster, and the ``neighborhood'' of spatially nearby stars.
-Stars labelled as ``cluster members'' are those reported by
+Stars labeled as ``cluster members'' are those reported by
 \citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
@@
 different approaches.  To derive the most precise possible ephemeris,
-we fitted the ground and space-based transits simultaneously.  To the
+we fitted the ground and space-based transits simultaneously.  To
 derive the physical parameters of the planet, we fitted the TESS data
@@
 CONICYT-PFCHA/Doctorado Nacional-21191829.
-%
-
+R.B.\ acknowledges support from FONDECYT Post-doctoral Fellowship Project 3180246.
+%
 C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for

### 2020-07-21 paper/ms.tex
Update manuscript

@@
   Cluster Difference Imaging Photometric Survey (CDIPS) II.
-  TOI$\,$837: A Young Validated Saturn-Sized Planet in IC~2602
+  TOI$\,$837: A Young Validated Planet in IC~2602
 }
@@
   NASA TESS mission, the ESA Gaia mission, ground-based photometry
-  from El Sauce and ASTEP400, and spectroscopy from the CHIRON, FEROS,
-  and Veloce spectrographs.  We find that TOI$\,$837 is a $T=9.9$ mag
+  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS,
+  and Veloce.  We find that TOI$\,$837 is a $T=9.9$ mag
   G0/F9 dwarf in the southern open cluster IC 2602.  The star
@@
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f10.png}
+		\includegraphics[width=0.48\textwidth]{f10.pdf}
 	\end{center}

### 2020-07-21 paper/collect.sh

@@ -25,7 +25,7 @@ cp ${rdir}lithium/lithium.pdf f9a.pdf
 
 cp ${rdir}rotation/rotation.pdf f9b.pdf
 
-cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.png f10.png
+cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.pdf f10.pdf
 
 cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200713_toi837.pdf f11.pdf
 

### 2020-07-21 timmy/plotting.py

@@ -2968,4 +2968,4 @@ def plot_subsetcorner(m, outpath):
         format_ax(a)
     # fig.tight_layout()
 
-    savefig(fig, outpath, writepdf=0, dpi=300)
+    savefig(fig, outpath, writepdf=1, dpi=300)

### 2020-07-22 paper/ms.tex
Update manuscript
Co-authored-by: Andrew Mann <awmann@unc.edu>

@@
   fit the upper main sequence well, but diverge from the data for
-  $M_\star \lesssim 0.7 M_\odot$. This is a known problem with PMS
-  models (see Section~\ref{subsec:hr}).
+  $M_\star \lesssim 0.7 M_\odot$. This is a known issue with the
+  M dwarf models (see Section~\ref{subsec:hr}).
   \label{fig:hr}
@@
 e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
-however fails to explain poor isochrone fits in old open clusters
-({\it e.g.}, M$\,$67) as well as the field, particularly in blue
-bandpasses. A more likely explanation could be that the molecular line
-lists for M dwarf atmospheres are incomplete in these wavelength
-ranges.
+however fails to explain poor isochrone fits in both old open clusters
+({\it e.g.}, M$\,$67) and the field, particularly in blue bandpasses.
+An alternative explanation is that the molecular line lists for M
+dwarf atmospheres are incomplete in these wavelength ranges
+\citep{rajpurohit_effective_2013,mann_spectrothermometry_2013}.
 
@@
 \acknowledgements
-%\raggedbottom
+\raggedbottom
 

### 2020-07-22 drivers/math_sine.py

@@ -1,0 +1,27 @@
+import numpy as np, matplotlib.pyplot as plt
+
+def simple():
+    period = 1
+    N_draws = 10000
+
+    #t = np.random.uniform(0, period/2, N_draws)
+    t = np.linspace(0, period/2, N_draws, endpoint=True)
+    ω = 2*np.pi/period
+    A = 10
+
+    x = ω*t
+
+    #y = A*np.abs(np.sin(x))
+    y = A*np.sin(x)
+
+    plt.close('all')
+    n, bins, patches = plt.hist(y, bins=1000, density=True, cumulative=True)
+
+    x_mod = np.linspace(np.min(y), np.max(y), 1000)
+    F_x = 2/np.pi * np.arcsin(np.sqrt(x_mod/A))
+    plt.plot(x_mod, F_x)
+
+    plt.savefig('temp.png')
+
+if __name__ == '__main__':
+    simple()

### 2020-07-22 drivers/plot_hr.py

@@ -4,7 +4,8 @@ from timmy.paths import RESULTSDIR
 
 PLOTDIR = os.path.join(RESULTSDIR, 'cluster_membership')
 
-tp.plot_hr(PLOTDIR, isochrone=1, do_cmd=1)
-tp.plot_hr(PLOTDIR, isochrone=0, do_cmd=1)
-tp.plot_hr(PLOTDIR, isochrone=1)
-tp.plot_hr(PLOTDIR, isochrone=0)
+for color0 in ['phot_bp_mean_mag', 'phot_g_mean_mag']:
+    tp.plot_hr(PLOTDIR, isochrone=1, color0=color0)
+    tp.plot_hr(PLOTDIR, isochrone=0, color0=color0)
+    tp.plot_hr(PLOTDIR, isochrone=1, do_cmd=1, color0=color0)
+    tp.plot_hr(PLOTDIR, isochrone=0, do_cmd=1, color0=color0)

### 2020-07-22 drivers/rvlimits_method2.py

@@ -1,0 +1,190 @@
+"""
+To get a more conservative limit on K as a function of P:
+    1. fit a linear relation to the data, using a uniform (non-logarithmic
+    prior) on the slope, that allows for positive and negative values.
+    2. The slope distribution will be tightly constrained, giving you a robust 3
+    sigma upper limit on its absolute value.
+    3. Then you can ask for a given value of P, what value of K would yield a
+    first derivative greater than the slope limit more than 99.7% of the time.
+"""
+
+import pymc3 as pm
+import numpy as np, matplotlib.pyplot as plt, pandas as pd
+import pickle, os, corner
+from pymc3.backends.tracetab import trace_to_dataframe
+from numpy import array as nparr
+from astropy import units as u, constants as c
+
+from timmy.paths import DATADIR, RESULTSDIR
+rdir = os.path.join(RESULTSDIR, 'rvlimits_method2')
+
+def get_K_lim(period, gammadot_limit, frac=0.997):
+    """
+    Given a period and limiting dv/dt,
+    return the minimum K such that
+
+        |K ω sin(ωt)| - gammadot_limit > 0
+
+    at least frac % of the time.
+    """
+
+    N_draws = 10000
+    N_req = int(frac*N_draws)
+
+    t = np.linspace(0, period, N_draws)
+    ω = 2*np.pi/period
+
+    assert 0
+
+
+    # rv_vals = 
+
+    return K
+
+def main(overwrite=0):
+
+    # steps 1 and 2. [m] = m/s/day
+    absm_threesig = get_abs_m(overwrite=overwrite)
+
+    assert 0
+
+    # step 3, get samples.
+    # 3. for a given value of P, what value of K would yield a first derivative
+    # greater than the slope limit more than 99.7% of the time.
+    N_samples = 1000
+    log_period = np.random.uniform(
+        low=np.log(0.1), high=np.log(1e15), size=N_samples
+    )
+
+
+    e = 0
+    sini = 1
+    Mstar = 1.1 * u.Msun
+    # NOTE: assuming log[k (m/s)]
+    # NOTE: this is the Mstar >> Mcomp approximation. If this doesn't hold, it's an
+    # implicit equation (the "binary mass function"). So in the large semimajor
+    # axis regime, your resulting converted contours are wrong.
[…]

### 2020-07-22 paper/collect.sh

@@ -17,7 +17,7 @@ cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f3
 
 cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
 
-cp ${rdir}cluster_membership/hr_withiso.pdf f7.pdf
+cp ${rdir}cluster_membership/hr_withiso_Bp_m_Rp.pdf f7.pdf
 
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
 

### 2020-07-22 paper/ms.tex
Update manuscript
RV limits on HEB scenarios

@@
   From radial velocity monitoring, we limit the minimum mass to less
-  than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits are a cause
+  than 1.20 $M_{\rm Jup}$ (3-$\sigma$).  Grazing transits are a cause
   for concern, as they are usually indicative of astrophysical false
@@
     is the best-fit model to the combined TESS and ground-based data.
-    Red and blue lines show $2\sigma$ lower limits on the transit
+    Red and blue lines show 2-$\sigma$ lower limits on the transit
     depths in the Cousins-R and Johnson-B bandpasses used to rule out
@@
     is not detected.  The black line shows a circular Keplerian orbit
-    representing the $3\sigma$ upper mass limit.
+    representing the 3-$\sigma$ upper mass limit.
 		\label{fig:followup}
@@
 \subsubsection{RVs}
-The combined radial velocities from FEROS, CHIRON, and Veloce can be
+The radial velocities from FEROS, CHIRON, and Veloce can be
 used to detect massive bound companions orbiting \tn.  We searched for
@@
 % timmy.drivers.oneoff_drivers.get_mass_upper_limit
-For the first fit, we assumed a restrictive prior on the period and
-time of periapse, using the known ephemeris from the transit.  We then
+For the first fit we set a prior on the period and
+time of periapse using the known ephemeris from the transit.  We then
 fitted for the semi-amplitude, instrument offsets, and jitter
@@
 eclipses are caused by a stellar-mass object orbiting \tn.  The lack
-of a linear trend in the radial velocities, particularly in the FEROS
+of a linear radial velocity trend, particularly in the FEROS
 data, further constrains the presence of a hierarchical binary system.
-The consistency of the Gaia DR2 RV ($17.44 \pm 0.64\,$\kms) with
-the FEROS RVs ($18.0 \pm 0.1$\kms) in theory places an even stronger limit on 
-linear trends, since the two observation epochs are separated by roughly
-five years.
-To derive limits for this second possibility, we placed a wide
-log-uniform prior on the semi-amplitude and period ($\log K\ [{\rm
-m\,s^{-1}}] \sim \mathcal{U}(1,10^5)$, $\log P\ [{\rm days}] \sim
-\mathcal{U}(0.1, 10^{15})$).  We then fitted for the semi-amplitude,
-period, time of conjunction, instrument offsets, and jitter
-parameters.  We converted the resulting posterior in period and
-semi-amplitude to minimum mass and semi-major axis assuming Kepler's
-third law.  The resulting $3\sigma$ limits are shown in
-Figure~\ref{fig:fpscenario}.
-{\it LGB NOTE: the procedure in the preceding paragraph might be modified to
-	instead convert the FEROS limit $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
-		day}^{-1}$ directly into a semi-amplitude limit.}
+Fitting a line to the FEROS velocities, we found that any third body
+in the system would need to induce a linear radial velocity trend with
+amplitude $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
+day}^{-1}$, at 3-$\sigma$ confidence.  The baseline of the FEROS data
+is 253 days; the agreement between the mean Gaia DR2 velocity ($17.44 \pm
+0.64\,$\kms) and that from FEROS ($18.0 \pm 0.1$\kms) in theory places
+an additional limit on linear trends, since the two observation
+epochs are separated by roughly five years.
+
+To place limits on the properties of a possible bound hierarchical companion, we fitted the radial
+velocity data for a Keplerian orbit using wide priors on
+the semi-amplitude and period: $\log K\ [{\rm m\,s^{-1}}] \sim
+\mathcal{U}(1,10^5)$, and $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
+10^{15})$.  We then fitted for the semi-amplitude, period, time of
+conjunction, instrument offsets, and jitter parameters.  We converted
+the resulting posterior in period and semi-amplitude to minimum mass
+and semi-major axis assuming Kepler's third law.  The resulting
+3-$\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
 
@@
 ephemeris was assumed from an initial fit of only the TESS data).  The
-corresponding $2$-$\sigma$ lower limits on the transit depths in
+corresponding 2-$\sigma$ lower limits on the transit depths in
 Cousins-R and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
@@
 populations need to be modeled at the Monte Carlo level.  We opt to
-use \texttt{VESPA} to perform this population modeling
+use \texttt{VESPA} to model the populations
 \citep{morton_efficient_2012,vespa_2015}.
@@
 directorate.
-\tn\ was included on the TESS ``short-cadence'' target list in part
+\tn\ was included on the TESS 2-minute target list in part
 thanks to the Guest Investigator program of G.\ Sacco (G011265).

### 2020-07-23 drivers/make_photometry_mrt_ready.py
make photometry MRT

@@ -1,0 +1,53 @@
+"""
+Make the photometry table.
+"""
+
+import os
+import numpy as np, pandas as pd
+from numpy import array as nparr
+from collections import OrderedDict
+from timmy.convenience import (
+    get_clean_tessphot, get_elsauce_phot, _subset_cut,
+    get_astep_phot
+)
+
+provenance = 'spoc' # could be "cdips"
+yval = 'PDCSAP_FLUX' # could be SAP_FLUX 
+x_obs, y_obs, y_err = get_clean_tessphot(provenance, yval, binsize=None,
+                                         maskflares=1)
+
+datasets = OrderedDict()
+# datasets['tess'] = [x_obs, y_obs, y_err]
+
+datestrs = ['20200401', '20200426', '20200521', '20200614']
+for ix, d in enumerate(datestrs):
+    x_obs, y_obs, y_err = get_elsauce_phot(datestr=d)
+    x_obs -= 2457000 # convert to BTJD
+    datasets[f'elsauce_{ix}'] = [x_obs, y_obs, y_err]
+
+datestrs = ['20200529', '20200614', '20200623']
+for ix, d in enumerate(datestrs):
+    x_obs, y_obs, y_err = get_astep_phot(datestr=d)
+    x_obs += 2450000 # convert to BJD_TDB
+    x_obs -= 2457000 # convert to BTJD
+    datasets[f'astep_{ix}'] = [x_obs, y_obs, y_err]
+
+times, fluxs, errs, instrs = nparr([]), nparr([]), nparr([]), nparr([])
+for k in datasets.keys():
+    times = np.hstack((times, datasets[k][0]))
+    fluxs = np.hstack((fluxs, datasets[k][1]))
+    errs = np.hstack((errs, datasets[k][2]))
+    instrs = np.hstack((instrs, np.repeat(k, len(datasets[k][0]))))
+
+df = pd.DataFrame({
+    'btjd_tdb': np.round(times,8),
+    'flux': np.round(fluxs,6),
+    'fluxerr': np.round(errs,6),
+    'instr': instrs
+})
+
+outpath = '../data/phot/photometry_mrt_ready.csv'
+df.to_csv(outpath, index=False)
+print(outpath)
+
+import IPython; IPython.embed()

### 2020-07-25 paper/ms.tex
update manuscript
Co-authored-by: George Zhou <george.zhou@cfa.harvard.edu>
make photometry MRT
tweak abstract

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-% TODO:
-% * gammadot second method check
-%
 
@@
   NASA TESS mission, the ESA Gaia mission, ground-based photometry
-  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS,
-  and Veloce.  We find that TOI$\,$837 is a $T=9.9$ mag
-  G0/F9 dwarf in the southern open cluster IC 2602.  The star
-  and planet are therefore $35^{+11}_{-5}$ million years old.
-  Combining the transit photometry with a prior on the stellar
-  parameters derived from the cluster color-magnitude diagram, we find
-  that the planet has an orbital period of $8.3\,{\rm d}$ and is
-  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
-  \,R_{\rm Jup}$).  The transits are either grazing or nearly grazing.
-  From radial velocity monitoring, we limit the minimum mass to less
-  than 1.20 $M_{\rm Jup}$ (3-$\sigma$).  Grazing transits are a cause
-  for concern, as they are usually indicative of astrophysical false
-  positive scenarios.  Our follow-up data show that such scenarios are
-  highly unlikely.  Our combined multi-color photometry,
-  high-resolution imaging, and radial velocities rule out hierarchical
-  eclipsing binary scenarios.  Background eclipsing binary scenarios,
-  though limited by speckle imaging, formally remain a 0.2\%
-  possibility.  TOI 837.01 is therefore a validated adolescent
-  exoplanet.  Further observations of its stellar obliquity,
-  atmosphere, and mass should confirm its planetary nature beyond
-  doubt, and could improve our understanding of how the physical and
-  orbital properties of exoplanets change in time.
+  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
+  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
+  southern open cluster IC 2602.  The star and planet are therefore
+  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
+  with a prior on the stellar parameters derived from the cluster
+  color-magnitude diagram, we find that the planet has an orbital
+  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
+  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  The transits
+  are either grazing or nearly grazing.  From radial velocity
+  monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm
+  Jup}$ (3-$\sigma$).  Grazing transits are a cause for concern, as
+  they are often indicative of astrophysical false positive scenarios.
+  Our follow-up data show that such scenarios are highly unlikely.
+  Our combined multi-color photometry, high-resolution imaging, and
+  radial velocities rule out hierarchical eclipsing binary scenarios.
+  Background eclipsing binary scenarios, though limited by speckle
+  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
+  therefore a validated adolescent exoplanet.  The planetary nature of
+  the system can be confirmed or refuted through observations of the
+  stellar obliquity or the planetary mass.  Such observations may also
+  improve our understanding of how the physical and orbital properties
+  of exoplanets change in time.
 \end{abstract}
@@
 shown in Figure~\ref{fig:followup}.
+To check for the presence of secondary lines, we performed a similar
+injection-recovery exercise as with the CHIRON data. 
+We achieved slightly worse limits, likely due to the lower spectral
+resolution of FEROS, and therefore adopted the CHIRON limits.
 

### 2020-07-25 paper/ms.tex
update manuscript
Co-authored-by: Alan Levine <aml@space.mit.edu>

@@
   Cluster Difference Imaging Photometric Survey (CDIPS) II.
-  TOI$\,$837: A Young Validated Planet in IC~2602
+  TOI~837: A Young Validated Planet in IC~2602
 }
@@
 photospheric lithium, and chromospheric diagnostics such as calcium
-emission and broadband UV emission.  Studies by for instance
+emission and broadband UV emission.  Studies by, for instance,
 \citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
@@
 transiting planets.  Many of these latter methods were summarized by
-\citet{mamajek_improved_2008}, and have since been calibrated by {\it
+\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
 e.g.},
@@
 \citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
-planets around V1298~Tau (23$\,$Myr) are also likely to be actively
+planets around V1298~Tau (23$\,$Myr) are also likely to be
 photoevaporating, and could represent a precursor to Kepler's compact
@@
 candidate young stars that have been reported in the literature.  At
-the time writing, of order $6\times10^5$ light curves from the first
-year of TESS observations have been reduced, and are available at
-MAST\footnote{\stscilink} through \datasetlink.  Searching these light
-curves yielded the candidate transiting planet, \pn, that is the
-subject of this analysis.
+the time of writing, we had made $\sim$$6\times10^5$ light curves from
+the first year of TESS observations. The light curves are available at
+MAST\footnote{\stscilink, and see \datasetlink}.  Searching through a
+subset of these light curves brought our attention to the candidate
+transiting planet, \pn, that is the subject of this analysis.
 
@@
 follow-up data show that this and related scenarios are unlikely to
-the degree that we can ``validate'' the planet, {\it i.e.}, rule that
-its probability of being an astrophysical false positive is negligibly
-small.  We considered this result worth reporting because of the
-planet's youth.
+the degree that we can ``validate'' the planet, {\it i.e.}, determine
+that its probability of being an astrophysical false positive is
+negligibly small.  We considered this result worth reporting because
+of the planet's youth.
 
@@
     Starspot-induced variability is the dominant signal; flares are
-    shown with gray crosses.  Dashed lines indicate the five transits
+    shown with red crosses.  Dashed lines indicate the five transits
     observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
@@
     transit.  Gray points are 2-minute measurements with the local
-    spot-induced variation removed.  Black points are binned to
-    6-minute intervals.  The black error-bar shows the median
+    spot-induced variation removed.  Binning at 6-minute intervals
+    yields the black points.  The black error-bar shows the median
     uncertainty for the black points.  The gray line shows the
@@
 The TESS project detected the transits in the 2-minute data and the
-community was alerted on 17 June 2019.  While our CDIPS FFI light
-curves also showed the transits, the 2-minute data had better sampling
-cadence, and so we opted to use the Presearch Data Conditioning (PDC)
-light curve with the default aperture for our
+community was alerted on 17 June 2019.  Our subsequent blind search of
+the CDIPS FFI light curves also showed the transits. Given that the
+2-minute data had better sampling cadence, we opted to use the
+Presearch Data Conditioning (PDC) light curve with the default
+aperture for our
 analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.
@@
   \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
-    Gaia parallax implies this is a giant background star.
+    Gaia parallax implies this is a background giant star.
 \end{itemize}
@@
 photometry was necessary to assess and rule out this possibility
-(Section~\ref{subsec:groundphot}).
+(Section~\ref{subsec:groundphot} and Figure~\ref{fig:groundphot}).
 
@@
     using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome
-    C.  Black points are binned to 10-minute intervals.  The gray line
-    is the best-fit model to the combined TESS and ground-based data.
-    Red and blue lines show 2-$\sigma$ lower limits on the transit
-    depths in the Cousins-R and Johnson-B bandpasses used to rule out
-    specific false positive scenarios (see
-    Section~\ref{subsec:colorphot}).
+    C.  Black points represent the measurements after binning at
+    10-minute intervals. The gray line is the model that best fits the
+    combined TESS and ground-based data.  Red and blue lines show
+    2-$\sigma$ lower limits on the transit depths in the Cousins-R and
+    Johnson-B bandpasses used to rule out specific false positive
+    scenarios (see Section~\ref{subsec:colorphot}).
 		\label{fig:groundphot}
@@
 2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
-of $25\,$s, readout and processed overhead of $25\,$s).  Except for 12
-May, our observations were conducted under stable weather conditions,
-with clear skies, temperatures of about $-70^\circ$C, and wind speeds
-less than 5\,ms$^{-1}$. Due to their poor quality, we exclude from the
-analysis all data collected on May 12. We found that the optimal
-calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
-and 14 pixel (12\,arcsec) radius aperture for observations carried out
-on June and May, respectively.  The data are reported in
-Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.
+of $25\,$s, readout and processing overhead of $25\,$s).  Except for
+12 May, our observations were conducted under stable weather
+conditions, with clear skies, temperatures of about $-70^\circ$C, and
+wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
+exclude from the analysis all data collected on May 12. We found that
+the optimal calibrated light curves of \tn\ correspond to an 11 pixel
+(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
+observations carried out on June and May, respectively.  The data are
+reported in Table~\ref{tab:phot}, and plotted in
+Figure~\ref{fig:groundphot}.
 
@@
 either associated or in chance alignment with TOI 837. No such set of
-lines were found. To determine our detection limits to a blended
-spectroscopic companion, we injected a second set of lines to the mean
-least-squares deconvolution profile derived from the CHIRON
+lines were found. To set limits on the contributions of a close-by
+star to the observed spectrum, we injected a second set of lines to
+the mean least-squares deconvolution profile derived from the CHIRON
 observations. The injection spanned 10,000 different combinations of
@@
 \citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
-telescope at the ESO La Sille Observatory, in Chile. FEROS has a
+telescope at the ESO La Silla Observatory, in Chile. FEROS has a
 resolution of $\approx$48,000 across a spectral range of 350–920 nm.
@@
 elimination of all false positive scenarios and determination that the
-planety's mass is in the substellar regime.
+planet's mass is in the substellar regime.
 
@@
 \subsubsection{Not SB2}
-We determined our detection limits to blended spectroscopic companions
-using the stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
-slowly rotating stellar companion well-separated in velocity, this
-would have revealed companions with flux fractions $F_2/F_1 \gtrsim
-3\%$.  For a companion with rotational broadening of $15\,{\rm
+We derived limits on blended spectroscopic companions using the
+stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
+slowly rotating stellar companion well-separated in velocity, the
+spectra would have revealed companions with flux fractions $F_2/F_1
+\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
 km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
@@
 latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
-For bound companions this is justified through reasoning that coeval
-binary companions to \tn\ would have both longer rotation periods and
-smaller stellar radii. The equatorial velocities of such companions
-would therefore be expected to be smaller than that of \tn.
+% For bound companions this is justified through reasoning that coeval
+% binary companions to \tn\ would have both longer rotation periods and
+% smaller stellar radii. The equatorial velocities of such companions
+% would therefore be expected to be smaller than that of \tn.
 
@@
 For the first fit we set a prior on the period and
-time of periapse using the known ephemeris from the transit.  We then
+time of conjunction using the known ephemeris from the transit.  We then
 fitted for the semi-amplitude, instrument offsets, and jitter
@@
 eclipses are caused by a stellar-mass object orbiting \tn.  The lack
-of a linear radial velocity trend, particularly in the FEROS
-data, further constrains the presence of a hierarchical binary system.
-Fitting a line to the FEROS velocities, we found that any third body
-in the system would need to induce a linear radial velocity trend with
-amplitude $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
-day}^{-1}$, at 3-$\sigma$ confidence.  The baseline of the FEROS data
-is 253 days; the agreement between the mean Gaia DR2 velocity ($17.44 \pm
-0.64\,$\kms) and that from FEROS ($18.0 \pm 0.1$\kms) in theory places
-an additional limit on linear trends, since the two observation
-epochs are separated by roughly five years.
-
-To place limits on the properties of a possible bound hierarchical companion, we fitted the radial
-velocity data for a Keplerian orbit using wide priors on
-the semi-amplitude and period: $\log K\ [{\rm m\,s^{-1}}] \sim
-\mathcal{U}(1,10^5)$, and $\log P\ [{\rm days}] \sim \mathcal{U}(0.1,
-10^{15})$.  We then fitted for the semi-amplitude, period, time of
-conjunction, instrument offsets, and jitter parameters.  We converted
-the resulting posterior in period and semi-amplitude to minimum mass
-and semi-major axis assuming Kepler's third law.  The resulting
-3-$\sigma$ limits are shown in Figure~\ref{fig:fpscenario}.
+of a linear radial velocity trend, particularly in the FEROS data,
+further constrains the presence of a hierarchical binary system.
+Fitting a line to the FEROS velocities yielded a 3-$\sigma$ limit on
+linear radial velocity trends of $|\dot{\gamma}| < 0.82\,{\rm
+m\,s}^{-1}\,{\rm day}^{-1}$, over the 253 day FEROS baseline.  The
+agreement between the mean Gaia DR2 velocity ($17.44 \pm 0.64\,$\kms)
+and that from FEROS ($18.0 \pm 0.1$\kms) in theory places an
+additional limit on linear trends, since the two observation epochs
+are separated by roughly five years.
+
+To place limits on the properties of a possible bound hierarchical
+companion, we fitted the radial velocity data for a Keplerian orbit
+assuming wide logarithmic priors on the semi-amplitude and period:
+$K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm
+days}] \sim \log \mathcal{U}(0.1, 10^{15})$.
+We then fitted for the semi-amplitude, period, time of conjunction,
+instrument offsets, and jitter parameters.  We converted the resulting
+posterior in period and semi-amplitude to minimum mass and semi-major
+axis assuming Kepler's third law.  The resulting 3-$\sigma$ limits are
+shown in Figure~\ref{fig:fpscenario}.
 
@@
 We fitted for the observed depths in different bandpasses using a
-similar machinery as described in Section~\ref{subsec:planet}.  We
+machinery similar to that described below in Section~\ref{subsec:planet}.  We
 fitted each ground-based transit individually for the planet-to-star
@@
 The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
-point-source detections from imaging, and sources that show an
-astrometric excess.  The curve was interpolated from Figure~4 of
+point-source detections from imaging and sources showing an
+astrometric noise excess relative to the single-source astrometric
+model.  The curve was interpolated from Figure~4 of
 \citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
@@
 \citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
-evaluated by forward-modeling a representative population of
-eclipsing bodies for model class, in which each population member has
-a particular trapezoidal eclipse depth, total duration, and ingress
+evaluated by forward-modeling a representative population of eclipsing
+bodies for each model class, in which each population member has a
+particular trapezoidal eclipse depth, total duration, and ingress
 duration.  The likelihood is then calculated by multiplying the
-probability distribution function of simulated population's shape
+probability distribution function of the simulated population's shape
 parameters with the posterior probability of the actual observed
@@
   \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
-  within 5 standard deviations of the mean \cn\ right ascension,
-  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
-  $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST isochrones (colored lines)
-  fit the upper main sequence well, but diverge from the data for
-  $M_\star \lesssim 0.7 M_\odot$. This is a known issue with the
-  M dwarf models (see Section~\ref{subsec:hr}).
+  with right ascension, declination, and parallax similar to \cn.
+  They are selected by drawing from a $(\alpha, \delta, \pi)$ cube
+  centered on the cluster with boundaries set at $5\times$ the
+  standard deviation in the cluster parameters.  $G$ denotes Gaia
+  broadband magnitudes, $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST
+  isochrones (colored lines) fit the upper main sequence well, but
+  diverge from the data for $M_\star \lesssim 0.7 M_\odot$. This is a
+  known issue with the M dwarf models (see Section~\ref{subsec:hr}).
   \label{fig:hr}
@@
   circles), and stars in the neighborhood (gray circles).} Members
-  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
+  were identified by \citet{cantatgaudin_gaia_2018}. 
+  Neighbors are as in Figure~\ref{fig:hr}. $\alpha$ denotes
   right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
@@
 
-Reliable ages reported for \cn\ range from 30--46$\,$Myr.  We have
+Reliable ages reported for \cn\ range from 30 to 46$\,$Myr.  We have
 collected ages reported over the years in Table~\ref{tab:ages}.  The
@@
 Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
-\cn\ cluster, and the ``neighborhood'' of spatially nearby stars.
-Stars labeled as ``cluster members'' are those reported by
+\cn\ cluster, and the neighborhood of spatially nearby stars.
+Stars labeled as cluster members are those reported by
 \citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
@@
 other members along the cluster isochrone.  This photometrically
-limits the presence of binary companions in the \tn\ system, to within
-perhaps half the brightness ($\approx0.75$ magnitudes) of the target
+limits the presence of binary companions in the \tn\ system to be less
+than half the brightness ($\approx0.75$ magnitudes) of the target
 star.
@@
 Figure~\ref{fig:hr} suggests that the membership census of \cn\ is
-incomplete.  We defined the reference ``neighborhood'' as the group of
-at most $10^4$ randomly selected non-member stars within 5 standard
+incomplete.  We defined the reference neighborhood as the group of at
+most $10^4$ randomly selected non-member stars within 5 standard
 deviations of the mean \cn\ right ascension, declination, and
-parallax.  We queried Gaia DR2 for these stars using
-\texttt{astroquery} \citep{astroquery_2018}.  Many low-mass stars
-appear above the main sequence, even though they were not identified
-as 5-dimensional kinematic members through the unsupervised
-\citet{cantatgaudin_gaia_2018} membership assignment process.
+parallax.  In other words, the neighborhood members are chosen based
+on the observed spread in the cluster's parameters.  We queried Gaia
+DR2 for these stars using \texttt{astroquery} \citep{astroquery_2018}.
+Many low-mass stars appear above the main sequence, even though they
+were not identified as 5-dimensional kinematic members through the
+unsupervised \citet{cantatgaudin_gaia_2018} membership assignment
+process.
 
@@
 \citep{choi_mesa_2016}.  We used the
-web-interace\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
+web interface\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
 \texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
@@
 Myr models align well with the data for stars with masses ranging from
-roughly $0.7$--$7\,M_\odot$.  The PMS K and M dwarf models are bluer
-than observed in the Gaia photometry.  This discrepancy was noted and
-discussed at length by \citet{choi_mesa_2016}.  One suggested
-explanation was that strong magnetic fields in low-mass
-pre-main-sequence stars inhibit convection and produce a high filling
-factor of starspots \citep[{\it
+roughly $0.7$--$7\,M_\odot$.  The pre-main-sequence (PMS) K and M
+dwarf models are bluer than observed in the Gaia photometry.  This
+discrepancy was noted and discussed at length by
+\citet{choi_mesa_2016}.  One suggested explanation was that strong
+magnetic fields in low-mass pre-main-sequence stars inhibit convection
+and produce a high filling factor of starspots \citep[{\it
 e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
@@
 initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
-2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier terms in
+2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier term in
 the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
-when allowing for two Fourier terms.  As the second model provides a
-better fit to the data, we adopt the second measurement.
+when allowing for two Fourier terms.  As the latter model provides a
+better fit to the data, we adopt it as the rotation period.
 
@@
 whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
-The transit is therefore either grazing, or nearly grazing.   The
-relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  From experimenting with the priors, we
+The relevant posterior probabilities are shown in
+Figure~\ref{fig:subsetcorner}.  The transit is therefore either
+grazing, or nearly grazing.  From experimenting with the priors, we
 found that in the absence of a strong prior on the stellar density,

### 2020-07-25 timmy/plotting.py

@@ -2853,8 +2853,8 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
     yval = (flux - np.nanmedian(flux))*1e3
     ax0.scatter(time[~flaresel], yval[~flaresel], c='k', zorder=3, s=0.5,
                 rasterized=True, linewidths=0)
-    ax0.scatter(time[flaresel], yval[flaresel], c='darkgray', zorder=3, s=1,
-                marker='x', rasterized=True, linewidth=0.1)
+    ax0.scatter(time[flaresel], yval[flaresel], c='red', zorder=3, s=1,
+                marker='x', rasterized=True, linewidth=0.2)
     ax0.set_ylim((-20, 20)) # omitting like 1 upper point from the big flare at time 38
     ymin, ymax = ax0.get_ylim()
     ax0.vlines(
@@ -2906,8 +2906,8 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
                            c='k', zorder=3, s=size, rasterized=False, linewidths=0)
                 ax.scatter(24*(time[s][_flaresel]-mid_time),
                            (flux[s] - np.nanmedian(flux[s]))[_flaresel]*1e3,
-                           c='darkgray', zorder=3, s=size, rasterized=False,
-                           linewidth=0.1, marker='x')
+                           c='red', zorder=3, s=size, rasterized=False,
+                           linewidth=0.2, marker='x')
             else:
                 ax.scatter(24*(time[s][~_flaresel]-mid_time),
                            (flux[s] - np.nanmedian(flux[s]))[~_flaresel]*1e3,
@@ -2915,8 +2915,8 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
                            linewidths=0, alpha=0.5)
                 ax.scatter(24*(time[s][_flaresel]-mid_time),
                            (flux[s] - np.nanmedian(flux[s]))[_flaresel]*1e3,
-                           c='darkgray', zorder=3, s=size, rasterized=False,
-                           linewidth=0.1, marker='x')
+                           c='red', zorder=3, s=size, rasterized=False,
+                           linewidth=0.2, marker='x')
                 xval, yval = (
                     (time[s][~_flaresel]-mid_time),
                     (flux[s] - np.nanmedian(flux[s]))[~_flaresel]*1e3

### 2020-07-27 paper/ms.tex
update manuscript

@@
 collision between the proto-Earth and a planetesimal during Earth's
-first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.
+first 100 million years \citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.
 
@@
 After accreting, planets with gaseous envelopes are thought to cool
-and contract, and their atmospheres are expected to undergo
-photoevaporation \citep[{\it
+and contract, and their atmospheres are expected to undergo a mix of
+photoevaporation and core-powered mass loss \citep[{\it
 e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
-The relative importance of contraction and photoevaporation is set by
-the planetary mass, as well as the radiation environment.  The
-effectiveness of photoevaporation can be inferred from observations of
+The relative importance of cooling and photoevaporation is set by the
+planetary surface gravity, as well as the radiation environment.  The
+timescale for core-powered mass loss may in some cases exceed the
+$\sim$100 Myr during which photoevaporation is expected to be
+effective \citep{ginzburg_superearth_2016,owen_evaporation_2017}.
+Both processes could be directly observed through observations of
 planetary winds in the metastable 1083$\,$nm He line
@@
 oscillations can also occur \citep[{\it
-e.g.},][]{chatterjee_dynamical_2008,lithwick_secular_2014,fabrycky_shrinking_2007}.
+e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
 The circularization timescale is thought to be such that for any giant
@@
 RV surveys of highly active pre-main sequence stars in Taurus also led
-to the youngest hot Jupiters yet reported
+to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
+CI~Tau
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
+Follow-up by Damasso et al{.} (2020, submitted) did not detect
+the planetary signal in V830~Tau.
 
@@
 the first year of TESS observations. The light curves are available at
-MAST\footnote{\stscilink, and see \datasetlink}.  Searching through a
+MAST\footnote{\stscilink}, and through \datasetlink.  Searching through a
 subset of these light curves brought our attention to the candidate

### 2020-07-28 paper/ms.tex
update manuscript

@@
 e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
-The relative importance of cooling and photoevaporation is set by the
-planetary surface gravity, as well as the radiation environment.  The
-timescale for core-powered mass loss may in some cases exceed the
-$\sim$100 Myr during which photoevaporation is expected to be
-effective \citep{ginzburg_superearth_2016,owen_evaporation_2017}.
-Both processes could be directly observed through observations of
-planetary winds in the metastable 1083$\,$nm He line
+Reported timescales for photoevaporation and core-powered mass loss
+range from 10$\,$Myr to over 1$\,$Gyr for typical transiting
+sub-Neptunes
+\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
+The relative importance of each process is set by the planetary surface
+gravity and the radiation environment.  Both processes can be
+directly observed through observations of planetary winds in the
+metastable 1083$\,$nm He line
 \citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.
@@
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
-Follow-up by Damasso et al{.} (2020, submitted) did not detect
-the planetary signal in V830~Tau.
+%Follow-up by Damasso et al{.} (2020, submitted) did not detect
+%the planetary signal in V830~Tau.
 

### 2020-07-28 paper/ms.tex
update manuscript
Co-authored-by: Chris Tinney <c.tinney@unsw.edu.au>

@@
 e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
-Reported timescales for photoevaporation and core-powered mass loss
-range from 10$\,$Myr to over 1$\,$Gyr for typical transiting
+Predicted timescales for photoevaporation and core-powered mass loss
+range from 10 million years to over 1 gigayear for typical transiting
 sub-Neptunes
@@
 RV surveys of highly active pre-main sequence stars in Taurus also led
-to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
-CI~Tau
+to the youngest hot Jupiters yet reported orbiting
+V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
+not detect the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
-%Follow-up by Damasso et al{.} (2020, submitted) did not detect
-%the planetary signal in V830~Tau.
 
@@
 
-The transits of \pn\ are grazing, which is a cause for concern.
-Particularly for a target near the galactic plane ($b=-5.8^\circ$),
-background eclipsing binaries are a major source of astrophysical
-false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
-follow-up data show that this and related scenarios are unlikely to
-the degree that we can ``validate'' the planet, {\it i.e.}, determine
-that its probability of being an astrophysical false positive is
-negligibly small.  We considered this result worth reporting because
-of the planet's youth.
+The transits of \pn\ are grazing the stellar limb, which is a cause
+for concern.  Particularly for a target near the galactic plane
+($b=-5.8^\circ$), background eclipsing binaries are a major source of
+astrophysical false positives \citep[{\it
+e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
+and related scenarios are unlikely to the degree that we can
+``validate'' the planet, {\it i.e.}, determine that its probability of
+being an astrophysical false positive is negligibly small.  We
+considered this result worth reporting because of the planet's youth.
 
@@
 induced by starspots coming into and out of view has a peak-to-peak
-amplitude of about 2.3\%, and a period of about 3 days.  The dips
-suggestive of a grazing transiting planet recur roughly every 8 days,
-and have a depth of about 0.4\%.  A few flares are also visible.  A
+amplitude of about 2.3\%, and a period of about 3 days.  The dips are
+suggestive of a grazing transiting planet, recurring roughly every 8
+days with a depth of about 0.4\%.  A few flares are also visible.  A
 phase-folded view of the TESS transits with starspot variability
@@
 We acquired 34 spectra over 10 visits of \tn\ using the Veloce
-spectrograph, mounted on the AAT 3.9$\,$m telescope at Siding Spring
-Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
-In the ``Rosso'' instrument-mode, Veloce provides coverage from
-600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
-of the exposures were taken in average or poor seeing conditions, when
-fiber-to-fiber cross-contamination on the IFU-style fiber feed is
-strongest.  To reduce the spectra to velocities, we cross-correlated
-against a high S/N template of $\delta$ Pavonis, because with spectral
-type G8 IV it was the closest \tn\ analog available in the Veloce
-spectral database.  The velocity RMS seen across each visit was
-hundreds of meters per second, likely due to uncorrected
-fiber-to-fiber cross-contamination.  For analysis purposes, we
-averaged across each visit, and set the velocity uncertainties to be
-the standard deviation of the per-visit exposures.  The velocities are
-given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.
+spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
+Siding Spring Observatory near Coonabarabran, Australia
+\citep{gilbert_veloce_2018}.  Veloce's currently implemented Rosso
+camera provides coverage from 600--950$\,$nm at a spectral resolution
+of $\approx 80{,}000$.  Many of the exposures were taken in average or
+poor seeing conditions, when fiber-to-fiber cross-contamination on the
+IFU-style fiber feed is strongest.  To reduce the spectra to
+velocities, we cross-correlated against a high S/N template of
+$\delta$ Pavonis, because with spectral type G8 IV it was the closest
+\tn\ analog available in the Veloce spectral database.  The velocity
+RMS seen across each visit was hundreds of meters per second, likely
+due to uncorrected fiber-to-fiber cross-contamination.  For analysis
+purposes, we averaged across each visit, and set the velocity
+uncertainties to be the standard deviation of the per-visit exposures.
+The velocities are given in Table~\ref{tab:rvs}, and shown in
+Figure~\ref{fig:followup}.
 
@@
 from FONDECYT project 1171208.  J.I.V\ acknowledges support from
-CONICYT-PFCHA/Doctorado Nacional-21191829.
-R.B.\ acknowledges support from FONDECYT Post-doctoral Fellowship Project 3180246.
+CONICYT-PFCHA/Doctorado Nacional-21191829.  R.B.\ acknowledges support
+from FONDECYT Post-doctoral Fellowship Project 3180246.
+%
+C.T.\ and C.B\ acknowledge support from Australian Research Council
+grants LE150100087, LE160100014, LE180100165, DP170103491 and
+DP190103688.
 %

### 2020-07-28 drivers/make_TOI837_rv_table.py

@@ -23,8 +23,8 @@ def main():
 
     outdf = pd.DataFrame(
         {'time': np.round(nparr(df.time-2450000),6),
-         'mnvel': np.round(nparr(df.mnvel),2),
-         'errvel': np.round(nparr(df.errvel),2),
+         'mnvel': np.round(nparr(df.mnvel),1),
+         'errvel': np.round(nparr(df.errvel),1),
          'tel': nparr(df.tel)
         }
     )

### 2020-07-28 paper/ms.tex
update manuscript
Co-authored-by: Alan Levine <aml@space.mit.edu>

@@
 by \citet{tokovinin_ten_2018}.  The points in
-Figure~\ref{fig:followup} show the resulting measured 5-$\sigma$
+Figure~\ref{fig:speckle} show the resulting measured 5-$\sigma$
 detectable contrasts.  The lines are linear smoothing fits between the
@@
 		\leavevmode
-		\subfloat{
-			\includegraphics[width=0.44\textwidth]{f6.pdf}
-		}
-
-		\vspace{-0.3cm}
-		\subfloat{
-			\includegraphics[width=0.47\textwidth]{f3.pdf}
-		}
+		\includegraphics[width=.44\textwidth]{f6.pdf}
 	\end{center}
-	\vspace{-0.6cm}
+	\vspace{-0.7cm}
 	\caption{
-    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:} SOAR
-    HRCam contrast limits derived from point-source injection-recovery
+    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR
+    HRCam imaging were derived from point-source injection-recovery
     experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
@@
     its parallax and on-sky position imply that it is physically
-    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
-    Radial velocity (RV) measurements, with best-fit instrument
-    offsets and jitter terms included.  The expected scatter from
-    starspots based on $v\sin i$ and the photometric modulation
-    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
-    measurements phased to the orbital ephemeris of \pn.  The planet
-    is not detected.  The black line shows a circular Keplerian orbit
-    representing the 3-$\sigma$ upper mass limit.
-		\label{fig:followup}
+    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  
+		\label{fig:speckle}
+	}
+\end{figure}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=.47\textwidth]{f3.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
+    measurements, with best-fit instrument offsets and jitter terms
+    included.  The expected scatter from starspots based on $v\sin i$
+    and the photometric modulation amplitude is of order
+    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
+    orbital ephemeris of \pn.  The planet is not detected.  The black
+    line shows a circular Keplerian orbit representing the 3-$\sigma$
+    upper mass limit.
+    \label{fig:rvs}
 	}
@@
 velocities listed in Table~\ref{tab:rvs} and shown in
-Figure~\ref{fig:followup}. We found a mean rotational broadening
+Figure~\ref{fig:rvs}. We found a mean rotational broadening
 velocity of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
@@
 G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
-shown in Figure~\ref{fig:followup}.
+shown in Figure~\ref{fig:rvs}.
 To check for the presence of secondary lines, we performed a similar
@@
 The velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:followup}.
+Figure~\ref{fig:rvs}.
 
@@
 		\leavevmode
-		\includegraphics[width=0.8\textwidth]{f4.pdf}
+		\includegraphics[width=0.75\textwidth]{f4.pdf}
 	\end{center}
@@
 In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
-binary host blend together, and reduce the ``true'' eclipse depth
+binary host blend together, and reduce the ``true'' TESS-band eclipse depth
 $\delta_{\rm true}$ to the observed depth
@@
 $M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
-model are shown in Figure~\ref{fig:followup}.
+model are shown in Figure~\ref{fig:rvs}.
 
@@
 \subsection{False positive probability}
+\label{subsec:fpp}
 
@@
 Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
-ages.  \tn\ is among the youngest transiting planets known.  While we
-have statistically validated that \tn\ is a planet, the possibility
-that it is a background eclipsing binary has not been excluded with
+ages.  \tn\ is among the youngest transiting planets known.
+
+While we
+have statistically validated that \tn\ is a planet,
+the possibility
+that it could be a background eclipsing binary has not been excluded with
 sufficient confidence to call the planet ``confirmed''.
-
-The easiest path towards definitively confirming whether \tn\ is a
-planet will be a Rossiter-McLaughlin (RM) measurement.  Detection of
+The distinction is methodological.
+Our calculations have shown that at a population
+level we expect negligibly few BEBs within $\approx0.3''$ of \tn\ to
+produce eclipses of the appropriate shape across all bandpasses, with
+no observed secondary eclipse or odd-even variations (Section~\ref{subsec:fpp}).
+This statement is tautologically ``validation'', but it is weaker
+than having data on hand that conclusively
+rules in favor of the planetary interpretation.
+
+The easiest path towards definitively confirming the planetary
+nature of \tn\ will be a Rossiter-McLaughlin (RM) measurement.  Detection of
 an RM signal consistent with the photometric transit would rule out
@@
 variation expected over the course of the $\approx 3\,{\rm d}$
-rotation period can then be estimated by multiplying the photometric
+rotation period can be estimated by multiplying the photometric
 amplitude and spectroscopic equatorial velocity.  This gives
@@
 with the scatter we observe in our radial velocities from FEROS.
-Detecting a planet's Doppler signal in these regimes is challenging,
-and requires a significant amount of data and care in signal
-extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
-measurement avoids the majority of this issue because the transit
-occurs over a much shorter duration than a single stellar rotation
-period.
+Detecting the radial velocity signature of a planet's Keplerian motion
+in this regime is challenging, and requires a significant amount of
+data and care in signal extraction \citep{barragan_radial_2019}.  The
+Rossiter-McLaughlin measurement avoids the majority of this issue
+because the transit occurs over a much shorter duration than a single
+stellar rotation period.
 
@@
 and 37 (late March to late May of 2021) would significantly ease the
-extraction of the planetary Doppler signal.  The reason is that the
-RVs, activity indicators, and photometry could be modeled
-simultaneously \citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This
-would greatly constrain models of the spot-induced RV signal.  The
-mass measurement would likely be worthwhile in order to improve
-understanding of the planet's contraction and photoevaporation
-history.
+extraction of the planetary mass.  The reason is that the RVs,
+activity indicators, and photometry could be modeled simultaneously
+\citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This would greatly
+constrain models of the spot-induced RV signal.  The mass measurement
+would be a worthy goal in order to improve understanding of the
+planet's contraction and photoevaporation history.
 
 While we hope that RV observations will be pursued, data acquired
-during the first TESS mission extension may also help in understanding
+during the TESS mission extension may also help in understanding
 the system \citep{bouma_extend_2017,huang_expected_2018}.  Any

### 2020-07-28 paper/ms.tex
latex column width

@@
 collision between the proto-Earth and a planetesimal during Earth's
-first 100 million years \citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.
+first 100 million years
+\citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.
 
@@
 \citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
-The relative importance of each process is set by the planetary surface
-gravity and the radiation environment.  Both processes can be
+The relative importance of each process is set by the planetary
+surface gravity and the radiation environment.  Both processes can be
 directly observed through observations of planetary winds in the
@@
 the first year of TESS observations. The light curves are available at
-MAST\footnote{\stscilink}, and through \datasetlink.  Searching through a
-subset of these light curves brought our attention to the candidate
-transiting planet, \pn, that is the subject of this analysis.
+MAST\footnote{\stscilink}, and through \datasetlink.  Searching
+through a subset of these light curves brought our attention to the
+candidate transiting planet, \pn, that is the subject of this
+analysis.
 
@@
   \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
-    proper motions and parallax of this star imply it is co-moving with
-    \tn\ and that the two stars are separated by $6.6\pm 0.1\,{\rm pc}$.
-    Star A is therefore likely an \cn\ member, but unlikely to be a bound
-    binary companion.
+    proper motions and parallax of this star imply it is co-moving
+    with \tn\ and that the two stars are separated by $6.6\pm
+    0.1\,{\rm pc}$.  Star A is therefore likely an \cn\ member, but
+    unlikely to be a bound binary companion.
   %
@@
 \citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
-by \citet{tokovinin_ten_2018}.  The points in
-Figure~\ref{fig:speckle} show the resulting measured 5-$\sigma$
-detectable contrasts.  The lines are linear smoothing fits between the
-regimes of the diffraction limit, the ``knee'' at $\approx 0.2''$, and
-the slow decrease until $\approx 1.5''$, beyond which the speckle
-patterns become de-correlated.  Star A (TIC 847769574) was detected at
-the expected location and brightness contrast, and no additional
-companions were found.  Star B was not detected; with a separation of
-$5.4''$ from \tn, it fell outside the field of view.
+by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:speckle}
+show the resulting measured 5-$\sigma$ detectable contrasts.  The
+lines are linear smoothing fits between the regimes of the diffraction
+limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
+$\approx 1.5''$, beyond which the speckle patterns become
+de-correlated.  Star A (TIC 847769574) was detected at the expected
+location and brightness contrast, and no additional companions were
+found.  Star B was not detected; with a separation of $5.4''$ from
+\tn, it fell outside the field of view.
 
@@
 	\caption{
-    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR
-    HRCam imaging were derived from point-source injection-recovery
+    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
+    imaging were derived from point-source injection-recovery
     experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
@@
 velocities listed in Table~\ref{tab:rvs} and shown in
-Figure~\ref{fig:rvs}. We found a mean rotational broadening
-velocity of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
+Figure~\ref{fig:rvs}. We found a mean rotational broadening velocity
+of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
 macroturbulent broadening of $v_\mathrm{Mac} = 8.4 \pm 2.9
@@
 4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.
-We ultimately adopted a different set of stellar parameters for 
-our analysis (see Section~\ref{subsec:starparams}).
+We ultimately adopted a different set of stellar parameters for our
+analysis (see Section~\ref{subsec:starparams}).
 
@@
 G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
-shown in Figure~\ref{fig:rvs}.
-To check for the presence of secondary lines, we performed a similar
-injection-recovery exercise as with the CHIRON data. 
-We achieved slightly worse limits, likely due to the lower spectral
-resolution of FEROS, and therefore adopted the CHIRON limits.
+shown in Figure~\ref{fig:rvs}.  To check for the presence of secondary
+lines, we performed a similar injection-recovery exercise as with the
+CHIRON data.  We achieved slightly worse limits, likely due to the
+lower spectral resolution of FEROS, and therefore adopted the CHIRON
+limits.
 
@@
 In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
-binary host blend together, and reduce the ``true'' TESS-band eclipse depth
-$\delta_{\rm true}$ to the observed depth
-$\delta_{\rm obs}$:
+binary host blend together, and reduce the ``true'' TESS-band eclipse
+depth $\delta_{\rm true}$ to the observed depth $\delta_{\rm obs}$:
 \begin{equation}
@@
 luminosities to expected magnitudes in instrumental bandpasses, we
-made the simplifying assumption that all sources had blackbody spectra.
-Using the theoretical stellar parameters and the measured transmission
-functions \citep{tokovinin_ten_2018}, we then calculated the apparent
-magnitudes of stellar companions of different masses, and interpolated
-to produce the scale shown on the upper-right in
+made the simplifying assumption that all sources had blackbody
+spectra.  Using the theoretical stellar parameters and the measured
+transmission functions \citep{tokovinin_ten_2018}, we then calculated
+the apparent magnitudes of stellar companions of different masses, and
+interpolated to produce the scale shown on the upper-right in
 Figure~\ref{fig:fpscenario}.
@@
 latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
-% For bound companions this is justified through reasoning that coeval
-% binary companions to \tn\ would have both longer rotation periods and
-% smaller stellar radii. The equatorial velocities of such companions
-% would therefore be expected to be smaller than that of \tn.
 
 \subsubsection{RVs}
-The radial velocities from FEROS, CHIRON, and Veloce can be
-used to detect massive bound companions orbiting \tn.  We searched for
-the presence of planetary and stellar-mass companions using
+The radial velocities from FEROS, CHIRON, and Veloce can be used to
+detect massive bound companions orbiting \tn.  We searched for the
+presence of planetary and stellar-mass companions using
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
@@
 % timmy.drivers.oneoff_drivers.get_mass_upper_limit
-For the first fit we set a prior on the period and
-time of conjunction using the known ephemeris from the transit.  We then
-fitted for the semi-amplitude, instrument offsets, and jitter
-parameters.  This yielded a non-detection of the planet's orbit.  The
-corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
-$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
-model are shown in Figure~\ref{fig:rvs}.
+For the first fit we set a prior on the period and time of conjunction
+using the known ephemeris from the transit.  We then fitted for the
+semi-amplitude, instrument offsets, and jitter parameters.  This
+yielded a non-detection of the planet's orbit.  The corresponding
+3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on $M_{\rm p} \sin
+i$ is $1.20 M_{\rm Jup}$.  The data and corresponding model are shown
+in Figure~\ref{fig:rvs}.
 
@@
 companion, we fitted the radial velocity data for a Keplerian orbit
-assuming wide logarithmic priors on the semi-amplitude and period:
-$K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm
-days}] \sim \log \mathcal{U}(0.1, 10^{15})$.
-We then fitted for the semi-amplitude, period, time of conjunction,
-instrument offsets, and jitter parameters.  We converted the resulting
-posterior in period and semi-amplitude to minimum mass and semi-major
-axis assuming Kepler's third law.  The resulting 3-$\sigma$ limits are
-shown in Figure~\ref{fig:fpscenario}.
+assuming wide logarithmic priors on the semi-amplitude and period: $K\
+[{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}]
+\sim \log \mathcal{U}(0.1, 10^{15})$.  We then fitted for the
+semi-amplitude, period, time of conjunction, instrument offsets, and
+jitter parameters.  We converted the resulting posterior in period and
+semi-amplitude to minimum mass and semi-major axis assuming Kepler's
+third law.  The resulting 3-$\sigma$ limits are shown in
+Figure~\ref{fig:fpscenario}.
 
@@
 We fitted for the observed depths in different bandpasses using a
-machinery similar to that described below in Section~\ref{subsec:planet}.  We
-fitted each ground-based transit individually for the planet-to-star
-size ratio, the impact parameter, and a local quadratic trend (the
-ephemeris was assumed from an initial fit of only the TESS data).  The
-corresponding 2-$\sigma$ lower limits on the transit depths in
-Cousins-R and Johnson-B band light curves were 2.82 and 1.77$\,$ppt,
-respectively, and are shown in Figure~\ref{fig:groundphot}.
-Particularly in our Johnson-B light curve, the transit depth is
-correlated with the mean and linear slope of the light curve: a
-smaller depth is allowed if the data are fitted with a larger linear
-slope and a larger mean.  Our quoted limits marginalize over these
-correlations, and the depth measurement itself is nearly Gaussian.
+machinery similar to that described below in
+Section~\ref{subsec:planet}.  We fitted each ground-based transit
+individually for the planet-to-star size ratio, the impact parameter,
+and a local quadratic trend (the ephemeris was assumed from an initial
+fit of only the TESS data).  The corresponding 2-$\sigma$ lower limits
+on the transit depths in Cousins-R and Johnson-B band light curves
+were 2.82 and 1.77$\,$ppt, respectively, and are shown in
+Figure~\ref{fig:groundphot}.  Particularly in our Johnson-B light
+curve, the transit depth is correlated with the mean and linear slope
+of the light curve: a smaller depth is allowed if the data are fitted
+with a larger linear slope and a larger mean.  Our quoted limits
+marginalize over these correlations, and the depth measurement itself
+is nearly Gaussian.
 
@@
   circles), and stars in the neighborhood (gray circles).} Members
-  were identified by \citet{cantatgaudin_gaia_2018}. 
-  Neighbors are as in Figure~\ref{fig:hr}. $\alpha$ denotes
-  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
-  \delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
-  direction, and ${\rm RV}$ radial velocity reported by Gaia DR2.  The
-  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
-  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
-  \alpha}\cos\delta$) highlights incompleteness in the membership
-  selection function.
+  were identified by \citet{cantatgaudin_gaia_2018}.  Neighbors are as
+  in Figure~\ref{fig:hr}. $\alpha$ denotes right ascension, $\delta$
+  declination, $\pi$ parallax, $\mu_{\rm \delta}$ and $\mu_{\rm
+  \alpha}$ proper motion in each equatorial direction, and ${\rm RV}$
+  radial velocity reported by Gaia DR2.  The RVs are for unblended
+  spectra of bright stars ($G\lesssim 12$).  The proper motion
+  projection ($\mu_{\delta}$ vs{.} $\mu_{\rm \alpha}\cos\delta$)
+  highlights incompleteness in the membership selection function.
   \label{fig:full_kinematics}
@@
   \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
-    and \citet{curtis_temporary_2019}, respectively.
-    {\it Bottom:} Lithium 6708\AA\ equivalent widths for \tn, field
-    stars, and young open clusters.  The field star sample is drawn
-    from Kepler planet hosts, and was measured by
-    \citet{berger_identifying_2018} using Keck-HIRES.  The young open
-    clusters members were surveyed by \citet{randich_gaiaeso_2018}
-    using the UVES and GIRAFFE spectrographs at the ESO VLT.
-    \citet{randich_gaiaeso_2018} found lithium depletion boundary ages
-    for these clusters of $37.7^{+5.7}_{-4.8}\,{\rm Myr}$
-    (NGC$\,$2547) and $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
+  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
+  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
+  open clusters.  The field star sample is drawn from Kepler planet
+  hosts, and was measured by \citet{berger_identifying_2018} using
+  Keck-HIRES.  The young open clusters members were surveyed by
+  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
+  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
+  lithium depletion boundary ages for these clusters of
+  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
+  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
     \label{fig:lithium_rotation}
@@
 Figure~\ref{fig:hr} also compares the data to the MIST isochrones
-\citep{choi_mesa_2016}.  We used the
-web interface\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
+\citep{choi_mesa_2016}.  We used the web
+interface\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
 \texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
@@
     {\bf Posterior probabilities of impact parameter, planet-to-star
-    size ratio, and stellar density.} 
-    Contours are shown at 1, 2, 3, and 4-$\sigma$ confidence.
-    The planet-to-star size ratio
+    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
+    and 4-$\sigma$ confidence.  The planet-to-star size ratio
     corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
@@
 
-While we
-have statistically validated that \tn\ is a planet,
-the possibility
-that it could be a background eclipsing binary has not been excluded with
-sufficient confidence to call the planet ``confirmed''.
-The distinction is methodological.
-Our calculations have shown that at a population
-level we expect negligibly few BEBs within $\approx0.3''$ of \tn\ to
-produce eclipses of the appropriate shape across all bandpasses, with
-no observed secondary eclipse or odd-even variations (Section~\ref{subsec:fpp}).
-This statement is tautologically ``validation'', but it is weaker
-than having data on hand that conclusively
-rules in favor of the planetary interpretation.
-
-The easiest path towards definitively confirming the planetary
-nature of \tn\ will be a Rossiter-McLaughlin (RM) measurement.  Detection of
-an RM signal consistent with the photometric transit would rule out
-BEB and HEB scenarios, as it would imply that the eclipsing object is
-bound to the target star. Combined with our non-detection of the
-planet's mass from radial velocity monitoring, this would confirm that
-\pn\ is a planet.
+While we have statistically validated that \tn\ is a planet, the
+possibility that it could be a background eclipsing binary has not
+been excluded with sufficient confidence to call the planet
+``confirmed''.  The distinction is methodological.  Our calculations
+have shown that at a population level we expect negligibly few BEBs
+within $\approx0.3''$ of \tn\ to produce eclipses of the appropriate
+shape across all bandpasses, with no observed secondary eclipse or
+odd-even variations (Section~\ref{subsec:fpp}).  This statement is
+tautologically ``validation'', but it is weaker than having data on
+hand that conclusively rules in favor of the planetary interpretation.
+
+The easiest way to definitively confirm the planetary nature of \tn\
+will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
+signal consistent with the photometric transit would rule out BEB and
+HEB scenarios, as it would imply that the eclipsing object is bound to
+the target star. Combined with our non-detection of the planet's mass
+from radial velocity monitoring, this would confirm that \pn\ is a
+planet.
 
@@
 While we hope that RV observations will be pursued, data acquired
-during the TESS mission extension may also help in understanding
-the system \citep{bouma_extend_2017,huang_expected_2018}.  Any
+during the TESS mission extension may also help in understanding the
+system \citep{bouma_extend_2017,huang_expected_2018}.  Any
 misalignment between the star's spin axis and the planet's orbit

### 2020-07-28 paper/ms.tex
update manuscript

@@
 \newcommand{\tn}{TOI~837} % target star name
-\newcommand{\pn}{TOI~837.01} % planet name
+\newcommand{\pn}{TOI~837b} % planet name
 \newcommand{\cn}{IC~2602} % cluster name
@@
 \begin{abstract}
-  We report the discovery of TOI 837.01 and its validation as a
+  We report the discovery of TOI 837b and its validation as a
   transiting planet.  We characterize the system using data from the
@@
   Background eclipsing binary scenarios, though limited by speckle
-  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
+  imaging, formally remain a 0.2\% possibility.  TOI 837b is
   therefore a validated adolescent exoplanet.  The planetary nature of
@@
 \subsubsection{FEROS}
-TOI 837.01 was monitored with the FEROS echelle spectrograph
+TOI 837b was monitored with the FEROS echelle spectrograph
 \citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m

### 2020-07-29 paper/collect.sh
update manuscript with pretty plots

@@ -27,6 +27,6 @@ cp ${rdir}rotation/rotation.pdf f9b.pdf
 
 cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.pdf f10.pdf
 
-cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200713_toi837.pdf f11.pdf
+cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200729_toi837.pdf f11.pdf
 
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-07-29 paper/ms.tex
update manuscript with pretty plots
update manuscript

@@
 
-Finding and studying systems undergoing these evolutionary changes is
+Finding and understanding systems undergoing these evolutionary changes is
 a major goal in contemporary exoplanet research.  To identify stars
@@
 V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
-not detect the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
+not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
@@
 
-With the aim of advancing the young planet census, we have been using
-data from the TESS spacecraft \citep{ricker_transiting_2015} to
-perform a Cluster Difference Imaging Photometric Survey
+To advance the young planet census, we have been using data from the
+TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
+Difference Imaging Photometric Survey
 \citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
@@
 The transits of \pn\ are grazing the stellar limb, which is a cause
-for concern.  Particularly for a target near the galactic plane
+for concern.  Particularly for a star near the galactic plane
 ($b=-5.8^\circ$), background eclipsing binaries are a major source of
@@
 and related scenarios are unlikely to the degree that we can
-``validate'' the planet, {\it i.e.}, determine that its probability of
+validate the planet, {\it i.e.}, determine that its probability of
 being an astrophysical false positive is negligibly small.  We
@@
 	\end{center}
-	\vspace{-0.6cm}
+	\vspace{-0.5cm}
 	\caption{ 
@@
 	\end{center}
-	\vspace{-0.5cm}
+	\vspace{-0.3cm}
 	\caption{ 
@@
 	\end{center}
-	\vspace{-0.7cm}
+	\vspace{-0.6cm}
 	\caption{
@@
     Systems younger than 100$\,$Myr are emphasized.  Ages and radii
-    are from the NASA Exoplanet Archive on 13 July 2020.  Precise ages
+    are from the NASA Exoplanet Archive on 29 July 2020.  Precise ages
     are known for only a small fraction of the gray points.
@@
 	}
-	\vspace{-0.5cm}
+	\vspace{-0.2cm}
 \end{figure}
@@
 with the scatter we observe in our radial velocities from FEROS.
-Detecting the radial velocity signature of a planet's Keplerian motion
-in this regime is challenging, and requires a significant amount of
-data and care in signal extraction \citep{barragan_radial_2019}.  The
-Rossiter-McLaughlin measurement avoids the majority of this issue
-because the transit occurs over a much shorter duration than a single
-stellar rotation period.
+Detecting a planet's Keplerian motion in this regime is challenging,
+and requires a significant amount of data and care in signal
+extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
+measurement avoids the majority of this issue because the transit
+occurs over a much shorter duration than a single stellar rotation
+period.
 
@@
 
-%\clearpage
+\clearpage
 \acknowledgements

### 2020-07-29 drivers/fit_tessindivtransit.py

@@ -28,7 +28,7 @@ def main(modelid):
 
     fitindiv = 1
     phaseplot = 1
-    cornerplot = 1
+    cornerplot = 0
     subsetcorner = 1
     grounddepth = 1
 

### 2020-07-29 timmy/plotting.py

@@ -2992,7 +2992,7 @@ def plot_fitindiv(m, summdf, outpath, overwrite=1, modelid=None):
              rotation=90)
     fig.text(0.5,-0.01, 'Hours from mid-transit', ha='center')
 
-    fig.tight_layout(h_pad=0.5, w_pad=0.1)
+    fig.tight_layout(h_pad=0.5, w_pad=0.2)
     savefig(fig, outpath, writepdf=1, dpi=400)
 
 

### 2020-07-31 paper/ms.tex
update manuscript

@@
 
-If the RM measurements prove that the validated planet is real, a
-campaign to measure the mass timed to coincide with TESS sectors 36
-and 37 (late March to late May of 2021) would significantly ease the
-extraction of the planetary mass.  The reason is that the RVs,
+If the RM measurements prove that the validated planet is real,
+measuring its mass may be worth the effort, because it would improve
+understanding of the planet's contraction and photoevaporation.  If an
+RV campaign were timed to coincide with TESS sectors 36 and 37 (3
+March 2021 through 28 April 2021), it would significantly ease
+extraction of the Keplerian signal.  The reason is that the RVs,
 activity indicators, and photometry could be modeled simultaneously
-\citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This would greatly
-constrain models of the spot-induced RV signal.  The mass measurement
-would be a worthy goal in order to improve understanding of the
-planet's contraction and photoevaporation history.
+\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
+Combining photometric and radial velocity data from non-overlapping
+epochs would also constrain the models, but perhaps not quite as
+convincingly.
 

### 2020-07-31 paper/ms.tex
update manuscript

@@
   they are often indicative of astrophysical false positive scenarios.
-  Our follow-up data show that such scenarios are highly unlikely.
+  Our follow-up data show that such scenarios are unlikely.
   Our combined multi-color photometry, high-resolution imaging, and
@@
   Background eclipsing binary scenarios, though limited by speckle
-  imaging, formally remain a 0.2\% possibility.  TOI 837b is
+  imaging, remain a 0.2\% possibility.  TOI 837b is
   therefore a validated adolescent exoplanet.  The planetary nature of
@@
 dispersal \citep{pollack_formation_1996}.  While rocky planets may
-fully form within only a few million years
+form within only a few million years
 \citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
@@
 validate the planet, {\it i.e.}, determine that its probability of
-being an astrophysical false positive is negligibly small.  We
+being an astrophysical false positive is small.  We
 considered this result worth reporting because of the planet's youth.
@@
     ascension are shown.  Two stars of interest are ``Star A'' and
-    ``Star B'', which were eventually excluded as being possible
+    ``Star B'', which were excluded as being possible
     sources of the transits.
@@
     {\bf Ground-based follow-up photometry.} The data were acquired
-    using the 0.36$\,$m at El Sauce and the 0.40$\,$m ASTEP400 at Dome
-    C.  Black points represent the measurements after binning at
-    10-minute intervals. The gray line is the model that best fits the
-    combined TESS and ground-based data.  Red and blue lines show
-    2-$\sigma$ lower limits on the transit depths in the Cousins-R and
-    Johnson-B bandpasses used to rule out specific false positive
-    scenarios (see Section~\ref{subsec:colorphot}).
+    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
+    ASTEP400 telescop at Dome C.  Black points represent the
+    measurements after binning at 10-minute intervals. The gray line
+    is the model that best fits the combined TESS and ground-based
+    data.  Red and blue lines show 2-$\sigma$ lower limits on the
+    transit depths in the Cousins-R and Johnson-B bandpasses used to
+    rule out specific false positive scenarios (see
+    Section~\ref{subsec:colorphot}).
 		\label{fig:groundphot}
@@
 \paragraph{Acquisition and reduction}
-We observed four transits with the 0.36$\,$m at Observatorio El Sauce,
-located in the R\'io Hurtado Valley in Chile, and operated by
-co-author P{.}~Evans.  The observations were obtained in Cousins-R
+We observed four transits with the 0.36$\,$m telescope at Observatorio
+El Sauce, located in the R\'io Hurtado Valley in Chile, and operated
+by co-author P{.}~Evans.  The observations were obtained in Cousins-R
 band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
@@
 Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
-Concordia base is operated jointly by the French and Italian polar
+Concordia base is operated by the French and Italian polar
 institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
@@
     300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
-    orbital ephemeris of \pn.  The planet is not detected.  The black
+    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
     line shows a circular Keplerian orbit representing the 3-$\sigma$
@@
 of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
-macroturbulent broadening of $v_\mathrm{Mac} = 8.4 \pm 2.9
+macroturbulent broadening of $v_\mathrm{mac} = 8.4 \pm 2.9
 \mathrm{km\,s}^{-1}$.
@@
 resolution of $\approx$48,000 across a spectral range of 350–920 nm.
-It has a remarkably high efficiency of $\approx$20\%. We obtained 13
+It has a high efficiency of $\approx$20\%. We obtained 13
 spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
@@
 
-\section{Elimination of False Positive Scenarios}
+\section{Assessment of False Positive Scenarios}
 \label{sec:validation}
@@
 (BEB), eclipses of a hierarchical system bound to the primary star
-(HEB), and the possibility that the eclipses are simply caused by a
+(HEB), and the possibility that the eclipses are caused by a
 stellar companion, rather than a planetary one (EB).
@@
 demonstrate that the probability \tn\ is an astrophysical false
-positive is small enough to formally validate it as a planet.
+positive is small enough to validate it as a planet.
 
@@
 
+L.G.B. and J.H. acknowledge support by the TESS GI Program, program
+G011103, through NASA grant 80NSSC19K0386.
+%
+This study was based in part on observations at Cerro Tololo
+Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
+2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
+Universities for Research in Astronomy (AURA) under a cooperative
+agreement with the National Science Foundation.
+%
+
 This paper includes data collected by the TESS mission, which are
@@
 Funding for the TESS mission is provided by NASA's Science Mission
-directorate.
-\tn\ was included on the TESS 2-minute target list in part
-thanks to the Guest Investigator program of G.\ Sacco (G011265).
+directorate.  \tn\ was included on the TESS 2-minute target list in
+part thanks to the Guest Investigator program of G.\ Sacco (G011265).
 %
@@
 (ERC) under the European Union's Horizon 2020 research and innovation
-programme (grant agreement n$^\circ$ 803193/BEBOP), and from the
+programme (grant n$^\circ$ 803193/BEBOP), and from the
 Science and Technology Facilities Council (STFC; grant n$^\circ$
@@
 
+This reserach was based in part on observations obtained at the
+Southern Astrophysical Research (SOAR) telescope, which is a joint
+project of the Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e
+Inova\c{c}\~{o}es (MCTI/LNA) do Brasil, the US National Science
+Foundation’s NOIRLab, the University of North Carolina at Chapel Hill
+(UNC), and Michigan State University (MSU).
+
 This research made use of the Exoplanet Follow-up Observation
@@
 Administration under the Exoplanet Exploration Program.
-%
-This research made use of the NASA Exoplanet Archive, which is
-operated by the California Institute of Technology, under contract
-with the National Aeronautics and Space Administration under the
-Exoplanet Exploration Program.
-%
+% %
+% This research made use of the NASA Exoplanet Archive, which is
+% operated by the California Institute of Technology, under contract
+% with the National Aeronautics and Space Administration under the
+% Exoplanet Exploration Program.
+% %
 

### 2020-07-31 drivers/plot_rvs.py

@@ -463,7 +463,7 @@ class MultipanelPlot(object):
         bint -= 1.0
 
         ax.axhline(0, color='k', linestyle=':', linewidth=1)
-        ax.plot(sorted(modph), rvmod2cat[np.argsort(modph)], 'k-', linewidth=self.fit_linewidth)
+        ax.plot(sorted(modph), rvmod2cat[np.argsort(modph)], 'k--', linewidth=self.fit_linewidth)
         #plot.labelfig(pltletter)
 
         telcat = np.concatenate((self.post.likelihood.telvec, self.post.likelihood.telvec))

### 2020-07-31 paper/ms.tex
update manuscript

@@
 %
-
 This paper includes data collected by the TESS mission, which are
@@
 
-This reserach was based in part on observations obtained at the
+This research was based in part on observations obtained at the
 Southern Astrophysical Research (SOAR) telescope, which is a joint
@@
 %
+D.D.\ acknowledges support through the TESS Guest Investigator Program
+Grant 80NSSC19K1727.
 

### 2020-08-01 paper/ms.tex
bugfix plot_scene
I'm pretty sure the invert_axis calls on WCSaxes have bugs. Possible
future astropy PR / issue...

@@
 	\caption{ {\bf Scene of \tn.}
-    Mean TESS image of \tn\ over Sector~10, with a logarithmic
+    Mean TESS image of \tn\ from Sector~10, with a logarithmic
     grayscale. The yellow star is the position of \tn.  White circles
-    are resolved Gaia sources with $T<16$ (brighter stars are larger).
+    are resolved Gaia sources with $T<16$. Brighter stars are larger.
     The black \texttt{X} and white \texttt{/} hatches show the

### 2020-08-01 drivers/plot_scene.py

@@ -21,6 +21,8 @@ def main():
 
     c_obj = SkyCoord(ra, dec, unit=(u.deg), frame='icrs')
 
+    # NOTE: S11 vs S10: not particularly different
+
     # hdul = fits.open(
     #     '/Users/luke/Dropbox/proj/timmy/data/MAST_2020-05-04T1852/TESS/tess2019112060037-s0011-0000000460205581-0143-s/'
     #     'tess2019112060037-s0011-0000000460205581-0143-s_tp.fits'

### 2020-08-01 timmy/plotting.py

@@ -926,10 +926,6 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
 
     plt.close('all')
 
-    # standard tick formatting fails for these images.
-    mpl.rcParams['xtick.direction'] = 'in'
-    mpl.rcParams['ytick.direction'] = 'in'
-
     #
     # wcs information parsing
     # follow Clara Brasseur's https://github.com/ceb8/tessworkshop_wcs_hack
@@ -1055,14 +1051,15 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
              markerfacecolor='yellow', markersize=18, marker='*',
              color='k', lw=0)
 
-    t = ax0.text(4.0, 5.2, 'A', fontsize=20, color='k', zorder=6)#, style='italic')
+    t = ax0.text(4.0, 5.2, 'A', fontsize=20, color='k', zorder=6)
     t.set_path_effects([path_effects.Stroke(linewidth=2.5, foreground='white'),
                         path_effects.Normal()])
-    t = ax0.text(4.6, 3.8, 'B', fontsize=20, color='k', zorder=6)#, style='italic')
+    t = ax0.text(4.6, 3.8, 'B', fontsize=20, color='k', zorder=6)
     t.set_path_effects([path_effects.Stroke(linewidth=2.5, foreground='white'),
                         path_effects.Normal()])
 
-    ax0.set_title('TESS', fontsize='xx-large')
+    if showdss:
+        ax0.set_title('TESS', fontsize='xx-large')
 
     if showcolorbar:
         cb0 = fig.colorbar(cset0, ax=ax0, extend='neither', fraction=0.046, pad=0.04)
@@ -1089,20 +1086,37 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
     # ITNERMEDIATE SINCE TESS IMAGES NOW PLOTTED
     #
     for ax in [ax0]:
-        ax.grid(ls='--', alpha=0.5)
+        lon = ax.coords[0]
+        lat = ax.coords[1]
+
+        lat.set_major_formatter('dd:mm:ss')
+        lon.set_major_formatter('hh:mm:ss')
+
+        lat.set_ticks(spacing=60*u.arcsec)
+        lon.set_ticks(spacing=120*u.arcsec)
+
+        lon.set_ticks_visible(False)
+        lat.set_ticks_visible(False)
+
[…]

### 2020-08-01 paper/ms.tex
minor

@@
   period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
-  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  The transits
-  are either grazing or nearly grazing.  From radial velocity
-  monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm
-  Jup}$ (3-$\sigma$).  Grazing transits are a cause for concern, as
-  they are often indicative of astrophysical false positive scenarios.
-  Our follow-up data show that such scenarios are unlikely.
-  Our combined multi-color photometry, high-resolution imaging, and
-  radial velocities rule out hierarchical eclipsing binary scenarios.
-  Background eclipsing binary scenarios, though limited by speckle
-  imaging, remain a 0.2\% possibility.  TOI 837b is
+  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
+  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
+  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
+  graze the stellar limb.  Grazing transits are a cause for concern,
+  as they are often indicative of astrophysical false positive
+  scenarios.  Our follow-up data show that such scenarios are
+  unlikely.  Our combined multi-color photometry, high-resolution
+  imaging, and radial velocities rule out hierarchical eclipsing
+  binary scenarios.  Background eclipsing binary scenarios, though
+  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
   therefore a validated adolescent exoplanet.  The planetary nature of
   the system can be confirmed or refuted through observations of the
-  stellar obliquity or the planetary mass.  Such observations may also
+  stellar obliquity and the planetary mass.  Such observations may also
   improve our understanding of how the physical and orbital properties

### 2020-08-01 timmy/plotting.py

@@ -1117,8 +1117,8 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
     else:
         axlist = [ax0]
     for ax in axlist:
-        ax.set_xlabel(r'$\alpha_{2000}$')
-        ax.set_ylabel(r'$\delta_{2000}$')
+        ax.set_xlabel(r'$\alpha_{2000}$', fontsize='large')
+        ax.set_ylabel(r'$\delta_{2000}$', fontsize='large')
 
     if showcolorbar:
         fig.tight_layout(h_pad=-8, w_pad=-8)
@@ -2832,12 +2832,12 @@ def plot_grounddepth(m, summdf, outpath, overwrite=1, modelid=None, showerror=1)
 
         shift += delta_y
 
-    ymin, ymax = ax.get_ylim()
-    ax.vlines(
-        0, ymin, ymax, colors='gray', alpha=0.5,
-        linestyles='--', zorder=-2, linewidths=0.5
-    )
-    ax.set_ylim((ymin, ymax))
+    # ymin, ymax = ax.get_ylim()
+    # ax.vlines(
+    #     0, ymin, ymax, colors='gray', alpha=0.5,
+    #     linestyles='--', zorder=-2, linewidths=0.5
+    # )
+    # ax.set_ylim((ymin, ymax))
 
     xval = np.arange(-3,4,1)
     ax.set_xticks(xval)

### 2020-08-01 paper/collect.sh
figure renaming

@@ -3,27 +3,27 @@
 rdir=/Users/luke/Dropbox/proj/timmy/results/
 pdir=../results/paper_plots/
 
-cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_fitindiv.pdf f1.pdf
+cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_fitindiv.pdf f1a.pdf
 
-cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_phaseplot.pdf f2a.pdf
+cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_phaseplot.pdf f1b.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200711/TOI_837_*_grounddepth.pdf f2b.pdf
+cp ${pdir}scene.pdf f2.pdf
 
-cp ${pdir}scene.pdf f5.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200711/TOI_837_*_grounddepth.pdf f3.pdf
 
-cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f6.pdf
+cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.pdf
 
-cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f3.pdf
+cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f5.pdf
 
-cp ${rdir}fpscenarios/fpscenarios.pdf f4.pdf
+cp ${rdir}fpscenarios/fpscenarios.pdf f6.pdf
 
 cp ${rdir}cluster_membership/hr_withiso_Bp_m_Rp.pdf f7.pdf
 
 cp ${rdir}cluster_membership/full_kinematics.pdf f8.pdf
 
-cp ${rdir}lithium/lithium.pdf f9a.pdf
+cp ${rdir}rotation/rotation.pdf f9a.pdf
 
-cp ${rdir}rotation/rotation.pdf f9b.pdf
+cp ${rdir}lithium/lithium.pdf f9b.pdf
 
 cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.pdf f10.pdf
 

### 2020-08-05 paper/ms.tex
figure renaming
update manuscript

@@
 \title{
-  Cluster Difference Imaging Photometric Survey (CDIPS) II.
+  Cluster Difference Imaging Photometric Survey. II.
   TOI~837: A Young Validated Planet in IC~2602
@@
 		\subfloat{
-			\includegraphics[width=0.79\textwidth]{f1.pdf}
+			\includegraphics[width=0.79\textwidth]{f1a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.77\textwidth]{f2a.pdf}
+			\includegraphics[width=0.77\textwidth]{f1b.pdf}
 		}
@@
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f5.pdf}
+		\includegraphics[width=0.48\textwidth]{f2.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=.44\textwidth]{f6.pdf}
+		\includegraphics[width=.44\textwidth]{f4.pdf}
 	\end{center}
@@
 		\leavevmode
-		\includegraphics[width=.47\textwidth]{f3.pdf}
+		\includegraphics[width=.47\textwidth]{f5.pdf}
 	\end{center}
@@
 Siding Spring Observatory near Coonabarabran, Australia
-\citep{gilbert_veloce_2018}.  Veloce's currently implemented Rosso
-camera provides coverage from 600--950$\,$nm at a spectral resolution
-of $\approx 80{,}000$.  Many of the exposures were taken in average or
-poor seeing conditions, when fiber-to-fiber cross-contamination on the
-IFU-style fiber feed is strongest.  To reduce the spectra to
-velocities, we cross-correlated against a high S/N template of
-$\delta$ Pavonis, because with spectral type G8 IV it was the closest
-\tn\ analog available in the Veloce spectral database.  The velocity
-RMS seen across each visit was hundreds of meters per second, likely
-due to uncorrected fiber-to-fiber cross-contamination.  For analysis
-purposes, we averaged across each visit, and set the velocity
-uncertainties to be the standard deviation of the per-visit exposures.
-The velocities are given in Table~\ref{tab:rvs}, and shown in
-Figure~\ref{fig:rvs}.
+\citep{gilbert_veloce_2018}.  The currently operational
+``Veloce-Rosso'' channel provides coverage from 600--950$\,$nm at a
+spectral resolution of $\approx 80{,}000$.  Many of the exposures were
+taken in average or poor seeing conditions, when the SNR is lowest and
+the fiber-to-fiber cross-contamination on the IFU-style fiber feed is
+strongest.  To reduce the spectra to velocities, we cross-correlated
+against a template of $\delta$ Pavonis, because with spectral type G8
+IV it was the closest high-SNR \tn\ analog available in the Veloce
+spectral database.  The velocity RMS seen across each visit was
+hundreds of meters per second, likely due to uncorrected
+fiber-to-fiber cross-contamination.  This cross-contamination severely
+affects the wavelength solutions for the 19 individual science fibres,
+ultimately leading to significantly increased RV scatter. For analysis
+purposes, we averaged the single-shot RVs across each visit, and set
+the velocity uncertainties to be the standard deviation of the
+per-visit exposures.  The velocities are given in Table~\ref{tab:rvs},
+and shown in Figure~\ref{fig:rvs}.
 
@@
 		\leavevmode
-		\includegraphics[width=0.75\textwidth]{f4.pdf}
+		\includegraphics[width=0.75\textwidth]{f6.pdf}
 	\end{center}
@@
 Grant 80NSSC19K1727.
-
 %

### 2020-08-05 paper/ms.tex
update manuscript

@@
 \citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
-$11\times11$ array surrounding the star were averaged and saved at
+$11\times11$ array surrounding the star were co-added and saved at
 2-minute cadence.  The $2048\times2048$ image from the entire CCD was
-also averaged into 30-minute stacks, and saved as a ``full frame
+also co-added into 30-minute stacks, and saved as a ``full frame
 image'' (FFI).
 
-The TESS project detected the transits in the 2-minute data and the
-community was alerted on 17 June 2019.  Our subsequent blind search of
-the CDIPS FFI light curves also showed the transits. Given that the
-2-minute data had better sampling cadence, we opted to use the
-Presearch Data Conditioning (PDC) light curve with the default
+The TESS Science Processing Operations Center
+\citep{jenkins_tess_2016} processed the image data and identified the
+transiting planet signature from two transits in
+Sector 10, again with three transits in Sector 11, and then for a
+final time when Sectors 1-13 were searched at the end of the first
+year of the mission. The transit signature was fitted with a
+limb-darkened transit model \citep{li_kepler_2019} and passed all the
+diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
+depth test, the weak secondary eclipse test, the ghost diagnostic
+test, and the difference image centroiding test, which placed the
+transit source within $\sim$2 arcsec of the location of TOI~837. No
+additional transit-like features were identified in any of the SPOC
+searches. The TESS Science Office alerted the community to this
+candidate transiting planet on 17 June 2019.  Our subsequent blind
+search of the CDIPS FFI light curves also showed the transits. Given
+that the 2-minute data had better sampling cadence, we opted to use
+the Presearch Data Conditioning (PDC) light curve with the default
 aperture for our
-analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.
+analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.
 
@@
 
-\clearpage
+%\clearpage
 \acknowledgements

### 2020-08-05 paper/authors.tex
update manuscript
Update manuscript
Co-authored-by: Andrew Mann <awmann@unc.edu>
Update manuscript
Co-authored-by: Rafael Brahm <rbrahm@gmail.com>
Update manuscript
RV limits on HEB scenarios
update manuscript
Co-authored-by: Alan Levine <aml@space.mit.edu>
update manuscript
Co-authored-by: Chris Tinney <c.tinney@unsw.edu.au>

@@
 
-%PENDING (MPIA)
+%OK
+\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
+\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
+\affiliation{Millennium Institute for Astrophysics, Chile}
+
+%OK
+\author[0000-0002-5674-2404]{P. Evans}
+\affiliation{El Sauce Observatory, Coquimbo Province, Chile}
+
+%OK
+\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%OK
+\author[0000-0002-4891-3517]{G. Zhou}
+\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+
+%OK
 \author{P. Sarkis} %Paula sarkis@mpia.de PI of FEROS time
@@
 
-%PENDING
-\author{P. Evans}
-\affiliation{El Sauce Observatory, Coquimbo Province, Chile}
-
-%PENDING
-\author[0000-0001-6588-9574]{K. A. Collins} % karenacollins@outlook.com
-\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
-
-%PENDING
-\author[0000-0002-4891-3517]{G. Zhou}
-\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
-
-%PENDING
+%OK
 \author[0000-0002-8964-8377]{S. N. Quinn} % squinn@cfa.harvard.edu
@@
 
-%PENDING
+%OK
 \author{J. de Leon}
@@
 
-%PENDING
+%OK
 \author[0000-0002-4881-3620]{J. Livingston}
@@
 
-%PENDING
+%OK
 \author[0000-0003-2989-7774]{C. Bergmann}
@@
 Sydney, NSW 2052, Australia}
+\affiliation{Deutsches Zentrum f\"ur Luft- und Raumfahrt, M\"unchener
+Str. 20, 82234 Wessling, Germany}
 
-%PENDING
+%OK
 \author[0000-0002-3481-9052]{K. G. Stassun}
@@
 %
-%PENDING
+%OK
 \author[0000-0002-0628-0088]{W. Bhatti}
@@
 % begin (ASTEP team)
-%PENDING
+%OK
 \author{L. Abe} % Lyu
@@
 
-%PENDING
+%OK
 \author[0000-0001-7866-8738]{N. Crouzet} % Nicolas
@@
 
-%PENDING
+%OK
 \author[0000-0002-3937-630X]{G. Dransfield} % Georgina
@@
 
-%PENDING
+%OK
 \author{W. Marie-Sainte} % Wenceslas
@@
 
-%PENDING
+%OK
 \author{D. M\'ekarnia} % Djamel
@@
 
-%PENDING
+%OK
 \author[0000-0002-5510-8751]{A. H.M.J. Triaud} % Amaury
@@
 
-%PENDING
+%OK
 \author[0000-0002-7595-0970]{C.~G.~Tinney}
 \affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW Sydney, NSW 2052, Australia}
-\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW 2052, Australia}
 
@@
 
-%PENDING
+%OK
 \author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
@@
 
-%PENDING
-\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
-\affiliation{Facultad de Ingenier\'{i}a y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
-\affiliation{Millennium Institute for Astrophysics, Chile}
-
-%PENDING
+%OK
 \author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
@@
 
-%PENDING
+%OK
 \author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
@@
 
-%PENDING
+%OK
 \author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
@@
 
-%PENDING
+%OK
 \author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
@@
 
-%PENDING
-\author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
+%OK
+\author[0000-0002-1896-2377]{J.~I.~Vines} %Jose jose.vines.l@gmail.com FEROS observations
 \affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}
 
-%PENDING
+%OK
 \author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
@@
 %
-%PENDING
+%OK
 \author[0000-0002-0619-7639]{C.~Ziegler} % carl.ziegler@dunlap.utoronto.ca
@@
 
-%PENDING
-\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
-\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La Serena, Chile}
+%%OMITTED
+%\author{C.~Brice\~{n}o} % cbriceno@ctio.noao.edu
+%\affiliation{Cerro Tololo Inter-American Observatory, Casilla 603, La Serena, Chile}
 
-%PENDING
+%OK
 \author{N.~Law} % nlaw@unc.edu
@@
 
-%PENDING
-\author{A.~W.~Mann} % awmann@unc.edu
+%OK
+\author[0000-0003-3654-1602]{A.~W.~Mann} % awmann@unc.edu
 \affiliation{Department of Physics and Astronomy, The University of North Carolina at Chapel Hill, Chapel Hill, NC 27599-3255, USA}
@@
 %
-%PENDING
+%OK
 \author{G. R. Ricker} % grr@space.mit.edu
@@
 %
-%PENDING
+%OK
 \author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
@@
 %
-%PENDING
-\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
-\affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
+% %OMITTED
+% \author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
+% \affiliation{Center for Astrophysics \textbar \ Harvard \& Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
 %
-%PENDING
+%OK
 \author{S. Seager} % seager@mit.edu
@@
 %
-%PENDING
+%OK
 \author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
@@
 
-%PENDING
-\author[0000-0002-7754-9486]{C~J.~Burke} % cjburke@mit.edu
+%OK
+\author[0000-0002-7754-9486]{C.~J.~Burke} % cjburke@mit.edu
 \affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 
-%PENDING
+%OK
 \author[0000-0003-2313-467X]{D.~Dragomir}
@@
 
-%PENDING
-\author{A.~M.~Levine} % aml@space.mit.edu
+%OK
+\author[0000-0001-8172-0453]{A.~M.~Levine} % aml@space.mit.edu
 \affiliation{Department of Physics and Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
 
-%PENDING
-\author{E. Quintana} % elisa.quintana@nasa.gov
+%OK
+\author{E.~V.~Quintana} % elisa.quintana@nasa.gov
 \affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
 
-%PENDING
+%OK
 \author[0000-0001-8812-0565]{J.~E.~Rodriguez}
@@
 
-%PENDING
+%OK
 \author[0000-0002-6148-7903]{J. C. Smith} % jeffrey.c.smith-1@nasa.gov
@@
 
-%PENDING
+%OK
 \author[0000-0002-5402-9613]{B. Wohler} % bill.wohler@nasa.gov

### 2020-08-05 paper/ms.tex
update manuscript
cleaning repo

@@
 either associated or in chance alignment with TOI 837. No such set of
-lines were found. To set limits on the contributions of a close-by
+lines was found. To set limits on the contributions of a close-by
 star to the observed spectrum, we injected a second set of lines to
@@
 Our model for time-series photometry data was an
-\citet{exoplanet:agol19} transit with physical and orbital parameters
+\citet{exoplanet:agol20} transit with physical and orbital parameters
 shared across all transit windows, plus a local quadratic trend
@@
   %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
-  \texttt{exoplanet} \citep{exoplanet:agol19}
   \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
-  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
+  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
   	exoplanet:theano},

### 2020-08-05 paper/clean.sh

@@ -1,0 +1,1 @@
+rm ms.log ms.out ms.aux ms.blg ms.bbl ms.synctex.gz

### 2020-08-06 paper/ms.tex
cleaning bib

@@
 TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
-\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
+\citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
 Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and

### 2020-08-06 paper/ms.tex
clean repo
update manuscript

@@
 		\leavevmode
-		\includegraphics[width=.49\textwidth]{f2b.pdf}
+		\includegraphics[width=.48\textwidth]{f3.pdf}
 	\end{center}
@@
 significantly change between different bandpasses.
+Our assumption in the false-positive probability calculation
+(Section~\ref{subsec:fpp}) of no odd-even variations was tested by
+independently fitting all odd and all even transits separately.
+The resulting best-fit depths were consistent within 1-$\sigma$.
+% odd: (Rp/R*)^2 = 0.005500 +0.000558 -0.000169
+% even: (Rp/R*)^2 = 0.005659 +0.000636 -0.000185
 
@@
 The relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  The transit is therefore either
+Figure~\ref{fig:subsetcorner}.  The transit is either
 grazing, or nearly grazing.  From experimenting with the priors, we
@@
 shape across all bandpasses, with no observed secondary eclipse or
-odd-even variations (Section~\ref{subsec:fpp}).  This statement is
+odd-even variations.  This statement is
 tautologically ``validation'', but it is weaker than having data on

### 2020-08-06 paper/abstract_aas.tex
add abstract for AAS

--- 2020-08-06 paper/ms.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[12pt,twocolumn,tighten]{aastex63}
-%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
-\usepackage{amsmath,amstext,amssymb}
-\usepackage[T1]{fontenc}
-\usepackage{apjfonts}
-\usepackage[figure,figure*]{hypcap}
-\usepackage{graphics,graphicx}
-\usepackage{hyperref}
-\usepackage{natbib}
-\usepackage[caption=false]{subfig} % for subfloat
-\usepackage{enumitem} % for specific spacing of enumerate
-\usepackage{epigraph}
-
-\renewcommand*{\sectionautorefname}{Section} %for \autoref
-\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-
-\newcommand{\tn}{TOI~837} % target star name
-\newcommand{\pn}{TOI~837b} % planet name
-\newcommand{\cn}{IC~2602} % cluster name
-
-\newcommand{\kms}{\,km\,s$^{-1}$}
-
-\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
-\newcommand{\datasetlink}{\textsc{\dataset[doi.org/10.17909/t9-ayd0-k727]{https://doi.org/10.17909/t9-ayd0-k727}}}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
-%% Add "Submitted to " argument.
-\received{\today}
-\revised{---}
-\accepted{---}
-\submitjournal{AAS journals.}
-\shorttitle{TOI~837 in IC~2602}
-
-\begin{document}
-
-\defcitealias{bouma_wasp4b_2019}{B19}
-
-\title{
-  Cluster Difference Imaging Photometric Survey. II.
-  TOI~837: A Young Validated Planet in IC~2602
-}
-
-%\suppressAffiliations
-%\NewPageAfterKeywords
-\input{authors.tex}
-
-\begin{abstract}
-  We report the discovery of TOI 837b and its validation as a
-  transiting planet.  We characterize the system using data from the
-  NASA TESS mission, the ESA Gaia mission, ground-based photometry
-  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
-  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
-  southern open cluster IC 2602.  The star and planet are therefore
-  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
-  with a prior on the stellar parameters derived from the cluster
-  color-magnitude diagram, we find that the planet has an orbital
-  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
-  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
-  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
-  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
-  graze the stellar limb.  Grazing transits are a cause for concern,
-  as they are often indicative of astrophysical false positive
-  scenarios.  Our follow-up data show that such scenarios are
-  unlikely.  Our combined multi-color photometry, high-resolution
-  imaging, and radial velocities rule out hierarchical eclipsing
-  binary scenarios.  Background eclipsing binary scenarios, though
-  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
-  therefore a validated adolescent exoplanet.  The planetary nature of
-  the system can be confirmed or refuted through observations of the
-  stellar obliquity and the planetary mass.  Such observations may also
-  improve our understanding of how the physical and orbital properties
-  of exoplanets change in time.
-\end{abstract}
-
-\keywords{
-	Exoplanets (498),
-  Transits (1711),
-	Exoplanet evolution (491),
-	Stellar ages (1581),
-	Young star clusters (1833)
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Over the first 100 million years of their lives, exoplanet systems are
-expected to undergo major physical and dynamical changes.  For a
-typical Sun-like star, the protoplanetary disk disperses within
-roughly 1--10 million years
-\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
-Gas giants presumably finish accreting before the end of disk
-dispersal \citep{pollack_formation_1996}.  While rocky planets may
-form within only a few million years
-\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
-over the next 10--100 million years through giant impacts \citep[{\it
-e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
-The Moon, for instance, may have formed from debris ejected during a
-collision between the proto-Earth and a planetesimal during Earth's
-first 100 million years
-\citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.
-
-A number of other processes are expected to shape young exoplanets.
-After accreting, planets with gaseous envelopes are thought to cool
-and contract, and their atmospheres are expected to undergo a mix of
-photoevaporation and core-powered mass loss \citep[{\it
-e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
-Predicted timescales for photoevaporation and core-powered mass loss
-range from 10 million years to over 1 gigayear for typical transiting
-sub-Neptunes
-\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
-The relative importance of each process is set by the planetary
-surface gravity and the radiation environment.  Both processes can be
-directly observed through observations of planetary winds in the
-metastable 1083$\,$nm He line
-\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.
-
-Beyond physical changes, dynamical changes are expected in the
-semi-major axes, eccentricities, and stellar obliquities of young
-planets.  When the gas disk is present, the planetary semi-major axis
-is thought to change in step with the viscous evolution of the disk
-\citep{lin_orbital_1996}.  High-eccentricity migration processes
-including planet-planet scattering, secular chaos, and Kozai-Lidov
-oscillations can also occur \citep[{\it
-e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
-The circularization timescale is thought to be such that for any giant
-planets that migrated early, their orbits should circularize within
-100 million years \citep{zahn_tidal_1977}.
-
-Finding and understanding systems undergoing these evolutionary changes is
-a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1$\,$Gyr, a number of direct and indirect methods are
-available \citep{soderblom_ages_2010}.  The traditional approach is to
-isochronally age-date coeval groups of stars, hereafter ``clusters''
-\citep[{\it
-e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
-Young field stars can also be identified isochronally, provided that
-they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
-age indicators include stellar rotation periods, the abundance of
-photospheric lithium, and chromospheric diagnostics such as calcium
-emission and broadband UV emission.  Studies by, for instance,
-\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
-have combined these methods to age-date individual field stars hosting
-transiting planets.  Many of these latter methods were summarized by
-\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
-e.g.},
-\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
-and \citet{curtis_tess_2019} for stellar rotation,
-\citet{zerjal_chromospherically_2017} for chromospheric activity, and
-{\it e.g.}, \citet{berger_identifying_2018} and
-\citet{zerjal_galah_2019} for lithium abundances.
-
-A few dozen planets in clusters have been detected, and fewer still
-have been closely characterized.  Despite the challenges of
-starspot-induced radial velocity (RV) variations, RV surveys found
-success in the Hyades, NGC~2523, Praesepe, and M~67
-\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
-RV surveys of highly active pre-main sequence stars in Taurus also led
-to the youngest hot Jupiters yet reported orbiting
-V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
-not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
-\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
-
-The transit method was comparatively slow to catch up.  Early deep
-transit searches of open clusters by many groups did not yield
-definitive planet detections
-\citep{mochejska_planets_2005,mochejska_planets_2006,burke_survey_2006,aigrain_monitor_2007,irwin_monitordata_2007,miller_monitor_2008,pepper_photometric_2008,hartman_MMT_IV_2009}.
-These searches were typically sensitive to planets larger than
-Jupiter, on $\lesssim 3$ day orbital periods.  Hot Jupiter occurrence
-rate limits were derived at the $\lesssim 5\%$ level \citep[{\it
-e.g.},][]{burke_survey_2006,hartman_MMT_IV_2009}.  The modern 0.5-1\%
-occurrence rate suggests that these early transit surveys would have
-needed a greater data volume at higher precision for detection to be
-possible
-\citep{mayor_harps_2011,wright_frequency_2012,howard_planet_2012,petigura_metallicity_2018}.
-
-Kepler observed a large enough number of stars with sufficient
-baseline and precision to detect transiting planets in open clusters:
-Kepler-66b and 67b, in the gigayear-old NGC~6811
-\citep{borucki_kepler_2010,Meibom_et_al_2013}.  Though a broken
-reaction wheel ended the prime Kepler mission, the repurposed K2
-\citep{howell_k2_2014} switched between fields along the ecliptic
-every quarter-year, and was able to observe far more clusters and
-young stars.
-
-The discoveries made by K2 through its surveys of Taurus, the Hyades,
-Praesepe, and Upper Sco were a major inspiration for the present work
-\citep[{\it
-e.g.},][]{Mann_K2_25_2016,obermeier_k2_2016,Mann_et_al_2017,vanderburg_zeitVII_2018,ciardi_k2-136_2018,livingston_three_2018,mann_ZEITVI_2018,rizzuto_zeitVIII_2018,livingston_k2-264_2019}.
-Observations with K2 convincingly showed that at least some close-in
-planets must form within about 10 Myr
-\citep{Mann_K2_33b_2016,David_et_al_2017}.  They also led to the first
-hints that young planets in clusters may in fact be qualitatively
-different from their field counterparts.  For instance, based on its
-observed mass, radius, and UV environment, the 700$\,$Myr K2-100b is
-probably actively losing its atmosphere, and should become a bare
-rocky planet over the next few hundred Myr
-\citep{Mann_et_al_2017,barragan_radial_2019}.  The four transiting
-planets around V1298~Tau (23$\,$Myr) are also likely to be
-photoevaporating, and could represent a precursor to Kepler's compact
-multiple systems \citep{david_four_2019,david_warm_2019}.
-
-To advance the young planet census, we have been using data from the
-TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
-Difference Imaging Photometric Survey
-\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
-candidate young stars that have been reported in the literature.  At
-the time of writing, we had made $\sim$$6\times10^5$ light curves from
-the first year of TESS observations. The light curves are available at
-MAST\footnote{\stscilink}, and through \datasetlink.  Searching
-through a subset of these light curves brought our attention to the
-candidate transiting planet, \pn, that is the subject of this
-analysis.
-
-The transits of \pn\ are grazing the stellar limb, which is a cause
-for concern.  Particularly for a star near the galactic plane
-($b=-5.8^\circ$), background eclipsing binaries are a major source of
-astrophysical false positives \citep[{\it
-e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
-and related scenarios are unlikely to the degree that we can
-validate the planet, {\it i.e.}, determine that its probability of
-being an astrophysical false positive is small.  We
-considered this result worth reporting because of the planet's youth.
-
-Section~\ref{sec:observations} describes the identification of the
-candidate, and our follow-up observations.
-Section~\ref{sec:validation} combines the available data to assess the
-system's false positive probability, and validates \pn\ as a planet.
-Section~\ref{sec:system} presents our knowledge of the cluster
-(Section~\ref{subsec:cluster}), the star (Section~\ref{subsec:star})
-and the planet (Section~\ref{subsec:planet}).  We conclude by
-discussing avenues for confirmation and improved characterization in
-Section~\ref{sec:discussion}.
-
-\section{Identification and Follow-up Observations}
-\label{sec:observations}
-
-\subsection{TESS Photometry}
-\label{subsec:tess}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\subfloat{
-			\includegraphics[width=0.79\textwidth]{f1a.pdf}
-		}
-
-		\vspace{-0.5cm}
-		\subfloat{
-			\includegraphics[width=0.77\textwidth]{f1b.pdf}
-		}
-	\end{center}
-	\vspace{-0.6cm}
-	\caption{
-    {\bf TESS light curve of \tn.}
-    {\it Top}:
-    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
-    sampling in units of parts-per-thousand ($\times 10^{-3}$).
-    Starspot-induced variability is the dominant signal; flares are
-    shown with red crosses.  Dashed lines indicate the five transits
-    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
-    transits.  Gray lines are the best-fit transit model, which
-    includes a local quadratic trend in each window. Gray points are
-    2-minute \texttt{PDCSAP} flux measurements, black points are
-    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
-    transit.  Gray points are 2-minute measurements with the local
-    spot-induced variation removed.  Binning at 6-minute intervals
-    yields the black points.  The black error-bar shows the median
-    uncertainty for the black points.  The gray line shows the
-    best-fit model to the TESS data. 
-		\label{fig:tessphot}
-	}
-\end{figure*}
-
-\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
-the tenth and eleventh sectors of science operations
-\citep{ricker_transiting_2015}.  The star was designated
-TIC\,460205581 in the TESS Input Catalog
-\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
-$11\times11$ array surrounding the star were co-added and saved at
-2-minute cadence.  The $2048\times2048$ image from the entire CCD was
-also co-added into 30-minute stacks, and saved as a ``full frame
-image'' (FFI).
-
-The TESS Science Processing Operations Center
-\citep{jenkins_tess_2016} processed the image data and identified the
-transiting planet signature from two transits in
-Sector 10, again with three transits in Sector 11, and then for a
-final time when Sectors 1-13 were searched at the end of the first
-year of the mission. The transit signature was fitted with a
-limb-darkened transit model \citep{li_kepler_2019} and passed all the
-diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
-depth test, the weak secondary eclipse test, the ghost diagnostic
-test, and the difference image centroiding test, which placed the
-transit source within $\sim$2 arcsec of the location of TOI~837. No
-additional transit-like features were identified in any of the SPOC
-searches. The TESS Science Office alerted the community to this
-candidate transiting planet on 17 June 2019.  Our subsequent blind
-search of the CDIPS FFI light curves also showed the transits. Given
-that the 2-minute data had better sampling cadence, we opted to use
-the Presearch Data Conditioning (PDC) light curve with the default
-aperture for our
-analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.
-
-Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
-induced by starspots coming into and out of view has a peak-to-peak
-amplitude of about 2.3\%, and a period of about 3 days.  The dips are
-suggestive of a grazing transiting planet, recurring roughly every 8
-days with a depth of about 0.4\%.  A few flares are also visible.  A
-phase-folded view of the TESS transits with starspot variability
-removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
-for the models shown in these plots is described in
-Section~\ref{subsec:planet}.
-
-\subsection{Gaia Astrometry and Imaging}
-\label{subsec:gaia}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f2.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ {\bf Scene of \tn.}
-    Mean TESS image of \tn\ from Sector~10, with a logarithmic
-    grayscale. The yellow star is the position of \tn.  White circles
-    are resolved Gaia sources with $T<16$. Brighter stars are larger.
-    The black \texttt{X} and white \texttt{/} hatches show the
-    apertures used to measure the background and target star flux,
-    respectively. Dashed lines of constant declination and right
-    ascension are shown.  Two stars of interest are ``Star A'' and
-    ``Star B'', which were excluded as being possible
-    sources of the transits.
-		\label{fig:scene}
-	}
-\end{figure}
-
-Between 25 July 2014 and 23 May 2016, the ESA Gaia satellite measured
-about 300 billion centroid positions of 1{.}6 billion stars.  The
-positions, proper motions, and parallaxes of the brightest 1{.}3
-billion were calculated for the second data release (DR2)
-\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
-\tn\ was assigned the Gaia DR2 identifier 5251470948229949568, and had
-276 ``good'' astrometric observations. Its brightness was measured in
-the $G$, $Rp$, and $Bp$ bands of the Radial Velocity Spectrometer
-\citep{cropper_gaia_2018,evans_gaia_2018}.
-
-The Gaia imaging, reduced to its point-source catalog, provides the
-initial context for analyzing the TESS data.  Stars brighter than
-$T=16$, as queried from the Gaia DR2 source catalog, are shown with
-white circles in Figure~\ref{fig:scene}, overlaid on the TESS image.
-Given its galactic latitude of $b=-6^\circ$, it is not surprising that
-the field of \tn\ is crowded.  The resolved stars that were of
-immediate concern for our false positive analysis were as follows.
-\begin{itemize}
-  %
-  \item \tn\ $\equiv$ TIC 460205581 ($T=9.9$). The target star.
-  %
-  \item Star A $\equiv$ TIC 847769574 ($T=14.6$), $2.3''$ West. The
-    proper motions and parallax of this star imply it is co-moving
-    with \tn\ and that the two stars are separated by $6.6\pm
-    0.1\,{\rm pc}$.  Star A is therefore likely an \cn\ member, but
-    unlikely to be a bound binary companion.
-  %
-  \item Star B $\equiv$ TIC 460205587 ($T=13.1$), $5.4''$ North.  The
-    Gaia parallax implies this is a background giant star.
-\end{itemize}
-An additional source, TIC 847769581, is $4.9''$ from the target, but
-too faint ($T=18.8$) to be the source of the observed transit signal.
-
-The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
-$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
-Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
-GAIA-C3-TN-LU-LL-124-01,
-\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
-\texttt{2020-07-08}. } value is available.  We suspect that the
-photometric failure to produce an $Rp$ magnitude as well as its poor
-astrometric fit are due to blending with \tn.
-
-At the $\approx1'$ resolution of the TESS data, if either Star A or
-Star B were eclipsing binaries, they could be the sources of the
-transit signal.  A detailed analysis of ground-based seeing-limited
-photometry was necessary to assess and rule out this possibility
-(Section~\ref{subsec:groundphot} and Figure~\ref{fig:groundphot}).
-
-\subsection{High-Resolution Imaging}
-\label{subsec:speckle}
-
-To determine if any fainter point sources existed closer to \tn\
-inside of Gaia's point-source detection limits, we acquired
-high-resolution speckle images. We then searched the autocorrelation
-functions of these images for peaks indicative of nearby companions.
-
-The observations of \tn\ were initially acquired by
-\citet{ziegler_soar_2020} as part of the Southern Astrophysical
-Research (SOAR) TESS Survey using the High Resolution Camera (HRCam;
-\citealt{tokovinin_ten_2018}).  The HRCam $I$-band filter is described
-by \citet{tokovinin_ten_2018}.  The points in Figure~\ref{fig:speckle}
-show the resulting measured 5-$\sigma$ detectable contrasts.  The
-lines are linear smoothing fits between the regimes of the diffraction
-limit, the ``knee'' at $\approx 0.2''$, and the slow decrease until
-$\approx 1.5''$, beyond which the speckle patterns become
-de-correlated.  Star A (TIC 847769574) was detected at the expected
-location and brightness contrast, and no additional companions were
-found.  Star B was not detected; with a separation of $5.4''$ from
-\tn, it fell outside the field of view.
-
-\subsection{Ground-based Time-Series Photometric Follow-up}
-\label{subsec:groundphot}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.49\textwidth]{f2b.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Ground-based follow-up photometry.} The data were acquired
-    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
-    ASTEP400 telescop at Dome C.  Black points represent the
-    measurements after binning at 10-minute intervals. The gray line
-    is the model that best fits the combined TESS and ground-based
-    data.  Red and blue lines show 2-$\sigma$ lower limits on the
-    transit depths in the Cousins-R and Johnson-B bandpasses used to
-    rule out specific false positive scenarios (see
-    Section~\ref{subsec:colorphot}).
-		\label{fig:groundphot}
-	}
-\end{figure}
-
-We obtained ground-based seeing-limited time series photometric
-observations of \tn\ bracketed around the times of transit.  These
-observations confirmed that the transits occurred on-target to within
-$\approx 2''$, and that they were achromatic. Both features are
-essential for our ability to eliminate false-positive scenarios.
-
-\subsubsection{El Sauce 0.36$\,$m}
-
-\paragraph{Acquisition and reduction}
-We observed four transits with the 0.36$\,$m telescope at Observatorio
-El Sauce, located in the R\'io Hurtado Valley in Chile, and operated
-by co-author P{.}~Evans.  The observations were obtained in Cousins-R
-band on the nights of 1 April 2020 and 26 April 2020, Cousins-I band
-on the night of 21 May 2020, and Johnson-B band on the night of 14
-June 2020.  The final 14 June transit began shortly after twilight.
-
-We scheduled our transit observations using the {\tt TESS Transit
-Finder}, which is a customized version of the {\tt Tapir} software
-package \citep{Jensen:2013}.  The photometric data were calibrated and
-extracted using \texttt{AstroImageJ} \citep{collins_astroimagej_2017}.
-Comparison stars of similar brightness were used to produce the final
-light curves, each of which showed a roughly 4$\,$ppt dip near the
-expected transit time.  The data are reported in Table~\ref{tab:phot}
-and plotted in Figure~\ref{fig:groundphot}.
-
-\paragraph{Custom aperture analysis}
-Based solely on the TESS data, both Star A and Star B were possible
-sources of blended eclipsing binary signals.  The typical FWHM for
-stars in the El Sauce observations was $\approx 2.3''$, with a
-variance of $\approx 0.2''$.  Star B is resolved in the 0.36$\,$m
-images; Star A is not.
-
-To rule out blend scenarios with the ground-based photometry, we
-produced light curves centered on \tn\ with circular apertures of
-radii ranging from 0.7$''$ to 5.1$''$.  We did not detect any
-statistically significant variation in the depth of the transits with
-aperture size.  Two lines of evidence rule out Star B as the eclipsing
-source: first, the transits were detected in the smallest apertures.
-Second, we made light curves with $2.1''$ apertures centered on Star
-B, and they did not show the transit.
-
-To assess the possibility that Star A is an eclipsing body, we created
-light curves with a custom set of circular apertures with radii of
-$2.1''$ and positions ranging from Star A (2.3$''$ West of \tn) to
-2.3$''$ East of \tn.  We did not detect any variation of the transit
-depth along this line of light curves. The apertures East of \tn\
-exclude over 90\% of the flux from Star A.  The eclipse on Star A
-would therefore need to have depth greater than unity to produce the
-observed eclipse depth.  We therefore interpret the lack of asymmetry
-between the Western-most (centered on Star A) and Eastern-most
-(furthest from Star A) light curves as conclusive evidence that \tn\
-is the source of the transit signal to within $\approx2.0''$.  To
-verify self-consistency, we checked that the maximum dilution from
-Star A ($\approx 1\%$) is less than the uncertainty of the transit
-depth measurements ($\approx 15\%$), and so the lack of variation of
-transit depth with aperture location is consistent with \tn\ being the
-source of transits.
-
-\subsubsection{ASTEP400}
-
-We observed three transits with the 0.40$\,$m ASTEP telescope at the
-Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
-Concordia base is operated by the French and Italian polar
-institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
-allows it to take advantage of the continuous night during Austral
-winter.  The weather is of photometric quality for about two-thirds of
-each winter \citep{crouzet_four_2018}.
-
-ASTEP is equipped with a FLI Proline science camera with a KAF-16801E,
-$4096\times4096$ front-illuminated CCD. The camera has an image scale
-of 0.93\,arcsec pixel$^{-1}$ resulting in a $1^{\circ}\times1^{\circ}$
-corrected field of view. The focal instrument dichroic plate splits
-the beam into a blue wavelength channel for guiding, and a
-non-filtered red science channel roughly matching a Cousins-R
-transmission curve
-\citep{abe_secondary_2013,mekarnia_transiting_2016}.  The images were
-processed on-site using an automated aperture  photometry pipeline
-based on the \texttt{daophot} package of the IDL astronomy user's
-library \citep{landsman_1995}.
-
-\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
-2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
-of $25\,$s, readout and processing overhead of $25\,$s).  Except for
-12 May, our observations were conducted under stable weather
-conditions, with clear skies, temperatures of about $-70^\circ$C, and
-wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
-exclude from the analysis all data collected on May 12. We found that
-the optimal calibrated light curves of \tn\ correspond to an 11 pixel
-(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
-observations carried out on June and May, respectively.  The data are
-reported in Table~\ref{tab:phot}, and plotted in
-Figure~\ref{fig:groundphot}.
-
-\input{TOI837_phot_table.tex}
-
-\subsection{Spectroscopic Follow-up}
-\label{subsec:spectra}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.44\textwidth]{f4.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
-    imaging were derived from point-source injection-recovery
-    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
-    and is also a resolved Gaia source.  It is co-moving with \tn, and
-    its parallax and on-sky position imply that it is physically
-    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
-    \label{fig:speckle}
-	}
-\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.47\textwidth]{f5.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
-    measurements, with best-fit instrument offsets and jitter terms
-    included.  The expected scatter from starspots based on $v\sin i$
-    and the photometric modulation amplitude is of order
-    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
-    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
-    line shows a circular Keplerian orbit representing the 3-$\sigma$
-    upper mass limit.
-    \label{fig:rvs}
-	}
-\end{figure}
-
-Reconnaissance spectroscopic follow-up is an essential step in vetting
-planet candidates.  Medium to high-resolution spectra enable physical
-characterization of the star and therefore planet.  Reducing multiple
-spectra to a radial velocity time-series can enable planet mass
-measurements, and also set limits on the mass of any nearby
-companions.  Finally, if there are close or bright companions,
-reconnaissance spectra can also reveal the presence of a secondary set
-of stellar lines.
-
-\subsubsection{SMARTS 1.5$\,$m / CHIRON}
-\label{subsec:chiron}
-
-We acquired nine spectra using CHIRON at the SMARTS 1.5$\,$m telescope
-at Cerro Tollo Inter-American Observatory, Chile
-\citep{tokovinin_chironfiber_2013}.  Six met our signal-to-noise
-requirements for radial velocity measurements and stellar parameter
-extraction.  We used CHIRON in its image slicer configuration,
-yielding a spectral resolution of $\approx 79{,}000$ across
-415--880$\,$nm.
-
-We derived radial velocities and spectroscopic line profiles from the
-CHIRON observations using a least-squares deconvolution of the spectra
-against non-rotating synthetic spectral templates
-\citep{donati_1997_spectropolarimetric}. The spectral templates were
-generated using ATLAS9 atmosphere models \citep{Castelli:2004} with
-the \texttt{SPECTRUM} script \citep{gray_1994_spectrum}. These line
-profiles were fitted with a broadening kernel that describes the
-rotational, radial-tangential macroturbulent, and instrumental
-broadening of the spectrum. The rotational and macroturbulent
-broadening are computed per \citet{gray_2005_book}, following the
-methods described in \citet{zhou_2018_hd106315obliq}. We fitted the
-line profile from each observation independently, yielding the radial
-velocities listed in Table~\ref{tab:rvs} and shown in
-Figure~\ref{fig:rvs}. We found a mean rotational broadening velocity
-of $v\sin I_\star = 16.2 \pm 1.1 \mathrm{km\,s}^{-1}$, and a
-macroturbulent broadening of $v_\mathrm{mac} = 8.4 \pm 2.9
-\mathrm{km\,s}^{-1}$.
-
-To derive the stellar parameters, we matched the set of CHIRON spectra
-against a library of observed spectra, previously obtained using the
-Tillinghast Reflect Echelle Spectrograph
-\citep[TRES,][]{furesz_tres_2008} on the 1.5\,m reflector at the Fred
-Lawrence Whipple Observatory (FLWO), Arizona, USA, and classified
-using the Stellar Parameter Classification pipeline
-\citep{buchhave_hatp16b_class_2010}.  We found the best matching
-stellar parameters to be $T_\mathrm{eff} = 5899 \pm 55$K, $\log g =
-4.496 \pm 0.011$ dex, and $\mathrm{[Fe/H]} = -0.069 \pm 0.042$ dex.
-We ultimately adopted a different set of stellar parameters for our
-analysis (see Section~\ref{subsec:starparams}).
-
-The spectroscopic line profiles were thoroughly examined for any signs
-of secondary lines that might indicate the presence of another star,
-either associated or in chance alignment with TOI 837. No such set of
-lines was found. To set limits on the contributions of a close-by
-star to the observed spectrum, we injected a second set of lines to
-the mean least-squares deconvolution profile derived from the CHIRON
-observations. The injection spanned 10,000 different combinations of
-line broadening, velocity separation, and flux ratio $F_2/F_1$. The
-recovery results showed that for rotational broadenings of the
-secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
-exclude sources with flux fractions $F_2/F_1$ brighter than roughly
-$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
-from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
-smaller velocity separations, the injected lines begin to blend with
-the target spectrum.
-
-\subsubsection{FEROS}
-TOI 837b was monitored with the FEROS echelle spectrograph
-\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
-telescope at the ESO La Silla Observatory, in Chile. FEROS has a
-resolution of $\approx$48,000 across a spectral range of 350–920 nm.
-It has a high efficiency of $\approx$20\%. We obtained 13
-spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
-context of the Warm gIaNts with tEss (WINE) collaboration, which
-focuses on the systematic characterization of TESS transiting giant
-planets with moderately long orbital periods \citep[{\it
-e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
-and 600 seconds and the observations were performed with the
-simultaneous calibration mode for tracing the instrumental velocity
-variations with a comparison fiber illuminated with a ThAr lamp. FEROS
-data was processed with the \texttt{ceres} pipeline
-\citep{brahm_2017_ceres}, which delivers precision radial velocities
-and bisector span measurements through cross-correlation of the
-extracted spectra with a binary mask resembling the properties of a
-G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
-shown in Figure~\ref{fig:rvs}.  To check for the presence of secondary
-lines, we performed a similar injection-recovery exercise as with the
-CHIRON data.  We achieved slightly worse limits, likely due to the
-lower spectral resolution of FEROS, and therefore adopted the CHIRON
-limits.
-
-\subsubsection{Veloce}
-We acquired 34 spectra over 10 visits of \tn\ using the Veloce
-spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
-Siding Spring Observatory near Coonabarabran, Australia
-\citep{gilbert_veloce_2018}.  The currently operational
-``Veloce-Rosso'' channel provides coverage from 600--950$\,$nm at a
-spectral resolution of $\approx 80{,}000$.  Many of the exposures were
-taken in average or poor seeing conditions, when the SNR is lowest and
-the fiber-to-fiber cross-contamination on the IFU-style fiber feed is
-strongest.  To reduce the spectra to velocities, we cross-correlated
-against a template of $\delta$ Pavonis, because with spectral type G8
-IV it was the closest high-SNR \tn\ analog available in the Veloce
-spectral database.  The velocity RMS seen across each visit was
-hundreds of meters per second, likely due to uncorrected
-fiber-to-fiber cross-contamination.  This cross-contamination severely
-affects the wavelength solutions for the 19 individual science fibres,
-ultimately leading to significantly increased RV scatter. For analysis
-purposes, we averaged the single-shot RVs across each visit, and set
-the velocity uncertainties to be the standard deviation of the
-per-visit exposures.  The velocities are given in Table~\ref{tab:rvs},
-and shown in Figure~\ref{fig:rvs}.
-
-\input{TOI837_rv_table.tex}
-
-\section{Assessment of False Positive Scenarios}
-\label{sec:validation}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.75\textwidth]{f6.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Astrophysical false positive scenarios.} {\it Top}: for bound
-    companions (EB and HEB scenarios), {\it Bottom}: for unassociated
-    companions along the same line of sight (BEB scenarios).  Each
-    constraint is described in Section~\ref{subsec:fp_constraints}.
-    Gray regions are ruled out by at least one constraint.
-		\label{fig:fpscenario}
-	}
-\end{figure*}
-
-Validating a transiting planet means statistically arguing that the
-data are much more likely to be explained by a planet than by an
-astrophysical false positive. The concept of validation has been
-developed and calibrated by {\it e.g.},
-\citet{torres_modeling_2011,morton_efficient_2012,diaz_pastis_2014,santerne_pastis_2015,morton_false_2016}
-and \citet{giacalone_triceratops_2020}.  ``Validation'' is different
-from ``confirmation'', which means that there is overwhelming evidence
-that the transits {\it must} be explained by a planet, through
-elimination of all false positive scenarios and determination that the
-planet's mass is in the substellar regime.
-
-Assuming an eclipse has been localized to the target star, potential
-false positive scenarios include eclipses of a background binary
-(BEB), eclipses of a hierarchical system bound to the primary star
-(HEB), and the possibility that the eclipses are caused by a
-stellar companion, rather than a planetary one (EB).
-
-Figure~\ref{fig:fpscenario} provides a visual summary of the possible
-astrophysical false positive scenarios, as well as our ability to rule
-them out based on our combined photometry, velocimetry, and imaging.
-In this Section we describe each constraint in turn, and then present
-a calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
-demonstrate that the probability \tn\ is an astrophysical false
-positive is small enough to validate it as a planet.
-
-\subsection{Constraints on False Positive Scenarios}
-\label{subsec:fp_constraints}
-
-\subsubsection{Transit Depth}
-In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
-binary host blend together, and reduce the ``true'' TESS-band eclipse
-depth $\delta_{\rm true}$ to the observed depth $\delta_{\rm obs}$:
-\begin{equation}
-  \delta_{\rm obs}
-  = 
-  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
-\end{equation}
-where the total system flux and the flux from only the companion
-(``comp'') binary are labeled appropriately.  The requirement that the
-eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
-translates to a bound on the faintest possible blended companion
-system:
-\begin{equation}
-  \Delta m < -\frac{5}{2} \log_{10}
-             \left( \frac{0.5}{\delta_{\rm obs}} \right).
-\end{equation}
-For \tn\ ($T=9.93$), this implies that any stellar companion invoked
-to explain the transit depth must be brighter than $T=15.07$.  In
-Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
-on the precision at which we have localized the transits using
-seeing-limited ground-based photometry.
-
-If the transit were box-shaped, this argument could be extended to
-even more restrictive depths \citep[{\it
-e.g.},][]{seager_unique_2003,vanderburg_hr858_2019,rizzuto_tess_2020}.
-Since the transits of \tn\ could be grazing, the second and third
-contact points do not necessarily occur, and the shape of the transit
-is not particularly restrictive.
-
-\subsubsection{Speckle Imaging}
-The contrast limits obtained through the SOAR $I$-band speckle imaging
-(Section~\ref{subsec:speckle}) are shown in
-Figure~\ref{fig:fpscenario}.  While ``Star A'' was detected in the
-SOAR images, our ground-based photometry rules it out as a possible
-source of the eclipse signal (Section~\ref{subsec:groundphot}).  To
-convert the remaining contrast constraints to limits on the masses of
-bound companions, we used the \citet{baraffe_evolutionary_2003} models
-for sub-stellar mass objects and the MIST models for stellar mass
-objects
-\citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015,dotter_mesa_2016,choi_mesa_2016}.
-We assumed that the system age was 35 Myr, so that companions would be
-at a plausible state of contraction.
-
-To convert from theoretical effective temperatures and bolometric
-luminosities to expected magnitudes in instrumental bandpasses, we
-made the simplifying assumption that all sources had blackbody
-spectra.  Using the theoretical stellar parameters and the measured
-transmission functions \citep{tokovinin_ten_2018}, we then calculated
-the apparent magnitudes of stellar companions of different masses, and
-interpolated to produce the scale shown on the upper-right in
-Figure~\ref{fig:fpscenario}.
-
-\subsubsection{Not SB2}
-We derived limits on blended spectroscopic companions using the
-stacked CHIRON spectra (see Section~\ref{subsec:chiron}).  For a
-slowly rotating stellar companion well-separated in velocity, the
-spectra would have revealed companions with flux fractions $F_2/F_1
-\gtrsim 3\%$.  For a companion with rotational broadening of $15\,{\rm
-km\,s}^{-1}$, roughly equivalent to that of \tn, we were able to
-exclude companions with flux fractions exceeding $\approx$8\%.  For
-plotting purposes, in Figure~\ref{fig:fpscenario} we have assumed the
-latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
-
-\subsubsection{RVs}
-The radial velocities from FEROS, CHIRON, and Veloce can be used to
-detect massive bound companions orbiting \tn.  We searched for the
-presence of planetary and stellar-mass companions using
-\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits, and performed two sets of fits.
-
-% timmy.drivers.oneoff_drivers.get_mass_upper_limit
-For the first fit we set a prior on the period and time of conjunction
-using the known ephemeris from the transit.  We then fitted for the
-semi-amplitude, instrument offsets, and jitter parameters.  This
-yielded a non-detection of the planet's orbit.  The corresponding
-3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on $M_{\rm p} \sin
-i$ is $1.20 M_{\rm Jup}$.  The data and corresponding model are shown
-in Figure~\ref{fig:rvs}.
-
-The above exercise ruled out the possibility that the observed
-eclipses are caused by a stellar-mass object orbiting \tn.  The lack
-of a linear radial velocity trend, particularly in the FEROS data,
-further constrains the presence of a hierarchical binary system.
-Fitting a line to the FEROS velocities yielded a 3-$\sigma$ limit on
-linear radial velocity trends of $|\dot{\gamma}| < 0.82\,{\rm
-m\,s}^{-1}\,{\rm day}^{-1}$, over the 253 day FEROS baseline.  The
-agreement between the mean Gaia DR2 velocity ($17.44 \pm 0.64\,$\kms)
-and that from FEROS ($18.0 \pm 0.1$\kms) in theory places an
-additional limit on linear trends, since the two observation epochs
-are separated by roughly five years.
-
-To place limits on the properties of a possible bound hierarchical
-companion, we fitted the radial velocity data for a Keplerian orbit
-assuming wide logarithmic priors on the semi-amplitude and period: $K\
-[{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}]
-\sim \log \mathcal{U}(0.1, 10^{15})$.  We then fitted for the
-semi-amplitude, period, time of conjunction, instrument offsets, and
-jitter parameters.  We converted the resulting posterior in period and
-semi-amplitude to minimum mass and semi-major axis assuming Kepler's
-third law.  The resulting 3-$\sigma$ limits are shown in
-Figure~\ref{fig:fpscenario}.
-
-\subsubsection{Multicolor Photometry}
-\label{subsec:colorphot}
-
-\paragraph{Multicolor photometry and HEB scenarios}
-The most plausible HEB scenarios for \tn\ involve pairs of eclipsing M
-dwarfs (Figure~\ref{fig:fpscenario}).  Eclipses of such stars are much
-redder than eclipses of the G-dwarf \tn.  Limits on whether the
-transit depth decreases in bluer bandpasses can therefore rule out
-some HEB scenarios.
-
-We fitted for the observed depths in different bandpasses using a
-machinery similar to that described below in
-Section~\ref{subsec:planet}.  We fitted each ground-based transit
-individually for the planet-to-star size ratio, the impact parameter,
-and a local quadratic trend (the ephemeris was assumed from an initial
-fit of only the TESS data).  The corresponding 2-$\sigma$ lower limits
-on the transit depths in Cousins-R and Johnson-B band light curves
-were 2.82 and 1.77$\,$ppt, respectively, and are shown in
-Figure~\ref{fig:groundphot}.  Particularly in our Johnson-B light
-curve, the transit depth is correlated with the mean and linear slope
-of the light curve: a smaller depth is allowed if the data are fitted
-with a larger linear slope and a larger mean.  Our quoted limits
-marginalize over these correlations, and the depth measurement itself
-is nearly Gaussian.
-
-To determine what classes of HEB are eliminated by these limits, we
-performed the following calculation.  We assumed that each system was
-composed of the primary (\tn), plus a tertiary companion eclipsing a
-secondary companion every 8.3 days.  For secondary masses ranging from
-0.07 to 1.10 $M_\odot$, and mass ratios ($M_3/M_2$) from 0.1 to 1, we
-then calculated the observed maximal eclipse depth caused by Star 3
-eclipsing Star 2 in each observed bandpass.  As before, we
-interpolated between mass, effective temperature, and radius assuming
-the MIST isochrones for a 35$\,$Myr old system, and also assumed that
-each source had a blackbody spectrum.  We used the transmission
-functions from the SVO filter profile
-service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.  For
-a typical HEB system ({\it e.g.}, $M_2=M_3=0.2M_\odot$), the bluest
-optical bandpasses produced eclipses roughly 10 times shallower than
-in TESS-band, because the M-dwarf blackbody function turns over at
-much redder wavelengths than the G-dwarf blackbody (Wien's law).
-
-For a fixed secondary mass, we then asked whether any tertiary
-companions existed for which the maximal expected eclipse depth could
-have been larger than the observed depth.  In cases for which the
-answer was yes, we could not rule out such hierarchical eclipsing
-binary systems.  Conversely, we ruled out systems for which at fixed
-secondary mass no tertiary mass could enable eclipses of the necessary
-depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The ${\rm
-R_C}$-band limit corresponded to a secondary mass limit of $M_2 > 0.27
-M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger limit of
-$M_2 > 0.70 M_\odot$.
-
-\paragraph{Multicolor photometry and BEB scenarios}
-
-While the above constraints rule out HEBs, certain configurations of
-BEB systems ({\it e.g.}, a background G0V+K3V binary) can produce blue
-eclipses while remaining undetected along the line of sight.  Such
-scenarios are constrained by the lack of an observed secondary
-eclipse, and therefore require either eccentric orbits to avoid
-secondary eclipses, or else a background twin binary system at double
-the orbital period.  The only way to definitively rule out such
-scenarios is to prove that the loss of light is from the target star,
-for instance by detecting the Rossiter-McLaughlin effect during a
-transit, and confirming that the spectroscopic transit is consistent
-with the photometric transit.
-
-\subsubsection{Gaia}
-
-The ``Gaia'' curve in Figure~\ref{fig:fpscenario} combines both
-point-source detections from imaging and sources showing an
-astrometric noise excess relative to the single-source astrometric
-model.  The curve was interpolated from Figure~4 of
-\citet{rizzuto_zeitVIII_2018}.  \tn\ has a RUWE statistic of 1.022,
-indicative that there are no obviously present astrometric companions.
-The UWE statistic (square-root of the reduced astrometric $\chi^2$) is
-1.38, which is consistent with stars of similar brightness and color
-\citep[][Appendix A]{lindegren_gaiasoln_2018}.
-
-\subsubsection{Patient Imaging}
-
-Archival SERC-J and AAO-SES plates are available for the \tn\
-field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
-These plates were acquired in 1982 and 1992, respectively.  For high
-proper motion stars archival imagery can be used to detect slowly
-moving background stars that might be an astrophysical false-positive
-source \citep[{\it
-e.g.},][]{bakos_stellar_2006,huang_pimen_2018,vanderburg_hr858_2019}.
-However \tn\ has only moved $\approx0.7''$ between 1982 and present,
-in comparison to the $\approx2.0''$ FWHM of the target on the plates.
-We therefore cannot resolve it from background sources not already
-resolved through more modern imaging.
-
-\subsection{False positive probability}
-\label{subsec:fpp}
-
-The constraints on false-positive scenarios summarized in
-Figure~\ref{fig:fpscenario} rule out the possibilities that {\it i)}
-the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
-are caused by hierarchical blends, and {\it iii)} the eclipses are
-caused by neighboring stars outside $\approx 2''$.  The only scenario
-not formally ruled out is a background eclipsing binary.  A simple
-(fallacious) argument on the a priori probability of background blends
-follows from counting statistics.  The local density of $T<15.1$ stars
-around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
-arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
-not excluded by the SOAR HRCam contrast curve, for a randomly selected
-star we would expect $1.0\times10^{-4}$ potential $T<15.1$
-contaminants, which appears small.
-
-The reason the above statement is an insufficient argument against
-BEBs is that \tn\ is not a randomly selected star---it was selected
-because it shows eclipses.  Given a foreground star that shows
-eclipses, the probability of a background star being present is much
-greater than for an arbitrary foreground star.  The relevant
-populations need to be modeled at the Monte Carlo level.  We opt to
-use \texttt{VESPA} to model the populations
-\citep{morton_efficient_2012,vespa_2015}.
-
-\texttt{VESPA} calculates the false positive probability for a transit
-signal as
-\begin{equation}
-  {\rm FPP} = 1 - P_{\rm pl},
-\end{equation}
-where in our case the probability that the signal comes from a planet,
-$P_{\rm pl}$, is given by
-\begin{align}
-  P_{\rm pl} = 
-  \frac{
-    \mathcal{L}_{\rm pl}\pi_{\rm pl}
-  }{
-    \mathcal{L}_{\rm pl}\pi_{\rm pl} + \mathcal{L}_{\rm BEB}\pi_{\rm BEB}
-  },
-\end{align}
-where $\mathcal{L}_i$ is the model likelihood for the planet and BEB
-scenarios, and $\pi_i$ is the model prior.  The terms labeled as
-``BEB'' usually include other false positive scenarios (HEBs and EBs),
-but our followup data have excluded these possibilities.  The priors
-are evaluated using a combination of galactic population synthesis
-\citep{girardi_star_2005}, binary star statistics
-\citep{raghavan_survey_2010}, and specific planet occurrence rates
-\citep[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
-evaluated by forward-modeling a representative population of eclipsing
-bodies for each model class, in which each population member has a
-particular trapezoidal eclipse depth, total duration, and ingress
-duration.  The likelihood is then calculated by multiplying the
-probability distribution function of the simulated population's shape
-parameters with the posterior probability of the actual observed
-eclipse shape.
-
-% results from 20200624_simple_fpp_weak_sec 
-We ran \texttt{VESPA}\footnote{We used \texttt{VESPA-0.6} and
-\texttt{isochrones-1.2.2}.}, and directly incorporated our constraints
-of the SOAR $I$-band contrast curve and a non-detection of secondary
-eclipses with a depth set at roughly twice the limits from the SPOC
-vetting report (0.1\%).  We verified that changing the secondary
-eclipse depth limit did not significantly affect the results.  We set
-the maximum aperture radius at $2''$, based on our ground-based
-photometry.  Incorporating the constraints from
-Figure~\ref{fig:fpscenario}, our nominal false positive probability
-analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
-for \pn, sufficient for formal validation as a planet
-\citep{morton_efficient_2012}.  We did not incorporate our constraint
-that \tn\ is not double-lined, which rules out an additional portion
-of BEB parameter space.  Had we not acquired multicolor ground-based
-photometry, and been unable to exclude HEB scenarios, the FPP would
-have risen to 8\%.  Since the transits are achromatic
-(Figure~\ref{fig:groundphot}), particularly in Johnson-B band, we can
-rule out HEB scenarios.
-
-One potential caveat in our approach is that \texttt{VESPA} uses a
-galactic population synthesis to model the sight-line. Since \tn\ is
-in the foreground of \cn\ (see Section~\ref{subsec:star}), for roughly
-$25\,{\rm pc}$ behind the sightline to the star, the number of
-background stars is higher than \texttt{VESPA} would predict due to
-the presence of the cluster.  To quantify the importance of this
-effect, we assessed the sky-plane density of potential contaminants by
-counting stars brighter than $T=15.07$ within 0.5 degrees of \tn\
-\citep{stassun_TIC8_2019}. We then compared this density against
-sightlines rotated in galactic longitude towards and away from the
-galactic center. Within $\pm10^\circ$ in galactic longitude, the
-sky-plane density of stars fluctuated at the level of $\approx 15\%$,
-with a local maximum a few degrees away from \tn, towards the center
-of \cn.  The overall density also slowly increased towards the
-galactic center.  We therefore do not expect this consideration to
-significantly alter our FPP calculation.
-
-\section{System Modeling}
-\label{sec:system}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f7.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ 
-  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
-  Members (black circles) were identified by
-  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
-  with right ascension, declination, and parallax similar to \cn.
-  They are selected by drawing from a $(\alpha, \delta, \pi)$ cube
-  centered on the cluster with boundaries set at $5\times$ the
-  standard deviation in the cluster parameters.  $G$ denotes Gaia
-  broadband magnitudes, $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST
-  isochrones (colored lines) fit the upper main sequence well, but
-  diverge from the data for $M_\star \lesssim 0.7 M_\odot$. This is a
-  known issue with the M dwarf models (see Section~\ref{subsec:hr}).
-  \label{fig:hr}
-	}
-\end{figure}
-
-\begin{figure*}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.65\textwidth]{f8.pdf}
-	\end{center}
-	\vspace{-0.5cm}
-	\caption{ 
-  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
-  circles), and stars in the neighborhood (gray circles).} Members
-  were identified by \citet{cantatgaudin_gaia_2018}.  Neighbors are as
-  in Figure~\ref{fig:hr}. $\alpha$ denotes right ascension, $\delta$
-  declination, $\pi$ parallax, $\mu_{\rm \delta}$ and $\mu_{\rm
-  \alpha}$ proper motion in each equatorial direction, and ${\rm RV}$
-  radial velocity reported by Gaia DR2.  The RVs are for unblended
-  spectra of bright stars ($G\lesssim 12$).  The proper motion
-  projection ($\mu_{\delta}$ vs{.} $\mu_{\rm \alpha}\cos\delta$)
-  highlights incompleteness in the membership selection function.
-  \label{fig:full_kinematics}
-	}
-\end{figure*}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9a.pdf}
-		}
-
-		\vspace{-0.5cm}
-		\subfloat{
-			\includegraphics[width=0.45\textwidth]{f9b.pdf}
-		}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{ {\bf Youth diagnostics.}
-  {\it Top:} Rotation periods for \tn\ and selected open clusters.
-  The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
-  (1000$\,$Myr) are shown.  Their rotation periods were measured by
-  \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
-  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
-  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
-  open clusters.  The field star sample is drawn from Kepler planet
-  hosts, and was measured by \citet{berger_identifying_2018} using
-  Keck-HIRES.  The young open clusters members were surveyed by
-  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
-  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
-  lithium depletion boundary ages for these clusters of
-  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
-  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
-    \label{fig:lithium_rotation}
-	}
-\end{figure}
-
-\subsection{The Cluster}
-\label{subsec:cluster}
-
-\input{ic2602_ages.tex}
-
-\subsubsection{Physical Characteristics}
-\label{subsec:clusterchar}
-
-The \cn\ cluster is about 150$\,$pc from the Earth, and is near the
-galactic plane with $(l,b)\approx(289.6^\circ, -5.0^\circ)$
-\citep{cantatgaudin_gaia_2018}.  It is also sometimes called the
-$\theta$ Carinae cluster, after its brightest member, or also the
-``Southern Pleiades''.  While \cn\ is close to the Lower Centaurus
-Crux subgroup of the Scorpio-Centaurus OB2 association in both
-position and proper motion space, its older age and clear kinematic
-separation indicate that it is a distinct stellar population
-\citep{de_zeeuw_hipparcos_1999,damiani_stellar_2019}.
-
-Reliable ages reported for \cn\ range from 30 to 46$\,$Myr.  We have
-collected ages reported over the years in Table~\ref{tab:ages}.  The
-Li depletion boundary technique yields slightly older absolute ages
-than isochrone fitting \citep{dobbie_ic_2010,randich_gaiaeso_2018}.
-Rather than redetermine the age of the cluster and add another line to
-the table, we simply adopt an absolute age range for \tn\ of
-30--46$\,$Myr.
-
-Reported mean metallicity values ${\rm [Fe/H]}$ for the cluster range
-between slightly super-solar ($0.04\pm0.01$,
-\citealt{baratella_gaia-eso_2020}) and slightly sub-solar ($-0.02 \pm
-0.02$, \citealt{netopil_metallicity_2016}).  The extinction $E(B-V)$
-is rather low, with reported values ranging from 0.03 to 0.07
-\citep[{\it e.g.},][]{randich_gaiaeso_2018}.
-
-Kinematically, IC~2602 seems to be supervirial, in the sense that the
-observed stellar velocity dispersion is larger than the value expected
-if it were in virial equilibrium by about a factor of two
-\citep{bravi_gaia-eso_2018}.  \citet{damiani_stellar_2019} also
-reported evidence for the ongoing evaporation of \cn, in the form of a
-diffuse $\approx10^\circ$ halo of young stars around the central
-density cusps.  A gyrochronological study of these stars could confirm
-that these stars are truly coeval with the cluster.
-
-\subsubsection{HR Diagram}
-\label{subsec:hr}
-
-Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
-\cn\ cluster, and the neighborhood of spatially nearby stars.
-Stars labeled as cluster members are those reported by
-\citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
-motions, and parallaxes.  We included candidate members with formal
-membership probability exceeding 10\%.  Most members appear to be
-young and coeval.  \tn\ is in its expected position relative to the
-other members along the cluster isochrone.  This photometrically
-limits the presence of binary companions in the \tn\ system to be less
-than half the brightness ($\approx0.75$ magnitudes) of the target
-star.
-
-Figure~\ref{fig:hr} suggests that the membership census of \cn\ is
-incomplete.  We defined the reference neighborhood as the group of at
-most $10^4$ randomly selected non-member stars within 5 standard
-deviations of the mean \cn\ right ascension, declination, and
-parallax.  In other words, the neighborhood members are chosen based
-on the observed spread in the cluster's parameters.  We queried Gaia
-DR2 for these stars using \texttt{astroquery} \citep{astroquery_2018}.
-Many low-mass stars appear above the main sequence, even though they
-were not identified as 5-dimensional kinematic members through the
-unsupervised \citet{cantatgaudin_gaia_2018} membership assignment
-process.
-
-Figure~\ref{fig:hr} also compares the data to the MIST isochrones
-\citep{choi_mesa_2016}.  We used the web
-interface\footnote{\url{http://waps.cfa.harvard.edu/MIST/interp_isos.html},
-\texttt{2020-07-08}} to interpolate isochrones at 10, 20, 30, and 40
-million years. We assumed solar metallicity, and a fixed extinction
-value of $A_V = 0.217$ \citep{randich_gaiaeso_2018}.  The 30 and 40
-Myr models align well with the data for stars with masses ranging from
-roughly $0.7$--$7\,M_\odot$.  The pre-main-sequence (PMS) K and M
-dwarf models are bluer than observed in the Gaia photometry.  This
-discrepancy was noted and discussed at length by
-\citet{choi_mesa_2016}.  One suggested explanation was that strong
-magnetic fields in low-mass pre-main-sequence stars inhibit convection
-and produce a high filling factor of starspots \citep[{\it
-e.g.},][]{stauffer_why_2003,feiden_magnetic_2013}.  This explanation
-however fails to explain poor isochrone fits in both old open clusters
-({\it e.g.}, M$\,$67) and the field, particularly in blue bandpasses.
-An alternative explanation is that the molecular line lists for M
-dwarf atmospheres are incomplete in these wavelength ranges
-\citep{rajpurohit_effective_2013,mann_spectrothermometry_2013}.
-
-\subsection{The Star}
-\label{subsec:star}
-
-%\input{starparams.tex}
-
-\subsubsection{Membership of \tn\ in \cn}
-\label{subsec:member}
-
-\tn\ has been reported as a member of \cn\ by many independent
-investigators \citep[{\it
-e.g.},][]{Kharchenko_et_al_2013,oh_comoving_2017,cantatgaudin_gaia_2018,damiani_stellar_2019,kounkel_untangling_2019}.
-The simplest way to verify the membership is through inspection of the
-Gaia DR2 position and kinematics.  Figure~\ref{fig:full_kinematics}
-shows the six-dimensional positions and kinematics of \tn, \cn\
-members, and nearby stars.  The ``neighborhood'' is defined as in
-Figure~\ref{fig:hr}.  The axes limits for the right ascension,
-declination, and parallax dimensions are set by being within 5
-standard deviations of the mean \cn\ right ascension, declination, and
-parallax.  The axes limits for the proper motion and radial velocity
-dimensions are set at the 25$^{\rm th}$ and 75$^{\rm th}$ percentiles,
-in order to give a sense of the population's distribution, while
-excluding outliers.  The radial velocities suffer the greatest
-incompleteness due to the current $G\approx12$ magnitude limit of the
-Gaia DR2 data processing.
-
-Figure~\ref{fig:full_kinematics} provides strong evidence that \tn\ is
-a member of \cn.  The only dimension that could lead to some worry is
-the parallax, as \tn\ is one of the closest \cn\ members reported by
-\citet{cantatgaudin_gaia_2018}.  Fortunately, there are independent
-means of verifying the star's youth.
-
-\subsubsection{Rotation}
-
-As stars get older, their rotation rates incrementally slow due to
-magnetic braking \cite{weber_angular_1967,skumanich_time_1972}.  One
-way to verify the youth of \tn\ is by comparing its rotation period to
-other stars with known ages.
-
-We measured the rotation period from the TESS \texttt{PDCSAP} light
-curve using the Lomb-Scargle periodogram implemented in
-\texttt{astropy}
-\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015}.
-We fitted the light curve without masking out the transits or flares,
-as these represent a small fraction of the overall time series.  To
-derive the uncertainty on the best period, we fitted a Gaussian to the
-dominant peak, after first ensuring that we had oversampled the
-initial frequency grid.  This gave a rotation period of $P_{\rm rot} =
-2.987 \pm 0.056\,{\rm d}$ when allowing for a single Fourier term in
-the periodogram model, and $P_{\rm rot} = 3.004 \pm 0.053\,{\rm d}$
-when allowing for two Fourier terms.  As the latter model provides a
-better fit to the data, we adopt it as the rotation period.
-
-As we will discuss in Section~\ref{subsec:starparams}, we measured the
-star's radius by combining the spectroscopic effective temperature
-with a broadband photometry SED fit.  We would expect, combining our
-$R_\star$ and $P_{\rm rot}$ measurements, that the equatorial velocity
-$v$ of the star would be $17.67 \pm 0.32 \,{\rm km\,s}^{-1}$.  Our
-spectroscopically measured $v\sin i$ from CHIRON, $16.2 \pm 1.1 \,{\rm
-km\,s}^{-1}$ agrees reasonably well with this expectation.
-
-The star is clearly a rapid rotator.
-Figure~\ref{fig:lithium_rotation} compares its rotation period with
-rotation periods that have been measured in a number of well-studied
-open clusters.  \tn\ seems to be gyrochronologically coeval with the
-Pleiades sequence.  This is not to say that \tn\ is ``Pleaides-aged'',
-because the observed scatter in the rotation-period diagram for the
-first 10--100$\,$Myr is quite high \citep[see Figure~9
-of][]{rebull_rotation_2020}.  Instead, we interpret the rotation
-period as evidence to support the claim that \tn\ is younger than
-$\sim$ $500\,{\rm Myr}$.
-
-\subsubsection{Lithium}
-
-Lithium depletion for early G-dwarfs like \tn\ requires hundreds of
-megayears \citep{soderblom_ages_2014}. This is because their
-convective envelopes are shallow, and so transport of photospheric
-lithium to the hot core takes place over diffusive timescales, rather
-than convective timescales.  Nonetheless, comparison of early G-dwarfs
-in the field to {\it e.g.}, 600 Myr old Hyads has shown that the
-depletion does indeed happen over many gigayears
-\citep{berger_identifying_2018}.
-
-The spectra of \tn\ all show the 6708$\,$\AA\ lithium doublet in
-absorption. Opting to use our FEROS spectra because of their high S/N,
-we measured the line's equivalent width (EW) to be $154 \pm 9 \,
-$m\AA.  Figure~\ref{fig:lithium_rotation} compares this EW to stars in
-the field, and other young open cluster members.  The field star
-measurements were collected by \citet{berger_identifying_2018}; we
-show their reported lithium detections with ${\rm S/N}>3$.  The young
-open cluster members were selected for the presence of lithium, as
-described by \citet{randich_gaiaeso_2018}.  The measured \tn\ Li EW is
-much larger than observed for field stars, and is consistent with
-lithium absorption seen in stars with similar colors in sub-100$\,{\rm
-Myr}$ moving groups.
-
-\subsubsection{Stellar Parameters}
-\label{subsec:starparams}
-
-Select properties of \tn\ from the literature and our analysis are
-presented in Table~\ref{tab:starparams}.  We calculated the stellar
-parameters using two different approaches.
-
-In ``Method 1'', we measured spectroscopic parameters from each of the
-CHIRON spectra (Section~\ref{subsec:chiron}).  We then calculated the
-stellar radius and reddening following \citet{stassun_accurate_2017}.
-We first derived the bolometric flux by combining available broadband
-magnitudes from Gaia, Tycho-2, APASS, 2MASS, and WISE.  We then fitted
-the SED with the \citet{kurucz_atlas12_2013} stellar atmopshere
-models, and summed to find $F_{\rm bol}$.  When fitting the atmosphere
-model, we varied the extinction ($A_{\rm V}$) and the overall
-normalization.  This procedure yielded $A_{\rm V} = 0.20\pm0.03$,
-which agrees with the average from the \cn\ isochrone fits of
-\citet{randich_gaiaeso_2018}.  Combining the spectroscopic effective
-temperature, bolometric flux, and Gaia distance, we determined the
-stellar radius using the Stefan-Boltzmann law.  Combining this radius
-with the spectroscopic $\log g$ also yields a stellar mass.
-
-In ``Method 2'', we simply used the observed location of \tn\ in the
-HR diagram and interpolated against the 40$\,$Myr isochrone.  This
-method leverages the relative location of \tn\ within the narrow \cn\
-isochrone to derive precise, theoretically self-consistent constraints
-on all of the stellar parameters.  Although this approach would fail
-for a low-mass star, \tn\ is above the stellar masses where the Gaia
-photometry and isochrone models begin to diverge.
-
-Method 1 yielded a stellar mass that seemed to be high relative to the
-observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
-K}$, with relative uncertainties of a few percent on each). To avoid
-poorly understood systematics,  we adopted the stellar parameters from
-Method 2, and report them in Table~\ref{tab:starparams}.
-
-\subsection{The Planet}
-\label{subsec:planet}
-
-%\input{model_posterior_table.tex}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f10.pdf}
-	\end{center}
-	\vspace{-0.3cm}
-	\caption{ 
-    {\bf Posterior probabilities of impact parameter, planet-to-star
-    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
-    and 4-$\sigma$ confidence.  The planet-to-star size ratio
-    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
-    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
-    This plot was made using \texttt{corner} \citep{corner_2016}.
-		\label{fig:subsetcorner}
-	}
-\end{figure}
-
-We also fitted the available time-series photometry of \pn\ using two
-different approaches.  To derive the most precise possible ephemeris,
-we fitted the ground and space-based transits simultaneously.  To
-derive the physical parameters of the planet, we fitted the TESS data
-alone, due to our better understanding of the underlying systematic
-trends and the higher precision.
-
-For the TESS \texttt{PDCSAP} light curve, we first eliminated points
-that had quality flags corresponding to any of bits $\{3, 4, 6, 8, 11,
-12\}$.  This excluded cadences affected by coarse spacecraft pointing,
-reaction wheel desaturation events, manual flags, cosmic ray hits, and
-straylight from the Earth or Moon being present.  Inspecting the data,
-we also manually excluded the two flares shown in
-Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
-of $\pm 7\,{\rm hr}$ centered on each transit.
-
-Our model for time-series photometry data was an
-\citet{exoplanet:agol20} transit with physical and orbital parameters
-shared across all transit windows, plus a local quadratic trend
-allowed within each window.  Select parameters and priors are listed
-in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
-fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
-u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
-p}/R_\star)\}$.  There were also three free trend parameters for each
-transit window to account for the local rotational variability.  In
-the TESS-only model this yielded 23 free parameters, of which 8 were
-physically relevant and 15 were nuisance parameters.  In the combined
-TESS and ground-based model, there were an additional 7 transits, and
-therefore an additional 21 nuisance parameters for a total of 44 free
-parameters.
-
-We fitted the model using \texttt{PyMC3}
-\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the exoplanet
-transit, we used the \texttt{exoplanet} code
-\citep{exoplanet:exoplanet}.  After initializing each model with the
-parameters of the maximum {\it a posteriori} model, we assumed a
-Gaussian likelihood, and sampled using \texttt{PyMC3}'s gradient-based
-No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as
-our convergence diagnostic \citep{gelman_inference_1992}.
-
-We opted for this approach rather than a joint fit of the photometry
-and radial velocities because the RVs on their own did not show
-evidence for a planetary signal.  Our preference for using only the
-TESS data to derive the transit parameters was in our view justified
-by the systematic uncertainties inherent to ground-based light curve
-production, particularly in comparison star selection.  Our assumption
-of a constant radius across all bandpasses was tested by independently
-fitting each ground-based transit while letting the planetary radius
-float (Section~\ref{subsec:colorphot}). The transit depths did not
-significantly change between different bandpasses.
-
-The posteriors from fitting the TESS data alone are given in
-Table~\ref{tab:posterior}.  The condition for a grazing transit is
-whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
-The relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  The transit is therefore either
-grazing, or nearly grazing.  From experimenting with the priors, we
-found that in the absence of a strong prior on the stellar density,
-the inherent degeneracy between the impact parameter and
-planet-to-star size ratio would have been much stronger.  In the
-absence of precise information about the star, a larger fraction of
-the posterior would therefore have been grazing.  However, our priors
-on the stellar parameters from the cluster isochrone fit break this
-degeneracy, enabling us to report two-sided limits on the
-planet-to-star size ratio.
-
-\section{Discussion}
-\label{sec:discussion}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f11.pdf}
-	\end{center}
-	\vspace{-0.6cm}
-	\caption{
-    {\bf Planet radii versus ages, for the known transiting planets.} 
-    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
-    are from the NASA Exoplanet Archive on 29 July 2020.  Precise ages
-    are known for only a small fraction of the gray points.
-		\label{fig:rpvsage}
-	}
-	\vspace{-0.2cm}
-\end{figure}
-
-\tn\ joins a number of other young planetary systems reported from
-TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
-\citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
-ages.  \tn\ is among the youngest transiting planets known.
-
-While we have statistically validated that \tn\ is a planet, the
-possibility that it could be a background eclipsing binary has not
-been excluded with sufficient confidence to call the planet
-``confirmed''.  The distinction is methodological.  Our calculations
-have shown that at a population level we expect negligibly few BEBs
-within $\approx0.3''$ of \tn\ to produce eclipses of the appropriate
-shape across all bandpasses, with no observed secondary eclipse or
-odd-even variations (Section~\ref{subsec:fpp}).  This statement is
-tautologically ``validation'', but it is weaker than having data on
-hand that conclusively rules in favor of the planetary interpretation.
-
-The easiest way to definitively confirm the planetary nature of \tn\
-will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
-signal consistent with the photometric transit would rule out BEB and
-HEB scenarios, as it would imply that the eclipsing object is bound to
-the target star. Combined with our non-detection of the planet's mass
-from radial velocity monitoring, this would confirm that \pn\ is a
-planet.
-
-The maximum amplitude of the Rossiter-McLaughlin anomaly is
-\citep{gaudi_prospects_2007}
-\begin{align}
-  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
-  \approx 14\,{\rm m\,s}^{-1},
-\end{align}
-for
-\begin{align}
-  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
-\end{align}
-where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
-assumed $b=0.95$ and used stellar and transit parameters from
-Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
-challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
-could be achieved with modern spectrographs.  The next viable total
-transit windows from Chile occur in January and February of 2021;
-there are also a few visible per season from other southern locations.
-The most precise available ephemeris, found from our joint fit of the
-TESS and ground-based photometry, is as follows.
-\begin{align}
-  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
-  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
-  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
-  \label{eq:ephem}
-\end{align}
-% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex
-
-The Rossiter-McLaughlin approach is more likely to yield short-term
-success than a direct mass measurement because of the RV noise
-expected to be induced by stellar rotation.  The photometric amplitude
-induced by starspots on \tn\ is $\approx 2\%$.  The spot-induced RV
-variation expected over the course of the $\approx 3\,{\rm d}$
-rotation period can be estimated by multiplying the photometric
-amplitude and spectroscopic equatorial velocity.  This gives
-$\sigma_{\rm RV,rot} \approx 300\,{\rm m\,s}^{-1}$, and is consistent
-with the scatter we observe in our radial velocities from FEROS.
-Detecting a planet's Keplerian motion in this regime is challenging,
-and requires a significant amount of data and care in signal
-extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
-measurement avoids the majority of this issue because the transit
-occurs over a much shorter duration than a single stellar rotation
-period.
-
-If the RM measurements prove that the validated planet is real,
-measuring its mass may be worth the effort, because it would improve
-understanding of the planet's contraction and photoevaporation.  If an
-RV campaign were timed to coincide with TESS sectors 36 and 37 (3
-March 2021 through 28 April 2021), it would significantly ease
-extraction of the Keplerian signal.  The reason is that the RVs,
-activity indicators, and photometry could be modeled simultaneously
-\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
-Combining photometric and radial velocity data from non-overlapping
-epochs would also constrain the models, but perhaps not quite as
-convincingly.
-
-While we hope that RV observations will be pursued, data acquired
-during the TESS mission extension may also help in understanding the
-system \citep{bouma_extend_2017,huang_expected_2018}.  Any
-misalignment between the star's spin axis and the planet's orbit
-should induce nodal precession, which could yield large changes in the
-transit duration given the system's high impact parameter.  If
-observed, this could be a spectroscopy-free method for confirming the
-planet.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-\acknowledgements
-\raggedbottom
-
-L.G.B. and J.H. acknowledge support by the TESS GI Program, program
-G011103, through NASA grant 80NSSC19K0386.
-%
-This study was based in part on observations at Cerro Tololo
-Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
-2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
-Universities for Research in Astronomy (AURA) under a cooperative
-agreement with the National Science Foundation.
-%
-This paper includes data collected by the TESS mission, which are
-publicly available from the Mikulski Archive for Space Telescopes
-(MAST).
-%
-Funding for the TESS mission is provided by NASA's Science Mission
-directorate.  \tn\ was included on the TESS 2-minute target list in
-part thanks to the Guest Investigator program of G.\ Sacco (G011265).
-%
-
-We acknowledge support from the French and Italian Polar Agencies,
-IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI
-(ANR-15-IDEX-01). We thank the dedicated staff at Concordia for their
-continuous presence and support throughout the Austral winter.
-%
-This research received funding from the European Research Council
-(ERC) under the European Union's Horizon 2020 research and innovation
-programme (grant n$^\circ$ 803193/BEBOP), and from the
-Science and Technology Facilities Council (STFC; grant n$^\circ$
-ST/S00193X/1).
-%
-% The Digitized Sky Survey was produced at the Space Telescope Science
-% Institute under U.S. Government grant NAG W-2166.
-% Figure~\ref{fig:scene} is based on photographic data obtained using
-% the Oschin Schmidt Telescope on Palomar Mountain.
-%
-
-This research was based in part on observations obtained at the
-Southern Astrophysical Research (SOAR) telescope, which is a joint
-project of the Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e
-Inova\c{c}\~{o}es (MCTI/LNA) do Brasil, the US National Science
-Foundation’s NOIRLab, the University of North Carolina at Chapel Hill
-(UNC), and Michigan State University (MSU).
-
-This research made use of the Exoplanet Follow-up Observation
-Program website, which is operated by the California Institute of
-Technology, under contract with the National Aeronautics and Space
-Administration under the Exoplanet Exploration Program.
-% %
-% This research made use of the NASA Exoplanet Archive, which is
-% operated by the California Institute of Technology, under contract
-% with the National Aeronautics and Space Administration under the
-% Exoplanet Exploration Program.
-% %
-
-This research made use of the SVO Filter Profile Service
-(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
-MINECO through grant AYA2017-84089.
-
-Resources supporting this work were provided by the NASA High-End
-Computing (HEC) Program through the NASA Advanced Supercomputing (NAS)
-Division at Ames Research Center for the production of the SPOC data
-products.
-%
-
-A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
-Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
-Chilean Ministry of Economy. A.J.\ acknowledges additional support
-from FONDECYT project 1171208.  J.I.V\ acknowledges support from
-CONICYT-PFCHA/Doctorado Nacional-21191829.  R.B.\ acknowledges support
-from FONDECYT Post-doctoral Fellowship Project 3180246.
-%
-C.T.\ and C.B\ acknowledge support from Australian Research Council
-grants LE150100087, LE160100014, LE180100165, DP170103491 and
-DP190103688.
-%
-C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
-Astronomy \& Astrophysics, funded through an endowment established by
-the Dunlap family and the University of Toronto.
-%
-D.D.\ acknowledges support through the TESS Guest Investigator Program
-Grant 80NSSC19K1727.
-%
-%
-%
-% %
-% Based on observations obtained at the Gemini Observatory, which is
-% operated by the Association of Universities for Research in Astronomy,
-% Inc., under a cooperative agreement with the NSF on behalf of the
-% Gemini partnership: the National Science Foundation (United States),
-% National Research Council (Canada), CONICYT (Chile), Ministerio de
-% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
-% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
-% and Korea Astronomy and Space Science Institute (Republic of Korea).
-% %
-% Observations in the paper made use of the High-Resolution Imaging
-% instrument Zorro at Gemini-South. Zorro was funded by the NASA
-% Exoplanet Exploration Program and built at the NASA Ames Research
-% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
-% Quigley.
-% %
-% This research has made use of the VizieR catalogue access tool, CDS,
-% Strasbourg, France. The original description of the VizieR service was
-% published in A\&AS 143, 23.
-% %
-% This work has made use of data from the European Space Agency (ESA)
-% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
-% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
-% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
-% for the DPAC has been provided by national institutions, in particular
-% the institutions participating in the {\it Gaia} Multilateral
-% Agreement.
-%
-% (Some of) The data presented herein were obtained at the W. M. Keck
-% Observatory, which is operated as a scientific partnership among the
-% California Institute of Technology, the University of California and
-% the National Aeronautics and Space Administration. The Observatory was
-% made possible by the generous financial support of the W. M. Keck
-% Foundation.
-% The authors wish to recognize and acknowledge the very significant
-% cultural role and reverence that the summit of Maunakea has always had
-% within the indigenous Hawaiian community.  We are most fortunate to
-% have the opportunity to conduct observations from this mountain.
-%
-% \newline
-%
-
-\software{
-  \texttt{astrobase} \citep{bhatti_astrobase_2018},
-  %\texttt{astroplan} \citep{astroplan2018},
-	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
-  \texttt{astropy} \citep{astropy_2018},
-  \texttt{astroquery} \citep{astroquery_2018},
-  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
-  \texttt{ceres} \citep{brahm_2017_ceres},
-  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
-  \texttt{corner} \citep{corner_2016},
-  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
-  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
-  dependencies \citep{exoplanet:agol20, exoplanet:kipping13, exoplanet:luger18,
-  	exoplanet:theano},
-	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
-  \texttt{IPython} \citep{perez_2007},
-	\texttt{isochrones} \citep{morton_2015_isochrones},
-	\texttt{lightkurve} \citep{lightkurve_2018},
-  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
-  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
-  \texttt{numpy} \citep{walt_numpy_2011}, 
-  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
-  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
-  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
-  \texttt{radvel} \citep{fulton_radvel_2018},
-  %\texttt{scikit-learn} \citep{scikit-learn},
-  \texttt{scipy} \citep{jones_scipy_2001},
-  \texttt{tesscut} \citep{brasseur_astrocut_2019},
-	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
-  \texttt{webplotdigitzer} \citep{rohatgi_2019},
-  \texttt{wotan} \citep{hippke_wotan_2019}.
-}
-\
-
-\facilities{
- 	{\it Astrometry}:
- 	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}.
- 	{\it Imaging}:
-    Second Generation Digitized Sky Survey,
-    SOAR~(HRCam; \citealt{tokovinin_ten_2018}).
- 	%Keck:II~(NIRC2; \url{www2.keck.hawaii.edu/inst/nirc2}).
- 	%Gemini:South~(Zorro; \citealt{scott_nessi_2018}.
- 	{\it Spectroscopy}:
-	CTIO1.5$\,$m~(CHIRON; \citealt{tokovinin_chironfiber_2013}),
-    MPG2.2$\,$m~(FEROS; \citealt{kaufer_commissioning_1999}),
-	AAT~(Veloce; \citealt{gilbert_veloce_2018}).
- 	%Keck:I~(HIRES; \citealt{vogt_hires_1994}).
- 	%{\bf VLT (number), UVES and GIRAFFE} (CITE: Pasquini et al 2002)
-% 	Euler1.2m~(CORALIE),
-% 	ESO:3.6m~(HARPS; \citealt{mayor_setting_2003}).
- 	{\it Photometry}:
- 	  ASTEP:0.40$\,$m (ASTEP400),
-% 	CTIO:1.0m (Y4KCam),
-% 	Danish 1.54m Telescope,
-	  El Sauce:0.356$\,$m,
-% 	Elizabeth 1.0m at SAAO,
-% 	Euler1.2m (EulerCam),
-% 	Magellan:Baade (MagIC),
-% 	Max Planck:2.2m	(GROND; \citealt{greiner_grond7-channel_2008})
-% 	NTT,
-% 	SOAR (SOI),
- 	TESS \citep{ricker_transiting_2015}.
-% 	TRAPPIST \citep{jehin_trappist_2011},
-% 	VLT:Antu (FORS2).
-}
-
-% \input{TOI837_phot_table.tex}
-% \input{TOI837_rv_table.tex}
-% \input{ic2602_ages.tex}
-\input{starparams.tex}
-\input{model_posterior_table.tex}
-
-\clearpage
-\bibliographystyle{yahapj}                            
-\bibliography{bibliography}
-
-\listofchanges
-
-%\allauthors
-\end{document}
+We report the discovery of TOI 837b and its validation as a transiting planet.
+We characterize the system using data from the NASA TESS mission, the ESA Gaia mission, ground-based photometry from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and Veloce.
+We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the southern open cluster IC 2602.
+The star and planet are therefore $35^{+11}_{-5}$ million years old.
+Combining the transit photometry with a prior on the stellar parameters derived from the cluster color-magnitude diagram, we find that the planet has an orbital period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).
+From radial velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm Jup}$ (3-$\sigma$).
+The transits either graze or nearly graze the stellar limb.
+Grazing transits are a cause for concern, as they are often indicative of astrophysical false positive scenarios.
+Our follow-up data show that such scenarios are unlikely.
+Our combined multi-color photometry, high-resolution imaging, and radial velocities rule out hierarchical eclipsing binary scenarios.
+Background eclipsing binary scenarios, though limited by speckle imaging, remain a 0.2\% possibility.
+TOI 837b is therefore a validated adolescent exoplanet.
+The planetary nature of the system can be confirmed or refuted through observations of the stellar obliquity and the planetary mass.
+Such observations may also improve our understanding of how the physical and orbital properties of exoplanets change in time.

### 2020-08-06 drivers/fit_oddevenindivtransit.py

@@ -129,18 +129,18 @@ def main(modelid):
                         kind='stats', stat_funcs={'median':np.nanmedian},
                         extend=True)
 
-    printparams = ['r_planet', 'b', 'r', 'r_sq']
+    printparams = ['r_planet', 'b', 'log_r', 'log_r_sq']
     print(42*'-')
     print(modelid)
     for p in printparams:
-        if p != 'r_sq':
+        if p != 'log_r_sq':
             med = np.percentile(m.trace[p], 50)
             up = np.percentile(m.trace[p], 84)
             low = np.percentile(m.trace[p], 36)
         else:
-            med = np.percentile(m.trace[p[0]]**2, 50)
-            up = np.percentile(m.trace[p[0]]**2, 84)
-            low = np.percentile(m.trace[p[0]]**2, 36)
+            med = np.percentile(np.exp(m.trace['log_r'])**2, 50)
+            up = np.percentile(np.exp(m.trace['log_r'])**2, 84)
+            low = np.percentile(np.exp(m.trace['log_r'])**2, 36)
         print(f'{p} limit: {med:.6f} +{up-med:.6f} -{med-low:.6f}')
     print(42*'-')
 

### 2020-08-06 paper/ms.tex
add abstract for AAS
update manuscript

@@
 candidate young stars that have been reported in the literature.  At
-the time of writing, we had made $\sim$$6\times10^5$ light curves from
-the first year of TESS observations. The light curves are available at
-MAST\footnote{\stscilink}, and through \datasetlink.  Searching
+the time of writing, $\sim$$6\times10^5$ light curves from
+Year 1 of TESS had been created and were available through
+MAST\footnote{\stscilink}, and via \datasetlink.  Searching
 through a subset of these light curves brought our attention to the
@@
 \tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
-the tenth and eleventh sectors of science operations
+Sector 10 and Sector 11 of science operations
 \citep{ricker_transiting_2015}.  The star was designated
@@
 Sector 10, again with three transits in Sector 11, and then for a
-final time when Sectors 1-13 were searched at the end of the first
+final time when Sectors 1--13 were searched at the end of the first
 year of the mission. The transit signature was fitted with a
@@
 phase-folded view of the TESS transits with starspot variability
-removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
-for the models shown in these plots is described in
+removed is also shown in Figure~\ref{fig:tessphot}. Our fitting procedure
+for the models in these plots is described in
 Section~\ref{subsec:planet}.
@@
 \texttt{2020-07-08}. } value is available.  We suspect that the
-photometric failure to produce an $Rp$ magnitude as well as its poor
-astrometric fit are due to blending with \tn.
+photometric failure to produce an $Rp$ magnitude as well as the poor
+astrometric fit of this star are due to blending with \tn.
 
@@
     using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
-    ASTEP400 telescop at Dome C.  Black points represent the
+    ASTEP400 telescope at Dome C.  Black points represent the
     measurements after binning at 10-minute intervals. The gray line
@@
 \tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
-2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
-of $25\,$s, readout and processing overhead of $25\,$s).  Except for
+2020, and 23 June 2020 (UT).  Except for
 12 May, our observations were conducted under stable weather
@@
 wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
-exclude from the analysis all data collected on May 12. We found that
+exclude from the analysis all data collected on 12 May. We found that
 the optimal calibrated light curves of \tn\ correspond to an 11 pixel
@@
     included.  The expected scatter from starspots based on $v\sin i$
-    and the photometric modulation amplitude is of order
-    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
+    and the photometric modulation amplitude is
+    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
     orbital ephemeris of \pn.  The planet is not detected.  The dashed black
@@
 characterization of the star and therefore planet.  Reducing multiple
-spectra to a radial velocity time-series can enable planet mass
-measurements, and also set limits on the mass of any nearby
+spectra to radial velocities can enable planet mass
+measurements, and can also lead to limits on the mass of nearby
 companions.  Finally, if there are close or bright companions,
@@
 a calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
-demonstrate that the probability \tn\ is an astrophysical false
+demonstrate that the probability of \tn\ being an astrophysical false
 positive is small enough to validate it as a planet.
@@
 where the total system flux and the flux from only the companion
-(``comp'') binary are labeled appropriately.  The requirement that the
+(``comp'') binary are labeled as such.  The requirement that the
 eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
@@
 transit depth decreases in bluer bandpasses can therefore rule out
-some HEB scenarios.
+certain HEB scenarios.
 
@@
 companions existed for which the maximal expected eclipse depth could
-have been larger than the observed depth.  In cases for which the
-answer was yes, we could not rule out such hierarchical eclipsing
-binary systems.  Conversely, we ruled out systems for which at fixed
+have been larger than the observed depth.  
+We could not rule out hierarchical eclipsing binary systems in cases
+for which the answer was yes.
+Conversely, we ruled out systems for which at fixed
 secondary mass no tertiary mass could enable eclipses of the necessary
@@
   with right ascension, declination, and parallax similar to \cn.
-  They are selected by drawing from a $(\alpha, \delta, \pi)$ cube
+  They are selected by drawing from a $\{\alpha, \delta, \pi\}$ cube
   centered on the cluster with boundaries set at $5\times$ the
@@
   hosts, and was measured by \citet{berger_identifying_2018} using
-  Keck-HIRES.  The young open clusters members were surveyed by
+  Keck-HIRES.  The young open cluster members were surveyed by
   \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
@@
 The resulting best-fit depths were consistent within 1-$\sigma$.
-% odd: (Rp/R*)^2 = 0.005500 +0.000558 -0.000169
-% even: (Rp/R*)^2 = 0.005659 +0.000636 -0.000185
+% odd:  log(r/rs) = -2.601528 +0.048317 -0.015647
+% even: log(r/rs) = -2.587273 +0.053236 -0.016607
 
@@
 
-The easiest way to definitively confirm the planetary nature of \tn\
+The easiest way to confirm the planetary nature of \tn\
 will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
@@
 \begin{align}
-  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
+  f_{\rm LD} &= 1 - u_1 ( 1 - \mu ) - u_2 (1 - \mu )^2,
 \end{align}
-where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
+where $\mu \approx (1 - b^2)^{1/2}$, $u_i$ are the limb-darkening
+parameters, and for calculation purposes we
 assumed $b=0.95$ and used stellar and transit parameters from
@@
 understanding of the planet's contraction and photoevaporation.  If an
-RV campaign were timed to coincide with TESS sectors 36 and 37 (3
+RV campaign were timed to coincide with TESS Sectors 36 and 37 (3
 March 2021 through 28 April 2021), it would significantly ease

### 2020-08-06 timmy/multicolor.py

@@ -70,7 +70,6 @@ def run_bulk_depth_color_grids(bandpass_to_use=None,
             # geometric scaling factor
             scalefactor = delta_obs_TESS / df['TESS']
             df['TESS_scaled'] = df['TESS'] * scalefactor
-            #FIXME Johnson-B
 
             if bp == 'Rc':
                 # for the HEB scenario to be plausible given  the depth observed in
@@ -82,6 +81,8 @@ def run_bulk_depth_color_grids(bandpass_to_use=None,
                 df['Johnson_B_scaled'] = df['Johnson_B'] * scalefactor
                 df['isviable_Johnson_B'] = df['Johnson_B_scaled'] > delta_lim_B
                 N_viable = len(df[df['isviable_TESS'] & df['isviable_Johnson_B']])
+            else:
+                raise NotImplementedError
 
             N_tot = len(df)
             frac_viable.append(N_viable / N_tot)

### 2020-08-28 paper/ms.tex
update submit date
update manuscript with amended f11

@@
 
-\documentclass[12pt,twocolumn,tighten]{aastex63}
-%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
+%\documentclass[12pt,twocolumn,tighten]{aastex63}
+\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
 \usepackage{amsmath,amstext,amssymb}
@@
 %% Add "Submitted to " argument.
-\received{\today}
+\received{August 6, 2020}
 \revised{---}
@@
 a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1$\,$Gyr, a number of direct and indirect methods are
+younger than say 1$\,$\replaced{Gyr}{gigayear}, a number of direct and indirect methods are
 available \citep{soderblom_ages_2010}.  The traditional approach is to
@@
 
+\explain{NOTE: removed footnote to Damasso et al 2020 in prep, since
+it has now been published, and added note to Donati et al 2020.}
 A few dozen planets in clusters have been detected, and fewer still
@@
 starspot-induced radial velocity (RV) variations, RV surveys found
-success in the Hyades, NGC~2523, Praesepe, and M~67
+success in the Hyades, NGC~\replaced{2523}{2423}, Praesepe, and M~67
 \citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
 RV surveys of highly active pre-main sequence stars in Taurus also led
-to the youngest hot Jupiters yet reported orbiting
-V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
-not confirm the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
+to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26,
+and CI~Tau
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
+\added{
+The planetary nature of at least two of these signals has been debated
+\citep{donati_magnetic_2020,damasso_gaps_2020}.
+}
 
@@
 diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
-depth test, the weak secondary eclipse test, the ghost diagnostic
-test, and the difference image centroiding test, which placed the
+depth test, the weak secondary eclipse test, \deleted{the ghost diagnostic
+test,} and the difference image centroiding test, which placed the
 transit source within $\sim$2 arcsec of the location of TOI~837. No
@@
 candidate transiting planet on 17 June 2019.  Our subsequent blind
-search of the CDIPS FFI light curves also showed the transits. Given
+search of the CDIPS FFI light curves also showed the transits\added{,
+as did that of \citet{nardiello_pathosII_2020}}. Given
 that the 2-minute data had better sampling cadence, we opted to use
@@
 		\leavevmode
-		\includegraphics[width=0.48\textwidth]{f11.pdf}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f11a.pdf}
+		}
+
+		\vspace{-0.5cm}
+		\subfloat{
+			\includegraphics[width=0.48\textwidth]{f11b.pdf}
+		}
 	\end{center}
@@
 	\caption{
-    {\bf Planet radii versus ages, for the known transiting planets.} 
-    Systems younger than 100$\,$Myr are emphasized.  Ages and radii
-    are from the NASA Exoplanet Archive on 29 July 2020.  Precise ages
-    are known for only a small fraction of the gray points.
-		\label{fig:rpvsage}
+    \explain{The bottom sub-panel of this figure has been added
+    in revision.}
+    {\bf \tn\ compared to known transiting planets}.
+    {\it Top}: Planet radii versus ages.  Systems younger than
+    100$\,$Myr are emphasized.  Ages and radii are from the NASA
+    Exoplanet Archive on 27 Aug 2020.  Precise ages are known for only
+    a small fraction of the gray points.
+    {\it Bottom}: Planet radii versus orbital periods. The known young
+    transiting planets do not obviously overlap with the populations of
+    known hot Jupiters or sub-Neptunes.
+		\label{fig:population}
 	}
@@
 \citep{newton_tess_2019,zhou_well_2020,montet_young_2020,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}.
-Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet sizes and
-ages.  \tn\ is among the youngest transiting planets known.
+\replaced{ Figure~\ref{fig:rpvsage} shows \tn\ in the space of planet
+sizes and ages.  \tn\ is among the youngest transiting planets known.
+}{ In the space of planet sizes and ages, the top panel of
+Figure~\ref{fig:population} shows that \tn\ is among the youngest
+transiting planets known.  }
+
+\added{In the space of planet sizes and orbital periods, the bottom
+panel of Figure~\ref{fig:population} highlights a peculiar feature of
+the known sub-100$\,$Myr transiting planets: they do not overlap with
+the known populations of either hot Jupiters or sub-Neptune sized
+planets.  The young planets instead have sizes ranging from
+4.2$\,R_\oplus$ (AU Mic b) to slightly smaller than Jupiter.  The lack
+of sub-Neptune sized planets could be a selection effect, because
+larger planets are easier to detect around highly variable stars.
+Another (speculative) explanation is that the known
+sub-100$\,$Myr planets are currently enveloped by primordial H/He
+atmospheres, and that they will become sub-Neptune sized planets after
+undergoing atmospheric escape \citep[{\it
+e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,gupta_sculpting_2019,gupta_signatures_2020}.
+}
 
@@
 measuring its mass may be worth the effort, because it would improve
-understanding of the planet's contraction and photoevaporation.  If an
-RV campaign were timed to coincide with TESS Sectors 36 and 37 (3
-March 2021 through 28 April 2021), it would significantly ease
-extraction of the Keplerian signal.  The reason is that the RVs,
-activity indicators, and photometry could be modeled simultaneously
-\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
-Combining photometric and radial velocity data from non-overlapping
-epochs would also constrain the models, but perhaps not quite as
-convincingly.
+understanding of the planet's \replaced{contraction and
+photoevaporation}{composition and therefore future atmospheric
+evolution}.  If an RV campaign were timed to coincide with TESS
+Sectors 36 and 37 (3 March 2021 through 28 April 2021), it would
+significantly ease extraction of the Keplerian signal.  The reason is
+that the RVs, activity indicators, and photometry could be modeled
+simultaneously \citep[{\it
+e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.  Combining
+photometric and radial velocity data from non-overlapping epochs would
+also constrain the models, but perhaps not quite as convincingly.
 
@@
 \software{
+  \texttt{arviz} \citep{arviz_2019},
   \texttt{astrobase} \citep{bhatti_astrobase_2018},

### 2020-08-28 paper_review/response_20200826.txt
[WIP] add referee report

Dear Dr. Endl,

We thank you for organizing the review of our paper, and also
thank the referee for constructive criticism.  We have considered
the referee's remarks carefully and revised our manuscript
accordingly.

Below, we have reproduced the relevant portions of the referee's
report, alongside our responses. A list of changes is appended to
the manuscript using the trackchanges AASTeX macros.

Sincerely,

Luke Bouma

******************************************
REFEREE COMMENT
----------
It appears that TOI 837 b was previously noted as a candidate planet and IC
2602 member in Nardiello et al. 2020
(https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.4924N/abstract).  If the
authors were unaware, it is still worth mentioning this in the text.

RESPONSE
----------
> Thank you for noting the omission. We have added the relevant
> citation in Section 2.1.

******************************************
REFEREE COMMENT
----------
Sec. 2.1
A number of validation tests are listed, but no detail is
provided about how these tests work. For example, what is the
ghost diagnostic test?

RESPONSE
----------
> For the sake of brevity, we prefer to continue with our
> refererence to Twicken et al., 2018. The optical ghost
> diagnostic test in the SPOC pipeline (Twicken et al., 2018,
> Section 3.7) flags threshold crossing events that are likely to
> be caused by reflections of light from bright sources between
> CCDs. Since few people know what it is, and it will therefore
> confuse the reader, we have omitted it from the manuscript.

******************************************
REFEREE COMMENT
----------
Sec. 2.1
Have the authors performed a by-eye search for additional
transits in the light curve?

RESPONSE
----------
> We did perform a by-eye search for additional transits in the
> light curve, and did not find any compelling events. The
> logical next step -- quantifying our sensitivity through
> injection-recovery simulations -- would be an interesting
> exercise.  However, for it to be valid, care would need to be
> taken to marginalize out dependence on the detrending method
> (e.g., David et al 2019 and 2020's experience which led to the
> four-planet V1298 Tau system).  Given the required level of
> work, we feel this exercise to be outside the scope of the
> present work.

******************************************
REFEREE COMMENT
----------
Sec. 2.2
Given that Gaia typically resolves binaries at separations > 1
arcsec, is the blending scenario between Star A and TOI 837
plausible?

RESPONSE
----------
> Referring to the "Gaia" line in the bottom sub-panel of our
> Figure 6 (which came from Rizzuto et al., 2018), at 2.3
> arcseconds of separation between Star A and TOI 837, Gaia
> typically resolves binaries to brightness contrasts of ΔG ~=
> 5.0. The actual brightness difference between the two is 4.7
> G-band magnitudes. So yes, we believe that the blending
> scenario is still plausible, primarily because Star A is much
> fainter than TOI 837, placing it near the resolution threshold.

******************************************
REFEREE COMMENT
----------
Sec. 2.2
It seems another line of evidence against Star B (rho=5.4 arcsec)
as the host is the difference imaging centroid test mentioned in
Section 2.1, which they state localizes the transit to within 2
arcseconds of the target.

RESPONSE
----------
> Correct -- we have modified the wording in Sec 2.4 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Given that TOI 837 and Star A have a large contrast but similar
distances, I would expect the two stars to have a large
difference in their expected densities. Can the mean stellar
density from the transit fit be used to further argue that the
planet orbits TOI 837?

RESPONSE
----------
FIXME FIXME FIXME
> -Unfortunately, we do not feel that this argument based on the
> stellar density can be convincingly made. The reason is that
> the transit is grazing, and so our "measurement" of the stellar
> density is in fact largely prior-dominated, rather than being
> determined by the transit data. In other words: in fitting the
> transit data, we assume a stellar radius and logg, and we use
> restrictive priors inferred from the star's position on the
> cluster isochrone (see Table 5). If we were to let those priors
> be much less restrictive (say, with logg being uniform from
> 3.8-4.8, or similar), then we would not be able to break the
> classic degeneracy between the impact parameter and Rp/R*. ...
> (....or would this work regardless?)

******************************************
REFEREE COMMENT
----------
The orientation of Figure 2 is confusing. The axes are labeled
as right ascension and declination, but the lines of constant RA
and Dec are at an angle.

RESPONSE
----------
> We have updated Figure 2, and opted to drop the axis labels
> entirely. We updated the caption to emphasize the orientation
> as given by the compass.

******************************************
REFEREE COMMENT
----------
Sec. 2.3
Suggest swapping the order of Figures 3 & 4, as the high
resolution imaging is discussed before the ground-based light
curves.

RESPONSE
----------
> Done, thank you for the suggestion.

******************************************
REFEREE COMMENT
----------
Sec. 2.5.1
For the secondary spectral line injection, it is not clear
whether a synthetic spectrum was added to the raw spectrum before
deriving the LSD profile - or whether a synthetic LSD profile was
added to the true profile. It is not clear that the two
procedures would yield the same results.

RESPONSE
----------
> TODO FIXME [Asked George Zhou about this...]

******************************************
REFEREE COMMENT
----------
Sec. 3.1.3
The outer separation of the "Not SB2" constraint in the top panel
of Fig. 6 seems optimistic. Wouldn't the velocity separation of a
binary with a=100 AU be less than the broadening of 15 km/s?

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
Sec. 3.1.4
It is not clear how the range of K-P parameter space stated was
explored in detail. MCMC sampling is inefficient for multimodal
distributions, and given the sparse sampling of the RV time
series, it seems likely that multiple modes exist. Was K fit
independently over a grid of periods? Orbital inclination would
also be an important parameter to include. If models were used to
transform mass ratio limits to contrast limits this should be
explicitly stated.

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
Sec. 3.2
The following sentence is somewhat imprecise: "The relevant
populations need to be modeled at the Monte Carlo level." Monte
Carlo is a sampling method, whereas the "modeling" step lies in
the choice of probability distributions for the variables being
sampled. Also, is it the sampling that gives a more reliable
estimate of the FPP or is it the Bayesian framework, which
incorporates priors from population occurrence rates?

RESPONSE
----------
> Thank you for this point. We have revised the relevant
> sentences in Sec 3.2 to clarify that the probabilistic
> framework is the important aspect, not the sampling technique.

******************************************
REFEREE COMMENT
----------
Does the secondary eclipse non-detection apply to a specific
phase (e.g. 0.5) or across all phases?

RESPONSE
----------
> All phases -- we have revised the text in Sec 3.2 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Sec. 4.1.2
The statement that TOI 837 lies along the empirical cluster
isochrone and this limits the presence of a companion to be <50%
the brightness seems to be misstated. I believe the authors mean
that TOI 837 appears to lie below the equal-brightness binary
sequence (which sits 0.75 mag above the single star sequence).
This limits a hypothetical companion to be less than the
brightness of the target star (or less than 50% the total system
brightness).

RESPONSE
----------
> Thank you for raising this point. Our original writing was in
> error, because we meant something slightly stronger. If TOI 837
> were an equal-brightness binary system, it would be 0.75
> magnitudes above the single star sequence. However TOI 837 is
> not only not on the equal-brightness binary sequence -- it is
> not at all elevated with respect to the single-star sequence. A
> binary companion with say half the brightness of the primary
> would make the system 0.44 mags brighter than the single star
> sequence. Based on the intrinsic scatter in the HR diagram,
> this is also ruled out.  We (imprecisely) meant this second
> point, and have modified the text accordingly.

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
-It is not immediately clear that the mass-temperature-age
combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
mass-temperature relation for stars in this mass range is not the
same on the pre-main sequence as it is on the main sequence.

RESPONSE
----------
> TODO FIXME

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
-The authors are encouraged to explore the effect of adopting a
different set of evolutionary models. The Dartmouth models of
Feiden (2016), which include a magnetic field prescription, have
been shown to more accurately reproduce the parameters of
pre-main sequence stars. In the mass range of TOI 837 the effects
may not be dramatic, but are likely to be significant compared to
the quoted uncertainty on e.g. the stellar mass. I would expect
that a 10% uncertainty on the stellar mass would be more
realistic (in the sense that it would accommodate systematic
uncertainties) than the currently quoted 1% uncertainty.

RESPONSE
----------
> Thank you for this suggestion. We have amended Section 4.2.4 to include an
> application of the same isochrone technique, but using the PARSEC models
> rather than MIST. The corresponding differences between MIST and PARSEC are
> now described in the text, and are taken as "systematic uncertainties", and
> propagated through the stellar parameters in Table 4, as well as the transit
> fit.
>
> As a note, we also checked the Feiden (2016) Dartmouth models, but from what
> we could tell, no synthetic Gaia-band photometry was available. Since this
> complicates the comparison between between the Gaia photometry and the
> models, we opted for the PARSEC models.

******************************************
REFEREE COMMENT
----------
Sec. 4.3
The authors perform a joint fit of the TESS and ground-based
photometry to derive a more precise ephemeris, but fit only the
TESS data for the remaining planet parameters. If the errors on
the respective data sets are properly scaled (including jitter
terms if needed), the extra noise from the ground-based
photometry should not significantly impact the inferred
parameters when including those data. This is merely a comment,
and no extra work is necessary.

RESPONSE
----------
> Noted, with thanks.

******************************************
REFEREE COMMENT
----------
Given the planet's young age, it would be interesting to know if
the transit photometry meaningfully constrains the eccentricity
(which along with impact parameter could explain the short
duration). Was a transit fit including eccentricity performed? If
not, there are methods to infer the eccentricity from the
posteriors of a circular orbit fit (see Dawson & Johnson 2012).

RESPONSE
----------
> FIXME TODO

******************************************
REFEREE COMMENT
----------
-"The condition for a grazing transit is whether the impact
parameter b is below 1 - Rp/R*" → below should be replaced with
"above" or "greater than".

RESPONSE
----------
> Corrected, thank you.

******************************************
REFEREE COMMENT
----------
Discussion
More emphasis could be placed on the unusually large size of the
planet. Some speculative discussion on the nature of this
inflation could be warranted. Figure 11 might also be revised to
also reflect the effect of insolation (or the data plotted could
be restricted to close-in planets).

RESPONSE
----------
> Thank you for this suggestion. We have added a sub-plot in Figure 11 showing
> planet sizes and orbital periods, with the sub-100 Myr old planets
> emphasized.  We considered also including a plot with planet insolations on
> the ordinate instead of orbital periods, but the NASA Exoplanet Archive
> column for planet insolation is much less complete, presumably owing to the
> sparsity of available stellar luminosities.  We have also added some words in
> the new paragraph 2 to the effect that that the young planets could be large
> because of i) a selection effect or ii) atmospheric escape.

******************************************
REFEREE COMMENT
----------
The paper ends on a note about nodal precession. Is it simple to
compute the nodal precession timescale given some reasonable
assumptions? This might help determine how likely it is that the
effect may be observed in the near term.

RESPONSE
----------
> FIXME TODO [have asked Kassandra about this...]

******************************************
ADDITIONAL CHANGES

A few additional changes are noted in the "List of Changes"
appended at the end of the manuscript:

* Citations to Donati+2020 and Damasso+2020 are added to clarify
  that the planetary nature of the RV-detected hot Jupiters in
  Taurus has been debated.

### 2020-08-28 paper/ms.tex
[WIP] update manuscript per referee suggestions

@@
 	\caption{ {\bf Scene of \tn.}
-    Mean TESS image of \tn\ from Sector~10, with a logarithmic
-    grayscale. The yellow star is the position of \tn.  White circles
-    are resolved Gaia sources with $T<16$. Brighter stars are larger.
-    The black \texttt{X} and white \texttt{/} hatches show the
-    apertures used to measure the background and target star flux,
-    respectively. Dashed lines of constant declination and right
-    ascension are shown.  Two stars of interest are ``Star A'' and
-    ``Star B'', which were excluded as being possible
-    sources of the transits.
+    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
+    pixel cutout}, with a logarithmic grayscale\added{ showing the
+    flux in each pixel}. The yellow star is
+    the position of \tn.  White circles are resolved Gaia sources with
+    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
+    being larger}.  The black \texttt{X} and white \texttt{/} hatches
+    show the apertures used to measure the background and target star
+    flux, respectively. \replaced{Dashed lines of constant declination
+    and right ascension are shown}{The compass shows cardinal
+    directions in celestial coordinates. Dashed lines of constant
+    declination are separated by 1$'$, while those of right ascension
+    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
+    ``Star B'', which were excluded as being possible sources of the
+    transits.
 		\label{fig:scene}
@@
 \label{subsec:speckle}
+
+\begin{figure}[!t]
+	\begin{center}
+		\leavevmode
+		\includegraphics[width=.44\textwidth]{f3.pdf}
+	\end{center}
+	\vspace{-0.7cm}
+	\caption{
+		{\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
+		imaging were derived from point-source injection-recovery
+		experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
+		and is also a resolved Gaia source.  It is co-moving with \tn, and
+		its parallax and on-sky position imply that it is physically
+		separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
+		\label{fig:speckle}
+	}
+\end{figure}
 
@@
 		\leavevmode
-		\includegraphics[width=.48\textwidth]{f3.pdf}
+		\includegraphics[width=.48\textwidth]{f4.pdf}
 	\end{center}
@@
 statistically significant variation in the depth of the transits with
-aperture size.  Two lines of evidence rule out Star B as the eclipsing
-source: first, the transits were detected in the smallest apertures.
-Second, we made light curves with $2.1''$ apertures centered on Star
-B, and they did not show the transit.
+aperture size.  \added{Beyond the difference image centroiding test
+performed by the SPOC pipeline}, \replaced{Two lines of evidence}{two
+additional lines of evidence} rule out Star B as the eclipsing source:
+first, the transits were detected in the smallest apertures.  Second,
+we made light curves with $2.1''$ apertures centered on Star B, and
+they did not show the transit.
 
@@
 \label{subsec:spectra}
-
-\begin{figure}[!t]
-	\begin{center}
-		\leavevmode
-		\includegraphics[width=.44\textwidth]{f4.pdf}
-	\end{center}
-	\vspace{-0.7cm}
-	\caption{
-    {\bf Speckle-imaging of \tn.} Contrast limits from SOAR HRCam
-    imaging were derived from point-source injection-recovery
-    experiments. Star A ($\Delta T=4.7$, $2.3''$ West) is detected,
-    and is also a resolved Gaia source.  It is co-moving with \tn, and
-    its parallax and on-sky position imply that it is physically
-    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
-    \label{fig:speckle}
-	}
-\end{figure}
 
@@
 eclipses, the probability of a background star being present is much
-greater than for an arbitrary foreground star.  The relevant
-populations need to be modeled at the Monte Carlo level.  We opt to
-use \texttt{VESPA} to model the populations
+greater than for an arbitrary foreground star.  \replaced{The relevant
+populations need to be modeled at the Monte Carlo level}{A
+probabilistic framework is required to calculate the chance that a
+background eclipsing binary causes the eclipses}.  We
+\replaced{opt to use \texttt{VESPA} to model the populations}{adopt
+the Bayesian framework implemented in \texttt{VESPA}}
 \citep{morton_efficient_2012,vespa_2015}.
@@
 eclipses with a depth set at roughly twice the limits from the SPOC
-vetting report (0.1\%).  We verified that changing the secondary
-eclipse depth limit did not significantly affect the results.  We set
-the maximum aperture radius at $2''$, based on our ground-based
-photometry.  Incorporating the constraints from
-Figure~\ref{fig:fpscenario}, our nominal false positive probability
-analysis excluded EB and HEB scenarios.  This yielded an FPP of 0.21\%
-for \pn, sufficient for formal validation as a planet
-\citep{morton_efficient_2012}.  We did not incorporate our constraint
-that \tn\ is not double-lined, which rules out an additional portion
-of BEB parameter space.  Had we not acquired multicolor ground-based
-photometry, and been unable to exclude HEB scenarios, the FPP would
-have risen to 8\%.  Since the transits are achromatic
-(Figure~\ref{fig:groundphot}), particularly in Johnson-B band, we can
-rule out HEB scenarios.
+vetting report (0.1\%).  \added{This limit applies across all phases.}
+We verified that changing the secondary eclipse depth limit did not
+significantly affect the results.  We set the maximum aperture radius
+at $2''$, based on our ground-based photometry.  Incorporating the
+constraints from Figure~\ref{fig:fpscenario}, our nominal false
+positive probability analysis excluded EB and HEB scenarios.  This
+yielded an FPP of 0.21\% for \pn, sufficient for formal validation as
+a planet \citep{morton_efficient_2012}.  We did not incorporate our
+constraint that \tn\ is not double-lined, which rules out an
+additional portion of BEB parameter space.  Had we not acquired
+multicolor ground-based photometry, and been unable to exclude HEB
+scenarios, the FPP would have risen to 8\%.  Since the transits are
+achromatic (Figure~\ref{fig:groundphot}), particularly in Johnson-B
+band, we can rule out HEB scenarios.
 
@@
 Figure~\ref{fig:hr} shows a Hertzsprung-Russell diagram of \tn, the
-\cn\ cluster, and the neighborhood of spatially nearby stars.
-Stars labeled as cluster members are those reported by
+\cn\ cluster, and the neighborhood of spatially nearby stars.  Stars
+labeled as cluster members are those reported by
 \citet{cantatgaudin_gaia_2018} based on Gaia DR2 positions, proper
@@
 membership probability exceeding 10\%.  Most members appear to be
-young and coeval.  \tn\ is in its expected position relative to the
-other members along the cluster isochrone.  This photometrically
-limits the presence of binary companions in the \tn\ system to be less
-than half the brightness ($\approx0.75$ magnitudes) of the target
-star.
+young and coeval.  \replaced{\tn\ is in its expected position relative
+to the other members along the cluster isochrone.  This
+photometrically limits the presence of binary companions in the \tn\
+system to be less than half the brightness ($\approx0.75$ magnitudes)
+of the target star.}{\tn\ lies on the single-star sequence.  Any
+hypothetical companions to \tn\ must therefore be $\lesssim 50\%$ of
+its brightness; brighter companions would have made the total
+system $\gtrsim 0.44$ magnitudes brighter than the single-star
+sequence, which can be ruled out based on the photometric
+uncertainties and the intrinsic scatter in the HR diagram.}
 
@@
 Table~\ref{tab:posterior}.  The condition for a grazing transit is
-whether the impact parameter $b$ is below $1 - R_{\rm p}/R_\star$.
-The relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  The transit is either
-grazing, or nearly grazing.  From experimenting with the priors, we
-found that in the absence of a strong prior on the stellar density,
-the inherent degeneracy between the impact parameter and
-planet-to-star size ratio would have been much stronger.  In the
-absence of precise information about the star, a larger fraction of
-the posterior would therefore have been grazing.  However, our priors
-on the stellar parameters from the cluster isochrone fit break this
-degeneracy, enabling us to report two-sided limits on the
-planet-to-star size ratio.
+whether the impact parameter $b$ is \replaced{below}{above} $1 -
+R_{\rm p}/R_\star$.  The relevant posterior probabilities are shown in
+Figure~\ref{fig:subsetcorner}.  The transit is either grazing, or
+nearly grazing.  From experimenting with the priors, we found that in
+the absence of a strong prior on the stellar density, the inherent
+degeneracy between the impact parameter and planet-to-star size ratio
+would have been much stronger.  In the absence of precise information
+about the star, a larger fraction of the posterior would therefore
+have been grazing.  However, our priors on the stellar parameters from
+the cluster isochrone fit break this degeneracy, enabling us to report
+two-sided limits on the planet-to-star size ratio.
 
@@
 
+\added{The authors are grateful to the anonymous referee for their
+constructive comments and suggestions.}
+%
 L.G.B. and J.H. acknowledge support by the TESS GI Program, program

### 2020-08-28 paper/collect.sh

@@ -9,9 +9,9 @@ cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_phaseplot.pdf
 
 cp ${pdir}scene.pdf f2.pdf
 
-cp ${rdir}TOI_837_allindivtransit_phot_results/20200711/TOI_837_*_grounddepth.pdf f3.pdf
+cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f3.pdf
 
-cp /Users/luke/Dropbox/proj/timmy/data/speckle/TIC460205581I-cz20190714.pdf f4.pdf
+cp ${rdir}TOI_837_allindivtransit_phot_results/20200711/TOI_837_*_grounddepth.pdf f4.pdf
 
 cp ${rdir}radvel_fitting/20200624_simple_planet/TOI837_rvlimit_multipanel.pdf f5.pdf
 
@@ -27,6 +27,8 @@ cp ${rdir}lithium/lithium.pdf f9b.pdf
 
 cp ${rdir}TOI_837_tessindivtransit_phot_results/20200711/TOI_837_*_subsetcorner.pdf f10.pdf
 
-cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200729_toi837.pdf f11.pdf
+cp ${rdir}rp_vs_age_scatter/rp_vs_age_scatter_20200827_toi837.pdf f11a.pdf
+
+cp ${rdir}rp_vs_period_scatter/rp_vs_period_scatter_20200827_toi837_nolegend.pdf f11b.pdf
 
 # cp ${pdir}toi_837_sed.png f6.png

### 2020-08-28 timmy/plotting.py

@@ -1097,6 +1097,8 @@ def plot_scene(c_obj, img_wcs, img, outpath, Tmag_cutoff=17, showcolorbar=0,
 
         lon.set_ticks_visible(False)
         lat.set_ticks_visible(False)
+        lon.set_ticklabel_visible(False)
+        lat.set_ticklabel_visible(False)
 
         invert_x, invert_y = False, False
         if shiftra_x - target_x > 0:

### 2020-09-01 paper/ms.tex
update manuscript

@@
     Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
-    pixel cutout}, with a logarithmic grayscale\added{ showing the
+    pixel cutout}, with a logarithmic grayscale\added{ indicating the
     flux in each pixel}. The yellow star is
@@
 either associated or in chance alignment with TOI 837. No such set of
-lines was found. To set limits on the contributions of a close-by
-star to the observed spectrum, we injected a second set of lines to
-the mean least-squares deconvolution profile derived from the CHIRON
+lines was found. To set limits on the contributions of a close-by star
+to the observed spectrum, we injected a \replaced{second set of lines
+to the mean least-squares deconvolution profile}{secondary signal into
+the mean least-squares deconvolution profile} derived from the CHIRON
 observations.  The injection spanned 10,000 different combinations of
@@
 the target spectrum.
+\added{
+  We verified these results by injecting secondary lines directly into
+  the spectrum and then deriving its LSD broadening profile as we
+  would for a normal observation.  The results were nearly identical,
+  save for greater computational cost.
+}
 
@@
 
+\explain{NOTE: the description of why we avoided Method 1 has been moved
+from a paragraph at the end of this section, to the paragraph below.}
+
 In ``Method 1'', we measured spectroscopic parameters from each of the
@@
 with the spectroscopic $\log g$ also yields a stellar mass.
-
-In ``Method 2'', we simply used the observed location of \tn\ in the
-HR diagram and interpolated against the 40$\,$Myr isochrone.  This
-method leverages the relative location of \tn\ within the narrow \cn\
-isochrone to derive precise, theoretically self-consistent constraints
-on all of the stellar parameters.  Although this approach would fail
-for a low-mass star, \tn\ is above the stellar masses where the Gaia
-photometry and isochrone models begin to diverge.
-
+\added{The stellar mass however seemed to be high relative to the
+observed CHIRON effective temperature ($1.21 M_\odot$ to $5946\,{\rm
+K}$, with relative uncertainties of a few percent on each). We
+therefore explored a second method, and ultimately adopted
+it because its systematic uncertainties were easier to quantify.}
+
+In ``Method 2'', we \deleted{simply} used the observed location of
+\tn\ in the HR diagram and interpolated against the 40$\,$Myr
+isochrone.  This method leverages the relative location of \tn\ within
+the \deleted{narrow} \cn\ isochrone to derive precise, theoretically
+self-consistent constraints on all of the stellar parameters.
+Although this approach would fail for a low-mass star, \tn\ is above
+the stellar masses where the Gaia photometry and isochrone models
+begin to diverge.
+\added{
+  The statistical uncertainties yielded by this approach are of order
+  1\% for the stellar mass and radius.  To quantify the systematic
+  uncertainties, we compared the parameters derived from the MIST
+  isochrones with those from the
+  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
+  \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
+  The PARSEC isochrones gave a stellar mass 5\% lower, effective
+  temperature 3\% lower, logarithmic surface gravity 1\% lower, and
+  radius 8\% lower than the MIST isochrones.  For the sake of
+  self-consistency, in Table~\ref{tab:starparams} and the ensuing
+  analysis we adopted the stellar
+  parameters from MIST.  The reported uncertainties are the quadrature
+  sum of the statistical and systematic components.
+}
+
+\deleted{
 Method 1 yielded a stellar mass that seemed to be high relative to the
@@
 Method 2, and report them in Table~\ref{tab:starparams}.
+}
 
@@
 
-We fitted the model using \texttt{PyMC3}
+We fitted the model\added{s} using \texttt{PyMC3}
 \citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the exoplanet
@@
 understanding of the planet's \replaced{contraction and
-photoevaporation}{composition and therefore future atmospheric
+photoevaporation}{composition and future atmospheric
 evolution}.  If an RV campaign were timed to coincide with TESS
@@
 during the TESS mission extension may also help in understanding the
-system \citep{bouma_extend_2017,huang_expected_2018}.  Any
+system \citep{bouma_extend_2017,huang_expected_2018}.  \deleted{Any
 misalignment between the star's spin axis and the planet's orbit
@@
 observed, this could be a spectroscopy-free method for confirming the
-planet.
+planet.}
+\added{
+  In particular, additional photometry will likely enable more
+  detailed exploration of whether the orbit of \tn\ is eccentric, and
+  also whether the system could host additional transiting planets.
+}
 
@@
 
-\added{The authors are grateful to the anonymous referee for their
-constructive comments and suggestions.}
+\added{The authors thank K.~Anderson for fruitful discussions, and are
+grateful to the anonymous referee for their constructive comments and
+suggestions.}
 %

### 2020-09-01 drivers/oneoff_drivers/starparam_uncert.py
update stellar parameters for systematic unc

@@ -1,0 +1,44 @@
+# PARSEC:
+# Mstar = 1.06 Msun, +/- 0.03
+# Teff = 5890, +/- 50
+# logg = 4.515, +/- 0.020
+# Rstar = 0.940 +/- 0.025 Rsun
+# rhostar = 1.80 +/- 0.05 g/cc
+# 
+# MIST:
+# Mstar = 1.118 +/- 0.011
+# Teff = 6047 +/- 40
+# logg = 4.467 +/- 0.010
+# Rstar = 1.022 +/- 0.015
+# rhostar = (post-transit-fit...) 1.47 +/- 0.04 g/cc
+
+import numpy as np
+
+d_parsec = {
+    'mstar': (1.06, 0.03),
+    'teff': (5890, 50),
+    'logg': (4.515, 0.02),
+    'rstar': (0.940, 0.025)
+}
+
+d_mist = {
+    'mstar': (1.118, 0.011),
+    'teff': (6047, 40),
+    'logg': (4.467, 0.010),
+    'rstar': (1.022, 0.015)
+}
+
+params = ['mstar', 'teff', 'logg', 'rstar']
+
+for p in params:
+
+    unc_sys = (d_mist[p][0] - d_parsec[p][0])
+    unc_stat = d_mist[p][1]
+
+    val = np.average([d_mist[p][0], d_parsec[p][0]])
+    unc = np.sqrt(unc_sys**2 + unc_stat**2)
+
+    print(f'AVERAGE {p}: {val} +/- {unc}')
+    print(f'MIST {p}: {d_mist[p][0]} +/- {unc}')
+
+

### 2020-09-01 drivers/plot_hr.py

@@ -5,7 +5,11 @@ from timmy.paths import RESULTSDIR
 PLOTDIR = os.path.join(RESULTSDIR, 'cluster_membership')
 
 for color0 in ['phot_bp_mean_mag', 'phot_g_mean_mag']:
-    tp.plot_hr(PLOTDIR, isochrone=1, color0=color0)
+
+    tp.plot_hr(PLOTDIR, isochrone='parsec', color0=color0)
+    tp.plot_hr(PLOTDIR, isochrone='mist', color0=color0)
     tp.plot_hr(PLOTDIR, isochrone=0, color0=color0)
-    tp.plot_hr(PLOTDIR, isochrone=1, do_cmd=1, color0=color0)
+
+    tp.plot_hr(PLOTDIR, isochrone='parsec', do_cmd=1, color0=color0)
+    tp.plot_hr(PLOTDIR, isochrone='mist', do_cmd=1, color0=color0)
     tp.plot_hr(PLOTDIR, isochrone=0, do_cmd=1, color0=color0)

### 2020-09-01 timmy/plotting.py

@@ -1172,18 +1172,27 @@ def plot_hr(outdir, isochrone=None, do_cmd=0, color0='phot_bp_mean_mag'):
      group_in_k13, group_in_cg18, group_in_kc19, group_in_k18
     ) = info
 
-    if isochrone:
-        from timmy.read_mist_model import ISOCMD
+    if isochrone in ['mist', 'parsec']:
 
-        isocmdpath = os.path.join(DATADIR, 'cluster',
-                                  'MIST_isochrones_age7pt60206_Av0pt217_FeH0',
-                                  'MIST_iso_5f04eb2b54f51.iso.cmd')
+        if isochrone == 'mist':
+            from timmy.read_mist_model import ISOCMD
 
-        # relevant params: star_mass log_g log_L log_Teff Gaia_RP_DR2Rev
-        # Gaia_BP_DR2Rev Gaia_G_DR2Rev
-        isocmd = ISOCMD(isocmdpath)
-        # 10, 20, 30, 40 Myr.
-        assert len(isocmd.isocmds) == 4
+            isocmdpath = os.path.join(DATADIR, 'cluster',
+                                      'MIST_isochrones_age7pt60206_Av0pt217_FeH0',
+                                      'MIST_iso_5f04eb2b54f51.iso.cmd')
+
+            # relevant params: star_mass log_g log_L log_Teff Gaia_RP_DR2Rev
+            # Gaia_BP_DR2Rev Gaia_G_DR2Rev
+            isocmd = ISOCMD(isocmdpath)
+            # 10, 20, 30, 40 Myr.
+            assert len(isocmd.isocmds) == 4
+
+        elif isochrone == 'parsec':
+
+            isopath = os.path.join(DATADIR, 'cluster', 'PARSEC_isochrones',
+                                   'output799447099984.dat')
+
+            iso_df = pd.read_csv(isopath, delim_whitespace=True)
 
 
     ##########
@@ -1206,7 +1215,16 @@ def plot_hr(outdir, isochrone=None, do_cmd=0, color0='phot_bp_mean_mag'):
 
     if not do_cmd:
         yval = group_df_dr2['phot_g_mean_mag'] + 5*np.log10(group_df_dr2['parallax']/1e3) + 5
-        mediancorr = np.nanmedian(5*np.log10(group_df_dr2['parallax']/1e3)) + 5 + 5.9
+        if isochrone == 'mist':
+            mediancorr = (
[…]

### 2020-09-01 paper_review/response_20200826.txt
update referee response

@@
 report, alongside our responses. A list of changes is appended to
-the manuscript using the trackchanges AASTeX macros.
+the manuscript using the trackchanges AASTeX macros. A figure
+supporting the verification of our SB2 injection-recovery test
+has also been uploaded for inspection.
 
@@
 ----------
-It appears that TOI 837 b was previously noted as a candidate planet and IC
-2602 member in Nardiello et al. 2020
-(https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.4924N/abstract).  If the
-authors were unaware, it is still worth mentioning this in the text.
+It appears that TOI 837 b was previously noted as a candidate
+planet and IC 2602 member in Nardiello et al. 2020
+(https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.4924N/abstract).
+If the authors were unaware, it is still worth mentioning this in
+the text.
 
@@
 > CCDs. Since few people know what it is, and it will therefore
-> confuse the reader, we have omitted it from the manuscript.
+> confuse rather than clarify, we have omitted it from the
+> manuscript.
 
@@
 > We did perform a by-eye search for additional transits in the
-> light curve, and did not find any compelling events. The
+> light curve, and we did not find any compelling events. The
 > logical next step -- quantifying our sensitivity through
 > injection-recovery simulations -- would be an interesting
-> exercise.  However, for it to be valid, care would need to be
-> taken to marginalize out dependence on the detrending method
-> (e.g., David et al 2019 and 2020's experience which led to the
+> exercise.  For it to be valid, care would need to be taken to
+> marginalize out dependence on the detrending method (e.g.,
+> David et al 2019 and 2020's experience which led to the
 > four-planet V1298 Tau system).  Given the required level of
-> work, we feel this exercise to be outside the scope of the
-> present work.
+> effort, we feel this exercise to be outside the scope of the
+> present analysis.
 
@@
 ----------
-FIXME FIXME FIXME
+FIXME FIXME FIXME ... maybe it can...
+
 > -Unfortunately, we do not feel that this argument based on the
@@
 ----------
-> TODO FIXME [Asked George Zhou about this...]
+> We have updated the manuscript to clarify that the SB2
+> grid-search injection and recovery exercise was conducted with
+> the secondary signal injected into the LSD profiles, not the
+> spectra. 
+> 
+> To test the validity of this technique, we injected a second
+> set of lines to the original spectra, and compared the
+> resulting derived LSD profiles. To inject a second set of lines
+> to the raw spectrum, we made use of a high SNR CHIRON spectrum
+> of a G0 RV standard star, scaled its flux, and blended it with
+> the averaged observed spectrum of TOI-837.  We then performed
+> the LSD routine on the blended spectrum to derive its LSD
+> broadening profile as we would for a normal observation.
+> 
+> The attached figure shows the resulting LSD profiles from our
+> injection test. The left column (black) shows the LSD profiles
+> when the secondary signals were injected directly into the LSD
+> profile. The right column (red) shows the results of our
+> blended spectrum analysis. There is minimal difference between
+> the two injection techniques.
 
@@
 Sec. 4.2.4
--It is not immediately clear that the mass-temperature-age
+It is not immediately clear that the mass-temperature-age
 combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
@@
 ----------
-> TODO FIXME
+> Looking at the MIST isochrones, it seems that a
+> solar-metallicity, 1.1Msun star reaches the ZAMS around
+> log(age) of 7.5, or ~32 Myr. So, TOI 837 seems likely to be
+> roughly at the ZAMS, rather than particularly early in its
+> pre-main sequence contraction.
+>
+> Regardless, we have modified the wording here to reflect that
+> our preference for "Method 2" is linked to our ability to
+> more easily quantify its uncertainties (statistical and
+> systematic -- see below).
 
@@
 Sec. 4.2.4
--The authors are encouraged to explore the effect of adopting a
+The authors are encouraged to explore the effect of adopting a
 different set of evolutionary models. The Dartmouth models of
@@
 ----------
-> Thank you for this suggestion. We have added a sub-plot in Figure 11 showing
-> planet sizes and orbital periods, with the sub-100 Myr old planets
-> emphasized.  We considered also including a plot with planet insolations on
-> the ordinate instead of orbital periods, but the NASA Exoplanet Archive
-> column for planet insolation is much less complete, presumably owing to the
-> sparsity of available stellar luminosities.  We have also added some words in
-> the new paragraph 2 to the effect that that the young planets could be large
-> because of i) a selection effect or ii) atmospheric escape.
+> Thank you for this suggestion. We have added a sub-plot in
+> Figure 11 showing planet sizes and orbital periods, with the
+> sub-100 Myr old planets emphasized.  We considered also
+> including a plot with planet insolations on the ordinate
+> instead of orbital periods, but the NASA Exoplanet Archive
+> column for planet insolation is much less complete, presumably
+> owing to the sparsity of available stellar luminosities.  We
+> have also added some words in the discussion to the effect that
+> that the young planets could be large because of i) a selection
+> effect or ii) atmospheric escape.
 
@@
 ----------
-> FIXME TODO [have asked Kassandra about this...]
+> Our thanks for this comment, which prompted us to calculate the
+> precession frequency of the orbital axis due to the stellar
+> oblateness using equations from Anderson+2018 and Lai+2018. We
+> found that given the observed parameters of the system and an
+> assumed stellar Love number (k2) equal to that of the Sun, the
+> precession period would be 45,000 years. To complete say 1% of
+> a precession cycle, which might roughly be what is needed to
+> observe noticeable changes, we would need to wait ~450 years.
+>
+> We have correspondingly modified the last sentence to say
+> something more generic, but actually true: more photometry
+> should improve our ability to constrain the orbital
+> eccentricity, and will let us search for additional transiting
+> planets.
 

### 2020-09-01 paper_review/response_20200826.txt
update manuscript and response
shifting preference to be TESS+ground, and explaining why.

@@
 ----------
-FIXME FIXME FIXME ... maybe it can...
-
-> -Unfortunately, we do not feel that this argument based on the
-> stellar density can be convincingly made. The reason is that
-> the transit is grazing, and so our "measurement" of the stellar
-> density is in fact largely prior-dominated, rather than being
-> determined by the transit data. In other words: in fitting the
-> transit data, we assume a stellar radius and logg, and we use
-> restrictive priors inferred from the star's position on the
-> cluster isochrone (see Table 5). If we were to let those priors
-> be much less restrictive (say, with logg being uniform from
-> 3.8-4.8, or similar), then we would not be able to break the
-> classic degeneracy between the impact parameter and Rp/R*. ...
-> (....or would this work regardless?)
+> Our thanks for pointing this out. We have added a paragraph at
+> the end of Section 2.4.1 to this effect.
 
@@
 > Regardless, we have modified the wording here to reflect that
-> our preference for "Method 2" is linked to our ability to
-> more easily quantify its uncertainties (statistical and
-> systematic -- see below).
+> our preference for the stellar parameters from "Method 2" is
+> linked to our ability to more easily quantify its uncertainties
+> (statistical and systematic -- see below).
 
@@
 ----------
-> Thank you for this suggestion. We have amended Section 4.2.4 to include an
-> application of the same isochrone technique, but using the PARSEC models
-> rather than MIST. The corresponding differences between MIST and PARSEC are
-> now described in the text, and are taken as "systematic uncertainties", and
-> propagated through the stellar parameters in Table 4, as well as the transit
-> fit.
+> Thank you for this suggestion, which we agree is important. We
+> amended Section 4.2.4 to explore the use of the PARSEC models
+> in addition to the MIST models. (We checked the Feiden 2016
+> Dartmouth models, but no synthetic Gaia-band photometry was
+> available, which complicates the comparison between between the
+> Gaia photometry and the models.) The differences between MIST
+> and PARSEC are now described in the text, and are used to
+> estimate systematic uncertainties on the stellar parameters.
+> These uncertainties are now reported in Table 4, and they are
+> also propagated through the transit fits (Table 5; Figure 1;
+> Figure 4; Figure 10). 
 >
-> As a note, we also checked the Feiden (2016) Dartmouth models, but from what
-> we could tell, no synthetic Gaia-band photometry was available. Since this
-> complicates the comparison between between the Gaia photometry and the
-> models, we opted for the PARSEC models.
+> Compared to the initially submitted TESS-only transit fit, the
+> wider priors on R* and logg* exacerbated the impact parameter
+> vs Rp/R* degeneracy.  With the wider stellar density prior,
+> impact parameters much greater than 1 became statistically
+> allowed (though not favored), if the planet-to-star radius
+> ratio were to be very large. Our ability to break the
+> degeneracy was broken! Given only the TESS data + the
+> isochronal stellar parameter priors with systematic
+> uncertainties included, only a one-sided limit on the planet
+> radius can be derived.
+>
+> One way to "fix" this issue would have been to impose a prior
+> constraint that Rp<3Rjup, based on our mass upper limit of
+> ~2Mjup and the fact that all known planetary and stellar
+> objects follow mass-radius relations that would require the
+> planet to be smaller than 3Rjup. However, this approach would
+> be somewhat atypical, and even when doing it, we found with our
+> updated stellar uncertainties that the TESS-only model (with Rp
+> limit prior) gave:
+>
+>   TESS-only, Rp<3Rjup assumed, systematic star uncertainties:
+>     r_planet [Rjup]: 0.836 +0.208 -0.121
+>     b: 0.957 +0.027 -0.017
+> 
+> where we quote median, 86th, and 14th percentiles. Conversely,
+> the fit to the combined TESS+ground data yielded a planet
+> radius more precise by a factor of ~2x: 
+>
+>   TESS+ground, broad Rp/R* prior, systematic star uncertainties:
+>     r_planet [Rjup]: 0.768 +0.091 -0.072
+>     b: 0.936 +0.013 -0.010
+>
+> Given the increase from 5 to 12 transits, this is presumably
+> because the transit depth is measured more precisely. (Both
+> sets of chains are fully converged, with Rhat-1 < 1e-4).
+> Despite our initial reservations about using the ground-based
+> data for the planet parameters, the combined data do yield a more
+> precise fit, and also seem to do a better job at breaking the Rp/R*
+> vs b degeneracy. These two points persuaded us to adopt it as our
+> preferred solution.  Nonetheless, this decision is one of
+> preference, and not modelling necessity. We have amended Section 4.3
+> at some length to present the points made in this response, and to
+> emphasize the key results from both approaches.  Consequent changes
+> include:
+>
+> * Bottom panel of Figure 1 now shows the TESS+ground data
+>   phase-folded, instead of TESS-only. Caption was updated
+>   accordingly.
+>
+> * Figure 10 is now the posterior from TESS+ground, instead of
+>   TESS-only.
+>
+> * Figure 11 was updated for the new planet radius.  
+>
+> * The planet radius was updated in the abstract and throughout
+>   the manuscript.
 
@@
 ----------
-> Noted, with thanks.
+> Noted with thanks. As described above, we have amended our preferred
+> solution to the TESS+ground solution, rather than the TESS-only
+> solution.
 
@@
 ----------
-> FIXME TODO
+> While we agree that the possibility of a non-circular orbit would be
+> interesting, we do not expect that given the present data we can
+> make credible statements about potential non-zero eccentricities. We
+> have updated the last paragraph of Sec 4.3 to justify this
+> assumption of a circular orbit, and have amended the conclusion to
+> mention this as a possible area for future work.
 
@@
 > precession frequency of the orbital axis due to the stellar
-> oblateness using equations from Anderson+2018 and Lai+2018. We
-> found that given the observed parameters of the system and an
-> assumed stellar Love number (k2) equal to that of the Sun, the
-> precession period would be 45,000 years. To complete say 1% of
-> a precession cycle, which might roughly be what is needed to
-> observe noticeable changes, we would need to wait ~450 years.
+> oblateness using equations from Anderson+2018 and Lai+2018. We found
+> that given the observed parameters of the system and an assumed
+> stellar Love number (k2) equal to that of the Sun, the precession
+> period would be 45,000 years. To complete say 1% of a precession
+> cycle, which might roughly be what is needed to observe noticeable
+> changes, we would need to wait ~450 years.
 >
-> We have correspondingly modified the last sentence to say
-> something more generic, but actually true: more photometry
-> should improve our ability to constrain the orbital
-> eccentricity, and will let us search for additional transiting
-> planets.
+> We have correspondingly amended the last sentence to omit the point
+> on nodal precession, in favor of the point that more photometry
+> should improve our ability to constrain the orbital eccentricity,
+> and will also let us search for additional transiting planets.
 
@@
 
-A few additional changes are noted in the "List of Changes"
-appended at the end of the manuscript:
+A few additional changes, most of which are noted in the "List of
+Changes" appended at the end of the manuscript:
+
+* Added citation to Bonomo+2017 in the introduction.
 
@@
   Taurus has been debated.
+
+* Last paragraph of Sec 2.1: added transition sentence.
+
+* Acknowledgements to K. Anderson, and to the referee, have been
+  added.
+
+* Table 5 has new rows for the ground-based transit nuisance
+  parameters, and the posterior values are updated for the propagation
+  of stellar parameter uncertainties.

### 2020-09-01 paper/ms.tex
update manuscript and response
shifting preference to be TESS+ground, and explaining why.

@@
 
-%\documentclass[12pt,twocolumn,tighten]{aastex63}
-\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
+\documentclass[12pt,twocolumn,tighten]{aastex63}
+%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
 \usepackage{amsmath,amstext,amssymb}
@@
   period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
-  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
+  ($R_{\rm p} = 0.77^{+0.09}_{-0.07} \,R_{\rm Jup}$).  From radial
   velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
@@
 dispersal \citep{pollack_formation_1996}.  While rocky planets may
-form within only a few million years
-\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
-over the next 10--100 million years through giant impacts \citep[{\it
+form within only a few million years \citep{dauphas_hf-w-th_2011},
+they can also undergo significant growth over the next 10--100 million
+years through giant impacts \citep[{\it
 e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
@@
 planets that migrated early, their orbits should circularize within
-100 million years \citep{zahn_tidal_1977}.
+100 million years \citep{zahn_tidal_1977,bonomo_gaps_2017}.
 
@@
 a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1$\,$\replaced{Gyr}{gigayear}, a number of direct and indirect methods are
+younger than say 1 \replaced{Gyr}{gigayear}, a number of direct and indirect methods are
 available \citep{soderblom_ages_2010}.  The traditional approach is to
@@
 	\caption{
-    {\bf TESS light curve of \tn.}
+    {\bf Light curves of \tn.}
     {\it Top}:
-    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
+    TESS \texttt{PDCSAP} median-subtracted relative flux at 2-minute
     sampling in units of parts-per-thousand ($\times 10^{-3}$).
@@
     observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
-    transits.  Gray lines are the best-fit transit model, which
-    includes a local quadratic trend in each window. Gray points are
-    2-minute \texttt{PDCSAP} flux measurements, black points are
-    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
-    transit.  Gray points are 2-minute measurements with the local
-    spot-induced variation removed.  Binning at 6-minute intervals
-    yields the black points.  The black error-bar shows the median
-    uncertainty for the black points.  The gray line shows the
-    best-fit model to the TESS data. 
-		\label{fig:tessphot}
+    TESS transits.  Gray lines are the best-fit model to the TESS
+    \added{and ground-based data}, which includes
+    a local quadratic trend for each transit. Gray points are 2-minute
+    \texttt{PDCSAP} flux measurements, black points are binned to
+    15-minute intervals.  {\it Bottom}: Phase-folded TESS and
+    ground-based transits. \added{Section~\ref{subsec:groundphot} presents
+    the ground-based data.} Gray points are flux
+    measurements with the local spot-induced variation removed.  A
+    weighted binning at 6-minute intervals yields the black points.
+    The black error-bar shows the median uncertainty for the black
+    points.  The gray line is the best-fit model for the entire
+    dataset.
+		\label{fig:thephot}
 	}
@@
 
-Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
-induced by starspots coming into and out of view has a peak-to-peak
-amplitude of about 2.3\%, and a period of about 3 days.  The dips are
-suggestive of a grazing transiting planet, recurring roughly every 8
-days with a depth of about 0.4\%.  A few flares are also visible.  A
-phase-folded view of the TESS transits with starspot variability
-removed is also shown in Figure~\ref{fig:tessphot}. Our fitting procedure
-for the models in these plots is described in
-Section~\ref{subsec:planet}.
+\added{The top panel of} Figure~\ref{fig:thephot} shows the
+\added{TESS} data.  The dominant modulation induced by starspots
+coming into and out of view has a peak-to-peak amplitude of about
+2.3\%, and a period of about 3 days.  The dips are suggestive of a
+grazing transiting planet, recurring roughly every 8 days with a depth
+of about 0.4\%.  A few flares are also visible.  A phase-folded view
+of the TESS transits \deleted{with starspot variability
+removed}\added{combined with ground-based follow-up photometry} is
+shown in \added{the bottom panel of }Figure~\ref{fig:thephot}.
+\added{The ground-based data }and our procedure for fitting the
+models \deleted{in these plots is described in }\added{are discussed
+in Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
+respectively}.  \added{First though, some prerequisite context on the
+stellar neighborhood of \tn\ is needed.}
 
@@
 	\end{center}
-	\vspace{-0.7cm}
+	\vspace{-0.6cm}
 	\caption{ {\bf Scene of \tn.}
@@
 
+\added{
+An additional line of evidence for Star A not being the transit host
+was also noted by the referee.  The $G$-band magnitude and the
+parallax suggest that Star A is an M dwarf. As a probable cluster
+member, it would have $Bp - Rp \approx 2.8$ (see
+Section~\ref{subsec:hr}), which corresponds roughly to a mass in the
+range of 0.15-0.45$\,M_\odot$, or densities roughly in the range of
+2-3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
+\citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
+These densities are inconsistent with those inferred from the transit
+fits in Section~\ref{subsec:planet}.
+}
+
 \subsubsection{ASTEP400}
@@
 		\leavevmode
-		\includegraphics[width=.47\textwidth]{f5.pdf}
+		\includegraphics[width=.48\textwidth]{f5.pdf}
 	\end{center}
@@
 the target spectrum.
-\added{
-  We verified these results by injecting secondary lines directly into
-  the spectrum and then deriving its LSD broadening profile as we
+\added{We verified these results by injecting secondary lines directly
+into the spectrum and then deriving its LSD broadening profile as we
 would for a normal observation.  The results were nearly identical,
-  save for greater computational cost.
-}
+save for greater computational cost.}
 
@@
 Assuming an eclipse has been localized to the target star, potential
-false positive scenarios include eclipses of a background binary
-(BEB), eclipses of a hierarchical system bound to the primary star
-(HEB), and the possibility that the eclipses are caused by a
-stellar companion, rather than a planetary one (EB).
+false positive scenarios include eclipses of a\added{n unresolved}
+background binary (BEB), eclipses of a hierarchical system bound to
+the primary star (HEB), and the possibility that the eclipses are
+caused by a stellar companion, rather than a planetary one (EB).
 
@@
 \tn\ in the HR diagram and interpolated against the 40$\,$Myr
-isochrone.  This method leverages the relative location of \tn\ within
-the \deleted{narrow} \cn\ isochrone to derive precise, theoretically
-self-consistent constraints on all of the stellar parameters.
-Although this approach would fail for a low-mass star, \tn\ is above
-the stellar masses where the Gaia photometry and isochrone models
-begin to diverge.
+\added{MIST} isochrone.  This method leverages the relative location
+of \tn\ within the \deleted{narrow} \cn\ isochrone to derive precise,
+theoretically self-consistent constraints on all of the stellar
+parameters.  Although this approach would fail for a low-mass star,
+\tn\ is above the stellar masses where the Gaia photometry and
+isochrone models begin to diverge.
 \added{
@@
   analysis we adopted the stellar
-  parameters from MIST.  The reported uncertainties are the quadrature
-  sum of the statistical and systematic components.
+  parameter values from MIST.  We took the uncertainties to be the
+  quadrature sum of the statistical and systematic components.
 }
@@
     and 4-$\sigma$ confidence.  The planet-to-star size ratio
-    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
-    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
-    This plot was made using \texttt{corner} \citep{corner_2016}.
+    corresponds to a planet size between \replaced{$0.68\,R_{\rm Jup}$
+    and $0.97\,R_{\rm Jup}$}{$0.62\,R_{\rm Jup}$ and $0.95\,R_{\rm
+    Jup}$} (3$^{\rm rd}$--97$^{\rm th}$ percentile).  This plot was
+    made using \texttt{corner} \citep{corner_2016}.
 		\label{fig:subsetcorner}
@@
 
-We also fitted the available time-series photometry of \pn\ using two
-different approaches.  To derive the most precise possible ephemeris,
-we fitted the ground and space-based transits simultaneously.  To
-derive the physical parameters of the planet, we fitted the TESS data
-alone, due to our better understanding of the underlying systematic
-trends and the higher precision.
-
-For the TESS \texttt{PDCSAP} light curve, we first eliminated points
-that had quality flags corresponding to any of bits $\{3, 4, 6, 8, 11,
-12\}$.  This excluded cadences affected by coarse spacecraft pointing,
-reaction wheel desaturation events, manual flags, cosmic ray hits, and
-straylight from the Earth or Moon being present.  Inspecting the data,
-we also manually excluded the two flares shown in
-Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
-of $\pm 7\,{\rm hr}$ centered on each transit.
+We also considered two different approaches for fitting the available
+time-series photometry of \pn.  \replaced{To derive the most precise
+possible ephemeris,}{In the first approach,} we fitted the ground and
+space-based transits simultaneously.  \replaced{To derive the physical
+parameters of the planet}{In the second}, we fitted the TESS data
+alone\deleted{, due to our better understanding of the underlying
+systematic trends and the higher precision}.
+
+To clean the TESS \texttt{PDCSAP} light curve, we first eliminated
+points that had quality flags corresponding to any of bits $\{3, 4, 6,
+8, 11, 12\}$.  This excluded cadences affected by coarse spacecraft
+pointing, reaction wheel desaturation events, manual flags, cosmic ray
+hits, and straylight from the Earth or Moon being present.  Inspecting
+the data, we also manually excluded the two flares shown in
+Figure~\ref{fig:thephot}.  We then trimmed the TESS data to windows of
+$\pm 7\,{\rm hr}$ centered on each transit.
 
@@
 allowed within each window.  Select parameters and priors are listed
-in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
-fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
-u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
-p}/R_\star)\}$.  There were also three free trend parameters for each
-transit window to account for the local rotational variability.  In
-the TESS-only model this yielded 23 free parameters, of which 8 were
-physically relevant and 15 were nuisance parameters.  In the combined
-TESS and ground-based model, there were an additional 7 transits, and
-therefore an additional 21 nuisance parameters for a total of 44 free
+in Table~\ref{tab:posterior}, for the \replaced{TESS-only model}{joint
+model of the TESS and ground-based data}.  In brief, we fitted for the
+shared stellar parameters $\{\log g, R_\star, u_0, u_1\}$, and the
+shared planetary parameters $\{t_0, P, b, \log(R_{\rm p}/R_\star)\}$.
+There were also three free trend parameters for each transit window to
+account for the local rotational variability.  In the TESS-only model
+this yielded 23 free parameters, of which 8 were physically relevant
+and 15 were nuisance parameters.  In the combined TESS and
+ground-based model, there were an additional 7 transits, and therefore
+an additional 21 nuisance parameters for a total of 44 free
 parameters.
@@
 and radial velocities because the RVs on their own did not show
-evidence for a planetary signal.  Our preference for using only the
-TESS data to derive the transit parameters was in our view justified
-by the systematic uncertainties inherent to ground-based light curve
-production, particularly in comparison star selection.  Our assumption
-of a constant radius across all bandpasses was tested by independently
-fitting each ground-based transit while letting the planetary radius
-float (Section~\ref{subsec:colorphot}). The transit depths did not
-significantly change between different bandpasses.
-Our assumption in the false-positive probability calculation
+evidence for a planetary signal.  \deleted{Our preference for using
+only the TESS data to derive the transit parameters was in our view
+justified by the systematic uncertainties inherent to ground-based
+light curve production, particularly in comparison star selection.}
+Our assumption of a constant radius across all bandpasses was tested
+by independently fitting each ground-based transit while letting the
+planetary radius float (Section~\ref{subsec:colorphot}). The transit
+depths did not significantly change between different bandpasses.  Our
+assumption in the false-positive probability calculation
 (Section~\ref{subsec:fpp}) of no odd-even variations was tested by
-independently fitting all odd and all even transits separately.
-The resulting best-fit depths were consistent within 1-$\sigma$.
+independently fitting all odd and all even transits separately.  The
+resulting best-fit depths were consistent within 1-$\sigma$.
 % odd:  log(r/rs) = -2.601528 +0.048317 -0.015647
@@
 
-The posteriors from fitting the TESS data alone are given in
-Table~\ref{tab:posterior}.  The condition for a grazing transit is
-whether the impact parameter $b$ is \replaced{below}{above} $1 -
-R_{\rm p}/R_\star$.  The relevant posterior probabilities are shown in
-Figure~\ref{fig:subsetcorner}.  The transit is either grazing, or
-nearly grazing.  From experimenting with the priors, we found that in
-the absence of a strong prior on the stellar density, the inherent
+\explain{The paragraphs below were heavily modified and/or newly added
+after submission, given the updated systematic uncertainties on the
+stellar parameters, and our revision in favor of the TESS+ground
+model. }
+
+The posteriors from fitting the TESS \added{and ground-based }data
+\deleted{alone }are given in Table~\ref{tab:posterior}.  The condition
+for a grazing transit is whether the impact parameter $b$ is
+\replaced{below}{above} $1 - R_{\rm p}/R_\star$.  The relevant
+posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
+The transit is either grazing, or nearly grazing.
+\added{The planet radius and impact parameter based on the
+TESS and ground-based data are as follows.
+\begin{align}
+  R_{\rm p} &= 0.768^{+0.091}_{-0.072} R_{\rm Jup}, \\
+  b &= 0.936^{+0.013}_{-0.010},
+\end{align}
+where we quote the median, 86$^{\rm th}$, and 14$^{\rm th}$
+percentiles of the marginalized posteriors.
+}
+\deleted{From experimenting with the priors, we found that in the
+absence of a strong prior on the stellar density, the inherent
 degeneracy between the impact parameter and planet-to-star size ratio
@@
 the cluster isochrone fit break this degeneracy, enabling us to report
-two-sided limits on the planet-to-star size ratio.
+two-sided limits on the planet-to-star size ratio.}
+
+\added{The second model, which used just the TESS data and the
+cluster-isochrone stellar parameter priors,
+formally yielded only a one-sided limit on the planet radius.  The
+reason is that the $b$--$R_{\rm p}/R_\star$ degeneracy was not broken:
+the combination of uncertain stellar parameters and
+the grazing geometry allowed very
+large planet-to-star radius ratios for very large impact parameters.
+Based on our mass upper limit of $1.20\,M_{\rm Jup}$, we might argue
+in favor of discarding the large-radius solution, since no sub-Jovian
+mass objects are known to be larger than $\sim$$3R_{\rm Jup}$.  Had we
+imposed this additional prior, then the TESS-only model would have
+yielded
+\begin{align}
+  R_{\rm p} &= 0.836^{+0.208}_{-0.121} R_{\rm Jup} \\
+  b &= 0.957^{+0.027}_{-0.017}.
+\end{align}
+Although these parameters are in 1-$\sigma$ agreement with our adopted
+joint model of the TESS and ground-based data, we preferred the first
+model both because it included all available data, and because it
+succeeded in breaking the $b$--$R_{\rm p}/R_\star$ degeneracy without
+requiring the adoption of informed priors.
+}
 
@@
 	\caption{
-    \explain{The bottom sub-panel of this figure has been added
-    in revision.}
     {\bf \tn\ compared to known transiting planets}.
@@
 understanding of the planet's \replaced{contraction and
-photoevaporation}{composition and future atmospheric
-evolution}.  If an RV campaign were timed to coincide with TESS
-Sectors 36 and 37 (3 March 2021 through 28 April 2021), it would
-significantly ease extraction of the Keplerian signal.  The reason is
-that the RVs, activity indicators, and photometry could be modeled
-simultaneously \citep[{\it
-e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.  Combining
-photometric and radial velocity data from non-overlapping epochs would
-also constrain the models, but perhaps not quite as convincingly.
+photoevaporation}{composition and future atmospheric evolution}.  If
+an RV campaign were timed to coincide with TESS Sectors 36 and 37 (3
+March 2021 through 28 April 2021), it would significantly ease
+extraction of the Keplerian signal.  The reason is that the RVs,
+activity indicators, and photometry could be modeled simultaneously
+\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
+Combining photometric and radial velocity data from non-overlapping
+epochs would also constrain the models, but perhaps not quite as
+convincingly.
 
@@
 during the TESS mission extension may also help in understanding the
-system \citep{bouma_extend_2017,huang_expected_2018}.  \deleted{Any
+system \citep{bouma_extend_2017,huang_expected_2018}.\deleted{ Any
 misalignment between the star's spin axis and the planet's orbit
@@
 observed, this could be a spectroscopy-free method for confirming the
-planet.}
-\added{
-  In particular, additional photometry will likely enable more
-  detailed exploration of whether the orbit of \tn\ is eccentric, and
-  also whether the system could host additional transiting planets.
-}
+planet.}\added{ In particular, additional photometry will likely
+enable more detailed exploration of whether the orbit of \tn\ is
+eccentric, and also whether the system could host additional
+transiting planets. }
 
@@
 
-We acknowledge support from the French and Italian Polar Agencies,
-IPEV and PNRA, and from Universit\'e C\^ote d’Azur under Idex UCAJEDI
-(ANR-15-IDEX-01). We thank the dedicated staff at Concordia for their
-continuous presence and support throughout the Austral winter.
+The ASTEP project acknowledges support from the French and Italian
+Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur
+under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at
+Concordia for their continuous presence and support throughout the
+Austral winter.
 %

### 2020-09-02 paper_review/response_20200826.txt
address comments on RV limits
better method for {semi-amplitude, period} constraints based on no RV
trend.

@@
 ----------
-> FIXME TODO
+> Prompted by this comment, we have amended our method for sampling
+> K-P parameter space to one that we feel is more robust against
+> inefficient sampling and the multimodal nature of the long-period
+> detection problem. The last paragraph of Section 3.1.4 has been
+> amended to the following:
+>
+> """
+> We performed the following injection-recovery exercise.  We
+> simulated $10^6$ two-body systems with random orbital phases and
+> inclinations, and semi-amplitudes and periods drawn from logarithmic
+> distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
+> and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
+> assuming circular orbits, we then analytically evaluated what the
+> radial velocities would have been at the observed FEROS times if the
+> system had the assumed parameters.  We then calculated what the
+> linear slope would have been for each simulated system.  If the
+> absolute value of the slope exceeded our 3-$\sigma$ limit of
+> $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we
+> assumed that we would have detected such a system.
+> Figure~\ref{fig:fpscenario} shows the resulting detection limits;
+> weakened sensitivity at harmonics of the baseline occur at lower
+> masses and smaller projected separations than shown on the plot.
+> The conversion from mass to brightness contrast was performed using
+> the same 35 Myr MIST isochrones and assumptions as in Section 3.1.2.
+> """
+>
+> As a supplement for the referee's inspection, we also attach a plot
+> showing the simulated "detections" and "non-detections" directly in
+> the Msini vs semi-major axis plane (yellow points are detected;
+> purple are not).
 

### 2020-09-02 paper/ms.tex
address comments on RV limits
better method for {semi-amplitude, period} constraints based on no RV
trend.

@@
 \subsubsection{Speckle Imaging}
+\label{subsec:speckleconstraint}
 The contrast limits obtained through the SOAR $I$-band speckle imaging
@@
 detect massive bound companions orbiting \tn.  We searched for the
-presence of planetary and stellar-mass companions using
+presence of planetary and stellar-mass companions \replaced{using
 \texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits, and performed two sets of fits.
+orbits, and performed two sets of fits}{in two different regimes:
+first, at the orbital period of the transiting object, and second, at
+longer orbital periods to constrain the presence of a massive bound
+companion. }.
 
@@
 using the known ephemeris from the transit.  We then fitted for the
-semi-amplitude, instrument offsets, and jitter parameters.  This
-yielded a non-detection of the planet's orbit.  The corresponding
-3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on $M_{\rm p} \sin
-i$ is $1.20 M_{\rm Jup}$.  The data and corresponding model are shown
-in Figure~\ref{fig:rvs}.
+semi-amplitude, instrument offsets, and jitter parameters \added{using
+\texttt{radvel} \citep{fulton_radvel_2018}, and assuming circular
+orbits}.  This yielded a non-detection of the planet's orbit.  The
+corresponding 3-$\sigma$ (99.7$^{\rm th}$ percentile) upper limit on
+$M_{\rm p} \sin i$ is $1.20 M_{\rm Jup}$.  The data and corresponding
+model are shown in Figure~\ref{fig:rvs}.
 
@@
 To place limits on the properties of a possible bound hierarchical
-companion, we fitted the radial velocity data for a Keplerian orbit
-assuming wide logarithmic priors on the semi-amplitude and period: $K\
-[{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}]
-\sim \log \mathcal{U}(0.1, 10^{15})$.  We then fitted for the
-semi-amplitude, period, time of conjunction, instrument offsets, and
-jitter parameters.  We converted the resulting posterior in period and
+companion, we \added{performed the following injection-recovery
+exercise.  We simulated $10^6$ two-body systems with random orbital
+phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
+distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
+and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
+assuming circular orbits, we then analytically evaluated what the
+radial velocities would have been at the observed FEROS times if the
+system had the assumed parameters.  We then calculated what the linear
+slope would have been for each simulated system.  If the absolute
+value of the slope exceeded our 3-$\sigma$ limit, we assumed that we
+would have detected such a system.  Figure~\ref{fig:fpscenario} shows
+the resulting detection limits; weakened sensitivity at harmonics of
+the baseline occur at lower masses and smaller projected separations
+than shown on the plot. The conversion from mass to brightness
+contrast was performed using the same 35 Myr MIST isochrones and
+assumptions as in
+Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
+velocity data for a Keplerian orbit assuming wide logarithmic priors
+on the semi-amplitude and period: $K\ [{\rm m\,s^{-1}}] \sim
+\log\mathcal{U}(1,10^5)$, and $P\ [{\rm days}] \sim \log
+\mathcal{U}(0.1, 10^{15})$.  We then fitted for the semi-amplitude,
+period, time of conjunction, instrument offsets, and jitter
+parameters.  We converted the resulting posterior in period and
 semi-amplitude to minimum mass and semi-major axis assuming Kepler's
 third law.  The resulting 3-$\sigma$ limits are shown in
-Figure~\ref{fig:fpscenario}.
+Figure~\ref{fig:fpscenario}.}
 

### 2020-09-02 drivers/oneoff_drivers/rvlimits_method2.py

@@ -88,6 +88,8 @@ def rv_injection_worker(task):
 def calc_semiamplitude_period_recovery(N_samples, gammadot_limit, delta_time,
                                        t_observed, do_serial=0):
 
+    np.random.seed(42)
+
     log_semiamplitude = np.random.uniform(
         np.log(1e1), np.log(1e7), size=N_samples
     )
@@ -192,7 +194,7 @@ def calc_semiamplitude_period_recovery(N_samples, gammadot_limit, delta_time,
     sini = 1
     Mstar = MSTAR * u.Msun
 
-    msini_msun = ((
+    msini_msun = sini*((
         (np.exp(np.array(df.logK)) / (28.4329)) * (1-e**2)**(1/2) *
         (Mstar.to(u.Msun).value)**(2/3) *
         ((np.exp(np.array(df.logP))*u.day).to(u.yr).value)**(1/3)

### 2020-09-02 paper/ms.tex
ditto

@@
 slope would have been for each simulated system.  If the absolute
-value of the slope exceeded our 3-$\sigma$ limit, we assumed that we
-would have detected such a system.  Figure~\ref{fig:fpscenario} shows
-the resulting detection limits; weakened sensitivity at harmonics of
-the baseline occur at lower masses and smaller projected separations
-than shown on the plot. The conversion from mass to brightness
-contrast was performed using the same 35 Myr MIST isochrones and
-assumptions as in
+value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
+0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
+detected such a system.  Figure~\ref{fig:fpscenario} shows the
+resulting limits; weakened sensitivity at harmonics of the baseline
+occur at lower masses and smaller projected separations than shown on
+the plot. The conversion from mass to brightness contrast was
+performed using the same 35 Myr MIST isochrones and assumptions as in
 Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial

### 2020-09-02 paper/ms.tex
update manuscript

@@
 latter flux-fraction limit of 8\% ($\Delta {\rm mag} \approx 2.7$).
+\added{The outer limit in projected separation for associated
+companions is the distance at which the Keplerian orbital velocity is
+well below the rotational broadening. This condition translates to a
+projected separation of $10$--$20\,{\rm AU}$, depending on the
+companion mass.  For chance alignments, the same restrictions on
+velocity separation apply, but out to a projected separation equal to
+the CHIRON slit width of $\approx 1''$.}
 
@@
 The radial velocities from FEROS, CHIRON, and Veloce can be used to
-detect massive bound companions orbiting \tn.  We searched for the
-presence of planetary and stellar-mass companions \replaced{using
-\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
-orbits, and performed two sets of fits}{in two different regimes:
-first, at the orbital period of the transiting object, and second, at
-longer orbital periods to constrain the presence of a massive bound
-companion. }.
+detect massive bound companions orbiting \tn.  We searched for
+\deleted{the presence of }planetary and stellar-mass companions
+\replaced{using \texttt{radvel} \citep{fulton_radvel_2018}.  We
+assumed circular orbits, and performed two sets of fits.}{in two
+different regimes: first, at the orbital period of the transiting
+object, and second, at longer orbital periods to constrain the
+presence of a massive bound companion.}
 
@@
 exercise.  We simulated $10^6$ two-body systems with random orbital
-phases and inclinations, and semi-amplitudes and periods drawn from logarithmic
+phases and inclinations, and drew their semi-amplitudes and periods from logarithmic
 distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
@@
 the plot. The conversion from mass to brightness contrast was
-performed using the same 35 Myr MIST isochrones and assumptions as in
+performed using the same isochrone models and assumptions as in
 Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
@@
 the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
-are caused by hierarchical blends, and {\it iii)} the eclipses are
-caused by neighboring stars outside $\approx 2''$.  The only scenario
-not formally ruled out is a background eclipsing binary.  A simple
-(fallacious) argument on the a priori probability of background blends
-follows from counting statistics.  The local density of $T<15.1$ stars
-around \tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
-arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
-not excluded by the SOAR HRCam contrast curve, for a randomly selected
-star we would expect $1.0\times10^{-4}$ potential $T<15.1$
-contaminants, which appears small.
+are caused by hierarchical blends\added{\footnote{There is
+a small gap in the upper panel of
+Figure~\ref{fig:fpscenario}, corresponding to a $\approx 0.7 M_\odot$
+companion HEB at a projected separation of $\approx$15$\,$AU. This
+region of parameter space is, in our view, small enough to be safely
+ignored.}}, and {\it iii)} the eclipses are caused by neighboring
+stars outside $\approx 2''$.  The only scenario not formally ruled out
+is a background eclipsing binary.  A simple, and fallacious, argument 
+against background blends follows from counting
+statistics.  The local density of $T<15.1$ stars around \tn, found by
+counting from TIC8, is $3.7\times10^{-4} \,{\rm arcsec}^{-2}$.
+Therefore within the relevant $\approx0.3''$ radius not excluded by
+the SOAR HRCam contrast curve, for a randomly selected star we would
+expect $1.0\times10^{-4}$ potential $T<15.1$ contaminants, which
+appears small.
 
@@
 in favor of discarding the large-radius solution, since no sub-Jovian
-mass objects are known to be larger than $\sim$$3R_{\rm Jup}$.  Had we
-imposed this additional prior, then the TESS-only model would have
+mass objects larger than $\sim$$3R_{\rm Jup}$ are known to exist.  Had
+we imposed this additional prior, then the TESS-only model would have
 yielded
@@
     {\it Top}: Planet radii versus ages.  Systems younger than
-    100$\,$Myr are emphasized.  Ages and radii are from the NASA
+    100 Myr are emphasized.  Ages and radii are from the NASA
     Exoplanet Archive on 27 Aug 2020.  Precise ages are known for only
     a small fraction of the gray points.
-    {\it Bottom}: Planet radii versus orbital periods. The known young
-    transiting planets do not obviously overlap with the populations of
-    known hot Jupiters or sub-Neptunes.
+    {\it Bottom}: Planet radii versus orbital periods. The youngest
+    known transiting planets do not obviously overlap with the
+    populations of known hot Jupiters or sub-Neptunes.
 		\label{fig:population}
@@
 \begin{align}
-  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
-  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
-  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
+  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272527 \pm 0.000593 \nonumber \\
+  P\ [{\rm d}] &= 8.3248762 \pm 0.0000157 \nonumber \\
+  T_{14}\ [{\rm hr}] &= 1.96 \pm 0.04.
   \label{eq:ephem}

### 2020-09-02 paper_review/response_20200826.txt
update response

--- 2020-09-01 paper_review/response_20200826.txt
@@
 report, alongside our responses. A list of changes is appended to
-the manuscript using the trackchanges AASTeX macros. A figure
-supporting the verification of our SB2 injection-recovery test
-has also been uploaded for inspection.
+the manuscript using the trackchanges AASTeX macros. Figures
+supporting the verification of our SB2 injection-recovery test,
+and supporting our radial velocity semi-amplitude/period upper
+limits have also been uploaded for inspection.
 
@@
 > G-band magnitudes. So yes, we believe that the blending
-> scenario is still plausible, primarily because Star A is much
-> fainter than TOI 837, placing it near the resolution threshold.
+> scenario is plausible, primarily because Star A is much fainter
+> than TOI 837, placing it near the resolution threshold.
 
@@
 ----------
-> Our thanks for pointing this out. We have added a paragraph at
-> the end of Section 2.4.1 to this effect.
+> Our thanks for this point. We have added a paragraph at the end
+> of Section 2.4.1 to this effect, though we continue to place
+> the strongest weight on our tests from the seeing-limited
+> photometric timeseries data.
 
@@
 ----------
-> FIXME TODO
+> Correct -- thank you raising for this point. We have amended
+> the outer limit in Figure 6 for the "Not SB2" associated
+> companion constraint to the distance at which the Keplerian
+> orbital velocity falls below the rotational broadening.  The
+> text in Sec 3.1.3 has been accordingly.
+>
+> This weaker constraint now leaves a miniscule region of the HEB
+> parameter space open. We do not think that this warrants a
+> recalculation of the false positive probability for the system,
+> but nonetheless we have added a footnote in the first paragraph
+> of Section 3.2 to draw attention to this point.
 
@@
 ----------
-> FIXME TODO
+> Prompted by this comment, we have amended our method for sampling
+> K-P parameter space to one that we feel is more robust against
+> inefficient sampling and the multimodal nature of the long-period
+> detection problem. The last paragraph of Section 3.1.4 has been
+> amended to the following:
+>
+> """
+> To place limits on the properties of a possible bound hierarchical
+> companion, we performed the following injection-recovery
+> exercise.  We simulated $10^6$ two-body systems with random orbital
+> phases and inclinations, and drew their semi-amplitudes and periods
+> from logarithmic distributions: $K\ [{\rm m\,s^{-1}}] \sim
+> \log\mathcal{U}(1,10^7)$, and $P\ [{\rm days}] \sim \log
+> \mathcal{U}(1, 10^{15})$. Again assuming circular orbits, we then
+> analytically evaluated what the radial velocities would have been at
+> the observed FEROS times if the system had the assumed parameters.
+> We then calculated what the linear slope would have been for each
+> simulated system.  If the absolute value of the slope exceeded our
+> 3-$\sigma$ limit of $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
+> day}^{-1}$, we assumed that we would have detected such a system.
+> Figure~\ref{fig:fpscenario} shows the resulting limits; weakened
+> sensitivity at harmonics of the baseline occur at lower masses and
+> smaller projected separations than shown on the plot. The conversion
+> from mass to brightness contrast was performed using the same
+> isochrone models and assumptions as in Section 3.1.2.}
+> """
+>
+> As a supplement for the referee's inspection, we also attach a plot
+> showing the simulated "detections" and "non-detections" directly in
+> the Msini vs semi-major axis plane (yellow points are detected;
+> purple are not).
 
@@
 > in addition to the MIST models. (We checked the Feiden 2016
-> Dartmouth models, but no synthetic Gaia-band photometry was
-> available, which complicates the comparison between between the
-> Gaia photometry and the models.) The differences between MIST
-> and PARSEC are now described in the text, and are used to
-> estimate systematic uncertainties on the stellar parameters.
-> These uncertainties are now reported in Table 4, and they are
-> also propagated through the transit fits (Table 5; Figure 1;
-> Figure 4; Figure 10). 
+> Dartmouth models, but could not find synthetic Gaia-band
+> photometry, which would have complicated the comparison between
+> between the Gaia photometry and the models.) The differences
+> between MIST and PARSEC are now described in the text, and are
+> used to estimate systematic uncertainties on the stellar
+> parameters.  These uncertainties are now reported in Table 4,
+> and they are also propagated through the transit fits (Table 5;
+> Figure 1; Figure 4; Figure 10). 
 >
@@
 > impact parameters much greater than 1 became statistically
-> allowed (though not favored), if the planet-to-star radius
+> allowed, though not favored, if the planet-to-star radius
 > ratio were to be very large. Our ability to break the
@@
 > Despite our initial reservations about using the ground-based
-> data for the planet parameters, the combined data do yield a more
-> precise fit, and also seem to do a better job at breaking the Rp/R*
-> vs b degeneracy. These two points persuaded us to adopt it as our
-> preferred solution.  Nonetheless, this decision is one of
-> preference, and not modelling necessity. We have amended Section 4.3
-> at some length to present the points made in this response, and to
-> emphasize the key results from both approaches.  Consequent changes
-> include:
+> data for the planet parameters, the combined data do yield a
+> more precise fit, and also seem to do a better job at breaking
+> the Rp/R* vs b degeneracy. These two points persuaded us to
+> adopt it as our preferred solution.  Nonetheless, this decision
+> is one of preference, and not modelling necessity. We have
+> amended Section 4.3 at some length to present the points made
+> in this response, and to emphasize the key results from both
+> approaches.  Consequent changes include:
 >
@@
 ----------
-> Noted with thanks. As described above, we have amended our preferred
-> solution to the TESS+ground solution, rather than the TESS-only
-> solution.
+> As described above, we have amended our preferred solution to
+> the TESS+ground solution, rather than the TESS-only solution.
 
@@
 ----------
-> While we agree that the possibility of a non-circular orbit would be
-> interesting, we do not expect that given the present data we can
-> make credible statements about potential non-zero eccentricities. We
-> have updated the last paragraph of Sec 4.3 to justify this
-> assumption of a circular orbit, and have amended the conclusion to
-> mention this as a possible area for future work.
+> While we agree that the possibility of a non-circular orbit
+> would be interesting, we do not expect that given the present
+> data we can make credible statements about potential non-zero
+> eccentricities. We have updated the last paragraph of Sec 4.3
+> to justify this assumption of a circular orbit, and have
+> amended the conclusion to mention this as a possible area for
+> future work.
 
@@
 > precession frequency of the orbital axis due to the stellar
-> oblateness using equations from Anderson+2018 and Lai+2018. We found
-> that given the observed parameters of the system and an assumed
-> stellar Love number (k2) equal to that of the Sun, the precession
-> period would be 45,000 years. To complete say 1% of a precession
-> cycle, which might roughly be what is needed to observe noticeable
-> changes, we would need to wait ~450 years.
+> oblateness using equations from Anderson+2018 and Lai+2018. We
+> found that given the observed parameters of the system and an
+> assumed stellar Love number (k2) equal to that of the Sun, the
+> precession period would be 45,000 years. To complete say 1% of
+> a precession cycle, which might roughly be what is needed to
+> observe noticeable changes, we would need to wait ~450 years.
 >
-> We have correspondingly amended the last sentence to omit the point
-> on nodal precession, in favor of the point that more photometry
-> should improve our ability to constrain the orbital eccentricity,
-> and will also let us search for additional transiting planets.
+> We have correspondingly amended the last sentence to omit the
+> point on nodal precession, in favor of the point that more
+> photometry should improve our ability to constrain the orbital
+> eccentricity, and will also let us search for additional
+> transiting planets.
 
@@
 * Table 5 has new rows for the ground-based transit nuisance
-  parameters, and the posterior values are updated for the propagation
-  of stellar parameter uncertainties.
+  parameters, and the posterior values are updated for the
+  propagation of stellar parameter uncertainties.

### 2020-09-02 paper/ms.tex
fix tex column width

@@
   the system can be confirmed or refuted through observations of the
-  stellar obliquity and the planetary mass.  Such observations may also
-  improve our understanding of how the physical and orbital properties
-  of exoplanets change in time.
+  stellar obliquity and the planetary mass.  Such observations may
+  also improve our understanding of how the physical and orbital
+  properties of exoplanets change in time.
 \end{abstract}
@@
 surface gravity and the radiation environment.  Both processes can be
-directly observed through observations of planetary winds in the
-metastable 1083$\,$nm He line
+directly observed \replaced{through observations of planetary winds
+in}{in favorable cases using} the metastable 1083$\,$nm He line
 \citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.
@@
 The circularization timescale is thought to be such that for any giant
-planets that migrated early, their orbits should circularize within
-100 million years \citep{zahn_tidal_1977,bonomo_gaps_2017}.
-
-Finding and understanding systems undergoing these evolutionary changes is
-a major goal in contemporary exoplanet research.  To identify stars
-younger than say 1 \replaced{Gyr}{gigayear}, a number of direct and indirect methods are
-available \citep{soderblom_ages_2010}.  The traditional approach is to
+planets that \replaced{migrated early}{do migrate early}, their orbits
+should circularize within 100 million years
+\citep{zahn_tidal_1977,bonomo_gaps_2017}.
+
+Finding and understanding systems undergoing these evolutionary
+changes is a major goal in contemporary exoplanet research.  To
+identify stars younger than say 1 \replaced{Gyr}{gigayear}, a number
+of direct and indirect methods are available
+\citep{soderblom_ages_2010}.  The traditional approach is to
 isochronally age-date coeval groups of stars, hereafter ``clusters''
@@
 it has now been published, and added note to Donati et al 2020.}
-A few dozen planets in clusters have been detected, and fewer still
-have been closely characterized.  Despite the challenges of
-starspot-induced radial velocity (RV) variations, RV surveys found
-success in the Hyades, NGC~\replaced{2523}{2423}, Praesepe, and M~67
+\replaced{A}{To date, a} few dozen planets in clusters have been
+detected, and fewer still have been closely characterized.  Despite
+the challenges of starspot-induced radial velocity (RV) variations, RV
+surveys found early success in the Hyades, NGC~\replaced{2523}{2423},
+Praesepe, and M~67
 \citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
@@
 \citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
-\added{
-The planetary nature of at least two of these signals has been debated
-\citep{donati_magnetic_2020,damasso_gaps_2020}.
-}
+\added{The planetary nature of at least two of these signals has been
+debated \citep{donati_magnetic_2020,damasso_gaps_2020}.}
 
@@
 candidate young stars that have been reported in the literature.  At
-the time of writing, $\sim$$6\times10^5$ light curves from
-Year 1 of TESS had been created and were available through
-MAST\footnote{\stscilink}, and via \datasetlink.  Searching
-through a subset of these light curves brought our attention to the
-candidate transiting planet, \pn, that is the subject of this
-analysis.
+the time of writing, $\sim$$6\times10^5$ light curves from Year 1 of
+TESS had been created and were available through
+MAST\footnote{\stscilink}, and via \datasetlink.  Searching through a
+subset of these light curves brought our attention to the candidate
+transiting planet, \pn, that is the subject of this analysis.
 
@@
 astrophysical false positives \citep[{\it
-e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
-and related scenarios are unlikely to the degree that we can
+e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data showed that
+this and related scenarios were unlikely to the degree that we could
 validate the planet, {\it i.e.}, determine that its probability of
-being an astrophysical false positive is small.  We
-considered this result worth reporting because of the planet's youth.
+being an astrophysical false positive was small.  We considered this
+result worth reporting because of the planet's youth.
 
@@
 		\subfloat{
-			\includegraphics[width=0.79\textwidth]{f1a.pdf}
+			\includegraphics[width=0.77\textwidth]{f1a.pdf}
 		}
@@
 		\subfloat{
-			\includegraphics[width=0.77\textwidth]{f1b.pdf}
+			\includegraphics[width=0.76\textwidth]{f1b.pdf}
 		}
@@
     TESS transits.  Gray lines are the best-fit model to the TESS
-    \added{and ground-based data}, which includes
-    a local quadratic trend for each transit. Gray points are 2-minute
-    \texttt{PDCSAP} flux measurements, black points are binned to
-    15-minute intervals.  {\it Bottom}: Phase-folded TESS and
-    ground-based transits. \added{Section~\ref{subsec:groundphot} presents
-    the ground-based data.} Gray points are flux
-    measurements with the local spot-induced variation removed.  A
-    weighted binning at 6-minute intervals yields the black points.
-    The black error-bar shows the median uncertainty for the black
-    points.  The gray line is the best-fit model for the entire
-    dataset.
+    \added{and ground-based data}, which includes a local quadratic
+    trend for each transit. Gray points are 2-minute \texttt{PDCSAP}
+    flux measurements, black points are binned to 15-minute intervals.
+    {\it Bottom}: Phase-folded TESS and ground-based transits.
+    \added{Section~\ref{subsec:groundphot} presents the ground-based
+    data.} Gray points are flux measurements with the local
+    spot-induced variation removed.  A weighted binning at 6-minute
+    intervals yields the black points.  The black error-bar shows the
+    median uncertainty for the black points.  The gray line is the
+    best-fit model for the entire dataset.
 		\label{fig:thephot}
@@
 \citep{jenkins_tess_2016} processed the image data and identified the
-transiting planet signature from two transits in
-Sector 10, again with three transits in Sector 11, and then for a
-final time when Sectors 1--13 were searched at the end of the first
-year of the mission. The transit signature was fitted with a
-limb-darkened transit model \citep{li_kepler_2019} and passed all the
-diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
-depth test, the weak secondary eclipse test, \deleted{the ghost diagnostic
-test,} and the difference image centroiding test, which placed the
-transit source within $\sim$2 arcsec of the location of TOI~837. No
-additional transit-like features were identified in any of the SPOC
-searches. The TESS Science Office alerted the community to this
-candidate transiting planet on 17 June 2019.  Our subsequent blind
-search of the CDIPS FFI light curves also showed the transits\added{,
-as did that of \citet{nardiello_pathosII_2020}}. Given
-that the 2-minute data had better sampling cadence, we opted to use
-the Presearch Data Conditioning (PDC) light curve with the default
-aperture for our
+transiting planet signature from two transits in Sector 10, again with
+three transits in Sector 11, and then for a final time when Sectors
+1--13 were searched at the end of the first year of the mission. The
+transit signature was fitted with a limb-darkened transit model
+\citep{li_kepler_2019} and passed all the diagnostic tests
+\citep{twicken_kepler_2018}, including the odd/even depth test, the
+weak secondary eclipse test, \deleted{the ghost diagnostic test,} and
+the difference image centroiding test, which placed the transit source
+within $\sim$2 arcsec of the location of TOI~837. No additional
+transit-like features were identified in any of the SPOC searches. The
+TESS Science Office alerted the community to this candidate transiting
+planet on 17 June 2019.  Our subsequent blind search of the CDIPS FFI
+light curves also showed the transits\added{, as did that of
+\citet{nardiello_pathosII_2020}}. Given that the 2-minute data had
+better sampling cadence, we opted to use the Presearch Data
+Conditioning (PDC) light curve with the default aperture for our
 analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.
@@
 shown in \added{the bottom panel of }Figure~\ref{fig:thephot}.
-\added{The ground-based data }and our procedure for fitting the
-models \deleted{in these plots is described in }\added{are discussed
-in Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
+\added{The ground-based data }and our fitting procedure \deleted{in
+these plots is described in }\added{are discussed in
+Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
 respectively}. \added{First though, some prerequisite context on the
@@
     pixel cutout}, with a logarithmic grayscale\added{ indicating the
-    flux in each pixel}. The yellow star is
-    the position of \tn.  White circles are resolved Gaia sources with
-    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
-    being larger}.  The black \texttt{X} and white \texttt{/} hatches
-    show the apertures used to measure the background and target star
-    flux, respectively. \replaced{Dashed lines of constant declination
-    and right ascension are shown}{The compass shows cardinal
-    directions in celestial coordinates. Dashed lines of constant
-    declination are separated by 1$'$, while those of right ascension
-    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
-    ``Star B'', which were excluded as being possible sources of the
-    transits.
+    flux in each pixel}. The yellow star is the position of \tn.
+    White circles are resolved Gaia sources with $T<16$\replaced{.
+    Brighter stars are larger}{, with brighter stars being larger}.
+    The black \texttt{X} and white \texttt{/} hatches show the
+    apertures used to measure the background and target star flux,
+    respectively. \replaced{Dashed lines of constant declination and
+    right ascension are shown}{The compass shows cardinal directions
+    in celestial coordinates. Dashed lines of constant declination are
+    separated by 1$'$, while those of right ascension are separated by
+    2$'$}.  Two stars of interest are ``Star A'' and ``Star B'', which
+    were excluded as being possible sources of the transits.
 		\label{fig:scene}
@@
 
-\added{
-An additional line of evidence for Star A not being the transit host
-was also noted by the referee.  The $G$-band magnitude and the
-parallax suggest that Star A is an M dwarf. As a probable cluster
-member, it would have $Bp - Rp \approx 2.8$ (see
+\added{An additional line of evidence for Star A not being the
+transit host was also noted by the referee.  The $G$-band magnitude
+and the parallax suggest that Star A is an M dwarf. As a probable
+cluster member, it would have $Bp - Rp \approx 2.8$ (see
 Section~\ref{subsec:hr}), which corresponds roughly to a mass in the
-range of 0.15-0.45$\,M_\odot$, or densities roughly in the range of
-2-3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
+range of 0.15--0.45$\,M_\odot$, or densities roughly in the range of
+2--3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
 \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
 These densities are inconsistent with those inferred from the transit
-fits in Section~\ref{subsec:planet}.
-}
+fits in Section~\ref{subsec:planet}.}
 
@@
 Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
-Concordia base is operated by the French and Italian polar
-institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
-allows it to take advantage of the continuous night during Austral
-winter.  The weather is of photometric quality for about two-thirds of
-each winter \citep{crouzet_four_2018}.
+Concordia base is operated by the French and Italian polar institutes,
+IPEV and PNRA.  Its position on the Antarctic Plateau allows it to
+take advantage of the continuous night during Austral winter.  The
+weather is of photometric quality for about two-thirds of each winter
+\citep{crouzet_four_2018}.
 
@@
 \tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
-2020, and 23 June 2020 (UT).  Except for
-12 May, our observations were conducted under stable weather
-conditions, with clear skies, temperatures of about $-70^\circ$C, and
-wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
-exclude from the analysis all data collected on 12 May. We found that
-the optimal calibrated light curves of \tn\ correspond to an 11 pixel
-(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
-observations carried out on June and May, respectively.  The data are
-reported in Table~\ref{tab:phot}, and plotted in
-Figure~\ref{fig:groundphot}.
+2020, and 23 June 2020 (UT).  Except for 12 May, our observations were
+conducted under stable weather conditions, with clear skies,
+temperatures of about $-70^\circ$C, and wind speeds less than
+5\,m$\,$s$^{-1}$. Due to their poor quality, we exclude from the
+analysis all data collected on 12 May. We found that the optimal
+calibrated light curves of \tn\ correspond to an 11 pixel (10\,arcsec)
+and 14 pixel (12\,arcsec) radius aperture for observations carried out
+on June and May, respectively.  The data are reported in
+Table~\ref{tab:phot}, and plotted in Figure~\ref{fig:groundphot}.
 
@@
     and the photometric modulation amplitude is
-    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
-    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
-    line shows a circular Keplerian orbit representing the 3-$\sigma$
-    upper mass limit.
+    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased
+    to the orbital ephemeris of \pn.  The planet is not detected.  The
+    dashed black line shows a circular Keplerian orbit representing
+    the 3-$\sigma$ upper mass limit.
     \label{fig:rvs}
@@
 characterization of the star and therefore planet.  Reducing multiple
-spectra to radial velocities can enable planet mass
-measurements, and can also lead to limits on the mass of nearby
-companions.  Finally, if there are close or bright companions,
-reconnaissance spectra can also reveal the presence of a secondary set
-of stellar lines.
+spectra to radial velocities can enable planet mass measurements, and
+can also lead to limits on the mass of nearby companions.  Finally, if
+there are close or bright companions, reconnaissance spectra can also
+reveal the presence of a secondary set of stellar lines.
 
@@
 smaller velocity separations, the injected lines begin to blend with
-the target spectrum.
-\added{We verified these results by injecting secondary lines directly
-into the spectrum and then deriving its LSD broadening profile as we
-would for a normal observation.  The results were nearly identical,
-save for greater computational cost.}
+the target spectrum. \added{We verified these results by injecting
+secondary lines directly into the spectrum and then deriving its LSD
+broadening profile as we would for a normal observation.  The results
+were nearly identical, save for greater computational cost.}
 
@@
 resolution of $\approx$48,000 across a spectral range of 350–920 nm.
-It has a high efficiency of $\approx$20\%. We obtained 13
-spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
-context of the Warm gIaNts with tEss (WINE) collaboration, which
-focuses on the systematic characterization of TESS transiting giant
-planets with moderately long orbital periods \citep[{\it
+It has a high efficiency of $\approx$20\%. We obtained 13 spectra of
+\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
+Warm gIaNts with tEss (WINE) collaboration, which focuses on the
+systematic characterization of TESS transiting giant planets with
+moderately long orbital periods \citep[{\it
 e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
@@
 exercise.  We simulated $10^6$ two-body systems with random orbital
-phases and inclinations, and drew their semi-amplitudes and periods from logarithmic
-distributions: $K\ [{\rm m\,s^{-1}}] \sim \log\mathcal{U}(1,10^7)$,
-and $P\ [{\rm days}] \sim \log \mathcal{U}(1, 10^{15})$. Again
-assuming circular orbits, we then analytically evaluated what the
-radial velocities would have been at the observed FEROS times if the
-system had the assumed parameters.  We then calculated what the linear
-slope would have been for each simulated system.  If the absolute
-value of the slope exceeded our 3-$\sigma$ limit of $|\dot{\gamma}| <
-0.82\,{\rm m\,s}^{-1}\,{\rm day}^{-1}$, we assumed that we would have
-detected such a system.  Figure~\ref{fig:fpscenario} shows the
-resulting limits; weakened sensitivity at harmonics of the baseline
-occur at lower masses and smaller projected separations than shown on
-the plot. The conversion from mass to brightness contrast was
-performed using the same isochrone models and assumptions as in
+phases and inclinations, and drew their semi-amplitudes and periods
+from logarithmic distributions: $K\ [{\rm m\,s^{-1}}] \sim
+\log\mathcal{U}(1,10^7)$, and $P\ [{\rm days}] \sim \log
+\mathcal{U}(1, 10^{15})$. Again assuming circular orbits, we then
+analytically evaluated what the radial velocities would have been at
+the observed FEROS times if the system had the assumed parameters.  We
+then calculated what the linear slope would have been for each
+simulated system.  If the absolute value of the slope exceeded our
+3-$\sigma$ limit of $|\dot{\gamma}| < 0.82\,{\rm m\,s}^{-1}\,{\rm
+day}^{-1}$, we assumed that we would have detected such a system.
+Figure~\ref{fig:fpscenario} shows the resulting limits; weakened
+sensitivity at harmonics of the baseline occur at lower masses and
+smaller projected separations than shown on the plot. The
+interpolation from mass to brightness contrast was performed using the
+same isochrone models and assumptions as in
 Section~\ref{subsec:speckleconstraint}.}\deleted{fitted the radial
@@
 companions existed for which the maximal expected eclipse depth could
-have been larger than the observed depth.  
-We could not rule out hierarchical eclipsing binary systems in cases
-for which the answer was yes.
-Conversely, we ruled out systems for which at fixed
+have been larger than the observed depth.  We could not rule out
+hierarchical eclipsing binary systems in cases for which the answer
+was yes.  Conversely, we ruled out systems for which at fixed
 secondary mass no tertiary mass could enable eclipses of the necessary
@@
 the eclipses are caused by a star orbiting \tn, {\it ii)} the eclipses
-are caused by hierarchical blends\added{\footnote{There is
-a small gap in the upper panel of
-Figure~\ref{fig:fpscenario}, corresponding to a $\approx 0.7 M_\odot$
-companion HEB at a projected separation of $\approx$15$\,$AU. This
-region of parameter space is, in our view, small enough to be safely
-ignored.}}, and {\it iii)} the eclipses are caused by neighboring
-stars outside $\approx 2''$.  The only scenario not formally ruled out
-is a background eclipsing binary.  A simple, and fallacious, argument 
-against background blends follows from counting
-statistics.  The local density of $T<15.1$ stars around \tn, found by
-counting from TIC8, is $3.7\times10^{-4} \,{\rm arcsec}^{-2}$.
-Therefore within the relevant $\approx0.3''$ radius not excluded by
-the SOAR HRCam contrast curve, for a randomly selected star we would
-expect $1.0\times10^{-4}$ potential $T<15.1$ contaminants, which
-appears small.
+are caused by hierarchical blends\added{\footnote{There is a small gap
+in the upper panel of Figure~\ref{fig:fpscenario}, corresponding to a
+$\approx 0.7 M_\odot$ companion HEB at a projected separation of
+$\approx$15$\,$AU. This region of parameter space is small, and we
+ignore it in the remaining analysis.}}, and {\it iii)} the eclipses
+are caused by neighboring stars outside $\approx 2''$.  The only
+scenario not formally ruled out is a background eclipsing binary.  A
+simple, and fallacious, argument against background blends follows
+from counting statistics.  The local density of $T<15.1$ stars around
+\tn, found by counting from TIC8, is $3.7\times10^{-4} \,{\rm
+arcsec}^{-2}$.  Therefore within the relevant $\approx0.3''$ radius
+not excluded by the SOAR HRCam contrast curve, for a randomly selected
+star we would expect $1.0\times10^{-4}$ potential $T<15.1$
+contaminants, which appears small.
 
@@
 probabilistic framework is required to calculate the chance that a
-background eclipsing binary causes the eclipses}.  We
-\replaced{opt to use \texttt{VESPA} to model the populations}{adopt
-the Bayesian framework implemented in \texttt{VESPA}}
+background eclipsing binary causes the eclipses}.  We \replaced{opt to
+use \texttt{VESPA} to model the populations}{adopt the Bayesian
+framework implemented in \texttt{VESPA}}
 \citep{morton_efficient_2012,vespa_2015}.
@@
 hypothetical companions to \tn\ must therefore be $\lesssim 50\%$ of
-its brightness; brighter companions would have made the total
-system $\gtrsim 0.44$ magnitudes brighter than the single-star
-sequence, which can be ruled out based on the photometric
-uncertainties and the intrinsic scatter in the HR diagram.}
+its brightness; brighter companions would have made the total system
+$\gtrsim 0.44$ magnitudes brighter than the single-star sequence,
+which can be ruled out based on the photometric uncertainties and the
+intrinsic scatter in the HR diagram.}
 
@@
 
-%\input{starparams.tex}
-
 \subsubsection{Membership of \tn\ in \cn}
@@
 \tn\ is above the stellar masses where the Gaia photometry and
-isochrone models begin to diverge.
-\added{
-  The statistical uncertainties yielded by this approach are of order
-  1\% for the stellar mass and radius.  To quantify the systematic
-  uncertainties, we compared the parameters derived from the MIST
-  isochrones with those from the
-  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
+isochrone models begin to diverge. \added{The statistical
+uncertainties yielded by this approach are of order 1\% for the
+stellar mass and radius.  To quantify the systematic uncertainties, we
+compared the parameters derived from the MIST isochrones with those
+from the PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}}
+isochrones
 \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
@@
 self-consistency, in Table~\ref{tab:starparams} and the ensuing
-  analysis we adopted the stellar
-  parameter values from MIST.  We took the uncertainties to be the
-  quadrature sum of the statistical and systematic components.
-}
+analysis we adopted the stellar parameter values from MIST.  We took
+the uncertainties to be the quadrature sum of the statistical and
+systematic components.}
 
@@
 \label{subsec:planet}
-
-%\input{model_posterior_table.tex}
 
@@
 where we quote the median, 86$^{\rm th}$, and 14$^{\rm th}$
-percentiles of the marginalized posteriors.
+percentiles of the marginalized one-dimensional posteriors.
 }
@@
 \end{align}
-% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex
+% from Table 5
 

### 2020-09-04 paper/ms.tex
add log10sma_vs_log10msini_detectable_check
minor updates

@@
 \received{August 6, 2020}
-\revised{---}
+\revised{September 7, 2020}
 \accepted{---}
@@
 
-\added{The authors thank K.~Anderson for fruitful discussions, and are
+\added{The authors thank K.~Anderson for fruitful discussions, and
+T.~Guillot for contributions to the ASTEP project.  We are also
 grateful to the anonymous referee for their constructive comments and

### 2020-09-05 paper/ms.tex
update manuscript
the corner plot aspect ratio is now better

@@
 emission and broadband UV emission.  Studies by, for instance,
-\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
-have combined these methods to age-date individual field stars hosting
-transiting planets.  Many of these latter methods were summarized by
+\citet{sanchis-ojeda_kepler-63b_2013}, \citet{david_discovery_2018},
+and G{.}~Zhou et al{.}~(2020, submitted) have combined these methods
+to age-date individual field stars hosting transiting planets.  Many
+of these latter methods were summarized by
 \citet{mamajek_improved_2008}, and have since been calibrated by, {\it
@@
 	\end{center}
-	\vspace{-0.3cm}
+	\vspace{-0.6cm}
 	\caption{ 

### 2020-09-05 timmy/plotting.py

@@ -3183,10 +3183,14 @@ def plot_subsetcorner(m, outpath):
     varnames = ['log_r', 'b', 'rho_star']
     labels = ['$\log(R_\mathrm{p}/R_{\star})$', '$b$',
               r'$\rho_\star$ [$\mathrm{g}\,\mathrm{cm}^{-3}$]']
+    ndim = len(varnames)
 
     trace_df = pm.trace_to_dataframe(m.trace, varnames=varnames)
 
+    fig, axs = plt.subplots(nrows=ndim,ncols=ndim,figsize=(5,5))
+
     fig = corner.corner(trace_df, quantiles=None,
+                        fig=fig,
                         show_titles=False,
                         fill_contours=True, plot_datapoints=False,
                         levels = (
@@ -3194,7 +3198,7 @@ def plot_subsetcorner(m, outpath):
                         ),
                         smooth=1.0,
                         title_fmt='.2g', labels=labels,
-                        label_kwargs={"fontsize":16})
+                        label_kwargs={"fontsize":11})
 
     axs = fig.axes
 

### 2020-09-07 paper/abstract_aas.tex
stage resubmitted manuscript

@@
 The star and planet are therefore $35^{+11}_{-5}$ million years old.
-Combining the transit photometry with a prior on the stellar parameters derived from the cluster color-magnitude diagram, we find that the planet has an orbital period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).
+Combining the transit photometry with a prior on the stellar parameters derived from the cluster color-magnitude diagram, we find that the planet has an orbital period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter ($R_{\rm p} = 0.77^{+0.09}_{-0.07} \,R_{\rm Jup}$).
 From radial velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm Jup}$ (3-$\sigma$).

### 2020-09-16 paper/ms.tex
aas resubmit stage
AAS accepted

@@
 \received{August 6, 2020}
-\revised{September 7, 2020}
-\accepted{---}
+\revised{September 6, 2020}
+\accepted{September 16, 2020}
 \submitjournal{AAS journals.}
@@
 and requires a significant amount of data and care in signal
-extraction \citep{barragan_radial_2019}.  The Rossiter-McLaughlin
-measurement avoids the majority of this issue because the transit
-occurs over a much shorter duration than a single stellar rotation
-period.
+extraction \citep{barragan_radial_2019,stefansson_k2-25_2020}.  The
+Rossiter-McLaughlin measurement avoids the majority of this issue
+because the transit occurs over a much shorter duration than a single
+stellar rotation period.
 
@@
 
-\added{The authors thank K.~Anderson for fruitful discussions, and
-T.~Guillot for contributions to the ASTEP project.  We are also
-grateful to the anonymous referee for their constructive comments and
-suggestions.}
+\added{The authors thank K.~Anderson for fruitful discussions, and are
+also grateful to the anonymous referee for their constructive comments
+and suggestions.}
 %

### 2020-09-16 paper/ms.tex
manuscript: UTF-8 insanity

@@
 This study was based in part on observations at Cerro Tololo
-Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
+Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop. ID
 2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
@@
 The ASTEP project acknowledges support from the French and Italian
-Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur
+Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d'Azur
 under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at
@@
 Inova\c{c}\~{o}es (MCTI/LNA) do Brasil, the US National Science
-Foundation’s NOIRLab, the University of North Carolina at Chapel Hill
+Foundation's NOIRLab, the University of North Carolina at Chapel Hill
 (UNC), and Michigan State University (MSU).
